### 2019-05-21 Initial_Analysis.Rmd
Methods

---
title: "Initial Analysis"
author: "Juliano Palacios-Abrantes"
date: '2019-02-04'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "cowplot",
  "rgdal",
  "RColorBrewer",
  "knitr",
  "kableExtra",
  "data.table",
  "ggrepel",
  "gridExtra",
  "ggmap",
  "rgeos",
  # "stringr",
  # "stringer",
  "spdep",
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis 
  # "rgdal", #Spatial analysis 
  "tools", #Spatial analysis 
  "png", # For reading plots in chunk codes
  "grid" # For reading plots in chunk codes
)

ipak(packages)

```

# Methods

These are the methods to follow:

1. Determine which countries have neighboring EEZs  
  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify neighboring polygons,
  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the neighboring data
2. Overlap distribution maps with neighbors data  
  2.1. For each species we merged the DBEM_Neighbors data with their known distribution (Gab's data)  
3. Determine transboundary if:  
  3.1. Species is present in both neighboring EEZs by INDEX

Alternatively, we could create a "confidence level" based on a ratio, i.e;
- How many grid cells of both the EEZs is the species present on. A species that covers all cells would have 100% but a species that covers, lets say, all of EEZ1 but only half of EEZ2 would be 75%.  
- Another option is to have the index based on the species distribution. That is to say, what proportion of the total species distribution actually falls within both EEZs....

### Current issues

- How to distinguish between North and South? Example of Brazil, Uruguay and French Guyana

## Data

```{r Speceis_Models, eval = F, echo = T}

# Get the DBEM list of species to extract from other modesl
#GFDL
DBEM_species_G <- data_frame(TaxonKey = list.files("/Volumes/DATA/DATA/DBEM/GFDL26F1"))
#IPSL
DBEM_species_I <- data_frame(TaxonKey = list.files("/Volumes/DATA/DATA/DBEM/IPSL26F1"))
#MPI
DBEM_species_M <- data_frame(TaxonKey = list.files("/Volumes/DATA/DATA/DBEM/MPI26F1"))

# Merge the, and save to send to gabs

DBEM_Species_List <- DBEM_species_I %>% 
  bind_rows(DBEM_species_G,
            DBEM_species_M) %>% 
  group_by(TaxonKey) %>% 
  summarise() %>% 
  filter(str_detect(TaxonKey, "^6"))

# Include species name, as well...

exploited_species <- read.csv("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

DBEM_Species_List <- DBEM_Species_List %>% 
  left_join(exploited_species,
            by ="TaxonKey")

# write.csv(DBEM_Species_List,
#           "DBEM_Species_List.csv",
#           row.names = F)

```

```{r Spatial_Data, eval=T, echo=T, results='hide'}

# Spatial analysis for Countries boundaries from marine regions ####

###_______________________________Read Me_____________________________________________#
#### Data License and references ###
# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
# Flanders Marine Institute (2018). Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10. Available online at http://www.marineregions.org/. https://doi.org/10.14284/312

#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
###________________________________________________________________________________#

# The path
path_world <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/SAU_Shapefile/"
#The File
fnam_world <- "SAUEEZ_July2015.shp"
#Load it!

# World_EEZ <- readOGR(dsn = path_world,
                     # layer =file_path_sans_ext(fnam_world))

World_EEZs <- st_read(dsn = path_world,
                      layer = file_path_sans_ext(fnam_world))

# head(World_EEZs)

#### Grid cell information ####

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam

EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# Species list

# DBEM exploited species list 
# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

# Use thisone for testing 
Selected_Species <- fread("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/List_Species.csv") %>% 
  select(1:2)

```

### Determine which countries are neighbors

```{r Testing_Neighbors, eval=F, echo=T}
# Determine which countries are neighbors

# Method adopted from Adrew Heiss
# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32

# Subset data for testing
South_America <-c("Mexico","Argentina","Chile","Peru","Ecuador","Colombia","Venezuela","Brazil")

South_Americasp <- World_EEZ[World_EEZ@data$Name %in% South_America, ]

#Look for comments in previous chunk

# Get the list using the poly2nb function
Neighbor_List <- poly2nb(South_Americasp)

# Convert te nb data to a Matrix of crossing references
Neighbor_Matrix <- nb2mat(Neighbor_List,
                          style="B", 
                          zero.policy=TRUE)

# Rename the matrix axis
colnames(Neighbor_Matrix) <- rownames(Neighbor_Matrix)

# Get the names of the countries for identifying them
Country_Names <- data_frame(id = row.names(South_Americasp@data),
                            Country_Territory = as.character(South_Americasp@data$Territory1),
                            Neighbor_Territory = Country_Territory)

# Clean up and transform the neighbor matrix
SA_Neighbors <- as.data.frame(Neighbor_Matrix) %>%
  mutate(country = row.names(.)) %>%  # Convert row names to actual column
  gather(neighbor, present, -country) %>%  # Convert to long
  filter(present == 1) %>%  # Only look at cells with a match
  # Add country names
  left_join(select(Country_Names,
                   -Neighbor_Territory), by=c("country" = "id")) %>%
  left_join(select(Country_Names, 
                   -Country_Territory), by=c("neighbor" = "id")) %>% 
  select(4,5) # select final column

head(SA_Neighbors)

# Remove duplicates (e.g. Country A - Country B and Country B - Country A)
### NOTE, I'm going to use the already created one. Load it fiz it and save it with the same name.

SA_Neighbors_Clear <- SA_Neighbors[!duplicated(SA_Neighbors[1:length(SA_Neighbors)]), ]

#### Works beautifully! 
```

```{r Determine_neighbors_Test, eval = F, echo=T}

#### SF package

SAU_Regions <- as.data.frame(unique(World_EEZs$Name))

Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")

# Test_sp <- World_EEZ[World_EEZ@data$Name %in% Test_Countries, ]

Test_sf <- filter(World_EEZs, Name %in% Test_Countries)

# ggplot(Test_sf) +
#   geom_sf() # 5 min

# Adds to the shapefile a column with the neighbourds 
Neighbours_sf <- Test_sf %>%
  mutate(Neighbours = map(.x = geometry, 
                          .f = st_intersects, 
                          y = st_geometry(Test_sf))
         ) %>% 
  st_transform(3832) %>% 
  st_simplify(10000)

head(Neighbours_sf)

```

### Merge Neighbors with DBEM data

```{r Data_Wrangling, eval=T, echo=T, results='hide'}

### Match DBEM list of countries wth Neighbors
Matching_Names <- Neighbours_sf %>% 
  semi_join(EEZIDs_List,
            by ="EEZID") # Only half of them match

head(Matching_Names)

```

```{r Trans_Spp_Function, eval=T,echo=T,warning=F,message=F}

# Function to determine whether or not a species is transboundary

# Varibales needed
# Spp: Species to be abalized, data with presence/absence per gridcell
# Index_EEZ: Reference list of all INDEX that fall within EEZs
# Neighbors: Reference list of all the neighboring EEZs that each country has

# The function
Trans_Spp_Fun <- function(Spp,Index_EEZ,Neighbors){

  Trans_Spp <- Spp %>%
    filter(V1 >= 1) %>% # Filter only presence
    left_join(Index_EEZ,
              by = "INDEX") %>% # Match the species distribution to the Countries EEZs
    group_by(Country_Territory=Name,
             Neighbor_Territory) %>% 
    summarise(N_INDEX = n()) %>% # The number of cells present within each country's EEZ
    mutate(Trans = 1) # Include one transboundary species

  # Result 1. Number of Countries that share the species
  Trans_Spp <- Neighbors %>% 
    left_join(Trans_Spp,
              by = c("Country_Territory","Neighbor_Territory")) %>% 
    mutate_if(is.numeric, funs(replace(., is.na(.),0))) #%>% # Replaces NAs for 0's to sum
    # mutate(Species = ifelse(Trans > 0,paste(Spp[1,2]),NA)) # Includes the species in question

  # Result 2. List of Countries that share the Species ####

  Countries_with_Specie <- Trans_Spp %>% 
    filter(Trans == 1) %>% 
    group_by(Neighbor_Territory) %>% 
    summarise()

# Function Results

  # print(Countries_with_Specie) # Prints the countries that share such species
  return(Trans_Spp) # A dataframe with each country and neighbouring states sharing the species
} # End function

### Testing Function ####
# WORKS!!!!

# Load Species data
# D_Path <- paste("./Data/123",".csv",sep="")

# Reads file
# Species <- read.csv(D_Path)

# Call the function (Works)
# Function_Test <- Trans_Spp_Fun(Species,DBEM_Neighbors_Data,Neighbors);View(Function_Test)

```

```{r World_Trans_Spp, eval=T,echo=T,warning=F,message=F}

World_Trans_Spp <- function(Species_List,Data_Path,Result){

  # Repeat for each species
  for (s in 1:nrow(Species_List)){ # Original code

    # Load species distribution data
    Species_Distribution_Path <- paste(Data_Path,Species_List[s,2],".csv",sep="")

    # Reads file
    Species_Distribution_Data <- read.csv(Species_Distribution_Path)

    # Pastes species name
    Species_Name = Species_List[s,1]

    # Call function to determine transboundary species
    Partial <- Trans_Spp_Fun(Species_Distribution_Data,
                             DBEM_Neighbors_Data,
                             Neighbors) %>% 
      mutate(Species = ifelse(Trans > 0,paste(Species_Name),NA)) # Include species name

    ### Result 1. Numnber of transboundary species by Country ####
    if(s == 1){
      Trans_Country = Partial
    }else{
      Trans_Country[,3] <- Trans_Country[,3] + Partial [,3] # Sum transboundary species
      Trans_Country[,4] <- Trans_Country[,4] + Partial [,4] # Sum Indexes within eez with TS
      Trans_Country[,5] <- ifelse(Trans_Country[,4] >= 0, paste(Trans_Country[,5],Partial[,5], sep=";"),Trans_Country[,5]) # Paste the species that are transboundary
    }

    # Result 2. Number of Countries per Transboundary Species ####

    Countries_with_Specie <- Partial %>% 
      filter(Trans == 1) %>% 
      group_by(Neighbor_Territory) %>% 
      summarise() %>% 
      summarise(Number_EEZ = n(),
                Countries = paste(Neighbor_Territory,
                                  collapse = ";")
      ) %>% # Number of territories in this species
      mutate(Species = Species_Name)

    if(s == 1){
      All_Countries_with_Specie <- Countries_with_Specie
    }else{
      All_Countries_with_Specie <- All_Countries_with_Specie %>% 
        bind_rows(Countries_with_Specie)
    }

  }# Closes species list

  # Function return
  if(Result =="Country"){ # returns results based on countries 
    return(Trans_Country)
  }
  if(Result == "Species"){ # returns results based on species 
    return(All_Countries_with_Specie)
  }
}

### Testing Function ####
# (Works!!!!!!!!)

### Dummy data ###
# SppA <- Julianus_Coor %>% 
#   filter(V1 >= 100000)
# 
# SppB <- Julianus_Coor %>% 
#   filter(V1 <= 100000)

# write.csv(SppB,
#           "456.csv",
#           row.names = F)

Dummy_Species <- data.frame(
  Species = c("SpeciesA","SpeciesB"),
  TaxonKey = c(123,456)
  )

D_Path <- "./Data/"

Function_Test <- World_Trans_Spp(Dummy_Species,D_Path, Result = "Country")

```

```{r Final_Analysis, eval=T, echo=F}

# Varibales needed
# Species_List
# Data_Path

# Data_Path <- Drobo... Gabs... Distributions...
# DBEM_Species <- Selected_Species

# World_Trans_Spp(DBEM_Species,Data_Path)

```

### 2019-05-21 Manuscript_Draft.Rmd
Methods

---
title: "How many fisheries need visas?"
author: "Juliano Palacios Abrantes"
date: "10/4/2018"
output: pdf_document
---

# Introduction

## Fisheries are important
Marine fishes are an important source of food and wealth to million of people worldwide. Just in 2016, fisheries landings were estimated to be 90 million tonnes representing an important source of food security in many developing countries [@SOFIA]. The fishing industry employees XX thousand people worldwide and, combined with trade, generate US$ xxx billion in profits. An important part of these fisheries are cataloged as shared stocks. Shared fish stocks can be classified in two categories [@Bailey:2010ga]; 1) Transboundary, stocks occurring in the EEZs of 2 or more coastal states and 2) Straddling stocks, those occurring in the EEZs of at least one coastal state and the high seas. The management of these stocks differed from each other and from discrete fish stocks (e.g. stocks that only occur within the EEZ of a coastal nation or in the high seas).

## Different ways to classify fisheries according to their distribution

The management of shared fish stocks has been mainly studied trough the lenses of game theory. Since its early work Gordon 1976 blablabla.... Cooperative game... Nash equilibrium... balbalba...

## Lack of information on it

Despite the importance of these stocks and the complex management reflected in years of research we still don't know how many fish stocks are actually transboundary in nations. Previous estimates suggest that there are around 1,500 transboundary fish stocks in the world [@Cady], however, such estimation lacks a proper assessment. Determine the nature of fish stocks (weather or not is a shared resource) can help the proper management of natural resources improving profits [@costello] and food security [@REF] worldwide.

## What we did

In the current paper we aimed to estimate the number of transboundary fished stocks and their contribution to food security and economics of the world. We used the known distribution [@GabsData] of all pelagic and demersal fish stocks listed in the Sea Around Us database [@Zeller] to determine what stocks are likely shared by two or more nations (transboundary), and what stocks are also likely to spend time in the high seas (straddling). Our results suggest that XXX global stocks are transboundary in nature from witch XXX also happen in the high seas. Transboundary stocks represent XX% of total landings and XX% of global revenues.

# Methods

We used the SAU database and filter the pelagic and demersal fish species fished by neighboring countries. We then used the SAU catch data and fishing distribution data to determine the central abundance of the stock. Assuming that this was the center of the distribution of the stock in question, we overlapped the current distribution of each species [@Gabriel] with the current location of coastal states EEZs [@Shapefile]. We used the average distribution (mobility) of each species from the stock abundance center. If the average distribution from the center reached within two or more coastal nations, such species was considered transboundary. IN the other hand, if the species range also included the high seas were classified as straddling.

# Results
# Discussion
# Conclussion
# References

### 2019-05-21 Initial_Analysis.Rmd
Initial methods (quite advanced)

@@
   "readxl", # Read dataframe
+  "data.table", # Read dataframe (Fast!)
   "dplyr", # Data manipulation
@@
   "ggplot2", #Nice grpahs and spatial analysis
-  "cowplot",
-  "rgdal",
-  "RColorBrewer",
-  "knitr",
-  "kableExtra",
-  "data.table",
-  "ggrepel",
-  "gridExtra",
-  "ggmap",
-  "rgeos",
+  # "cowplot",
+  # "rgdal",
+  # "RColorBrewer",
+  # "knitr",
+  # "kableExtra",
+  # "ggrepel",
+  # "gridExtra",
+  # "ggmap",
+  # "rgeos",
   # "stringr",
   # "stringer",
-  "spdep",
+  "spdep", # for poly2nb
   "sf", #Spatial analysis 
@@
   "purrr",#Spatial analysis
-  # "rgdal", #Spatial analysis 
-  "tools", #Spatial analysis 
-  "png", # For reading plots in chunk codes
-  "grid" # For reading plots in chunk codes
+  "rgdal", #Spatial analysis
+  "tools"#, #Spatial analysis 
+  # "png", # For reading plots in chunk codes
+  # "grid" # For reading plots in chunk codes
 )
@@
 
+### Check Gabs Data ####
+
+# Does all data have the same number of files?
+
+SAU <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
+ENM <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/ENM/"))
+Occ <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/Occurence/"))
+
+####### Yes they do! ####
+
 ```
 
-```{r Spatial_Data, eval=T, echo=T, results='hide'}
+```{r Spatial_Data, eval = T, echo = T, results='hide'}
 
@@
 
-# World_EEZ <- readOGR(dsn = path_world,
-                     # layer =file_path_sans_ext(fnam_world))
+World_EEZs <- readOGR(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
 
-World_EEZs <- st_read(dsn = path_world,
-                      layer = file_path_sans_ext(fnam_world))
+# World_EEZs_sf <- st_read(dsn = path_world,
+#                       layer = file_path_sans_ext(fnam_world))
 
@@
 
-# Species list
+#### Estimate the number of grid-cells that each EEZ as
 
-# DBEM exploited species list 
-# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
-
-# Use thisone for testing 
-Selected_Species <- fread("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/List_Species.csv") %>% 
-  select(1:2)
+EEZ_Size <- EEZ_CellID %>% 
+  group_by(EEZID) %>% 
+  summarise(n_grid = n()) %>% 
+  left_join(EEZIDs_List,
+            by = "EEZID")
 
@@
 
-### Determine which countries are neighbors
+## Functions
 
-```{r Testing_Neighbors, eval=F, echo=T}
+### Function `EstNeighbors`
+
+This function determines what EEZs are neighbors and returns a data.frame of it
+
+```{r funEstNeighbors, eval = T, echo=T}
 # Determine which countries are neighbors
@@
 
-# Subset data for testing
-South_America <-c("Mexico","Argentina","Chile","Peru","Ecuador","Colombia","Venezuela","Brazil")
-
-South_Americasp <- World_EEZ[World_EEZ@data$Name %in% South_America, ]
-
-#Look for comments in previous chunk
+EstNeighbors <- function(Shapefile){
 
   # Get the list using the poly2nb function
-Neighbor_List <- poly2nb(South_Americasp)
+  Neighbor_List <- poly2nb(Shapefile)
 
@@
   # Get the names of the countries for identifying them
-Country_Names <- data_frame(id = row.names(South_Americasp@data),
-                            Country_Territory = as.character(South_Americasp@data$Territory1),
-                            Neighbor_Territory = Country_Territory)
+  Country_Names <- data_frame(id = row.names(Shapefile@data),
+                              Country_Territory = as.character(Shapefile@data$Name),
+                              Neighbor_Territory = Country_Territory,
+                              EEZID = Shapefile@data$EEZID
+                              )
 
   # Clean up and transform the neighbor matrix
-SA_Neighbors <- as.data.frame(Neighbor_Matrix) %>%
+  Neighbors <- as.data.frame(Neighbor_Matrix) %>%
     mutate(country = row.names(.)) %>%  # Convert row names to actual column
@@
                      -Country_Territory), by=c("neighbor" = "id")) %>% 
-  select(4,5) # select final column
+    select(EEZID = EEZID.x,Country_Territory,Neighbor_Territory) # select final column
 
-head(SA_Neighbors)
+    # Merge them with SAU data
 
-# Remove duplicates (e.g. Country A - Country B and Country B - Country A)
-### NOTE, I'm going to use the already created one. Load it fiz it and save it with the same name.
+  DBEM_Neighbors_Data <- EEZIDs_List %>% 
+  left_join(EEZ_CellID, 
+            by = "EEZID") %>% # Asign EEZ id to each country
+  left_join(Neighbors, 
+            by = "EEZID") %>% # Include all neighboring countries 
+  filter(Neighbor_Territory != "NA") %>% 
+  left_join(Coor,
+            by = "INDEX") # Inclu
 
-SA_Neighbors_Clear <- SA_Neighbors[!duplicated(SA_Neighbors[1:length(SA_Neighbors)]), ]
+  return(DBEM_Neighbors_Data)
+
+}
+
+### Test function
+
+# Subset data for testing function
+# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
+
+# Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
+# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
+
+# Running function
+# getNeighbors(Test)
 
 #### Works beautifully!
-```
-
-```{r Determine_neighbors_Test, eval = F, echo=T}
-
-#### SF package
-
-SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
-
-Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
-
-# Test_sp <- World_EEZ[World_EEZ@data$Name %in% Test_Countries, ]
-
-Test_sf <- filter(World_EEZs, Name %in% Test_Countries)
-
-# ggplot(Test_sf) +
-#   geom_sf() # 5 min
-
-# Adds to the shapefile a column with the neighbourds 
-Neighbours_sf <- Test_sf %>%
-  mutate(Neighbours = map(.x = geometry, 
-                          .f = st_intersects, 
-                          y = st_geometry(Test_sf))
-         ) %>% 
-  st_transform(3832) %>% 
-  st_simplify(10000)
-
-head(Neighbours_sf)
 
@@
 
-### Merge Neighbors with DBEM data
+### Function `GetSppDist`
 
-```{r Data_Wrangling, eval=T, echo=T, results='hide'}
+This function Read in species distribution from the observation data, ESM models and SAU data, still missing DBEM
 
-### Match DBEM list of countries wth Neighbors
-Matching_Names <- Neighbours_sf %>% 
-  semi_join(EEZIDs_List,
-            by ="EEZID") # Only half of them match
+```{r GetSppDist, eval = T, echo = T}
 
-head(Matching_Names)
+### Notes
+# Function originally created by William (#WC)
+# Juliano modifications (#JC)
+# This funtion is used in estAbdBinTemp.R
+# We are using only summer distribution
+
+### Variables used
+# spplisttemp <- Species list template. Information of the species used in the DBEM under TaxaDataC. 
+# Distpath <- Path to where the initial distribution of the species is. AKA. Files that start with "S"
+
+#### The function
+
+GetSppDist=function(Spp,Model){
+
+  Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/"
+  INDEX <- seq(1,259200,1)
+
+  # SAU Distributions
+  if(Model == "SAU"){
+    File_Name <- paste("SAU_Distribution/DIST_GOOD_SP_")
+  }
+
+  # Occurence
+  if(Model == "Occurence"){
+    File_Name <- paste("Occurence/OCCURENCE_JULIANO_")
+  }
+
+  # ENM Model
+  if(Model == "ENM"){
+    File_Name <- paste("ENM/ENM_JULIANO_")
+  }
+
+  # DBEM Data
+  # if(Model == "DBEM"){
+  #   Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData
+  #   Final_Path <- "ENM"
+  #   File_Name <- paste("ENM_JULIANO",Spp,".mat",sep="")
+  # }
+
+  if(Model == "All"){
+
+    Models_List <- c(paste(Distpath,"SAU_Distribution/DIST_GOOD_SP_",Spp,".mat",sep =""),
+                     paste(Distpath,"Occurence/OCCURENCE_JULIANO_",Spp,".mat",sep=""),
+                     paste(Distpath,"ENM/ENM_JULIANO_",Spp,".mat",sep="")
+    )
+
+    # Jumps species not modeled. NOTE: We only need one as ENM, Occ and SAU Dis have all the same 939 spp
+    if(file.exists(Models_List[1])){
+
+    Load <- lapply(Models_List, FUN=R.matlab::readMat, na.strings=0)
+    sppdist <- as.data.frame(bind_cols(Load))
+    sppdist$INDEX <- INDEX
+    colnames(sppdist) <- c("SAU","Occ","ENM","INDEX")
+
+    getSppDist = sppdist
+
+    }else{
+
+      # print(paste("No info for this species"))
+    }
+
+  }else{
+
+    # Merge paths
+    SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
+
+    if(file.exists(SppPath) == TRUE){
+
+    #Install (if needed) R.matlab package
+    if(!require(R.matlab)){
+      install.packages("R.matlab")
+    }
+
+    # Read Files
+
+    sppdist <- as.data.frame(R.matlab::readMat(SppPath))
+    colnames(sppdist) <- Model
+
+    # Return 
+    getSppDist=sppdist
+
+    }else{
+    print(paste("No info for this species",Spp, "in",Model))
+  }
+
+  }
+}
+
+#______ Test ______#
+
+# Variables outside function
+# head(getSppDist(600004,"SAU")) # Works
+# head(getSppDist(600004,"Occurence")) # Works
+# head(getSppDist(600004,"ENM")) # Works
+# head(getSppDist(600004,"All")) # Works
 
 ```
+
+### Function `EstTransIndex`
 
@@
 # Varibales needed
-# Spp: Species to be abalized, data with presence/absence per gridcell
+# Spp: Species to be analized, data with presence/absence per gridcell
 # Index_EEZ: Reference list of all INDEX that fall within EEZs
-# Neighbors: Reference list of all the neighboring EEZs that each country has
+# EEZ_Size: Number of grid-cells that each EEZ has
+# Neighbors: Reference list of neighbouring countries
+
+# Needs getSppDist
 
 # The function
-Trans_Spp_Fun <- function(Spp,Index_EEZ,Neighbors){
+EstTransIndex <- function(SppDist,EEZ_Size,Neighbors){
 
-  Trans_Spp <- Spp %>%
-    filter(V1 >= 1) %>% # Filter only presence
-    left_join(Index_EEZ,
+  Index_EEZ <- Neighbors %>% 
+    select(INDEX)
+      # Result 1. Number of Countries that share the species
+  # Trans_Index
+
+  Trans_Spp <- SppDist %>%
+    # gather("Model","Value",1:3) %>% 
+    filter(
+      INDEX %in% Index_EEZ$INDEX,
+      # Value != 0
+      SAU != 0
+      ) %>%
+    left_join(Neighbors,
               by = "INDEX") %>% # Match the species distribution to the Countries EEZs
-    group_by(Country_Territory=Name,
-             Neighbor_Territory) %>% 
-    summarise(N_INDEX = n()) %>% # The number of cells present within each country's EEZ
-    mutate(Trans = 1) # Include one transboundary species
-
-  # Result 1. Number of Countries that share the species
-  Trans_Spp <- Neighbors %>% 
-    left_join(Trans_Spp,
-              by = c("Country_Territory","Neighbor_Territory")) %>% 
-    mutate_if(is.numeric, funs(replace(., is.na(.),0))) #%>% # Replaces NAs for 0's to sum
-    # mutate(Species = ifelse(Trans > 0,paste(Spp[1,2]),NA)) # Includes the species in question
+    group_by(Name = Country_Territory,
+             Neighbor_Territory#,
+             # Model
+             ) %>% 
+    summarise(n_spp = n()) %>% # The number of cells present within each country's EEZ
+    left_join(EEZ_Size,
+              by = "Name") %>% 
+    mutate(Trans_Index = n_spp/n_grid) %>%  # Include one transboundary species
+    select(EEZID,everything())  # For the sake of my brain
 
@@
   Countries_with_Specie <- Trans_Spp %>% 
-    filter(Trans == 1) %>% 
+    filter(Trans_Index == 1) %>% 
     group_by(Neighbor_Territory) %>% 
@@
 
-  # print(Countries_with_Specie) # Prints the countries that share such species
-  return(Trans_Spp) # A dataframe with each country and neighbouring states sharing the species
+  EstTransIndex=Trans_Spp # A dataframe with each country and neighbouring states sharing the species
+
 } # End function
@@
 ### Testing Function ####
-# WORKS!!!!
+# SppDist <- Spp_Dist
+# EEZ_Size <- EEZ_Size
+# 
+# Neighbors <- Neighbor_List
 
-# Load Species data
-# D_Path <- paste("./Data/123",".csv",sep="")
+```
 
-# Reads file
-# Species <- read.csv(D_Path)
+# Routine
 
-# Call the function (Works)
-# Function_Test <- Trans_Spp_Fun(Species,DBEM_Neighbors_Data,Neighbors);View(Function_Test)
+```{r Control_Pannel, eval = T, echo = F}
+
+#### TESTING PERIOD ####
+# I'm substetting central america to do the whole analysis (smaller EEZs = faster computation) once I have figure out things I'll run for all
+
+### Data 
+# For now using only the subdata
+
+## Spatial Test Data
+# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
+
+Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
+
+Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
+
+## Species Test Data
+
+# Species list
+
+# DBEM exploited species list 
+exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
+
+SAU_Data <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
+
+#### Species per country
+
+Spps <- SAU_Data %>% 
+  filter(data_layer == "Reconstructed domestic catch") %>% 
+  group_by(area_name,TaxonName = scientific_name) %>% 
+  summarise(n()) %>% 
+  left_join(exploited_species_list,
+            by = "TaxonName")
+
+# TakonKey <- Spps$TaxonKey[1:2]
+TakonKey <- c("600004","600006",600107)
+# Spp = 600988
+TaxonKey <- unique(Spps$TaxonKey)
+
+```
+
+NOTA: Explorando resultados y hay que arrelgar la cuestion de los tres modelos
+
+```{Routine, eval = T, echo = F}
+
+# Step 1; EstNeighbordList 
+Neighbor_List <- EstNeighbors(Test)
+# head(Neighbor_List)
+
+# Step 2; GetSppDist
+# Spp_Dist <- GetSppDist(TakonKey[1],"All")
+# head(Spp_Dist)
+
+# Multiple TaxonKeys
+Spp_Dist <- NULL
+Spp_Dist <- lapply(TaxonKey, FUN = GetSppDist, "All")
+
+Spp_Dist <- Spp_Dist[!sapply(Spp_Dist, is.null)]
+# Step 3; EstTransIndex
+# Spp_Trans <- EstTransIndex(Spp_Dist,EEZ_Size,Neighbor_List)
+# Spp_Trans
+
+# Multiple TaxonKeys
+Spp_Trans <- NULL
+Spp_Trans <- bind_rows(lapply(Spp_Dist, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Neighbors = Neighbor_List))
+
+Spp_Trans %>% 
+  mutate(Uncert = ifelse(Trans_Index >= 0.10 & Trans_Index <= 0.25,"10 %",
+                         ifelse(Trans_Index >= 0.25 & Trans_Index <= 0.50,"25 %",
+                                ifelse(Trans_Index >= 0.50,">50 %","No Trans")))
+         ) %>% 
+  group_by(Name,Uncert) %>% 
+    summarise(nspp=n()) %>% 
+  ggplot(.,
+         aes(
+           x = Name,
+           y = nspp
+         )
+         )+
+  geom_bar(stat ="identity") +
+  facet_wrap(~Uncert)
 

### 2019-05-23 Initial_Analysis.Rmd
Ready to run in Beast

@@
 
-```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}
+```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
   "rgdal", #Spatial analysis
-  "tools"#, #Spatial analysis 
+  "tools", #Spatial analysis 
   # "png", # For reading plots in chunk codes
   # "grid" # For reading plots in chunk codes
+  "parallel" # for parallelization
 )
@@
 
-SAU <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
-ENM <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/ENM/"))
-Occ <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/Occurence/"))
+# SAU <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
+# ENM <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/ENM/"))
+# Occ <- length(list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/Occurence/"))
 
 ####### Yes they do! ####
+
+#### List of species we have data for...
+
+# Removes everything before the number
+Step_One <- gsub(".*_","",list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
+
+# Species List
+Species_List <- gsub("\\..*","",Step_One)
 
@@
   group_by(EEZID) %>% 
-  summarise(n_grid = n()) %>% 
+  summarise(n_tot_grid = n()) %>% 
   left_join(EEZIDs_List,
@@
   # SAU Distributions
-  if(Model == "SAU"){
+  if(Model == "SAU_D"){
     File_Name <- paste("SAU_Distribution/DIST_GOOD_SP_")
+  }
+
+  # SAU Catch
+  if(Model == "SAU_C"){
+    File_Name <- paste("SAU_data_per_species/CATCH_SP_")
   }
@@
     Load <- lapply(Models_List, FUN=R.matlab::readMat, na.strings=0)
-    sppdist <- as.data.frame(bind_cols(Load))
-    sppdist$INDEX <- INDEX
-    colnames(sppdist) <- c("SAU","Occ","ENM","INDEX")
+
+    sppdist <- as.data.frame(bind_cols(Load)) %>% 
+      mutate(
+        INDEX = INDEX,
+        TaxonKey = Spp
+      )
+    colnames(sppdist) <- c("SAU_D","Occ","ENM","INDEX","TaxonKey")
+
+    #### Step for SAU catch data that has to be averaged
+    File_Name <- paste("SAU_data_per_species/CATCH_SP_")
+    SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
+
+    # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
+    SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
+      select(CATCH.56:CATCH.65) %>% 
+      mutate(INDEX = INDEX) %>% 
+      gather("Year","Catch",1:10) %>% # Last 10 years of data
+      group_by(INDEX) %>% 
+      summarise(SAU_C = mean(Catch,na.rm=T))
+
+    # Join both tables
+    sppdist <- sppdist %>% 
+      left_join(SAU_C_data,
+                by = "INDEX") %>% 
+      select(TaxonKey,INDEX,everything())
 
@@
 # Variables outside function
-# head(getSppDist(600004,"SAU")) # Works
-# head(getSppDist(600004,"Occurence")) # Works
-# head(getSppDist(600004,"ENM")) # Works
-# head(getSppDist(600004,"All")) # Works
+# head(GetSppDist(600004,"SAU_D")) # Works
+# head(GetSppDist(600004,"SAU_C")) # Works
+# head(GetSppDist(600004,"Occurence")) # Works
+# head(GetSppDist(600004,"ENM")) # Works
+# head(GetSppDist(600004,"All")) # Works
 
@@
 
-```{r Trans_Spp_Function, eval=T,echo=T,warning=F,message=F}
+```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
 
@@
 # The function
-EstTransIndex <- function(SppDist,EEZ_Size,Neighbors){
+EstTransIndex <- function(Spp,Model,EEZ_Size,Neighbors){
+
+  # Get model data from spps
+  SppDist <- GetSppDist(600004,"All")
 
@@
 
-  Trans_Spp <- SppDist %>%
-    # gather("Model","Value",1:3) %>% 
+  Trans_Spp <- suppressWarnings(SppDist %>%
+    gather("Model","Value",3:6) %>%
     filter(
       INDEX %in% Index_EEZ$INDEX,
-      # Value != 0
-      SAU != 0
+      Value != 0
       ) %>%
@@
     group_by(Name = Country_Territory,
-             Neighbor_Territory#,
-             # Model
+             Neighbor_Territory,
+             TaxonKey,
+             Model
              ) %>% 
-    summarise(n_spp = n()) %>% # The number of cells present within each country's EEZ
+    summarise(n_cells_spp = n()) %>% # The number of cells present within each country's EEZ
     left_join(EEZ_Size,
               by = "Name") %>% 
-    mutate(Trans_Index = n_spp/n_grid) %>%  # Include one transboundary species
-    select(EEZID,everything())  # For the sake of my brain
-
-  # Result 2. List of Countries that share the Species ####
-
-  Countries_with_Specie <- Trans_Spp %>% 
-    filter(Trans_Index == 1) %>% 
-    group_by(Neighbor_Territory) %>% 
-    summarise()
-
-  # Function Results
+    mutate(Trans_Index = n_cells_spp/n_tot_grid) %>%  # Include one transboundary species
+    select(EEZID,everything())
+    ) # For the sake of my brain
 
@@
 ### Testing Function ####
-# SppDist <- Spp_Dist
+# Spp <- 600006
+# Model <- "All"
 # EEZ_Size <- EEZ_Size
-# 
 # Neighbors <- Neighbor_List
@@
 
-# Routine
+## Routine
 
@@
 
-#### TESTING PERIOD ####
+# Removes everything before the number
+Step_One <- gsub(".*_","",list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
+
+# Species List
+Species_List <- gsub("\\..*","",Step_One)
+
+# Set Spceies list
+Exploited_Species <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv") %>% 
+  filter(TaxonKey %in% Species_List)
+
+# For Function
+Exploited_Species_List <- Exploited_Species$TaxonKey
+
+####_________________________________________ TESTING PERIOD_________________________________________####
 # I'm substetting central america to do the whole analysis (smaller EEZs = faster computation) once I have figure out things I'll run for all
@@
 
-## Species Test Data
+## Species Test Data Just to know what's captured in these countries 
+# 
+# SAU_Data <- fread("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
+# # 
+# # #### Species per country
+# # 
+# Spps <- SAU_Data %>%
+#   filter(data_layer == "Reconstructed domestic catch") %>%
+#   group_by(area_name,TaxonName = scientific_name) %>%
+#   summarise(n()) %>%
+#   left_join(Exploited_Species,
+#             by = "TaxonName") %>% 
+#   filter(TaxonKey %in% Exploited_Species_List$TaxonKey)
+# 
+# Exploited_Species_List <- Spps$TaxonKey
 
-# Species list
-
-# DBEM exploited species list 
-exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")
-
-SAU_Data <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
-
-#### Species per country
-
-Spps <- SAU_Data %>% 
-  filter(data_layer == "Reconstructed domestic catch") %>% 
-  group_by(area_name,TaxonName = scientific_name) %>% 
-  summarise(n()) %>% 
-  left_join(exploited_species_list,
-            by = "TaxonName")
-
-# TakonKey <- Spps$TaxonKey[1:2]
-TakonKey <- c("600004","600006",600107)
-# Spp = 600988
-TaxonKey <- unique(Spps$TaxonKey)
+# Exploited_Species <- c("600004","600006",600107)
+# Exploited_Species = 600004
+# TaxonKey <- unique(Spps$TaxonKey)
 
@@
 
-NOTA: Explorando resultados y hay que arrelgar la cuestion de los tres modelos
-
-```{Routine, eval = T, echo = F}
+```{r Routine, eval = F, echo = F}
 
@@
 Neighbor_List <- EstNeighbors(Test)
+# Neighbor_List <- EstNeighbors(World_EEZs)
 # head(Neighbor_List)
 
-# Step 2; GetSppDist
-# Spp_Dist <- GetSppDist(TakonKey[1],"All")
-# head(Spp_Dist)
+# Step 2; EstTransIndex 
+system.time(
+  Spp_Trans <- bind_rows(
+    lapply(
+      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List
+    )
+  )
+)
 
-# Multiple TaxonKeys
-Spp_Dist <- NULL
-Spp_Dist <- lapply(TaxonKey, FUN = GetSppDist, "All")
+```
 
-Spp_Dist <- Spp_Dist[!sapply(Spp_Dist, is.null)]
-# Step 3; EstTransIndex
-# Spp_Trans <- EstTransIndex(Spp_Dist,EEZ_Size,Neighbor_List)
-# Spp_Trans
+```{r Routine_parallel, eval = T, echo = F}
 
-# Multiple TaxonKeys
+# Step 1; EstNeighbordList 
+Neighbor_List <- EstNeighbors(Test)
+# Neighbor_List <- EstNeighbors(World_EEZs)
+# head(Neighbor_List)
+
+# Check number of cores
+n_Cores <- detectCores()
+n_Cores
+
 Spp_Trans <- NULL
-Spp_Trans <- bind_rows(lapply(Spp_Dist, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Neighbors = Neighbor_List))
+
+system.time(
+  Spp_Trans <- bind_rows(
+    mclapply(
+      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List, mc.cores = n_Cores
+    )
+  )
+)
+
+### Save Test
+
+# write.csv(Spp_Trans,
+#           "central_america_trans.csv",
+#           row.names = F)
+# 
+```
+
+# Results
+
+```{r, Trans_Results, eval = F, echo = F}
+
+# Result 1. Number of tran spp per EEZ
 
 Spp_Trans %>% 
-  mutate(Uncert = ifelse(Trans_Index >= 0.10 & Trans_Index <= 0.25,"10 %",
-                         ifelse(Trans_Index >= 0.25 & Trans_Index <= 0.50,"25 %",
-                                ifelse(Trans_Index >= 0.50,">50 %","No Trans")))
+  group_by(Name,TaxonKey) %>% 
+  summarise(Mean_Index = mean(Trans_Index)) %>%  # The higher the less uncertain
+  mutate(Uncert = ifelse(Mean_Index >= 0.50 ,"50 %",
+                         ifelse(Mean_Index >= 0.25 ,"25 %",
+                                ifelse(Mean_Index >= 0.10,">10 %","No Trans")))
          ) %>% 
@@
            x = Name,
-           y = nspp
+           y = nspp#,
+           # fill = Model
          )
@@
 
+# Result 2. List of Countries that share the Species ####
+
+Spp_Trans %>% 
+  group_by(Name,TaxonKey,Neighbor_Territory) %>% 
+  summarise(Mean_Index = mean(Trans_Index)) %>%  # The higher the less uncertain
+  mutate(Uncert = ifelse(Mean_Index >= 0.10 & Mean_Index <= 0.25,"10 %",
+                         ifelse(Mean_Index >= 0.25 & Mean_Index <= 0.50,"25 %",
+                                ifelse(Mean_Index >= 0.50,">50 %","No Trans")))
+         ) %>% 
+    group_by(Name,Neighbor_Territory,Uncert) %>% 
+    summarise(nspp=n())
+
 ```
 
-```{r World_Trans_Spp, eval=T,echo=T,warning=F,message=F}
+```{r World_Trans_Spp, eval = F,echo = T,warning = F,message = F}
 
@@
 
-```{r Final_Analysis, eval=T, echo=F}
+```{r Final_Analysis, eval = F, echo=F}
 

### 2019-05-23 Initial_Analysis.Rmd
Changed proportion to b species bazed

@@
 
-### Notes
-# Function originally created by William (#WC)
-# Juliano modifications (#JC)
-# This funtion is used in estAbdBinTemp.R
-# We are using only summer distribution
-
-### Variables used
-# spplisttemp <- Species list template. Information of the species used in the DBEM under TaxaDataC. 
-# Distpath <- Path to where the initial distribution of the species is. AKA. Files that start with "S"
-
 #### The function
+# NOTES
+# For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
 
@@
   # Get model data from spps
-  SppDist <- GetSppDist(600004,"All")
+  SppDist <- GetSppDist(Spp,Model)
+  # suppressWarnings(
 
+  # Estimate total spp distribution within neighbours
+  Spp_Total_Dist <- SppDist %>%
+    gather("Model","Value",3:6) %>%
+    filter(
+      INDEX %in% Index_EEZ$INDEX,
+      Value != 0
+    ) %>% 
+    # group_by(INDEX) %>% 
+    # summarise(n()) %>% 
+    left_join(Neighbors,
+              by = "INDEX") %>% 
+    group_by(Name = Country_Territory,
+             Neighbor_Territory,
+             Model) %>% 
+    summarise(n_cells_spp = n()) %>% 
+    ungroup()
+
+  # Split dataframes to merge latter
+  Tone <- select(Spp_Total_Dist,1,3,4)
+  Ttwo <- select(Spp_Total_Dist,Name=2,3,4) # Change column name
+
+  # Merge dataframes
+  Merged_data <- merge(Tone,Ttwo, by = c("Name","Model")) %>% 
+    rowwise() %>% 
+    mutate(Total = sum(n_cells_spp.x,n_cells_spp.y)) %>% 
+    select(Name,Model,Total) %>% 
+    left_join(Spp_Total_Dist,
+              by = c("Name","Model")) %>% 
+    select(Name,Model,Total)
+
+  # Get the index for testing
   Index_EEZ <- Neighbors %>% 
     select(INDEX)
+
   # Result 1. Number of Countries that share the species
@@
     summarise(n_cells_spp = n()) %>% # The number of cells present within each country's EEZ
-    left_join(EEZ_Size,
-              by = "Name") %>% 
-    mutate(Trans_Index = n_cells_spp/n_tot_grid) %>%  # Include one transboundary species
-    select(EEZID,everything())
-    ) # For the sake of my brain
+    # Commented out because EEZ size might not be the best
+      # left_join(EEZ_Size,
+    #           by = "Name") %>% 
+      # Trying with the distribution of the speices
+      left_join(Merged_data,
+              by = c("Name","Model")) %>% 
+    mutate(Trans_Index = n_cells_spp/Total) %>%  # Include one transboundary species
+    group_by(Name,Neighbor_Territory,TaxonKey) %>% 
+      summarise(Mean_Trans = mean(Trans_Index))
+    )# Mean of all data
 
@@
 ### Testing Function ####
-# Spp <- 600006
-# Model <- "All"
-# EEZ_Size <- EEZ_Size
-# Neighbors <- Neighbor_List
+Spp <- 600006
+Model <- "All"
+EEZ_Size <- EEZ_Size
+Neighbors <- Neighbor_List
 
@@
 
-Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
+Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras (Pacific)","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
 

### 2019-05-24 Initial_Analysis.Rmd
Ready for first try in THE BEAST

--- 2019-05-23 Initial_Analysis.Rmd
@@
 
-```{r Spatial_Data, eval = T, echo = T, results='hide'}
-
-# Spatial analysis for Countries boundaries from marine regions ####
-
-###_______________________________Read Me_____________________________________________#
-#### Data License and references ###
-# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
-# Flanders Marine Institute (2018).
-Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10.
-Available online at http://www.marineregions.org/.
-https://doi.org/10.14284/312
-
-#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
-###________________________________________________________________________________#
-
-# The path
-path_world <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/SAU_Shapefile/"
-#The File
-fnam_world <- "SAUEEZ_July2015.shp"
-#Load it!
-
-World_EEZs <- readOGR(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-
-# World_EEZs_sf <- st_read(dsn = path_world,
-#                       layer = file_path_sans_ext(fnam_world))
-
-# head(World_EEZs)
-
-#### Grid cell information ####
-
-# List of DBEM INDEX within the EEZ
-#Data provided by Vicki Lam
-
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
-#### Estimate the number of grid-cells that each EEZ as
-
-EEZ_Size <- EEZ_CellID %>% 
-  group_by(EEZID) %>% 
-  summarise(n_tot_grid = n()) %>% 
-  left_join(EEZIDs_List,
-            by = "EEZID")
-
-```
-
 ## Functions
@@
 
-  Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/"
+  Distpath <- paste(Data_Path,"Distribution_Data/",sep="")
   INDEX <- seq(1,259200,1)
@@
     SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
-      select(CATCH.56:CATCH.65) %>% 
+      select(CATCH.1:CATCH.65) %>% 
       mutate(INDEX = INDEX) %>% 
@@
                 by = "INDEX") %>% 
-      select(TaxonKey,INDEX,everything())
+      select(TaxonKey,INDEX,everything()) %>% 
+      gather("Model","Value",3:6) %>%
+      mutate(Value = ifelse(is.na(Value), 0, Value))# Converting NA's to ceros
 
@@
 
+#### NOTES:
+
+##### General:
+- For now using SAU_C as presence absence
+- Grouping by species distribution within EEZ and not EEZ area
+
+##### Tresholds:
+##### Model Index, line ~479
+
+This first treshold estimates the uncertanty of models. Goes from 0 - 1 as follows:
+
+- 1 or 0; All models agree that in the presence of the species
+- 0.75; Three out of four models agree on speices presence
+- 0.50; Two out of four models agree on speices presence
+- 0.25; Only one model flags a speices presence
+- 0; All models agree there is no species there
+
+##### Distribution Index, line ~482
+
 ```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
@@
 # The function
-EstTransIndex <- function(Spp,Model,EEZ_Size,Neighbors){
+EstTransIndex <- function(Spp,Model,Neighbors){
 
   # Get model data from spps
-  SppDist <- GetSppDist(600004,"All")
+  SppDist <- GetSppDist(Spp,Model)
 
+  # Get the index for testing
   Index_EEZ <- Neighbors %>% 
     select(INDEX)
-      # Result 1. Number of Countries that share the species
-  # Trans_Index
 
-  Trans_Spp <- suppressWarnings(SppDist %>%
-    gather("Model","Value",3:6) %>%
-    filter(
-      INDEX %in% Index_EEZ$INDEX,
-      Value != 0
+  # Estimate total spp distribution within neighbours
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Index_EEZ$INDEX) %>% 
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
+    group_by(TaxonKey,
+             INDEX
     ) %>%
+    summarise(Model_Index = mean(Value,na.rm=T)) %>% 
+    filter(Model_Index > 0) %>% 
+    mutate(Model_Index = Model_Index*100) %>% 
     left_join(Neighbors,
-              by = "INDEX") %>% # Match the species distribution to the Countries EEZs
+              by = "INDEX")
+
+  # Estimating total grids per country
+  Spp_Grid <- Trans_Spp %>% 
     group_by(Name = Country_Territory,
              Neighbor_Territory,
+             Model_Index) %>% 
+    summarise(n_cells_spp = n()) %>% 
+    ungroup()
+
+  # Split dataframes to merge latter
+  Tone <- select(Spp_Grid,1,3,4)
+  Ttwo <- select(Spp_Grid,Name=2,3,4) # Change column name
+
+  # Merge dataframes
+  Merged_data <- full_join(Tone,Ttwo, by = c("Name","Model_Index")) %>% 
+    rowwise() %>% 
+    mutate(Spp_Total = sum(n_cells_spp.x,n_cells_spp.y,na.rm=T)) %>% 
+    select(Name,Model_Index,Spp_Total) %>% 
+    left_join(Spp_Grid,
+              by = c("Name","Model_Index")) %>% 
+    ungroup() %>% 
+    group_by(Name,Model_Index) %>% 
+    summarise(Spp_Total = sum(Spp_Total))
+
+  # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
+  Indexes <- Trans_Spp %>% 
+    group_by(Name,
+             Neighbor_Territory,
              TaxonKey,
-             Model
+             Model_Index
     ) %>% 
     summarise(n_cells_spp = n()) %>% # The number of cells present within each country's EEZ
-    left_join(EEZ_Size,
-              by = "Name") %>% 
-    mutate(Trans_Index = n_cells_spp/n_tot_grid) %>%  # Include one transboundary species
-    select(EEZID,everything())
-    ) # For the sake of my brain
+    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 2)_________ #
+    left_join(Merged_data,
+              by = c("Name","Model_Index")) %>% 
+    mutate(Trans_Index = n_cells_spp/Spp_Total)
 
-  EstTransIndex=Trans_Spp # A dataframe with each country and neighbouring states sharing the species
+  ### Save spp dataframe
 
-} # End function
+  if(nrow(Indexes) > 0){
+
+    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
+    Save_Path <- paste(Results_Path,File_Name,sep="")
+
+    write.csv(Indexes,
+              Save_Path,
+              row.names = F)
+
+  }
+
+  ### Function return
+
+  EstTransIndex=Indexes # A dataframe with
+
+}
 
@@
 # Model <- "All"
-# EEZ_Size <- EEZ_Size
 # Neighbors <- Neighbor_List
+
+# Spp <- NULL
+# Model <- NULL
 
@@
 
+#### Set paths for computer ####
+
+# Set paths depending on machine Beas or Hall1000
+if(Sys.info()[7] == "jepa88"){
+  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
+  Path <- paste(Data_Path,"Results/",sep = "")
+}else{
+  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
+  Path <- paste(Data_Path,"Results/",sep = "")
+}
+
+# Path for saving Results
+
+# If path exists overrite it, otherwise creats a new path for that year
+if(file.exists(Path) == TRUE){
+  Results_Path = Path
+}else{
+  dir.create(Path)
+  Results_Path = Path
+}
+
+#### Load Data Needed ####
+
+# Spatial analysis for Countries boundaries from marine regions ####
+
+###_______________________________Read Me_____________________________________________#
+#### Data License and references ###
+# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
+# Flanders Marine Institute (2018).
+Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10.
+Available online at http://www.marineregions.org/.
+https://doi.org/10.14284/312
+
+#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
+###________________________________________________________________________________#
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+#The File
+fnam_world <- "SAUEEZ_July2015.shp"
+#Load it!
+
+World_EEZs <- readOGR(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
+
+#### Grid cell information ####
+
+# List of DBEM INDEX within the EEZ 
+#Data provided by Vicki Lam
+
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# DBEM Coordinate system
+Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+
 # Removes everything before the number
-Step_One <- gsub(".*_","",list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
+Step_One <- gsub(".*_","",list.files(paste(Data_Path,"/Distribution_Data/SAU_Distribution/",sep="")))
 
@@
 # Set Spceies list
-Exploited_Species <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv") %>% 
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>% 
   filter(TaxonKey %in% Species_List)
@@
 
-Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
+# Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras (Pacific)","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
 
-Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
+# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
 
@@
 
-# Exploited_Species <- c("600004","600006",600107)
-# Exploited_Species = 600004
+# Exploited_Species_List <- c(600004,"600006",600107)
+# Exploited_Species_List = 600006
 # TaxonKey <- unique(Spps$TaxonKey)
@@
 # Step 1; EstNeighbordList 
-Neighbor_List <- EstNeighbors(Test)
-# Neighbor_List <- EstNeighbors(World_EEZs)
+Neighbor_List <- EstNeighbors(World_EEZs)
 # head(Neighbor_List)
@@
 
-Spp_Trans <- NULL
+# Spp_Trans <- NULL
 
@@
     mclapply(
-      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List, mc.cores = n_Cores
+      Exploited_Species_List[1], FUN=EstTransIndex, Model = "All", Neighbors = Neighbor_List, mc.cores = n_Cores
     )

### 2019-05-24 Initial_Analysis.Rmd
Small details

@@
   # Get the index for testing
-  Index_EEZ <- Neighbors %>% 
-    select(INDEX)
+  # Index_EEZ <- Neighbors %>% 
+  #   select(INDEX)
 
@@
   Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Index_EEZ$INDEX) %>% 
+    # filter(INDEX %in% Index_EEZ$INDEX) %>% # For testing
     mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence

### 2019-05-25 Initial_Analysis.Rmd
Trying to figure out windows parallel

@@
 
-```{r Routine, eval = F, echo = F}
+```{r Routine_parallel_Windows, eval = F, echo = F}
 
-# Step 1; EstNeighbordList 
-Neighbor_List <- EstNeighbors(Test)
-# Neighbor_List <- EstNeighbors(World_EEZs)
-# head(Neighbor_List)
+## Step 1: Create a cluster of child processes 
+# Check number of cores
+n_Cores <- detectCores()
+n_Cores 
+cl <- makeCluster(n_Cores)
 
-# Step 2; EstTransIndex 
-system.time(
-  Spp_Trans <- bind_rows(
-    lapply(
-      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List
-    )
-  )
-)
+## Step 2: Load the necessary R package(s)
+## N.B. length(cl) is the number of child processes
+##      in the cluster 
+par.setup <- parLapply( cl, 1:length(cl),
+    function(xx) {
+        require(packages) 
+    })
+
+## Step 3: Distribute the necessary R objects 
+clusterExport( cl, c('Neighbor_List') )
+
+## Step 4: Do the computation
+par.output <- parLapply(cl, 1:4,
+    function(xx) {
+       return( EstTransIndex(xx) + Neighbor_List )
+    })
+
+## Step 5: Remember to stop the cluster!
+stopCluster(cl)
 

### 2019-05-28 Initial_Analysis.Rmd
Ran neighbours list and fixed parallel to run in both windows and mac

--- 2019-05-24 Initial_Analysis.Rmd
@@
 
-## Functions
+## Sub Routine Estimating Neighbords
 
-### Function `EstNeighbors`
+### Functions `EstNeighbors`
 
@@
 
-```{r funEstNeighbors, eval = T, echo=T}
+```{r funEstNeighbors, eval = F, echo=T}
 # Determine which countries are neighbors
@@
   # Get the list using the poly2nb function
+
   Neighbor_List <- poly2nb(Shapefile)
@@
   # Get the names of the countries for identifying them
-  Country_Names <- data_frame(id = row.names(Shapefile@data),
+  Country_Names <- tibble(id = row.names(Shapefile@data),
                               Country_Territory = as.character(Shapefile@data$Name),
                               Neighbor_Territory = Country_Territory,
-                              EEZID = Shapefile@data$EEZID
+                              EEZID = Shapefile@data$EEZID # specific of SAU sf
                               )
@@
 #### Works beautifully!
+
+```
+
+## Sub Routine
+
+```{r Neighbords_Control_Pannel, eval = F, echo = F}
+
+#### Load Data Needed ####
+
+# Spatial analysis for Countries boundaries from marine regions ####
+
+###_______________________________Read Me_____________________________________________#
+#### Data License and references ###
+# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
+# Flanders Marine Institute (2018).
+Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10.
+Available online at http://www.marineregions.org/.
+https://doi.org/10.14284/312
+
+#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
+###________________________________________________________________________________#
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
+#The File
+fnam_world <- "SAUEEZ_July2015.shp"
+#Load it!
+
+World_EEZs <- readOGR(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
+
+#### Grid cell information ####
+
+# List of DBEM INDEX within the EEZ 
+#Data provided by Vicki Lam
+
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# DBEM Coordinate system
+Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+
+# Run Function (Ran and saved May 27 2019 at 6pm)
+ system.time(
+  Neighbor_List <- EstNeighbors(World_EEZs)
+ )
+# 8203.05    0.25 8204.51 (around 2 hours 30 min)
+
+write.csv(Neighbor_List,
+          paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""),
+          row.names = F)
+
+####_________________________________________ TESTING PERIOD_________________________________________####
+# I'm substetting central america to do the whole analysis (smaller EEZs = faster computation) once I have figure out things I'll run for all
+
+### Data
+# For now using only the subdata
+
+## Spatial Test Data
+# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
+
+# Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras (Pacific)","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
+
+# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
 
@@
 
-  # Get the index for testing
-  Index_EEZ <- Neighbors %>% 
-    select(INDEX)
-
     # Estimate total spp distribution within neighbours
   Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Index_EEZ$INDEX) %>% 
+    filter(INDEX %in% Neighbors$INDEX) %>% # Filter data only located within EEZs
     mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
@@
 
+```{r Mclapply_Hack_Fun, eval= T , echo = T, warning = F, message = F}
+
+# The hack
+# https://www.r-bloggers.com/implementing-mclapply-on-windows-a-primer-on-embarrassingly-parallel-computation-on-multicore-systems-with-r/
+
+Mclapply_Hack <- function(...){
+    ## Create a cluster
+    size.of.list <- length(list(...)[[1]])
+    cl <- makeCluster(min(size.of.list, detectCores()))
+
+  ## Find out the names of the loaded packages 
+    loaded.package.names <- c(
+        ## Base packages
+        sessionInfo()$basePkgs,
+        ## Additional packages
+        names(sessionInfo()$otherPkgs))
+    tryCatch( {
+
+       ## Copy over all of the objects within scope to
+       ## all clusters. 
+       this.env <- environment()
+       while( identical( this.env, globalenv() ) == FALSE ) {
+           clusterExport(cl,
+                         ls(all.names=TRUE, env=this.env),
+                         envir=this.env)
+           this.env <- parent.env(environment())
+       }
+       clusterExport(cl,
+                     ls(all.names=TRUE, env=globalenv()),
+                     envir=globalenv())
+
+       ## Load the libraries on all the clusters
+       ## N.B. length(cl) returns the number of clusters
+       parLapply( cl, 1:length(cl), function(xx){
+           lapply(loaded.package.names, function(yy) {
+               require(yy , character.only=TRUE)})
+       })
+
+       ## Run the lapply in parallel 
+       return( parLapply( cl, ...) )
+    }, finally = {        
+       ## Stop the cluster
+       stopCluster(cl)
+    })
+}
+
+## Warn the user if they are using Windows
+if( Sys.info()[['sysname']] == 'Windows' ){
+    message(paste(
+      "\n", 
+      "   *** Microsoft Windows detected ***\n",
+      "   \n",
+      "   For technical reasons, the MS Windows version of mclapply()\n",
+      "   is implemented as a serial function instead of a parallel\n",
+      "   function.",
+      "   \n\n",
+      "   As a quick hack, we replace this serial version of mclapply()\n",
+      "   with a wrapper to parLapply() for this R session. Please see\n\n",
+      "     http://www.stat.cmu.edu/~nmv/2014/07/14/implementing-mclapply-on-windows \n\n",
+      "   for details.\n\n"))
+}
+
+## If the OS is Windows, set mclapply to the
+## the hackish version. Otherwise, leave the
+## definition alone. 
+mclapply <- switch( Sys.info()[['sysname']],
+   Windows = {Mclapply_Hack}, 
+   Linux   = {mclapply},
+   Darwin  = {mclapply})
+
+## end mclapply.hack.R
+
+```
+
 ## Routine
@@
 
-#### Load Data Needed ####
-
-# Spatial analysis for Countries boundaries from marine regions ####
-
-###_______________________________Read Me_____________________________________________#
-#### Data License and references ###
-# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
-# Flanders Marine Institute (2018).
-Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10.
-Available online at http://www.marineregions.org/.
-https://doi.org/10.14284/312
-
-#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
-###________________________________________________________________________________#
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-#The File
-fnam_world <- "SAUEEZ_July2015.shp"
-#Load it!
-
-World_EEZs <- readOGR(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-
-#### Grid cell information ####
-
-# List of DBEM INDEX within the EEZ 
-#Data provided by Vicki Lam
-
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
 # Removes everything before the number
@@
 
+# Load neighbours data from previouse routine
+Neighbor_List <- fread(paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""))
+
 ####_________________________________________ TESTING PERIOD_________________________________________####
-# I'm substetting central america to do the whole analysis (smaller EEZs = faster computation) once I have figure out things I'll run for all
-
-### Data
-# For now using only the subdata
-
-## Spatial Test Data
-# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
-
-# Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras (Pacific)","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
-
-# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
-
 ## Species Test Data Just to know what's captured in these countries
@@
 
-# Exploited_Species_List <- c(600004,"600006",600107)
-# Exploited_Species_List = 600006
+# Exploited_Species_List <- c("600006",600107)
+# Exploited_Species_List = 600107
 # TaxonKey <- unique(Spps$TaxonKey)
@@
 
-```{r Routine, eval = F, echo = F}
-
-# Step 1; EstNeighbordList 
-Neighbor_List <- EstNeighbors(Test)
-# Neighbor_List <- EstNeighbors(World_EEZs)
-# head(Neighbor_List)
-
-# Step 2; EstTransIndex 
-system.time(
-  Spp_Trans <- bind_rows(
-    lapply(
-      Exploited_Species_List, FUN=EstTransIndex, EEZ_Size = EEZ_Size, Model = "All", Neighbors = Neighbor_List
-    )
-  )
-)
-
-```
-
 ```{r Routine_parallel, eval = T, echo = F}
-
-# Step 1; EstNeighbordList 
-Neighbor_List <- EstNeighbors(World_EEZs)
-# head(Neighbor_List)
-
-# Check number of cores
-n_Cores <- detectCores()
-n_Cores
 
@@
     mclapply(
-      Exploited_Species_List[1], FUN=EstTransIndex, Model = "All", Neighbors = Neighbor_List, mc.cores = n_Cores
+      Exploited_Species_List[1], fun =EstTransIndex, Model = "All", Neighbors = Neighbor_List
     )
@@
 )
+
+# u ser  system elapsed 
+# 72.20    9.33   91.30
 

### 2019-05-28 Initial_Analysis.Rmd
Fixed coordinates issues, ready to run!

@@
 
-GetSppDist=function(Spp,Model){
+GetSppDist=function(Spp,Model,Coord){
 
   Distpath <- paste(Data_Path,"Distribution_Data/",sep="")
-  INDEX <- seq(1,259200,1)
+  INDEX = seq(1,259200,1)
+  # INDEX <- Coordinates$INDEX
 
@@
   # Occurence
-  if(Model == "Occurence"){
+  if(Model == "Occ"){
     File_Name <- paste("Occurence/OCCURENCE_JULIANO_")
@@
       select(TaxonKey,INDEX,everything()) %>% 
+      left_join(CoorG,
+                by = "INDEX")
+
+    # Fix coordinate system incompatibility between Gab and DBEM
+    sppdist <- suppressWarnings(sppdist[order(sppdist$Latitude, rev(sppdist$Longitude),decreasing=TRUE), ] %>% 
+      mutate(INDEX = seq(1,259200,1)) %>% 
       gather("Model","Value",3:6) %>%
-      mutate(Value = ifelse(is.na(Value), 0, Value))# Converting NA's to ceros
+      mutate(Value = ifelse(is.na(Value), 0, Value)) # Converting NA's to ceros
+    )
 
@@
 
-    sppdist <- as.data.frame(R.matlab::readMat(SppPath))
-    colnames(sppdist) <- Model
+    sppdist <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
+      mutate(INDEX = INDEX,
+             Species = Spp) %>% 
+      left_join(Coord)
+
+    # Fix coordinate system incompatibility between Gab and DBEM
+    sppdist <- sppdist[order(sppdist$Latitude, rev(sppdist$Longitude),decreasing=TRUE), ] %>% 
+      mutate(INDEX = seq(1,259200,1))
 
@@
 
+#### For testing ###
+# Spp <- 600004
+# Model <- "All"
+# Neighbors <- Neighbor_List
+# Coord = CoorG
+# __________________________________
+
 # The function
-EstTransIndex <- function(Spp,Model,Neighbors){
+EstTransIndex <- function(Spp,Model,Neighbors,Coord){
 
   # Get model data from spps
-  SppDist <- GetSppDist(Spp,Model)
+  SppDist <- GetSppDist(Spp,Model,Coord)
 
   # Estimate total spp distribution within neighbours
+
   Trans_Spp <- SppDist %>%
@@
     ) %>%
-    summarise(Model_Index = mean(Value,na.rm=T)) %>% 
+    summarise(Model_Index = mean(Value,na.rm=T)
+              ) %>%
     filter(Model_Index > 0) %>%
@@
 
+# Gabriel's coordinate system
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>% 
+  mutate(INDEX = seq(1,259200,1))
+
 ####_________________________________________ TESTING PERIOD_________________________________________####
@@
     mclapply(
-      Exploited_Species_List[1], fun =EstTransIndex, Model = "All", Neighbors = Neighbor_List
+      Exploited_Species_List[1:3], FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
     )
@@
 
-# u ser  system elapsed 
-# 72.20    9.33   91.30
-
+   # user  system elapsed (For three spp in Hall1000)
+ # 13.430   5.126  35.059 
 ### Save Test
@@
 # 
+```
+
+# Details
+
+## First world Anchovies
+
+In a first run the model suggests anchovies "Engraulis ringens" (600004) is transboundary between US-Mex-Can. I'm exploring this since all four models agree...
+
+Found the probelm, Gab's coordinate system, hecne the data, are in different system than DBEM and SAU data...
+
+```{r Trans_Spp_Function, eval= F ,echo = T,warning = F,message = F}
+
+### DATA EXTRA NEEDED
+
+# DBEM Coordinate system
+Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>% 
+  mutate(INDEX = seq(1,259200,1))
+
+# colnames(CoorG) <- c("INDEX","Longitude","Latitude")
+coords <- CoorG[order(CoorG$Latitude, rev(CoorG$Longitude),decreasing=TRUE), ]
+
+# Explore model step by step
+
+# Get Catch Data
+Anchoveta_Dist <- GetSppDist(600004,"All",CoorG)
+
+Anchoveta_Dist_Coor <- Anchoveta_Dist %>% 
+  left_join(CoorG)
+
+# Swap coordinate system to match DBEM and SAU
+Anchoveta_Dist_Coor_Fix <- Anchoveta_Dist_Coor[order(Anchoveta_Dist_Coor$Latitude, rev(Anchoveta_Dist_Coor$Longitude),decreasing=TRUE), ]
+
+x <- Anchoveta_Dist %>% 
+  left_join(EEZ_CellID) %>% 
+  left_join(EEZIDs_List) %>% 
+  filter(
+    # Model == "Occ",
+    Value >0)
+
+# head(x)
+# Exploring using Vicky's data
+
+ggplot(x) +
+  geom_tile(aes(
+    x = Longitude,
+    y = Latitude,
+    fill = Name,
+    color = Name
+  )
+  ) +
+  facet_wrap(~Model)
+
+Spp_Trans <- bind_rows(
+    mclapply(
+      600004, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
+    )
+  )
+
+  # Estimate total spp distribution within neighbours
+
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Neighbors$INDEX) %>% # Filter data only located within EEZs
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
+    group_by(TaxonKey,
+             INDEX
+    ) %>%
+    summarise(Model_Index = mean(Value,na.rm=T)) %>%
+    filter(Model_Index > 0) %>%
+    mutate(Model_Index = Model_Index*100) %>%
+    left_join(Neighbors,
+              by = "INDEX")
+
+    Test <- Trans_Spp %>% 
+      filter(Name == "USA (West Coast)" & Model_Index ==100)
+
+ # Explore only SAU catch data
+
+# Get Catch Data
+Anchoveta_Dist <- GetSppDist(Spp,"SAU_C")
+
+# Get Mex, Can and USA W coast Grid
+Anchoveta_Dist_EEZ <- Anchoveta_Dist %>%
+
+Anchoveta_NA <-  Anchoveta_Dist%>% 
+  filter(INDEX %in% North_America$INDEX) %>% 
+  gather("Year","Tonnes",CATCH.1:CATCH.65) %>% 
+  group_by(Year) %>% 
+  summarise(Sum_T = sum(Tonnes, na.rm =T))
+
 ```

### 2019-05-28 Initial_Analysis.Rmd
Model Results code

@@
 
-```{r, Trans_Results, eval = F, echo = F}
+```{r Fun_GetTransResults, eval = T}
 
-# Result 1. Number of tran spp per EEZ
+GetTransResults=function(Spp){
 
-Spp_Trans %>% 
-  group_by(Name,TaxonKey) %>% 
-  summarise(Mean_Index = mean(Trans_Index)) %>%  # The higher the less uncertain
-  mutate(Uncert = ifelse(Mean_Index >= 0.50 ,"50 %",
-                         ifelse(Mean_Index >= 0.25 ,"25 %",
-                                ifelse(Mean_Index >= 0.10,">10 %","No Trans")))
-         ) %>% 
-  group_by(Name,Uncert) %>%
-    summarise(nspp=n()) %>%
-  ggplot(.,
-         aes(
-           x = Name,
-           y = nspp#,
-           # fill = Model
-         )
-         )+
-  geom_bar(stat ="identity") +
-  facet_wrap(~Uncert)
+  # Set the path for each file
+  Distpath <- paste(Results_Path,Spp,sep="")
 
-# Result 2. List of Countries that share the Species ####
+  # Loads all files in a df
+  Load_Data <- bind_rows(lapply(Distpath, FUN=fread))
 
-Spp_Trans %>% 
-  group_by(Name,TaxonKey,Neighbor_Territory) %>% 
-  summarise(Mean_Index = mean(Trans_Index)) %>%  # The higher the less uncertain
-  mutate(Uncert = ifelse(Mean_Index >= 0.10 & Mean_Index <= 0.25,"10 %",
-                         ifelse(Mean_Index >= 0.25 & Mean_Index <= 0.50,"25 %",
-                                ifelse(Mean_Index >= 0.50,">50 %","No Trans")))
-         ) %>% 
-    group_by(Name,Neighbor_Territory,Uncert) %>% 
-    summarise(nspp=n())
+  return(Load_Data)
+
+}
 
@@
 
-```{r World_Trans_Spp, eval = F,echo = T,warning = F,message = F}
+## Number of transboundary species per country
 
-World_Trans_Spp <- function(Species_List,Data_Path,Result){
+```{r Load_Data, eval = T}
 
-  # Repeat for each species
-  for (s in 1:nrow(Species_List)){ # Original code
+# Transboundary data
+Spp <- list.files(Results_Path)
+Results_Data <- GetTransResults(Spp)
 
-    # Load species distribution data
-    Species_Distribution_Path <- paste(Data_Path,Species_List[s,2],".csv",sep="")
+# TI of 10% and MI > 50
 
-    # Reads file
-    Species_Distribution_Data <- read.csv(Species_Distribution_Path)
+TenFifty <- Results_Data %>% 
+  filter(Model_Index >= 50,
+         Trans_Index >= 0.10) %>% 
+  group_by(Name,Model_Index) %>% 
+  summarise(n_Trans_Spp = n()) %>% 
+  filter(Model_Index == 50)
+  head(Results_Data)
 
-    # Pastes species name
-    Species_Name = Species_List[s,1]
+# SAU shapefile
 
-    # Call function to determine transboundary species
-    Partial <- Trans_Spp_Fun(Species_Distribution_Data,
-                             DBEM_Neighbors_Data,
-                             Neighbors) %>% 
-      mutate(Species = ifelse(Trans > 0,paste(Species_Name),NA)) # Include species name
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
+#The File
+fnam_world <- "SAUEEZ_July2015.shp"
+#Load it!
 
-    ### Result 1. Numnber of transboundary species by Country ####
-    if(s == 1){
-      Trans_Country = Partial
-    }else{
-      Trans_Country[,3] <- Trans_Country[,3] + Partial [,3] # Sum transboundary species
-      Trans_Country[,4] <- Trans_Country[,4] + Partial [,4] # Sum Indexes within eez with TS
-      Trans_Country[,5] <- ifelse(Trans_Country[,4] >= 0, paste(Trans_Country[,5],Partial[,5], sep=";"),Trans_Country[,5]) # Paste the species that are transboundary
-    }
+World_EEZs <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
 
-    # Result 2. Number of Countries per Transboundary Species ####
+head(World_EEZs)
 
-    Countries_with_Specie <- Partial %>% 
-      filter(Trans == 1) %>% 
-      group_by(Neighbor_Territory) %>% 
-      summarise() %>% 
-      summarise(Number_EEZ = n(),
-                Countries = paste(Neighbor_Territory,
-                                  collapse = ";")
-      ) %>% # Number of territories in this species
-      mutate(Species = Species_Name)
+World_EEZs_simple <- World_EEZs %>% 
+  st_transform(crs = 3832) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% 
+  left_join(TenFifty, by ="Name") %>% 
+  filter(!is.na(n_Trans_Spp)) %>% 
+  st_transform(crs = 4326)
 
-    if(s == 1){
-      All_Countries_with_Specie <- Countries_with_Specie
-    }else{
-      All_Countries_with_Specie <- All_Countries_with_Specie %>% 
-        bind_rows(Countries_with_Specie)
-    }
+head(World_EEZs_simple)
 
-  }# Closes species list
-
-  # Function return
-  if(Result =="Country"){ # returns results based on countries 
-    return(Trans_Country)
-  }
-  if(Result == "Species"){ # returns results based on species 
-    return(All_Countries_with_Specie)
-  }
-}
-
-### Testing Function ####
-# (Works!!!!!!!!)
-
-### Dummy data ###
-# SppA <- Julianus_Coor %>% 
-#   filter(V1 >= 100000)
-# 
-# SppB <- Julianus_Coor %>% 
-#   filter(V1 <= 100000)
-
-# write.csv(SppB,
-#           "456.csv",
-#           row.names = F)
-
-Dummy_Species <- data.frame(
-  Species = c("SpeciesA","SpeciesB"),
-  TaxonKey = c(123,456)
-  )
-
-D_Path <- "./Data/"
-
-Function_Test <- World_Trans_Spp(Dummy_Species,D_Path, Result = "Country")
+ggplot(World_EEZs_simple) +
+  geom_sf(aes(fill = n_Trans_Spp))
 
@@
 
-```{r Final_Analysis, eval = F, echo=F}
-
-# Varibales needed
-# Species_List
-# Data_Path
-
-# Data_Path <- Drobo... Gabs... Distributions...
-# DBEM_Species <- Selected_Species
-
-# World_Trans_Spp(DBEM_Species,Data_Path)
-
+```{r, Trans_Results, eval = F, echo = F}
 ```

### 2019-05-28 Initial_Analysis.Rmd
Include a step to jump already computed species

@@
 
+# Step to run function for species not computed
+Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))
+
+Exploited_Species <- Exploited_Species %>%
+  filter(!TaxonKey %in% Computed_Spp)
+
 # For Function
@@
 
-```{r Routine_parallel, eval = T, echo = F}
+```{r Routine_parallel, eval = F, echo = F}
 
@@
     mclapply(
-      Exploited_Species_List[1:3], FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
+      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
     )
@@
 
-```{r Fun_GetTransResults, eval = T}
+```{r Fun_GetTransResults, eval = F}
 
@@
 
-```{r Load_Data, eval = T}
+```{r Load_Data, eval = F}
 

### 2019-05-29 Initial_Analysis.Rmd
Done first analysis. Next step fix Transboundary Index and include step 3 (if species has been catch at least once in that gridcell)

@@
   "ggplot2", #Nice grpahs and spatial analysis
+  "wesanderson",
   # "cowplot",
@@
 ipak(packages)
+
+ggtheme_map <- function(base_size = 9, Region = "NA") {
+
+  theme(text             = element_text(#family = "Helvetica",
+    color = "gray30", size = base_size),
+    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
+    panel.background = element_blank(),
+    panel.border     = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_line(color = "transparent"),
+    strip.background =element_rect(fill = "transparent"),
+    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
+    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
+    axis.ticks       = element_blank(),
+    axis.text        = element_blank(),
+    axis.title       = element_blank(),
+    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
+    legend.position = "bottom",
+    legend.key.width =unit(6,"line")
+  )
+}
 
@@
 TenFifty <- Results_Data %>% 
-  filter(Model_Index >= 50,
-         Trans_Index >= 0.10) %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
+         ) %>% 
   group_by(Name,Model_Index) %>% 
   summarise(n_Trans_Spp = n()) %>% 
-  filter(Model_Index == 50)
-  head(Results_Data)
+  filter(Model_Index == 100)
+  # head(Results_Data)
 
@@
 path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
-#The File
+# #The File
 fnam_world <- "SAUEEZ_July2015.shp"
-#Load it!
-
+# #Load it!
+# 
 World_EEZs <- st_read(dsn = path_world,
                       layer =file_path_sans_ext(fnam_world))
-
-head(World_EEZs)
+# 
+# head(World_EEZs)
 
 World_EEZs_simple <- World_EEZs %>% 
-  st_transform(crs = 3832) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
   left_join(TenFifty, by ="Name") %>%
-  filter(!is.na(n_Trans_Spp)) %>% 
-  st_transform(crs = 4326)
+  filter(!is.na(n_Trans_Spp)) #%>%
+  # st_transform(crs = 3832)
 
-head(World_EEZs_simple)
+# head(World_EEZs_simple)
 
-ggplot(World_EEZs_simple) +
-  geom_sf(aes(fill = n_Trans_Spp))
+pal <- wes_palette("Zissou1", 100, type = "continuous")
+
+Plot <- ggplot(World_EEZs_simple) +
+  geom_sf(aes(fill = n_Trans_Spp)) +
+  scale_fill_gradientn(colours = pal) +
+  ggtheme_map()
+
+ggsave("MI_100_TI_all_plot.png",
+       plot = Plot,
+       width = 16,
+       height = 8,
+       units = "in",
+       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+)
+
+### Map exploration
+
+# Salvador <- Results_Data %>% 
+#   filter(Name == "El Salvador",
+#          Model_Index >= 50)
+# 
+# Guat_Pac <- Results_Data %>% 
+#   filter(Name == "Guatemala (Pacific)",
+#          Model_Index >= 50)
+
+Spp_Results <- Results_Data %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
+         ) %>% 
+  group_by(TaxonKey,Model_Index) %>% 
+  summarise(n_Trans_Spp = n()/2)
+
+ggplot(Spp_Results) +
+  geom_bar(
+    aes(
+      x = as.character(TaxonKey),
+      y = n_Trans_Spp
+    ),
+    stat = "identity"
+  ) +
+  facet_wrap(~Model_Index,
+             scales = "free")
 

### 2019-07-19 Initial_Analysis.Rmd
Modified code to address issues discussed with Gabriel. Now SAU catch data works as a treshold and area index is fixed

@@
 
+#### Set paths for computer ####
+
+# Set paths depending on machine Beas or Hall1000
+if(Sys.info()[7] == "jepa88"){
+  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
+  Path <- paste(Data_Path,"Results/",sep = "")
+}else{
+  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
+  Path <- paste(Data_Path,"Results/",sep = "")
+}
+
+# Path for saving Results
+
+# If path exists overrite it, otherwise creats a new path for that year
+if(file.exists(Path) == TRUE){
+  Results_Path = Path
+}else{
+  dir.create(Path)
+  Results_Path = Path
+}
+
 ```
@@
 # The function
-EstTransIndex <- function(Spp,Model,Neighbors,Coord){
+EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){
 
@@
 
-  # Estimate total spp distribution within neighbours
-
+  # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
   Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbors$INDEX) %>% # Filter data only located within EEZs
-    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
+    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
+           Model != "SAU_C") %>% # Only using observational and modelled data
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
     group_by(TaxonKey,
@@
     filter(Model_Index > 0) %>%
+    #____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
+    left_join(SppDist,
+              by = c("TaxonKey","INDEX")) %>% 
+    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
+           Value > 0) %>% 
     mutate(Model_Index = Model_Index*100) %>% 
-    left_join(Neighbors,
-              by = "INDEX")
-
-  # Estimating total grids per country
-  Spp_Grid <- Trans_Spp %>% 
-    group_by(Name = Country_Territory,
-             Neighbor_Territory,
-             Model_Index) %>% 
-    summarise(n_cells_spp = n()) %>% 
-    ungroup()
-
-  # Split dataframes to merge latter
-  Tone <- select(Spp_Grid,1,3,4)
-  Ttwo <- select(Spp_Grid,Name=2,3,4) # Change column name
-
-  # Merge dataframes
-  Merged_data <- full_join(Tone,Ttwo, by = c("Name","Model_Index")) %>% 
-    rowwise() %>% 
-    mutate(Spp_Total = sum(n_cells_spp.x,n_cells_spp.y,na.rm=T)) %>% 
-    select(Name,Model_Index,Spp_Total) %>% 
-    left_join(Spp_Grid,
-              by = c("Name","Model_Index")) %>% 
-    ungroup() %>% 
-    group_by(Name,Model_Index) %>% 
-    summarise(Spp_Total = sum(Spp_Total))
-
-  # Result 1. Number of Countries that share the species
-
-  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
-  Indexes <- Trans_Spp %>% 
+    select(-Model, -Value, -Latitude,-Longitude) %>% 
+    left_join(EEZ_CellID,
+              by = "INDEX") %>% 
+    left_join(EEZIDs_List,
+              by = "EEZID")
+
+  # MODEL INDEX (TRESHOLDS 1 & 2) #
+  Model_Index_D <- Trans_Spp %>% 
     group_by(Name,
-             Neighbor_Territory,
              TaxonKey,
@@
     ) %>% 
-    summarise(n_cells_spp = n()) %>% # The number of cells present within each country's EEZ
-    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 2)_________ #
-    left_join(Merged_data,
-              by = c("Name","Model_Index")) %>% 
-    mutate(Trans_Index = n_cells_spp/Spp_Total)
+    summarise(n_cells_spp = n()) %>% 
+    select(-n_cells_spp)
+
+    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
+   # The number of species' cells present within each country's EEZ
+
+  #Step 1.  Get EEZ id and neighbor
+  Neighbors_EEZ <- Neighbors %>% 
+  group_by(EEZID,Country_Territory,Neighbor_Territory) %>% 
+  summarise(n=n()) %>% 
+  ungroup() %>% 
+  select(-n)
+
+  # Step 2. Determines the amount of grids present in each country
+  Spp_Grid <- Trans_Spp %>% 
+    group_by(TaxonKey,Model_Index,EEZID) %>% 
+    summarise(n_spp_eez = length(unique(INDEX))) %>% 
+    left_join(Neighbors_EEZ,
+              by = "EEZID") %>% 
+    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
+           Neighbor_Territory %in% Trans_Spp$Name)
+
+  # Step 3. Sum total grids per neighbors
+
+  # Split dataframes to merge latter
+  Country_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(Model_Index,TaxonKey,Name=Country_Territory,n_spp_eez)
+
+  Neighbor_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(Model_Index,TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory)
+
+  # Merge dataframes to get totals per neighbords
+  Area_Index_D <- full_join(Country_Territory_T,
+                           Neighbor_Territory_T, by = c("Model_Index","Name","TaxonKey")) %>% 
+    rowwise() %>%
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
+    distinct() %>% # Removes false duplicates from `full_join()`
+    rename(Neighbor_Territory = Name,
+           n_spp_Country = n_spp_eez.x,
+           n_spp_Neighbor = n_spp_eez.y) %>% 
+    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
+    select(1:3,6,8)
+
+  #____________ FINAL INDEX TABLE_________ #
+  Indexes <- Model_Index_D %>% 
+  rename(Country_Territory = Name) %>% 
+  full_join(Area_Index_D,
+            by = c("TaxonKey","Country_Territory","Model_Index")
+  ) %>% 
+    filter(!is.na(Area_Index),
+           !is.na(Model_Index)
+           )%>%  # Remove cases where the country does not pass the area_index and viceversa
+    select(TaxonKey,Country_Territory,Neighbor_Territory,everything())
 
@@
 
-  if(nrow(Indexes) > 0){
+  if(nrow(Indexes) > 0 & Save == "Y"){
 
@@
 # Neighbors <- Neighbor_List
+# 
+# Tryout <- EstTransIndex(Spp,Model,Neighbors,CoorG,Save="N")
+# 
+# Over_20 <-Tryout %>% 
+#     filter(Area_Index > 0.20,
+#            Area_Index < 0.80)
 
@@
 
-#### Set paths for computer ####
-
-# Set paths depending on machine Beas or Hall1000
-if(Sys.info()[7] == "jepa88"){
-  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/",sep = "")
-}else{
-  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/",sep = "")
-}
-
-# Path for saving Results
-
-# If path exists overrite it, otherwise creats a new path for that year
-if(file.exists(Path) == TRUE){
-  Results_Path = Path
-}else{
-  dir.create(Path)
-  Results_Path = Path
-}
-
 # Removes everything before the number
@@
   mutate(INDEX = seq(1,259200,1))
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
 
@@
 
-## Number of transboundary species per country
-
 ```{r Load_Data, eval = F}
@@
 
+```
+
+### Problem solving
+
+#### Overcounting transboundary stocks
+
+In a first run, Australia results in many transboundary stocks, I believe this is because it is counting the number of countries that that the species share (e.g.
+one species 6 countries = 6 transboundary spp) rather than 1 speces 6 countries = 1 trans spp.
+
+**Problem fixed.** Now we can estimate the number of transboundary species as well as the number of countries/regions that each country shares per species.
+
+```{Australia_case, eval =F, echo = F}
+
+Australia <- Results_Data %>% 
+  filter(Name == "Australia")
+
+Original_Australia <-Australia %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
+         ) %>% 
+  group_by(Name,Model_Index) %>% 
+  summarise(n_Trans_Spp = n()) %>% 
+  filter(Model_Index == 100)
+
+## Testing the waters
+
+Explore_Australia <- Australia %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
+         ) %>% 
+  slice(1:20) %>% 
+  group_by(Name,Model_Index) %>% 
+  summarise(
+    n_trans = length(unique(TaxonKey)),
+    n_countries = length(unique(Neighbor_Territory)),
+    )
+
+```
+
+#### Fixing counts within EEZs
+
+In the first run. Countries where EEZs are devided but touching (e.g. South Africa inidan and atlantic coasts) are double counted.
+
+This might be fixed with Tayler's data of EEZs to ISOs
+
+```{South_Africa_case, eval =F, echo = F}
+
+# Tyler E.'s' data
+EEZ_ISO <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/EEZID_ISO_TylEd.csv", comment.char="#")
+
+#SAU / Vicky's data
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# Worlds adata
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/World_EEZ_v10_2018",sep="")
+# #The File
+fnam_world <- "eez_v10.shp"
+# #Load it!
+# 
+World_EEZs <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
+
+head(World_EEZs)
+
+World_EEZs %>% 
+  filter(
+    # Territory1 == "South Africa",
+    ISO_Ter1 == "ZAF") %>% 
+  head()
+
+# Get ISO and territory names from world map
+ISO_Ter <- World_EEZs %>%
+  select(ISO_Ter1,Territory1) %>% 
+  as.data.frame() %>% 
+  select(ISO_Ter1,Territory1)
+
+head(ISO_Ter)
+
+# I think EEZID equals ISO when not devided...
+
+EZZID_Yes_ISO <- ISO_Ter %>% 
+  semi_join(ISO_Ter,
+            by ="ISO_Ter1") %>% 
+  rename(Name = Territory1) %>% 
+  # head() %>% 
+  left_join(EEZIDs_List,
+            by = "Name")
+
+EEZ_ISO_Clean <- ISO_Ter %>% 
+  left_join(EEZ_ISO,
+            by = "ISO_Ter1")
+
+SA <- Results_Data %>% 
+  filter(stringr::str_detect(Name,"South Africa"))
+
+```
+
+## Number of transboundary species per country
+
+```{Number_Tran_country, eval =T, echo =F}
 # TI of 10% and MI > 50
@@
   group_by(Name,Model_Index) %>% 
-  summarise(n_Trans_Spp = n()) %>% 
+  summarise(
+    n_trans = length(unique(TaxonKey)),
+    n_countries = length(unique(Neighbor_Territory))
+    ) 
   filter(Model_Index == 100)
@@
 
+  Area_Index_D <- Merged_data %>% 
+    filter(Area_Index > 0.10,
+           Area_Index < 0.90)
+
 Spp_Results <- Results_Data %>% 

### 2019-08-20 Initial_Analysis.Rmd
Updates on results

@@
 
+Clean_Results <- Results_Data %>% 
+  filter(is.na(Trans_Index)) %>% 
+  select(1:5)
+
+length(unique(Clean_Results$TaxonKey))
+
+head(Clean_Results)
 ```
@@
 
-TenFifty <- Results_Data %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
+TenFifty <- Clean_Results %>% 
+  filter(Model_Index == 100,
+         Area_Index >= 0.25,
+         Area_Index <= 0.75
          ) %>% 
-  group_by(Name,Model_Index) %>% 
+  group_by(Name=Country_Territory,Model_Index) %>% 
   summarise(
@@
   st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
-  left_join(TenFifty, by ="Name") %>%
-  filter(!is.na(n_Trans_Spp)) #%>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(TenFifty, by ="Name") #%>%
+  # filter(!is.na(n_trans)) #%>%
   # st_transform(crs = 3832)
@@
 Plot <- ggplot(World_EEZs_simple) +
-  geom_sf(aes(fill = n_Trans_Spp)) +
+  geom_sf(aes(fill = n_trans)) +
   scale_fill_gradientn(colours = pal) +
@@
 
-ggsave("MI_100_TI_all_plot.png",
+ggsave("R2_100_25_Fine_plot.png",
        plot = Plot,

### 2019-08-20 Initial_Analysis.Rmd
Created file to deal with country duplications

@@
     })
-}
 
@@
 
+}
 ## end mclapply.hack.R
@@
 Results_Data <- GetTransResults(Spp)
-
-Clean_Results <- Results_Data %>% 
-  filter(is.na(Trans_Index)) %>% 
-  select(1:5)
-
-length(unique(Clean_Results$TaxonKey))
-
-head(Clean_Results)
+head(Results_Data)
+unique(Results_Data$Model_Index)
+length(unique(Results_Data$TaxonKey)) #672 spp
+
+Clean_Results <- Results_Data
+
 ```
@@
 
-This might be fixed with Tayler's data of EEZs to ISOs
+This might be fixed with Tayler's data of EEZs to ISOs... He did it manually so it does not work!
 
@@
 
+## Creating a subset dataset so i can work on my laptop and not remoteley
+SubsetData <- TenTwenyfive %>% 
+  filter(Name=="USA (East Coast)")
+
+write.csv(SubsetData,
+          "SubsetData.csv",
+          row.names = F)
 ```
@@
 
-```{Number_Tran_country, eval =T, echo =F}
+```{Number_Tran_country, eval =F, echo =F}
 # TI of 10% and MI > 50
 
-TenFifty <- Clean_Results %>% 
+TenTwenyfive <- Clean_Results %>% 
   filter(Model_Index == 100,
@@
     n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbor_Territory))
+    n_countries = length(unique(Neighbor_Territory)),
+    Trans_Rate = n_trans/n_countries
     ) 
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(TenFifty, by ="Name") #%>%
+  left_join(TenTwenyfive, by ="Name") #%>%
   # filter(!is.na(n_trans)) #%>%
@@
 
-ggsave("R2_100_25_Fine_plot.png",
+ggsave("R4_100_25.png",
        plot = Plot,
@@
 
-### Map exploration
-
-# Salvador <- Results_Data %>% 
-#   filter(Name == "El Salvador",
-#          Model_Index >= 50)
-# 
-# Guat_Pac <- Results_Data %>% 
-#   filter(Name == "Guatemala (Pacific)",
-#          Model_Index >= 50)
-
-  Area_Index_D <- Merged_data %>% 
-    filter(Area_Index > 0.10,
-           Area_Index < 0.90)
-
-Spp_Results <- Results_Data %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
-         ) %>% 
-  group_by(TaxonKey,Model_Index) %>% 
-  summarise(n_Trans_Spp = n()/2)
-
-ggplot(Spp_Results) +
-  geom_bar(
-    aes(
-      x = as.character(TaxonKey),
-      y = n_Trans_Spp
-    ),
-    stat = "identity"
-  ) +
-  facet_wrap(~Model_Index,
-             scales = "free")
-
-```
-
-```{r, Trans_Results, eval = F, echo = F}
-```
+```

### 2019-08-20 Initial_Analysis.Rmd
Created file to deal with country duplications

@@
 ## Creating a subset dataset so i can work on my laptop and not remoteley
-SubsetData <- TenTwenyfive %>% 
-  filter(Name=="USA (East Coast)")
-
-write.csv(SubsetData,
-          "SubsetData.csv",
-          row.names = F)
+SubsetData <- TenTwentyFive %>% 
+  filter(Country_Territory=="USA (East Coast)")
+
 ```

### 2019-08-20 Initial_Analysis.Rmd
I think I fixed the duplicate data issue

--- 2019-08-20 Initial_Analysis.Rmd
@@
   Path <- paste(Data_Path,"Results/",sep = "")
+  }
+if(Sys.info()[7] == "carmelia"){
+  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
+  Path <- paste(Data_Path,sep = "")
 }else{
@@
 
-Clean_Results <- Results_Data %>% 
-  filter(is.na(Trans_Index)) %>% 
-  select(1:5)
-
-length(unique(Clean_Results$TaxonKey))
-
-head(Clean_Results)
 ```
@@
 
-TenFifty <- Clean_Results %>% 
-  filter(Model_Index == 100,
-         Area_Index >= 0.25,
-         Area_Index <= 0.75
+TenFifty <- Non_duplicate_Data %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
          ) %>% 
-  group_by(Name=Country_Territory,Model_Index) %>% 
+  group_by(Territory1=fishing_entity,Model_Index) %>% 
   summarise(
@@
     n_countries = length(unique(Neighbor_Territory))
-    ) 
+    ) %>% 
   filter(Model_Index == 100)
@@
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
+path_world <- paste("~/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/World_EEZ_v9_20161021",sep="")
 # #The File
-fnam_world <- "SAUEEZ_July2015.shp"
+fnam_world <- "eez_boundaries.shp"
 # #Load it!
@@
 # 
-# head(World_EEZs)
+head(World_EEZs)
 
@@
   st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(TenFifty, by ="Name") #%>%
-  # filter(!is.na(n_trans)) #%>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
+  left_join(TenFifty, by ="Name") %>%
+  filter(!is.na(n_Trans_Spp)) #%>%
   # st_transform(crs = 3832)
@@
 Plot <- ggplot(World_EEZs_simple) +
-  geom_sf(aes(fill = n_trans)) +
+  geom_sf(aes(fill = n_Trans_Spp)) +
   scale_fill_gradientn(colours = pal) +
@@
 
-ggsave("R2_100_25_Fine_plot.png",
+ggsave("MI_100_TI_all_plot.png",
        plot = Plot,
@@
 
-```{r, Trans_Results, eval = F, echo = F}
-```
+```{r, SOM_Trans_Results, eval = F, echo = F}
+
+Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv") %>% 
+  filter(!is.na(Country_Territory))
+
+sau_eez_fes <- read.csv("~/Desktop/sau_eez_fes.csv")
+
+EEZID_D <- readxl::read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
+
+# Trying to fix EEZ problem...
+
+sau_eez_fes <-sau_eez_fes %>% 
+rename(EEZID = eez_id)
+
+eez_list <- EEZID_D %>% 
+  rename(Country_Territory=Name)
+
+xx <- Clean_Results %>% 
+  left_join(eez_list,
+            by = "Country_Territory") %>% 
+  left_join(sau_eez_fes,
+            by = "EEZID")
+
+Neighbord_Territory_T <- Clean_Results %>% 
+  group_by(Neighbor_Territory) %>% 
+  summarise() %>% 
+  left_join(eez_list_n,
+            by = "Neighbor_Territory") %>% 
+  left_join(sau_eez_fes,
+            by = "EEZID") %>% 
+  select(Neighbor_Territory,neighbor_entity = fishing_entity)
+
+Non_duplicate_Data <- xx %>%   
+  left_join(Neighbord_Territory_T,
+              by ="Neighbor_Territory") %>% 
+  mutate(
+    fishing_entity = ifelse(is.na(fishing_entity),paste(Country_Territory),paste(fishing_entity)),
+    Same_Nation = ifelse(fishing_entity==neighbor_entity,paste("Yes"),"No")
+  ) %>% 
+  filter(Same_Nation == "No")
+
+write.csv(Non_duplicate_Data,
+          "New_Clean_Results.csv")
+
+```

### 2019-08-20 Initial_Analysis.Rmd

@@
 Results_Data <- GetTransResults(Spp)
+head(Results_Data)
+unique(Results_Data$Model_Index)
+length(unique(Results_Data$TaxonKey)) #672 spp
+
+Clean_Results <- Results_Data
 
@@
 
+## Creating a subset dataset so i can work on my laptop and not remoteley
+
+SubsetData <- TenTwenyfive %>% 
+  filter(Name=="USA (East Coast)")
+
+write.csv(SubsetData,
+          "SubsetData.csv",
+          row.names = F)
 ```
@@
 
-```{Number_Tran_country, eval =T, echo =F}
+```{Number_Tran_country, eval =F, echo =F}
 # TI of 10% and MI > 50
 
-TenFifty <- Non_duplicate_Data %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
+TenTwenyfive <- Clean_Results %>% 
+  filter(Model_Index == 100,
+         Area_Index >= 0.25,
+         Area_Index <= 0.75
          ) %>% 
-  group_by(Territory1=fishing_entity,Model_Index) %>% 
+  group_by(Name=Country_Territory,Model_Index) %>% 
   summarise(
     n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbor_Territory))
+    n_countries = length(unique(Neighbor_Territory)),
+    Trans_Rate = n_trans/n_countries
     ) %>% 
@@
   st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
-  left_join(TenFifty, by ="Name") %>%
-  filter(!is.na(n_Trans_Spp)) #%>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(TenTwenyfive, by ="Name") #%>%
+  # filter(!is.na(n_trans)) #%>%
   # st_transform(crs = 3832)
@@
 
-ggsave("MI_100_TI_all_plot.png",
+ggsave("R4_100_25.png",
        plot = Plot,
@@
 )
-
-### Map exploration
-
-# Salvador <- Results_Data %>% 
-#   filter(Name == "El Salvador",
-#          Model_Index >= 50)
-# 
-# Guat_Pac <- Results_Data %>% 
-#   filter(Name == "Guatemala (Pacific)",
-#          Model_Index >= 50)
-
-  Area_Index_D <- Merged_data %>% 
-    filter(Area_Index > 0.10,
-           Area_Index < 0.90)
-
-Spp_Results <- Results_Data %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
-         ) %>% 
-  group_by(TaxonKey,Model_Index) %>% 
-  summarise(n_Trans_Spp = n()/2)
-
-ggplot(Spp_Results) +
-  geom_bar(
-    aes(
-      x = as.character(TaxonKey),
-      y = n_Trans_Spp
-    ),
-    stat = "identity"
-  ) +
-  facet_wrap(~Model_Index,
-             scales = "free")
 

### 2019-08-20 Initial_Analysis.Rmd
Updated subseted data
Just moved the analysis to a proper region

@@
           row.names = F)
+
+###_____________________________ ###
+
+# Loading subsetted data
+
+Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/SubsetData.csv")
+
+sau_eez_fes <- read.csv("~/Desktop/sau_eez_fes.csv")
+
+EEZID_D <- readxl::read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
+
+# Trying to fix EEZ problem...
+
+sau_eez_fes <-sau_eez_fes %>% 
+rename(EEZID = eez_id)
+
+eez_list <- EEZID_D %>% 
+  rename(Country_Territory=Name)
+
+xx <- Clean_Results %>% 
+  left_join(eez_list,
+            by = "Country_Territory") %>% 
+  left_join(sau_eez_fes,
+            by = "EEZID")
+
+Neighbord_Territory_T <- Clean_Results %>% 
+  group_by(Neighbor_Territory) %>% 
+  summarise() %>% 
+  left_join(eez_list_n,
+            by = "Neighbor_Territory") %>% 
+  left_join(sau_eez_fes,
+            by = "EEZID") %>% 
+  select(Neighbor_Territory,neighbor_entity = fishing_entity)
+
+Non_duplicate_Data <- xx %>%   
+  left_join(Neighbord_Territory_T,
+              by ="Neighbor_Territory") %>% 
+  mutate(
+    fishing_entity = ifelse(is.na(fishing_entity),paste(Country_Territory),paste(fishing_entity)),
+    Same_Nation = ifelse(fishing_entity==neighbor_entity,paste("Yes"),"No")
+  ) %>% 
+  filter(Same_Nation == "No")
+
+write.csv(Non_duplicate_Data,
+          "New_Clean_Results.csv")
+
+```
+
 ```
@@
 ```
-
-```{r, SOM_Trans_Results, eval = F, echo = F}
-
-Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv") %>% 
-  filter(!is.na(Country_Territory))
-
-sau_eez_fes <- read.csv("~/Desktop/sau_eez_fes.csv")
-
-EEZID_D <- readxl::read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-
-# Trying to fix EEZ problem...
-
-sau_eez_fes <-sau_eez_fes %>% 
-rename(EEZID = eez_id)
-
-eez_list <- EEZID_D %>% 
-  rename(Country_Territory=Name)
-
-xx <- Clean_Results %>% 
-  left_join(eez_list,
-            by = "Country_Territory") %>% 
-  left_join(sau_eez_fes,
-            by = "EEZID")
-
-Neighbord_Territory_T <- Clean_Results %>% 
-  group_by(Neighbor_Territory) %>% 
-  summarise() %>% 
-  left_join(eez_list_n,
-            by = "Neighbor_Territory") %>% 
-  left_join(sau_eez_fes,
-            by = "EEZID") %>% 
-  select(Neighbor_Territory,neighbor_entity = fishing_entity)
-
-Non_duplicate_Data <- xx %>%   
-  left_join(Neighbord_Territory_T,
-              by ="Neighbor_Territory") %>% 
-  mutate(
-    fishing_entity = ifelse(is.na(fishing_entity),paste(Country_Territory),paste(fishing_entity)),
-    Same_Nation = ifelse(fishing_entity==neighbor_entity,paste("Yes"),"No")
-  ) %>% 
-  filter(Same_Nation == "No")
-
-write.csv(Non_duplicate_Data,
-          "New_Clean_Results.csv")
-
-```

### 2019-08-20 Initial_Analysis.Rmd
Fixed double counting between same-nations eez issue (e.g. USA East coast and USA Gulf of Mexico)

@@
 
+### Message for my brain
+
+print("_____________________ WARNING DO NOT FORGET TO PULL/PUSH BEFORE YOU START_____________________")
+
 ```
@@
 Results_Data <- GetTransResults(Spp)
+
 head(Results_Data)
@@
 
-SubsetData <- TenTwenyfive %>% 
-  filter(Name=="USA (East Coast)")
+SubsetData <- Clean_Results %>% 
+  filter(Country_Territory=="USA (East Coast)")
 
@@
           "SubsetData.csv",
-          row.names = F)
+          row.names = F) # Using USA East coast and Gulf as example
 
@@
 
-sau_eez_fes <- read.csv("~/Desktop/sau_eez_fes.csv")
-
-EEZID_D <- readxl::read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-
-# Trying to fix EEZ problem...
-
-sau_eez_fes <-sau_eez_fes %>% 
-rename(EEZID = eez_id)
-
-eez_list <- EEZID_D %>% 
-  rename(Country_Territory=Name)
-
-xx <- Clean_Results %>% 
-  left_join(eez_list,
-            by = "Country_Territory") %>% 
+sau_eez_fes <- read.csv("~/GitHub/FishForVisa/Temporal_Data/sau_eez_fes.csv")
+
+Neighbord_Territory_T <- Clean_Results %>% 
+  group_by(eez_name=Neighbor_Territory) %>% 
+  summarise() %>%
   left_join(sau_eez_fes,
-            by = "EEZID")
-
-Neighbord_Territory_T <- Clean_Results %>% 
-  group_by(Neighbor_Territory) %>% 
+            by = "eez_name") %>% 
+  select(Neighbor_Territory= eez_name,
+         NT_fishing_entity=fishing_entity
+         )
+
+Country_Territory_T <- Clean_Results %>% 
+  group_by(eez_name=Country_Territory) %>% 
   summarise() %>%
-  left_join(eez_list_n,
-            by = "Neighbor_Territory") %>% 
   left_join(sau_eez_fes,
-            by = "EEZID") %>% 
-  select(Neighbor_Territory,neighbor_entity = fishing_entity)
-
-Non_duplicate_Data <- xx %>%   
+            by = "eez_name")  %>% 
+  select(Country_Territory= eez_name,
+         CT_fishing_entity=fishing_entity)
+
+Non_duplicate_Data <- Clean_Results %>%   
   left_join(Neighbord_Territory_T,
               by ="Neighbor_Territory") %>% 
+  left_join(Country_Territory_T,
+              by ="Country_Territory") %>% 
   mutate(
-    fishing_entity = ifelse(is.na(fishing_entity),paste(Country_Territory),paste(fishing_entity)),
-    Same_Nation = ifelse(fishing_entity==neighbor_entity,paste("Yes"),"No")
+    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
   ) %>% 
@@
 
-write.csv(Non_duplicate_Data,
-          "New_Clean_Results.csv")
-
-```
-
-```
+# FIXED!!!!!
+
+```
+
+- **Done debugging**
 
@@
 ```{Number_Tran_country, eval =F, echo =F}
+
+# Clean out countries that share with their own borders
+
+Neighbord_Territory_T <- Results_Data %>% 
+  group_by(eez_name=Neighbor_Territory) %>% 
+  summarise() %>%
+  left_join(sau_eez_fes,
+            by = "eez_name") %>% 
+  select(Neighbor_Territory= eez_name,
+         NT_fishing_entity=fishing_entity
+         )
+
+Country_Territory_T <- Results_Data %>% 
+  group_by(eez_name=Country_Territory) %>% 
+  summarise() %>%
+  left_join(sau_eez_fes,
+            by = "eez_name")  %>% 
+  select(Country_Territory= eez_name,
+         CT_fishing_entity=fishing_entity)
+
+Clean_Results <- Results_Data %>%   
+  left_join(Neighbord_Territory_T,
+              by ="Neighbor_Territory") %>% 
+  left_join(Country_Territory_T,
+              by ="Country_Territory") %>% 
+  mutate(
+    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
+  ) %>% 
+  filter(Same_Nation == "No")
+
 # TI of 10% and MI > 50

### 2019-08-21 Initial_Analysis.Rmd
Updated analuysis and did some results exploration (de-bugging). Updated function to output all models and non transboundary species

@@
 
-# Set paths depending on machine Beas or Hall1000
+# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
 if(Sys.info()[7] == "jepa88"){
   Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/",sep = "")
+  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
   }
@@
 
+** NOTE THAT THE FUNCTION IS SETTED TO OUTPUT RESULTS FOR LL MODELS **
+
 ##### Distribution Index, line ~482
@@
 
-#### For testing ###
-# Spp <- 600004
+#### For testing 
+# Spp <- 600059
 # Model <- "All"
@@
     mutate(Value = ifelse(Value > 0, 1,0)) %>%  
-    group_by(TaxonKey,
-             INDEX
-    ) %>%
-    summarise(Model_Index = mean(Value,na.rm=T)
-              ) %>%
-    filter(Model_Index > 0) %>%
+    filter(Value > 0) %>%  # Remove latter, just keeps places with 1
+    # Commented out to produce a map for each dataset
+    # group_by(TaxonKey,
+    #          INDEX
+    # ) %>%
+    # summarise(Model_Index = mean(Value,na.rm=T)
+    #           ) %>%
+    # filter(Model_Index > 0) %>%
     #____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
-    left_join(SppDist,
-              by = c("TaxonKey","INDEX")) %>% 
-    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
-           Value > 0) %>% 
-    mutate(Model_Index = Model_Index*100) %>% 
-    select(-Model, -Value, -Latitude,-Longitude) %>% 
+    # left_join(SppDist,
+    #           by = c("TaxonKey","INDEX")) %>% 
+    # filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
+    #        Value > 0) %>%
+    # mutate(Model_Index = Model_Index*100) %>% 
+    # select(-Model, -Value, -Latitude,-Longitude) %>% 
     left_join(EEZ_CellID,
@@
              TaxonKey,
-             Model_Index
+             # Model_Index, # Un-comment after producing models x datasets
+             Model # Remove after producing models x datasets
     ) %>% 
@@
   Spp_Grid <- Trans_Spp %>% 
-    group_by(TaxonKey,Model_Index,EEZID) %>% 
+    group_by(TaxonKey,
+             # Model_Index, # Un-comment after producing models x datasets
+             Model, # Remove after producing models x datasets
+             EEZID) %>% 
     summarise(n_spp_eez = length(unique(INDEX))) %>% 
@@
     ungroup() %>% 
-    select(Model_Index,TaxonKey,Name=Country_Territory,n_spp_eez)
+    select(
+      # Model_Index, # Un-comment after producing models x datasets
+      Model, # Remove after producing models x datasets
+      TaxonKey,Name=Country_Territory,n_spp_eez
+    )
 
@@
     ungroup() %>% 
-    select(Model_Index,TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory)
+    select(
+      # Model_Index,
+      Model, # Remove after producing models x datasets
+      TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory
+    )
 
@@
   Area_Index_D <- full_join(Country_Territory_T,
-                           Neighbor_Territory_T, by = c("Model_Index","Name","TaxonKey")) %>% 
+                           Neighbor_Territory_T, by = c(#"Model_Index",
+                             "Name","TaxonKey","Model")) %>% # Remove Model abd undomment Model_Index after producing Models x datasets
     rowwise() %>%
@@
     mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
-    select(1:3,6,8)
+    # select(1:3,6,8) # Commented out for all models analysis
+    select(1:4,6,8)
 
@@
   full_join(Area_Index_D,
-            by = c("TaxonKey","Country_Territory","Model_Index")
+            by = c("TaxonKey","Country_Territory",
+                   #"Model_Index"
+                   "Model") # Remove Model abd undomment Model_Index after producing Models x datasets
   ) %>% 
-    filter(!is.na(Area_Index),
-           !is.na(Model_Index)
+    filter(!is.na(Area_Index)#,
+           # !is.na(Model_Index) # Uncomment after producing Models x datasets
            )%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(TaxonKey,Country_Territory,Neighbor_Territory,everything())
+    select(Model,TaxonKey,Country_Territory,Neighbor_Territory,everything())
 
@@
               row.names = F)
+
+  }
+
+  if(nrow(Indexes) == 0 & Save == "Y"){
+
+# Reads dataset of Non transboundary species
+    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+
+    # Get current Spp that is not transboundary 
+    Current_Spp <- tibble(Non_trans = Spp)
+
+    # Combine new spp with others
+    New_Non <- Non_Transboundary_Data %>% 
+      bind_rows(Current_Spp)
+
+    # Set a name for file and saves data
+    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
+    write.csv(New_Non, New_Non_Name, row.names = F)
 
@@
 # For Function
-Exploited_Species_List <- Exploited_Species$TaxonKey
+Exploited_Species_List <- Exploited_Species$TaxonKey[1:3]
 
@@
 colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# Creates dummy dataset for Non transboundary species
+write.csv(tibble(Non_trans = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
 
@@
 
-# Details
-
-## First world Anchovies
+# Results
+
+```{r Fun_GetTransResults, eval = F}
+
+GetTransResults=function(Spp){
+
+  # Set the path for each file
+  Distpath <- paste(Results_Path,Spp,sep="")
+
+  # Loads all files in a df
+  Load_Data <- bind_rows(lapply(Distpath, FUN=fread))
+
+  return(Load_Data)
+
+}
+
+```
+
+```{r Load_Data, eval = F}
+
+# Transboundary data
+Spp <- list.files(Results_Path)
+Results_Data <- GetTransResults(Spp)
+
+# Data needed to remove duplicates
+sau_eez_fes <- read.csv(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
+
+Clean_sau_eez_fes <- sau_eez_fes %>% 
+  gather("Type","FishingRegion",2,4) %>% 
+  left_join(sau_eez_fes,
+            by = ("fishing_entity_id")
+            ) %>% 
+  group_by(FishingRegion,fishing_entity) %>% 
+  summarise(n())
+
+# head(Results_Data)
+# unique(Results_Data$Model_Index)
+length(unique(Results_Data$TaxonKey)) #672 spp
+
+# Clean_Results <- Results_Data
+
+# SAU shapefile
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
+fnam_world <- "SAUEEZ_July2015.shp"
+# #Load it!
+# 
+World_EEZs <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
+# 
+# head(World_EEZs)
+
+```
+
+## Number of transboundary species per country
+
+```{Number_Tran_country, eval =F, echo =F}
+
+# Clean out countries that share with their own borders
+
+Clean_Results <- Indexes %>%   
+  rename(FishingRegion=Country_Territory) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "FishingRegion") %>% 
+  select(Model,
+         TaxonKey,
+         Country_Territory= FishingRegion,
+         FishingRegion=Neighbor_Territory,
+         Area_Index,
+         CT_fishing_entity= fishing_entity) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "FishingRegion") %>% 
+  select(#1,2, 
+         Neighbor_Territory = FishingRegion,
+         #Model_Index:CT_fishing_entity,
+         NT_fishing_entity= fishing_entity,
+         everything()
+  ) %>% 
+  mutate(
+    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
+    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
+    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
+  )
+
+# Manually deal with NAs... Ughhhhh
+Results_NA <- Clean_Results %>% 
+  filter(is.na(Same_Nation)) %>% 
+  group_by(Country_Territory,Neighbor_Territory) %>% 
+  summarise(n())
+
+# TI of 10% and MI > 50
+
+TenTwenyfive <- Clean_Results %>% 
+  filter(#Model_Index == 100,
+         Area_Index >= 0.25,
+         Area_Index <= 0.75,
+         Same_Nation == "No"
+         ) %>% 
+  group_by(Name=Country_Territory,Model #,Model_Index
+           ) %>% 
+  summarise(
+    n_trans = length(unique(TaxonKey)),
+    n_countries = length(unique(Neighbor_Territory)),
+    Trans_Rate = n_trans/n_countries
+    ) #%>% 
+  # filter(Model_Index == 100)
+  # head(Results_Data)
+
+World_EEZs_simple <- World_EEZs %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(TenTwenyfive, by ="Name") #%>%
+  # filter(!is.na(n_trans)) #%>%
+  # st_transform(crs = 3832)
+
+# head(World_EEZs_simple)
+# World_EEZs_simple %>% 
+#   filter(Name == "Chile")
+
+pal <- wes_palette("Zissou1", 1000, type = "continuous")
+
+Plot <- ggplot(World_EEZs_simple) +
+  geom_sf(aes(fill = n_trans)) +
+  scale_fill_gradientn(colours = pal,
+                       na.value = "white") +
+  ggtheme_map() +
+  facet_wrap(~Model)
+
+ggsave("R4_100_25.png",
+       plot = Plot,
+       width = 16,
+       height = 8,
+       units = "in",
+       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+)
+
+```
+
+# Problem solving
+
+### First world Anchovies
 
@@
 
-# Results
-
-```{r Fun_GetTransResults, eval = F}
-
-GetTransResults=function(Spp){
-
-  # Set the path for each file
-  Distpath <- paste(Results_Path,Spp,sep="")
-
-  # Loads all files in a df
-  Load_Data <- bind_rows(lapply(Distpath, FUN=fread))
-
-  return(Load_Data)
-
-}
-
-```
-
-```{r Load_Data, eval = F}
-
-# Transboundary data
-Spp <- list.files(Results_Path)
-Results_Data <- GetTransResults(Spp)
-
-head(Results_Data)
-unique(Results_Data$Model_Index)
-length(unique(Results_Data$TaxonKey)) #672 spp
-
-Clean_Results <- Results_Data
-
-```
-
-### Problem solving
-
 #### Overcounting transboundary stocks
@@
 
-## Number of transboundary species per country
-
-```{Number_Tran_country, eval =F, echo =F}
-
-# Clean out countries that share with their own borders
-
-Neighbord_Territory_T <- Results_Data %>% 
-  group_by(eez_name=Neighbor_Territory) %>% 
-  summarise() %>%
+#### Missing stocks
+
+There are places like Peru-Chile or Alaska-Canada that should have trans spp... In Alaska the issue is that Alaska doesn't actually exist as a separate shapefile...
+
+```{r Missing_stocks, eval =F}
+
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
+
+Clean_sau_eez_fes <- sau_eez_fes %>% 
+  gather("Type","FishingRegion",2,4) %>% 
   left_join(sau_eez_fes,
-            by = "eez_name") %>% 
-  select(Neighbor_Territory= eez_name,
-         NT_fishing_entity=fishing_entity
-         )
-
-Country_Territory_T <- Results_Data %>% 
-  group_by(eez_name=Country_Territory) %>% 
-  summarise() %>%
-  left_join(sau_eez_fes,
-            by = "eez_name")  %>% 
-  select(Country_Territory= eez_name,
-         CT_fishing_entity=fishing_entity)
-
-Clean_Results <- Results_Data %>%   
-  left_join(Neighbord_Territory_T,
-              by ="Neighbor_Territory") %>% 
-  left_join(Country_Territory_T,
-              by ="Country_Territory") %>% 
-  mutate(
-    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
+            by = ("fishing_entity_id")
             ) %>% 
-  filter(Same_Nation == "No")
-
-# TI of 10% and MI > 50
-
-TenTwenyfive <- Clean_Results %>% 
-  filter(Model_Index == 100,
-         Area_Index >= 0.25,
-         Area_Index <= 0.75
-         ) %>% 
-  group_by(Name=Country_Territory,Model_Index) %>% 
-  summarise(
-    n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbor_Territory)),
-    Trans_Rate = n_trans/n_countries
-    ) %>% 
-  filter(Model_Index == 100)
-  # head(Results_Data)
-
-# SAU shapefile
-
-# The path
-path_world <- paste("~/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/World_EEZ_v9_20161021",sep="")
-# #The File
-fnam_world <- "eez_boundaries.shp"
-# #Load it!
-# 
-World_EEZs <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-# 
-head(World_EEZs)
-
-World_EEZs_simple <- World_EEZs %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(TenTwenyfive, by ="Name") #%>%
-  # filter(!is.na(n_trans)) #%>%
-  # st_transform(crs = 3832)
-
-# head(World_EEZs_simple)
-
-pal <- wes_palette("Zissou1", 100, type = "continuous")
-
-Plot <- ggplot(World_EEZs_simple) +
-  geom_sf(aes(fill = n_trans)) +
-  scale_fill_gradientn(colours = pal) +
-  ggtheme_map()
-
-ggsave("R4_100_25.png",
-       plot = Plot,
-       width = 16,
-       height = 8,
-       units = "in",
-       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-)
-
-```
+  group_by(FishingRegion,fishing_entity) %>% 
+  summarise(n())
+
+# The Alaska paradox
+# It's a problem of the NAs, fixed.
+
+USA_West <- Results_Data %>% 
+  filter(Country_Territory == "USA (West Coast)") %>% 
+  left_join(Exploited_Species,
+            by = "TaxonKey")
+
+# Northern sea Russia
+Russia_map <- World_EEZs %>% 
+  filter(stringr::str_detect(Name,"Russia")) %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 100)
+
+head(Russia_map)
+
+ggplot(Russia_map) +
+  geom_sf(aes(fill = Name)) 
+# Shapefiles not matching
+# Russia (Laptev to Chukchi Sea)
+# Russia (Kara Sea)
+
+Russian_Regions <- c("Russia (Laptev to Chukchi Sea)","Russia (Kara Sea)")
+
+Russia_Results <- Results_Data %>% 
+  filter(stringr::str_detect(Country_Territory,"Russia"))
+
+unique(Russia_Results$Country_Territory)
+# Missing Laptev to Chukchi sea
+
+### What about Vicky's data
+#SAU / Vicky's data
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+
+Russia_EEZlist <- EEZIDs_List %>% 
+  filter(stringr::str_detect(Name,"Russia"))
+
+unique(Russia_EEZlist$Name)
+
+### So maybe there are no neighbors?
+Neighbor_List <- fread(paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""))
+
+Russia_Neighbor <- Neighbor_List %>% 
+  filter(stringr::str_detect(Name,"Russia"))
+
+unique(Russia_Neighbor$Country_Territory)
+
+# OK So Kara Sea has no borders outside Russia, hence white. Now Laptev does have borders but No species... which is weird... Paific Halibut?
+
+# I manually ran the function to see what's going on
+
+# ggplot() +
+#   geom_sf(data = Russia_map, aes(colour = Name)) +
+#   geom_tile(data = subset(SppDist, Value !=0),
+#             aes(
+#     x = Longitude,
+#     y = Latitude,
+#     fill = log10(Value)
+#   ) 
+#   ) +
+#   facet_wrap(~Model)
+
+# The main issue is that there is no catch data there...
+
+```

### 2019-08-21 Initial_Analysis.Rmd
Changed result path for all models file and included a n_core variable to determine number of cores used in computaion

@@
   Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/",sep = "")
+  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
 }
@@
     size.of.list <- length(list(...)[[1]])
-    cl <- makeCluster(min(size.of.list, detectCores()))
+    n_cores <- detectCores()-6
+    cl <- makeCluster(min(size.of.list, n_cores))
 
@@
 # For Function
-Exploited_Species_List <- Exploited_Species$TaxonKey[1:3]
+Exploited_Species_List <- Exploited_Species$TaxonKey
 

### 2019-08-21 Initial_Analysis.Rmd
Made some ch-ch-ch-changes to script

--- 2019-08-21 Initial_Analysis.Rmd
@@
   Path <- paste(Data_Path,sep = "")
-}else{
+}
+if(Sys.info()[7] == "hall1000"){
   Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
@@
 
-```{r Speceis_Models, eval = F, echo = T}
+```{r Speceis_List_For_Data, eval = F, echo = T}
 
@@
 Species_List <- gsub("\\..*","",Step_One)
+
+# Get All SAU species for the final analysis
 
@@
     size.of.list <- length(list(...)[[1]])
-    cl <- makeCluster(min(size.of.list, detectCores()))
+
+    cl <- makeCluster(min(size.of.list, n_cores))
 
@@
 Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
-  filter(TaxonKey %in% Species_List)
+  filter(!TaxonKey %in% Species_List)
 
@@
 write.csv(tibble(Non_trans = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
+
+# NUmber of cores to us 
+# n_cores <- detectCores()
 
@@
     mclapply(
-      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
-    )
-  )
-)
-
-   # user  system elapsed (For three spp in Hall1000)
- # 13.430   5.126  35.059 
-### Save Test
-
-# write.csv(Spp_Trans,
-#           "central_america_trans.csv",
-#           row.names = F)
-# 
+      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
+    )
+  )
+)
+
 ```
@@
 
-```{r Load_Data, eval = F}
-
-# Transboundary data
-Spp <- list.files(Results_Path)
-Results_Data <- GetTransResults(Spp)
-
-# Data needed to remove duplicates
+```{r Load_Results_Data, eval = F}
+
+# Spatial Data needed to remove duplicates
 sau_eez_fes <- read.csv(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
@@
 
-# head(Results_Data)
-# unique(Results_Data$Model_Index)
-length(unique(Results_Data$TaxonKey)) #672 spp
-
-# Clean_Results <- Results_Data
-
-# SAU shapefile
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-# #The File
-fnam_world <- "SAUEEZ_July2015.shp"
-# #Load it!
-# 
-World_EEZs <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-# 
-# head(World_EEZs)
-
-```
-
-## Number of transboundary species per country
-
-```{Number_Tran_country, eval =F, echo =F}
+# Transboundary Results
+Spp <- list.files(Results_Path)[1:675]
+
+Results_Trans <- GetTransResults(Spp)
 
@@
 
-Clean_Results <- Indexes %>%   
+Clean_Results_Trans <- Results_Trans %>%   
   rename(FishingRegion=Country_Territory) %>% 
@@
 
-# Manually deal with NAs... Ughhhhh
-Results_NA <- Clean_Results %>% 
-  filter(is.na(Same_Nation)) %>% 
-  group_by(Country_Territory,Neighbor_Territory) %>% 
-  summarise(n())
-
-# TI of 10% and MI > 50
+# Load results for non transboundary (discrete) stocks
+Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+
+# SAU shapefile
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
+fnam_world <- "SAUEEZ_July2015.shp"
+# #Load it!
+# 
+World_EEZs <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
+# 
+# head(World_EEZs)
+
+```
+
+```{r Results_Tresholds, eval =F, echo = F}
 
@@
 
+```
+
+## Number of transboundary species per country
+
+```{Tran_country, eval =F, echo =F}
+
+# Number of Transboundary Species
+length(unique(Results_Trans$TaxonKey)) #675 spp
+
+# Number of Discret EEZ species
+length(unique(Results_Discrete$TaxonKey))
+
+```
+
+```{Tran_country_Map, eval =F, echo =F}
+
 World_EEZs_simple <- World_EEZs %>%

### 2019-08-21 Initial_Analysis.Rmd
Included time that took to run model in the Beast
Created a function to do the analysis per dataset

@@
   "wesanderson",
+  "circlize", # For circular plot
   # "cowplot",
@@
 # The function
-EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){
+EstTransIndex_All <- function(Spp,Model,Neighbors,Coord,Save="Y"){
 
@@
     mutate(Value = ifelse(Value > 0, 1,0)) %>%  
-    filter(Value > 0) %>%  # Remove latter, just keeps places with 1
-    # Commented out to produce a map for each dataset
-    # group_by(TaxonKey,
-    #          INDEX
-    # ) %>%
-    # summarise(Model_Index = mean(Value,na.rm=T)
-    #           ) %>%
-    # filter(Model_Index > 0) %>%
-    #____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
-    # left_join(SppDist,
-    #           by = c("TaxonKey","INDEX")) %>% 
-    # filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
-    #        Value > 0) %>%
-    # mutate(Model_Index = Model_Index*100) %>% 
-    # select(-Model, -Value, -Latitude,-Longitude) %>% 
+    filter(Value > 0) %>%
+    group_by(TaxonKey,
+             INDEX
+    ) %>%
+    summarise(Model_Index = mean(Value,na.rm=T)
+              ) %>%
+    filter(Model_Index > 0) %>%
+    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
+    left_join(SppDist,
+              by = c("TaxonKey","INDEX")) %>%
+    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
+           Value > 0) %>%
+    mutate(Model_Index = Model_Index*100) %>%
+    select(-Model, -Value, -Latitude,-Longitude) %>%
     left_join(EEZ_CellID,
@@
              TaxonKey,
-             # Model_Index, # Un-comment after producing models x datasets
-             Model # Remove after producing models x datasets
+             Model
              ) %>% 
@@
     group_by(TaxonKey,
-             # Model_Index, # Un-comment after producing models x datasets
-             Model, # Remove after producing models x datasets
+             Model_Index, # Un-comment after producing models x datasets
              EEZID) %>% 
@@
     select(
-      # Model_Index, # Un-comment after producing models x datasets
-      Model, # Remove after producing models x datasets
-      TaxonKey,Name=Country_Territory,n_spp_eez
+      Model_Index, # Un-comment after producing models x datasets
+      TaxonKey,
+      Name=Country_Territory,
+      n_spp_eez
     )
@@
     select(
-      # Model_Index,
-      Model, # Remove after producing models x datasets
-      TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory
+      Model_Index,
+      TaxonKey,n_spp_eez,
+      Name=Neighbor_Territory, 
+      Country_Territory
     )
@@
   Area_Index_D <- full_join(Country_Territory_T,
-                           Neighbor_Territory_T, by = c(#"Model_Index",
-                             "Name","TaxonKey","Model")) %>% # Remove Model abd undomment Model_Index after producing Models x datasets
+                           Neighbor_Territory_T, 
+                           by = c("Model_Index","Name","TaxonKey")
+                           ) %>%
     rowwise() %>%
@@
     mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
-    # select(1:3,6,8) # Commented out for all models analysis
-    select(1:4,6,8)
+    select(1:3,6,8)
 
@@
   full_join(Area_Index_D,
-            by = c("TaxonKey","Country_Territory",
-                   #"Model_Index"
-                   "Model") # Remove Model abd undomment Model_Index after producing Models x datasets
-  ) %>% 
-    filter(!is.na(Area_Index)#,
-           # !is.na(Model_Index) # Uncomment after producing Models x datasets
+            by = c("TaxonKey","Country_Territory","Model_Index")
+            ) %>% 
+    filter(!is.na(Area_Index),
+           !is.na(Model_Index) # Uncomment after producing Models x datasets
            )%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(Model,TaxonKey,Country_Territory,Neighbor_Territory,everything())
+    select(TaxonKey,Country_Territory,Neighbor_Territory,everything())
 
@@
     # Get current Spp that is not transboundary 
-    Current_Spp <- tibble(Non_trans = Spp)
+    Current_Spp <- tibble(TaxonKey = Spp)
 
@@
 }
-
-### Testing Function ####
-# Spp <- 600006
-# Model <- "All"
-# Neighbors <- Neighbor_List
-# 
-# Tryout <- EstTransIndex(Spp,Model,Neighbors,CoorG,Save="N")
-# 
-# Over_20 <-Tryout %>% 
-#     filter(Area_Index > 0.20,
-#            Area_Index < 0.80)
-
-# Spp <- NULL
-# Model <- NULL
-
 ```
@@
 # Creates dummy dataset for Non transboundary species
-write.csv(tibble(Non_trans = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
+write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
 
@@
 )
+
+# Data on time for the Beast with 30 cores
+# user   system  elapsed 
+ #8117.72  1991.91 10296.00
 
@@
 
+# For Carmelia
+Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
+
 # Load results for non transboundary (discrete) stocks
@@
 
+```{r Circle_Diagram, eval =F, echo = F}
+
+Test_Data <- Clean_Results_Trans %>% 
+  rename(FishingRegion=Country_Territory) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "FishingRegion") %>% 
+  select(TaxonKey,
+         Country_Territory= FishingRegion,
+         FishingRegion=Neighbor_Territory,
+         Model_Index,
+         Area_Index,
+         CT_fishing_entity= fishing_entity) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "FishingRegion") %>% 
+  select(1,2, 
+    Neighbor_Territory = FishingRegion,
+    Model_Index:CT_fishing_entity,
+    NT_fishing_entity = fishing_entity,
+    everything()
+  ) %>% 
+  mutate(
+    # CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
+    # NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
+    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
+  ) %>% 
+  filter(Model_Index == 100,
+         Area_Index >= 0.25,
+         Area_Index <= 0.75,
+         Same_Nation == "No"
+         ) %>% 
+  group_by(from=CT_fishing_entity,
+           to = NT_fishing_entity,
+           Model_Index
+           ) %>% 
+  summarise(value = length(unique(TaxonKey))) %>% 
+  # filter(from %in% c("Chile","Brazil","Argentina","Peru","Equator")) %>%
+  select(from,to,value)
+
+####________________###
+# Circulize package ####
+####________________###
+
+col_mat = rand_color(length(Test_Data), transparency = 0.5)
+col_mat[Test_Data < 10] = "#00000000"
+
+chordDiagram(Test_Data, annotationTrack = "grid")
+
+circos.track(track.index = 1, panel.fun = function(x, y) {
+    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
+        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
+}, bg.border = NA) # here set bg.border to NA is important
+
+```
+
 # Problem solving
@@
 ```
+
+# Extra Analysis
+
+## Extra Analysis; Functions
+
+```{r Trans_Spp_Function_All, eval = F ,echo = T,warning = F,message = F}
+
+# Function to determine whether or not a species is transboundary for each model
+
+# Varibales needed
+# Spp: Species to be analized, data with presence/absence per gridcell
+# Index_EEZ: Reference list of all INDEX that fall within EEZs
+# EEZ_Size: Number of grid-cells that each EEZ has
+# Neighbors: Reference list of neighbouring countries
+
+# Needs getSppDist
+
+#### For testing 
+# Spp <- 600059
+# Model <- "All"
+# Neighbors <- Neighbor_List
+# Coord = CoorG
+# __________________________________
+
+# The function
+EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){
+
+  # Get model data from spps
+  SppDist <- GetSppDist(Spp,Model,Coord)
+
+  # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
+           Model != "SAU_C") %>% # Only using observational and modelled data
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%
+    left_join(EEZ_CellID,
+              by = "INDEX") %>% 
+    left_join(EEZIDs_List,
+              by = "EEZID")
+
+  # MODEL INDEX (TRESHOLDS 1 & 2) #
+  Model_Index_D <- Trans_Spp %>% 
+    group_by(Name,
+             TaxonKey,
+             Model
+    ) %>% 
+    summarise(n_cells_spp = n()) %>% 
+    select(-n_cells_spp)
+
+    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
+   # The number of species' cells present within each country's EEZ
+
+  #Step 1.  Get EEZ id and neighbor
+  Neighbors_EEZ <- Neighbors %>% 
+  group_by(EEZID,Country_Territory,Neighbor_Territory) %>% 
+  summarise(n=n()) %>% 
+  ungroup() %>% 
+  select(-n)
+
+  # Step 2. Determines the amount of grids present in each country
+  Spp_Grid <- Trans_Spp %>% 
+    group_by(TaxonKey,
+             Model, 
+             EEZID) %>% 
+    summarise(n_spp_eez = length(unique(INDEX))) %>% 
+    left_join(Neighbors_EEZ,
+              by = "EEZID") %>% 
+    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
+           Neighbor_Territory %in% Trans_Spp$Name)
+
+  # Step 3. Sum total grids per neighbors
+
+  # Split dataframes to merge latter
+  Country_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index, # Un-comment after producing models x datasets
+      TaxonKey,Name=Country_Territory,n_spp_eez
+    )
+
+  Neighbor_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index,
+      TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory
+    )
+
+  # Merge dataframes to get totals per neighbords
+  Area_Index_D <- full_join(Country_Territory_T,
+                           Neighbor_Territory_T, by = c("Name","TaxonKey","Model")) %>%
+    rowwise() %>%
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
+    distinct() %>% # Removes false duplicates from `full_join()`
+    rename(Neighbor_Territory = Name,
+           n_spp_Country = n_spp_eez.x,
+           n_spp_Neighbor = n_spp_eez.y) %>% 
+    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
+    select(1:4,6,8)
+
+  #____________ FINAL INDEX TABLE_________ #
+  Indexes <- Model_Index_D %>% 
+  rename(Country_Territory = Name) %>% 
+  full_join(Area_Index_D,
+            by = c("TaxonKey","Country_Territory","Model")
+  ) %>% 
+    filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
+    select(Model,TaxonKey,Country_Territory,Neighbor_Territory,everything())
+
+  ### Save spp dataframe
+
+  if(nrow(Indexes) > 0 & Save == "Y"){
+
+    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
+    Save_Path <- paste(Results_Path,"All_Models/",File_Name,sep="")
+
+    write.csv(Indexes,
+              Save_Path,
+              row.names = F)
+
+  }
+
+  if(nrow(Indexes) == 0 & Save == "Y"){
+
+# Reads dataset of Non transboundary species
+    Non_Transboundary_Data <- fread(paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep=""))
+
+    # Get current Spp that is not transboundary 
+    Current_Spp <- tibble(Non_trans = Spp)
+
+    # Combine new spp with others
+    New_Non <- Non_Transboundary_Data %>% 
+      bind_rows(Current_Spp)
+
+    # Set a name for file and saves data
+    New_Non_Name <- paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep="")
+    write.csv(New_Non, New_Non_Name, row.names = F)
+
+  }
+
+  ### Function return
+
+  EstTransIndex=Indexes # A dataframe with
+
+}
+
+### Testing Function ####
+# Spp <- 600006
+# Model <- "All"
+# Neighbors <- Neighbor_List
+# 
+# Tryout <- EstTransIndex(Spp,Model,Neighbors,CoorG,Save="N")
+# 
+# Over_20 <-Tryout %>% 
+#     filter(Area_Index > 0.20,
+#            Area_Index < 0.80)
+
+# Spp <- NULL
+# Model <- NULL
+
+```
+
+## Extra Analysis; Results
+
+```{Tran_country_Map_All, eval =F, echo =F}
+
+World_EEZs_simple <- World_EEZs %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(TenTwenyfive, by ="Name") #%>%
+  # filter(!is.na(n_trans)) #%>%
+  # st_transform(crs = 3832)
+
+# head(World_EEZs_simple)
+# World_EEZs_simple %>% 
+#   filter(Name == "Chile")
+
+pal <- wes_palette("Zissou1", 100, type = "continuous")
+
+Mod <- unique(TenTwenyfive$Model)
+
+# Loop through all variables
+for(v in 1:length(Mod)){
+
+  Model_List <- Mod[v]
+
+  plot <- ggplot(data = subset(World_EEZs_simple,Model %in% Model_List)) +
+    geom_sf(aes(fill = n_trans)) +
+    scale_fill_gradientn(colours = pal,
+                         na.value = "white") +
+    ggtheme_map() +
+    ggtitle(paste(Model_List))
+
+  # Name plot
+  Plot_Name <- paste(Model_List,"plot.png",sep="_")
+
+  # Save plot
+  ggsave(
+    plot = plot,
+    width = 14,
+    height = 10,
+    units = "in",
+    filename = Plot_Name,
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
+  )
+
+  }
+
+```

### 2019-08-21 Initial_Analysis.Rmd
Removed all models from data_path of all computers

@@
   Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
+  Path <- paste(Data_Path,"Results/",sep = "")
   }
@@
 # Spp <- 600059
-# Model <- "All"
-# Neighbors <- Neighbor_List
-# Coord = CoorG
+ #Model <- "All"
+ #Neighbors <- Neighbor_List
+ #Coord = CoorG
 # __________________________________
@@
 # The function
-EstTransIndex_All <- function(Spp,Model,Neighbors,Coord,Save="Y"){
+EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){
 
@@
              TaxonKey,
-             Model
+             Model_Index
     ) %>% 
@@
 Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
-  filter(!TaxonKey %in% Species_List)
+  filter(TaxonKey %in% Species_List)
 
 # Step to run function for species not computed
-Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))
-
-Exploited_Species <- Exploited_Species %>%
-  filter(!TaxonKey %in% Computed_Spp)
+# Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))
+
+# Exploited_Species <- Exploited_Species %>%
+  #filter(!TaxonKey %in% Computed_Spp)
 
 # For Function
-Exploited_Species_List <- Exploited_Species$TaxonKey[1:3]
+Exploited_Species_List <- Exploited_Species$TaxonKey
 
@@
 
-# NUmber of cores to us 
-# n_cores <- detectCores()
+# Number of cores to us 
+n_cores <- detectCores()-8
 
@@
     mclapply(
-      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
+      Exploited_Species_List, FUN = EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
     )

### 2019-08-21 Initial_Analysis.Rmd
small changes

@@
 # Step to run function for species not computed
-# Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))
-
-# Exploited_Species <- Exploited_Species %>%
-  #filter(!TaxonKey %in% Computed_Spp)
+Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))
+
+Exploited_Species <- Exploited_Species %>%
+  filter(!TaxonKey %in% Computed_Spp)
 
@@
 # Number of cores to us 
-n_cores <- detectCores()-8
+n_cores <- detectCores()
 
@@
 # Transboundary Results
-Spp <- list.files(Results_Path)[1:675]
+Spp <- list.files(Results_Path)[1:672]
 
@@
             by = "FishingRegion") %>% 
-  select(Model,
-         TaxonKey,
+  select(TaxonKey,
          Country_Territory= FishingRegion,
          FishingRegion=Neighbor_Territory,
+         Model_Index,
          Area_Index,
@@
             by = "FishingRegion") %>% 
-  select(#1,2, 
+  select(1,2, 
     Neighbor_Territory = FishingRegion,
-    #Model_Index:CT_fishing_entity,
+    Model_Index:CT_fishing_entity,
     NT_fishing_entity= fishing_entity,
-    everything()
-  ) %>% 
+    everything()) %>% 
   mutate(
@@
 # For Carmelia
-Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
+#Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
 

### 2019-08-28 Initial_Analysis.Rmd
Exploring results per species

@@
   # "grid" # For reading plots in chunk codes
-  "parallel" # for parallelization
+  "parallel", # for parallelization
+  "taxize", # For getting species names
+  "rfishbase" # for species ecosystem affinity
 )
@@
 
+# Species list to get species names
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
+Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/SppTaxonName.csv",sep=""))
+
 # Spatial Data needed to remove duplicates
-sau_eez_fes <- read.csv(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
+sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
 
@@
 
-Clean_Results_Trans <- Results_Trans %>%   
+Auto_Remove_Territories <- Results_Trans %>%   
   rename(FishingRegion=Country_Territory) %>% 
@@
 
+#### Manual removal of those left...
+
+# List of territories to eliminate (No other neighobors but mainland)
+Islands_to_Remove <- c(
+  "Brazil (Fernando de Noronha)",
+  "Brazil (St Paul and St. Peter Archipelago)",
+  "Hawaii Main Islands (USA)",
+  "Hawaii Northwest Islands (USA)",
+  "Juan Fernandez Islands (Chile)",
+  "Kermadec Isl. (New Zealand)"
+)
+
+# Complete list of territories to remove from dataset (Including islands)
+
+Territories_to_Remove <- Results_Trans %>% 
+  filter(
+    Country_Territory %in% Islands_to_Remove |
+      Neighbor_Territory %in% Islands_to_Remove |
+      Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
+      Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
+      Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
+      Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
+      Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
+      Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
+      Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
+      Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
+      Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
+      Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
+      Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
+      Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
+      Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
+      Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
+      Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
+      Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
+      Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
+      Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
+      Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
+      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
+      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
+      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
+      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
+      Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
+      Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
+      Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
+      Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
+      Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
+      Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
+      Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
+      Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
+  ) %>%
+  group_by(Country_Territory,Neighbor_Territory) %>% 
+  summarise(n())
+
+# Cleaned results 
+Clean_Results_Trans <- Auto_Remove_Territories %>% 
+  anti_join(Territories_to_Remove,
+            by = c("Country_Territory","Neighbor_Territory")
+  ) %>% 
+  filter(Same_Nation == "No")
+
 # For Carmelia
-#Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
+# Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
 
 # Load results for non transboundary (discrete) stocks
-Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+# Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
 
@@
 
-TenTwenyfive <- Clean_Results %>% 
-  filter(#Model_Index == 100,
-         Area_Index >= 0.25,
-         Area_Index <= 0.75,
+#### Determine transboundary stocks and countries based on selected trsholds ####
+
+#### Select Tresholds ###
+
+# Area Index
+Min_AI <- 0.25 # Min area index
+Max_AI <- 1-Min_AI # Max Area Index
+
+# Model Index
+MI <- 100 # Model Index
+
+####_____End Select Tresholds_______ ###
+
+#### Determine transboundary and non-transboundary species and nations
+
+TenTwenyfive <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index >= Min_AI,
+         Area_Index <= Max_AI,
+         Model_Index == MI,
          Same_Nation == "No"
          ) %>% 
-  group_by(Name=Country_Territory,Model #,Model_Index
-           ) %>% 
+  group_by(Name=Country_Territory) %>% 
   summarise(
@@
     Trans_Rate = n_trans/n_countries
-    ) #%>% 
+    )
   # filter(Model_Index == 100)
@@
 
-```
-
-## Number of transboundary species per country
-
-```{Tran_country, eval =F, echo =F}
-
-# Number of Transboundary Species
-length(unique(Results_Trans$TaxonKey)) #675 spp
-
-# Number of Discret EEZ species
-length(unique(Results_Discrete$TaxonKey))
-
-```
+### Non-transboundary
+
+Non_trans_Area_TenTwenyfive <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No"
+         ) %>% 
+  group_by(Name=Country_Territory) %>% 
+  summarise(
+    n_no_trans = length(unique(TaxonKey)),
+    n_countries = length(unique(Neighbor_Territory))
+  )
+
+```
+
+## Analysis per Country
 
@@
   # st_transform(crs = 3832)
-
-# head(World_EEZs_simple)
-# World_EEZs_simple %>% 
-#   filter(Name == "Chile")
 
@@
 
+## Analysis per Species
+
+```{Tran_country, eval =F, echo =F}
+
+# Number of Transboundary Species
+length(unique(Clean_Results_Trans$TaxonKey)) #664 spp
+
+# Number of Discret EEZ species
+
+# Ge those stocks that are not trans due to Area_Index
+length(unique(Results_Discrete$TaxonKey))
+
+```
+
+```{n_species_country, eval =F, echo =F}
+
+# Number of countries shared by each Species
+Species_Trans <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No"
+         ) %>% 
+  group_by(TaxonKey) %>% 
+  summarise(
+    n_countries = length(unique(Country_Territory))
+  ) %>% 
+  left_join(Exploited_Species) %>%
+  left_join(Spp_Clasification)
+
+hist(Species_Trans$n_countries)
+
+# use taxize to get species family name
+
+Species_family_list <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>% 
+  pull(scientific_name) %>% 
+  tax_name(Species_list, get = "family", db = 'itis')
+
+# Use rfishbase to get species environment
+
+Species_list <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>% 
+  pull(scientific_name)
+
+Species_environ_list <- rbind(species(Species_list, 
+                                      fields = species_fields$habitat[4])
+                              ) %>% 
+  mutate(scientific_name = Species_list)
+
+```
+
+```{n_species_barplot, eval =F, echo =F}
+
+Species_Trans %>% 
+  group_by(Genus,DemPel) %>% 
+  summarise(Countries_Genus = sum(n_countries,na.rm=T)) %>% 
+  mutate(Bins = cut(Countries_Genus, breaks = 5)) %>% 
+  filter(Countries_Genus < 200,
+         !is.na(DemPel)) %>%
+  ggplot(.,
+       aes(
+         x = reorder(Genus,Countries_Genus),
+         y = Countries_Genus,
+         fill = Countries_Genus,
+         colour = Countries_Genus
+       )
+       ) +
+  geom_bar(stat = "identity") +
+  coord_flip() +
+  theme(axis.text.y = element_text(size = 5,
+                               angle = 0,
+                               face = "italic")
+        ) +
+  facet_wrap(~DemPel,
+             scales = "free")
+
+```
+
 # Problem solving

### 2019-08-29 Initial_Analysis.Rmd
Created the circular plot for species to country

@@
   "circlize", # For circular plot
+  "EBImage", #for reading images to the circular plot
   # "cowplot",
@@
   # "kableExtra",
-  # "ggrepel",
+  "ggrepel", # for nice plot labels
   # "gridExtra",
@@
 
+ggtheme_plot <- function() {
+  theme(
+    plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
+    panel.background = element_blank(),
+    strip.background = element_blank(),
+    # strip.text       = element_text(size = base_size, face = "italic"),
+    panel.border     = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_blank(),
+    axis.ticks = element_blank(),
+    axis.text.x = element_text(size = 12,
+                               angle = 0,
+                               face = "plain"),
+    axis.text.y = element_text(size = 12),
+    axis.title = element_text(size = 14),
+    legend.key = element_rect(colour = NA, fill = NA),
+    legend.position  = "right",
+    legend.title = element_text(size = 14),
+    legend.text = element_text(size = 12),
+    strip.text.x = element_text(size = 12, colour = "black"),
+    strip.text = element_text(size = 12)
+  )
+}
+
 #### Set paths for computer ####
@@
   Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/",sep = "")
   }
@@
   Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
-  Path <- paste(Data_Path,sep = "")
 }
@@
   Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
-  Path <- paste(Data_Path,"Results/",sep = "")
-}
+}
+
+# Setting up paths 
+# If path exists overrite it, otherwise creats a new path for that year
 
 # Path for saving Results
-
-# If path exists overrite it, otherwise creats a new path for that year
-if(file.exists(Path) == TRUE){
-  Results_Path = Path
+Results_Path = paste(Data_Path,"Results/",sep = "")
+if(file.exists(Results_Path) == TRUE){
+  Results_Path = paste(Data_Path,"Results/",sep = "")
 }else{
-  dir.create(Path)
-  Results_Path = Path
+  dir.create(paste(Data_Path,"Results/",sep = ""))
+  Results_Path = paste(Data_Path,"Results/",sep = "")
+}
+
+# Path for saving Figures
+Figures_Path = paste(Data_Path,"Figures/",sep = "")
+
+if(file.exists(Figures_Path) == TRUE){
+  Figures_Path = paste(Data_Path,"Figures/",sep = "")
+}else{
+  dir.create(paste(Data_Path,"Figures/",sep = ""))
+  Figures_Path = paste(Data_Path,"Figures/",sep = "")
 }
@@
 
-# Transboundary Results
+# Transboundary Results ####
+
+# For Carmelia
+Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
+
+# For Hall and The Beast
+
 Spp <- list.files(Results_Path)[1:672]
@@
 
-# For Carmelia
-# Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
-
 # Load results for non transboundary (discrete) stocks
@@
 
-```{r Circle_Diagram, eval =F, echo = F}
-
-Test_Data <- Clean_Results_Trans %>% 
-  rename(FishingRegion=Country_Territory) %>% 
-  left_join(Clean_sau_eez_fes,
-            by = "FishingRegion") %>% 
-  select(TaxonKey,
-         Country_Territory= FishingRegion,
-         FishingRegion=Neighbor_Territory,
-         Model_Index,
-         Area_Index,
-         CT_fishing_entity= fishing_entity) %>% 
-  left_join(Clean_sau_eez_fes,
-            by = "FishingRegion") %>% 
-  select(1,2, 
-    Neighbor_Territory = FishingRegion,
-    Model_Index:CT_fishing_entity,
-    NT_fishing_entity = fishing_entity,
-    everything()
-  ) %>% 
-  mutate(
-    # CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
-    # NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
-    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
-  ) %>% 
-  filter(Model_Index == 100,
-         Area_Index >= 0.25,
-         Area_Index <= 0.75,
+```{r Top_country_Circle_Diagram, eval =F, echo = F}
+
+# Top 10 species
+
+# Number of countries shared by each Species
+Top_10_Countries <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
          Same_Nation == "No"
          ) %>% 
+  group_by(Country_Territory) %>% 
+  summarise(
+    n_countries = length(unique(TaxonKey))
+  ) %>% 
+  top_n(10,n_countries)
+
+# Countries that share the top 10
+Top_Ten_Countries <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No",
+         Country_Territory %in% Top_10_Countries$Country_Territory
+         ) %>% 
   group_by(from=CT_fishing_entity,
-           to = NT_fishing_entity,
-           Model_Index
-           ) %>% 
-  summarise(value = length(unique(TaxonKey))) %>% 
-  # filter(from %in% c("Chile","Brazil","Argentina","Peru","Equator")) %>%
-  select(from,to,value)
+           to=NT_fishing_entity
+           ) %>% 
+  summarise(value=n()
+            ) %>% 
+  ungroup() %>% 
+  mutate(from = paste("F", from),
+         to = paste("T", to)
+         )
 
@@
 # Circulize package ####
+# https://jokergoo.github.io/circlize_book/book/
 ####________________###
 
-col_mat = rand_color(length(Test_Data), transparency = 0.5)
-col_mat[Test_Data < 10] = "#00000000"
-
-chordDiagram(Test_Data, annotationTrack = "grid")
-
+# To set links collor 
+Bins <- as.numeric(cut(Top_Ten_Countries$value,breaks = 5))
+
+# Basic plot
+circos.clear()
+chordDiagram(Top_Ten_Countries, 
+             annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
+             annotationTrackHeight = c(0.001, 0.05), # set links close to the axis
+             directional = 1, # direction of arrows
+             direction.type = c("diffHeight", "arrows"), # use arrows
+             grid.col = "white",
+             col = ifelse(Bins == 1,"#046C9A", # deep blue
+                          ifelse(Bins == 2,"#78B7C5", #light blue
+                                 ifelse(Bins == 3,"#EBCC2A", #yellow
+                                        ifelse(Bins == 4, "#E1AF00", #cream
+                                               "#F21A00")))), #red
+             link.arr.col = wes_palette("Zissou1"),
+             link.arr.type = "big.arrow",# make links big arrows
+             diffHeight = uh(1, "mm"), # brings the arrow to the bottom of the source
+             # annotationTrack = "grid", # no labels
+             scale = FALSE, # fraction of total instead of absolute value
+             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Top_Ten_Countries))))) # I have no idea but helps with the labels
+    ) 
+#  Rest of eddits
 circos.track(track.index = 1, panel.fun = function(x, y) {
-    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
-        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
-}, bg.border = NA) # here set bg.border to NA is important
+    xlim = get.cell.meta.data("xlim")
+    xplot = get.cell.meta.data("xplot")
+    ylim = get.cell.meta.data("ylim")
+    sector.name = get.cell.meta.data("sector.index")
+
+    circos.text(mean(xlim),
+                ylim[1], 
+                sector.name, 
+                facing = "clockwise",
+                niceFacing = TRUE,
+                adj = c(-0.2, 0.5),
+                col = "black")
+
+}, bg.border = NA)
 
@@
 
-hist(Species_Trans$n_countries)
-
-# use taxize to get species family name
-
-Species_family_list <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>% 
-  pull(scientific_name) %>% 
-  tax_name(Species_list, get = "family", db = 'itis')
+# hist(Species_Trans$n_countries)
 
@@
 
-```{n_species_barplot, eval =F, echo =F}
-
-Species_Trans %>% 
-  group_by(Genus,DemPel) %>% 
-  summarise(Countries_Genus = sum(n_countries,na.rm=T)) %>% 
-  mutate(Bins = cut(Countries_Genus, breaks = 5)) %>% 
-  filter(Countries_Genus < 200,
-         !is.na(DemPel)) %>%
-  ggplot(.,
+```{habitat_barplot, eval =F, echo =F}
+
+Species_data <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
+  mutate(Distance = ifelse(DemersPelag == "reef-associated", 1,
+                           ifelse(DemersPelag =="pelagic-neritic",2,
+                                  ifelse(DemersPelag == "demersal",3,
+                                         ifelse(DemersPelag == "pelagic-oceanic",4,
+                                                ifelse(DemersPelag =="benthopelagic",5,
+                                                       ifelse(DemersPelag =="bathypelagic",6,
+                                                              ifelse(DemersPelag =="bathydemersal",7,
+                                                                     8)))))))
+  ) %>% 
+  group_by(DemersPelag,Distance) %>% 
+  summarise(Countries_Genus = sum(n_countries,na.rm=T),
+            Mean_Countries_Genus = mean(n_countries,na.rm=T),
+            sd_Countries_Genus = sd(n_countries,na.rm=T),
+            N_spp =length(unique(TaxonName))
+  )
+
+ggplot(Species_data,
        aes(
-         x = reorder(Genus,Countries_Genus),
-         y = Countries_Genus,
-         fill = Countries_Genus,
-         colour = Countries_Genus
+         x = reorder(DemersPelag,desc(Distance)),
+         y = Mean_Countries_Genus,
+         fill = Countries_Genus#,
+         # colour = Countries_Genus
        )
@@
   geom_bar(stat = "identity") +
+  # geom_errorbar(data = Species_data,
+  #               aes(
+  #                 x = reorder(DemersPelag,desc(Distance)),
+  #                 ymin=Mean_Countries_Genus-sd_Countries_Genus, # mean +- 2*sd
+  #                 ymax=Mean_Countries_Genus+sd_Countries_Genus
+  #               ),
+  #               colour = "black",
+  #               width=.2,
+  #               linetype = 2,
+  #               size = 0.6,
+  #               alpha = 0.5
+  # ) +
+  geom_text(data = Species_data, 
+            aes(
+              x = reorder(DemersPelag,desc(Distance)),
+              y = 2,
+              label = paste(as.character(N_spp), "species"),
+            ),
+            colour = "black"
+  ) +
   coord_flip() +
-  theme(axis.text.y = element_text(size = 5,
-                               angle = 0,
-                               face = "italic")
+  scale_fill_gradientn("Total number\nof countries",
+                       colours = wes_palette("Zissou1"),
+                       limits = c(0,1500),
+                       breaks = seq(0,1500,250)
   ) +
-  facet_wrap(~DemPel,
-             scales = "free")
+  scale_colour_gradientn("Total number\nof countries",
+                         colours = wes_palette("Zissou1"),
+                         limits = c(0,1500),
+                         breaks = seq(0,1500,250)
+  ) +
+  scale_y_continuous(breaks=seq(0, 40, 5), 
+                     limits=c(0, 40)
+                     )+
+  labs(
+    x = "Habitat type",
+    y = "Mean number of countries per habitat"
+  ) +
+  ggtheme_plot()
+
+```
+
+```{r Top_spp_Circle_Diagram, eval =F, echo = F}
+
+# Top 5 shared species per marine environment (number of countries sharing the species)
+Top_Species <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
+  # group_by(TaxonKey,TaxonName,CommonName,DemersPelag) %>% 
+  # summarise(Sum_Countries =sum(n_countries,na.rm=T)) %>% 
+  group_by(DemersPelag) %>% 
+  top_n(5,n_countries)
+
+# Countries that share the top 10
+Top_Spp_Countries <- Clean_Results_Trans %>% 
+  filter(
+    Area_Index < Min_AI |
+      Area_Index > Max_AI,
+    Model_Index == MI,
+    Same_Nation == "No",
+    TaxonKey %in% Top_Species$TaxonKey
+  ) %>% 
+  left_join(Species_Trans) %>% 
+  rename(scientific_name =TaxonName) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(from = paste(Genus,"\n",Species,sep=""),
+         DemersPelag = replace_na(DemersPelag, "Other")) %>%
+  group_by(
+    # from,
+    from = scientific_name,
+           to=CT_fishing_entity,
+           DemersPelag
+  ) %>% 
+  summarise(value=n()
+  ) #%>%
+  # filter(DemersPelag == "demersal") %>%
+  # select(-DemersPelag)
+
+####________________###
+# Circulize package ####
+# https://jokergoo.github.io/circlize_book/book/
+####________________###
+
+# To set links color 
+Bins <- as.numeric(cut(Top_Spp_Countries$value,breaks = 5)) # By size of sharing
+
+# To get country's flags... https://flagpedia.net/download
+flags <- c(paste("Temporal_Data/flags-mini/",list.files("Temporal_Data/flags-mini/"),sep=""))
+
+# List of Ecosystems
+Classification <- Top_Species %>% group_by(DemersPelag) %>% summarise(n()) %>%  pull(DemersPelag)
+
+####________________ PLOT PER ECOSYSTEM _____________________ ###
+
+for(s in 1:2){ # sclae loop
+  for(i in 1:length(Classification)) {
+    # for(i in 1:2) { # for testing
+
+    # Set scales to plott both absolut and proportional values
+    if(s == 1){
+      Scales <- "TRUE"
+    }else{
+      Scales <- "FALSE"
+    }
+
+    # Saving the plot
+    Plot_name <- paste(Figures_Path,Classification[i],Scales,".tiff",sep="")
+    tiff(Plot_name, width = 5, height = 5, units = 'in', res = 500)
+
+    # Subsetting the data for each plot
+    DemersPelag_i <- Classification[i]
+
+    Data <- Top_Ten_Spp_Countries %>% 
+      filter(DemersPelag %in% DemersPelag_i) %>% 
+      select(-3)
+
+    # Use to set links' colors to each species
+    Speceis_cols <- Data %>% group_by(from) %>% summarise(n()) %>% pull(from)
+
+    # The base plot
+    circos.clear()
+    chordDiagram(Data, 
+                 annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
+                 annotationTrackHeight = c(0.001, 0.1), # set links close to the axis
+                 directional = 1, # direction of arrows
+                 direction.type = c("diffHeight", "arrows"), # use arrows
+                 grid.col = "grey",
+                 # if col == Bins then colors will change depending of value
+                 # col = ifelse(Bins == 1,"#046C9A", # deep blue
+                 #              ifelse(Bins == 2,"#78B7C5", #light blue
+                 #                     ifelse(Bins == 3,"#EBCC2A", #yellow
+                 #                            ifelse(Bins == 4, "#E1AF00", #cream
+                 #                                   "#F21A00")))), #red
+                 # if col == Species_cols then colors will change depending of species
+                 col = ifelse(Data$from == Speceis_cols[1],"#FF0000", # deep blue
+                              ifelse(Data$from == Speceis_cols[2],"#00A08A", #light blue
+                                     ifelse(Data$from == Speceis_cols[3],"#F2AD00", #yellow
+                                            ifelse(Data$from == Speceis_cols[4], "#F98400", #cream
+                                                   "#5BBCD6")))), #red
+                 # link.arr.col = wes_palette("Zissou1"), 
+                 link.arr.type = "big.arrow",# make links big arrows
+                 diffHeight = uh(-0.5, "mm"), # brings the arrow to the bottom of the source
+                 scale = Scales, # fraction of each species to total share of each country instead of absolute value
+                 preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Data))))) # I have no idea but helps with the labels
+    )
+
+    #  Function to inlcude other layers
+    circos.track(track.index = 1, panel.fun = function(x, y) {
+      xlim = get.cell.meta.data("xlim")
+      xplot = get.cell.meta.data("xplot")
+      ylim = get.cell.meta.data("ylim")
+      sector.name = get.cell.meta.data("sector.index")
+
+      # Add labels
+      circos.text(mean(xlim),
+                  ylim[1],
+                  sector.name,
+                  facing = "clockwise",
+                  niceFacing = TRUE,
+                  adj = c(-0.2, 0.5),
+                  col = "black",
+                  cex = 0.6) # size of labels
+
+      # Add country's flags instead of names (still need to link names to falgs)
+
+      # library(EBImage)
+      # pos = circlize:::polar2Cartesian(circlize(CELL_META$xcenter, CELL_META$ycenter))
+      # image = EBImage::readImage(flags[CELL_META$sector.numeric.index])
+      # 
+      # rasterImage(image,
+      #             xleft = pos[1, 1] - 0.006, 
+      #             ybottom = pos[1, 2] - 0.005,
+      #             xright = pos[1, 1] + 0.05,
+      #             ytop = pos[1, 2]+ 0.04
+      #             )
+
+      # END FLAGS TRYOUT
+
+      # Set plot Title
+      Title <- paste("Top",Classification[i], "Species",sep =" ")
+      title(Title)
+
+    }, bg.border = NA) #end of circos.track
+
+    dev.off()
+  } # close for loop
+} #close scale loop
 

### 2019-08-30 Initial_Analysis.Rmd
Updates to the find neighbour method. hopefully faster

@@
 
+### Maps for each model/dataset
 ```{Tran_country_Map_All, eval =F, echo =F}
@@
 ```
+
+### RFMO analysis
+
+```{r Find_Neighbours_sf, eval = F, echo =F}
+
+#load North Carolia Data from sf
+nc <- st_read(system.file("shape/nc.shp", package="sf"), quiet = TRUE)
+
+# Get sparse matrix
+int = st_intersects(nc)
+
+# Intitalize new object
+mat = NULL
+
+# Fill
+for(i in 1:NROW(int)){
+  #Create matrix with ID and intersecting IDs
+  tmp = cbind(i, int[[i]])
+  # Join to Initalized object
+  mat  = rbind(mat, tmp)
+}
+
+# Build final data.frame substituting ID for name (in this case nc$name)
+matrix = data.frame(country = nc$NAME[mat[,1]], neighbor = nc$NAME[mat[,2]] )
+
+# Remove duplicates... eg of course an object intersects with itself...
+matrix = matrix[matrix$country != matrix$neighbor,]
+
+# Check it out, 
+head(matrix)
+
+```

### 2019-08-30 Initial_Analysis.Rmd
updated EstNeighFun for faster processing

--- 2019-08-29 Initial_Analysis.Rmd
@@
 
-# Method adopted from Adrew Heiss
-# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32
-
 EstNeighbors <- function(Shapefile){
 
-  # Get the list using the poly2nb function
-
-  Neighbor_List <- poly2nb(Shapefile)
-
-  # Convert te nb data to a Matrix of crossing references
-  Neighbor_Matrix <- nb2mat(Neighbor_List,
-                            style="B", 
-                            zero.policy=TRUE)
-
-  # Rename the matrix axis
-  colnames(Neighbor_Matrix) <- rownames(Neighbor_Matrix)
-
-  # Get the names of the countries for identifying them
-  Country_Names <- tibble(id = row.names(Shapefile@data),
-                              Country_Territory = as.character(Shapefile@data$Name),
-                              Neighbor_Territory = Country_Territory,
-                              EEZID = Shapefile@data$EEZID # specific of SAU sf
-                              )
-
-  # Clean up and transform the neighbor matrix
-  Neighbors <- as.data.frame(Neighbor_Matrix) %>%
-    mutate(country = row.names(.)) %>%  # Convert row names to actual column
-    gather(neighbor, present, -country) %>%  # Convert to long
-    filter(present == 1) %>%  # Only look at cells with a match
-    # Add country names
-    left_join(select(Country_Names,
-                     -Neighbor_Territory), by=c("country" = "id")) %>%
-    left_join(select(Country_Names, 
-                     -Country_Territory), by=c("neighbor" = "id")) %>% 
-    select(EEZID = EEZID.x,Country_Territory,Neighbor_Territory) # select final column
+  # Get sparse matrix
+  int = suppressMessages(st_intersects(Shapefile))
+  # Warnning message
+  # although coordinates are longitude/latitude, st_intersects assumes that they are planar
+
+  # Intitalize new object
+  mat = NULL
+
+  # Fill
+  for(i in 1:NROW(int)){
+    #Create matrix with ID and intersecting IDs
+    tmp = cbind(i, int[[i]])
+
+    # Join to Initalized object
+    mat  = rbind(mat, tmp)
+  }
+
+  # Build final data.frame substituting ID for name (in this case nc$name)
+  Result_table = data.frame(Name = Shapefile$Name[mat[,1]], 
+                            Neighbor_Territory = Shapefile$Name[mat[,2]]
+  )
+
+  # Remove duplicates... eg of course an object intersects with itself...
+  Result_table = Result_table[Result_table$Name != Result_table$Neighbor_Territory,]
 
   # Merge them with SAU data
-
-  DBEM_Neighbors_Data <- EEZIDs_List %>% 
+  suppressWarnings(
+    # warning for characters in name, no problem
+  DBEM_Neighbors_Data <- Result_table %>% 
+     left_join(EEZIDs_List, 
+              by = "Name") %>% # Asign EEZ id to each country
     left_join(EEZ_CellID, 
               by = "EEZID") %>% # Asign EEZ id to each country
-  left_join(Neighbors, 
-            by = "EEZID") %>% # Include all neighboring countries 
-  filter(Neighbor_Territory != "NA") %>% 
     left_join(Coor,
-            by = "INDEX") # Inclu
+              by = "INDEX") %>%  # Inclu
+    rename(Country_Territory = Name)
+
+  )
 
@@
 }
-
-### Test function
-
-# Subset data for testing function
-# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
-
-# Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
-# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
-
-# Running function
-# getNeighbors(Test)
-
-#### Works beautifully!
 
@@
 
+# SAU shapefile
+
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
-#The File
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
 fnam_world <- "SAUEEZ_July2015.shp"
-#Load it!
-
-World_EEZs <- readOGR(dsn = path_world,
+# #Load it!
+# 
+World_EEZs <- st_read(dsn = path_world,
                       layer =file_path_sans_ext(fnam_world))
 
+subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru","Brazil"))
 #### Grid cell information ####
@@
 ```
+
+### RFMO analysis
+
+# Old code
+```{r OLD_funEstNeighbors, eval = F, echo=T}
+# Determine which countries are neighbors
+
+# Method adopted from Adrew Heiss
+# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32
+
+EstNeighbors <- function(Shapefile){
+
+  # Get the list using the poly2nb function
+
+  Neighbor_List <- poly2nb(Shapefile)
+
+  # Convert te nb data to a Matrix of crossing references
+  Neighbor_Matrix <- nb2mat(Neighbor_List,
+                            style="B", 
+                            zero.policy=TRUE)
+
+  # Rename the matrix axis
+  colnames(Neighbor_Matrix) <- rownames(Neighbor_Matrix)
+
+  # Get the names of the countries for identifying them
+  Country_Names <- tibble(id = row.names(Shapefile@data),
+                              Country_Territory = as.character(Shapefile@data$Name),
+                              Neighbor_Territory = Country_Territory,
+                              EEZID = Shapefile@data$EEZID # specific of SAU sf
+                              )
+
+  # Clean up and transform the neighbor matrix
+  Neighbors <- as.data.frame(Neighbor_Matrix) %>%
+    mutate(country = row.names(.)) %>%  # Convert row names to actual column
+    gather(neighbor, present, -country) %>%  # Convert to long
+    filter(present == 1) %>%  # Only look at cells with a match
+    # Add country names
+    left_join(select(Country_Names,
+                     -Neighbor_Territory), by=c("country" = "id")) %>%
+    left_join(select(Country_Names, 
+                     -Country_Territory), by=c("neighbor" = "id")) %>% 
+    select(EEZID = EEZID.x,Country_Territory,Neighbor_Territory) # select final column
+
+    # Merge them with SAU data
+
+  DBEM_Neighbors_Data <- EEZIDs_List %>% 
+  left_join(EEZ_CellID, 
+            by = "EEZID") %>% # Asign EEZ id to each country
+  left_join(Neighbors, 
+            by = "EEZID") %>% # Include all neighboring countries 
+  filter(Neighbor_Territory != "NA") %>% 
+  left_join(Coor,
+            by = "INDEX") # Inclu
+
+  return(DBEM_Neighbors_Data)
+
+}
+
+### Test function
+
+# Subset data for testing function
+# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
+
+# Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
+# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
+
+# Running function
+# getNeighbors(Test)
+
+#### Works beautifully!
+
+```

### 2019-08-30 Initial_Analysis.Rmd
Modified Neighbour list to be used on other shapefiles. Created an RFMO sub-routine

@@
 
-EstNeighbors <- function(Shapefile){
+EstNeighbors <- function(Shapefile, Partial = "NA"){
 
@@
 
+  if(Partial == T){
+    # If only partial analysis just returns neighbor list
+    return(Result_table)
+
+  }else{
   # Merge them with SAU data
@@
 
-}
-
-```
-
-## Sub Routine
-
-```{r Neighbords_Control_Pannel, eval = F, echo = F}
+  } # end ifelse
+} # end function
+
+# subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru"))
+# EstNeighbors(subset)
+# EstNeighbors(subset,T)
+
+```
+
+### Sub Routine
+
+#### EEZ
+
+```{r EEZ_Neighbords_Control_Pannel, eval = F, echo = F}
 
@@
 
-subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru","Brazil"))
-#### Grid cell information ####
-
-# List of DBEM INDEX within the EEZ 
-#Data provided by Vicki Lam
-
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
 # Run Function (Ran and saved May 27 2019 at 6pm)
  system.time(
-  Neighbor_List <- EstNeighbors(World_EEZs)
+  Neighbor_List <- EstNeighbors(World_EEZs, Partial = T)
  )
@@
 
+#### RFMOs
+
+```{r RFMO_Neighbords_Control_Pannel, eval = F, echo = F}
+
+#### Load Data Needed ####
+
+# Spatial analysis for Countries boundaries from marine regions ####
+
+###_______________________________Read Me_____________________________________________#
+#### Data License and references ###
+# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
+# Flanders Marine Institute (2018).
+Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10.
+Available online at http://www.marineregions.org/.
+https://doi.org/10.14284/312
+
+#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
+###________________________________________________________________________________#
+
+# SAU shapefile
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO/",sep="")
+# #The File
+fnam_world <- "SAU_RFMO_Sept_2015.shx"
+# #Load it!
+# 
+RFMOs_sf <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(Name = RFMO_nm_s)
+
+# Run Function (Ran and saved May 27 2019 at 6pm)
+ system.time(
+  RFMO_Neighbor_List <- EstNeighbors(RFMOs_sf, Partial = T)
+ )
+# 8203.05    0.25 8204.51 (around 2 hours 30 min)
+
+write.csv(RFMO_Neighbor_List,
+          paste(Data_Path,"Spatial_Data/RFMO_Neighbor_List.csv", sep =""),
+          row.names = F)
+
+####_________________________________________ TESTING PERIOD_________________________________________####
+# I'm substetting central america to do the whole analysis (smaller EEZs = faster computation) once I have figure out things I'll run for all
+
+### Data
+# For now using only the subdata
+
+## Spatial Test Data
+# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
+
+# Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras (Pacific)","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
+
+# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
+
+```
 ### Function `GetSppDist`
@@
 
-### RFMO analysis
-
 # Old code

### 2019-08-30 Initial_Analysis.Rmd
Determined RFMOs

@@
 
+#### Grid cell information ####
+
+# List of DBEM INDEX within the EEZ 
+#Data provided by Vicki Lam
+
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# DBEM Coordinate system
+Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+
 # Run Function (Ran and saved May 27 2019 at 6pm)
  system.time(
-  Neighbor_List <- EstNeighbors(World_EEZs, Partial = T)
+  EEZ_Neighbor_List <- EstNeighbors(World_EEZs, Partial = T)
  )
@@
 
-write.csv(Neighbor_List,
-          paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""),
+write.csv(EEZ_Neighbor_List,
+          paste(Data_Path,"Spatial_Data/EEZ_Neighbor_List.csv", sep =""),
           row.names = F)
@@
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO/",sep="")
+path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO",sep="")
 # #The File
@@
                       layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(Name = RFMO_nm_s)
+  dplyr::rename(Name = RFMO_nm_s)
 

### 2019-09-02 Initial_Analysis.Rmd
Updated the analysis to run the RFMO part on the Beast

--- 2019-08-30 Initial_Analysis.Rmd
@@
 
-1. Determine which countries have neighboring EEZs  
-  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify neighboring polygons,
-  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the neighboring data
-2. Overlap distribution maps with neighbors data  
-  2.1. For each species we merged the DBEM_Neighbors data with their known distribution (Gab's data)  
+1. Determine which countries have Neighbouring EEZs  
+  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify Neighbouring polygons,
+  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the Neighbouring data
+2. Overlap distribution maps with Neighbours data  
+  2.1. For each species we merged the DBEM_Neighbours data with their known distribution (Gab's data)  
 3. Determine transboundary if:  
-  3.1. Species is present in both neighboring EEZs by INDEX
+  3.1. Species is present in both Neighbouring EEZs by INDEX
 
@@
 
-## Sub Routine Estimating Neighbords
-
-### Functions `EstNeighbors`
-
-This function determines what EEZs are neighbors and returns a data.frame of it
-
-```{r funEstNeighbors, eval = F, echo=T}
-# Determine which countries are neighbors
-
-EstNeighbors <- function(Shapefile){
+## Sub Routine Estimating Neighbourds
+
+### Functions `EstNeighbours`
+
+This function determines what EEZs are Neighbours and returns a data.frame of it
+
+```{r funEstNeighbours, eval = F, echo=T}
+# Determine which countries are Neighbours
+
+EstNeighbours <- function(Shapefile, Partial = "NA"){
 
@@
   Result_table = data.frame(Name = Shapefile$Name[mat[,1]], 
-                            Neighbor_Territory = Shapefile$Name[mat[,2]]
+                            Neighbour_Territory = Shapefile$Name[mat[,2]]
   )
@@
   # Remove duplicates... eg of course an object intersects with itself...
-  Result_table = Result_table[Result_table$Name != Result_table$Neighbor_Territory,]
-
+  Result_table = Result_table[Result_table$Name != Result_table$Neighbour_Territory,]
+
+  if(Partial == T){
+    # If only partial analysis just returns Neighbour list
+    return(Result_table)
+
+  }else{
   # Merge them with SAU data
@@
     # warning for characters in name, no problem
-  DBEM_Neighbors_Data <- Result_table %>% 
+  DBEM_Neighbours_Data <- Result_table %>% 
      left_join(EEZIDs_List, 
@@
 
-  return(DBEM_Neighbors_Data)
-
-}
-
-```
-
-## Sub Routine
-
-```{r Neighbords_Control_Pannel, eval = F, echo = F}
+  return(DBEM_Neighbours_Data)
+
+  } # end ifelse
+} # end function
+
+# subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru"))
+# EstNeighbours(subset)
+# EstNeighbours(subset,T)
+
+```
+
+### Sub Routine
+
+#### EEZ
+
+```{r EEZ_Neighbourds_Control_Pannel, eval = F, echo = F}
 
@@
 
-subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru","Brazil"))
 #### Grid cell information ####
@@
  system.time(
-  Neighbor_List <- EstNeighbors(World_EEZs)
+  EEZ_Neighbour_List <- EstNeighbours(World_EEZs, Partial = T)
  )
@@
 
-write.csv(Neighbor_List,
-          paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""),
+write.csv(EEZ_Neighbour_List,
+          paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.csv", sep =""),
           row.names = F)
@@
 
+#### RFMO
+
+```{r RFMO_Index, eval = F, echo = F}
+
+#### Load Data Needed ####
+
+# SAU RFMO shapefile
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO",sep="")
+# #The File
+fnam_world <- "SAU_RFMO_Sept_2015.shx"
+# #Load it!
+# 
+RFMOs_sf <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world)) %>% 
+  dplyr::rename(Name = RFMO_nm_s) %>% 
+  st_set_crs(3832) %>% # Making sure is same proyection
+  st_transform(3832) # to match shapefiles
+
+# Load coordinate system
+
+Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+
+# COnvert Coor system to sf
+Coor_sf = st_as_sf(Coor,
+                        coords = c("Longitude", "Latitude")) %>% 
+  st_set_crs(3832) %>% # to match shapefiles
+  st_transform(3832) # to match shapefiles
+
+# Merge RFMO and coor datasets
+RFMO_Coor <- st_join(RFMOs_sf,
+                         Coor_sf,
+                         join = st_contains) %>% 
+  filter(!is.na(INDEX)) # Remove regions beyond RFMOs
+
+# head(RFMO_Coor)
+
+# Convert it back to a data frame and select only the two columns we want
+RFMO_INDEX <- as.data.frame(RFMO_Coor) %>% 
+  select(INDEX,Name) %>% 
+  arrange(INDEX)
+
+# head(RFMO_INDEX)
+
+# Save new data
+write.csv(RFMO_INDEX,
+          paste(Data_Path,"Spatial_Data/RFMO/RFMO_INDEX.csv",sep=""),
+          row.names = F
+          )
+
+# Map it (works!)
+
+# RFMO_INDEX %>%
+#   left_join(Coor,
+#             by = "INDEX") %>%
+#   ggplot(.,
+#             aes(x = Longitude,
+#                 y = Latitude,
+#                 color = Territory,
+#                 fill = Territory)
+#             ) +
+#   geom_tile() 
+# 
+# 
+# RFMO_INDEX %>%
+#   left_join(Coor,
+#             by = "INDEX") %>%
+#   ggplot(.,
+#             aes(x = Longitude,
+#                 y = Latitude,
+#                 color = INDEX,
+#                 fill = INDEX)
+#             ) +
+#   geom_tile() +
+#   facet_wrap(~Territory)
+
+```
+
+```{r RFMO_Neighbourds_Control_Pannel, eval = F, echo = F}
+
+#### Load Data Needed ####
+
+# SAU RFMO shapefile
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO",sep="")
+# #The File
+fnam_world <- "SAU_RFMO_Sept_2015.shx"
+# #Load it!
+# 
+RFMOs_sf <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world)) %>% 
+  dplyr::rename(Name = RFMO_nm_s)
+
+# Run Function (Ran and saved May 27 2019 at 6pm)
+ system.time(
+  RFMO_Neighbour_List <- EstNeighbours(RFMOs_sf, Partial = T)
+ )
+# 8203.05    0.25 8204.51 (around 2 hours 30 min)
+
+ ## Include Index column
+
+RFMO_Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbour_List.csv",sep=""),header = TRUE) %>% 
+  left_join(RFMO_INDEX,
+            by = "Name") %>% 
+  rename(Territory = Name,
+         Neighbour = Neighbour_Territory)
+
+# head(RFMO_Neighbour_List)
+
+write.csv(RFMO_Neighbour_List,
+          paste(Data_Path,"Spatial_Data/RFMO_Neighbour_List.csv", sep =""),
+          row.names = F)
+
+```
 ### Function `GetSppDist`
@@
 # EEZ_Size: Number of grid-cells that each EEZ has
-# Neighbors: Reference list of neighbouring countries
+# Neighbours: Reference list of neighbouring countries
 
@@
 #### For testing 
-# Spp <- 600059
- #Model <- "All"
- #Neighbors <- Neighbor_List
- #Coord = CoorG
+# Spp <- #600004  # Anchovie Equator, Chile and Peru
+# Spp <- 600107 # Tuna Many RFMOs
+# Model <- "All"
+# Coord = CoorG
+
+# For EEZ
+ # Neighbours <- Neighbours_EEZ
+ # Index_Code <- EEZ_Index_Code
+
+ # For RFMO 
+ # Index_Code <- RFMO_INDEX
+ # Neighbours <- RFMO_Neighbor_List %>% 
+ #   rename(Territory = Name,
+ #         Neighbour = Neighbor_Territory)
+
 # __________________________________
+# __________________________________
 
 # The function
-EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){
+EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){
 
@@
   Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
+    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
            Model != "SAU_C") %>% # Only using observational and modelled data
@@
     select(-Model, -Value, -Latitude,-Longitude) %>%
-    left_join(EEZ_CellID,
-              by = "INDEX") %>% 
-    left_join(EEZIDs_List,
-              by = "EEZID")
+    left_join(Index_Code,
+              by = "INDEX")
 
@@
   Model_Index_D <- Trans_Spp %>% 
-    group_by(Name,
+    group_by(Territory,
              TaxonKey,
@@
 
-  #Step 1.  Get EEZ id and neighbor
-  Neighbors_EEZ <- Neighbors %>% 
-    group_by(EEZID,Country_Territory,Neighbor_Territory) %>% 
+  #Step 1.  Get EEZ id and Neighbour
+  Neighbours_List <- Neighbours %>% 
+    group_by(Territory,Neighbour) %>% 
     summarise(n=n()) %>% 
@@
              Model_Index, # Un-comment after producing models x datasets
-             EEZID) %>% 
+             Territory) %>% 
     summarise(n_spp_eez = length(unique(INDEX))) %>% 
-    left_join(Neighbors_EEZ,
-              by = "EEZID") %>% 
-    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
-           Neighbor_Territory %in% Trans_Spp$Name)
-
-  # Step 3. Sum total grids per neighbors
+    left_join(Neighbours_List,
+              by = "Territory") %>% 
+    filter(Territory %in% Trans_Spp$Territory, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
+           Neighbour %in% Trans_Spp$Territory)
+
+  # Step 3. Sum total grids per Neighbours
 
   # Split dataframes to merge latter
-  Country_Territory_T <- Spp_Grid %>% 
+  Territory_T <- Spp_Grid %>% 
     ungroup() %>% 
@@
       TaxonKey,
-      Name=Country_Territory,
+      Name=Territory,
       n_spp_eez
@@
 
-  Neighbor_Territory_T <- Spp_Grid %>% 
+  Neighbour_T <- Spp_Grid %>% 
     ungroup() %>% 
@@
       TaxonKey,n_spp_eez,
-      Name=Neighbor_Territory, 
-      Country_Territory
-    )
-
-  # Merge dataframes to get totals per neighbords
-  Area_Index_D <- full_join(Country_Territory_T,
-                            Neighbor_Territory_T, 
+      Name=Neighbour, 
+      Territory
+    )
+
+  # Merge dataframes to get totals per Neighbourds
+  Area_Index_D <- full_join(Territory_T,
+                            Neighbour_T, 
                             by = c("Model_Index","Name","TaxonKey")
@@
     rowwise() %>%
-    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
     distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbor_Territory = Name,
+    rename(Neighbour = Name,
            n_spp_Country = n_spp_eez.x,
-           n_spp_Neighbor = n_spp_eez.y) %>% 
+           n_spp_Neighbour = n_spp_eez.y) %>% 
     mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
@@
   Indexes <- Model_Index_D %>% 
-    rename(Country_Territory = Name) %>% 
+    # rename(Territory = Name) %>% 
     full_join(Area_Index_D,
-              by = c("TaxonKey","Country_Territory","Model_Index")
+              by = c("TaxonKey","Territory","Model_Index")
     ) %>% 
@@
            !is.na(Model_Index) # Uncomment after producing Models x datasets
-    )%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(TaxonKey,Country_Territory,Neighbor_Territory,everything())
+    ) %>%  # Remove cases where the country does not pass the area_index and viceversa
+    select(TaxonKey,Territory,Neighbour,everything())
 
@@
 }
+
+# __________________________________
+# Test function
+# __________________________________
+# EstTransIndex(Spp = 600107,
+#               Mode = "All",
+#               Neighbours = ,Coord,Index_Code,Save="Y")
+# 
+# Spp <-  # Tuna Many RFMOs
+# Model <- "All"
+# Coord = CoorG
+# 
+# # For EEZ
+#  # Neighbours <- Neighbours_EEZ
+#  # Index_Code <- EEZ_Index_Code
+#  
+#  # For RFMO 
+#  Index_Code <- RFMO_INDEX
+#  Neighbours <- RFMO_Neighbor_List %>% 
+#    rename(Territory = Name,
+#          Neighbour = Neighbor_Territory)
+
 ```
@@
 
-## Routine
-
-```{r Control_Pannel, eval = T, echo = F}
+## Routine for estimating transboundary species
+
+```{r EEZ_Control_Pannel, eval = T, echo = F}
+
+# Set Jurisdiction to EEZ or RFMO
+Jurisdiction <- "EEZ"
+
+# Updates result's path for the jurisdiction
+Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
 
@@
 
-# For Function
-Exploited_Species_List <- Exploited_Species$TaxonKey
-
-# Load neighbours data from previouse routine
-Neighbor_List <- fread(paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""))
-
 # Gabriel's coordinate system
@@
   mutate(INDEX = seq(1,259200,1))
+
+# For Function
+Exploited_Species_List <- Exploited_Species$TaxonKey
+
+# Load Jursidiction-dependant data
+if(Jurisdiction == "EEZ"){
+  # Load neighbours data from previouse routine
+  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.csv", sep =""))
 
@@
 
+  Index_Code <- EEZIDs_List %>% 
+    left_join(EEZ_CellID) %>% 
+    rename(Territory = Name)
+
+}else{
+
+  # Load neighbours data from previouse routine
+  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbours_List.csv", sep =""))
+
+  Index_Code <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Index_Code.csv", sep =""))
+
+}
+
 # Creates dummy dataset for Non transboundary species
@@
 
-####_________________________________________ TESTING PERIOD_________________________________________####
-## Species Test Data Just to know what's captured in these countries
-#
-# SAU_Data <- fread("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
-# #
-# # #### Species per country
-# #
-# Spps <- SAU_Data %>%
-#   filter(data_layer == "Reconstructed domestic catch") %>%
-#   group_by(area_name,TaxonName = scientific_name) %>%
-#   summarise(n()) %>%
-#   left_join(Exploited_Species,
-#             by = "TaxonName") %>%
-#   filter(TaxonKey %in% Exploited_Species_List$TaxonKey)
-#
-# Exploited_Species_List <- Spps$TaxonKey
-
-# Exploited_Species_List <- c("600006",600107)
-# Exploited_Species_List = 600107
-# TaxonKey <- unique(Spps$TaxonKey)
-
+# Just a warning for me not to forget
+print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level"))
 ```
@@
 
-# Spp_Trans <- NULL
-
+# Run model in parallel
 system.time(
@@
     mclapply(
-      Exploited_Species_List, FUN = EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
+      Exploited_Species_List,
+      FUN = EstTransIndex,
+      Model = "All", # all data sources
+      Neighbours = Neighbours_Data,
+      Coord = CoorG,  # Gabriels coordinate system for read species dist
+      Index_Code = Index_Code, 
+      Save = "Y",  # For saving
+      Jurisdiction_Type = Jurisdiction # For saving in proper path
     )
@@
 # Results
+
+## Function `GetTransResults`
 
@@
 # For Carmelia
+if(Sys.info()[7] == "carmelia"){
   Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
+}else{
 
@@
            Country_Territory= FishingRegion,
-         FishingRegion=Neighbor_Territory,
+           FishingRegion=Neighbour_Territory,
            Model_Index,
@@
     select(1,2, 
-    Neighbor_Territory = FishingRegion,
+           Neighbour_Territory = FishingRegion,
            Model_Index:CT_fishing_entity,
@@
       CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
-    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
+      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour_Territory),paste(NT_fishing_entity)),
       Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
@@
       Country_Territory %in% Islands_to_Remove |
-      Neighbor_Territory %in% Islands_to_Remove |
-      Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
-      Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
-      Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
-      Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
-      Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
-      Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
-      Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
-      Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
-      Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
-      Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
-      Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
-      Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
-      Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
-      Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
-      Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
-      Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
-      Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
-      Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
-      Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
-      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
-      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
-      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
-      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
-      Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
-      Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
-      Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
-      Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
-      Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
-      Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
-      Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
-      Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
-  ) %>%
-  group_by(Country_Territory,Neighbor_Territory) %>% 
+        Neighbour_Territory %in% Islands_to_Remove |
+        Country_Territory == "Balearic Island (Spain)" & Neighbour_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
+        Country_Territory == "British Virgin Isl. (UK)" & Neighbour_Territory == "Anguilla" |
+        Neighbour_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
+        Country_Territory == "Corsica (France)" & Neighbour_Territory == "France (Mediterranean)" |
+        Neighbour_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
+        Country_Territory == "Crete (Greece)" & Neighbour_Territory == "Grece" |
+        Neighbour_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
+        Country_Territory == "Cyprus (North)" & Neighbour_Territory == "Cyprus (South)" |
+        Neighbour_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
+        Country_Territory == "Channel Isl. (UK)" & Neighbour_Territory == "United Kingdom" |
+        Neighbour_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
+        Country_Territory == "Glorieuse Islands (France)" & Neighbour_Territory == "Mayotte (France)" |
+        Neighbour_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
+        Country_Territory == "Guam (USA)" & Neighbour_Territory == "Northern Marianas (USA)" |
+        Neighbour_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
+        Country_Territory == "Italy" & Neighbour_Territory == "Sardinia (Italy)" |
+        Neighbour_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
+        Country_Territory == "Italy" & Neighbour_Territory == "Sicily (Italy)" |
+        Neighbour_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
+        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (main islands)"|
+        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
+        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (Ogasawara Islands)"|
+        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
+        Country_Territory == "Norway" & Neighbour_Territory == "Svalbard Isl. (Norway)" |
+        Neighbour_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
+        Country_Territory == "Sicily (Italy)" & Neighbour_Territory == "Sardinia (Italy)" |
+        Neighbour_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
+        Country_Territory == "South Africa (Atlantic Coast)" & Neighbour_Territory == "South Africa (Indian Ocean Coast)" |
+        Neighbour_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
+        Country_Territory == "USA (Alaska, Arctic)" & Neighbour_Territory == "USA (Alaska, Subarctic)" |
+        Neighbour_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
+    ) %>%
+    group_by(Country_Territory,Neighbour_Territory) %>% 
     summarise(n())
@@
     anti_join(Territories_to_Remove,
-            by = c("Country_Territory","Neighbor_Territory")
+              by = c("Country_Territory","Neighbour_Territory")
     ) %>% 
@@
 
+} # closes ifstatement for carmelia temporal files
 # Load results for non transboundary (discrete) stocks
@@
 
-TenTwenyfive <- Clean_Results_Trans %>% 
+Transboundary_Spp <- Clean_Results_Trans %>% 
   filter(
@@
     n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbor_Territory)),
+    n_countries = length(unique(Neighbour_Territory)),
     Trans_Rate = n_trans/n_countries
@@
 
-Non_trans_Area_TenTwenyfive <- Clean_Results_Trans %>% 
+Discrete_Spp <- Clean_Results_Trans %>% 
   filter(
@@
     n_no_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbor_Territory))
-  )
+    n_countries = length(unique(Neighbour_Territory))
+  )
+
+```
+
+## Validate Results using RFMOs
+
+```{Validation_RFMOs}
+
+#### Load RFMO data provided by Vicky (SAU)
+
+RFMOs_sf <- fread(paste(Data_Path,"Spatial_Data/SAU_RFMO/SAU_RFMO_Sept_2015.shp",sep=""))
 
@@
     mclapply(
-      600004, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
+      600004, FUN =EstTransIndex, Model = "All", Neighbours = Neighbour_List, Coord = CoorG
     )
@@
   Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbors$INDEX) %>% # Filter data only located within EEZs
+    filter(INDEX %in% Neighbours$INDEX) %>% # Filter data only located within EEZs
     mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
@@
     mutate(Model_Index = Model_Index*100) %>%
-    left_join(Neighbors,
+    left_join(Neighbours,
               by = "INDEX")
@@
     n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbor_Territory)),
+    n_countries = length(unique(Neighbour_Territory)),
     )
@@
 
-Neighbord_Territory_T <- Clean_Results %>% 
-  group_by(eez_name=Neighbor_Territory) %>% 
+Neighbourd_Territory_T <- Clean_Results %>% 
+  group_by(eez_name=Neighbour_Territory) %>% 
   summarise() %>%
@@
             by = "eez_name") %>% 
-  select(Neighbor_Territory= eez_name,
+  select(Neighbour_Territory= eez_name,
          NT_fishing_entity=fishing_entity
@@
 Non_duplicate_Data <- Clean_Results %>%   
-  left_join(Neighbord_Territory_T,
-              by ="Neighbor_Territory") %>% 
+  left_join(Neighbourd_Territory_T,
+              by ="Neighbour_Territory") %>% 
   left_join(Country_Territory_T,
@@
 
-### So maybe there are no neighbors?
-Neighbor_List <- fread(paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""))
-
-Russia_Neighbor <- Neighbor_List %>% 
+### So maybe there are no Neighbours?
+Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/Neighbour_List.csv", sep =""))
+
+Russia_Neighbour <- Neighbour_List %>% 
   filter(stringr::str_detect(Name,"Russia"))
 
-unique(Russia_Neighbor$Country_Territory)
+unique(Russia_Neighbour$Country_Territory)
 
@@
 # Model <- "All"
-# Neighbors <- Neighbor_List
+# Neighbours <- Neighbour_List
 # Coord = CoorG
@@
 # The function
-EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){
+EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
 
@@
 
-  #Step 1.  Get EEZ id and neighbor
-  Neighbors_EEZ <- Neighbors %>% 
-  group_by(EEZID,Country_Territory,Neighbor_Territory) %>% 
+  #Step 1.  Get EEZ id and Neighbour
+  Neighbours_EEZ <- Neighbours %>% 
+  group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
   summarise(n=n()) %>% 
@@
     summarise(n_spp_eez = length(unique(INDEX))) %>% 
-    left_join(Neighbors_EEZ,
+    left_join(Neighbours_EEZ,
               by = "EEZID") %>% 
-    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
-           Neighbor_Territory %in% Trans_Spp$Name)
-
-  # Step 3. Sum total grids per neighbors
+    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
+           Neighbour_Territory %in% Trans_Spp$Name)
+
+  # Step 3. Sum total grids per Neighbours
 
@@
 
-  Neighbor_Territory_T <- Spp_Grid %>% 
+  Neighbour_Territory_T <- Spp_Grid %>% 
     ungroup() %>% 
@@
       Model_Index,
-      TaxonKey,n_spp_eez,Name=Neighbor_Territory, Country_Territory
-    )
-
-  # Merge dataframes to get totals per neighbords
+      TaxonKey,n_spp_eez,Name=Neighbour_Territory, Country_Territory
+    )
+
+  # Merge dataframes to get totals per Neighbourds
   Area_Index_D <- full_join(Country_Territory_T,
-                           Neighbor_Territory_T, by = c("Name","TaxonKey","Model")) %>%
+                           Neighbour_Territory_T, by = c("Name","TaxonKey","Model")) %>%
     rowwise() %>%
-    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
     distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbor_Territory = Name,
+    rename(Neighbour_Territory = Name,
            n_spp_Country = n_spp_eez.x,
-           n_spp_Neighbor = n_spp_eez.y) %>% 
+           n_spp_Neighbour = n_spp_eez.y) %>% 
     mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
@@
     filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(Model,TaxonKey,Country_Territory,Neighbor_Territory,everything())
+    select(Model,TaxonKey,Country_Territory,Neighbour_Territory,everything())
 
@@
 # Model <- "All"
-# Neighbors <- Neighbor_List
+# Neighbours <- Neighbour_List
 # 
-# Tryout <- EstTransIndex(Spp,Model,Neighbors,CoorG,Save="N")
+# Tryout <- EstTransIndex(Spp,Model,Neighbours,CoorG,Save="N")
 # 
@@
 
-### RFMO analysis
-
 # Old code
-```{r OLD_funEstNeighbors, eval = F, echo=T}
-# Determine which countries are neighbors
+```{r OLD_funEstNeighbours, eval = F, echo=T}
+# Determine which countries are Neighbours
 
@@
 
-EstNeighbors <- function(Shapefile){
+EstNeighbours <- function(Shapefile){
 
@@
 
-  Neighbor_List <- poly2nb(Shapefile)
+  Neighbour_List <- poly2nb(Shapefile)
 
   # Convert te nb data to a Matrix of crossing references
-  Neighbor_Matrix <- nb2mat(Neighbor_List,
+  Neighbour_Matrix <- nb2mat(Neighbour_List,
                             style="B", 
@@
   # Rename the matrix axis
-  colnames(Neighbor_Matrix) <- rownames(Neighbor_Matrix)
+  colnames(Neighbour_Matrix) <- rownames(Neighbour_Matrix)
 
@@
                               Country_Territory = as.character(Shapefile@data$Name),
-                              Neighbor_Territory = Country_Territory,
+                              Neighbour_Territory = Country_Territory,
                               EEZID = Shapefile@data$EEZID # specific of SAU sf
@@
 
-  # Clean up and transform the neighbor matrix
-  Neighbors <- as.data.frame(Neighbor_Matrix) %>%
+  # Clean up and transform the Neighbour matrix
+  Neighbours <- as.data.frame(Neighbour_Matrix) %>%
     mutate(country = row.names(.)) %>%  # Convert row names to actual column
-    gather(neighbor, present, -country) %>%  # Convert to long
+    gather(Neighbour, present, -country) %>%  # Convert to long
     filter(present == 1) %>%  # Only look at cells with a match
@@
     left_join(select(Country_Names,
-                     -Neighbor_Territory), by=c("country" = "id")) %>%
+                     -Neighbour_Territory), by=c("country" = "id")) %>%
     left_join(select(Country_Names, 
-                     -Country_Territory), by=c("neighbor" = "id")) %>% 
-    select(EEZID = EEZID.x,Country_Territory,Neighbor_Territory) # select final column
+                     -Country_Territory), by=c("Neighbour" = "id")) %>% 
+    select(EEZID = EEZID.x,Country_Territory,Neighbour_Territory) # select final column
 
@@
 
-  DBEM_Neighbors_Data <- EEZIDs_List %>% 
+  DBEM_Neighbours_Data <- EEZIDs_List %>% 
   left_join(EEZ_CellID, 
             by = "EEZID") %>% # Asign EEZ id to each country
-  left_join(Neighbors, 
-            by = "EEZID") %>% # Include all neighboring countries 
-  filter(Neighbor_Territory != "NA") %>% 
+  left_join(Neighbours, 
+            by = "EEZID") %>% # Include all Neighbouring countries 
+  filter(Neighbour_Territory != "NA") %>% 
   left_join(Coor,
@@
 
-  return(DBEM_Neighbors_Data)
+  return(DBEM_Neighbours_Data)
 
@@
 # Running function
-# getNeighbors(Test)
+# getNeighbours(Test)
 
@@
 ```
+
+```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
+
+# Function to determine whether or not a species is transboundary
+
+# Varibales needed
+# Spp: Species to be analized, data with presence/absence per gridcell
+# Index_EEZ: Reference list of all INDEX that fall within EEZs
+# EEZ_Size: Number of grid-cells that each EEZ has
+# Neighbours: Reference list of neighbouring countries
+
+# Needs getSppDist
+
+#### For testing 
+# Spp <- 600059
+ #Model <- "All"
+ #Neighbours <- Neighbour_List
+ #Coord = CoorG
+# __________________________________
+
+# The function
+EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
+
+  # Get model data from spps
+  SppDist <- GetSppDist(Spp,Model,Coord)
+
+  # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
+           Model != "SAU_C") %>% # Only using observational and modelled data
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
+    filter(Value > 0) %>%
+    group_by(TaxonKey,
+             INDEX
+    ) %>%
+    summarise(Model_Index = mean(Value,na.rm=T)
+    ) %>%
+    filter(Model_Index > 0) %>%
+    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
+    left_join(SppDist,
+              by = c("TaxonKey","INDEX")) %>%
+    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
+           Value > 0) %>%
+    mutate(Model_Index = Model_Index*100) %>%
+    select(-Model, -Value, -Latitude,-Longitude) %>%
+    left_join(EEZ_CellID,
+              by = "INDEX") %>% 
+    left_join(EEZIDs_List,
+              by = "EEZID")
+
+  # MODEL INDEX (TRESHOLDS 1 & 2) #
+  Model_Index_D <- Trans_Spp %>% 
+    group_by(Name,
+             TaxonKey,
+             Model_Index
+    ) %>% 
+    summarise(n_cells_spp = n()) %>% 
+    select(-n_cells_spp)
+
+  #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
+  # The number of species' cells present within each country's EEZ
+
+  #Step 1.  Get EEZ id and Neighbour
+  Neighbours_EEZ <- Neighbours %>% 
+    group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
+    summarise(n=n()) %>% 
+    ungroup() %>% 
+    select(-n)
+
+  # Step 2. Determines the amount of grids present in each country
+  Spp_Grid <- Trans_Spp %>% 
+    group_by(TaxonKey,
+             Model_Index, # Un-comment after producing models x datasets
+             EEZID) %>% 
+    summarise(n_spp_eez = length(unique(INDEX))) %>% 
+    left_join(Neighbours_EEZ,
+              by = "EEZID") %>% 
+    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
+           Neighbour_Territory %in% Trans_Spp$Name)
+
+  # Step 3. Sum total grids per Neighbours
+
+  # Split dataframes to merge latter
+  Country_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index, # Un-comment after producing models x datasets
+      TaxonKey,
+      Name=Country_Territory,
+      n_spp_eez
+    )
+
+  Neighbour_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index,
+      TaxonKey,n_spp_eez,
+      Name=Neighbour_Territory, 
+      Country_Territory
+    )
+
+  # Merge dataframes to get totals per Neighbourds
+  Area_Index_D <- full_join(Country_Territory_T,
+                            Neighbour_Territory_T, 
+                            by = c("Model_Index","Name","TaxonKey")
+  ) %>%
+    rowwise() %>%
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
+    distinct() %>% # Removes false duplicates from `full_join()`
+    rename(Neighbour_Territory = Name,
+           n_spp_Country = n_spp_eez.x,
+           n_spp_Neighbour = n_spp_eez.y) %>% 
+    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
+    select(1:3,6,8)
+
+  #____________ FINAL INDEX TABLE_________ #
+  Indexes <- Model_Index_D %>% 
+    rename(Country_Territory = Name) %>% 
+    full_join(Area_Index_D,
+              by = c("TaxonKey","Country_Territory","Model_Index")
+    ) %>% 
+    filter(!is.na(Area_Index),
+           !is.na(Model_Index) # Uncomment after producing Models x datasets
+    )%>%  # Remove cases where the country does not pass the area_index and viceversa
+    select(TaxonKey,Country_Territory,Neighbour_Territory,everything())
+
+  ### Save spp dataframe
+
+  if(nrow(Indexes) > 0 & Save == "Y"){
+
+    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
+    Save_Path <- paste(Results_Path,File_Name,sep="")
+
+    write.csv(Indexes,
+              Save_Path,
+              row.names = F)
+
+  }
+
+  if(nrow(Indexes) == 0 & Save == "Y"){
+
+    # Reads dataset of Non transboundary species
+    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+
+    # Get current Spp that is not transboundary 
+    Current_Spp <- tibble(TaxonKey = Spp)
+
+    # Combine new spp with others
+    New_Non <- Non_Transboundary_Data %>% 
+      bind_rows(Current_Spp)
+
+    # Set a name for file and saves data
+    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
+    write.csv(New_Non, New_Non_Name, row.names = F)
+
+  }
+
+  ### Function return
+
+  EstTransIndex=Indexes # A dataframe with
+
+}
+```

### 2019-09-09 Initial_Analysis.Rmd
Included a missing headding
Updates results

@@
   "ggrepel", # for nice plot labels
+  "ggsflabel", # for nice sf_plots labels
   # "gridExtra",
@@
 
-### Sub Routine
+### Sub Routine; Neighbours
 
@@
 ```
-### Function `GetSppDist`
+
+### Estimate Transboundary Species
+
+#### Function `GetSppDist`
 
@@
 
-### Function `EstTransIndex`
-
-#### NOTES:
-
-##### General:
+#### Function `EstTransIndex`
+
+##### NOTES:
+
+###### General:
 - For now using SAU_C as presence absence
@@
 
-##### Tresholds:
-##### Model Index, line ~479
+###### Tresholds:
+###### Model Index, line ~479
 
@@
 
-##### Distribution Index, line ~482
+###### Distribution Index, line ~482
 
@@
 
+#### Function 'Mclapply_Hack'
+
 ```{r Mclapply_Hack_Fun, eval= T , echo = T, warning = F, message = F}
@@
 
-## Routine for estimating transboundary species
+## Principal Routine
+
+#### Control Pannel
 
@@
 # Set Jurisdiction to EEZ or RFMO
-Jurisdiction <- "EEZ"
+Jurisdiction <- "RFMO"
 
@@
 
+#### Run Routine
 ```{r Routine_parallel, eval = F, echo = F}
@@
 
+## Sub Routine; SAU Catch
+
+###`getSAucat`
+
+```{r getSAUCatch, eval = F, echo = F}
+
+# Function to get sau Catch data and total per country over a mean of (standarized 10 years )
+getSAUCatch <-function(TaxonKey, Coord, nyears = 10){
+  suppressMessages(
+
+  year <- 67-nyears-1
+
+Catch_Data <- GetSppDist(TaxonKey,Model="SAU_C",Coord = Coord) %>% 
+  select(year:67) %>% 
+  gather("Year","Catch",1:nyears) %>% 
+  filter(!is.na(Catch)) %>%  # remove NAs earlier
+  left_join(Index_Code,
+            by ="INDEX") %>% 
+  group_by(Species,Territory,Year) %>% 
+  summarise(Total_Catch = sum(Catch,na.rm=T)) %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Mean_Catch = mean(Total_Catch,na.rm=T))
+)
+return(Catch_Data)
+
+}
+
+```
+
+#### Run Subroutine
+
+```{r SAU_Catch_Data, eval = F, echo = F}
+
+# get SAU catch data per species per nation
+
+# Data needed for function
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+  Index_Code <- EEZIDs_List %>% 
+    left_join(EEZ_CellID) %>% 
+    rename(Territory = Name)
+
+  # Get list of species catch
+Trans_Spp_List <- unique(Clean_Results_Trans$TaxonKey)
+
+# Run routine and save it for latter
+Sau_Catch_Data <- bind_rows(mclapply(Trans_Spp_List, getSAUCatch, Coord=CoorG))
+
+write.csv(Sau_Catch_Data,
+          paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep=""),
+          row.names = F)
+
+```
+
 # Results
@@
 
+## Load Results data
+
 ```{r Load_Results_Data, eval = F}
+
+# Set Jurisdiction to EEZ or RFMO
+Jurisdiction <- "EEZ"
+
+# Updates result's path for the jurisdiction
+Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
 
@@
 
+# UN Regions dataset
+UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
+  select(Territory = Country.or.Area,
+         georegion = Region.Name)
+
+# Load Land shapefile
+path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
+# #The File
+fnam_world_land <- "ne_50m_admin_0_countries.shp"
+
+World_land_sf <- st_read(dsn = path_world_land,
+                         layer =file_path_sans_ext(fnam_world_land)) %>% 
+  rename(Territory = NAME)
+
+# head(World_land_sf)
 # Transboundary Results ####
@@
 # For Carmelia
+if(Jurisdiction == "EEZ"){
   if(Sys.info()[7] == "carmelia"){
-  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
+    Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
   }else{
-
+    # Read Sau Catch Data
+    Sau_Catch_Data <- fread(paste(Results_Path,"Speceies_Data/Sau_Catch_Data.csv")) %>% 
+      filter(!is.na(Territory))
     # For Hall and The Beast
-
+    # List of species
     Spp <- list.files(Results_Path)[1:672]
 
+    # Get resukts for all species
     Results_Trans <- GetTransResults(Spp)
 
-  # Clean out countries that share with their own borders
-
+    # Clean out countries that share with their own borders (Will be outdated soon)
     Auto_Remove_Territories <- Results_Trans %>%   
@@
              Country_Territory= FishingRegion,
-           FishingRegion=Neighbour_Territory,
+             FishingRegion=Neighbor_Territory, #Neighbour_Territory
              Model_Index,
@@
       select(1,2, 
-           Neighbour_Territory = FishingRegion,
+             Neighbor_Territory = FishingRegion,
              Model_Index:CT_fishing_entity,
@@
         CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
-      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour_Territory),paste(NT_fishing_entity)),
+        NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
         Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
@@
         Country_Territory %in% Islands_to_Remove |
-        Neighbour_Territory %in% Islands_to_Remove |
-        Country_Territory == "Balearic Island (Spain)" & Neighbour_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
-        Country_Territory == "British Virgin Isl. (UK)" & Neighbour_Territory == "Anguilla" |
-        Neighbour_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
-        Country_Territory == "Corsica (France)" & Neighbour_Territory == "France (Mediterranean)" |
-        Neighbour_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
-        Country_Territory == "Crete (Greece)" & Neighbour_Territory == "Grece" |
-        Neighbour_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
-        Country_Territory == "Cyprus (North)" & Neighbour_Territory == "Cyprus (South)" |
-        Neighbour_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
-        Country_Territory == "Channel Isl. (UK)" & Neighbour_Territory == "United Kingdom" |
-        Neighbour_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
-        Country_Territory == "Glorieuse Islands (France)" & Neighbour_Territory == "Mayotte (France)" |
-        Neighbour_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
-        Country_Territory == "Guam (USA)" & Neighbour_Territory == "Northern Marianas (USA)" |
-        Neighbour_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
-        Country_Territory == "Italy" & Neighbour_Territory == "Sardinia (Italy)" |
-        Neighbour_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
-        Country_Territory == "Italy" & Neighbour_Territory == "Sicily (Italy)" |
-        Neighbour_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
-        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (main islands)"|
-        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
-        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (Ogasawara Islands)"|
-        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
-        Country_Territory == "Norway" & Neighbour_Territory == "Svalbard Isl. (Norway)" |
-        Neighbour_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
-        Country_Territory == "Sicily (Italy)" & Neighbour_Territory == "Sardinia (Italy)" |
-        Neighbour_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
-        Country_Territory == "South Africa (Atlantic Coast)" & Neighbour_Territory == "South Africa (Indian Ocean Coast)" |
-        Neighbour_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
-        Country_Territory == "USA (Alaska, Arctic)" & Neighbour_Territory == "USA (Alaska, Subarctic)" |
-        Neighbour_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
-    ) %>%
-    group_by(Country_Territory,Neighbour_Territory) %>% 
+          Neighbor_Territory %in% Islands_to_Remove |
+          Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
+          Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
+          Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
+          Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
+          Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
+          Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
+          Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
+          Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
+          Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
+          Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
+          Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
+          Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
+          Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
+          Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
+          Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
+          Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
+          Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
+          Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
+          Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
+          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
+          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
+          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
+          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
+          Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
+          Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
+          Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
+          Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
+          Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
+          Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
+          Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
+          Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
+      ) %>%
+      group_by(Country_Territory,Neighbor_Territory) %>% 
       summarise(n())
@@
       anti_join(Territories_to_Remove,
-              by = c("Country_Territory","Neighbour_Territory")
-    ) %>% 
-    filter(Same_Nation == "No")
-
-} # closes ifstatement for carmelia temporal files
-# Load results for non transboundary (discrete) stocks
-# Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+                by = c("Country_Territory","Neighbor_Territory")
+      ) %>% 
+      filter(Same_Nation == "No") %>% 
+      rename(Territory = Country_Territory,
+             Neighbour = Neighbor_Territory)
 
@@
     # #Load it!
-# 
-World_EEZs <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-# 
-# head(World_EEZs)
-
-```
+
+    ### Sau Catch Data
+
+    SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep = ""), deader = TRUE)
+
+  } # closes ifstatement for carmelia temporal files
+}else{ # Closes EEZ ifelse
+
+  # List of files without the non-trans data file
+  Spp <- list.files(Results_Path)
+  Spp <- Spp[Spp !="Non_Transboundary_Data.csv"]
+
+  # Results loaing 
+  Results_Trans <- GetTransResults(Spp)
+
+  # Cleaning results (No cleaning needed for now)
+  Clean_Results_Trans <- Results_Trans
+
+  # Load results for non transboundary (discrete) stocks
+  Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
+    filter(!is.na(TaxonKey))
+
+  # Shapefiles 
+  path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO/",sep="")
+  # #The File
+  fnam_world <- "SAU_RFMO_Sept_2015.shp"
+
+}
+
+#  GLobal data depending on jursidiction
+# Load Regional shapefiles 
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(Territory = Name)
+
+```
+
+## Determine Tresholds
 
@@
 Transboundary_Spp <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index >= Min_AI,
+         Area_Index <= Max_AI,
+         Model_Index == MI#,
+         # Same_Nation == "No"
+         ) %>% 
+  group_by(Territory) %>% 
+  summarise(
+    n_trans_spp = length(unique(TaxonKey)),
+    n_Neighbours = length(unique(Neighbour)),
+    Trans_Rate = n_trans_spp/n_Neighbours
+    )
+
+### Non-transboundary
+
+Discrete_Spp <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI#,
+         # Same_Nation == "No"
+         ) %>% 
+  group_by(Territory) %>% 
+  summarise(
+    n_no_discrete_spp = length(unique(TaxonKey)),
+    n_Territories = length(unique(Territory))
+    )
+
+```
+
+## Results per Territory
+
+### Map of Transboundary Species
+
+```{r Territory_Map, eval =F, echo =F}
+
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Transboundary_Spp, by ="Territory")
+
+Catch_Country <- Sau_Catch_Data %>% 
+  group_by(FishingRegion=Territory) %>% 
+  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000,2)) %>% 
+  filter(!(is.na(FishingRegion))) %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  group_by(Territory = fishing_entity) %>% 
+  summarise(Total_Catch = sum(Total_Catch,na.rm=T))
+
+World_sf_si_land <- World_land_sf %>%
+  # st_transform(crs = 4326) %>% # 4326
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
+  left_join(Catch_Country, by ="Territory") # Include total specices catch
+
+# head(World_sf_si)s
+
+# Create a pellet for plotting
+# pal <- wes_palette("Zissou1", 1000, type = "continuous")
+
+World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 5)
+World_sf_si_land$BinsLan <- cut(World_sf_si_land$Total_Catch,breaks = 6)
+
+unique(World_sf_si$Bins)
+unique(World_sf_si_land$Bins)
+
+# levels(World_sf_si$Bins)
+# levels(World_sf_si_land$Bins_C)
+
+Plot <- ggplot() +
+  geom_sf(data = World_sf_si,aes(fill = Bins),colour="white") + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land,aes(fill = BinsLan),show.legend = FALSE) +
+  # scale_fill_gradientn(colours = pal,
+  #                      na.value = "white") +
+  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
+  #                              rev(wes_palette(n = 4, name = "Darjeeling1"))
+  #                              ),
+  #                    na.value = "white"
+  # ) +
+  scale_fill_manual(values = c("#5BBCD6","#5BBCD6","#F98400","#F98400","#F2AD00","#F2AD00","#00A08A","#00A08A","#FF0000","#FF0000"),
+                     na.value = "white"
+  ) +
+  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
+  #                    na.value = "white"
+  # ) +
+  ggtheme_map()
+
+Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Land.png", sep = "")
+
+ggsave(Plot_Name,
+       plot = Plot,
+       width = 16,
+       height = 8,
+       units = "in",
+       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+)
+
+```
+
+### OHI-inspired Circular plot Countries
+
+```{r species_circluar_plot, eval = F, echo =F}
+
+Countries_Data <- Clean_Results_Trans %>% 
   filter(
@@
          ) %>% 
-  group_by(Name=Country_Territory) %>% 
-  summarise(
-    n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbour_Territory)),
-    Trans_Rate = n_trans/n_countries
-    )
-  # filter(Model_Index == 100)
-  # head(Results_Data)
-
-### Non-transboundary
-
-Discrete_Spp <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No"
-         ) %>% 
-  group_by(Name=Country_Territory) %>% 
-  summarise(
-    n_no_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbour_Territory))
-  )
-
-```
-
-## Validate Results using RFMOs
-
-```{Validation_RFMOs}
-
-#### Load RFMO data provided by Vicky (SAU)
-
-RFMOs_sf <- fread(paste(Data_Path,"Spatial_Data/SAU_RFMO/SAU_RFMO_Sept_2015.shp",sep=""))
-
-```
-
-## Analysis per Country
-
-```{Tran_country_Map, eval =F, echo =F}
-
-World_EEZs_simple <- World_EEZs %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(TenTwenyfive, by ="Name") #%>%
-  # filter(!is.na(n_trans)) #%>%
-  # st_transform(crs = 3832)
-
-pal <- wes_palette("Zissou1", 1000, type = "continuous")
-
-Plot <- ggplot(World_EEZs_simple) +
-  geom_sf(aes(fill = n_trans)) +
-  scale_fill_gradientn(colours = pal,
-                       na.value = "white") +
-  ggtheme_map() +
-  facet_wrap(~Model)
-
-ggsave("R4_100_25.png",
-       plot = Plot,
-       width = 16,
-       height = 8,
+  group_by(Territory = CT_fishing_entity) %>% 
+  summarise(value = length(unique(TaxonKey))) %>% 
+  left_join(UN_Regions, by ="Territory") %>%
+  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+  rename(FishingRegion=Territory) %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  group_by(individual = fishing_entity,group) %>% 
+  summarise(Total_Catch = sum(value,na.rm=T)) %>% 
+  arrange(group,Total_Catch) %>% 
+  filter(!is.na(individual)) %>% 
+  select(individual,group,value=Total_Catch)
+
+# hist(Countries_Data$value)
+# unique(Countries_Data$group)
+Median_trans <- median(Countries_Data$value,na.rm=T)
+Char <- as.factor(Countries_Data$group)
+
+# Set a number of 'empty bar' to add at the end of each group
+empty_bar <- length(unique(Countries_Data$group))
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data)) )
+colnames(to_add) <- colnames(Countries_Data)
+to_add$group <- rep(levels(Char), each=empty_bar)
+Countries_Data <- bind_rows(Countries_Data, to_add)
+Countries_Data <- Countries_Data %>% arrange(group,value)
+Countries_Data$id <- seq(1, nrow(Countries_Data))
+
+# Get the name and the y position of each label
+label_data <- Countries_Data
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# prepare a data frame for base lines
+base_data <- Countries_Data %>% 
+  group_by(group) %>% 
+  summarize(start=min(id), end=max(id) - empty_bar) %>% 
+  rowwise() %>% 
+  mutate(title=mean(c(start, end)))
+
+# prepare a data frame for grid (scales)
+grid_data <- base_data
+grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
+grid_data$start <- grid_data$start - 1
+grid_data <- grid_data[-1,]
+
+# Make the plot
+ggplot(Countries_Data, 
+       aes(x=as.factor(id), 
+           y=value,
+           fill=group)
+       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=group),
+           stat="identity",
+           alpha=0.5) +
+  scale_fill_manual("Ecosystem Preference",
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 4, name = "Darjeeling2")
+                               ),
+                     na.value = "white"
+  ) +
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") +
+  # Add text showing the value of each line
+  annotate("text", 
+           x = rep(max(Countries_Data$id),4),
+           y = c(20, 40, 60, 80,100),
+           label = c("20", "40", "60"),
+           color="grey", 
+           size=3 , 
+           angle=0, 
+           fontface="bold",
+           hjust=1) +
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=group),
+           stat="identity",
+           alpha=0.5) +
+  ylim(-100,200) + # sets the circle the first value the central the last value how wide
+  theme_minimal() +
+  theme(
+    legend.position = c(0.5,0.5),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() + 
+  geom_text(data=label_data, 
+            aes(x=id, y=110,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            # fontface="bold",
+            alpha=0.6,
+            size=2.5,
+            angle= label_data$angle,
+            inherit.aes = FALSE ) +
+  geom_text(aes(x = 229, 
+                y = 14,
+                label = "Median"),
+            colour = "grey", 
+            size = 2.5,
+            alpha=0.6,
+            angle=5,
+            inherit.aes = FALSE) +
+  # Add base line information
+  geom_segment(data=base_data, 
+               aes(x = start, 
+                   y = -5, 
+                   xend = end, 
+                   yend = -5
+                   ), 
+               colour = "black",
+               alpha=0.8, 
+               size=0.6 , 
+               inherit.aes = FALSE)
+
+ggsave(
+    plot = last_plot(),
+    width = 14,
+    height = 10,
     units = "in",
+    filename = "Territory_circular_over10.tiff",
     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
@@
   summarise(
-    n_countries = length(unique(Country_Territory))
+    n_countries = length(unique(Territory))
   ) %>% 
@@
 
+### OHI-inspired Circular plot Species
+
+```{r species_circluar_plot, eval = F, echo =F}
+
+Species_Data <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index >= Min_AI,
+         Area_Index <= Max_AI,
+         Model_Index == MI#,
+         # Same_Nation == "No"
+         ) %>% 
+  group_by(TaxonKey) %>% 
+  summarise(n_trans_spp = length(unique(Territory))) %>% 
+  left_join(Exploited_Species) %>%
+  rename(scientific_name = TaxonName) %>% 
+  left_join(Species_environ_list) %>%
+  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag))) %>% 
+  select(individual=scientific_name,
+         value = n_trans_spp,
+         group = DemersPelag) %>% 
+  arrange(group,value) %>% 
+  filter(value > 10)
+
+Median_trans <- median(Species_Data$value)
+# hist(Species_Data$value)
+# unique(Species_Data$group)
+
+Char <- as.factor(Species_Data$group)
+
+# Set a number of 'empty bar' to add at the end of each group
+empty_bar <- 8
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
+colnames(to_add) <- colnames(Species_Data)
+to_add$group <- rep(levels(Char), each=empty_bar)
+Species_Data <- rbind(Species_Data, to_add)
+Species_Data <- Species_Data %>% arrange(group,value)
+Species_Data$id <- seq(1, nrow(Species_Data))
+
+# Get the name and the y position of each label
+label_data <- Species_Data
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# prepare a data frame for base lines
+base_data <- Species_Data %>% 
+  group_by(group) %>% 
+  summarize(start=min(id), end=max(id) - empty_bar) %>% 
+  rowwise() %>% 
+  mutate(title=mean(c(start, end)))
+
+# prepare a data frame for grid (scales)
+grid_data <- base_data
+grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
+grid_data$start <- grid_data$start - 1
+grid_data <- grid_data[-1,]
+
+# Make the plot
+ggplot(Species_Data, 
+       aes(x=as.factor(id), 
+           y=value,
+           fill=group)
+       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=group),
+           stat="identity",
+           alpha=0.5) +
+  scale_fill_manual("Ecosystem Preference",
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 4, name = "Darjeeling2")
+                               ),
+                     na.value = "white"
+  ) +
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") +
+  # Add text showing the value of each line
+  annotate("text", 
+           x = rep(max(Species_Data$id),5),
+           y = c(20, 40, 60, 80,100),
+           label = c("20", "40", "60", "80","100"),
+           color="grey", 
+           size=3 , 
+           angle=0, 
+           fontface="bold",
+           hjust=1) +
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=group),
+           stat="identity",
+           alpha=0.5) +
+  ylim(-100,200) + # sets the circle the first value the central the last value how wide
+  theme_minimal() +
+  theme(
+    legend.position = c(0.5,0.5),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  geom_text(aes(x = 229, 
+                y = 14,
+                label = "Median"),
+            colour = "grey", 
+            size = 2.5,
+            alpha=0.6,
+            angle=5,
+            inherit.aes = FALSE) +
+  geom_text(data=label_data, 
+            aes(x=id, y=110,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            # fontface="bold",
+            alpha=0.6,
+            size=2.5,
+            angle= label_data$angle,
+            inherit.aes = FALSE ) +
+  # Add base line information
+  geom_segment(data=base_data, 
+               aes(x = start, 
+                   y = -5, 
+                   xend = end, 
+                   yend = -5
+                   ), 
+               colour = "black",
+               alpha=0.8, 
+               size=0.6 , 
+               inherit.aes = FALSE) +
+  coord_polar()
+
+ggsave(
+    plot = last_plot(),
+    width = 14,
+    height = 10,
+    units = "in",
+    filename = "Species_circular_over10.tiff",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+  )
+
+```
+
 ```{r Top_spp_Circle_Diagram, eval =F, echo = F}

### 2019-09-09 Initial_Analysis.Rmd
small updates
Include catches in main function

@@
               by = "INDEX") %>%  # Inclu
-    rename(Country_Territory = Name)
+    rename(Country_Territory = Territory)
 
@@
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
 # #The File
@@
  system.time(
-  EEZ_Neighbour_List <- EstNeighbours(World_EEZs, Partial = T)
+  EEZ_Neighbour_List <- EstNeighbours(World_EEZs, Partial = F)
  )
 # 8203.05    0.25 8204.51 (around 2 hours 30 min)
+
+# user  system elapsed 
+# 291.53  238.73  530.73 (SO MUCH FASTER!)
 
@@
 #### For testing 
-# Spp <- #600004  # Anchovie Equator, Chile and Peru
+#Spp <- 600004  # Anchovie Equator, Chile and Peru
 # Spp <- 600107 # Tuna Many RFMOs
-# Model <- "All"
-# Coord = CoorG
+#Model <- "All"
+#Coord = CoorG
 
 # For EEZ
- # Neighbours <- Neighbours_EEZ
- # Index_Code <- EEZ_Index_Code
+# Neighbours <- Neighbours_Data
+# Index_Code <- Index_Code
 
@@
 # The function
-EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){
+EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type,Catch = "N"){
 
@@
     File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
-    Save_Path <- paste(Results_Path,File_Name,sep="")
+    Save_Path <- paste(Results_Path,"/Trans_Results/",File_Name,sep="")
 
@@
     # Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+    Non_Transboundary_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep=""))
 
@@
     # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
+    New_Non_Name <- paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")
     write.csv(New_Non, New_Non_Name, row.names = F)
+
+  }
+
+  ### Get Specie's catch
+
+Catch_Data <- SppDist %>%
+  filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
+           Model == "SAU_C",
+         Value > 0) %>%
+  left_join(Index_Code,
+            by ="INDEX") %>% 
+  group_by(TaxonKey,Territory) %>% 
+  summarise(Total_Catch = sum(Value,na.rm=T))
+
+  ### Save Catch data
+
+ if(nrow(Catch_Data) > 0 & Catch == "Y"){
+
+    File_Name <- paste(Spp,"_Catch.csv",sep = "")
+    Save_Path <- paste(Results_Path,"/Catch_Results/",File_Name,sep="")
+
+    write.csv(Catch_Data,
+              Save_Path,
+              row.names = F)
 
@@
 # __________________________________
-# EstTransIndex(Spp = 600107,
+# EstTransIndex(Spp = 600004,
  #              Mode = "All",
-#               Neighbours = ,Coord,Index_Code,Save="Y")
-# 
+  #             Neighbours = Neighbours_Data,
+   #            Coord = CoorG,
+    #           Index_Code=Index_Code,
+     #          Jurisdiction_Type = "EEZ",
+      #         Save="Y",
+       #        Catch = "Y")
+
 # Spp <-  # Tuna Many RFMOs
@@
 # Set Jurisdiction to EEZ or RFMO
-Jurisdiction <- "RFMO"
+Jurisdiction <- "EEZ"
 
@@
 # Creates dummy dataset for Non transboundary species
-write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
+write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Trans_Results/Non_Transboundary_Data.csv",sep=""), row.names = F)
 
@@
       Save = "Y",  # For saving
+      Catch = "Y",
       Jurisdiction_Type = Jurisdiction # For saving in proper path

### 2019-09-09 Initial_Analysis.Rmd
Good luck...

--- 2019-09-09 Initial_Analysis.Rmd
@@
 Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
+Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"
 
@@
 UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
-  select(Territory = Country.or.Area,
-         georegion = Region.Name)
+  group_by(Territory = Country.or.Area,
+    georegion = Region.Name) %>% 
+  summarise(n=n()) %>% #merge china's 3 rows
+  select(-n) %>% 
+  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
+  ungroup() %>% 
+  mutate(
+    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
+    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
+    Territory = gsub( "United States of America", "USA",Territory),
+    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
+    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
+    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
+    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
+    # Territory = gsub("Congo", "Congo, R. of",Territory),
+    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
+    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
+    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
+    Territory = gsub(" and ", " & ",Territory),
+    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
+    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
+  )
+
+# Manually change congo
+UN_Regions[52,1] <- "Congo, R. of"
 
@@
     # Read Sau Catch Data
-    Sau_Catch_Data <- fread(paste(Results_Path,"Speceies_Data/Sau_Catch_Data.csv")) %>% 
+    Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
       filter(!is.na(Territory))
@@
 
-    SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep = ""), deader = TRUE)
+    SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep = ""), header = TRUE)
 
@@
   st_transform(crs = 4326) %>% # 4326
+  # st_transform(crs = "+proj=moll") %>% # tubed world
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
@@
   group_by(FishingRegion=Territory) %>% 
-  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000,2)) %>% 
+  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
   filter(!(is.na(FishingRegion))) %>% 
@@
 World_sf_si_land <- World_land_sf %>%
-  # st_transform(crs = 4326) %>% # 4326
-  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
+  st_transform(crs = 4326) %>% # 4326
+  # st_transform(crs = "+proj=moll") %>% # tubed world
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
   left_join(Catch_Country, by ="Territory") # Include total specices catch
@@
 World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 5)
-World_sf_si_land$BinsLan <- cut(World_sf_si_land$Total_Catch,breaks = 6)
+World_sf_si_land$BinsLan <- cut(World_sf_si_land$Total_Catch,breaks = 5)
 
 unique(World_sf_si$Bins)
-unique(World_sf_si_land$Bins)
-
-# levels(World_sf_si$Bins)
-# levels(World_sf_si_land$Bins_C)
+unique(World_sf_si_land$BinsLan)
+
+levels(World_sf_si$Bins)
+levels(World_sf_si_land$BinsLan)
 
 Plot <- ggplot() +
-  geom_sf(data = World_sf_si,aes(fill = Bins),colour="white") + # n_trans_spp or Bins
-  geom_sf(data = World_sf_si_land,aes(fill = BinsLan),show.legend = FALSE) +
+  geom_sf(data = World_sf_si_land,aes(fill = BinsLan)) +
+  geom_sf(data = World_sf_si,aes(fill = Bins)) + # n_trans_spp or Bins
   # scale_fill_gradientn(colours = pal,
@@
   # ) +
-  scale_fill_manual(values = c("#5BBCD6","#5BBCD6","#F98400","#F98400","#F2AD00","#F2AD00","#00A08A","#00A08A","#FF0000","#FF0000"),
+  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#F98400","#F98400","#F2AD00","#F2AD00","#00A08A","#FF0000","#FF0000","#FF0000"),
                      na.value = "white"
@@
 
-### OHI-inspired Circular plot Countries
-
-```{r species_circluar_plot, eval = F, echo =F}
+### OHI-inspired Circular plot for Territories
+
+```{r Territories_Circluar_Plot, eval = T, echo = T}
 
@@
   group_by(individual = fishing_entity,group) %>% 
-  summarise(Total_Catch = sum(value,na.rm=T)) %>% 
-  arrange(group,Total_Catch) %>% 
+  summarise(Total_trans = sum(value,na.rm=T)) %>% 
   filter(!is.na(individual)) %>% 
-  select(individual,group,value=Total_Catch)
+  select(individual,group,value=Total_trans) %>% 
+  arrange(group,value)
 
@@
 # Get the name and the y position of each label
+
+# Top n of each group label
+Top_Countries <- Countries_Data %>% 
+  group_by(group) %>% 
+  top_n(5,value)
+
+# Create labels for all but top 5
 label_data <- Countries_Data 
@@
 
+# Remove top 5
+label_data_rest <- label_data %>% 
+  filter(!individual %in% Top_Countries$individual)
+
+# Create labels for top 5
+Top_label_data <- label_data %>% 
+  filter(individual %in% Top_Countries$individual)
+
 # prepare a data frame for base lines
@@
   group_by(group) %>% 
-  summarize(start=min(id), end=max(id) - empty_bar) %>% 
+  summarize(start=min(id), 
+            end=max(id) - empty_bar, 
+            median = median(value, na.rm = T)
+            ) %>% 
   rowwise() %>% 
@@
 grid_data$start <- grid_data$start - 1
-grid_data <- grid_data[-1,]
-
+grid_data[1,2] <- 5 # Manually include Africa for the median
+grid_data[1,3] <- 1
+
+# Median data
+median_data <- grid_data %>% 
+  mutate_at(vars(start,end),
+            .funs = as.numeric)
+
+# -------------------------- #
 # Make the plot
+# -------------------------- #
+# Base plot
 ggplot(Countries_Data, 
@@
            alpha=0.5) +
-  scale_fill_manual("Ecosystem Preference",
-                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 4, name = "Darjeeling2")
-                               ),
-                     na.value = "white"
-  ) +
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
   geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
@@
   geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") +
+  # Add median lines for each gropup
+  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
+               alpha=1, size=0.5 , inherit.aes = FALSE ) +
+  # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median
   # Add text showing the value of each line
   annotate("text", 
-           x = rep(max(Countries_Data$id),4),
-           y = c(20, 40, 60, 80,100),
-           label = c("20", "40", "60"),
+           x = rep(max(Countries_Data$id),5),
+           y = c(20, 40, 60, 80, 100),
+           label = c("20", "40", "60","80",">100"),
            color="grey", 
@@
            alpha=0.5) +
-  ylim(-100,200) + # sets the circle the first value the central the last value how wide
-  theme_minimal() +
-  theme(
-    legend.position = c(0.5,0.5),
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() + 
-  geom_text(data=label_data, 
+  geom_text(data=label_data_rest,
             aes(x=id, y=110,
@@
             size=2.5,
-            angle= label_data$angle,
-            inherit.aes = FALSE ) +
-  geom_text(aes(x = 229, 
-                y = 14,
-                label = "Median"),
-            colour = "grey", 
-            size = 2.5,
+            angle= label_data_rest$angle,
+            inherit.aes = FALSE) +
+  # Bold top 3 
+  geom_text(data=Top_label_data,
+            aes(x=id, y=110,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
             alpha=0.6,
-            angle=5,
+            size=2.5,
+            angle= Top_label_data$angle,
             inherit.aes = FALSE) +
@@
                size=0.6 , 
-               inherit.aes = FALSE)
-
-ggsave(
-    plot = last_plot(),
-    width = 14,
-    height = 10,
-    units = "in",
-    filename = "Territory_circular_over10.tiff",
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-  )
+               inherit.aes = FALSE) +
+  ylim(-140,140) + # sets the circle the first value the central the last value how wide
+  theme_minimal() +
+  theme(
+    legend.position = c(0.5,0.5),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() + 
+  scale_fill_manual("Continent",
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 4, name = "Darjeeling2")
+                    ),
+                    na.value = "white"
+  ) +
+  scale_colour_manual("Continent",
+                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                                 wes_palette(n = 4, name = "Darjeeling2")
+                      ),
+                      na.value = "white"
+  )
+
+#  Warring of missing values are the NA's for the columns
+
+# Save plot
+
+# ggsave(
+#     plot = last_plot(),
+#     width = 14,
+#     height = 10,
+#     units = "in",
+#     filename = "Territory_circular.tiff",
+#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+#   )
 
@@
 
-```{n_species_country, eval =F, echo =F}
-
+```{r n_species_country, eval = T, echo =F}
 # Number of countries shared by each Species
@@
 
-```{r species_circluar_plot, eval = F, echo =F}
+```{r species_circluar_plot, eval = T, echo = T}
 
@@
   left_join(Species_environ_list) %>%
-  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag))) %>% 
+  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
+         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
   select(individual=scientific_name,
@@
   arrange(group,value) %>% 
-  filter(value > 10)
+  filter(value > 10) # remove all species under 10 (way too many to plot!)
 
@@
 # Get the name and the y position of each label
+
+# Create labels for all but top 5
+label_data <- Countries_Data 
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# Get the name and the y position of each label
+# Top n of each group label
+Top_spp <- Species_Data %>% 
+  group_by(group) %>% 
+  top_n(5,value)
+
+# Create labels for all but top 5
 label_data <- Species_Data
@@
 
+# Remove top 5
+label_data_rest <- label_data %>% 
+  filter(!individual %in% Top_spp$individual)
+
+# Create labels for top 5
+Top_label_data <- label_data %>% 
+  filter(individual %in% Top_spp$individual)
+
 # prepare a data frame for base lines
@@
 grid_data$start <- grid_data$start - 1
-grid_data <- grid_data[-1,]
+# grid_data <- grid_data[-1,]
+grid_data[1,2] <- 5 # Manually include bathydemerssal
+grid_data[1,3] <- 1
+
+# Median data
+median_data <- grid_data %>% 
+  mutate_at(vars(start,end),
+            .funs = as.numeric)
 
@@
            alpha=0.5) +
-  scale_fill_manual("Ecosystem Preference",
-                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 4, name = "Darjeeling2")
-                               ),
-                     na.value = "white"
-  ) +
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
@@
   geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") +
+  # Add median lines for each gropup
+  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
+               alpha=1, size=0.5 , inherit.aes = FALSE ) +
+  # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median
   # Add text showing the value of each line
@@
            x = rep(max(Species_Data$id),5),
-           y = c(20, 40, 60, 80,100),
-           label = c("20", "40", "60", "80","100"),
+           y = c(20, 40, 60, 80, 100),
+           label = c("20", "40", "60","80",">100"),
            color="grey", 
@@
            alpha=0.5) +
-  ylim(-100,200) + # sets the circle the first value the central the last value how wide
-  theme_minimal() +
-  theme(
-    legend.position = c(0.5,0.5),
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  geom_text(aes(x = 229, 
-                y = 14,
-                label = "Median"),
-            colour = "grey", 
-            size = 2.5,
-            alpha=0.6,
-            angle=5,
-            inherit.aes = FALSE) +
-  geom_text(data=label_data, 
+  geom_text(data=label_data_rest,
             aes(x=id, y=110,
@@
             size=2.5,
-            angle= label_data$angle,
-            inherit.aes = FALSE ) +
+            angle= label_data_rest$angle,
+            inherit.aes = FALSE) +
+  # Bold top 3 
+  geom_text(data=Top_label_data,
+            aes(x=id, y=110,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
+            alpha=0.6,
+            size=2.5,
+            angle= Top_label_data$angle,
+            inherit.aes = FALSE) +
   # Add base line information
@@
                inherit.aes = FALSE) +
-  coord_polar()
+  ylim(-140,140) + # sets the circle the first value the central the last value how wide
+  theme_minimal() +
+  theme(
+    legend.position = c(0.5,0.5),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() + 
+  scale_fill_manual("Ecosystem Preference",
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 4, name = "Darjeeling2")
+                    ),
+                    na.value = "white"
+  ) +
+  scale_colour_manual("Ecosystem Preference",
+                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                                 wes_palette(n = 4, name = "Darjeeling2")
+                      ),
+                      na.value = "white"
+  )
 
@@
 # Extra Analysis
-
 ## Extra Analysis; Functions

### 2019-09-10 RFMO Analysis.Rmd
Created an extra file for RFMO and worked some plots

--- 2019-09-09 Initial_Analysis.Rmd
@@
 ---
-title: "Initial Analysis"
+title: "RFMO Initial Analysis"
 author: "Juliano Palacios-Abrantes"

### 2019-09-12 Initial_Analysis.Rmd
Updated main function to account for "discrete" stocks. Still need to modify path to new folder

--- 2019-09-09 Initial_Analysis.Rmd
@@
 
-#### RFMO
-
-```{r RFMO_Index, eval = F, echo = F}
-
-#### Load Data Needed ####
-
-# SAU RFMO shapefile
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO",sep="")
-# #The File
-fnam_world <- "SAU_RFMO_Sept_2015.shx"
-# #Load it!
-# 
-RFMOs_sf <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world)) %>% 
-  dplyr::rename(Name = RFMO_nm_s) %>% 
-  st_set_crs(3832) %>% # Making sure is same proyection
-  st_transform(3832) # to match shapefiles
-
-# Load coordinate system
-
-Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
-# COnvert Coor system to sf
-Coor_sf = st_as_sf(Coor,
-                        coords = c("Longitude", "Latitude")) %>% 
-  st_set_crs(3832) %>% # to match shapefiles
-  st_transform(3832) # to match shapefiles
-
-# Merge RFMO and coor datasets
-RFMO_Coor <- st_join(RFMOs_sf,
-                         Coor_sf,
-                         join = st_contains) %>% 
-  filter(!is.na(INDEX)) # Remove regions beyond RFMOs
-
-# head(RFMO_Coor)
-
-# Convert it back to a data frame and select only the two columns we want
-RFMO_INDEX <- as.data.frame(RFMO_Coor) %>% 
-  select(INDEX,Name) %>% 
-  arrange(INDEX)
-
-# head(RFMO_INDEX)
-
-# Save new data
-write.csv(RFMO_INDEX,
-          paste(Data_Path,"Spatial_Data/RFMO/RFMO_INDEX.csv",sep=""),
-          row.names = F
-          )
-
-# Map it (works!)
-
-# RFMO_INDEX %>%
-#   left_join(Coor,
-#             by = "INDEX") %>%
-#   ggplot(.,
-#             aes(x = Longitude,
-#                 y = Latitude,
-#                 color = Territory,
-#                 fill = Territory)
-#             ) +
-#   geom_tile() 
-# 
-# 
-# RFMO_INDEX %>%
-#   left_join(Coor,
-#             by = "INDEX") %>%
-#   ggplot(.,
-#             aes(x = Longitude,
-#                 y = Latitude,
-#                 color = INDEX,
-#                 fill = INDEX)
-#             ) +
-#   geom_tile() +
-#   facet_wrap(~Territory)
-
-```
-
-```{r RFMO_Neighbourds_Control_Pannel, eval = F, echo = F}
-
-#### Load Data Needed ####
-
-# SAU RFMO shapefile
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO",sep="")
-# #The File
-fnam_world <- "SAU_RFMO_Sept_2015.shx"
-# #Load it!
-# 
-RFMOs_sf <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world)) %>% 
-  dplyr::rename(Name = RFMO_nm_s)
-
-# Run Function (Ran and saved May 27 2019 at 6pm)
- system.time(
-  RFMO_Neighbour_List <- EstNeighbours(RFMOs_sf, Partial = T)
- )
-# 8203.05    0.25 8204.51 (around 2 hours 30 min)
-
- ## Include Index column
-
-RFMO_Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbour_List.csv",sep=""),header = TRUE) %>% 
-  left_join(RFMO_INDEX,
-            by = "Name") %>% 
-  rename(Territory = Name,
-         Neighbour = Neighbour_Territory)
-
-# head(RFMO_Neighbour_List)
-
-write.csv(RFMO_Neighbour_List,
-          paste(Data_Path,"Spatial_Data/RFMO_Neighbour_List.csv", sep =""),
-          row.names = F)
-
-```
-
 ### Estimate Transboundary Species
@@
       mutate(INDEX = INDEX) %>% 
-      gather("Year","Catch",1:10) %>% # Last 10 years of data
+      gather("Year","Catch",CATCH.56:CATCH.65) %>% # Last 10 years of data
       group_by(INDEX) %>% 
@@
 #### For testing 
-# Spp <- #600004  # Anchovie Equator, Chile and Peru
+# Spp <- 604250  # Anchovie Equator, Chile and Peru
 # Spp <- 600107 # Tuna Many RFMOs
+# Spp <- 600464 # Discrete species 
+# x <- c(600464, # Discreat spp in one nation
+      # 600059, # nowhere to be found spp
+       # 601352, # Discrete spp in two nations
+       # 600004) # transboundary spp
 # Model <- "All"
-# Coord = CoorG
-
-# For EEZ
- # Neighbours <- Neighbours_EEZ
- # Index_Code <- EEZ_Index_Code
-
- # For RFMO 
- # Index_Code <- RFMO_INDEX
- # Neighbours <- RFMO_Neighbor_List %>% 
- #   rename(Territory = Name,
- #         Neighbour = Neighbor_Territory)
-
+# Coord <- CoorG
+# 
+# # For EEZ
+# Neighbours <- Neighbours_Data
+# Index_Code <- Index_Code
+#  
 # __________________________________
@@
 
+  # if(n_Territory > 1){
+
   #Step 1.  Get EEZ id and Neighbour
@@
 
+  # IF SPECIES DISCRETE AND APEARS IN ONLY 1 REGION OR > 1 REGION BUT NOT NEIGHBOURS #
+
+  if(nrow(Spp_Grid) == 0 & Save == "Y"){
+
+    # IF SPECIES IS DISCRETE AND ONLY APEARS IN ONE REGION
+  Discrete_Territory <- unique(Model_Index_D$Territory)
+  n_Territory <- length(Discrete_Territory)
+
+    # Reads dataset of Non transboundary species
+    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+
+    # Get current Spp that is not transboundary 
+    Current_Spp <- tibble(TaxonKey = as.integer(Spp),
+                          Territory = Discrete_Territory)
+
+    # Combine new spp with others
+    New_Non <- Non_Transboundary_Data %>% 
+      bind_rows(Current_Spp)
+
+    # Set a name for file and saves data
+    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
+    write.csv(New_Non, New_Non_Name, row.names = F)
+
+    if(n_Territory ==1){
+
+    To_Print <- paste(Spp, "is only present in",Discrete_Territory)
+    print(To_Print)
+    paste(Spp, "is only present in",Discrete_Territory)
+    }else{
+
+      To_Print <- paste(Spp, "is in both (non-neighbouring)",Discrete_Territory[1],Discrete_Territory[2])
+      print(To_Print)
+    }
+
+  EstTransIndex=Current_Spp
+    print(To_Print)
+  }
+
+  if(nrow(Spp_Grid) > 0 & Save == "Y"){
+
   # Step 3. Sum total grids per Neighbours
@@
   }
-
-  if(nrow(Indexes) == 0 & Save == "Y"){
-
-    # Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
-
-    # Get current Spp that is not transboundary 
-    Current_Spp <- tibble(TaxonKey = Spp)
-
-    # Combine new spp with others
-    New_Non <- Non_Transboundary_Data %>% 
-      bind_rows(Current_Spp)
-
-    # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
-    write.csv(New_Non, New_Non_Name, row.names = F)
-
-  }
-
   ### Function return
-
   EstTransIndex=Indexes # A dataframe with
 
+  } # Closes Treshold 3
 }
@@
 # __________________________________
+
+# Spp <-  # Tuna Many RFMOs
+# Model <- "All"
+# Coord = CoorG
+# #
+# 
+# # For EEZ
+# Neighbours <- Neighbours_EEZ
+# Index_Code <- EEZ_Index_Code
+# 
+# 
 # EstTransIndex(Spp = 600107,
@@
 #               Neighbours = ,Coord,Index_Code,Save="Y")
-# 
-# Spp <-  # Tuna Many RFMOs
-# Model <- "All"
-# Coord = CoorG
-# 
-# # For EEZ
-#  # Neighbours <- Neighbours_EEZ
-#  # Index_Code <- EEZ_Index_Code
-#  
-#  # For RFMO 
-#  Index_Code <- RFMO_INDEX
-#  Neighbours <- RFMO_Neighbor_List %>% 
-#    rename(Territory = Name,
-#          Neighbour = Neighbor_Territory)
 
@@
 # Creates dummy dataset for Non transboundary species
-write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
+write.csv(tibble(), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)
 
@@
 system.time(
-  Spp_Trans <- bind_rows(
+  Dis_Trans <- bind_rows(
     mclapply(
@@
 
-## Sub Routine; SAU Catch
-
-###`getSAucat`
-
-```{r getSAUCatch, eval = F, echo = F}
-
-# Function to get sau Catch data and total per country over a mean of (standarized 10 years )
-getSAUCatch <-function(TaxonKey, Coord, nyears = 10){
-  suppressMessages(
-
-  year <- 67-nyears-1
-
-Catch_Data <- GetSppDist(TaxonKey,Model="SAU_C",Coord = Coord) %>% 
-  select(year:67) %>% 
-  gather("Year","Catch",1:nyears) %>% 
-  filter(!is.na(Catch)) %>%  # remove NAs earlier
-  left_join(Index_Code,
-            by ="INDEX") %>% 
-  group_by(Species,Territory,Year) %>% 
-  summarise(Total_Catch = sum(Catch,na.rm=T)) %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Mean_Catch = mean(Total_Catch,na.rm=T))
-)
-return(Catch_Data)
-
-}
-
-```
-
-#### Run Subroutine
-
-```{r SAU_Catch_Data, eval = F, echo = F}
-
-# get SAU catch data per species per nation
-
-# Data needed for function
-CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
-  mutate(INDEX = seq(1,259200,1))
-
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-  Index_Code <- EEZIDs_List %>% 
-    left_join(EEZ_CellID) %>% 
-    rename(Territory = Name)
-
-  # Get list of species catch
-Trans_Spp_List <- unique(Clean_Results_Trans$TaxonKey)
-
-# Run routine and save it for latter
-Sau_Catch_Data <- bind_rows(mclapply(Trans_Spp_List, getSAUCatch, Coord=CoorG))
-
-write.csv(Sau_Catch_Data,
-          paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep=""),
-          row.names = F)
-
-```
-
 # Results
@@
   # Set the path for each file
-  Distpath <- paste(Results_Path,Spp,sep="")
+  Distpath <- paste(Results_Path,"/Trans_Results/",Spp,sep="")
 
@@
 Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
-Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"
+
+# In case you want to use old results (ran with older verion of neighbours)
+# Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"
 
@@
   ungroup() %>% 
+  # Change names to match SAU data and for shorter versions
   mutate(
@@
 # head(World_land_sf)
+
+# Load EEZ shapefiles 
+# SAU shapefile name and paths
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
+
+fnam_world <- "SAUEEZ_July2015.shp"
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(Territory = Name)
+
+# ---------------------------- #
 # Transboundary Results ####
-
-# For Carmelia
-if(Jurisdiction == "EEZ"){
-  if(Sys.info()[7] == "carmelia"){
+# ---------------------------- #
+
+if(Sys.info()[7] == "carmelia"){ # For Carmelia
+
   Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
-  }else{
+}else{  # For Hall and The Beast
+
   # Read Sau Catch Data
@@
     filter(!is.na(Territory))
-    # For Hall and The Beast
+
   # List of species
-    Spp <- list.files(Results_Path)[1:672]
-
-    # Get resukts for all species
+  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[1:672]
+
+  # ---------------------------- #
+  # Load and clean Transboundary results
   Results_Trans <- GetTransResults(Spp)
 
-    # Clean out countries that share with their own borders (Will be outdated soon)
+  # Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
   Auto_Remove_Territories <- Results_Trans %>%   
-      rename(FishingRegion=Country_Territory) %>% 
+    rename(FishingRegion=Territory) %>% 
     left_join(Clean_sau_eez_fes,
@@
     select(TaxonKey,
-             Country_Territory= FishingRegion,
-             FishingRegion=Neighbor_Territory, #Neighbour_Territory
+           Territory= FishingRegion,
+           FishingRegion=Neighbour, #Neighbour_Territory
            Model_Index,
@@
     select(1,2, 
-             Neighbor_Territory = FishingRegion,
+           Neighbour = FishingRegion,
            Model_Index:CT_fishing_entity,
@@
     mutate(
-        CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
-        NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
+      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
+      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
       Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
@@
   # List of territories to eliminate (No other neighobors but mainland)
+
   Islands_to_Remove <- c(
@@
     filter(
-        Country_Territory %in% Islands_to_Remove |
-          Neighbor_Territory %in% Islands_to_Remove |
-          Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
-          Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
-          Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
-          Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
-          Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
-          Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
-          Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
-          Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
-          Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
-          Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
-          Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
-          Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
-          Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
-          Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
-          Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
-          Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
-          Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
-          Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
-          Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
-          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
-          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
-          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
-          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
-          Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
-          Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
-          Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
-          Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
-          Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
-          Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
-          Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
-          Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
-      ) %>%
-      group_by(Country_Territory,Neighbor_Territory) %>% 
+      Territory %in% Islands_to_Remove |
+        Neighbour %in% Islands_to_Remove |
+        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
+        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
+        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
+        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
+        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
+        Territory == "Crete (Greece)" & Neighbour == "Grece" |
+        Neighbour == "Crete (Greece)" & Territory == "Grece" |
+        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
+        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
+        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
+        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
+        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
+        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
+        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
+        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
+        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
+        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
+        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
+        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
+        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
+        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
+        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
+        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
+        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
+        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
+        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
+        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
+        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
+        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
+        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
+        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
+    ) %>%
+    group_by(Territory,Neighbour) %>% 
     summarise(n())
@@
     anti_join(Territories_to_Remove,
-                by = c("Country_Territory","Neighbor_Territory")
+              by = c("Territory","Neighbour")
     ) %>% 
     filter(Same_Nation == "No") %>% 
-      rename(Territory = Country_Territory,
-             Neighbour = Neighbor_Territory)
-
-    # SAU shapefile
-
-    # The path
-    path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-    # #The File
-    fnam_world <- "SAUEEZ_July2015.shp"
-    # #Load it!
-
-    ### Sau Catch Data
-
-    SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep = ""), header = TRUE)
+    select(-8,-9)
+
+  # ---------------------------- #
+
+  # Load and clean Discrete results
+  Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
+    left_join(Exploited_Species)
 
 } # closes ifstatement for carmelia temporal files
-}else{ # Closes EEZ ifelse
-
-  # List of files without the non-trans data file
-  Spp <- list.files(Results_Path)
-  Spp <- Spp[Spp !="Non_Transboundary_Data.csv"]
-
-  # Results loaing 
-  Results_Trans <- GetTransResults(Spp)
-
-  # Cleaning results (No cleaning needed for now)
-  Clean_Results_Trans <- Results_Trans
-
-  # Load results for non transboundary (discrete) stocks
-  Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
-    filter(!is.na(TaxonKey))
-
-  # Shapefiles 
-  path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO/",sep="")
-  # #The File
-  fnam_world <- "SAU_RFMO_Sept_2015.shp"
-
-}
-
-#  GLobal data depending on jursidiction
-# Load Regional shapefiles 
-World_sf <- st_read(dsn = path_world,
-                    layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(Territory = Name)
 
@@
          Area_Index <= Max_AI,
-         Model_Index == MI#,
-         # Same_Nation == "No"
+         Model_Index == MI
          ) %>% 
@@
   st_transform(crs = 4326) %>% # 4326
-  # st_transform(crs = "+proj=moll") %>% # tubed world
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
@@
   group_by(FishingRegion=Territory) %>% 
-  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
+  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000000,2)) %>% 
   filter(!(is.na(FishingRegion))) %>% 
@@
   group_by(Territory = fishing_entity) %>% 
-  summarise(Total_Catch = sum(Total_Catch,na.rm=T))
+  summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
+  mutate(Territory = gsub("USA","United States of America",Territory))
 
@@
   st_transform(crs = 4326) %>% # 4326
-  # st_transform(crs = "+proj=moll") %>% # tubed world
+  # st_transform(crs = "+proj=wintri") %>% # tubed world
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
@@
 
+# Get the NA's to be grey
+Grey_land <- World_sf_si_land %>% 
+  filter(is.na(BinsLan))
+
 # head(World_sf_si)s
@@
 
-unique(World_sf_si$Bins)
-unique(World_sf_si_land$BinsLan)
-
-levels(World_sf_si$Bins)
-levels(World_sf_si_land$BinsLan)
+# unique(World_sf_si$Bins)
+# unique(World_sf_si_land$BinsLan)
+
+# levels(World_sf_si$Bins)
+# levels(World_sf_si_land$BinsLan)
 
 Plot <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = BinsLan)) +
-  geom_sf(data = World_sf_si,aes(fill = Bins)) + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land,aes(fill = BinsLan), colour = "grey80") +
+  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
+  geom_sf(data = Grey_land,aes(fill = BinsLan),fill = "grey80") + # n_trans_spp or Bins
   # scale_fill_gradientn(colours = pal,
   #                      na.value = "white") +
-  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
-  #                              rev(wes_palette(n = 4, name = "Darjeeling1"))
-  #                              ),
+  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
+                               rev(wes_palette(n = 5, name = "Darjeeling2"))
+                               ),
+                     na.value = "white"
+  ) +
+  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#F98400","#FF0000","#FF0000","#FF0000"),
   #                    na.value = "white"
   # ) +
-  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#F98400","#F98400","#F2AD00","#F2AD00","#00A08A","#FF0000","#FF0000","#FF0000"),
-                     na.value = "white"
-  ) +
   # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
@@
 
-Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Land.png", sep = "")
+Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Landb.png", sep = "")
 
@@
 
+Data <- World_sf_si_land %>% 
+  as_tibble() %>% 
+  select(Territory, BinsLan)
+
+Data_EEZ <- World_sf_si %>% 
+  as_tibble() %>% 
+  select(Territory, Bins)
+
+### EEZ shapefile
+eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
+
+eez = spTransform(eez, CRS("+proj=longlat"))
+eez = spTransform(eez, CRS("+proj=wintri"))
+eez = fortify(eez)
+
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326
+
+#### Round map tryout 
+mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
+
+mapworld<- mapworld %>% 
+  rename(Territory = id) %>% 
+  left_join(Data,
+            by = "Territory") %>% 
+  left_join(Data_EEZ,
+            by = "Territory") %>% 
+  rename(id = Territory)
+
+# head(mapworld)
+
+#create map boundary
+ll.to.wt <- function (points)
+  as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
+                            CRS("+proj=wintri")))
+
+lseq = seq(-85, 85, by=.25)
+boundary <- ll.to.wt(data.frame(
+  long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
+  lat  = c(lseq,                    rev(lseq),          lseq[1])))
+
+# New facet label names for dose variable
+ggplot()+
+  geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
+  geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
+  geom_polygon(data = mapworld, 
+               aes(
+                 x = long,
+                 y = lat,
+                 group = group,
+                 fill = BinsLan
+               ),
+               colour="grey") +
+  geom_polygon(data = mapworld, 
+               aes(
+                 x = long,
+                 y = lat,
+                 group = group,
+                 fill = Bins)
+               ) +
+  geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
+  # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
+  # geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
+  #                 box.padding = unit(0.5, "lines"),
+  #                 point.padding = unit(0.5, "lines"),
+  #                 segment.color = 'grey50') +
+  scale_radius(range = c(1, 2)) #+
+  # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
+  # theme_map()+
+#   theme(legend.key = element_blank(),
+#         strip.background = element_blank(),
+#         legend.position = "none",
+#         text = element_text(size=12,face="bold"))+
+#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
+# y=tag_facet(q, tag_pool = c("d","e","f"))
+
 ```
@@
          Area_Index <= Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No"
+         Model_Index == MI
          ) %>% 
@@
 
-# hist(Countries_Data$value)
-# unique(Countries_Data$group)
+Discrete_Data <- Countries_Data %>% 
+  group_by(group) %>% 
+  top_n(-3) %>% 
+  mutate(value = value*-1)
+
 Median_trans <- median(Countries_Data$value,na.rm=T)
@@
            alpha=0.5) +
+  geom_bar(data = Discrete_Data,
+           aes(x=as.factor(id),
+               y=value),
+           stat="identity",
+           alpha=0.5) +
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
@@
   geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) + # Cero
+  geom_segment(data=grid_data, aes(x = end, y = -20, xend = start, yend = -20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
   # Add median lines for each gropup
@@
   annotate("text", 
-           x = rep(max(Countries_Data$id),5),
-           y = c(20, 40, 60, 80, 100),
-           label = c("20", "40", "60","80",">100"),
+           x = rep(max(Countries_Data$id),7),
+           y = c(-20,0,20, 40, 60, 80, 100),
+           label = c("-20","0","20", "40", "60","80",">100"),
            color="grey", 
@@
                aes(x = start, 
-                   y = -5, 
+                   y = 0, 
                    xend = end, 
-                   yend = -5
+                   yend = 0
                    ), 
@@
 
-# ggsave(
-#     plot = last_plot(),
-#     width = 14,
-#     height = 10,
-#     units = "in",
-#     filename = "Territory_circular.tiff",
-#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-#   )
+ggsave(
+    plot = last_plot(),
+    width = 14,
+    height = 10,
+    units = "in",
+    filename = "Territory_circular.tiff",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+  )
 
@@
          Area_Index > Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No"
+         Model_Index == MI
          ) %>% 
@@
   )
-
-ggsave(
-    plot = last_plot(),
-    width = 14,
-    height = 10,
-    units = "in",
-    filename = "Species_circular_over10.tiff",
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-  )
+# 
+# ggsave(
+#     plot = last_plot(),
+#     width = 14,
+#     height = 10,
+#     units = "in",
+#     filename = "Species_circular_over10.tiff",
+#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+#   )
 
@@
 
+### Potential connections Map
+
+```{r connection_map, eval = F, echo = F}
+
+# https://www.data-to-viz.com/story/MapConnection.html
+
+# Load dataset from github (Surfer project)
+data <- read.table("https://github.com/holtzy/data_to_viz/raw/master/Example_dataset/19_MapConnection.csv", header=T, sep=",")
+
+head(data)
+Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv")
+
+Clean_Results <- Clean_Results %>% 
+  select(TaxonKey, homename = Country_Territory, travelname = Neighbor_Territory)
+
+library(readxl)
+EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
+EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
+
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# DBEM Coordinate system
+Coor <- read.csv("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name) %>% 
+  left_join(Coor, by = "INDEX") %>% 
+  group_by(Territory) %>% 
+  summarise(Latitude = mean(Latitude),
+            Longitude = mean(Longitude)
+  )
+
+Home_coor <- Index_Code %>% 
+  rename(
+    homename = Territory,
+    homelat = Latitude,
+    homelon = Longitude)
+
+Travel_coor <- Index_Code %>% 
+  rename(
+    travelname = Territory,
+    travellat = Latitude,
+    travellon = Longitude)
+
+# Download NASA night lights image
+download.file("https://www.nasa.gov/specials/blackmarble/2016/globalmaps/BlackMarble_2016_01deg.jpg", 
+              destfile = "BlackMarble_2016_01deg.jpg", mode = "wb")
+# Load picture and render
+earth <- jpeg::readJPEG("BlackMarble_2016_01deg.jpg", native = TRUE)
+earth <- grid::rasterGrob(earth, interpolate = TRUE)
+
+# Count how many times we have each unique connexion + order by importance
+summary=data %>% 
+  dplyr::count(homelat,homelon,homecontinent, travellat,travellon,travelcontinent) %>%
+  arrange(n)
+
+summary <- Data %>%
+  group_by(homename,travelname) %>% 
+  summarise(n = n()) %>% 
+  left_join(Home_coor) %>% 
+  left_join(Travel_coor)
+
+# A function that makes a dateframe per connection (we will use these connections to plot each lines)
+data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
+  inter <- geosphere::gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
+  inter=data.frame(inter)
+  inter$group=NA
+  diff_of_lon=abs(dep_lon) + abs(arr_lon)
+  if(diff_of_lon > 180){
+    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
+    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
+  }else{
+    inter$group=group
+  }
+  return(inter)
+}
+
+# Création d'un dataframe complet avec les points de toutes les lignes à faire.
+data_ready_plot=data.frame()
+for(i in c(1:nrow(summary))){
+tmp=data_for_connection(summary$homelon[i], summary$homelat[i], summary$travellon[i], summary$travellat[i] , i)
+  # tmp$homecontinent=summary$homecontinent[i]
+  tmp$n=summary$n[i]
+  data_ready_plot=rbind(data_ready_plot, tmp)
+}
+
+data_ready_plot$homecontinent=factor(data_ready_plot$homecontinent, levels=c("Asia","Europe","Australia","Africa","North America","South America","Antarctica"))
+
+# Plot
+library(ggplot2)
+pal <- wesanderson::wes_palette("Zissou1", 1000, type = "continuous")
+ggplot() +
+  annotation_custom(earth, xmin = -180, xmax = 180, ymin = -90, ymax = 90) +
+  geom_line(data=data_ready_plot, aes(x=lon,
+                                      y=lat, 
+                                      group=group,
+                                      colour=n
+                                      )
+            ) +
+  # scale_color_brewer(palette="Set3") +
+  scale_colour_gradientn(colours = pal) +
+  theme_void() +
+  theme(
+    legend.position="bottom",
+    panel.background = element_rect(fill = "black", colour = "black"), 
+    panel.spacing=unit(c(0,0,0,0), "null"),
+    plot.margin=grid::unit(c(0,0,0,0), "cm")
+    ) +
+  xlim(-180,180) +
+  ylim(-60,80) +
+  scale_x_continuous(expand = c(0.006, 0.006)) +
+  coord_equal()
+
+````
+
 # Problem solving

### 2019-09-16 Initial_Analysis.Rmd
Continued to eddit circular plot. Set new list of spp to Gabriel (~800). Fixed error in EstTranSpp fun

@@
   "circlize", # For circular plot
-  "EBImage", #for reading images to the circular plot
+  "ggimage", #for reading images to the circular plot
   # "cowplot",
@@
 
+# Send second set of species
+
+# Get species already modelled
+# Removes everything before the number
+Step_One <- gsub(".*_","",list.files(paste(Data_Path,"/Distribution_Data/SAU_Distribution/",sep="")))
+
+# Species List
+Species_List <- gsub("\\..*","",Step_One)
+
+exploited_species <- read.csv("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv") #%>% 
+  # left_join(Spp_Clasification) %>% 
+  # filter(!is.na(DemPel)) # remove freshwater spp
+
+# Get all species in SAU database (2080)
+Species_list <- exploited_species %>% 
+  rename(scientific_name = TaxonName) %>% 
+  pull(scientific_name)
+
+# get their environ. association according to FishBase (species())
+
+Species_environ_list <- rbind(species(Species_list, 
+                                      fields = species_fields$habitat)
+                              ) %>% 
+  mutate(TaxonName = Species_list) %>% 
+  left_join(exploited_species,  by ="TaxonName") %>% 
+  filter(!TaxonKey %in% Species_List) %>% 
+  filter(Saltwater == -1) %>%  # remove those that are not happy with saltwater
+  select(TaxonKey,TaxonName,CommonName)
+
+# write.csv(Species_environ_list,
+#           "Transboundary_Spp_Set2.csv",
+#           row.names = F)
+
+# Sent to Gabs Seprember 16th
+
 ### Check Gabs Data ####
@@
 ####### Yes they do! ####
-
-#### List of species we have data for...
-
-# Removes everything before the number
-Step_One <- gsub(".*_","",list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))
-
-# Species List
-Species_List <- gsub("\\..*","",Step_One)
-
-# Get All SAU species for the final analysis
 
@@
 
-#### EEZ
-
 ```{r EEZ_Neighbourds_Control_Pannel, eval = F, echo = F}
@@
 #### For testing 
-# Spp <- 604250  # Anchovie Equator, Chile and Peru
+# Spp <- 600004  # Anchovie Equator, Chile and Peru
 # Spp <- 600107 # Tuna Many RFMOs
 # Spp <- 600464 # Discrete species 
+# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
 # x <- c(600464, # Discreat spp in one nation
@@
 # # For EEZ
-# Neighbours <- Neighbours_Data
-# Index_Code <- Index_Code
+Neighbours <- Neighbours_Data
+Index_Code <- Index_Code
 #  
@@
 # The function
-EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){
+EstTransIndex <- function(Spp,Model = "All",Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){
 
@@
 
+  # Step 2.1. Determines discrete spp
   if(nrow(Spp_Grid) == 0 & Save == "Y"){
 
-    # IF SPECIES IS DISCRETE AND ONLY APEARS IN ONE REGION
+    #  Get the Territory where species happen
   Discrete_Territory <- unique(Model_Index_D$Territory)
@@
 
-    # Get current Spp that is not transboundary 
+    # Set new data
     Current_Spp <- tibble(TaxonKey = as.integer(Spp),
@@
 
-    if(n_Territory ==1){
-
-    To_Print <- paste(Spp, "is only present in",Discrete_Territory)
-    print(To_Print)
-    paste(Spp, "is only present in",Discrete_Territory)
-    }else{
-
-      To_Print <- paste(Spp, "is in both (non-neighbouring)",Discrete_Territory[1],Discrete_Territory[2])
-      print(To_Print)
-    }
-
   EstTransIndex=Current_Spp
@@
 
+  # Step 3. Sum total grids per Neighbours
   if(nrow(Spp_Grid) > 0 & Save == "Y"){
-
-  # Step 3. Sum total grids per Neighbours
 
@@
     distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbour = Name,
+    rename(Territory = Name,
+           Neighbour =Territory,
            n_spp_Country = n_spp_eez.x,
@@
   Indexes <- Model_Index_D %>% 
-    # rename(Territory = Name) %>% 
     full_join(Area_Index_D,
@@
 
-  } # Closes Treshold 3
-}
+  } # Closes Treshold (Step 3)
+} # closes function
 
@@
 
-# Updates result's path for the jurisdiction
-Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
+# Determine forlder for saving results
+Folder <- "Trans_Results"
+Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
+
+if(file.exists(Results_Path) == TRUE){
+  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
+}else{
+  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = ""))
+  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
+}
 
@@
 # Load Jursidiction-dependant data
-if(Jurisdiction == "EEZ"){
+
 # Load neighbours data from previouse routine
@@
 
-}else{
-
-  # Load neighbours data from previouse routine
-  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbours_List.csv", sep =""))
-
-  Index_Code <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Index_Code.csv", sep =""))
-
-}
-
 # Creates dummy dataset for Non transboundary species
@@
 # Just a warning for me not to forget
-print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level"))
+print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level and will be saved at",Folder))
 ```
@@
 
-## Load Results data
-
-```{r Load_Results_Data, eval = F}
-
-# Set Jurisdiction to EEZ or RFMO
-Jurisdiction <- "EEZ"
-
-# Updates result's path for the jurisdiction
-Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
-
-# In case you want to use old results (ran with older verion of neighbours)
-# Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"
-
-# Species list to get species names
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
-Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/SppTaxonName.csv",sep=""))
-
-# Spatial Data needed to remove duplicates
-sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
-
-Clean_sau_eez_fes <- sau_eez_fes %>% 
-  gather("Type","FishingRegion",2,4) %>% 
-  left_join(sau_eez_fes,
-            by = ("fishing_entity_id")
-  ) %>% 
-  group_by(FishingRegion,fishing_entity) %>% 
-  summarise(n())
-
-# UN Regions dataset
-UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
-  group_by(Territory = Country.or.Area,
-           georegion = Region.Name) %>% 
-  summarise(n=n()) %>% #merge china's 3 rows
-  select(-n) %>% 
-  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
-  ungroup() %>% 
-  # Change names to match SAU data and for shorter versions
-  mutate(
-    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
-    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
-    Territory = gsub( "United States of America", "USA",Territory),
-    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
-    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
-    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
-    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
-    # Territory = gsub("Congo", "Congo, R. of",Territory),
-    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
-    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
-    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
-    Territory = gsub(" and ", " & ",Territory),
-    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
-    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
-  )
-
-# Manually change congo
-UN_Regions[52,1] <- "Congo, R. of"
-
-# Load Land shapefile
-path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
-# #The File
-fnam_world_land <- "ne_50m_admin_0_countries.shp"
-
-World_land_sf <- st_read(dsn = path_world_land,
-                         layer =file_path_sans_ext(fnam_world_land)) %>% 
-  rename(Territory = NAME)
-
-# head(World_land_sf)
-
-# Load EEZ shapefiles 
-# SAU shapefile name and paths
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-# #The File
-
-fnam_world <- "SAUEEZ_July2015.shp"
-World_sf <- st_read(dsn = path_world,
-                    layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(Territory = Name)
-
-# ---------------------------- #
-# Transboundary Results ####
-# ---------------------------- #
-
-if(Sys.info()[7] == "carmelia"){ # For Carmelia
-
-  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
-}else{  # For Hall and The Beast
-
-  # Read Sau Catch Data
-  Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
-    filter(!is.na(Territory))
-
-  # List of species
-  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[1:672]
-
-  # ---------------------------- #
-  # Load and clean Transboundary results
-  Results_Trans <- GetTransResults(Spp)
+## Function `CleanResults`
+
+```{r cleaning_function, eval = T, echo = F}
+
+# Requires Clean_sau_eez_fes
+
+CleanResults <- function(Data){
 
 # Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
-  Auto_Remove_Territories <- Results_Trans %>%   
+  Auto_Remove_Territories <- Data %>%   
     rename(FishingRegion=Territory) %>% 
@@
            Territory= FishingRegion,
-           FishingRegion=Neighbour, #Neighbour_Territory
+           FishingRegion=Neighbour, 
            Model_Index,
@@
 
-  Territories_to_Remove <- Results_Trans %>% 
+  Territories_to_Remove <- Data %>% 
     filter(
@@
   # Cleaned results 
-  Clean_Results_Trans <- Auto_Remove_Territories %>% 
+  Clean_Results <- Auto_Remove_Territories %>% 
     anti_join(Territories_to_Remove,
@@
 
+  return(Clean_Results)
+
+}
+
+# x <- Clean_Results(Discrete_Data)
+
+```
+
+## Load Results data
+
+```{r Load_Results_Data, eval = F}
+
+# Set Jurisdiction to EEZ or RFMO
+Jurisdiction <- "EEZ"
+
+# Updates result's path for the jurisdiction
+Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
+
+# Species list to get species names
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
+Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/SppTaxonName.csv",sep=""))
+
+# Spatial Data needed to remove duplicates
+sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
+
+Clean_sau_eez_fes <- sau_eez_fes %>% 
+  gather("Type","FishingRegion",2,4) %>% 
+  left_join(sau_eez_fes,
+            by = ("fishing_entity_id")
+  ) %>% 
+  group_by(FishingRegion,fishing_entity) %>% 
+  summarise(n())
+
+# UN Regions dataset
+UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
+  group_by(Territory = Country.or.Area,
+           georegion = Region.Name) %>% 
+  summarise(n=n()) %>% #merge china's 3 rows
+  select(-n) %>% 
+  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
+  ungroup() %>% 
+  # Change names to match SAU data and for shorter versions
+  mutate(
+    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
+    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
+    Territory = gsub( "United States of America", "USA",Territory),
+    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
+    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
+    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
+    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
+    # Territory = gsub("Congo", "Congo, R. of",Territory),
+    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
+    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
+    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
+    Territory = gsub(" and ", " & ",Territory),
+    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
+    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
+  )
+
+# Manually change congo
+UN_Regions[52,1] <- "Congo, R. of"
+
+# Load Land shapefile
+path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
+# #The File
+fnam_world_land <- "ne_50m_admin_0_countries.shp"
+
+World_land_sf <- st_read(dsn = path_world_land,
+                         layer =file_path_sans_ext(fnam_world_land)) %>% 
+  rename(Territory = NAME)
+
+# head(World_land_sf)
+
+# Load EEZ shapefiles 
+# SAU shapefile name and paths
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
+
+fnam_world <- "SAUEEZ_July2015.shp"
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(Territory = Name)
+
 # ---------------------------- #
+# Transboundary Results ####
+# ---------------------------- #
+
+if(Sys.info()[7] == "carmelia"){ # For Carmelia
+
+  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
+}else{  # For Hall and The Beast
+
+  # Read Sau Catch Data
+  Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
+    filter(!is.na(Territory))
+
+  # List of species
+  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[-829]
+
+  # Load and clean Transboundary results
+  Results_Trans <- GetTransResults(Spp)
+
+  # Clean results susing function CleanResultsfun
+  Clean_Results_Trans <- CleanResults(Results_Trans)
 
@@
   Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
-    left_join(Exploited_Species)
+    filter(!is.na(TaxonKey)) %>% 
+    select(2:3)
 
@@
 ### Non-transboundary
-
-Discrete_Spp <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI#,
-         # Same_Nation == "No"
-         ) %>% 
-  group_by(Territory) %>% 
-  summarise(
-    n_no_discrete_spp = length(unique(TaxonKey)),
-    n_Territories = length(unique(Territory))
-    )
+# 
+# Partial_Transboundary_Spp <- Clean_Results_Trans %>% 
+#   filter(
+#          Area_Index >= Min_AI,
+#          Area_Index <= Max_AI,
+#          Model_Index == MI
+#          ) 
+# 
+# Discrete_Spp_Area_Index <- Clean_Results_Trans %>% 
+#   filter(
+#     Area_Index >= Max_AI, # Discrete spp only on countryes with > 75%
+#     # Area_Index <= Min_AI,
+#          Model_Index == MI
+#          ) %>% 
+#   anti_join(Partial_Transboundary_Spp, # Removes species if it is already transboundary in a country
+#             by = c("TaxonKey","Territory")
+#   ) %>% 
+#   group_by(Territory) %>% 
+#   summarise(
+#     n_discrete_spp = length(unique(TaxonKey))
+    )
+
+# Discrete_Spp <- Discrete_Data %>% 
+#   group_by(Territory) %>% 
+#   summarise(
+#     n_discrete_spp = length(unique(TaxonKey))
+#     ) %>% 
+#   bind_rows(Discrete_Spp_Area_Index) %>% 
+#   group_by(Territory) %>% 
+#   summarise(n_discrete = sum(n_discrete_spp))
+
+  # Merging eezs by territories (e.g. Mex Atlantic and pacific to Mez)
+Country_Discrete_Data <- Discrete_Data %>% 
+  rename(eez_name = Territory) %>% 
+  left_join(sau_eez_fes) %>% 
+  group_by(Territory = fishing_entity) %>% 
+  summarise(value = length(unique(TaxonKey)))
 
@@
 
-```{r Territories_Circluar_Plot, eval = T, echo = T}
+```{r Circular_Data, eval = T, echo = F}
+
+# -------------------------- #
+# Transboundary data
+# -------------------------- #
 
@@
   summarise(Total_trans = sum(value,na.rm=T)) %>% 
+  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
   filter(!is.na(individual)) %>% 
-  select(individual,group,value=Total_trans) %>% 
+  select(individual,group,value) %>% 
   arrange(group,value)
 
+# -------------------------- #
+# Discrete data
+# -------------------------- #
+
+Discrete_Data <- Clean_Results_Trans %>% 
+  filter(Model_Index == MI) %>% 
+  ## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
+  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
+                                ifelse(Area_Index < Min_AI,NA,
+                                "Transboundary"))
+         ) %>% 
+  filter(!is.na(Species_Type)) %>% 
+  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
+  summarise(n=n()) %>%
+  spread(Species_Type,n) %>% 
+  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
+  gather("Species_Type","value", Discrete:Transboundary) %>% 
+  filter(!is.na(value),
+         Species_Type == "Discrete") %>% 
+  group_by(Territory = CT_fishing_entity) %>% 
+  summarise(value = length(unique(TaxonKey)),
+            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
+  #  Include discrete species of Trsh. 1
+  bind_rows(Country_Discrete_Data) %>%
+  # Data cleaning (group by territory and include georegions for plot)
+  rename(FishingRegion=Territory) %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  group_by(Territory = fishing_entity) %>% 
+  summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
+  mutate(value = ifelse(value <= -100,-100,value)) %>% 
+  left_join(UN_Regions, by ="Territory") %>%
+  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+  filter(!is.na(Territory)) %>% 
+  select(individual = Territory,
+         group,
+         value)
+
+# Include possible missing countries in bothe datasets
+Countries_Data <- Discrete_Data %>% 
+  anti_join(Countries_Data,
+            by = c("individual","group")) %>% 
+  mutate(Total_Discrete = 0) %>% 
+  bind_rows(Countries_Data)
+
 Discrete_Data <- Countries_Data %>% 
-  group_by(group) %>% 
-  top_n(-3) %>% 
-  mutate(value = value*-1)
-
-Median_trans <- median(Countries_Data$value,na.rm=T)
-Char <- as.factor(Countries_Data$group)
+  anti_join(Discrete_Data,
+            by = c("individual","group")) %>% 
+  mutate(value = 0) %>% 
+  bind_rows(Discrete_Data)
+
+```
+
+```{r Territories_Circluar_Plot, eval = T, echo = T}
+
+# -------------------------- #
+# Data manipulation for plot
+# -------------------------- #
 
 # Set a number of 'empty bar' to add at the end of each group
+Char <- as.factor(Countries_Data$group) # Set groups to factors
 empty_bar <- length(unique(Countries_Data$group))
@@
 # -------------------------- #
+# Get id to Discrete data
+# -------------------------- #
+
+Discrete_Data_Plot <- Discrete_Data %>% 
+  left_join(Countries_Data,
+            by =c("individual","group")
+  ) %>%
+  mutate(value = ifelse(value.x <= -100,-100,value.x)) %>%
+  select(individual,group,value,id) %>%
+  arrange(group,value)
+
+### make sure they have all same countries
+
+Discrete_Data_Plot %>% 
+  anti_join(Countries_Data,
+            by = c("individual","group","id"))
+
+# -------------------------- #
 # Make the plot
 # -------------------------- #
+
+# Global Variables
+Seq_axis <- seq(-100,100,20)
+Plot_Limit <- max(Countries_Data$value,na.rm=T)
+Plot_Limit_Low <- -110
+Ticks_Color <- "grey50"
+
 # Base plot
@@
            alpha=0.5) +
-  geom_bar(data = Discrete_Data,
+  geom_bar(data = Discrete_Data_Plot,
            aes(x=as.factor(id),
@@
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
   geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) + # Cero
-  geom_segment(data=grid_data, aes(x = end, y = -20, xend = start, yend = -20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = -100, xend = start, yend = -100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = -80, xend = start, yend = -80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = -60, xend = start, yend = -60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = -40, xend = start, yend = -40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = -20, xend = start, yend = -20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
   # Add median lines for each gropup
-  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
-               alpha=1, size=0.5 , inherit.aes = FALSE ) +
+  geom_segment(data=median_data,
+               aes(x = end,
+                   y = median,
+                   xend = start+5, 
+                   yend = median,
+                   colour = group),
+               alpha=1,
+               size=0.5 , 
+               inherit.aes = FALSE ) +
   # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median
   # Add text showing the value of each line
+  annotate("text", label = "Transboundary", x = 214, y = 45, size = 5, colour = "grey10", angle = 90) +
+  annotate("text", label = "Discrete", x = 210, y = -45, size = 5, colour = "grey10", angle = 90) +
   annotate("text", 
-           x = rep(max(Countries_Data$id),7),
-           y = c(-20,0,20, 40, 60, 80, 100),
-           label = c("-20","0","20", "40", "60","80",">100"),
-           color="grey", 
-           size=3 , 
-           angle=0, 
-           fontface="bold",
+           x = rep(max(Countries_Data$id),length(Seq_axis)),
+           y = Seq_axis,
+           label = c("<-100",as.character(Seq_axis)[2:(length(Seq_axis)-1)],">100"),
+           color = Ticks_Color, 
+           size= 4, 
+           angle = 0, 
+           # fontface="bold",
            hjust=1) +
@@
            alpha=0.5) +
+  #Country labels
   geom_text(data=label_data_rest,
-            aes(x=id, y=110,
+            aes(x=id, y=Plot_Limit,
                 label=individual,
@@
             # fontface="bold",
-            alpha=0.6,
+            alpha=1,
             size=2.5,
@@
   geom_text(data=Top_label_data,
-            aes(x=id, y=110,
+            aes(x=id, y=Plot_Limit,
                 label=individual,
@@
             fontface="bold",
-            alpha=0.6,
+            alpha=1,
             size=2.5,
@@
                inherit.aes = FALSE) +
-  ylim(-140,140) + # sets the circle the first value the central the last value how wide
+  ylim(Plot_Limit_Low,Plot_Limit) + # sets the circle the first value the central the last value how wide
   theme_minimal() +
   theme(
-    legend.position = c(0.5,0.5),
+    # legend.position = c(0.5,0.5),
+    legend.position = "",
     axis.text = element_blank(),
@@
                       ),
-                      na.value = "white"
-  )
-
-#  Warring of missing values are the NA's for the columns
+                      na.value = "white")
 
@@
     plot = last_plot(),
-    width = 14,
-    height = 10,
+    width = 12,
+    height = 12,
     units = "in",
-    filename = "Territory_circular.tiff",
+    filename = "Territory_circular_both.png",
     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
@@
 ```{r n_species_country, eval = T, echo =F}
+
 # Number of countries shared by each Species
@@
 
-#### Overcounting transboundary stocks
+### Overcounting transboundary stocks
 
@@
 
-#### Fixing counts within EEZs
+### Fixing counts within EEZs
 
@@
 
-#### Missing stocks
+### Missing stocks
 
@@
 # The main issue is that there is no catch data there...
+
+```
+
+### Pierrs massive discrete stocks
+
+```{r Pierrs_Discretion, eval = F ,echo = T,warning = F,message = F}
+
+Pierre <-  Clean_Results_Trans %>% 
+  filter(Territory == "Saint Pierre & Miquelon (France)") %>% 
+  left_join(Exploited_Species,
+            by = "TaxonKey")
+
+# Very wrong!
+# using 600051 to see what's the problem with the Area index
+
+# Found the problem, Territory and Neighbour were switched un the last step of the EstTransSpp function
 
@@
     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
+  )
+
+  }
+
+```
+
+```{r Continent_PNG, eval =F }
+
+names(UN_Regions)
+# Load Land shapefile
+path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
+# #The File
+fnam_world_land <- "ne_50m_admin_0_countries.shp"
+
+World_land_sf <- st_read(dsn = path_world_land,
+                         layer =file_path_sans_ext(fnam_world_land)) %>% 
+  st_transform(crs = 4326)
+
+head(World_land_sf)
+
+Regions <- unique(World_land_sf$REGION_UN)
+# r= 1
+
+for(r in 1:length(Regions)){
+
+  Oceania <- World_land_sf %>%
+    st_transform(crs = 3832)
+
+  Oceania %>% 
+    filter(REGION_UN %in% Regions[5]) %>% 
+    ggplot() +
+    geom_sf(aes(),fill="black",colour = "black") +
+    ggtheme_map() #+
+    # coord_sf(xlim = c(-180, 90), ylim = c(-90, 90), expand = FALSE)
+
+  Plot_Name <-paste(Regions[5],".png",sep="")
+
+  ggsave(Plot_Name,
+       plot = last_plot(),
+       width = 4,
+       height = 4,
+       units = "in",
+       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Images_Data/"
 )

### 2019-09-17 Initial_Analysis.Rmd
Discrete stocks

@@
   # Load and clean Discrete results
-  Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
+  Non_Transboundary_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
     filter(!is.na(TaxonKey)) %>% 
@@
 
-Transboundary_Spp <- Clean_Results_Trans %>% 
+Tresholded_T_Data <- Clean_Results_Trans %>% 
   filter(
@@
          Model_Index == MI
-         ) %>% 
+         )
+
+### Non-transboundary Tresh 1
+Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
+  rename(eez_name = Territory) %>% 
+  left_join(sau_eez_fes) %>% 
+  group_by(Territory = fishing_entity) %>% 
+  summarise(value = length(unique(TaxonKey)),
+            Taxons = paste(unique(TaxonKey),collapse = ";"))
+
+## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
+Tresholded_D_Data <- Clean_Results_Trans %>% 
+  filter(Model_Index == MI) %>% 
+  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
+                                ifelse(Area_Index < Min_AI,NA,
+                                "Transboundary"))
+         ) %>% 
+  filter(!is.na(Species_Type)) %>% 
+  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
+  summarise(n=n()) %>%
+  spread(Species_Type,n) %>% 
+  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
+  gather("Species_Type","value", Discrete:Transboundary) %>% 
+  filter(!is.na(value),
+         Species_Type == "Discrete") %>% 
+  group_by(Territory = CT_fishing_entity) %>% 
+  summarise(value = length(unique(TaxonKey)),
+            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
+  #  Include discrete species of Trsh. 1
+  bind_rows(Clean_Non_Transboundary_Data) %>%
+  # Data cleaning (group by territory and include georegions for plot)
+  rename(FishingRegion=Territory) %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  group_by(Territory = fishing_entity)
+
+```
+
+## Results per Territory
+
+```{r Data_per_Territory}
+
+# Data per Territory
+Transboundary_Spp <- Tresholded_Data %>% 
   group_by(Territory) %>% 
@@
 
-### Non-transboundary
-# 
-# Partial_Transboundary_Spp <- Clean_Results_Trans %>% 
-#   filter(
-#          Area_Index >= Min_AI,
-#          Area_Index <= Max_AI,
-#          Model_Index == MI
-#          ) 
-# 
-# Discrete_Spp_Area_Index <- Clean_Results_Trans %>% 
-#   filter(
-#     Area_Index >= Max_AI, # Discrete spp only on countryes with > 75%
-#     # Area_Index <= Min_AI,
-#          Model_Index == MI
-#          ) %>% 
-#   anti_join(Partial_Transboundary_Spp, # Removes species if it is already transboundary in a country
-#             by = c("TaxonKey","Territory")
-#   ) %>% 
-#   group_by(Territory) %>% 
-#   summarise(
-#     n_discrete_spp = length(unique(TaxonKey))
-    )
-
-# Discrete_Spp <- Discrete_Data %>% 
-#   group_by(Territory) %>% 
-#   summarise(
-#     n_discrete_spp = length(unique(TaxonKey))
-#     ) %>% 
-#   bind_rows(Discrete_Spp_Area_Index) %>% 
-#   group_by(Territory) %>% 
-#   summarise(n_discrete = sum(n_discrete_spp))
-
-  # Merging eezs by territories (e.g. Mex Atlantic and pacific to Mez)
-Country_Discrete_Data <- Discrete_Data %>% 
-  rename(eez_name = Territory) %>% 
-  left_join(sau_eez_fes) %>% 
-  group_by(Territory = fishing_entity) %>% 
-  summarise(value = length(unique(TaxonKey)))
-
-```
-
-## Results per Territory
+# Number of Transboundary Species
+Total_trans_n <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index >= Min_AI,
+         Area_Index <= Max_AI,
+         Model_Index == MI
+         )
+
+length(unique(Total_trans_n$TaxonKey)) #674 spp
+
+```
 
@@
   group_by(FishingRegion=Territory) %>% 
-  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000000,2)) %>% 
+  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
   filter(!(is.na(FishingRegion))) %>% 
@@
   st_transform(crs = 4326) %>% # 4326
-  # st_transform(crs = "+proj=wintri") %>% # tubed world
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
   left_join(Catch_Country, by ="Territory") # Include total specices catch
+
+# head(World_sf_si)s
+
+# Create a pellet for plotting
+# pal <- wes_palette("Zissou1", 1000, type = "continuous")
+
+World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 4)
+World_sf_si_land$Bins <- cut(World_sf_si_land$Total_Catch,breaks = 4)
+
+head(World_sf_si)
+head(World_sf_si_land)
+
+unique(World_sf_si$Bins)
+unique(World_sf_si_land$BinsLan)
+
+# levels(World_sf_si$Bins)
+# levels(World_sf_si_land$BinsLan)
 
@@
   filter(is.na(BinsLan))
-
-# head(World_sf_si)s
-
-# Create a pellet for plotting
-# pal <- wes_palette("Zissou1", 1000, type = "continuous")
-
-World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 5)
-World_sf_si_land$BinsLan <- cut(World_sf_si_land$Total_Catch,breaks = 5)
-
-# unique(World_sf_si$Bins)
-# unique(World_sf_si_land$BinsLan)
-
-# levels(World_sf_si$Bins)
-# levels(World_sf_si_land$BinsLan)
 
@@
   #                      na.value = "white") +
-  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
-                               rev(wes_palette(n = 5, name = "Darjeeling2"))
-                               ),
+  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
+                               # rev(wes_palette(n = 4, name = "Darjeeling2"))
+                               # ),
+                     # na.value = "white"
+  # ) +
+  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
                      na.value = "white"
   ) +
-  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#F98400","#FF0000","#FF0000","#FF0000"),
-  #                    na.value = "white"
-  # ) +
   # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
@@
 
-Countries_Data <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index >= Min_AI,
-    Area_Index <= Max_AI,
-    Model_Index == MI
-  ) %>% 
+Countries_Data_Plot <- Tresholded_Data %>% 
   group_by(Territory = CT_fishing_entity) %>% 
@@
 
-Discrete_Data <- Clean_Results_Trans %>% 
-  filter(Model_Index == MI) %>% 
-  ## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
-  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
-                                ifelse(Area_Index < Min_AI,NA,
-                                "Transboundary"))
-         ) %>% 
-  filter(!is.na(Species_Type)) %>% 
-  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
-  summarise(n=n()) %>%
-  spread(Species_Type,n) %>% 
-  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
-  gather("Species_Type","value", Discrete:Transboundary) %>% 
-  filter(!is.na(value),
-         Species_Type == "Discrete") %>% 
-  group_by(Territory = CT_fishing_entity) %>% 
-  summarise(value = length(unique(TaxonKey)),
-            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
-  #  Include discrete species of Trsh. 1
-  bind_rows(Country_Discrete_Data) %>%
-  # Data cleaning (group by territory and include georegions for plot)
-  rename(FishingRegion=Territory) %>% 
-  left_join(Clean_sau_eez_fes) %>% 
-  group_by(Territory = fishing_entity) %>% 
+Discrete_Data_Plot <- Tresholded_D_Data %>% 
   summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
@@
 # Include possible missing countries in bothe datasets
-Countries_Data <- Discrete_Data %>% 
-  anti_join(Countries_Data,
+Countries_Data_Plot <- Discrete_Data_Plot %>% 
+  anti_join(Countries_Data_Plot,
             by = c("individual","group")) %>% 
   mutate(Total_Discrete = 0) %>% 
-  bind_rows(Countries_Data)
-
-Discrete_Data <- Countries_Data %>% 
-  anti_join(Discrete_Data,
+  bind_rows(Countries_Data_Plot)
+
+Discrete_Data_Plot <- Countries_Data_Plot %>% 
+  anti_join(Discrete_Data_Plot,
             by = c("individual","group")) %>% 
   mutate(value = 0) %>% 
-  bind_rows(Discrete_Data)
+  bind_rows(Discrete_Data_Plot)
 
@@
 # Set a number of 'empty bar' to add at the end of each group
-Char <- as.factor(Countries_Data$group) # Set groups to factors
-empty_bar <- length(unique(Countries_Data$group))
-to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data)) )
-colnames(to_add) <- colnames(Countries_Data)
+Char <- as.factor(Countries_Data_Plot$group) # Set groups to factors
+empty_bar <- length(unique(Countries_Data_Plot$group))
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data_Plot)) )
+colnames(to_add) <- colnames(Countries_Data_Plot)
 to_add$group <- rep(levels(Char), each=empty_bar)
-Countries_Data <- bind_rows(Countries_Data, to_add)
-Countries_Data <- Countries_Data %>% arrange(group,value)
-Countries_Data$id <- seq(1, nrow(Countries_Data))
+Countries_Data_Plot <- bind_rows(Countries_Data_Plot, to_add)
+Countries_Data_Plot <- Countries_Data_Plot %>% arrange(group,value)
+Countries_Data_Plot$id <- seq(1, nrow(Countries_Data_Plot))
 
@@
 # Top n of each group label
-Top_Countries <- Countries_Data %>% 
+Top_Countries <- Countries_Data_Plot %>% 
   group_by(group) %>% 
@@
 # Create labels for all but top 5
-label_data <- Countries_Data 
+label_data <- Countries_Data_Plot 
 number_of_bar <- nrow(label_data)
@@
 # prepare a data frame for base lines
-base_data <- Countries_Data %>% 
+base_data <- Countries_Data_Plot %>% 
   group_by(group) %>% 
@@
 
-Discrete_Data_Plot <- Discrete_Data %>% 
-  left_join(Countries_Data,
+Discrete_Data_Plot <- Discrete_Data_Plot %>% 
+  left_join(Countries_Data_Plot,
             by =c("individual","group")
@@
 Discrete_Data_Plot %>% 
-  anti_join(Countries_Data,
+  anti_join(Countries_Data_Plot,
             by = c("individual","group","id"))
@@
 Seq_axis <- seq(-100,100,20)
-Plot_Limit <- max(Countries_Data$value,na.rm=T)
+Plot_Limit <- max(Countries_Data_Plot$value,na.rm=T)
 Plot_Limit_Low <- -110
@@
 # Base plot
-ggplot(Countries_Data,
+ggplot(Countries_Data_Plot,
        aes(x=as.factor(id), 
@@
   annotate("text", 
-           x = rep(max(Countries_Data$id),length(Seq_axis)),
+           x = rep(max(Countries_Data_Plot$id),length(Seq_axis)),
            y = Seq_axis,
@@
 
-```{Tran_country, eval =F, echo =F}
-
-# Number of Transboundary Species
-length(unique(Clean_Results_Trans$TaxonKey)) #664 spp
-
-# Number of Discret EEZ species
-
-# Ge those stocks that are not trans due to Area_Index
-length(unique(Results_Discrete$TaxonKey))
-
-```
-
 ```{r n_species_country, eval = T, echo =F}
@@
 # Number of countries shared by each Species
-Species_Trans <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI
-         ) %>% 
+Species_Trans <- Tresholded_T_Data %>% 
   group_by(TaxonKey) %>% 
@@
 
-Species_Data <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index >= Min_AI,
-         Area_Index <= Max_AI,
-         Model_Index == MI#,
-         # Same_Nation == "No"
-         ) %>% 
+Species_Data <- Tresholded_T_Data %>% 
   group_by(TaxonKey) %>% 
@@
   arrange(group,value) %>% 
-  filter(value > 10) # remove all species under 10 (way too many to plot!)
+  filter(value > 20) # remove all species under 10 (way too many to plot!)
 
@@
             .funs = as.numeric)
+
+Seq_axis_spp <- seq(20,100,20)
+Plot_Limit <- max(Species_Data$value,na.rm=T)
 
@@
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
   # Add median lines for each gropup
@@
                alpha=1, size=0.5 , inherit.aes = FALSE ) +
-  # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median
   # Add text showing the value of each line
@@
            x = rep(max(Species_Data$id),5),
-           y = c(20, 40, 60, 80, 100),
-           label = c("20", "40", "60","80",">100"),
-           color="grey", 
+           y = Seq_axis_spp,
+           label = c(Seq_axis_spp[-5],">100"),
+           color=Ticks_Color, 
            size=3 , 
@@
   geom_text(data=label_data_rest,
-            aes(x=id, y=110,
+            aes(x=id, y=101,
                 label=individual,
@@
             color="black",
-            # fontface="bold",
-            alpha=0.6,
+            fontface="italic",
+            alpha=1,
             size=2.5,
@@
   geom_text(data=Top_label_data,
-            aes(x=id, y=110,
+            aes(x=id, y=101,
                 label=individual,
@@
             color="black",
-            fontface="bold",
-            alpha=0.6,
+            fontface="bold.italic",
+            alpha=1,
             size=2.5,
@@
                inherit.aes = FALSE) +
-  ylim(-140,140) + # sets the circle the first value the central the last value how wide
+  ylim(-100,110) + # sets the circle the first value the central the last value how wide
   theme_minimal() +
@@
   scale_fill_manual("Ecosystem Preference",
-                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 4, name = "Darjeeling2")
+                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
+                               wes_palette(n = 4, name = "GrandBudapest2")
                     ),
@@
   scale_colour_manual("Ecosystem Preference",
-                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                                 wes_palette(n = 4, name = "Darjeeling2")
+                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
+                                 wes_palette(n = 4, name = "GrandBudapest2")
                       ),
@@
 # 
-# ggsave(
-#     plot = last_plot(),
-#     width = 14,
-#     height = 10,
-#     units = "in",
-#     filename = "Species_circular_over10.tiff",
-#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-#   )
+ggsave(
+    plot = last_plot(),
+    width = 12,
+    height = 12,
+    units = "in",
+    filename = "Species_circular_over20.png",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+  )
 
@@
 
-### Potential connections Map
-
-```{r connection_map, eval = F, echo = F}
-
-# https://www.data-to-viz.com/story/MapConnection.html
-
-# Load dataset from github (Surfer project)
-data <- read.table("https://github.com/holtzy/data_to_viz/raw/master/Example_dataset/19_MapConnection.csv", header=T, sep=",")
-
-head(data)
-Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv")
-
-Clean_Results <- Clean_Results %>% 
-  select(TaxonKey, homename = Country_Territory, travelname = Neighbor_Territory)
-
-library(readxl)
-EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
-EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")
-
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# DBEM Coordinate system
-Coor <- read.csv("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-
-Index_Code <- EEZIDs_List %>% 
-  left_join(EEZ_CellID) %>% 
-  rename(Territory = Name) %>% 
-  left_join(Coor, by = "INDEX") %>% 
+# Sensitivity Analysis
+
+```{r Sensitivity_Area_Treshold, eval = T, echo = F}
+
+# Model Index
+MI <- 100 # Model Index
+
+####_____End Select Tresholds_______ ###
+
+Area_Index_Level <- seq(.1,0.5,0.1)
+
+p <- list()
+i = NULL
+
+for(i in 1:length(Area_Index_Level)){
+
+  data <- Clean_Results_Trans %>% 
+    filter(
+      Area_Index >= Area_Index_Level[i],
+      Area_Index <= 1-Area_Index_Level[i],
+      Model_Index == MI
+    ) %>% 
     group_by(Territory) %>% 
-  summarise(Latitude = mean(Latitude),
-            Longitude = mean(Longitude)
-  )
-
-Home_coor <- Index_Code %>% 
-  rename(
-    homename = Territory,
-    homelat = Latitude,
-    homelon = Longitude)
-
-Travel_coor <- Index_Code %>% 
-  rename(
-    travelname = Territory,
-    travellat = Latitude,
-    travellon = Longitude)
-
-# Download NASA night lights image
-download.file("https://www.nasa.gov/specials/blackmarble/2016/globalmaps/BlackMarble_2016_01deg.jpg", 
-              destfile = "BlackMarble_2016_01deg.jpg", mode = "wb")
-# Load picture and render
-earth <- jpeg::readJPEG("BlackMarble_2016_01deg.jpg", native = TRUE)
-earth <- grid::rasterGrob(earth, interpolate = TRUE)
-
-# Count how many times we have each unique connexion + order by importance
-summary=data %>% 
-  dplyr::count(homelat,homelon,homecontinent, travellat,travellon,travelcontinent) %>%
-  arrange(n)
-
-summary <- Data %>%
-  group_by(homename,travelname) %>% 
-  summarise(n = n()) %>% 
-  left_join(Home_coor) %>% 
-  left_join(Travel_coor)
-
-# A function that makes a dateframe per connection (we will use these connections to plot each lines)
-data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
-  inter <- geosphere::gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
-  inter=data.frame(inter)
-  inter$group=NA
-  diff_of_lon=abs(dep_lon) + abs(arr_lon)
-  if(diff_of_lon > 180){
-    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
-    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
-  }else{
-    inter$group=group
-  }
-  return(inter)
-}
-
-# Création d'un dataframe complet avec les points de toutes les lignes à faire.
-data_ready_plot=data.frame()
-for(i in c(1:nrow(summary))){
-tmp=data_for_connection(summary$homelon[i], summary$homelat[i], summary$travellon[i], summary$travellat[i] , i)
-  # tmp$homecontinent=summary$homecontinent[i]
-  tmp$n=summary$n[i]
-  data_ready_plot=rbind(data_ready_plot, tmp)
-}
-
-data_ready_plot$homecontinent=factor(data_ready_plot$homecontinent, levels=c("Asia","Europe","Australia","Africa","North America","South America","Antarctica"))
-
-# Plot
-library(ggplot2)
-pal <- wesanderson::wes_palette("Zissou1", 1000, type = "continuous")
-ggplot() +
-  annotation_custom(earth, xmin = -180, xmax = 180, ymin = -90, ymax = 90) +
-  geom_line(data=data_ready_plot, aes(x=lon,
-                                      y=lat, 
-                                      group=group,
-                                      colour=n
-                                      )
+    summarise(
+      n_trans_spp = length(unique(TaxonKey)),
+      n_Neighbours = length(unique(Neighbour)),
+      Trans_Rate = n_trans_spp/n_Neighbours
+    )
+
+  Median_data <- median(data$n_trans_spp)
+  print(Median_data)
+
+  p[[i]] <- ggplot(data) +
+    geom_histogram(aes(n_trans_spp),
+                   binwidth = 10, 
+                   colour = "white"
     ) +
-  # scale_color_brewer(palette="Set3") +
-  scale_colour_gradientn(colours = pal) +
-  theme_void() +
-  theme(
-    legend.position="bottom",
-    panel.background = element_rect(fill = "black", colour = "black"), 
-    panel.spacing=unit(c(0,0,0,0), "null"),
-    plot.margin=grid::unit(c(0,0,0,0), "cm")
+    labs(
+      x = "Transboundary species (n)",
+      y = "Frequency of EEZs",
+      title= paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")
     ) +
-  xlim(-180,180) +
-  ylim(-60,80) +
-  scale_x_continuous(expand = c(0.006, 0.006)) +
-  coord_equal()
-
-````
-
-# Problem solving
+    # ggtitle(paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")) +
+    ggtheme_plot()
+
+}
+
+ggsave(
+    plot = do.call(gridExtra::grid.arrange,p),
+    width = 8,
+    height = 8,
+    units = "in",
+    filename = "Area_Tresholds.png",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Sensitivity_Analysis"
+  )
+
+```
+
+#Problem solving
 

### 2019-09-17 Manuscript_Draft.Rmd

@@
 ---
-title: "How many fisheries need visas?"
+title: "Fish do not need visa"
 author: "Juliano Palacios Abrantes"
 date: "10/4/2018"
-output: pdf_document
+output:
+  word_document: default
+  pdf_document: default
 ---
@@
 
-## Fisheries are important
-Marine fishes are an important source of food and wealth to million of people worldwide.
-Just in 2016, fisheries landings were estimated to be 90 million tonnes representing an important source of food security in many developing countries [@SOFIA].
-The fishing industry employees XX thousand people worldwide and, combined with trade, generate US$ xxx billion in profits.
-An important part of these fisheries are cataloged as shared stocks.
-Shared fish stocks can be classified in two categories [@Bailey:2010ga]; 1) Transboundary, stocks occurring in the EEZs of 2 or more coastal states and 2) Straddling stocks, those occurring in the EEZs of at least one coastal state and the high seas.
-The management of these stocks differed from each other and from discrete fish stocks (e.g.
-stocks that only occur within the EEZ of a coastal nation or in the high seas).
+## Species Niche
 
-## Different ways to classify fisheries according to their distribution
+Species are not randomly distributed in the world.
+Species fundamental niche, that is, the area in space and time where a stable population lives and reproduces, is determined by the species' fitness response to a series of environmental variables such as temperature, salinity, and oxygen [@Hunch].
+Once species interactions are included, we obtain the realize nich, that is the "real" area where a population can be mantained [@Hutchinson:1957].
+The nich concept has been wildly used in determine species distributions, and hence, implement management programs.
 
-The management of shared fish stocks has been mainly studied trough the lenses of game theory. Since its early work Gordon 1976 blablabla.... Cooperative game... Nash equilibrium... balbalba...
+## UNCLOS and deffinitions
 
-## Lack of information on it
+However, this has not allways been the case in fisheries management.
+From 1973 to 1982 the members of the United Nations held a series of meetings to discuss a series of regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].
+The third Conference on the Law of the Sea resulted the UN Convention on the Law of the Sea (UNCLOS) which allowed coastal states to claim jurisdiction over 200 nautical mile Exclusive Economic Zones (EEZs) of their coasts [@UN:1982].
+Despite intended to improve fisheries management, this arbritary delimitation of management area had no input from biogeography, ignoring species distributions, and thus creating what we know today as shared stocks.
+Share stocks, as their name suggest, are fish stocks that live within the waters of two or more nations.
+The Food and Agricultural Organization of the UN (FAO) recognizes three types: (*i*) transboundary stocks, those stocks that are shared by 2 or more neighbouring coastal nations (e.g.
+Pacific halibu *Hippoglossus stenolepsis*); (*ii*) stradling, those stocks that are shared by two or more nations and also the high seas (e.g.
+Atlantic cod, *Gadus morhua*); (*iii*) higly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarilly neighbours, and the high seas (e.g.
+all tunas and tuna-like species); and (*iv) discrete high seas stocks; those species that are only found in the high seas.
 
-Despite the importance of these stocks and the complex management reflected in years of research we still don't know how many fish stocks are actually transboundary in nations.
-Previous estimates suggest that there are around 1,500 transboundary fish stocks in the world [@Cady], however, such estimation lacks a proper assessment.
-Determine the nature of fish stocks (weather or not is a shared resource) can help the proper management of natural resources improving profits [@costello] and food security [@REF] worldwide.
+## Cady and Teh
+
+Despite the importance of shared stocks and their complex management, it is not clear, to date, how many shared stocks are there in the world, wich ones are the most productive, and something else.
+In 1997, that is 10 years after UNCLOS, Caddy (1997) estimated, with limited data and mehtods, that there could be up to 1,500 transboundary fish stocks in the world [@Cady], however, such estimation lacks a proper assessment.
+More recently, Teh and Sumaila (2015) carried a litterature review of shared stocks an estimated 344 shared species according to all UN categories [@Teh:2015gd].
 
@@
 In the current paper we aimed to estimate the number of transboundary fished stocks and their contribution to food security and economics of the world.
-We used the known distribution [@GabsData] of all pelagic and demersal fish stocks listed in the Sea Around Us database [@Zeller] to determine what stocks are likely shared by two or more nations (transboundary), and what stocks are also likely to spend time in the high seas (straddling).
+We used the known distribution [@GabsData] of all pelagic and demersal fish stocks listed in the Sea Around Us database [@Zeller2016] to determine what stocks are likely shared by two or more nations (transboundary), and what stocks are also likely to spend time in the high seas (straddling).
 Our results suggest that XXX global stocks are transboundary in nature from witch XXX also happen in the high seas.
@@
 
-# Methods
+# Materials and Methods
 
-We used the SAU database and filter the pelagic and demersal fish species fished by neighboring countries.
-We then used the SAU catch data and fishing distribution data to determine the central abundance of the stock.
-Assuming that this was the center of the distribution of the stock in question, we overlapped the current distribution of each species [@Gabriel] with the current location of coastal states EEZs [@Shapefile].
-We used the average distribution (mobility) of each species from the stock abundance center.
-If the average distribution from the center reached within two or more coastal nations, such species was considered transboundary.
-IN the other hand, if the species range also included the high seas were classified as straddling.
+For the current proyect we define a transboundary species as those that spend partial or total part of their life within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf].
+Such is the case of Pacific salmons (*Oncorhynchus sp.*) that live part of their life cycle within the US west coast and part within Canadian waters.
 
-# Results
-# Discussion
-# Conclussion
-# References
+## Databases on species geographic distributions
+
+To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs, we first determined their current distributions.
+For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) species distribution models, and (*iii*) fisheries catch data, in order to determine presence or absence of each species within each EEZ.
+(*i*) The observational data was collected from multiple databases online...**GABS** (*ii*) We then used data from two species distribution models.
+The Sea Around Us (SAU) distributions [@Close:2006ux], and an environmental niche model (ENM) [@REFGabs].
+(*iii*) Finally, we used the historical fisheries catch reconstructions provided by the SAU [@Zeller2016], **Version and updates GABS** spatially distributed along the world's EEZs [@Close:2006ux].
+All data was gridded on 0.5 x 0.5 grid cells.
+Only those species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species (**See S1_Data**).
+
+In order to determine the presence or absence of each species in any given EEZ we define the EEZ boundaries using the Sea Around Us dataset (updated 1 July 2015, available from http://www.seaaroundus.org) sub-divided by regions (e.g.
+Mexico Pacific and Mexico Atlantic).
+
+## Determine if a species is transboundary
+
+We developed three steps for determining whether or not a species was transboundary.
+Such steps work as indexes to measure the uncertainty in the analysis.
+Only species that meet the criteria of the three steps were considered as transboundary species, those which did not were considered as discrete species only happening within one EEZ.
+
+For each species and grid cell we firstly determine the presence or absence within each database.
+The *species Index* was computed by dividing the number of datasets that confirm presence over the total amount of datasets.
+Environmental niche models project the distribution of a certain species based on certain parameters such as environmental, behavioral or physiological of individuals and their environmental interaction (fundamental niche).
+However, such distribution does not represent the actual presence (realized niche) of the species after other factors such as species interactions have been taken into account [@Kearney:2010ip].
+To differentiate the fundamental from the realize niche models with the ENMs we used the SAU catch data reconstruction.
+All species that were reported as caught in any single year between 1950 and 2014 in a given EEZ were kept while those with absent catch data were dropped from the specific country.
+The assumption relies in that if a ESM projects a commercial species in any fishing country, such species would been fished, and reported, at some period of time (**S1_Figure**), validating the ESM result, thus, the existence of the species.
+Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed the *area Index*.
+For this we estimate, for each species, the proportion of the total species distribution within both EEZs for each neighboring EEZ (**S2_Figure**).
+
+## Model validation
+
+While we do not know the transboundary nature of many species, some are jointly managed by neighboring countries or Regional Fisheries Management Organizations (RFMOs).
+Hence, in order to validate our results, we cross-check our transboundary species with the fished species and countries of 18 RFMOs all around the globe [@CullisSuzuki:2010fi].
+
+<!-- # Results -->
+<!-- # Discussion -->
+<!-- # Conclussion -->
+<!-- # References -->
+
+```

### 2019-09-17 Initial_Analysis.Rmd
Trying to figure out Cotdevor

@@
 
-### Current issues
-
-- How to distinguish between North and South? Example of Brazil, Uruguay and French Guyana
-
 ## Data
+
+### Determine species list
 
@@
 
-This function Read in species distribution from the observation data, ESM models and SAU data, still missing DBEM
+This function Read in species distribution from the observation data, ESM models and SAU data
 
@@
 # # For EEZ
-Neighbours <- Neighbours_Data
-Index_Code <- Index_Code
+# Neighbours <- Neighbours_Data
+# Index_Code <- Index_Code
 #  
@@
   EstTransIndex=Current_Spp
-    print(To_Print)
+
   }
@@
 Folder <- "Trans_Results"
-Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
+Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "/")
 
@@
   # Set the path for each file
-  Distpath <- paste(Results_Path,"/Trans_Results/",Spp,sep="")
+  Distpath <- paste(Results_Path,Spp,sep="")
 
@@
 Jurisdiction <- "EEZ"
+Folder <- "Trans_Results"
 
 # Updates result's path for the jurisdiction
-Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
+Results_Path <- paste(Results_Path,Jurisdiction,"/",Folder,"/",sep="")
 
@@
   # List of species
-  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[-829]
+  Spp <- list.files(paste(Results_Path,sep=""))[-829]
 
@@
 # Data per Territory
-Transboundary_Spp <- Tresholded_Data %>% 
+Transboundary_Spp <- Tresholded_T_Data %>% 
   group_by(Territory) %>% 
@@
 
-head(World_sf_si)
-head(World_sf_si_land)
-
-unique(World_sf_si$Bins)
-unique(World_sf_si_land$BinsLan)
+# head(World_sf_si)
+# head(World_sf_si_land)
+
+# unique(World_sf_si$Bins)
+# unique(World_sf_si_land$BinsLan)
 
@@
 Grey_land <- World_sf_si_land %>% 
-  filter(is.na(BinsLan))
+  filter(is.na(Bins))
 
 Plot <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = BinsLan), colour = "grey80") +
+  # geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
   geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
-  geom_sf(data = Grey_land,aes(fill = BinsLan),fill = "grey80") + # n_trans_spp or Bins
+  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80") + # n_trans_spp or Bins
   # scale_fill_gradientn(colours = pal,
   #                      na.value = "white") +
-  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
-                               # rev(wes_palette(n = 4, name = "Darjeeling2"))
-                               # ),
+  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
+                               rev(wes_palette(n = 4, name = "Darjeeling2"))
+                               ),
+                     na.value = "white"
+  ) +
+  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
                      # na.value = "white"
   # ) +
-  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
-                     na.value = "white"
-  ) +
   # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
@@
 
-Data <- World_sf_si_land %>% 
-  as_tibble() %>% 
-  select(Territory, BinsLan)
-
-Data_EEZ <- World_sf_si %>% 
-  as_tibble() %>% 
-  select(Territory, Bins)
-
-### EEZ shapefile
-eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
-
-eez = spTransform(eez, CRS("+proj=longlat"))
-eez = spTransform(eez, CRS("+proj=wintri"))
-eez = fortify(eez)
-
-World_sf_si <- World_sf %>%
-  st_transform(crs = 4326
-
-#### Round map tryout 
-mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
-
-mapworld<- mapworld %>% 
-  rename(Territory = id) %>% 
-  left_join(Data,
-            by = "Territory") %>% 
-  left_join(Data_EEZ,
-            by = "Territory") %>% 
-  rename(id = Territory)
-
-# head(mapworld)
-
-#create map boundary
-ll.to.wt <- function (points)
-  as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
-                            CRS("+proj=wintri")))
-
-lseq = seq(-85, 85, by=.25)
-boundary <- ll.to.wt(data.frame(
-  long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
-  lat  = c(lseq,                    rev(lseq),          lseq[1])))
-
-# New facet label names for dose variable
-ggplot()+
-  geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
-  geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
-  geom_polygon(data = mapworld, 
-               aes(
-                 x = long,
-                 y = lat,
-                 group = group,
-                 fill = BinsLan
-               ),
-               colour="grey") +
-  geom_polygon(data = mapworld, 
-               aes(
-                 x = long,
-                 y = lat,
-                 group = group,
-                 fill = Bins)
-               ) +
-  geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
+# Data <- World_sf_si_land %>% 
+#   as_tibble() %>% 
+#   select(Territory, BinsLan)
+# 
+# Data_EEZ <- World_sf_si %>% 
+#   as_tibble() %>% 
+#   select(Territory, Bins)
+# 
+# 
+# ### EEZ shapefile
+# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
+# 
+# eez = spTransform(eez, CRS("+proj=longlat"))
+# eez = spTransform(eez, CRS("+proj=wintri"))
+# eez = fortify(eez) 
+# 
+# World_sf_si <- World_sf %>%
+#   st_transform(crs = 4326
+# 
+# #### Round map tryout 
+# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
+# 
+# mapworld<- mapworld %>% 
+#   rename(Territory = id) %>% 
+#   left_join(Data,
+#             by = "Territory") %>% 
+#   left_join(Data_EEZ,
+#             by = "Territory") %>% 
+#   rename(id = Territory)
+# 
+# # head(mapworld)
+# 
+# #create map boundary
+# ll.to.wt <- function (points)
+#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
+#                             CRS("+proj=wintri")))
+#  
+# lseq = seq(-85, 85, by=.25)
+# boundary <- ll.to.wt(data.frame(
+#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
+#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
+#  
+# # New facet label names for dose variable
+# ggplot()+
+#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
+#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
+#   geom_polygon(data = mapworld, 
+#                aes(
+#                  x = long,
+#                  y = lat,
+#                  group = group,
+#                  fill = BinsLan
+#                ),
+#                colour="grey") +
+#   geom_polygon(data = mapworld, 
+#                aes(
+#                  x = long,
+#                  y = lat,
+#                  group = group,
+#                  fill = Bins)
+#                ) +
+#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
   # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
@@
   #                 segment.color = 'grey50') +
-  scale_radius(range = c(1, 2)) #+
+  # scale_radius(range = c(1, 2)) #+
   # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
@@
 
+### Côte de Ivory missing data
+
+For some reason Côte de ivory is missing data. It was fixed at the begining when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to cero.
+
+```{Cote_Deivory, eval =F, echo =F}
+
+# It might be a problem in the name côte de'ivory....
+# Nope, both INDEX and neighbours datasets are names alike
+
+# Run getSppDistribution function with this:
+Model="All"
+Coord=CoorG
+
+Spp <- 600423 #This species should work
+
+```
+
 # Extra Analysis

### 2019-09-17 Initial_Analysis.Rmd
Figure out issues with Russia (Finally!)

@@
 # Load neighbours data from previouse routine
-Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.csv", sep =""))
+Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.xlsx", sep =""))
+
+# Modifications have to be made if ran un Hall
+# R<e9>union (Réunion) and C<f4>te d'Ivoire (Côte d'Ivoire)
 
@@
 
-Spp <- 600423 #This species should work
+# Spp <- 600423 #This species should work
+
+# Its a problem with compabillity between Windows and MAC. Fixed by changing the neighbours csv. to excell
+
+# Now Check Vietnam...Curacao and Réunion...
+# In INDEXES "Vietnam" in all others "Viet Nam"
+# Fixed directly on the excell
+
+# The russioan probelmo
+
+# Load neighbours data from previouse routine
+Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.xlsx", sep =""))
+
+EEZCellIUD913 <- EEZ_CellID %>% 
+  filter(EEZID == 913)
+
+R912 <- Neighbours_Data %>% 
+  filter(ID == 912)
+
+R913 <- Neighbours_Data %>% 
+  filter(ID == 913)
+
+anti_join(R912,R913)
+
+Index_Code913 <- Index_Code %>% 
+  filter(EEZID == 913)
+
+Neighbours_Data %>% 
+  filter(INDEX %in% Index_Code913$INDEX)
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+# EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+# EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
+
+fnam_world <- "SAUEEZ_July2015.shp"
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(Territory = Name)
+
+x <- Neighbours_Data %>%
+  select(-Neighbour) %>% 
+  group_by(Territory) %>% 
+  distinct() %>% 
+  anti_join(Index_Code) %>% 
+  group_by(Territory) %>% 
+  summarise(n());x
+
+# World_sf %>% 
+#   filter(Territory %in% x$Territory)
+
+# Fuck it! Re-run Neighbours code...
+
+Russians <- c("Russia (Laptev to Chukchi Sea)", #913
+              "US Virgin Islands") #912
+
+SF_Names <- 850
+
+Russian_Index <- Index_Code %>% 
+  filter(Territory %in% Russians)
+
+unique(Russian_Index$EEZID)
+unique(Russian_Index$Territory)
+
+World_sf %>% 
+  # filter(Territory == "Russia (Laptev to Chukchi Sea)") # EEZid 912
+  # filter(Territory == "Russia (Kara Sea)") # EEZid also 912
+  filter(Territory %in% Russians) %>% 
+  ggplot() +
+  geom_sf(aes(fill = Territory))
+
+unique(Russian_sf$Territory)
+
+# split shapefile by DF
+ Russian_id <- World_sf %>% 
+  filter(Territory %in% Russians) %>% 
+  left_join(Russian_Index, by= "Territory") %>%  
+  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
+  filter(EEZID == 913) %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 1000)
+
+ ggplot(Russian_id) +
+   geom_sf(aes())
+
+ # ok!
+
+# split shapefile by DF
+Russia_id_912_913 <- World_sf %>% 
+  filter(Territory %in% Russians) %>% 
+  left_join(Russian_Index, by= "Territory") %>%  
+  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
+  as.data.frame() %>% 
+  ungroup() %>% 
+  select(Territory,INDEX,EEZID)
+
+write.csv(Russia_id_912_913,
+         "Russia_id_912_913.csv",
+         row.names = F)
+
+head(x)
 

### 2019-09-17 Initial_Analysis.Rmd
Changes in paths

@@
 Folder <- "Trans_Results"
-Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "/")
+Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
 
 if(file.exists(Results_Path) == TRUE){
-  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
+  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
 }else{
-  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = ""))
-  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
+  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = ""))
+  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
 }
@@
 # Load neighbours data from previouse routine
-Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.xlsx", sep =""))
+Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.xlsx", sep =""))
 

### 2019-09-18 Initial_Analysis.Rmd
Creeated a function to fix the coding errors, not working fully. Will deal with it later

@@
     filter(Same_Nation == "No") %>% 
-    select(-8,-9)
+    select(-8,-9) %>% 
+    # Fixe coding issues between MAC and Windows
+    mutate(
+    Territory = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Territory),
+    Territory = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Territory),
+    Territory = gsub("R<e9>union (France)","Réunion",Territory),
+    Neighbour = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Neighbour),
+    Neighbour = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Neighbour),
+    Neighbour = gsub(" R<e9>union (France)","Réunion",Neighbour)
+    )
 
@@
   # Load and clean Discrete results
-  Non_Transboundary_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
+  Non_Transboundary_Data <- fread(paste(Results_Path,"/Non_Transboundary_Data.csv",sep="")) %>% 
     filter(!is.na(TaxonKey)) %>% 
@@
 
+World_sf_si %>% 
+  filter(Territory == "Côte d'Ivoire")
+
 Catch_Country <- Sau_Catch_Data %>% 
@@
 Plot <- ggplot() +
-  # geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
+  geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
   geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
@@
   #                      na.value = "white") +
-  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
-                               rev(wes_palette(n = 4, name = "Darjeeling2"))
-                               ),
+  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
+  #                              rev(wes_palette(n = 4, name = "Darjeeling2"))
+  #                              ),
+  #                    na.value = "white"
+  # ) +
+  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
   na.value = "white"
   ) +
-  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
-                     # na.value = "white"
-  # ) +
   # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),

### 2019-09-18 Cover_Letter.Rmd
Manuscript structure created

---
title: 'Fish do nor need Visas: Reference Letter'
author: "Juliano Palacios Abrantes"
date: '2019-09-18'
output: pdf_document
---

Should include:
- Reference to any pre-submission discussions with editors.
- The title of the paper and a statement of its main point.
- Any information needed to ensure a fair review process, including related manuscripts submitted to other journals.
- Names of colleagues who have reviewed the paper.
- A statement that none of the material has been published or is under consideration for publication elsewhere.
- Specification of where all data underlying the study are available, or will be deposited, and whether there are any restrictions on data availability such as an MTA.
- Information on any reference material or additional data files uploaded to the Auxiliary files section (see below).
- Please also upload a .docx version of your cover letter – see below.

### 2019-09-18 Manuscript_Draft.Rmd
Manuscript structure created

@@
 ---
-title: "Fish do not need visa"
-author: "Juliano Palacios Abrantes"
-date: "10/4/2018"
+title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum )"
+authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1^, William W.L. Cheung^1^"
+date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
+# subtitle: "Fish do not need Visas (16/40 character maximum)"
 output:
-  word_document: default
-  pdf_document: default
+  pdf_document:
+    fig_caption: yes
+  word_document:
+    reference_docx: ./Manuscript_Instructions/science_template.docx
+geometry: margin=1in
+editor_options:
+  chunk_output_type: console
+bibliography: ./References/FishForVisa_Ref.bib
+csl: ./References/science.csl
 ---
 
-# Introduction
+<!-- # Instructions for submission -->
 
-## Species Niche
+<!-- - Journal: *Science* (Research article ~4000 words) -->
+<!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
+<!-- - There are two types of article: -->
+
+<!-- -- **Research Articles** (up to ~4500 words, including references, notes and captions–corresponds to ~5 printed pages in the journal) are expected to present a major advance.
+Research Articles include an abstract, an introduction, up to six figures or tables, sections with brief subheadings, and about 40 references.
+-->
+
+<!-- --- Instructions for preparing an initial manuscript https://www.sciencemag.org/authors/instructions-preparing-initial-manuscript -->
+
+<!-- -- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance.
+Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.
+-->
+
+<!-- In both cases Materials and Methods should be included in supplementary material -->
+
+<!-- - Reviewers: Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers. -->
+
+# **One Sentence Summary** (~ 125 characters)
+
+<!-- A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
+This will appear online adjacent to the title and should not repeat phrases already present there -->
+
+- Field code: *Fisheries*
+
+# **Abstract** (~125 words)
+
+<!-- An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
+It should be a single paragraph.
+-->
+
+<!-- # Introduction (~600 words) -->
+
+<!-- (1-2 paragraph) plus a statement of specific scope  -->
 
 Species are not randomly distributed in the world.
-Species fundamental niche, that is, the area in space and time where a stable population lives and reproduces, is determined by the species' fitness response to a series of environmental variables such as temperature, salinity, and oxygen [@Hunch].
-Once species interactions are included, we obtain the realize nich, that is the "real" area where a population can be mantained [@Hutchinson:1957].
-The nich concept has been wildly used in determine species distributions, and hence, implement management programs.
+The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of environmental variables such as temperature, salinity, and oxygen (fundamental niche), as well as interactions with other species (realized niche) [@Hunch].
+Thus, species distributions are key elements in marine resources management and policy, as human-made spatial boundaries are an indispensable part of the fisheries management system, from small marine protected areas to nation's economic exclusive zones (EEZs), to Regional Fisheries Management Organizations [@Song:2017iua].
 
-## UNCLOS and deffinitions
-
-However, this has not allways been the case in fisheries management.
+However, incorporating the concept of species distribution has not allays been the case in fisheries management as in the case of EEZs where 90% of wild fish is catched [@].
 From 1973 to 1982 the members of the United Nations held a series of meetings to discuss a series of regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].
 The third Conference on the Law of the Sea resulted the UN Convention on the Law of the Sea (UNCLOS) which allowed coastal states to claim jurisdiction over 200 nautical mile Exclusive Economic Zones (EEZs) of their coasts [@UN:1982].
-Despite intended to improve fisheries management, this arbritary delimitation of management area had no input from biogeography, ignoring species distributions, and thus creating what we know today as shared stocks.
+Despite intended to improve fisheries management, this arbitrary delimitation of management area had no input from biogeography, ignoring species distributions, and thus creating what we know today as shared stocks.
 Share stocks, as their name suggest, are fish stocks that live within the waters of two or more nations.
-The Food and Agricultural Organization of the UN (FAO) recognizes three types: (*i*) transboundary stocks, those stocks that are shared by 2 or more neighbouring coastal nations (e.g.
-Pacific halibu *Hippoglossus stenolepsis*); (*ii*) stradling, those stocks that are shared by two or more nations and also the high seas (e.g.
-Atlantic cod, *Gadus morhua*); (*iii*) higly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarilly neighbours, and the high seas (e.g.
+The Food and Agricultural Organization of the UN (FAO) recognizes three types: (*i*) transboundary stocks, those stocks that are shared by 2 or more neighboring coastal nations (e.g.
+Pacific halibu *Hippoglossus stenolepsis*); (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas (e.g.
+Atlantic cod, *Gadus morhua*); (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas (e.g.
 all tunas and tuna-like species); and (*iv) discrete high seas stocks; those species that are only found in the high seas.
 
-## Cady and Teh
+Despite previous attempts, is still not clear how many shared species exist and what is their contribution to global economy and protein production.
+It was estimated in 1997, that is 10 years after UNCLOS, that there could be up to 1,500 transboundary fish species in the world, however, such estimation lacked a proper assessment due to limited information at the time [@Caddy:1997ue].
+More recently, it was estimated there were 344 shared species, representing a capture of 34.2 × 10^6^ t and a global landed value of USD 30.7 × 10^9^ [@Teh:2015gd].
+While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the species distribution [@Teh:2015gd].
+Therefore, 40 years after UNCLOS, the question of how many transboundary species exists in the world is still unanswered.
+This is of uppermost need as the fisheries management approach differs substantially between EEZ-discreet and shared species [@Mills].
 
-Despite the importance of shared stocks and their complex management, it is not clear, to date, how many shared stocks are there in the world, wich ones are the most productive, and something else.
-In 1997, that is 10 years after UNCLOS, Caddy (1997) estimated, with limited data and mehtods, that there could be up to 1,500 transboundary fish stocks in the world [@Cady], however, such estimation lacks a proper assessment.
-More recently, Teh and Sumaila (2015) carried a litterature review of shared stocks an estimated 344 shared species according to all UN categories [@Teh:2015gd].
+ <!-- **Results and discussion** (1000 words) -->
 
-## What we did
+We combined a series of datasets and species distribution models to estimate the number of transboundary fished species and their contribution to food security and economics of the world.
+We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species.
+Our results suggest that there are XXX transboundary species in the world that account for XXX t landings generating USD xxx in fishing revenue to a total of USD xxxx in the fishing sector.
+Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
+The overall fish production of transboundary species is relative lower than the number of species within each EEZ, with the exception of some punctual cases like Peru, Chile, Norway, and Ireland where fewer species produce higher landings (Fig 1).
 
-In the current paper we aimed to estimate the number of transboundary fished stocks and their contribution to food security and economics of the world.
-We used the known distribution [@GabsData] of all pelagic and demersal fish stocks listed in the Sea Around Us database [@Zeller2016] to determine what stocks are likely shared by two or more nations (transboundary), and what stocks are also likely to spend time in the high seas (straddling).
-Our results suggest that XXX global stocks are transboundary in nature from witch XXX also happen in the high seas.
-Transboundary stocks represent XX% of total landings and XX% of global revenues.
+![**Number of transboundary species by EEZ and their production by country**](./Figures/Fig1.png)
 
-# Materials and Methods
+It is not surprising then, that countries within this regions hold the most amount of transboundary species.
+Some African, Asian, and European countries house over 100 species within their EEZs.
+Only the US presents over 100 transboundary species outside those continents, once all three sub-EEZs (Atlantic and Pacific coast as well as Alaska arctic and subarctic) are accounted for (Fig.
+2).
+![**Number of transboundary and discrete species by country and continent**](./Figures/Fig2.png)
 
-For the current proyect we define a transboundary species as those that spend partial or total part of their life within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf].
+<!-- Will run statistics to see if I can show the "why" of trans spp -->
+There is no clear visual pattern regarding transboundary and discrete species, however, from the three countries that house the most amount of discrete stocks, Australia, New Zeland and the US are among the larger in terms of EEZ lenght, in the other hand, Brazil has only two neighbors along its large latitudinal coast, suggesting not a lot of connection points for sharing species.
+<!-- End of statistics paragraph -->
+
+All species that share over >100 countries are widly distributed pelagic species suchas as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) with a median of 65, 42, and 38 species per pelagic oceanic, bathymetric and nerictic species, respectively.
+The median for all other ecosystem preferences is under 35 as many of these species are not so widely distribute globally.
+
+100
+pelagic-oceanic
+3
+
+100
+pelagic-oceanic
+8
+Auxis thazard
+
+![**Number of countries shared by transboundary species.** Showing only species that share > 20 countries](./Figures/Fig3.png)
+
+# **References** (up to 40)
+
+# **Acknowledgments* *
+
+<!-- ## Funding: include complete funding information;  -->
+<!-- ## Authors contributions: a complete list of contributions to the paper (we encourage you to follow the CRediT model), -->
+<!-- ## Competing interests: competing interests of any of the authors must be listed (all authors must also fill out the Conflict of Interest form).
+Where authors have no competing interests, this should also be declared.
+-->
+<!-- ## Data and materials availability: Any restrictions on materials such as MTAs.  -->
+
+<!-- # Materials and Methods  -->
+
+<!-- For the current proyect we define a transboundary species as those that spend partial or total part of their life within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf].
 Such is the case of Pacific salmons (*Oncorhynchus sp.*) that live part of their life cycle within the US west coast and part within Canadian waters.
+-->
 
-## Databases on species geographic distributions
+<!-- ## Databases on species geographic distributions -->
 
-To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs, we first determined their current distributions.
+<!-- To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs, we first determined their current distributions.
 For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) species distribution models, and (*iii*) fisheries catch data, in order to determine presence or absence of each species within each EEZ.
@@
 Only those species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species (**See S1_Data**).
+-->
 
-In order to determine the presence or absence of each species in any given EEZ we define the EEZ boundaries using the Sea Around Us dataset (updated 1 July 2015, available from http://www.seaaroundus.org) sub-divided by regions (e.g.
+<!-- In order to determine the presence or absence of each species in any given EEZ we define the EEZ boundaries using the Sea Around Us dataset (updated 1 July 2015, available from http://www.seaaroundus.org) sub-divided by regions (e.g.
 Mexico Pacific and Mexico Atlantic).
+-->
 
-## Determine if a species is transboundary
+<!-- ## Determine if a species is transboundary -->
 
-We developed three steps for determining whether or not a species was transboundary.
+<!-- We developed three steps for determining whether or not a species was transboundary.
 Such steps work as indexes to measure the uncertainty in the analysis.
 Only species that meet the criteria of the three steps were considered as transboundary species, those which did not were considered as discrete species only happening within one EEZ.
+-->
 
-For each species and grid cell we firstly determine the presence or absence within each database.
+<!-- For each species and grid cell we firstly determine the presence or absence within each database.
 The *species Index* was computed by dividing the number of datasets that confirm presence over the total amount of datasets.
@@
 For this we estimate, for each species, the proportion of the total species distribution within both EEZs for each neighboring EEZ (**S2_Figure**).
+-->
 
-## Model validation
+<!-- ## Model validation  -->
 
-While we do not know the transboundary nature of many species, some are jointly managed by neighboring countries or Regional Fisheries Management Organizations (RFMOs).
+<!-- While we do not know the transboundary nature of many species, some are jointly managed by neighboring countries or Regional Fisheries Management Organizations (RFMOs).
 Hence, in order to validate our results, we cross-check our transboundary species with the fished species and countries of 18 RFMOs all around the globe [@CullisSuzuki:2010fi].
-
-<!-- # Results -->
-<!-- # Discussion -->
-<!-- # Conclussion -->
-<!-- # References -->
+-->
 

### 2019-09-19 Manuscript_Draft.Rmd
updaates

@@
 
-However, incorporating the concept of species distribution has not allays been the case in fisheries management as in the case of EEZs where 90% of wild fish is catched [@].
+However, incorporating the concept of species distribution has not allays been the case in fisheries management as in the case of EEZs where most of wild fish is catched [@Zeller].
 From 1973 to 1982 the members of the United Nations held a series of meetings to discuss a series of regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].

### 2019-09-19 Initial_Analysis.Rmd
Finished function to estimate the species status according to the SAU method

@@
   "taxize", # For getting species names
-  "rfishbase" # for species ecosystem affinity
+  "rfishbase", # for species ecosystem affinity
+  "zoo" #for runing mean
 )
@@
 # Index_Code <- Index_Code
-#  
-# __________________________________
-# __________________________________
+
+# __________________________________ #
 
@@
   }
+
+  if(nrow(Indexes) > 0 & Save == "N"){
+  EstTransIndex=Indexes # A dataframe with   
+  }
+
   ### Function return
@@
 
+## Function `EstSppStatus`
+
+```{r Species_Status_fun, eval = T, echo =F}
+
+EstSppStatus <- function(Spp,Coord){
+
+  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
+    gather("Year","Value",CATCH.1:CATCH.65) %>% 
+    arrange(INDEX) %>% 
+    mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
+    left_join(Index_Code,
+              by = "INDEX") %>% 
+    filter(!is.na(EEZID),
+           Value > 0) %>% 
+    group_by(Species,Year,Territory) %>% # Total catch per country
+    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
+    group_by(Species,Territory,Year) %>% 
+    mutate(RMean = rollmean(x = Total_Catch, 3,
+                            align = "right",
+                            fill = Total_Catch)
+           ) %>% # Running mean
+    group_by(Species,Territory) %>% 
+    select(-Total_Catch)
+
+  # Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
+  Tresholds_Data <- Data %>% 
+    arrange(Territory) %>% 
+    group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
+    group_by(Species,Territory) %>% 
+    summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
+              Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
+              Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
+    ) %>% 
+    gather("Step","Treshold",Years_appart:Catch_over) %>% 
+    group_by(Species,Territory) %>% 
+    summarise(Met_Criteria = paste(unique(Treshold),collapse =";")
+              )
+
+  # Remove species that do not met the criterias
+
+    No_Status_Data <- Tresholds_Data %>% 
+      filter(Met_Criteria != "Yes") %>% 
+      select(Species,Territory) %>% 
+      mutate(Status = "No Status")
+
+  # Evaluate species that met the criteria
+
+    # Get Variables to perform status metric
+    Status_Data <- Data %>% 
+      anti_join(No_Status_Data, # Removes no status data
+                by = c("Species","Territory")
+      ) %>% 
+      # Get Max catch and max catch year
+      group_by(Species,Territory) %>% 
+      top_n(1,RMean) %>% 
+      rename(Max_Peak = RMean,
+             Y_Max_Peak = Year) %>% 
+      # Get Min catch after peak catch
+      left_join(Data,
+                by = c("Species","Territory")
+                ) %>% 
+      filter(Year > Y_Max_Peak) %>% 
+      group_by(Species,Territory) %>% 
+      top_n(-1,RMean) %>% 
+      rename(Post_Max_Min = RMean,
+             Y_Post_Max_Min = Year) %>% 
+      left_join(Data,
+                by = c("Species","Territory")
+                ) %>% 
+      # Final Evaluation 
+      mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                             ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
+                                    ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                           ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
+                                                  ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                         "No Status")
+                                           )
+                                    )
+                             )
+      )
+      ) %>% 
+      filter(Year > 2004) %>% # last 10 years of data
+      group_by(Species,Territory,Status) %>% 
+      summarise(n_Status= n()) %>% 
+      group_by(Species,Territory) %>% 
+      top_n(1,n_Status) %>%
+      select(-n_Status)
+
+    # If both datasets have value RETURN BOTH
+    if(nrow(No_Status_Data) > 0 & nrow(Status_Data) > 0){
+
+      Fun_Result <- bind_rows(No_Status_Data,
+                              Status_Data)
+    }
+
+    # If only No status data, then just return that
+    if(nrow(No_Status_Data) > 0 & nrow(Status_Data) == 0){
+      return(No_Status_Data)
+    }else{
+      return(Status_Data)
+    }
+
+}
+
+# Testing
+# Test_1 <- EstSppStatus(Species_List[1],CoorG)
+
+Species_Status <- bind_rows(
+    mclapply(
+      Species_List,
+      FUN = EstSppStatus,
+      Coord = CoorG  # Gabriels coordinate system for read species dist
+    )
+  )
+
+```
+
 ## Load Results data
@@
 
+  # Read Sau Value Data (Thank you Tim!)
+  Sau_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
+    group_by(fishing_entity_id,TaxonKey=taxon_key) %>% 
+    summarise(Mean_Value = mean(value,na.rm=T))
+
   # List of species
@@
 
-World_sf_si %>% 
-  filter(Territory == "Côte d'Ivoire")
+#  Top 10 Larger EEZs...
+# World_sf_si %>% 
+#   arrange(desc(Area_km2)) %>% 
+#   head(10)
 
@@
 
+# Or revenue data %>%
+
+Tresholded_T_Data_x <- Tresholded_T_Data %>% 
+  select(TaxonKey, Territory=CT_fishing_entity)
+
+Revenue_Country <- sau_eez_fes %>% 
+  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
+  summarise(n=n()) %>% 
+  select(-n) %>% 
+  left_join(Tresholded_T_Data_x) %>% 
+  left_join(Sau_Revenue_Data) %>% 
+  group_by(Territory) %>% 
+  summarise(Total_USD = sum(Mean_Value,na.rm=T)) %>% 
+  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory))
+
+hist(Revenue_Country$Total_USD)
+
 World_sf_si_land <- World_land_sf %>%
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
-  left_join(Catch_Country, by ="Territory") # Include total specices catch
+  left_join(Revenue_Country, by ="Territory") # Include total specices catch
 
@@
 World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 4)
-World_sf_si_land$Bins <- cut(World_sf_si_land$Total_Catch,breaks = 4)
+World_sf_si_land$Bins <- cut(World_sf_si_land$Total_USD,breaks = 4)
+
+World_sf_si_land <- World_sf_si_land %>% 
+  arrange(Total_USD)
+
+World_sf_si <- World_sf_si %>% 
+  arrange(n_trans_spp)
 
@@
 Plot <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
-  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
-  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80") + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80",size = 0.1) +
+  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
+  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
   # scale_fill_gradientn(colours = pal,
@@
 
-Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Landb.png", sep = "")
+Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Value.png", sep = "")
 
@@
 
-Countries_Data_Plot <- Tresholded_Data %>% 
+Countries_Data_Plot <- Tresholded_T_Data %>% 
   group_by(Territory = CT_fishing_entity) %>% 
@@
 
+### Species status (SAU methods)
+
+Note that (n), the number of ‘stocks’ is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area is at least 1000 tonnes.
+
+ 1) The first and last reported landings are at least ten years apart;
+
+2) There are at least five years of consecutive catches; and
+
+3) The catch in a particular area (LME) is at least 1,000 tonnes.
+
+Once those tresholds are met, the status of the species is determined as follows:
+
+- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
+- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
+- Exploited	Landing > 50% of max. landing
+- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
+- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
+
+*Notes* = 3 years average mean
+
+```{r Species_Status, eval = T, echo =F}
+
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+Spp <- GetSppDist(600004, Model = "SAU_C", Coord = CoorG)
+
+Data <- Spp %>% 
+  gather("Year","Value",CATCH.1:CATCH.65) %>% 
+  arrange(INDEX) %>% 
+  mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
+  left_join(Index_Code) %>% 
+  filter(!is.na(EEZID),
+         Value > 0) %>% 
+  group_by(Species,Year,EEZID,Territory) %>% # Total catch per country
+  summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
+  group_by(Species,Territory,EEZID,Year) %>% 
+  mutate(RMean = rollmean(x = Total_Catch, 5, align = "right", fill = Total_Catch)) %>% 
+  group_by(Species,Territory,EEZID)
+
+# head(Data)
+
+# Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
+ Tresholds <- Data %>% 
+  arrange(Territory) %>% 
+  group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
+            Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
+            Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
+            ) %>% 
+   gather("Step","Treshold",Years_appart:Catch_over) %>% 
+   filter(Treshold == "Yes")
+
+ # Evaluate stocks
+
+ # Filter data that does not satisfy tresholds
+
+ Landings_Peaks <- Data %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Max_Peak = max(RMean,na.rm=T))
+
+ Eval_Data <- Data %>% 
+  semi_join(Tresholds,
+            by = c("Species","Territory")) %>% 
+   left_join(Landings_Peaks,
+             by = c("Species","Territory"))
+
+ Peak_Year <- Eval_Data %>% 
+   filter(RMean == Max_Peak) %>% 
+   select(Species,Territory,EEZID,Y_Max_Peak = Year)
+
+ Post_Max_Min <- Eval_Data %>% 
+   left_join(Peak_Year) %>% 
+   filter(Year > Y_Max_Peak) %>% 
+   group_by(Species,Territory,EEZID) %>% 
+   summarise(Post_Max_Min = min(RMean,na.rm=T))
+
+ Y_Post_Max_Min <- Eval_Data %>% 
+   left_join(Post_Max_Min) %>% 
+   filter(RMean == Post_Max_Min) %>% 
+   select(Species,Territory,EEZID,Y_Post_Max_Min = Year)
+
+ Data_Status <- Eval_Data %>% 
+   left_join(Peak_Year,
+             by = c("Species","Territory","EEZID")) %>%
+   left_join(Post_Max_Min,
+             by = c("Species","Territory","EEZID")) %>% 
+   left_join(Y_Post_Max_Min,
+             by = c("Species","Territory","EEZID")) %>% 
+   rename(Y_RMean = Year) %>% 
+   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
+                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
+                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                      "No Status")
+                                        )
+                                 )
+                          )
+   )
+   ) %>% 
+   filter(Y_RMean > 2004) %>% 
+   group_by(Species,EEZID,Territory,Status) %>% 
+   summarise(n_Status= n()) %>% 
+   group_by(Species,EEZID,Territory) %>% 
+   top_n(1,n_Status)
+
+ # Manual estimation
+
+ data.frame(
+   Y_RMean = 1980,
+   RMean = 642187,
+   Max_Peak = 1298712,
+   Y_Max_Peak = 1990,
+   Post_Max_Min = 681967,
+   Y_Post_Max_Min = 2010,
+   Y_RMean = 2014
+ ) %>% 
+   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
+                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))," Over Exploited",
+                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                      "NA")
+                                        )
+                                 )
+                          )
+   )
+   )
+
+```
+
 ```{r Top_spp_Circle_Diagram, eval =F, echo = F}

### 2019-09-20 Manuscript_Draft.Rmd
Updates on introduction draft (good for now)

--- 2019-09-18 Manuscript_Draft.Rmd
@@
 
-<!-- - Journal: *Science* (Research article ~4000 words) -->
+<!-- - Journal: *Science*  -->
 <!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
 <!-- - There are two types of article: -->
-
-<!-- -- **Research Articles** (up to ~4500 words, including references, notes and captions–corresponds to ~5 printed pages in the journal) are expected to present a major advance.
-Research Articles include an abstract, an introduction, up to six figures or tables, sections with brief subheadings, and about 40 references.
--->
-
-<!-- --- Instructions for preparing an initial manuscript https://www.sciencemag.org/authors/instructions-preparing-initial-manuscript -->
 
@@
 
+<!-- Policy Forums (1000 to 2000 words, 1-2 figures, and up to 15 references) presents issues related to the intersections between science and society that have policy implications. -->
+
 <!-- In both cases Materials and Methods should be included in supplementary material -->
+
+<!-- --- Instructions for preparing an initial manuscript https://www.sciencemag.org/authors/instructions-preparing-initial-manuscript -->
 
@@
 
-<!-- (1-2 paragraph) plus a statement of specific scope  -->
+Species are not randomly distributed in the world.
+The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutaionary process [@REF].
+Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua].
+However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy.
+The delimitation of Economic Exclusive Zones (EEZs) virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
+However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
+In here, we show that many species are shared, representing an important contrubution to national economies and food security, and hilighting the importance to aknowledge this in the policy arena.
 
-Species are not randomly distributed in the world.
-The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of environmental variables such as temperature, salinity, and oxygen (fundamental niche), as well as interactions with other species (realized niche) [@Hunch].
-Thus, species distributions are key elements in marine resources management and policy, as human-made spatial boundaries are an indispensable part of the fisheries management system, from small marine protected areas to nation's economic exclusive zones (EEZs), to Regional Fisheries Management Organizations [@Song:2017iua].
+From 1973 to 1982 the members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].
+The stablishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over 200 nautical miles of their coasts [@UN:1982].
+Despite intended to improve fisheries management by granting property rights over shared ressources, this arbitrary delimitation of management area had no input from biogeography; ignoring species distributions created what we know today as shared stocks [@REF].
+The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary, those stocks that are shared by 2 or more neighboring coastal nations; (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas; and (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas.
 
-However, incorporating the concept of species distribution has not allays been the case in fisheries management as in the case of EEZs where 90% of wild fish is catched [@].
-From 1973 to 1982 the members of the United Nations held a series of meetings to discuss a series of regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].
-The third Conference on the Law of the Sea resulted the UN Convention on the Law of the Sea (UNCLOS) which allowed coastal states to claim jurisdiction over 200 nautical mile Exclusive Economic Zones (EEZs) of their coasts [@UN:1982].
-Despite intended to improve fisheries management, this arbitrary delimitation of management area had no input from biogeography, ignoring species distributions, and thus creating what we know today as shared stocks.
-Share stocks, as their name suggest, are fish stocks that live within the waters of two or more nations.
-The Food and Agricultural Organization of the UN (FAO) recognizes three types: (*i*) transboundary stocks, those stocks that are shared by 2 or more neighboring coastal nations (e.g.
-Pacific halibu *Hippoglossus stenolepsis*); (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas (e.g.
-Atlantic cod, *Gadus morhua*); (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas (e.g.
-all tunas and tuna-like species); and (*iv) discrete high seas stocks; those species that are only found in the high seas.
+The origination of shared stocks required the establishment of new fisheries management methods.
+Managers and scientists adopted a game theory apporach where collaboration would most likely result in the best overall outcome for nations sharing a common ressource [@REF].
+Lack of collaboration in shared stocks threatens the stocs's sustainabillity [@REF], reduces the profitabillity potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica?].
+Moreover, new emerging conflicts are expected as climate change shifts the distribution of marine species and new shared fisheries emerge [@Pinsky:2018cb].
 
-Despite previous attempts, is still not clear how many shared species exist and what is their contribution to global economy and protein production.
-It was estimated in 1997, that is 10 years after UNCLOS, that there could be up to 1,500 transboundary fish species in the world, however, such estimation lacked a proper assessment due to limited information at the time [@Caddy:1997ue].
+There is a gap in assessing transboundary species in the world based on their spatial distribution.
+It was estimated in 1997 that there could be up to 1,500 transboundary fish species in the world, however, such estimation lacked a proper assessment due to limited information at the time [@Caddy:1997ue].
 More recently, it was estimated there were 344 shared species, representing a capture of 34.2 × 10^6^ t and a global landed value of USD 30.7 × 10^9^ [@Teh:2015gd].
-While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the species distribution [@Teh:2015gd].
+While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the transboundary nature of the species [@Teh:2015gd].
 Therefore, 40 years after UNCLOS, the question of how many transboundary species exists in the world is still unanswered.
@@
 Our results suggest that there are XXX transboundary species in the world that account for XXX t landings generating USD xxx in fishing revenue to a total of USD xxxx in the fishing sector.
+These numbers represent an important contribution to global fish production and revenue estimated in XXX and XXX, respectiveley, hilighting the importance of transboundary stocks worldwide[@REf][@REf].
+
 Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
@@
 2).
+
 ![**Number of transboundary and discrete species by country and continent**](./Figures/Fig2.png)
@@
 
-100
-pelagic-oceanic
-3
-
-100
-pelagic-oceanic
-8
-Auxis thazard
-
 ![**Number of countries shared by transboundary species.** Showing only species that share > 20 countries](./Figures/Fig3.png)
 
-# **References** (up to 40)
+<!-- # **References** (up to 40 for reports and 15 for policy forum) -->
 
-# **Acknowledgments* *
+<!-- # **Acknowledgments* * -->
 

### 2019-09-20 Manuscript_Draft.Rmd
Methods advances

@@
 
-<!-- # Materials and Methods  -->
+# Materials and Methods
 
-<!-- For the current proyect we define a transboundary species as those that spend partial or total part of their life within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf].
-Such is the case of Pacific salmons (*Oncorhynchus sp.*) that live part of their life cycle within the US west coast and part within Canadian waters.
--->
+In here we present a novel method to estimate whether or not a species is transboundary.
+Our method is based on a series of criteria to be met and the overlap of species distributions and the spatial boundary of the world's EEZs.
+For the current analysis we work at the species level and adopt FAO's definition of transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf; @FAO].
 
-<!-- ## Databases on species geographic distributions -->
+## Databases on species geographic distributions
 
-<!-- To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs, we first determined their current distributions.
-For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) species distribution models, and (*iii*) fisheries catch data, in order to determine presence or absence of each species within each EEZ.
-(*i*) The observational data was collected from multiple databases online...**GABS** (*ii*) We then used data from two species distribution models.
+To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs, we first determined their current distributions.
+For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) Environmental Distribution Models (ENMs), and (*iii*) fisheries catch data.
+
+(*i*) The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+
+(*ii*) The ourrance data was used to determine a species presence but also to run two ENMs, hereafter refered as ENM-Nereus and ENM-SAU.
+For the ENM-Nereus [@REF] we employed all the data collected in the previous dataset.
+The model...
+
+In the case of the ENM-SAU [@Close:2006ux], the data was colelcted from Fishbase, OBIS, and FAO (www.fao.org).
+
 The Sea Around Us (SAU) distributions [@Close:2006ux], and an environmental niche model (ENM) [@REFGabs].
+
 (*iii*) Finally, we used the historical fisheries catch reconstructions provided by the SAU [@Zeller2016], **Version and updates GABS** spatially distributed along the world's EEZs [@Close:2006ux].
@@
 Only those species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species (**See S1_Data**).
--->
 
-<!-- In order to determine the presence or absence of each species in any given EEZ we define the EEZ boundaries using the Sea Around Us dataset (updated 1 July 2015, available from http://www.seaaroundus.org) sub-divided by regions (e.g.
+In order to determine the presence or absence of each species in any given EEZ we define the EEZ boundaries using the Sea Around Us dataset (updated 1 July 2015, available from http://www.seaaroundus.org) sub-divided by regions (e.g.
 Mexico Pacific and Mexico Atlantic).
--->
 
-<!-- ## Determine if a species is transboundary -->
+## Determine if a species is transboundary
 
-<!-- We developed three steps for determining whether or not a species was transboundary.
+We developed three steps for determining whether or not a species was transboundary.
 Such steps work as indexes to measure the uncertainty in the analysis.
 Only species that meet the criteria of the three steps were considered as transboundary species, those which did not were considered as discrete species only happening within one EEZ.
--->
 
-<!-- For each species and grid cell we firstly determine the presence or absence within each database.
+For each species and grid cell we firstly determine the presence or absence within each database.
 The *species Index* was computed by dividing the number of datasets that confirm presence over the total amount of datasets.
@@
 For this we estimate, for each species, the proportion of the total species distribution within both EEZs for each neighboring EEZ (**S2_Figure**).
--->
 
-<!-- ## Model validation  -->
+## Model validation
 
-<!-- While we do not know the transboundary nature of many species, some are jointly managed by neighboring countries or Regional Fisheries Management Organizations (RFMOs).
+While we do not know the transboundary nature of many species, some are jointly managed by neighboring countries or Regional Fisheries Management Organizations (RFMOs).
 Hence, in order to validate our results, we cross-check our transboundary species with the fished species and countries of 18 RFMOs all around the globe [@CullisSuzuki:2010fi].
--->
 

### 2019-10-14 Manuscript_Draft.Rmd
Advances in manuscript

@@
 ---
+
+```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+
+#### READ ME !!! ####
+# Run this chunk before knit so you make sure you have all pkgs installed in R
+
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg)) 
+    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
+  sapply(pkg, require, character.only = TRUE)
+}
+
+#### Library ####
+packages <- c(
+  "dplyr", # Data manipulation
+  "knitr",
+  "kableExtra"
+)
+
+ipak(packages)
+
+```
 
@@
 Species are not randomly distributed in the world.
-The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutaionary process [@REF].
+The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutionary process [@REF].
 Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua].
@@
 However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
-In here, we show that many species are shared, representing an important contrubution to national economies and food security, and hilighting the importance to aknowledge this in the policy arena.
+In here, we show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.
 
 From 1973 to 1982 the members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].
-The stablishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over 200 nautical miles of their coasts [@UN:1982].
-Despite intended to improve fisheries management by granting property rights over shared ressources, this arbitrary delimitation of management area had no input from biogeography; ignoring species distributions created what we know today as shared stocks [@REF].
+The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over 200 nautical miles of their coasts [@UN:1982].
+Despite intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management area had no input from biogeography; ignoring species distributions created what we know today as shared stocks [@REF].
 The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary, those stocks that are shared by 2 or more neighboring coastal nations; (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas; and (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas.
@@
 The origination of shared stocks required the establishment of new fisheries management methods.
-Managers and scientists adopted a game theory apporach where collaboration would most likely result in the best overall outcome for nations sharing a common ressource [@REF].
-Lack of collaboration in shared stocks threatens the stocs's sustainabillity [@REF], reduces the profitabillity potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica?].
+Managers and scientists adopted a game theory approach where collaboration would most likely result in the best overall outcome for nations sharing a common resource [@REF].
+Lack of collaboration in shared stocks threatens the stock's sustainability [@REF], reduces the profitability potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica?].
 Moreover, new emerging conflicts are expected as climate change shifts the distribution of marine species and new shared fisheries emerge [@Pinsky:2018cb].
@@
 Our results suggest that there are XXX transboundary species in the world that account for XXX t landings generating USD xxx in fishing revenue to a total of USD xxxx in the fishing sector.
-These numbers represent an important contribution to global fish production and revenue estimated in XXX and XXX, respectiveley, hilighting the importance of transboundary stocks worldwide[@REf][@REf].
+These numbers represent an important contribution to global fish production and revenue estimated in XXX and XXX, respectively, highlighting the importance of transboundary stocks worldwide[@REf][@REf].
 
@@
 <!-- Will run statistics to see if I can show the "why" of trans spp -->
-There is no clear visual pattern regarding transboundary and discrete species, however, from the three countries that house the most amount of discrete stocks, Australia, New Zeland and the US are among the larger in terms of EEZ lenght, in the other hand, Brazil has only two neighbors along its large latitudinal coast, suggesting not a lot of connection points for sharing species.
+There is no clear visual pattern regarding transboundary and discrete species, however, from the three countries that house the most amount of discrete stocks, Australia, New Zeland and the US are among the larger in terms of EEZ length, in the other hand, Brazil has only two neighbors along its large latitudinal coast, suggesting not a lot of connection points for sharing species.
 <!-- End of statistics paragraph -->
 
-All species that share over >100 countries are widly distributed pelagic species suchas as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) with a median of 65, 42, and 38 species per pelagic oceanic, bathymetric and nerictic species, respectively.
+All species that share over >100 countries are widely distributed pelagic species such as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) with a median of 65, 42, and 38 species per pelagic oceanic, bathymetric and nerictic species, respectively.
 The median for all other ecosystem preferences is under 35 as many of these species are not so widely distribute globally.
@@
 For the current analysis we work at the species level and adopt FAO's definition of transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf; @FAO].
+All data was scaled at a 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
 
@@
 
-To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs, we first determined their current distributions.
-For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) Environmental Distribution Models (ENMs), and (*iii*) fisheries catch data.
+To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs we first extract all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions.
+For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
+Each source represent a different method of estimating the distribution of a given species and thus, provides a more robust result.
+Only those commercial fished species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species, XX% of the reported marine species in the SAU database and XX% of the reported taxa of the FAO (**See S1_Data**).
 
-(*i*) The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+*i* The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
-(*ii*) The ourrance data was used to determine a species presence but also to run two ENMs, hereafter refered as ENM-Nereus and ENM-SAU.
-For the ENM-Nereus [@REF] we employed all the data collected in the previous dataset.
-The model...
+In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU.
+Although they use the same data, the models are structurally different complementing each other and providing robustness to the results.
 
-In the case of the ENM-SAU [@Close:2006ux], the data was colelcted from Fishbase, OBIS, and FAO (www.fao.org).
+*ii* The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxtent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+Environmental variables modeled were sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
+The ENM-Nereus employed all of the observational data-sources previously mention.
+Global environmental conditions were obtained and results averaged from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory's (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+For each species, we only considered models with an area under the curve larger than 0.7 and outputs from the models were average between *1970* and *2000* [@Asch:2018ca; @Reygondeau:2019uh].
 
-The Sea Around Us (SAU) distributions [@Close:2006ux], and an environmental niche model (ENM) [@REFGabs].
+*iii* The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
+For each commercial fish species, the model first uses the FAO major fishing areas and countries EEZs to determine a broad distribution.
+It then uses life history information to delimit its range within the FAO fishing area (e.g.
+thermal preference, depth limits).
+The range is delimited even further by expert-review polygons and compared with that of AquaMaps [@Kaschner:2016tl], OBIS and GBIF occurrence data.
+The model then determines a species habitat preference based on the assumptions that the relative abundance of a species is determine by the number of habitats in a grid cell and the distance of the species to each habitat, and the importance of the habitat to the species size.
+Finally, the species equatorial submergence (e.g.
+the latitudinal region where a species is not seen in between poles) is estimated for each species.
 
-(*iii*) Finally, we used the historical fisheries catch reconstructions provided by the SAU [@Zeller2016], **Version and updates GABS** spatially distributed along the world's EEZs [@Close:2006ux].
-All data was gridded on 0.5 x 0.5 grid cells.
-Only those species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species (**See S1_Data**).
+*iv* The previous models combine observational data with a series of biotic and abiotic information to determine the probability of a species to be in a given space and time.
+However, this does not mean that the species in question will actually be there.
+Although the models used have their own methods of double-check species distributions (e.g.
+ENM-Nereus uses four different species distribution algorithms and SPD-SAU verifies with other models), we used  a fourth data-source to corroborate the models' outputs.
+The *Sea Around Us* estimates catch that was not originally reported in the FAO database for each country based on all publicly available information sources.
+Fishing catch are also spatially allocated following a country-by-country catch reconstruction and spatial layers according to each species [@Zeller2016].
+Thus, we used the SAU catch reconstruction from 1970 to 2000 as the fourth dataset to estimate transboundary species and was also used to estimate their catch contribution within EEZs (average 1970-2000).
 
-In order to determine the presence or absence of each species in any given EEZ we define the EEZ boundaries using the Sea Around Us dataset (updated 1 July 2015, available from http://www.seaaroundus.org) sub-divided by regions (e.g.
-Mexico Pacific and Mexico Atlantic).
+```{r Data_Table, eval = T, echo = F}
+
+Dasets_names <- c(
+  "Occurrence",
+  "ENM-Nereus",
+  "SDM-SAU",
+  "Catch-SAU"
+)
+Brieff_Description <- c(
+  "Occurrence data from multiple sources",
+  "Environmental niche model based on environmental variables and different algorithms",
+  "Species distribution model based on species traits",
+  "Spatial catch allocation based on country-by-country reconstructions"
+)
+
+Sources <-  c(
+  "Reygondeau 2019",
+  "Asch et al., 2017 & Reygondeau 2019",
+  "Palomares et al., 2016",
+  "Zeller et al., 2016"
+)
+
+data.frame(Dasets_names,
+           Brieff_Description,
+           Sources) %>% 
+  kable("latex", booktabs = T,
+        caption = "Summary table of data sources ussed in the current analysis") %>%
+  kable_styling(full_width = F) %>%
+  column_spec(2,width = "8cm") %>% #wraps text in column2
+  column_spec(3,width = "3cm") #%>% #wraps text in column2
+
+```
 
@@
 
-We developed three steps for determining whether or not a species was transboundary.
-Such steps work as indexes to measure the uncertainty in the analysis.
-Only species that meet the criteria of the three steps were considered as transboundary species, those which did not were considered as discrete species only happening within one EEZ.
+We developed a four-criteria method for determining whether or not a species was transboundary.
+Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states.
+In some cases, criteria also work as indexes to measure the uncertainty in the analysis.
+All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* and code is available at https://github.com/jepa/FishForVisa.
 
-For each species and grid cell we firstly determine the presence or absence within each database.
-The *species Index* was computed by dividing the number of datasets that confirm presence over the total amount of datasets.
-Environmental niche models project the distribution of a certain species based on certain parameters such as environmental, behavioral or physiological of individuals and their environmental interaction (fundamental niche).
-However, such distribution does not represent the actual presence (realized niche) of the species after other factors such as species interactions have been taken into account [@Kearney:2010ip].
-To differentiate the fundamental from the realize niche models with the ENMs we used the SAU catch data reconstruction.
-All species that were reported as caught in any single year between 1950 and 2014 in a given EEZ were kept while those with absent catch data were dropped from the specific country.
-The assumption relies in that if a ESM projects a commercial species in any fishing country, such species would been fished, and reported, at some period of time (**S1_Figure**), validating the ESM result, thus, the existence of the species.
-Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed the *area Index*.
-For this we estimate, for each species, the proportion of the total species distribution within both EEZs for each neighboring EEZ (**S2_Figure**).
+### Criteria 1; Neighbouring EEZs
 
-## Model validation
+As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries.
+Hence, the first criteria was that the species would only be transboundary between two neighboring countries, regardless of the species extended distribution.
+This way, a species such as Atlantic cod (*Gadus morhua*) distributed along the north Atlantic, was only considered transboundary between each of the neighboring nations covering its distribution, rather than the region as a whole.
+We assume that this would reduce the differences between species and stock as is more likely that neighboring species belong to the same stock, rather than, lets say, Cod in Norway and Canada.
+However, the analysis here presented was kept at the species level.
 
-While we do not know the transboundary nature of many species, some are jointly managed by neighboring countries or Regional Fisheries Management Organizations (RFMOs).
-Hence, in order to validate our results, we cross-check our transboundary species with the fished species and countries of 18 RFMOs all around the globe [@CullisSuzuki:2010fi].
+We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
+Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf* *R* package [@SF:package].
+When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appears in more than one sub-region.
+Species that were present in EEZs that were non-continental territories neighboring other countries were kept (e.g.
+Argentina and Falkland Islands), but removed when the non-continental territory belonged to the same nation (e.g.
+Brazil and Fernando de Noronha).
+
+### Criteria 2; Data agreement
+
+We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells.
+We computed a *Species Index* by dividing the number of datasets that confirm presence of a species in a grid cell over the total amount of datasets (*n* = 3).
+The index is unit-less and represents a scale from 0.3 to 1 where 0.3 means only one dataset reports presence of the species in a grid cell and 1 means agreement between all datasets.
+We selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species (**S1_Map_per_dataset**).
+
+### Criteria 3; Modeling verification
+
+We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
+Therefore, all species that were not reported as caught in any single year between the reference years (1970 to 2000) in a given grid-cell were dropped, regardless of the *Species Index*.
+The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, and thus validating the models.
+
+### Criteria 4; Spatial distribution
+
+Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*.
+The *Area Index* consist in the proportion of the total species distribution within both EEZs that each neighboring EEZ has.
+We determine that a species would be transboundary if both neighboring EEZs enclosed over 25% of the species joint distribution.
+Such threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).
+
+## Fisheries trends
+
+Fisheries are important contributors to the world economy and livelihoods.
+We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
+The data includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
+similar countries, species) to fill in data gaps [@Sumaila:2015uc].
+Additionally, we used a previously estimated country-level multiplyer to understand the total direct, indirect, and induced impact of transboundary species on each country [@Dyck:2010ez].
+A continent average was used when no country-level multiplyer was available.
+
+We use the SAU catch data to estimate catch trends over time and determine the potential exploitation status of each species within a EEZ [@Grainger:1996tk; @Kleisner:2011wn].
+Despite a possible overestimation of overexploited and collapsed stocks when using only catch data [@Branch:2011br], this method can still shed a light on stock status when only catch data is available [@FAO:2011vz; @FAO:2018KK; @Kleisner:2011wn].
+However, the results should be seen as potential species status, rather than the true status of each species.
+We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years, and their catch was more than 1,000 tonnes.
+Five categories were drown from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
+Finally, we reported the predominant status over the last ten years of catch data (2004-2014).
+
+```{r Status_Table, eval = T, echo = F}
+
+Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")
+
+Rules <- c(
+  "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
+  "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
+  "Catch > (Max Catch*0.50)", #Max Exp.
+  "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
+  "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
+  "Non of the above rules applyed"
+)
+
+data.frame(Stock_Status,
+           Rules) %>% 
+  kable("latex", booktabs = T,
+        caption = "Rules to determine the status of each transboundary species") %>%
+  kable_styling(full_width = F) %>%
+  column_spec(1,width = "3cm") %>% #wraps text in column2
+  column_spec(2,width = "13cm") #%>% #wraps text in column2
 
 ```
+
+```

### 2019-10-14 Initial_Analysis.Rmd

@@
 
-## Sub Routine Estimating Neighbourds
+## Estimating Neighbourds
 
@@
 
-### Estimate Transboundary Species
+## Determine Species Status
+
+### Function `EstSppStatus`
+
+```{r Species_Status_fun, eval = T, echo =F}
+
+EstSppStatus <- function(Spp,Coord){
+
+  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
+    set_names(c(seq(1950,2014,1),"INDEX","Species","Longitude","Latitude")) %>% 
+    gather("Year","Value",`1950`:`2014`) %>%
+    arrange(INDEX) %>% 
+    left_join(Index_Code,
+              by = "INDEX") %>% 
+    filter(!is.na(EEZID),
+           Value > 0) %>% 
+    group_by(TaxonKey=Species,Year,Territory) %>% # Total catch per country
+    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
+    group_by(TaxonKey,Territory,Year) %>% 
+    mutate(RMean = rollmean(x = Total_Catch, 3,
+                            align = "right",
+                            fill = Total_Catch)
+           ) %>% # Running mean
+    select(-Total_Catch) %>% 
+    ungroup() %>% 
+    mutate(Year = as.numeric(Year))
+
+  # Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
+  Tresholds_Data <- Data %>% 
+    arrange(Territory) %>% 
+    group_by(TaxonKey,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
+    group_by(TaxonKey,Territory) %>% 
+    summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
+              Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
+              Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
+    ) %>% 
+    gather("Step","Treshold",Years_appart:Catch_over) %>% 
+    group_by(TaxonKey,Territory) %>% 
+    summarise(Met_Criteria = paste(unique(Treshold),collapse =";")
+              )
+
+  # Remove species that do not met the criterias
+
+    No_Status_Data <- Tresholds_Data %>% 
+      filter(Met_Criteria != "Yes") %>% 
+      select(TaxonKey,Territory) %>% 
+      mutate(Status = "No Status")
+
+  # Evaluate species that met the criteria
+
+    # Get Variables to perform status metric
+    Status_Data <- Data %>% 
+      anti_join(No_Status_Data, # Removes no status data
+                by = c("TaxonKey","Territory")
+      ) %>% 
+      # Get Max catch and max catch year
+      group_by(TaxonKey,Territory) %>% 
+      top_n(1,RMean) %>% 
+      rename(Max_Peak = RMean,
+             Y_Max_Peak = Year) %>% 
+      # Get Min catch after peak catch
+      left_join(Data,
+                by = c("TaxonKey","Territory")
+                ) %>% 
+      filter(Year > Y_Max_Peak) %>% 
+      group_by(TaxonKey,Territory) %>% 
+      top_n(-1,RMean) %>% 
+      rename(Post_Max_Min = RMean,
+             Y_Post_Max_Min = Year) %>% 
+      left_join(Data,
+                by = c("TaxonKey","Territory")
+                ) %>% 
+      # Final Evaluation 
+      mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                             ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
+                                    ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                           ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
+                                                  ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                         "No Status")
+                                           )
+                                    )
+                             )
+      )
+      ) %>% 
+      filter(Year > 2004) %>% # last 10 years of data
+      group_by(TaxonKey,Territory,Status) %>% 
+      summarise(n_Status= n()) %>% 
+      group_by(TaxonKey,Territory) %>% 
+      top_n(1,n_Status) %>%
+      select(-n_Status)
+
+    # If both datasets have value RETURN BOTH
+    if(nrow(No_Status_Data) > 0 & nrow(Status_Data) > 0){
+
+      Fun_Result <- bind_rows(No_Status_Data,
+                              Status_Data)
+    }
+
+    # If only No status data, then just return that
+    if(nrow(No_Status_Data) > 0 & nrow(Status_Data) == 0){
+      return(No_Status_Data)
+    }else{
+      return(Status_Data)
+    }
+
+}
+
+# Testing
+# Test_1 <- EstSppStatus(Species_List[1],CoorG)
+
+```
+
+### Data Species Status
+
+### Sub routine for Species Status
+
+```{r spp_status_data eval = T, echo = F}
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+# Gabriel's coordinate system
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+# Removes everything before the number
+Step_One <- gsub(".*_","",list.files(paste(Data_Path,"/Distribution_Data/SAU_Distribution/",sep="")))
+
+# Species List
+Species_List <- gsub("\\..*","",Step_One)
+
+```
+
+```{r species_status_routine eval = T, echo = F}
+# Needs to have trans species 
+Species_Status <- bind_rows(
+    mclapply(
+      Species_List,
+      FUN = EstSppStatus,
+      Coord = CoorG  # Gabriels coordinate system for read species dist
+    )
+  )
+
+# x <-Species_Status %>% 
+#   group_by(Territory,Status) %>% 
+#   summarise(n())
+
+write.csv(Species_Status,
+          paste(Data_Path,"Distribution_Data/Species_Status.csv",sep=""),
+                row.names = F)
+
+```
+
+## Estimate Transboundary Species
 
@@
 
-## Function `EstSppStatus`
-
-```{r Species_Status_fun, eval = T, echo =F}
-
-EstSppStatus <- function(Spp,Coord){
-
-  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
-    gather("Year","Value",CATCH.1:CATCH.65) %>% 
-    arrange(INDEX) %>% 
-    mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
-    left_join(Index_Code,
-              by = "INDEX") %>% 
-    filter(!is.na(EEZID),
-           Value > 0) %>% 
-    group_by(Species,Year,Territory) %>% # Total catch per country
-    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
-    group_by(Species,Territory,Year) %>% 
-    mutate(RMean = rollmean(x = Total_Catch, 3,
-                            align = "right",
-                            fill = Total_Catch)
-           ) %>% # Running mean
-    group_by(Species,Territory) %>% 
-    select(-Total_Catch)
-
-  # Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
-  Tresholds_Data <- Data %>% 
-    arrange(Territory) %>% 
-    group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
-    group_by(Species,Territory) %>% 
-    summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
-              Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
-              Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
-    ) %>% 
-    gather("Step","Treshold",Years_appart:Catch_over) %>% 
-    group_by(Species,Territory) %>% 
-    summarise(Met_Criteria = paste(unique(Treshold),collapse =";")
-              )
-
-  # Remove species that do not met the criterias
-
-    No_Status_Data <- Tresholds_Data %>% 
-      filter(Met_Criteria != "Yes") %>% 
-      select(Species,Territory) %>% 
-      mutate(Status = "No Status")
-
-  # Evaluate species that met the criteria
-
-    # Get Variables to perform status metric
-    Status_Data <- Data %>% 
-      anti_join(No_Status_Data, # Removes no status data
-                by = c("Species","Territory")
-      ) %>% 
-      # Get Max catch and max catch year
-      group_by(Species,Territory) %>% 
-      top_n(1,RMean) %>% 
-      rename(Max_Peak = RMean,
-             Y_Max_Peak = Year) %>% 
-      # Get Min catch after peak catch
-      left_join(Data,
-                by = c("Species","Territory")
-                ) %>% 
-      filter(Year > Y_Max_Peak) %>% 
-      group_by(Species,Territory) %>% 
-      top_n(-1,RMean) %>% 
-      rename(Post_Max_Min = RMean,
-             Y_Post_Max_Min = Year) %>% 
-      left_join(Data,
-                by = c("Species","Territory")
-                ) %>% 
-      # Final Evaluation 
-      mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                             ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
-                                    ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                           ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
-                                                  ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                         "No Status")
-                                           )
-                                    )
-                             )
-      )
-      ) %>% 
-      filter(Year > 2004) %>% # last 10 years of data
-      group_by(Species,Territory,Status) %>% 
-      summarise(n_Status= n()) %>% 
-      group_by(Species,Territory) %>% 
-      top_n(1,n_Status) %>%
-      select(-n_Status)
-
-    # If both datasets have value RETURN BOTH
-    if(nrow(No_Status_Data) > 0 & nrow(Status_Data) > 0){
-
-      Fun_Result <- bind_rows(No_Status_Data,
-                              Status_Data)
-    }
-
-    # If only No status data, then just return that
-    if(nrow(No_Status_Data) > 0 & nrow(Status_Data) == 0){
-      return(No_Status_Data)
-    }else{
-      return(Status_Data)
-    }
-
-}
-
-# Testing
-# Test_1 <- EstSppStatus(Species_List[1],CoorG)
-
-Species_Status <- bind_rows(
-    mclapply(
-      Species_List,
-      FUN = EstSppStatus,
-      Coord = CoorG  # Gabriels coordinate system for read species dist
-    )
-  )
-
-```
-
 ## Load Results data
@@
 
+  # Read SAu Status Data
+  Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep ="")) %>% 
+    rename(TaxonKey = Species)
+
   # List of species
@@
     Trans_Rate = n_trans_spp/n_Neighbours
+    ) %>% 
+  mutate(
+  Bins = cut(n_trans_spp,breaks = 4),
+  Bins_Plot = cut(n_trans_spp,breaks = 4,
+             labels = c('super low', 'low', 'high','super high'))
   )
@@
 
-```
-
-### Map of Transboundary Species
-
-```{r Territory_Map, eval =F, echo =F}
-
-World_sf_si <- World_sf %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="Territory")
-
-#  Top 10 Larger EEZs...
-# World_sf_si %>% 
-#   arrange(desc(Area_km2)) %>% 
-#   head(10)
+# Get Catch and Revenue data for mapping
 
@@
   group_by(Territory) %>% 
-  summarise(Total_USD = sum(Mean_Value,na.rm=T)) %>% 
-  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory))
-
-hist(Revenue_Country$Total_USD)
-
+  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% 
+  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
+         Bins = cut(Total_USD,breaks = 4),
+         Bins_Plot = cut(Total_USD,breaks = 4,
+                    labels = c('super low', 'low','high','super high'))
+         ) %>% 
+  filter(Total_USD > 0)
+
+```
+
+### Map of Transboundary Species
+
+```{r Territory_Map, eval =F, echo =F}
+
+# Transboundary Species shapefile
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Transboundary_Spp, by ="Territory")
+
+# Total catch/Revenue shapefile
 World_sf_si_land <- World_land_sf %>%
   st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
-  left_join(Revenue_Country, by ="Territory") # Include total specices catch
-
-# head(World_sf_si)s
-
-# Create a pellet for plotting
-# pal <- wes_palette("Zissou1", 1000, type = "continuous")
-
-World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 4)
-World_sf_si_land$Bins <- cut(World_sf_si_land$Total_USD,breaks = 4)
-
-World_sf_si_land <- World_sf_si_land %>% 
-  arrange(Total_USD)
-
-World_sf_si <- World_sf_si %>% 
-  arrange(n_trans_spp)
-
-# head(World_sf_si)
-# head(World_sf_si_land)
-
-# unique(World_sf_si$Bins)
-# unique(World_sf_si_land$BinsLan)
-
-# levels(World_sf_si$Bins)
-# levels(World_sf_si_land$BinsLan)
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
+  left_join(Revenue_Country, by ="Territory")
 
@@
 
+# Make map
 Plot <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80",size = 0.1) +
-  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
+  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
   geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
@@
   # ) +
-  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
+  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+                                  "#00A08A",#"#00A08A", #green
+                                  "#F2AD00",#"#F2AD00", # Yellow
+                                  # "#F98400",#"#F98400", #Orange
+                                  "#FF0000"#,"#FF0000" #Red
+                                  ),
   na.value = "white"
@@
 
+# -------------------------- #
+# Stock status Data
+# -------------------------- #
+
+Status_Data_Plot <- Tresholded_T_Data %>% 
+  mutate(TaxonKey = as.character(TaxonKey)) %>% 
+  # rename(Territory = CT_fishing_entity) %>% 
+  left_join(Status_Data, 
+            by =c("Territory","TaxonKey")
+            ) %>%
+  mutate(Status = ifelse(is.na(Status),"No Status",Status)) %>% 
+  group_by(Territory,Status) %>% 
+  summarise(value = length(unique(TaxonKey))) %>% 
+  left_join(UN_Regions, by ="Territory") %>%
+  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+  rename(FishingRegion=Territory) %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  group_by(individual = fishing_entity,
+           group = Georegion,
+           observation = Status) %>% 
+  summarise(Total_trans = sum(value,na.rm=T)) %>% 
+  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
+  filter(!is.na(individual)) %>% 
+  select(individual,observation,group,value) %>% 
+  arrange(group,value) %>% 
+  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value))
+
 # Include possible missing countries in bothe datasets
@@
   bind_rows(Discrete_Data_Plot)
+
+```
+
+```{r}
+
+data <- data.frame(
+  individual=paste( "Mister ", seq(1,60), sep=""),
+  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
+  value1=sample( seq(10,100), 60, replace=T),
+  value2=sample( seq(10,100), 60, replace=T),
+  value3=sample( seq(10,100), 60, replace=T)
+)
+
+# Transform data in a tidy format (long format)
+data <- data %>% gather(key = "observation", value="value", -c(1,2))
+
+# Set a number of 'empty bar' to add at the end of each group
+empty_bar <- 2
+nObsType <- nlevels(as.factor(data$observation))
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group)*nObsType, ncol(data)) )
+colnames(to_add) <- colnames(data)
+to_add$group <- rep(levels(data$group), each=empty_bar*nObsType )
+data <- rbind(data, to_add)
+data <- data %>% arrange(group, individual)
+data$id <- rep( seq(1, nrow(data)/nObsType) , each=nObsType)
+
+# Get the name and the y position of each label
+label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# prepare a data frame for base lines
+base_data <- data %>% 
+  group_by(group) %>% 
+  summarize(start=min(id), end=max(id) - empty_bar) %>% 
+  rowwise() %>% 
+  mutate(title=mean(c(start, end)))
+
+# prepare a data frame for grid (scales)
+grid_data <- base_data
+grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
+grid_data$start <- grid_data$start - 1
+grid_data <- grid_data[-1,]
+
+# Make the plot
+ggplot(data) +
+
+  # Add the stacked bar
+  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
+  scale_fill_viridis(discrete=TRUE) +
+
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+
+  # Add text showing the value of each 100/75/50/25 lines
+  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
+
+  ylim(-150,max(label_data$tot, na.rm=T)) +
+  theme_minimal() +
+  theme(
+    legend.position = "none",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() +
+
+  # Add labels on top of each bar
+  geom_text(data=label_data, aes(x=id, y=tot+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +
+
+  # Add base line information
+  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
+  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
+
+```
+
+```{r Territories_Circluar_Plot, eval = T, echo = T}
+
+# -------------------------- #
+# Data manipulation for plot
+# -------------------------- #
+
+# Set a number of 'empty bar' to add at the end of each Georegion
+Char <- as.factor(Status_Data_Plot$group) # Set groups to factors
+
+##### COPY PASTE
+
+# Transform data in a tidy format (long format)
+data <- Status_Data_Plot
+
+# Set a number of 'empty bar' to add at the end of each group
+empty_bar <- 5
+nObsType <- nlevels(as.factor(data$observation))
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(data)) )
+colnames(to_add) <- colnames(data)
+to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
+to_add$individual <- rep(letters[1:6], each=empty_bar*nObsType)
+data <- bind_rows(data, to_add)
+data <- data %>% arrange(group, individual) %>% rowwise() %>%  mutate(id = as.numeric(as.factor(individual)))
+data$id <- as.numeric(as.factor(data$individual))
+
+# Get the name and the y position of each label
+label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# prepare a data frame for base lines
+base_data <-  data %>% 
+  group_by(group) %>% 
+  summarize(start=min(id,na.rm=T), end=max(id,na.rm=T) - empty_bar) %>% 
+  rowwise() %>% 
+  mutate(title=mean(c(start, end)))
+
+# prepare a data frame for grid (scales)
+grid_data <- base_data
+grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
+grid_data$start <- grid_data$start - 1
+grid_data <- grid_data[-1,]
+
+data <- data %>% 
+  ungroup() %>% 
+  mutate(individual = ifelse(is.na(observation),NA,observation))
+
+ggplot(data) + 
+  # Add the stacked bar
+  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
+  scale_fill_manual("Continent",
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 1, name = "Darjeeling2")
+                    ),
+                    na.value = "white"
+  ) +
+
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+
+  # Add text showing the value of each 100/75/50/25 lines
+  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
+
+  ylim(-150,max(label_data$tot, na.rm=T)) +
+  theme_minimal() +
+  theme(
+    legend.position = "right",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() +
+
+  # Add labels on top of each bar
+  geom_text(data=label_data, aes(x=id, y=max(tot,na.rm=T), label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2, angle= label_data$angle, inherit.aes = FALSE ) +
+
+  # Add base line information
+  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
+  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,1,0,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
+
+#### END COPY PASTE
+
+empty_bar <- 5
+nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
+colnames(to_add) <- colnames(Status_Data_Plot)
+to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
+Status_Data_Plot <- bind_rows(Status_Data_Plot, to_add)
+Status_Data_Plot <- Status_Data_Plot %>% arrange(group, individual)
+# Status_Data_Plot$id <- c(rep(seq(1,round(nrow(Status_Data_Plot)/nObsType)) , each=nObsType),128)
+Status_Data_Plot$id <- as.numeric(as.factor(Status_Data_Plot$individual))
+
+# Get the name and the y position of each label
+
+# Top n of each group label
+Top_Countries <- Status_Data_Plot %>% 
+  group_by(group) %>% 
+  top_n(5,value)
+
+# Create labels for all but top 5
+# Get the name and the y position of each label
+
+label_data <- Status_Data_Plot %>% 
+  group_by(id, individual) %>% 
+  summarize(tot=sum(value))
+
+label_data <- Status_Data_Plot 
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# Remove top 5
+label_data_rest <- label_data %>% 
+  filter(!individual %in% Top_Countries$individual)
+
+# Create labels for top 5
+Top_label_data <- label_data %>% 
+  filter(individual %in% Top_Countries$individual)
+
+# prepare a data frame for base lines
+base_data <- Status_Data_Plot %>% 
+  group_by(group) %>% 
+  summarize(start=min(id,na.rm=T), 
+            end=max(id,na.rm=T) - empty_bar, 
+            median = median(value, na.rm = T)
+            ) %>% 
+  rowwise() %>% 
+  mutate(title=mean(c(start, end)))
+
+# prepare a data frame for grid (scales)
+grid_data <- base_data
+grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
+grid_data$start <- grid_data$start - 1
+# grid_data[1,2] <- 5 # Manually include Africa for the median
+# grid_data[1,3] <- 1
+
+# Median data
+median_data <- grid_data %>% 
+  mutate_at(vars(start,end),
+            .funs = as.numeric)
+
+# -------------------------- #
+# Make the plot
+# -------------------------- #
+
+# Global Variables
+Seq_axis <- seq(0,100,20)
+Plot_Limit <- max(Status_Data_Plot$value,na.rm=T)
+Plot_Limit_Low <- -50
+Ticks_Color <- "grey50"
+
+ggplot(Status_Data_Plot) +
+
+  # Add the stacked bar
+  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
+  # scale_fill_viridis(discrete=TRUE) +
+
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+
+  # Add text showing the value of each 100/75/50/25 lines
+  ggplot2::annotate("text", x = rep(max(Status_Data_Plot$id,na.rm=T),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
+
+  ylim(-150,max(label_data$value, na.rm=T)) +
+  theme_minimal() +
+  theme(
+    legend.position = "none",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() +
+
+  # Add labels on top of each bar
+  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +
+
+  # Add base line information
+  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
+  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0,1,1), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
+
+# Base plot
+ggplot(Status_Data_Plot,
+       aes(x=as.factor(id), 
+           y=value,
+           fill=observation)
+) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=observation),
+           stat="identity",
+           alpha=0.5) +
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) +
+  # Add median lines for each gropup
+  # geom_segment(data=median_data,
+  #              aes(x = end,
+  #                  y = median,
+  #                  xend = start+5, 
+  #                  yend = median,
+  #                  colour = group),
+  #              alpha=1,
+  #              size=0.5 , 
+  #              inherit.aes = FALSE ) +
+  # Add text showing the value of each line
+  annotate("text", 
+           x = rep(max(Status_Data_Plot$id),length(Seq_axis)),
+           y = Seq_axis,
+           label = c("<-100",as.character(Seq_axis)[2:(length(Seq_axis)-1)],">100"),
+           color = Ticks_Color, 
+           size= 4, 
+           angle = 0, 
+           # fontface="bold",
+           hjust=1) +
+  ylim(-150,max(label_data$value, na.rm=T)) +
+  theme_minimal() +
+  theme(
+    legend.position = "none",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() +
+  #Country labels
+  geom_text(data=label_data_rest,
+            aes(x=id,
+                y=Plot_Limit,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            # fontface="bold",
+            alpha=1,
+            size=2.5,
+            angle= label_data_rest$angle,
+            inherit.aes = FALSE) +
+  # Bold top 3 
+  geom_text(data=Top_label_data,
+            aes(x=id, y=Plot_Limit,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
+            alpha=1,
+            size=2.5,
+            angle= Top_label_data$angle,
+            inherit.aes = FALSE) +
+  # Add base line information
+  geom_segment(data=base_data, 
+               aes(x = start, 
+                   y = 0, 
+                   xend = end, 
+                   yend = 0
+                   ), 
+               colour = "black",
+               alpha=0.8, 
+               size=0.6 , 
+               inherit.aes = FALSE) +
+  ylim(Plot_Limit_Low,Plot_Limit) + # sets the circle the first value the central the last value how wide
+  theme_minimal() +
+  coord_polar()
+  theme(
+    # legend.position = c(0.5,0.5),
+    # legend.position = "",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() + 
+  scale_fill_manual("Continent",
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 4, name = "Darjeeling2"),
+                               "black","grey","blue"
+                    ),
+                    na.value = "white"
+  ) +
+  scale_colour_manual("Continent",
+                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                                 wes_palette(n = 4, name = "Darjeeling2"),
+                                 "black","grey","blue"
+                      ),
+                      na.value = "white")
+
+# Save plot
+
+ggsave(
+    plot = last_plot(),
+    width = 12,
+    height = 12,
+    units = "in",
+    filename = "Territory_circular_both.png",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+  )
+
+```
+
+```{r Top_country_Circle_Diagram, eval =F, echo = F}
+
+# Top 10 species
+
+# Number of countries shared by each Species
+Top_10_Countries <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No"
+         ) %>% 
+  group_by(Country_Territory) %>% 
+  summarise(
+    n_countries = length(unique(TaxonKey))
+  ) %>% 
+  top_n(10,n_countries)
+
+# Countries that share the top 10
+Top_Ten_Countries <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No",
+         Country_Territory %in% Top_10_Countries$Country_Territory
+         ) %>% 
+  group_by(from=CT_fishing_entity,
+           to=NT_fishing_entity
+           ) %>% 
+  summarise(value=n()
+            ) %>% 
+  ungroup() %>% 
+  mutate(from = paste("F", from),
+         to = paste("T", to)
+         )
+
+####________________###
+# Circulize package ####
+# https://jokergoo.github.io/circlize_book/book/
+####________________###
+
+# To set links collor 
+Bins <- as.numeric(cut(Top_Ten_Countries$value,breaks = 5))
+
+# Basic plot
+circos.clear()
+chordDiagram(Top_Ten_Countries, 
+             annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
+             annotationTrackHeight = c(0.001, 0.05), # set links close to the axis
+             directional = 1, # direction of arrows
+             direction.type = c("diffHeight", "arrows"), # use arrows
+             grid.col = "white",
+             col = ifelse(Bins == 1,"#046C9A", # deep blue
+                          ifelse(Bins == 2,"#78B7C5", #light blue
+                                 ifelse(Bins == 3,"#EBCC2A", #yellow
+                                        ifelse(Bins == 4, "#E1AF00", #cream
+                                               "#F21A00")))), #red
+             link.arr.col = wes_palette("Zissou1"),
+             link.arr.type = "big.arrow",# make links big arrows
+             diffHeight = uh(1, "mm"), # brings the arrow to the bottom of the source
+             # annotationTrack = "grid", # no labels
+             scale = FALSE, # fraction of total instead of absolute value
+             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Top_Ten_Countries))))) # I have no idea but helps with the labels
+    ) 
+#  Rest of eddits
+circos.track(track.index = 1, panel.fun = function(x, y) {
+    xlim = get.cell.meta.data("xlim")
+    xplot = get.cell.meta.data("xplot")
+    ylim = get.cell.meta.data("ylim")
+    sector.name = get.cell.meta.data("sector.index")
+
+    circos.text(mean(xlim),
+                ylim[1], 
+                sector.name, 
+                facing = "clockwise",
+                niceFacing = TRUE,
+                adj = c(-0.2, 0.5),
+                col = "black")
+
+}, bg.border = NA)
+
+```
+
+## Analysis per Species
+
+```{r n_species_country, eval = T, echo =F}
+
+# Number of countries shared by each Species
+Species_Trans <- Tresholded_T_Data %>% 
+  group_by(TaxonKey) %>% 
+  summarise(
+    n_countries = length(unique(Territory))
+  ) %>% 
+  left_join(Exploited_Species) %>%
+  left_join(Spp_Clasification)
+
+# hist(Species_Trans$n_countries)
+
+# Use rfishbase to get species environment
+
+Species_list <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>% 
+  pull(scientific_name)
+
+Species_environ_list <- rbind(species(Species_list, 
+                                      fields = species_fields$habitat[4])
+) %>% 
+  mutate(scientific_name = Species_list)
+
+Species_Data <- Tresholded_T_Data %>% 
+  group_by(TaxonKey) %>% 
+  summarise(n_trans_spp = length(unique(Territory))) %>% 
+  left_join(Exploited_Species) %>%
+  rename(scientific_name = TaxonName) %>% 
+  left_join(Species_environ_list) %>%
+  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
+         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
+  select(individual=scientific_name,
+         value = n_trans_spp,
+         group = DemersPelag) %>% 
+  arrange(group,value) %>% 
+  filter(value > 20)  # remove all species under 10 (way too many to plot!)
+
+```
+
+### OHI-inspired Circular plot Species
+
+```{r species_circluar_plot, eval = T, echo = T}
+
+Median_trans <- median(Species_Data$value)
+# hist(Species_Data$value)
+# unique(Species_Data$group)
+
+Char <- as.factor(Species_Data$group)
+
+# Set a number of 'empty bar' to add at the end of each group
+empty_bar <- 2
+to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
+colnames(to_add) <- colnames(Species_Data)
+to_add$group <- rep(levels(Char), each=empty_bar)
+Species_Data <- rbind(Species_Data, to_add)
+Species_Data <- Species_Data %>% arrange(group,value)
+Species_Data$id <- seq(1, nrow(Species_Data))
+
+# Get the name and the y position of each label
+
+# Create labels for all but top 5
+label_data <- Countries_Data 
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# Get the name and the y position of each label
+# Top n of each group label
+Top_spp <- Species_Data %>% 
+  group_by(group) %>% 
+  top_n(5,value)
+
+# Create labels for all but top 5
+label_data <- Species_Data
+number_of_bar <- nrow(label_data)
+angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
+label_data$hjust <- ifelse( angle < -90, 1, 0)
+label_data$angle <- ifelse(angle < -90, angle+180, angle)
+
+# Remove top 5
+label_data_rest <- label_data %>% 
+  filter(!individual %in% Top_spp$individual)
+
+# Create labels for top 5
+Top_label_data <- label_data %>% 
+  filter(individual %in% Top_spp$individual)
+
+# prepare a data frame for base lines
+base_data <- Species_Data %>% 
+  group_by(group) %>% 
+  summarize(start=min(id), 
+            end=max(id) - empty_bar, 
+            median = median(value, na.rm = T)
+            ) %>% 
+  rowwise() %>% 
+  mutate(title=mean(c(start, end)))
+
+# prepare a data frame for grid (scales)
+grid_data <- base_data
+grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
+grid_data$start <- grid_data$start - 1
+# grid_data <- grid_data[-1,]
+grid_data[1,2] <- 5 # Manually include bathydemerssal
+grid_data[1,3] <- 1
+
+# Median data
+median_data <- grid_data %>% 
+  mutate_at(vars(start,end),
+            .funs = as.numeric)
+
+Seq_axis_spp <- seq(20,100,20)
+Plot_Limit <- max(Species_Data$value,na.rm=T)
+
+# Make the plot
+ggplot(Species_Data, 
+       aes(x=as.factor(id), 
+           y=value,
+           fill=group)
+       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=group),
+           stat="identity",
+           alpha=0.5) +
+  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  # Add median lines for each gropup
+  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
+               alpha=1, size=0.5 , inherit.aes = FALSE ) +
+  # Add text showing the value of each line
+  annotate("text", 
+           x = rep(max(Species_Data$id),5),
+           y = Seq_axis_spp,
+           label = c(Seq_axis_spp[-5],">100"),
+           color=Ticks_Color, 
+           size=3 , 
+           angle=0, 
+           fontface="bold",
+           hjust=1) +
+  geom_bar(aes(x=as.factor(id),
+               y=value,
+               fill=group),
+           stat="identity",
+           alpha=0.5) +
+  geom_text(data=label_data_rest,
+            aes(x=id, y=101,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            fontface="italic",
+            alpha=1,
+            size=2.5,
+            angle= label_data_rest$angle,
+            inherit.aes = FALSE) +
+  # Bold top 3 
+  geom_text(data=Top_label_data,
+            aes(x=id, y=101,
+                label=individual,
+                hjust=hjust), 
+            color="black",
+            fontface="bold.italic",
+            alpha=1,
+            size=2.5,
+            angle= Top_label_data$angle,
+            inherit.aes = FALSE) +
+  # Add base line information
+  geom_segment(data=base_data, 
+               aes(x = start, 
+                   y = -5, 
+                   xend = end, 
+                   yend = -5
+                   ), 
+               colour = "black",
+               alpha=0.8, 
+               size=0.6 , 
+               inherit.aes = FALSE) +
+  ylim(-100,110) + # sets the circle the first value the central the last value how wide
+  theme_minimal() +
+  theme(
+    legend.position = c(0.5,0.5),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-1,4), "cm") 
+  ) +
+  coord_polar() + 
+  scale_fill_manual("Ecosystem Preference",
+                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
+                               wes_palette(n = 4, name = "GrandBudapest2")
+                    ),
+                    na.value = "white"
+  ) +
+  scale_colour_manual("Ecosystem Preference",
+                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
+                                 wes_palette(n = 4, name = "GrandBudapest2")
+                      ),
+                      na.value = "white"
+  )
+# 
+ggsave(
+    plot = last_plot(),
+    width = 12,
+    height = 12,
+    units = "in",
+    filename = "Species_circular_over20.png",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+  )
+
+```
+
+### Species status (SAU methods)
+
+Note that (n), the number of ‘stocks’ is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area is at least 1000 tonnes.
+
+ 1) The first and last reported landings are at least ten years apart;
+
+2) There are at least five years of consecutive catches; and
+
+3) The catch in a particular area (LME) is at least 1,000 tonnes.
+
+Once those tresholds are met, the status of the species is determined as follows:
+
+- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
+- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
+- Exploited	Landing > 50% of max. landing
+- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
+- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
+
+*Notes* = 3 years average mean
+
+```{r Species_Status, eval = T, echo =F}
+
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+Spp <- GetSppDist(600004, Model = "SAU_C", Coord = CoorG)
+
+Data <- Spp %>% 
+  gather("Year","Value",CATCH.1:CATCH.65) %>% 
+  arrange(INDEX) %>% 
+  mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
+  left_join(Index_Code) %>% 
+  filter(!is.na(EEZID),
+         Value > 0) %>% 
+  group_by(Species,Year,EEZID,Territory) %>% # Total catch per country
+  summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
+  group_by(Species,Territory,EEZID,Year) %>% 
+  mutate(RMean = rollmean(x = Total_Catch, 5, align = "right", fill = Total_Catch)) %>% 
+  group_by(Species,Territory,EEZID)
+
+# head(Data)
+
+# Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
+ Tresholds <- Data %>% 
+  arrange(Territory) %>% 
+  group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
+            Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
+            Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
+            ) %>% 
+   gather("Step","Treshold",Years_appart:Catch_over) %>% 
+   filter(Treshold == "Yes")
+
+ # Evaluate stocks
+
+ # Filter data that does not satisfy tresholds
+
+ Landings_Peaks <- Data %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Max_Peak = max(RMean,na.rm=T))
+
+ Eval_Data <- Data %>% 
+  semi_join(Tresholds,
+            by = c("Species","Territory")) %>% 
+   left_join(Landings_Peaks,
+             by = c("Species","Territory"))
+
+ Peak_Year <- Eval_Data %>% 
+   filter(RMean == Max_Peak) %>% 
+   select(Species,Territory,EEZID,Y_Max_Peak = Year)
+
+ Post_Max_Min <- Eval_Data %>% 
+   left_join(Peak_Year) %>% 
+   filter(Year > Y_Max_Peak) %>% 
+   group_by(Species,Territory,EEZID) %>% 
+   summarise(Post_Max_Min = min(RMean,na.rm=T))
+
+ Y_Post_Max_Min <- Eval_Data %>% 
+   left_join(Post_Max_Min) %>% 
+   filter(RMean == Post_Max_Min) %>% 
+   select(Species,Territory,EEZID,Y_Post_Max_Min = Year)
+
+ Data_Status <- Eval_Data %>% 
+   left_join(Peak_Year,
+             by = c("Species","Territory","EEZID")) %>%
+   left_join(Post_Max_Min,
+             by = c("Species","Territory","EEZID")) %>% 
+   left_join(Y_Post_Max_Min,
+             by = c("Species","Territory","EEZID")) %>% 
+   rename(Y_RMean = Year) %>% 
+   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
+                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
+                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                      "No Status")
+                                        )
+                                 )
+                          )
+   )
+   ) %>% 
+   filter(Y_RMean > 2004) %>% 
+   group_by(Species,EEZID,Territory,Status) %>% 
+   summarise(n_Status= n()) %>% 
+   group_by(Species,EEZID,Territory) %>% 
+   top_n(1,n_Status)
+
+ # Manual estimation
+
+ data.frame(
+   Y_RMean = 1980,
+   RMean = 642187,
+   Max_Peak = 1298712,
+   Y_Max_Peak = 1990,
+   Post_Max_Min = 681967,
+   Y_Post_Max_Min = 2010,
+   Y_RMean = 2014
+ ) %>% 
+   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
+                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))," Over Exploited",
+                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                      "NA")
+                                        )
+                                 )
+                          )
+   )
+   )
+
+```
+
+```{r Top_spp_Circle_Diagram, eval =F, echo = F}
+
+# Top 5 shared species per marine environment (number of countries sharing the species)
+Top_Species <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
+  # group_by(TaxonKey,TaxonName,CommonName,DemersPelag) %>% 
+  # summarise(Sum_Countries =sum(n_countries,na.rm=T)) %>% 
+  group_by(DemersPelag) %>% 
+  top_n(5,n_countries)
+
+# Countries that share the top 10
+Top_Spp_Countries <- Clean_Results_Trans %>% 
+  filter(
+    Area_Index < Min_AI |
+      Area_Index > Max_AI,
+    Model_Index == MI,
+    Same_Nation == "No",
+    TaxonKey %in% Top_Species$TaxonKey
+  ) %>% 
+  left_join(Species_Trans) %>% 
+  rename(scientific_name =TaxonName) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(from = paste(Genus,"\n",Species,sep=""),
+         DemersPelag = replace_na(DemersPelag, "Other")) %>%
+  group_by(
+    # from,
+    from = scientific_name,
+           to=CT_fishing_entity,
+           DemersPelag
+  ) %>% 
+  summarise(value=n()
+  ) #%>%
+  # filter(DemersPelag == "demersal") %>%
+  # select(-DemersPelag)
+
+####________________###
+# Circulize package ####
+# https://jokergoo.github.io/circlize_book/book/
+####________________###
+
+# To set links color 
+Bins <- as.numeric(cut(Top_Spp_Countries$value,breaks = 5)) # By size of sharing
+
+# To get country's flags... https://flagpedia.net/download
+flags <- c(paste("Temporal_Data/flags-mini/",list.files("Temporal_Data/flags-mini/"),sep=""))
+
+# List of Ecosystems
+Classification <- Top_Species %>% group_by(DemersPelag) %>% summarise(n()) %>%  pull(DemersPelag)
+
+####________________ PLOT PER ECOSYSTEM _____________________ ###
+
+for(s in 1:2){ # sclae loop
+  for(i in 1:length(Classification)) {
+    # for(i in 1:2) { # for testing
+
+    # Set scales to plott both absolut and proportional values
+    if(s == 1){
+      Scales <- "TRUE"
+    }else{
+      Scales <- "FALSE"
+    }
+
+    # Saving the plot
+    Plot_name <- paste(Figures_Path,Classification[i],Scales,".tiff",sep="")
+    tiff(Plot_name, width = 5, height = 5, units = 'in', res = 500)
+
+    # Subsetting the data for each plot
+    DemersPelag_i <- Classification[i]
+
+    Data <- Top_Ten_Spp_Countries %>% 
+      filter(DemersPelag %in% DemersPelag_i) %>% 
+      select(-3)
+
+    # Use to set links' colors to each species
+    Speceis_cols <- Data %>% group_by(from) %>% summarise(n()) %>% pull(from)
+
+    # The base plot
+    circos.clear()
+    chordDiagram(Data, 
+                 annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
+                 annotationTrackHeight = c(0.001, 0.1), # set links close to the axis
+                 directional = 1, # direction of arrows
+                 direction.type = c("diffHeight", "arrows"), # use arrows
+                 grid.col = "grey",
+                 # if col == Bins then colors will change depending of value
+                 # col = ifelse(Bins == 1,"#046C9A", # deep blue
+                 #              ifelse(Bins == 2,"#78B7C5", #light blue
+                 #                     ifelse(Bins == 3,"#EBCC2A", #yellow
+                 #                            ifelse(Bins == 4, "#E1AF00", #cream
+                 #                                   "#F21A00")))), #red
+                 # if col == Species_cols then colors will change depending of species
+                 col = ifelse(Data$from == Speceis_cols[1],"#FF0000", # deep blue
+                              ifelse(Data$from == Speceis_cols[2],"#00A08A", #light blue
+                                     ifelse(Data$from == Speceis_cols[3],"#F2AD00", #yellow
+                                            ifelse(Data$from == Speceis_cols[4], "#F98400", #cream
+                                                   "#5BBCD6")))), #red
+                 # link.arr.col = wes_palette("Zissou1"), 
+                 link.arr.type = "big.arrow",# make links big arrows
+                 diffHeight = uh(-0.5, "mm"), # brings the arrow to the bottom of the source
+                 scale = Scales, # fraction of each species to total share of each country instead of absolute value
+                 preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Data))))) # I have no idea but helps with the labels
+    )
+
+    #  Function to inlcude other layers
+    circos.track(track.index = 1, panel.fun = function(x, y) {
+      xlim = get.cell.meta.data("xlim")
+      xplot = get.cell.meta.data("xplot")
+      ylim = get.cell.meta.data("ylim")
+      sector.name = get.cell.meta.data("sector.index")
+
+      # Add labels
+      circos.text(mean(xlim),
+                  ylim[1],
+                  sector.name,
+                  facing = "clockwise",
+                  niceFacing = TRUE,
+                  adj = c(-0.2, 0.5),
+                  col = "black",
+                  cex = 0.6) # size of labels
+
+      # Add country's flags instead of names (still need to link names to falgs)
+
+      # library(EBImage)
+      # pos = circlize:::polar2Cartesian(circlize(CELL_META$xcenter, CELL_META$ycenter))
+      # image = EBImage::readImage(flags[CELL_META$sector.numeric.index])
+      # 
+      # rasterImage(image,
+      #             xleft = pos[1, 1] - 0.006, 
+      #             ybottom = pos[1, 2] - 0.005,
+      #             xright = pos[1, 1] + 0.05,
+      #             ytop = pos[1, 2]+ 0.04
+      #             )
+
+      # END FLAGS TRYOUT
+
+      # Set plot Title
+      Title <- paste("Top",Classification[i], "Species",sep =" ")
+      title(Title)
+
+    }, bg.border = NA) #end of circos.track
+
+    dev.off()
+  } # close for loop
+} #close scale loop
+
+```
+
+# Sensitivity Analysis
+
+```{r Sensitivity_Area_Treshold, eval = T, echo = F}
+
+# Model Index
+MI <- 100 # Model Index
+
+####_____End Select Tresholds_______ ###
+
+Area_Index_Level <- seq(.1,0.5,0.1)
+
+p <- list()
+i = NULL
+
+for(i in 1:length(Area_Index_Level)){
+
+  data <- Clean_Results_Trans %>% 
+    filter(
+      Area_Index >= Area_Index_Level[i],
+      Area_Index <= 1-Area_Index_Level[i],
+      Model_Index == MI
+    ) %>% 
+    group_by(Territory) %>% 
+    summarise(
+      n_trans_spp = length(unique(TaxonKey)),
+      n_Neighbours = length(unique(Neighbour)),
+      Trans_Rate = n_trans_spp/n_Neighbours
+    )
+
+  Median_data <- median(data$n_trans_spp)
+  print(Median_data)
+
+  p[[i]] <- ggplot(data) +
+    geom_histogram(aes(n_trans_spp),
+                   binwidth = 10, 
+                   colour = "white"
+    ) +
+    labs(
+      x = "Transboundary species (n)",
+      y = "Frequency of EEZs",
+      title= paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")
+    ) +
+    # ggtitle(paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")) +
+    ggtheme_plot()
+
+}
+
+ggsave(
+    plot = do.call(gridExtra::grid.arrange,p),
+    width = 8,
+    height = 8,
+    units = "in",
+    filename = "Area_Tresholds.png",
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Sensitivity_Analysis"
+  )
+
+```
+
+#Problem solving
+
+### First world Anchovies
+
+In a first run the model suggests anchovies "Engraulis ringens" (600004) is transboundary between US-Mex-Can. I'm exploring this since all four models agree...
+
+Found the probelm, Gab's coordinate system, hecne the data, are in different system than DBEM and SAU data...
+
+```{r Trans_Spp_Function, eval= F ,echo = T,warning = F,message = F}
+
+### DATA EXTRA NEEDED
+
+# DBEM Coordinate system
+Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
+colnames(Coor) <- c("INDEX","Longitude","Latitude")
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>% 
+  mutate(INDEX = seq(1,259200,1))
+
+# colnames(CoorG) <- c("INDEX","Longitude","Latitude")
+coords <- CoorG[order(CoorG$Latitude, rev(CoorG$Longitude),decreasing=TRUE), ]
+
+# Explore model step by step
+
+# Get Catch Data
+Anchoveta_Dist <- GetSppDist(600004,"All",CoorG)
+
+Anchoveta_Dist_Coor <- Anchoveta_Dist %>% 
+  left_join(CoorG)
+
+# Swap coordinate system to match DBEM and SAU
+Anchoveta_Dist_Coor_Fix <- Anchoveta_Dist_Coor[order(Anchoveta_Dist_Coor$Latitude, rev(Anchoveta_Dist_Coor$Longitude),decreasing=TRUE), ]
+
+x <- Anchoveta_Dist %>% 
+  left_join(EEZ_CellID) %>% 
+  left_join(EEZIDs_List) %>% 
+  filter(
+    # Model == "Occ",
+    Value >0)
+
+# head(x)
+# Exploring using Vicky's data
+
+ggplot(x) +
+  geom_tile(aes(
+    x = Longitude,
+    y = Latitude,
+    fill = Name,
+    color = Name
+  )
+  ) +
+  facet_wrap(~Model)
+
+Spp_Trans <- bind_rows(
+    mclapply(
+      600004, FUN =EstTransIndex, Model = "All", Neighbours = Neighbour_List, Coord = CoorG
+    )
+  )
+
+  # Estimate total spp distribution within neighbours
+
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Neighbours$INDEX) %>% # Filter data only located within EEZs
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
+    group_by(TaxonKey,
+             INDEX
+    ) %>%
+    summarise(Model_Index = mean(Value,na.rm=T)) %>%
+    filter(Model_Index > 0) %>%
+    mutate(Model_Index = Model_Index*100) %>%
+    left_join(Neighbours,
+              by = "INDEX")
+
+    Test <- Trans_Spp %>% 
+      filter(Name == "USA (West Coast)" & Model_Index ==100)
+
+ # Explore only SAU catch data
+
+# Get Catch Data
+Anchoveta_Dist <- GetSppDist(Spp,"SAU_C")
+
+# Get Mex, Can and USA W coast Grid
+Anchoveta_Dist_EEZ <- Anchoveta_Dist %>%
+
+Anchoveta_NA <-  Anchoveta_Dist%>% 
+  filter(INDEX %in% North_America$INDEX) %>% 
+  gather("Year","Tonnes",CATCH.1:CATCH.65) %>% 
+  group_by(Year) %>% 
+  summarise(Sum_T = sum(Tonnes, na.rm =T))
+
+```
+
+### Overcounting transboundary stocks
+
+In a first run, Australia results in many transboundary stocks, I believe this is because it is counting the number of countries that that the species share (e.g.
+one species 6 countries = 6 transboundary spp) rather than 1 speces 6 countries = 1 trans spp.
+
+**Problem fixed.** Now we can estimate the number of transboundary species as well as the number of countries/regions that each country shares per species.
+
+```{Australia_case, eval =F, echo = F}
+
+Australia <- Results_Data %>% 
+  filter(Name == "Australia")
+
+Original_Australia <-Australia %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
+         ) %>% 
+  group_by(Name,Model_Index) %>% 
+  summarise(n_Trans_Spp = n()) %>% 
+  filter(Model_Index == 100)
+
+## Testing the waters
+
+Explore_Australia <- Australia %>% 
+  filter(Model_Index >= 50#,
+         # Trans_Index >= 0.10
+         ) %>% 
+  slice(1:20) %>% 
+  group_by(Name,Model_Index) %>% 
+  summarise(
+    n_trans = length(unique(TaxonKey)),
+    n_countries = length(unique(Neighbour_Territory)),
+    )
+
+```
+
+### Fixing counts within EEZs
+
+In the first run. Countries where EEZs are devided but touching (e.g. South Africa inidan and atlantic coasts) are double counted.
+
+This might be fixed with Tayler's data of EEZs to ISOs... He did it manually so it does not work!
+
+```{South_Africa_case, eval =F, echo = F}
+
+# Tyler E.'s' data
+EEZ_ISO <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/EEZID_ISO_TylEd.csv", comment.char="#")
+
+#SAU / Vicky's data
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+# Worlds adata
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/World_EEZ_v10_2018",sep="")
+# #The File
+fnam_world <- "eez_v10.shp"
+# #Load it!
+# 
+World_EEZs <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world))
+
+head(World_EEZs)
+
+World_EEZs %>% 
+  filter(
+    # Territory1 == "South Africa",
+    ISO_Ter1 == "ZAF") %>% 
+  head()
+
+# Get ISO and territory names from world map
+ISO_Ter <- World_EEZs %>%
+  select(ISO_Ter1,Territory1) %>% 
+  as.data.frame() %>% 
+  select(ISO_Ter1,Territory1)
+
+head(ISO_Ter)
+
+# I think EEZID equals ISO when not devided...
+
+EZZID_Yes_ISO <- ISO_Ter %>% 
+  semi_join(ISO_Ter,
+            by ="ISO_Ter1") %>% 
+  rename(Name = Territory1) %>% 
+  # head() %>% 
+  left_join(EEZIDs_List,
+            by = "Name")
+
+EEZ_ISO_Clean <- ISO_Ter %>% 
+  left_join(EEZ_ISO,
+            by = "ISO_Ter1")
+
+SA <- Results_Data %>% 
+  filter(stringr::str_detect(Name,"South Africa"))
+
+## Creating a subset dataset so i can work on my laptop and not remoteley
+
+SubsetData <- Clean_Results %>% 
+  filter(Country_Territory=="USA (East Coast)")
+
+write.csv(SubsetData,
+          "SubsetData.csv",
+          row.names = F) # Using USA East coast and Gulf as example
+
+###_____________________________ ###
+
+# Loading subsetted data
+
+Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/SubsetData.csv")
+
+sau_eez_fes <- read.csv("~/GitHub/FishForVisa/Temporal_Data/sau_eez_fes.csv")
+
+Neighbourd_Territory_T <- Clean_Results %>% 
+  group_by(eez_name=Neighbour_Territory) %>% 
+  summarise() %>%
+  left_join(sau_eez_fes,
+            by = "eez_name") %>% 
+  select(Neighbour_Territory= eez_name,
+         NT_fishing_entity=fishing_entity
+         )
+
+Country_Territory_T <- Clean_Results %>% 
+  group_by(eez_name=Country_Territory) %>% 
+  summarise() %>%
+  left_join(sau_eez_fes,
+            by = "eez_name")  %>% 
+  select(Country_Territory= eez_name,
+         CT_fishing_entity=fishing_entity)
+
+Non_duplicate_Data <- Clean_Results %>%   
+  left_join(Neighbourd_Territory_T,
+              by ="Neighbour_Territory") %>% 
+  left_join(Country_Territory_T,
+              by ="Country_Territory") %>% 
+  mutate(
+    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
+  ) %>% 
+  filter(Same_Nation == "No")
+
+# FIXED!!!!!
+
+```
+
+- **Done debugging**
+
+### Missing stocks
+
+There are places like Peru-Chile or Alaska-Canada that should have trans spp... In Alaska the issue is that Alaska doesn't actually exist as a separate shapefile...
+
+```{r Missing_stocks, eval =F}
+
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
+
+Clean_sau_eez_fes <- sau_eez_fes %>% 
+  gather("Type","FishingRegion",2,4) %>% 
+  left_join(sau_eez_fes,
+            by = ("fishing_entity_id")
+            ) %>% 
+  group_by(FishingRegion,fishing_entity) %>% 
+  summarise(n())
+
+# The Alaska paradox
+# It's a problem of the NAs, fixed.
+
+USA_West <- Results_Data %>% 
+  filter(Country_Territory == "USA (West Coast)") %>% 
+  left_join(Exploited_Species,
+            by = "TaxonKey")
+
+# Northern sea Russia
+Russia_map <- World_EEZs %>% 
+  filter(stringr::str_detect(Name,"Russia")) %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 100)
+
+head(Russia_map)
+
+ggplot(Russia_map) +
+  geom_sf(aes(fill = Name)) 
+# Shapefiles not matching
+# Russia (Laptev to Chukchi Sea)
+# Russia (Kara Sea)
+
+Russian_Regions <- c("Russia (Laptev to Chukchi Sea)","Russia (Kara Sea)")
+
+Russia_Results <- Results_Data %>% 
+  filter(stringr::str_detect(Country_Territory,"Russia"))
+
+unique(Russia_Results$Country_Territory)
+# Missing Laptev to Chukchi sea
+
+### What about Vicky's data
+#SAU / Vicky's data
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+
+Russia_EEZlist <- EEZIDs_List %>% 
+  filter(stringr::str_detect(Name,"Russia"))
+
+unique(Russia_EEZlist$Name)
+
+### So maybe there are no Neighbours?
+Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/Neighbour_List.csv", sep =""))
+
+Russia_Neighbour <- Neighbour_List %>% 
+  filter(stringr::str_detect(Name,"Russia"))
+
+unique(Russia_Neighbour$Country_Territory)
+
+# OK So Kara Sea has no borders outside Russia, hence white. Now Laptev does have borders but No species... which is weird... Paific Halibut?
+
+# I manually ran the function to see what's going on
+
+# ggplot() +
+#   geom_sf(data = Russia_map, aes(colour = Name)) +
+#   geom_tile(data = subset(SppDist, Value !=0),
+#             aes(
+#     x = Longitude,
+#     y = Latitude,
+#     fill = log10(Value)
+#   ) 
+#   ) +
+#   facet_wrap(~Model)
+
+# The main issue is that there is no catch data there...
+
+```
+
+### Pierrs massive discrete stocks
+
+```{r Pierrs_Discretion, eval = F ,echo = T,warning = F,message = F}
+
+Pierre <-  Clean_Results_Trans %>% 
+  filter(Territory == "Saint Pierre & Miquelon (France)") %>% 
+  left_join(Exploited_Species,
+            by = "TaxonKey")
+
+# Very wrong!
+# using 600051 to see what's the problem with the Area index
+
+# Found the problem, Territory and Neighbour were switched un the last step of the EstTransSpp function
+
+```
+
+### Côte de Ivory missing data
+
+For some reason Côte de ivory is missing data. It was fixed at the begining when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to cero.
+
+```{Cote_Deivory, eval =F, echo =F}
+
+# It might be a problem in the name côte de'ivory....
+# Nope, both INDEX and neighbours datasets are names alike
+
+# Run getSppDistribution function with this:
+Model="All"
+Coord=CoorG
+
+# Spp <- 600423 #This species should work
+
+# Its a problem with compabillity between Windows and MAC. Fixed by changing the neighbours csv. to excell
+
+# Now Check Vietnam...Curacao and Réunion...
+# In INDEXES "Vietnam" in all others "Viet Nam"
+# Fixed directly on the excell
+
+# The russioan probelmo
+
+# Load neighbours data from previouse routine
+Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.xlsx", sep =""))
+
+EEZCellIUD913 <- EEZ_CellID %>% 
+  filter(EEZID == 913)
+
+R912 <- Neighbours_Data %>% 
+  filter(ID == 912)
+
+R913 <- Neighbours_Data %>% 
+  filter(ID == 913)
+
+anti_join(R912,R913)
+
+Index_Code913 <- Index_Code %>% 
+  filter(EEZID == 913)
+
+Neighbours_Data %>% 
+  filter(INDEX %in% Index_Code913$INDEX)
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+# EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+# EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+# The path
+path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+# #The File
+
+fnam_world <- "SAUEEZ_July2015.shp"
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(Territory = Name)
+
+x <- Neighbours_Data %>%
+  select(-Neighbour) %>% 
+  group_by(Territory) %>% 
+  distinct() %>% 
+  anti_join(Index_Code) %>% 
+  group_by(Territory) %>% 
+  summarise(n());x
+
+# World_sf %>% 
+#   filter(Territory %in% x$Territory)
+
+# Fuck it! Re-run Neighbours code...
+
+Russians <- c("Russia (Laptev to Chukchi Sea)", #913
+              "US Virgin Islands") #912
+
+SF_Names <- 850
+
+Russian_Index <- Index_Code %>% 
+  filter(Territory %in% Russians)
+
+unique(Russian_Index$EEZID)
+unique(Russian_Index$Territory)
+
+World_sf %>% 
+  # filter(Territory == "Russia (Laptev to Chukchi Sea)") # EEZid 912
+  # filter(Territory == "Russia (Kara Sea)") # EEZid also 912
+  filter(Territory %in% Russians) %>% 
+  ggplot() +
+  geom_sf(aes(fill = Territory))
+
+unique(Russian_sf$Territory)
+
+# split shapefile by DF
+ Russian_id <- World_sf %>% 
+  filter(Territory %in% Russians) %>% 
+  left_join(Russian_Index, by= "Territory") %>%  
+  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
+  filter(EEZID == 913) %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 1000)
+
+ ggplot(Russian_id) +
+   geom_sf(aes())
+
+ # ok!
+
+# split shapefile by DF
+Russia_id_912_913 <- World_sf %>% 
+  filter(Territory %in% Russians) %>% 
+  left_join(Russian_Index, by= "Territory") %>%  
+  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
+  as.data.frame() %>% 
+  ungroup() %>% 
+  select(Territory,INDEX,EEZID)
+
+write.csv(Russia_id_912_913,
+         "Russia_id_912_913.csv",
+         row.names = F)
+
+head(x)
+
+```
+
+# Extra Analysis
+## Extra Analysis; Functions
+
+```{r Trans_Spp_Function_All, eval = F ,echo = T,warning = F,message = F}
+
+# Function to determine whether or not a species is transboundary for each model
+
+# Varibales needed
+# Spp: Species to be analized, data with presence/absence per gridcell
+# Index_EEZ: Reference list of all INDEX that fall within EEZs
+# EEZ_Size: Number of grid-cells that each EEZ has
+# Neighbours: Reference list of neighbouring countries
+
+# Needs getSppDist
+
+#### For testing 
+# Spp <- 600059
+# Model <- "All"
+# Neighbours <- Neighbour_List
+# Coord = CoorG
+# __________________________________
+
+# The function
+EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
+
+  # Get model data from spps
+  SppDist <- GetSppDist(Spp,Model,Coord)
+
+  # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
+           Model != "SAU_C") %>% # Only using observational and modelled data
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%
+    left_join(EEZ_CellID,
+              by = "INDEX") %>% 
+    left_join(EEZIDs_List,
+              by = "EEZID")
+
+  # MODEL INDEX (TRESHOLDS 1 & 2) #
+  Model_Index_D <- Trans_Spp %>% 
+    group_by(Name,
+             TaxonKey,
+             Model
+    ) %>% 
+    summarise(n_cells_spp = n()) %>% 
+    select(-n_cells_spp)
+
+    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
+   # The number of species' cells present within each country's EEZ
+
+  #Step 1.  Get EEZ id and Neighbour
+  Neighbours_EEZ <- Neighbours %>% 
+  group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
+  summarise(n=n()) %>% 
+  ungroup() %>% 
+  select(-n)
+
+  # Step 2. Determines the amount of grids present in each country
+  Spp_Grid <- Trans_Spp %>% 
+    group_by(TaxonKey,
+             Model, 
+             EEZID) %>% 
+    summarise(n_spp_eez = length(unique(INDEX))) %>% 
+    left_join(Neighbours_EEZ,
+              by = "EEZID") %>% 
+    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
+           Neighbour_Territory %in% Trans_Spp$Name)
+
+  # Step 3. Sum total grids per Neighbours
+
+  # Split dataframes to merge latter
+  Country_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index, # Un-comment after producing models x datasets
+      TaxonKey,Name=Country_Territory,n_spp_eez
+    )
+
+  Neighbour_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index,
+      TaxonKey,n_spp_eez,Name=Neighbour_Territory, Country_Territory
+    )
+
+  # Merge dataframes to get totals per Neighbourds
+  Area_Index_D <- full_join(Country_Territory_T,
+                           Neighbour_Territory_T, by = c("Name","TaxonKey","Model")) %>%
+    rowwise() %>%
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
+    distinct() %>% # Removes false duplicates from `full_join()`
+    rename(Neighbour_Territory = Name,
+           n_spp_Country = n_spp_eez.x,
+           n_spp_Neighbour = n_spp_eez.y) %>% 
+    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
+    select(1:4,6,8)
+
+  #____________ FINAL INDEX TABLE_________ #
+  Indexes <- Model_Index_D %>% 
+  rename(Country_Territory = Name) %>% 
+  full_join(Area_Index_D,
+            by = c("TaxonKey","Country_Territory","Model")
+  ) %>% 
+    filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
+    select(Model,TaxonKey,Country_Territory,Neighbour_Territory,everything())
+
+  ### Save spp dataframe
+
+  if(nrow(Indexes) > 0 & Save == "Y"){
+
+    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
+    Save_Path <- paste(Results_Path,"All_Models/",File_Name,sep="")
+
+    write.csv(Indexes,
+              Save_Path,
+              row.names = F)
+
+  }
+
+  if(nrow(Indexes) == 0 & Save == "Y"){
+
+# Reads dataset of Non transboundary species
+    Non_Transboundary_Data <- fread(paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep=""))
+
+    # Get current Spp that is not transboundary 
+    Current_Spp <- tibble(Non_trans = Spp)
+
+    # Combine new spp with others
+    New_Non <- Non_Transboundary_Data %>% 
+      bind_rows(Current_Spp)
+
+    # Set a name for file and saves data
+    New_Non_Name <- paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep="")
+    write.csv(New_Non, New_Non_Name, row.names = F)
+
+  }
+
+  ### Function return
+
+  EstTransIndex=Indexes # A dataframe with
+
+}
+
+### Testing Function ####
+# Spp <- 600006
+# Model <- "All"
+# Neighbours <- Neighbour_List
+# 
+# Tryout <- EstTransIndex(Spp,Model,Neighbours,CoorG,Save="N")
+# 
+# Over_20 <-Tryout %>% 
+#     filter(Area_Index > 0.20,
+#            Area_Index < 0.80)
+
+# Spp <- NULL
+# Model <- NULL
+
+```
+
+## Extra Analysis; Results
+
+### Maps for each model/dataset
+```{Tran_country_Map_All, eval =F, echo =F}
+
+World_EEZs_simple <- World_EEZs %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(TenTwenyfive, by ="Name") #%>%
+  # filter(!is.na(n_trans)) #%>%
+  # st_transform(crs = 3832)
+
+# head(World_EEZs_simple)
+# World_EEZs_simple %>% 
+#   filter(Name == "Chile")
+
+pal <- wes_palette("Zissou1", 100, type = "continuous")
+
+Mod <- unique(TenTwenyfive$Model)
+
+# Loop through all variables
+for(v in 1:length(Mod)){
+
+  Model_List <- Mod[v]
+
+  plot <- ggplot(data = subset(World_EEZs_simple,Model %in% Model_List)) +
+    geom_sf(aes(fill = n_trans)) +
+    scale_fill_gradientn(colours = pal,
+                         na.value = "white") +
+    ggtheme_map() +
+    ggtitle(paste(Model_List))
+
+  # Name plot
+  Plot_Name <- paste(Model_List,"plot.png",sep="_")
+
+  # Save plot
+  ggsave(
+    plot = plot,
+    width = 14,
+    height = 10,
+    units = "in",
+    filename = Plot_Name,
+    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
+  )
+
+  }
+
+```
+
+```{r Continent_PNG, eval =F }
+
+names(UN_Regions)
+# Load Land shapefile
+path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
+# #The File
+fnam_world_land <- "ne_50m_admin_0_countries.shp"
+
+World_land_sf <- st_read(dsn = path_world_land,
+                         layer =file_path_sans_ext(fnam_world_land)) %>% 
+  st_transform(crs = 4326)
+
+head(World_land_sf)
+
+Regions <- unique(World_land_sf$REGION_UN)
+# r= 1
+
+for(r in 1:length(Regions)){
+
+  Oceania <- World_land_sf %>%
+    st_transform(crs = 3832)
+
+  Oceania %>% 
+    filter(REGION_UN %in% Regions[5]) %>% 
+    ggplot() +
+    geom_sf(aes(),fill="black",colour = "black") +
+    ggtheme_map() #+
+    # coord_sf(xlim = c(-180, 90), ylim = c(-90, 90), expand = FALSE)
+
+  Plot_Name <-paste(Regions[5],".png",sep="")
+
+  ggsave(Plot_Name,
+       plot = last_plot(),
+       width = 4,
+       height = 4,
+       units = "in",
+       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Images_Data/"
+)
+
+}
+
+```
+
+# Old code
+```{r OLD_funEstNeighbours, eval = F, echo=T}
+# Determine which countries are Neighbours
+
+# Method adopted from Adrew Heiss
+# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32
+
+EstNeighbours <- function(Shapefile){
+
+  # Get the list using the poly2nb function
+
+  Neighbour_List <- poly2nb(Shapefile)
+
+  # Convert te nb data to a Matrix of crossing references
+  Neighbour_Matrix <- nb2mat(Neighbour_List,
+                            style="B", 
+                            zero.policy=TRUE)
+
+  # Rename the matrix axis
+  colnames(Neighbour_Matrix) <- rownames(Neighbour_Matrix)
+
+  # Get the names of the countries for identifying them
+  Country_Names <- tibble(id = row.names(Shapefile@data),
+                              Country_Territory = as.character(Shapefile@data$Name),
+                              Neighbour_Territory = Country_Territory,
+                              EEZID = Shapefile@data$EEZID # specific of SAU sf
+                              )
+
+  # Clean up and transform the Neighbour matrix
+  Neighbours <- as.data.frame(Neighbour_Matrix) %>%
+    mutate(country = row.names(.)) %>%  # Convert row names to actual column
+    gather(Neighbour, present, -country) %>%  # Convert to long
+    filter(present == 1) %>%  # Only look at cells with a match
+    # Add country names
+    left_join(select(Country_Names,
+                     -Neighbour_Territory), by=c("country" = "id")) %>%
+    left_join(select(Country_Names, 
+                     -Country_Territory), by=c("Neighbour" = "id")) %>% 
+    select(EEZID = EEZID.x,Country_Territory,Neighbour_Territory) # select final column
+
+    # Merge them with SAU data
+
+  DBEM_Neighbours_Data <- EEZIDs_List %>% 
+  left_join(EEZ_CellID, 
+            by = "EEZID") %>% # Asign EEZ id to each country
+  left_join(Neighbours, 
+            by = "EEZID") %>% # Include all Neighbouring countries 
+  filter(Neighbour_Territory != "NA") %>% 
+  left_join(Coor,
+            by = "INDEX") # Inclu
+
+  return(DBEM_Neighbours_Data)
+
+}
+
+### Test function
+
+# Subset data for testing function
+# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
+
+# Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
+# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
+
+# Running function
+# getNeighbours(Test)
+
+#### Works beautifully!
+
+```
+
+```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
+
+# Function to determine whether or not a species is transboundary
+
+# Varibales needed
+# Spp: Species to be analized, data with presence/absence per gridcell
+# Index_EEZ: Reference list of all INDEX that fall within EEZs
+# EEZ_Size: Number of grid-cells that each EEZ has
+# Neighbours: Reference list of neighbouring countries
+
+# Needs getSppDist
+
+#### For testing 
+# Spp <- 600059
+ #Model <- "All"
+ #Neighbours <- Neighbour_List
+ #Coord = CoorG
+# __________________________________
+
+# The function
+EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
+
+  # Get model data from spps
+  SppDist <- GetSppDist(Spp,Model,Coord)
+
+  # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
+  Trans_Spp <- SppDist %>%
+    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
+           Model != "SAU_C") %>% # Only using observational and modelled data
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
+    filter(Value > 0) %>%
+    group_by(TaxonKey,
+             INDEX
+    ) %>%
+    summarise(Model_Index = mean(Value,na.rm=T)
+    ) %>%
+    filter(Model_Index > 0) %>%
+    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
+    left_join(SppDist,
+              by = c("TaxonKey","INDEX")) %>%
+    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
+           Value > 0) %>%
+    mutate(Model_Index = Model_Index*100) %>%
+    select(-Model, -Value, -Latitude,-Longitude) %>%
+    left_join(EEZ_CellID,
+              by = "INDEX") %>% 
+    left_join(EEZIDs_List,
+              by = "EEZID")
+
+  # MODEL INDEX (TRESHOLDS 1 & 2) #
+  Model_Index_D <- Trans_Spp %>% 
+    group_by(Name,
+             TaxonKey,
+             Model_Index
+    ) %>% 
+    summarise(n_cells_spp = n()) %>% 
+    select(-n_cells_spp)
+
+  #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
+  # The number of species' cells present within each country's EEZ
+
+  #Step 1.  Get EEZ id and Neighbour
+  Neighbours_EEZ <- Neighbours %>% 
+    group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
+    summarise(n=n()) %>% 
+    ungroup() %>% 
+    select(-n)
+
+  # Step 2. Determines the amount of grids present in each country
+  Spp_Grid <- Trans_Spp %>% 
+    group_by(TaxonKey,
+             Model_Index, # Un-comment after producing models x datasets
+             EEZID) %>% 
+    summarise(n_spp_eez = length(unique(INDEX))) %>% 
+    left_join(Neighbours_EEZ,
+              by = "EEZID") %>% 
+    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
+           Neighbour_Territory %in% Trans_Spp$Name)
+
+  # Step 3. Sum total grids per Neighbours
+
+  # Split dataframes to merge latter
+  Country_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index, # Un-comment after producing models x datasets
+      TaxonKey,
+      Name=Country_Territory,
+      n_spp_eez
+    )
+
+  Neighbour_Territory_T <- Spp_Grid %>% 
+    ungroup() %>% 
+    select(
+      Model_Index,
+      TaxonKey,n_spp_eez,
+      Name=Neighbour_Territory, 
+      Country_Territory
+    )
+
+  # Merge dataframes to get totals per Neighbourds
+  Area_Index_D <- full_join(Country_Territory_T,
+                            Neighbour_Territory_T, 
+                            by = c("Model_Index","Name","TaxonKey")
+  ) %>%
+    rowwise() %>%
+    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
+    distinct() %>% # Removes false duplicates from `full_join()`
+    rename(Neighbour_Territory = Name,
+           n_spp_Country = n_spp_eez.x,
+           n_spp_Neighbour = n_spp_eez.y) %>% 
+    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
+    select(1:3,6,8)
+
+  #____________ FINAL INDEX TABLE_________ #
+  Indexes <- Model_Index_D %>% 
+    rename(Country_Territory = Name) %>% 
+    full_join(Area_Index_D,
+              by = c("TaxonKey","Country_Territory","Model_Index")
+    ) %>% 
+    filter(!is.na(Area_Index),
+           !is.na(Model_Index) # Uncomment after producing Models x datasets
+    )%>%  # Remove cases where the country does not pass the area_index and viceversa
+    select(TaxonKey,Country_Territory,Neighbour_Territory,everything())
+
+  ### Save spp dataframe
+
+  if(nrow(Indexes) > 0 & Save == "Y"){
+
+    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
+    Save_Path <- paste(Results_Path,File_Name,sep="")
+
+    write.csv(Indexes,
+              Save_Path,
+              row.names = F)
+
+  }
+
+  if(nrow(Indexes) == 0 & Save == "Y"){
+
+    # Reads dataset of Non transboundary species
+    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+
+    # Get current Spp that is not transboundary 
+    Current_Spp <- tibble(TaxonKey = Spp)
+
+    # Combine new spp with others
+    New_Non <- Non_Transboundary_Data %>% 
+      bind_rows(Current_Spp)
+
+    # Set a name for file and saves data
+    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
+    write.csv(New_Non, New_Non_Name, row.names = F)
+
+  }
+
+  ### Function return
+
+  EstTransIndex=Indexes # A dataframe with
+
+}
+```
+
+```{habitat_barplot, eval =F, echo =F}
+
+Species_data <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
+  mutate(Distance = ifelse(DemersPelag == "reef-associated", 1,
+                           ifelse(DemersPelag =="pelagic-neritic",2,
+                                  ifelse(DemersPelag == "demersal",3,
+                                         ifelse(DemersPelag == "pelagic-oceanic",4,
+                                                ifelse(DemersPelag =="benthopelagic",5,
+                                                       ifelse(DemersPelag =="bathypelagic",6,
+                                                              ifelse(DemersPelag =="bathydemersal",7,
+                                                                     8)))))))
+  ) %>% 
+  group_by(DemersPelag,Distance) %>% 
+  summarise(Countries_Genus = sum(n_countries,na.rm=T),
+            Mean_Countries_Genus = mean(n_countries,na.rm=T),
+            sd_Countries_Genus = sd(n_countries,na.rm=T),
+            N_spp =length(unique(TaxonName))
+  )
+
+ggplot(Species_data,
+       aes(
+         x = reorder(DemersPelag,desc(Distance)),
+         y = Mean_Countries_Genus,
+         fill = Countries_Genus#,
+         # colour = Countries_Genus
+       )
+) +
+  geom_bar(stat = "identity") +
+  # geom_errorbar(data = Species_data,
+  #               aes(
+  #                 x = reorder(DemersPelag,desc(Distance)),
+  #                 ymin=Mean_Countries_Genus-sd_Countries_Genus, # mean +- 2*sd
+  #                 ymax=Mean_Countries_Genus+sd_Countries_Genus
+  #               ),
+  #               colour = "black",
+  #               width=.2,
+  #               linetype = 2,
+  #               size = 0.6,
+  #               alpha = 0.5
+  # ) +
+  geom_text(data = Species_data, 
+            aes(
+              x = reorder(DemersPelag,desc(Distance)),
+              y = 2,
+              label = paste(as.character(N_spp), "species"),
+            ),
+            colour = "black"
+  ) +
+  coord_flip() +
+  scale_fill_gradientn("Total number\nof countries",
+                       colours = wes_palette("Zissou1"),
+                       limits = c(0,1500),
+                       breaks = seq(0,1500,250)
+  ) +
+  scale_colour_gradientn("Total number\nof countries",
+                         colours = wes_palette("Zissou1"),
+                         limits = c(0,1500),
+                         breaks = seq(0,1500,250)
+  ) +
+  scale_y_continuous(breaks=seq(0, 40, 5), 
+                     limits=c(0, 40)
+                     )+
+  labs(
+    x = "Habitat type",
+    y = "Mean number of countries per habitat"
+  ) +
+  ggtheme_plot()
 
@@
 
-ggsave(
-    plot = last_plot(),
-    width = 12,
-    height = 12,
-    units = "in",
-    filename = "Territory_circular_both.png",
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-  )
+# ggsave(
+#     plot = last_plot(),
+#     width = 12,
+#     height = 12,
+#     units = "in",
+#     filename = "Territory_circular_both.png",
+#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+#   )
 
 ```
-
-```{r Top_country_Circle_Diagram, eval =F, echo = F}
-
-# Top 10 species
-
-# Number of countries shared by each Species
-Top_10_Countries <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No"
-         ) %>% 
-  group_by(Country_Territory) %>% 
-  summarise(
-    n_countries = length(unique(TaxonKey))
-  ) %>% 
-  top_n(10,n_countries)
-
-# Countries that share the top 10
-Top_Ten_Countries <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No",
-         Country_Territory %in% Top_10_Countries$Country_Territory
-         ) %>% 
-  group_by(from=CT_fishing_entity,
-           to=NT_fishing_entity
-           ) %>% 
-  summarise(value=n()
-            ) %>% 
-  ungroup() %>% 
-  mutate(from = paste("F", from),
-         to = paste("T", to)
-         )
-
-####________________###
-# Circulize package ####
-# https://jokergoo.github.io/circlize_book/book/
-####________________###
-
-# To set links collor 
-Bins <- as.numeric(cut(Top_Ten_Countries$value,breaks = 5))
-
-# Basic plot
-circos.clear()
-chordDiagram(Top_Ten_Countries, 
-             annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
-             annotationTrackHeight = c(0.001, 0.05), # set links close to the axis
-             directional = 1, # direction of arrows
-             direction.type = c("diffHeight", "arrows"), # use arrows
-             grid.col = "white",
-             col = ifelse(Bins == 1,"#046C9A", # deep blue
-                          ifelse(Bins == 2,"#78B7C5", #light blue
-                                 ifelse(Bins == 3,"#EBCC2A", #yellow
-                                        ifelse(Bins == 4, "#E1AF00", #cream
-                                               "#F21A00")))), #red
-             link.arr.col = wes_palette("Zissou1"),
-             link.arr.type = "big.arrow",# make links big arrows
-             diffHeight = uh(1, "mm"), # brings the arrow to the bottom of the source
-             # annotationTrack = "grid", # no labels
-             scale = FALSE, # fraction of total instead of absolute value
-             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Top_Ten_Countries))))) # I have no idea but helps with the labels
-    ) 
-#  Rest of eddits
-circos.track(track.index = 1, panel.fun = function(x, y) {
-    xlim = get.cell.meta.data("xlim")
-    xplot = get.cell.meta.data("xplot")
-    ylim = get.cell.meta.data("ylim")
-    sector.name = get.cell.meta.data("sector.index")
-
-    circos.text(mean(xlim),
-                ylim[1], 
-                sector.name, 
-                facing = "clockwise",
-                niceFacing = TRUE,
-                adj = c(-0.2, 0.5),
-                col = "black")
-
-}, bg.border = NA)
-
-```
-
-## Analysis per Species
-
-```{r n_species_country, eval = T, echo =F}
-
-# Number of countries shared by each Species
-Species_Trans <- Tresholded_T_Data %>% 
-  group_by(TaxonKey) %>% 
-  summarise(
-    n_countries = length(unique(Territory))
-  ) %>% 
-  left_join(Exploited_Species) %>%
-  left_join(Spp_Clasification)
-
-# hist(Species_Trans$n_countries)
-
-# Use rfishbase to get species environment
-
-Species_list <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>% 
-  pull(scientific_name)
-
-Species_environ_list <- rbind(species(Species_list, 
-                                      fields = species_fields$habitat[4])
-) %>% 
-  mutate(scientific_name = Species_list)
-
-```
-
-```{habitat_barplot, eval =F, echo =F}
-
-Species_data <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
-  mutate(Distance = ifelse(DemersPelag == "reef-associated", 1,
-                           ifelse(DemersPelag =="pelagic-neritic",2,
-                                  ifelse(DemersPelag == "demersal",3,
-                                         ifelse(DemersPelag == "pelagic-oceanic",4,
-                                                ifelse(DemersPelag =="benthopelagic",5,
-                                                       ifelse(DemersPelag =="bathypelagic",6,
-                                                              ifelse(DemersPelag =="bathydemersal",7,
-                                                                     8)))))))
-  ) %>% 
-  group_by(DemersPelag,Distance) %>% 
-  summarise(Countries_Genus = sum(n_countries,na.rm=T),
-            Mean_Countries_Genus = mean(n_countries,na.rm=T),
-            sd_Countries_Genus = sd(n_countries,na.rm=T),
-            N_spp =length(unique(TaxonName))
-  )
-
-ggplot(Species_data,
-       aes(
-         x = reorder(DemersPelag,desc(Distance)),
-         y = Mean_Countries_Genus,
-         fill = Countries_Genus#,
-         # colour = Countries_Genus
-       )
-) +
-  geom_bar(stat = "identity") +
-  # geom_errorbar(data = Species_data,
-  #               aes(
-  #                 x = reorder(DemersPelag,desc(Distance)),
-  #                 ymin=Mean_Countries_Genus-sd_Countries_Genus, # mean +- 2*sd
-  #                 ymax=Mean_Countries_Genus+sd_Countries_Genus
-  #               ),
-  #               colour = "black",
-  #               width=.2,
-  #               linetype = 2,
-  #               size = 0.6,
-  #               alpha = 0.5
-  # ) +
-  geom_text(data = Species_data, 
-            aes(
-              x = reorder(DemersPelag,desc(Distance)),
-              y = 2,
-              label = paste(as.character(N_spp), "species"),
-            ),
-            colour = "black"
-  ) +
-  coord_flip() +
-  scale_fill_gradientn("Total number\nof countries",
-                       colours = wes_palette("Zissou1"),
-                       limits = c(0,1500),
-                       breaks = seq(0,1500,250)
-  ) +
-  scale_colour_gradientn("Total number\nof countries",
-                         colours = wes_palette("Zissou1"),
-                         limits = c(0,1500),
-                         breaks = seq(0,1500,250)
-  ) +
-  scale_y_continuous(breaks=seq(0, 40, 5), 
-                     limits=c(0, 40)
-                     )+
-  labs(
-    x = "Habitat type",
-    y = "Mean number of countries per habitat"
-  ) +
-  ggtheme_plot()
-
-```
-
-### OHI-inspired Circular plot Species
-
-```{r species_circluar_plot, eval = T, echo = T}
-
-Species_Data <- Tresholded_T_Data %>% 
-  group_by(TaxonKey) %>% 
-  summarise(n_trans_spp = length(unique(Territory))) %>% 
-  left_join(Exploited_Species) %>%
-  rename(scientific_name = TaxonName) %>% 
-  left_join(Species_environ_list) %>%
-  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
-         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
-  select(individual=scientific_name,
-         value = n_trans_spp,
-         group = DemersPelag) %>% 
-  arrange(group,value) %>% 
-  filter(value > 20) # remove all species under 10 (way too many to plot!)
-
-Median_trans <- median(Species_Data$value)
-# hist(Species_Data$value)
-# unique(Species_Data$group)
-
-Char <- as.factor(Species_Data$group)
-
-# Set a number of 'empty bar' to add at the end of each group
-empty_bar <- 8
-to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
-colnames(to_add) <- colnames(Species_Data)
-to_add$group <- rep(levels(Char), each=empty_bar)
-Species_Data <- rbind(Species_Data, to_add)
-Species_Data <- Species_Data %>% arrange(group,value)
-Species_Data$id <- seq(1, nrow(Species_Data))
-
-# Get the name and the y position of each label
-
-# Create labels for all but top 5
-label_data <- Countries_Data 
-number_of_bar <- nrow(label_data)
-angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
-label_data$hjust <- ifelse( angle < -90, 1, 0)
-label_data$angle <- ifelse(angle < -90, angle+180, angle)
-
-# Get the name and the y position of each label
-# Top n of each group label
-Top_spp <- Species_Data %>% 
-  group_by(group) %>% 
-  top_n(5,value)
-
-# Create labels for all but top 5
-label_data <- Species_Data
-number_of_bar <- nrow(label_data)
-angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
-label_data$hjust <- ifelse( angle < -90, 1, 0)
-label_data$angle <- ifelse(angle < -90, angle+180, angle)
-
-# Remove top 5
-label_data_rest <- label_data %>% 
-  filter(!individual %in% Top_spp$individual)
-
-# Create labels for top 5
-Top_label_data <- label_data %>% 
-  filter(individual %in% Top_spp$individual)
-
-# prepare a data frame for base lines
-base_data <- Species_Data %>% 
-  group_by(group) %>% 
-  summarize(start=min(id), 
-            end=max(id) - empty_bar, 
-            median = median(value, na.rm = T)
-            ) %>% 
-  rowwise() %>% 
-  mutate(title=mean(c(start, end)))
-
-# prepare a data frame for grid (scales)
-grid_data <- base_data
-grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
-grid_data$start <- grid_data$start - 1
-# grid_data <- grid_data[-1,]
-grid_data[1,2] <- 5 # Manually include bathydemerssal
-grid_data[1,3] <- 1
-
-# Median data
-median_data <- grid_data %>% 
-  mutate_at(vars(start,end),
-            .funs = as.numeric)
-
-Seq_axis_spp <- seq(20,100,20)
-Plot_Limit <- max(Species_Data$value,na.rm=T)
-
-# Make the plot
-ggplot(Species_Data, 
-       aes(x=as.factor(id), 
-           y=value,
-           fill=group)
-       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
-  geom_bar(aes(x=as.factor(id),
-               y=value,
-               fill=group),
-           stat="identity",
-           alpha=0.5) +
-  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  # Add median lines for each gropup
-  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
-               alpha=1, size=0.5 , inherit.aes = FALSE ) +
-  # Add text showing the value of each line
-  annotate("text", 
-           x = rep(max(Species_Data$id),5),
-           y = Seq_axis_spp,
-           label = c(Seq_axis_spp[-5],">100"),
-           color=Ticks_Color, 
-           size=3 , 
-           angle=0, 
-           fontface="bold",
-           hjust=1) +
-  geom_bar(aes(x=as.factor(id),
-               y=value,
-               fill=group),
-           stat="identity",
-           alpha=0.5) +
-  geom_text(data=label_data_rest,
-            aes(x=id, y=101,
-                label=individual,
-                hjust=hjust), 
-            color="black",
-            fontface="italic",
-            alpha=1,
-            size=2.5,
-            angle= label_data_rest$angle,
-            inherit.aes = FALSE) +
-  # Bold top 3 
-  geom_text(data=Top_label_data,
-            aes(x=id, y=101,
-                label=individual,
-                hjust=hjust), 
-            color="black",
-            fontface="bold.italic",
-            alpha=1,
-            size=2.5,
-            angle= Top_label_data$angle,
-            inherit.aes = FALSE) +
-  # Add base line information
-  geom_segment(data=base_data, 
-               aes(x = start, 
-                   y = -5, 
-                   xend = end, 
-                   yend = -5
-                   ), 
-               colour = "black",
-               alpha=0.8, 
-               size=0.6 , 
-               inherit.aes = FALSE) +
-  ylim(-100,110) + # sets the circle the first value the central the last value how wide
-  theme_minimal() +
-  theme(
-    legend.position = c(0.5,0.5),
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() + 
-  scale_fill_manual("Ecosystem Preference",
-                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                               wes_palette(n = 4, name = "GrandBudapest2")
-                    ),
-                    na.value = "white"
-  ) +
-  scale_colour_manual("Ecosystem Preference",
-                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                                 wes_palette(n = 4, name = "GrandBudapest2")
-                      ),
-                      na.value = "white"
-  )
-# 
-ggsave(
-    plot = last_plot(),
-    width = 12,
-    height = 12,
-    units = "in",
-    filename = "Species_circular_over20.png",
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-  )
-
-```
-
-### Species status (SAU methods)
-
-Note that (n), the number of ‘stocks’ is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area is at least 1000 tonnes.
-
- 1) The first and last reported landings are at least ten years apart;
-
-2) There are at least five years of consecutive catches; and
-
-3) The catch in a particular area (LME) is at least 1,000 tonnes.
-
-Once those tresholds are met, the status of the species is determined as follows:
-
-- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
-- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
-- Exploited	Landing > 50% of max. landing
-- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
-- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
-
-*Notes* = 3 years average mean
-
-```{r Species_Status, eval = T, echo =F}
-
-CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
-  mutate(INDEX = seq(1,259200,1))
-
-# SAU relations between INDEX and Country's EEZs
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-Index_Code <- EEZIDs_List %>% 
-  left_join(EEZ_CellID) %>% 
-  rename(Territory = Name)
-
-Spp <- GetSppDist(600004, Model = "SAU_C", Coord = CoorG)
-
-Data <- Spp %>% 
-  gather("Year","Value",CATCH.1:CATCH.65) %>% 
-  arrange(INDEX) %>% 
-  mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
-  left_join(Index_Code) %>% 
-  filter(!is.na(EEZID),
-         Value > 0) %>% 
-  group_by(Species,Year,EEZID,Territory) %>% # Total catch per country
-  summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
-  group_by(Species,Territory,EEZID,Year) %>% 
-  mutate(RMean = rollmean(x = Total_Catch, 5, align = "right", fill = Total_Catch)) %>% 
-  group_by(Species,Territory,EEZID)
-
-# head(Data)
-
-# Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
- Tresholds <- Data %>% 
-  arrange(Territory) %>% 
-  group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
-            Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
-            Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
-            ) %>% 
-   gather("Step","Treshold",Years_appart:Catch_over) %>% 
-   filter(Treshold == "Yes")
-
- # Evaluate stocks
-
- # Filter data that does not satisfy tresholds
-
- Landings_Peaks <- Data %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Max_Peak = max(RMean,na.rm=T))
-
- Eval_Data <- Data %>% 
-  semi_join(Tresholds,
-            by = c("Species","Territory")) %>% 
-   left_join(Landings_Peaks,
-             by = c("Species","Territory"))
-
- Peak_Year <- Eval_Data %>% 
-   filter(RMean == Max_Peak) %>% 
-   select(Species,Territory,EEZID,Y_Max_Peak = Year)
-
- Post_Max_Min <- Eval_Data %>% 
-   left_join(Peak_Year) %>% 
-   filter(Year > Y_Max_Peak) %>% 
-   group_by(Species,Territory,EEZID) %>% 
-   summarise(Post_Max_Min = min(RMean,na.rm=T))
-
- Y_Post_Max_Min <- Eval_Data %>% 
-   left_join(Post_Max_Min) %>% 
-   filter(RMean == Post_Max_Min) %>% 
-   select(Species,Territory,EEZID,Y_Post_Max_Min = Year)
-
- Data_Status <- Eval_Data %>% 
-   left_join(Peak_Year,
-             by = c("Species","Territory","EEZID")) %>%
-   left_join(Post_Max_Min,
-             by = c("Species","Territory","EEZID")) %>% 
-   left_join(Y_Post_Max_Min,
-             by = c("Species","Territory","EEZID")) %>% 
-   rename(Y_RMean = Year) %>% 
-   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
-                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
-                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                      "No Status")
-                                        )
-                                 )
-                          )
-   )
-   ) %>% 
-   filter(Y_RMean > 2004) %>% 
-   group_by(Species,EEZID,Territory,Status) %>% 
-   summarise(n_Status= n()) %>% 
-   group_by(Species,EEZID,Territory) %>% 
-   top_n(1,n_Status)
-
- # Manual estimation
-
- data.frame(
-   Y_RMean = 1980,
-   RMean = 642187,
-   Max_Peak = 1298712,
-   Y_Max_Peak = 1990,
-   Post_Max_Min = 681967,
-   Y_Post_Max_Min = 2010,
-   Y_RMean = 2014
- ) %>% 
-   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
-                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))," Over Exploited",
-                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                      "NA")
-                                        )
-                                 )
-                          )
-   )
-   )
-
-```
-
-```{r Top_spp_Circle_Diagram, eval =F, echo = F}
-
-# Top 5 shared species per marine environment (number of countries sharing the species)
-Top_Species <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
-  # group_by(TaxonKey,TaxonName,CommonName,DemersPelag) %>% 
-  # summarise(Sum_Countries =sum(n_countries,na.rm=T)) %>% 
-  group_by(DemersPelag) %>% 
-  top_n(5,n_countries)
-
-# Countries that share the top 10
-Top_Spp_Countries <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index < Min_AI |
-      Area_Index > Max_AI,
-    Model_Index == MI,
-    Same_Nation == "No",
-    TaxonKey %in% Top_Species$TaxonKey
-  ) %>% 
-  left_join(Species_Trans) %>% 
-  rename(scientific_name =TaxonName) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(from = paste(Genus,"\n",Species,sep=""),
-         DemersPelag = replace_na(DemersPelag, "Other")) %>%
-  group_by(
-    # from,
-    from = scientific_name,
-           to=CT_fishing_entity,
-           DemersPelag
-  ) %>% 
-  summarise(value=n()
-  ) #%>%
-  # filter(DemersPelag == "demersal") %>%
-  # select(-DemersPelag)
-
-####________________###
-# Circulize package ####
-# https://jokergoo.github.io/circlize_book/book/
-####________________###
-
-# To set links color 
-Bins <- as.numeric(cut(Top_Spp_Countries$value,breaks = 5)) # By size of sharing
-
-# To get country's flags... https://flagpedia.net/download
-flags <- c(paste("Temporal_Data/flags-mini/",list.files("Temporal_Data/flags-mini/"),sep=""))
-
-# List of Ecosystems
-Classification <- Top_Species %>% group_by(DemersPelag) %>% summarise(n()) %>%  pull(DemersPelag)
-
-####________________ PLOT PER ECOSYSTEM _____________________ ###
-
-for(s in 1:2){ # sclae loop
-  for(i in 1:length(Classification)) {
-    # for(i in 1:2) { # for testing
-
-    # Set scales to plott both absolut and proportional values
-    if(s == 1){
-      Scales <- "TRUE"
-    }else{
-      Scales <- "FALSE"
-    }
-
-    # Saving the plot
-    Plot_name <- paste(Figures_Path,Classification[i],Scales,".tiff",sep="")
-    tiff(Plot_name, width = 5, height = 5, units = 'in', res = 500)
-
-    # Subsetting the data for each plot
-    DemersPelag_i <- Classification[i]
-
-    Data <- Top_Ten_Spp_Countries %>% 
-      filter(DemersPelag %in% DemersPelag_i) %>% 
-      select(-3)
-
-    # Use to set links' colors to each species
-    Speceis_cols <- Data %>% group_by(from) %>% summarise(n()) %>% pull(from)
-
-    # The base plot
-    circos.clear()
-    chordDiagram(Data, 
-                 annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
-                 annotationTrackHeight = c(0.001, 0.1), # set links close to the axis
-                 directional = 1, # direction of arrows
-                 direction.type = c("diffHeight", "arrows"), # use arrows
-                 grid.col = "grey",
-                 # if col == Bins then colors will change depending of value
-                 # col = ifelse(Bins == 1,"#046C9A", # deep blue
-                 #              ifelse(Bins == 2,"#78B7C5", #light blue
-                 #                     ifelse(Bins == 3,"#EBCC2A", #yellow
-                 #                            ifelse(Bins == 4, "#E1AF00", #cream
-                 #                                   "#F21A00")))), #red
-                 # if col == Species_cols then colors will change depending of species
-                 col = ifelse(Data$from == Speceis_cols[1],"#FF0000", # deep blue
-                              ifelse(Data$from == Speceis_cols[2],"#00A08A", #light blue
-                                     ifelse(Data$from == Speceis_cols[3],"#F2AD00", #yellow
-                                            ifelse(Data$from == Speceis_cols[4], "#F98400", #cream
-                                                   "#5BBCD6")))), #red
-                 # link.arr.col = wes_palette("Zissou1"), 
-                 link.arr.type = "big.arrow",# make links big arrows
-                 diffHeight = uh(-0.5, "mm"), # brings the arrow to the bottom of the source
-                 scale = Scales, # fraction of each species to total share of each country instead of absolute value
-                 preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Data))))) # I have no idea but helps with the labels
-    )
-
-    #  Function to inlcude other layers
-    circos.track(track.index = 1, panel.fun = function(x, y) {
-      xlim = get.cell.meta.data("xlim")
-      xplot = get.cell.meta.data("xplot")
-      ylim = get.cell.meta.data("ylim")
-      sector.name = get.cell.meta.data("sector.index")
-
-      # Add labels
-      circos.text(mean(xlim),
-                  ylim[1],
-                  sector.name,
-                  facing = "clockwise",
-                  niceFacing = TRUE,
-                  adj = c(-0.2, 0.5),
-                  col = "black",
-                  cex = 0.6) # size of labels
-
-      # Add country's flags instead of names (still need to link names to falgs)
-
-      # library(EBImage)
-      # pos = circlize:::polar2Cartesian(circlize(CELL_META$xcenter, CELL_META$ycenter))
-      # image = EBImage::readImage(flags[CELL_META$sector.numeric.index])
-      # 
-      # rasterImage(image,
-      #             xleft = pos[1, 1] - 0.006, 
-      #             ybottom = pos[1, 2] - 0.005,
-      #             xright = pos[1, 1] + 0.05,
-      #             ytop = pos[1, 2]+ 0.04
-      #             )
-
-      # END FLAGS TRYOUT
-
-      # Set plot Title
-      Title <- paste("Top",Classification[i], "Species",sep =" ")
-      title(Title)
-
-    }, bg.border = NA) #end of circos.track
-
-    dev.off()
-  } # close for loop
-} #close scale loop
-
-```
-
-# Sensitivity Analysis
-
-```{r Sensitivity_Area_Treshold, eval = T, echo = F}
-
-# Model Index
-MI <- 100 # Model Index
-
-####_____End Select Tresholds_______ ###
-
-Area_Index_Level <- seq(.1,0.5,0.1)
-
-p <- list()
-i = NULL
-
-for(i in 1:length(Area_Index_Level)){
-
-  data <- Clean_Results_Trans %>% 
-    filter(
-      Area_Index >= Area_Index_Level[i],
-      Area_Index <= 1-Area_Index_Level[i],
-      Model_Index == MI
-    ) %>% 
-    group_by(Territory) %>% 
-    summarise(
-      n_trans_spp = length(unique(TaxonKey)),
-      n_Neighbours = length(unique(Neighbour)),
-      Trans_Rate = n_trans_spp/n_Neighbours
-    )
-
-  Median_data <- median(data$n_trans_spp)
-  print(Median_data)
-
-  p[[i]] <- ggplot(data) +
-    geom_histogram(aes(n_trans_spp),
-                   binwidth = 10, 
-                   colour = "white"
-    ) +
-    labs(
-      x = "Transboundary species (n)",
-      y = "Frequency of EEZs",
-      title= paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")
-    ) +
-    # ggtitle(paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")) +
-    ggtheme_plot()
-
-}
-
-ggsave(
-    plot = do.call(gridExtra::grid.arrange,p),
-    width = 8,
-    height = 8,
-    units = "in",
-    filename = "Area_Tresholds.png",
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Sensitivity_Analysis"
-  )
-
-```
-
-#Problem solving
-
-### First world Anchovies
-
-In a first run the model suggests anchovies "Engraulis ringens" (600004) is transboundary between US-Mex-Can. I'm exploring this since all four models agree...
-
-Found the probelm, Gab's coordinate system, hecne the data, are in different system than DBEM and SAU data...
-
-```{r Trans_Spp_Function, eval= F ,echo = T,warning = F,message = F}
-
-### DATA EXTRA NEEDED
-
-# DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>% 
-  mutate(INDEX = seq(1,259200,1))
-
-# colnames(CoorG) <- c("INDEX","Longitude","Latitude")
-coords <- CoorG[order(CoorG$Latitude, rev(CoorG$Longitude),decreasing=TRUE), ]
-
-# Explore model step by step
-
-# Get Catch Data
-Anchoveta_Dist <- GetSppDist(600004,"All",CoorG)
-
-Anchoveta_Dist_Coor <- Anchoveta_Dist %>% 
-  left_join(CoorG)
-
-# Swap coordinate system to match DBEM and SAU
-Anchoveta_Dist_Coor_Fix <- Anchoveta_Dist_Coor[order(Anchoveta_Dist_Coor$Latitude, rev(Anchoveta_Dist_Coor$Longitude),decreasing=TRUE), ]
-
-x <- Anchoveta_Dist %>% 
-  left_join(EEZ_CellID) %>% 
-  left_join(EEZIDs_List) %>% 
-  filter(
-    # Model == "Occ",
-    Value >0)
-
-# head(x)
-# Exploring using Vicky's data
-
-ggplot(x) +
-  geom_tile(aes(
-    x = Longitude,
-    y = Latitude,
-    fill = Name,
-    color = Name
-  )
-  ) +
-  facet_wrap(~Model)
-
-Spp_Trans <- bind_rows(
-    mclapply(
-      600004, FUN =EstTransIndex, Model = "All", Neighbours = Neighbour_List, Coord = CoorG
-    )
-  )
-
-  # Estimate total spp distribution within neighbours
-
-  Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbours$INDEX) %>% # Filter data only located within EEZs
-    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
-    group_by(TaxonKey,
-             INDEX
-    ) %>%
-    summarise(Model_Index = mean(Value,na.rm=T)) %>%
-    filter(Model_Index > 0) %>%
-    mutate(Model_Index = Model_Index*100) %>%
-    left_join(Neighbours,
-              by = "INDEX")
-
-    Test <- Trans_Spp %>% 
-      filter(Name == "USA (West Coast)" & Model_Index ==100)
-
- # Explore only SAU catch data
-
-# Get Catch Data
-Anchoveta_Dist <- GetSppDist(Spp,"SAU_C")
-
-# Get Mex, Can and USA W coast Grid
-Anchoveta_Dist_EEZ <- Anchoveta_Dist %>%
-
-Anchoveta_NA <-  Anchoveta_Dist%>% 
-  filter(INDEX %in% North_America$INDEX) %>% 
-  gather("Year","Tonnes",CATCH.1:CATCH.65) %>% 
-  group_by(Year) %>% 
-  summarise(Sum_T = sum(Tonnes, na.rm =T))
-
-```
-
-### Overcounting transboundary stocks
-
-In a first run, Australia results in many transboundary stocks, I believe this is because it is counting the number of countries that that the species share (e.g.
-one species 6 countries = 6 transboundary spp) rather than 1 speces 6 countries = 1 trans spp.
-
-**Problem fixed.** Now we can estimate the number of transboundary species as well as the number of countries/regions that each country shares per species.
-
-```{Australia_case, eval =F, echo = F}
-
-Australia <- Results_Data %>% 
-  filter(Name == "Australia")
-
-Original_Australia <-Australia %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
-         ) %>% 
-  group_by(Name,Model_Index) %>% 
-  summarise(n_Trans_Spp = n()) %>% 
-  filter(Model_Index == 100)
-
-## Testing the waters
-
-Explore_Australia <- Australia %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
-         ) %>% 
-  slice(1:20) %>% 
-  group_by(Name,Model_Index) %>% 
-  summarise(
-    n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbour_Territory)),
-    )
-
-```
-
-### Fixing counts within EEZs
-
-In the first run. Countries where EEZs are devided but touching (e.g. South Africa inidan and atlantic coasts) are double counted.
-
-This might be fixed with Tayler's data of EEZs to ISOs... He did it manually so it does not work!
-
-```{South_Africa_case, eval =F, echo = F}
-
-# Tyler E.'s' data
-EEZ_ISO <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/EEZID_ISO_TylEd.csv", comment.char="#")
-
-#SAU / Vicky's data
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# Worlds adata
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/World_EEZ_v10_2018",sep="")
-# #The File
-fnam_world <- "eez_v10.shp"
-# #Load it!
-# 
-World_EEZs <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-
-head(World_EEZs)
-
-World_EEZs %>% 
-  filter(
-    # Territory1 == "South Africa",
-    ISO_Ter1 == "ZAF") %>% 
-  head()
-
-# Get ISO and territory names from world map
-ISO_Ter <- World_EEZs %>%
-  select(ISO_Ter1,Territory1) %>% 
-  as.data.frame() %>% 
-  select(ISO_Ter1,Territory1)
-
-head(ISO_Ter)
-
-# I think EEZID equals ISO when not devided...
-
-EZZID_Yes_ISO <- ISO_Ter %>% 
-  semi_join(ISO_Ter,
-            by ="ISO_Ter1") %>% 
-  rename(Name = Territory1) %>% 
-  # head() %>% 
-  left_join(EEZIDs_List,
-            by = "Name")
-
-EEZ_ISO_Clean <- ISO_Ter %>% 
-  left_join(EEZ_ISO,
-            by = "ISO_Ter1")
-
-SA <- Results_Data %>% 
-  filter(stringr::str_detect(Name,"South Africa"))
-
-## Creating a subset dataset so i can work on my laptop and not remoteley
-
-SubsetData <- Clean_Results %>% 
-  filter(Country_Territory=="USA (East Coast)")
-
-write.csv(SubsetData,
-          "SubsetData.csv",
-          row.names = F) # Using USA East coast and Gulf as example
-
-###_____________________________ ###
-
-# Loading subsetted data
-
-Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/SubsetData.csv")
-
-sau_eez_fes <- read.csv("~/GitHub/FishForVisa/Temporal_Data/sau_eez_fes.csv")
-
-Neighbourd_Territory_T <- Clean_Results %>% 
-  group_by(eez_name=Neighbour_Territory) %>% 
-  summarise() %>%
-  left_join(sau_eez_fes,
-            by = "eez_name") %>% 
-  select(Neighbour_Territory= eez_name,
-         NT_fishing_entity=fishing_entity
-         )
-
-Country_Territory_T <- Clean_Results %>% 
-  group_by(eez_name=Country_Territory) %>% 
-  summarise() %>%
-  left_join(sau_eez_fes,
-            by = "eez_name")  %>% 
-  select(Country_Territory= eez_name,
-         CT_fishing_entity=fishing_entity)
-
-Non_duplicate_Data <- Clean_Results %>%   
-  left_join(Neighbourd_Territory_T,
-              by ="Neighbour_Territory") %>% 
-  left_join(Country_Territory_T,
-              by ="Country_Territory") %>% 
-  mutate(
-    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
-  ) %>% 
-  filter(Same_Nation == "No")
-
-# FIXED!!!!!
-
-```
-
-- **Done debugging**
-
-### Missing stocks
-
-There are places like Peru-Chile or Alaska-Canada that should have trans spp... In Alaska the issue is that Alaska doesn't actually exist as a separate shapefile...
-
-```{r Missing_stocks, eval =F}
-
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
-
-Clean_sau_eez_fes <- sau_eez_fes %>% 
-  gather("Type","FishingRegion",2,4) %>% 
-  left_join(sau_eez_fes,
-            by = ("fishing_entity_id")
-            ) %>% 
-  group_by(FishingRegion,fishing_entity) %>% 
-  summarise(n())
-
-# The Alaska paradox
-# It's a problem of the NAs, fixed.
-
-USA_West <- Results_Data %>% 
-  filter(Country_Territory == "USA (West Coast)") %>% 
-  left_join(Exploited_Species,
-            by = "TaxonKey")
-
-# Northern sea Russia
-Russia_map <- World_EEZs %>% 
-  filter(stringr::str_detect(Name,"Russia")) %>% 
-  st_simplify(preserveTopology = TRUE, dTolerance = 100)
-
-head(Russia_map)
-
-ggplot(Russia_map) +
-  geom_sf(aes(fill = Name)) 
-# Shapefiles not matching
-# Russia (Laptev to Chukchi Sea)
-# Russia (Kara Sea)
-
-Russian_Regions <- c("Russia (Laptev to Chukchi Sea)","Russia (Kara Sea)")
-
-Russia_Results <- Results_Data %>% 
-  filter(stringr::str_detect(Country_Territory,"Russia"))
-
-unique(Russia_Results$Country_Territory)
-# Missing Laptev to Chukchi sea
-
-### What about Vicky's data
-#SAU / Vicky's data
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-
-Russia_EEZlist <- EEZIDs_List %>% 
-  filter(stringr::str_detect(Name,"Russia"))
-
-unique(Russia_EEZlist$Name)
-
-### So maybe there are no Neighbours?
-Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/Neighbour_List.csv", sep =""))
-
-Russia_Neighbour <- Neighbour_List %>% 
-  filter(stringr::str_detect(Name,"Russia"))
-
-unique(Russia_Neighbour$Country_Territory)
-
-# OK So Kara Sea has no borders outside Russia, hence white. Now Laptev does have borders but No species... which is weird... Paific Halibut?
-
-# I manually ran the function to see what's going on
-
-# ggplot() +
-#   geom_sf(data = Russia_map, aes(colour = Name)) +
-#   geom_tile(data = subset(SppDist, Value !=0),
-#             aes(
-#     x = Longitude,
-#     y = Latitude,
-#     fill = log10(Value)
-#   ) 
-#   ) +
-#   facet_wrap(~Model)
-
-# The main issue is that there is no catch data there...
-
-```
-
-### Pierrs massive discrete stocks
-
-```{r Pierrs_Discretion, eval = F ,echo = T,warning = F,message = F}
-
-Pierre <-  Clean_Results_Trans %>% 
-  filter(Territory == "Saint Pierre & Miquelon (France)") %>% 
-  left_join(Exploited_Species,
-            by = "TaxonKey")
-
-# Very wrong!
-# using 600051 to see what's the problem with the Area index
-
-# Found the problem, Territory and Neighbour were switched un the last step of the EstTransSpp function
-
-```
-
-### Côte de Ivory missing data
-
-For some reason Côte de ivory is missing data. It was fixed at the begining when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to cero.
-
-```{Cote_Deivory, eval =F, echo =F}
-
-# It might be a problem in the name côte de'ivory....
-# Nope, both INDEX and neighbours datasets are names alike
-
-# Run getSppDistribution function with this:
-Model="All"
-Coord=CoorG
-
-# Spp <- 600423 #This species should work
-
-# Its a problem with compabillity between Windows and MAC. Fixed by changing the neighbours csv. to excell
-
-# Now Check Vietnam...Curacao and Réunion...
-# In INDEXES "Vietnam" in all others "Viet Nam"
-# Fixed directly on the excell
-
-# The russioan probelmo
-
-# Load neighbours data from previouse routine
-Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.xlsx", sep =""))
-
-EEZCellIUD913 <- EEZ_CellID %>% 
-  filter(EEZID == 913)
-
-R912 <- Neighbours_Data %>% 
-  filter(ID == 912)
-
-R913 <- Neighbours_Data %>% 
-  filter(ID == 913)
-
-anti_join(R912,R913)
-
-Index_Code913 <- Index_Code %>% 
-  filter(EEZID == 913)
-
-Neighbours_Data %>% 
-  filter(INDEX %in% Index_Code913$INDEX)
-
-# SAU relations between INDEX and Country's EEZs
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-# EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-# EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-Index_Code <- EEZIDs_List %>% 
-  left_join(EEZ_CellID) %>% 
-  rename(Territory = Name)
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-# #The File
-
-fnam_world <- "SAUEEZ_July2015.shp"
-World_sf <- st_read(dsn = path_world,
-                    layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(Territory = Name)
-
-x <- Neighbours_Data %>%
-  select(-Neighbour) %>% 
-  group_by(Territory) %>% 
-  distinct() %>% 
-  anti_join(Index_Code) %>% 
-  group_by(Territory) %>% 
-  summarise(n());x
-
-# World_sf %>% 
-#   filter(Territory %in% x$Territory)
-
-# Fuck it! Re-run Neighbours code...
-
-Russians <- c("Russia (Laptev to Chukchi Sea)", #913
-              "US Virgin Islands") #912
-
-SF_Names <- 850
-
-Russian_Index <- Index_Code %>% 
-  filter(Territory %in% Russians)
-
-unique(Russian_Index$EEZID)
-unique(Russian_Index$Territory)
-
-World_sf %>% 
-  # filter(Territory == "Russia (Laptev to Chukchi Sea)") # EEZid 912
-  # filter(Territory == "Russia (Kara Sea)") # EEZid also 912
-  filter(Territory %in% Russians) %>% 
-  ggplot() +
-  geom_sf(aes(fill = Territory))
-
-unique(Russian_sf$Territory)
-
-# split shapefile by DF
- Russian_id <- World_sf %>% 
-  filter(Territory %in% Russians) %>% 
-  left_join(Russian_Index, by= "Territory") %>%  
-  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
-  filter(EEZID == 913) %>% 
-  st_simplify(preserveTopology = TRUE, dTolerance = 1000)
-
- ggplot(Russian_id) +
-   geom_sf(aes())
-
- # ok!
-
-# split shapefile by DF
-Russia_id_912_913 <- World_sf %>% 
-  filter(Territory %in% Russians) %>% 
-  left_join(Russian_Index, by= "Territory") %>%  
-  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
-  as.data.frame() %>% 
-  ungroup() %>% 
-  select(Territory,INDEX,EEZID)
-
-write.csv(Russia_id_912_913,
-         "Russia_id_912_913.csv",
-         row.names = F)
-
-head(x)
-
-```
-
-# Extra Analysis
-## Extra Analysis; Functions
-
-```{r Trans_Spp_Function_All, eval = F ,echo = T,warning = F,message = F}
-
-# Function to determine whether or not a species is transboundary for each model
-
-# Varibales needed
-# Spp: Species to be analized, data with presence/absence per gridcell
-# Index_EEZ: Reference list of all INDEX that fall within EEZs
-# EEZ_Size: Number of grid-cells that each EEZ has
-# Neighbours: Reference list of neighbouring countries
-
-# Needs getSppDist
-
-#### For testing 
-# Spp <- 600059
-# Model <- "All"
-# Neighbours <- Neighbour_List
-# Coord = CoorG
-# __________________________________
-
-# The function
-EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
-
-  # Get model data from spps
-  SppDist <- GetSppDist(Spp,Model,Coord)
-
-  # Result 1. Number of Countries that share the species
-
-  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
-  Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
-           Model != "SAU_C") %>% # Only using observational and modelled data
-    mutate(Value = ifelse(Value > 0, 1,0)) %>%
-    left_join(EEZ_CellID,
-              by = "INDEX") %>% 
-    left_join(EEZIDs_List,
-              by = "EEZID")
-
-  # MODEL INDEX (TRESHOLDS 1 & 2) #
-  Model_Index_D <- Trans_Spp %>% 
-    group_by(Name,
-             TaxonKey,
-             Model
-    ) %>% 
-    summarise(n_cells_spp = n()) %>% 
-    select(-n_cells_spp)
-
-    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
-   # The number of species' cells present within each country's EEZ
-
-  #Step 1.  Get EEZ id and Neighbour
-  Neighbours_EEZ <- Neighbours %>% 
-  group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
-  summarise(n=n()) %>% 
-  ungroup() %>% 
-  select(-n)
-
-  # Step 2. Determines the amount of grids present in each country
-  Spp_Grid <- Trans_Spp %>% 
-    group_by(TaxonKey,
-             Model, 
-             EEZID) %>% 
-    summarise(n_spp_eez = length(unique(INDEX))) %>% 
-    left_join(Neighbours_EEZ,
-              by = "EEZID") %>% 
-    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
-           Neighbour_Territory %in% Trans_Spp$Name)
-
-  # Step 3. Sum total grids per Neighbours
-
-  # Split dataframes to merge latter
-  Country_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index, # Un-comment after producing models x datasets
-      TaxonKey,Name=Country_Territory,n_spp_eez
-    )
-
-  Neighbour_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index,
-      TaxonKey,n_spp_eez,Name=Neighbour_Territory, Country_Territory
-    )
-
-  # Merge dataframes to get totals per Neighbourds
-  Area_Index_D <- full_join(Country_Territory_T,
-                           Neighbour_Territory_T, by = c("Name","TaxonKey","Model")) %>%
-    rowwise() %>%
-    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
-    distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbour_Territory = Name,
-           n_spp_Country = n_spp_eez.x,
-           n_spp_Neighbour = n_spp_eez.y) %>% 
-    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
-    select(1:4,6,8)
-
-  #____________ FINAL INDEX TABLE_________ #
-  Indexes <- Model_Index_D %>% 
-  rename(Country_Territory = Name) %>% 
-  full_join(Area_Index_D,
-            by = c("TaxonKey","Country_Territory","Model")
-  ) %>% 
-    filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(Model,TaxonKey,Country_Territory,Neighbour_Territory,everything())
-
-  ### Save spp dataframe
-
-  if(nrow(Indexes) > 0 & Save == "Y"){
-
-    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
-    Save_Path <- paste(Results_Path,"All_Models/",File_Name,sep="")
-
-    write.csv(Indexes,
-              Save_Path,
-              row.names = F)
-
-  }
-
-  if(nrow(Indexes) == 0 & Save == "Y"){
-
-# Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep=""))
-
-    # Get current Spp that is not transboundary 
-    Current_Spp <- tibble(Non_trans = Spp)
-
-    # Combine new spp with others
-    New_Non <- Non_Transboundary_Data %>% 
-      bind_rows(Current_Spp)
-
-    # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep="")
-    write.csv(New_Non, New_Non_Name, row.names = F)
-
-  }
-
-  ### Function return
-
-  EstTransIndex=Indexes # A dataframe with
-
-}
-
-### Testing Function ####
-# Spp <- 600006
-# Model <- "All"
-# Neighbours <- Neighbour_List
-# 
-# Tryout <- EstTransIndex(Spp,Model,Neighbours,CoorG,Save="N")
-# 
-# Over_20 <-Tryout %>% 
-#     filter(Area_Index > 0.20,
-#            Area_Index < 0.80)
-
-# Spp <- NULL
-# Model <- NULL
-
-```
-
-## Extra Analysis; Results
-
-### Maps for each model/dataset
-```{Tran_country_Map_All, eval =F, echo =F}
-
-World_EEZs_simple <- World_EEZs %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(TenTwenyfive, by ="Name") #%>%
-  # filter(!is.na(n_trans)) #%>%
-  # st_transform(crs = 3832)
-
-# head(World_EEZs_simple)
-# World_EEZs_simple %>% 
-#   filter(Name == "Chile")
-
-pal <- wes_palette("Zissou1", 100, type = "continuous")
-
-Mod <- unique(TenTwenyfive$Model)
-
-# Loop through all variables
-for(v in 1:length(Mod)){
-
-  Model_List <- Mod[v]
-
-  plot <- ggplot(data = subset(World_EEZs_simple,Model %in% Model_List)) +
-    geom_sf(aes(fill = n_trans)) +
-    scale_fill_gradientn(colours = pal,
-                         na.value = "white") +
-    ggtheme_map() +
-    ggtitle(paste(Model_List))
-
-  # Name plot
-  Plot_Name <- paste(Model_List,"plot.png",sep="_")
-
-  # Save plot
-  ggsave(
-    plot = plot,
-    width = 14,
-    height = 10,
-    units = "in",
-    filename = Plot_Name,
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
-  )
-
-  }
-
-```
-
-```{r Continent_PNG, eval =F }
-
-names(UN_Regions)
-# Load Land shapefile
-path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
-# #The File
-fnam_world_land <- "ne_50m_admin_0_countries.shp"
-
-World_land_sf <- st_read(dsn = path_world_land,
-                         layer =file_path_sans_ext(fnam_world_land)) %>% 
-  st_transform(crs = 4326)
-
-head(World_land_sf)
-
-Regions <- unique(World_land_sf$REGION_UN)
-# r= 1
-
-for(r in 1:length(Regions)){
-
-  Oceania <- World_land_sf %>%
-    st_transform(crs = 3832)
-
-  Oceania %>% 
-    filter(REGION_UN %in% Regions[5]) %>% 
-    ggplot() +
-    geom_sf(aes(),fill="black",colour = "black") +
-    ggtheme_map() #+
-    # coord_sf(xlim = c(-180, 90), ylim = c(-90, 90), expand = FALSE)
-
-  Plot_Name <-paste(Regions[5],".png",sep="")
-
-  ggsave(Plot_Name,
-       plot = last_plot(),
-       width = 4,
-       height = 4,
-       units = "in",
-       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Images_Data/"
-)
-
-}
-
-```
-
-# Old code
-```{r OLD_funEstNeighbours, eval = F, echo=T}
-# Determine which countries are Neighbours
-
-# Method adopted from Adrew Heiss
-# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32
-
-EstNeighbours <- function(Shapefile){
-
-  # Get the list using the poly2nb function
-
-  Neighbour_List <- poly2nb(Shapefile)
-
-  # Convert te nb data to a Matrix of crossing references
-  Neighbour_Matrix <- nb2mat(Neighbour_List,
-                            style="B", 
-                            zero.policy=TRUE)
-
-  # Rename the matrix axis
-  colnames(Neighbour_Matrix) <- rownames(Neighbour_Matrix)
-
-  # Get the names of the countries for identifying them
-  Country_Names <- tibble(id = row.names(Shapefile@data),
-                              Country_Territory = as.character(Shapefile@data$Name),
-                              Neighbour_Territory = Country_Territory,
-                              EEZID = Shapefile@data$EEZID # specific of SAU sf
-                              )
-
-  # Clean up and transform the Neighbour matrix
-  Neighbours <- as.data.frame(Neighbour_Matrix) %>%
-    mutate(country = row.names(.)) %>%  # Convert row names to actual column
-    gather(Neighbour, present, -country) %>%  # Convert to long
-    filter(present == 1) %>%  # Only look at cells with a match
-    # Add country names
-    left_join(select(Country_Names,
-                     -Neighbour_Territory), by=c("country" = "id")) %>%
-    left_join(select(Country_Names, 
-                     -Country_Territory), by=c("Neighbour" = "id")) %>% 
-    select(EEZID = EEZID.x,Country_Territory,Neighbour_Territory) # select final column
-
-    # Merge them with SAU data
-
-  DBEM_Neighbours_Data <- EEZIDs_List %>% 
-  left_join(EEZ_CellID, 
-            by = "EEZID") %>% # Asign EEZ id to each country
-  left_join(Neighbours, 
-            by = "EEZID") %>% # Include all Neighbouring countries 
-  filter(Neighbour_Territory != "NA") %>% 
-  left_join(Coor,
-            by = "INDEX") # Inclu
-
-  return(DBEM_Neighbours_Data)
-
-}
-
-### Test function
-
-# Subset data for testing function
-# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
-
-# Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
-# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
-
-# Running function
-# getNeighbours(Test)
-
-#### Works beautifully!
-
-```
-
-```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
-
-# Function to determine whether or not a species is transboundary
-
-# Varibales needed
-# Spp: Species to be analized, data with presence/absence per gridcell
-# Index_EEZ: Reference list of all INDEX that fall within EEZs
-# EEZ_Size: Number of grid-cells that each EEZ has
-# Neighbours: Reference list of neighbouring countries
-
-# Needs getSppDist
-
-#### For testing 
-# Spp <- 600059
- #Model <- "All"
- #Neighbours <- Neighbour_List
- #Coord = CoorG
-# __________________________________
-
-# The function
-EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
-
-  # Get model data from spps
-  SppDist <- GetSppDist(Spp,Model,Coord)
-
-  # Result 1. Number of Countries that share the species
-
-  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
-  Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
-           Model != "SAU_C") %>% # Only using observational and modelled data
-    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
-    filter(Value > 0) %>%
-    group_by(TaxonKey,
-             INDEX
-    ) %>%
-    summarise(Model_Index = mean(Value,na.rm=T)
-    ) %>%
-    filter(Model_Index > 0) %>%
-    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
-    left_join(SppDist,
-              by = c("TaxonKey","INDEX")) %>%
-    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
-           Value > 0) %>%
-    mutate(Model_Index = Model_Index*100) %>%
-    select(-Model, -Value, -Latitude,-Longitude) %>%
-    left_join(EEZ_CellID,
-              by = "INDEX") %>% 
-    left_join(EEZIDs_List,
-              by = "EEZID")
-
-  # MODEL INDEX (TRESHOLDS 1 & 2) #
-  Model_Index_D <- Trans_Spp %>% 
-    group_by(Name,
-             TaxonKey,
-             Model_Index
-    ) %>% 
-    summarise(n_cells_spp = n()) %>% 
-    select(-n_cells_spp)
-
-  #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
-  # The number of species' cells present within each country's EEZ
-
-  #Step 1.  Get EEZ id and Neighbour
-  Neighbours_EEZ <- Neighbours %>% 
-    group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
-    summarise(n=n()) %>% 
-    ungroup() %>% 
-    select(-n)
-
-  # Step 2. Determines the amount of grids present in each country
-  Spp_Grid <- Trans_Spp %>% 
-    group_by(TaxonKey,
-             Model_Index, # Un-comment after producing models x datasets
-             EEZID) %>% 
-    summarise(n_spp_eez = length(unique(INDEX))) %>% 
-    left_join(Neighbours_EEZ,
-              by = "EEZID") %>% 
-    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
-           Neighbour_Territory %in% Trans_Spp$Name)
-
-  # Step 3. Sum total grids per Neighbours
-
-  # Split dataframes to merge latter
-  Country_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index, # Un-comment after producing models x datasets
-      TaxonKey,
-      Name=Country_Territory,
-      n_spp_eez
-    )
-
-  Neighbour_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index,
-      TaxonKey,n_spp_eez,
-      Name=Neighbour_Territory, 
-      Country_Territory
-    )
-
-  # Merge dataframes to get totals per Neighbourds
-  Area_Index_D <- full_join(Country_Territory_T,
-                            Neighbour_Territory_T, 
-                            by = c("Model_Index","Name","TaxonKey")
-  ) %>%
-    rowwise() %>%
-    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
-    distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbour_Territory = Name,
-           n_spp_Country = n_spp_eez.x,
-           n_spp_Neighbour = n_spp_eez.y) %>% 
-    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
-    select(1:3,6,8)
-
-  #____________ FINAL INDEX TABLE_________ #
-  Indexes <- Model_Index_D %>% 
-    rename(Country_Territory = Name) %>% 
-    full_join(Area_Index_D,
-              by = c("TaxonKey","Country_Territory","Model_Index")
-    ) %>% 
-    filter(!is.na(Area_Index),
-           !is.na(Model_Index) # Uncomment after producing Models x datasets
-    )%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(TaxonKey,Country_Territory,Neighbour_Territory,everything())
-
-  ### Save spp dataframe
-
-  if(nrow(Indexes) > 0 & Save == "Y"){
-
-    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
-    Save_Path <- paste(Results_Path,File_Name,sep="")
-
-    write.csv(Indexes,
-              Save_Path,
-              row.names = F)
-
-  }
-
-  if(nrow(Indexes) == 0 & Save == "Y"){
-
-    # Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
-
-    # Get current Spp that is not transboundary 
-    Current_Spp <- tibble(TaxonKey = Spp)
-
-    # Combine new spp with others
-    New_Non <- Non_Transboundary_Data %>% 
-      bind_rows(Current_Spp)
-
-    # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
-    write.csv(New_Non, New_Non_Name, row.names = F)
-
-  }
-
-  ### Function return
-
-  EstTransIndex=Indexes # A dataframe with
-
-}
-```

### 2019-10-23 Initial_Analysis.Rmd
Cleaned the script

@@
 1. Determine which countries have Neighbouring EEZs  
-  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify Neighbouring polygons,
-  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the Neighbouring data
+  1.1. For this we used the Sea Around Us EEZ map that discriminate by oceans and a routine (*Estimate Transboundary Species*) to identify Neighbouring polygons,
+  1.2. Then we match the SAU spatial information (e.g. INDEX within EEZ and coordinates) with the Neighbouring data
+
 2. Overlap distribution maps with Neighbours data  
-  2.1. For each species we merged the DBEM_Neighbours data with their known distribution (Gab's data)  
+  2.1. For each species we merged the Neighbours data with their known distribution (SAU distribution and catch,ESMs, and Observation)  
 3. Determine transboundary if:  
@@
 
-Alternatively, we could create a "confidence level" based on a ratio, i.e;
-- How many grid cells of both the EEZs is the species present on. A species that covers all cells would have 100% but a species that covers, lets say, all of EEZ1 but only half of EEZ2 would be 75%.  
-- Another option is to have the index based on the species distribution. That is to say, what proportion of the total species distribution actually falls within both EEZs....
-
-## Data
-
-### Determine species list
+We create two "confidence level" based on data and area covered, i.e;
+
+-
+-
+
+## Determine species list
+
+This part is to determine the list of species to be analized in the project.
+Initially this list was limited by the species data from the DBEM, however, as we are not using the DBEM, the limit is now the SAU.
 
@@
 
-## Estimating Neighbourds
-
-### Functions `EstNeighbours`
+## Determine Neighbourds
+
+This is the first step of the analysis and will determine what EEZs are neighbouring. THe routine creates a final dataset that we then use to estimate transboundary species.
+
+### Function `EstNeighbours`
 
@@
   }else{
-  # Merge them with SAU data
+
+  # Merge them with SAU data so we have the INDEX and lat long info
   suppressWarnings(
@@
     left_join(Coor,
-              by = "INDEX") %>%  # Inclu
+              by = "INDEX") %>%  # Include lat long
     rename(Country_Territory = Name)
@@
 
-```{r EEZ_Neighbourds_Control_Pannel, eval = F, echo = F}
-
-#### Load Data Needed ####
-
-# Spatial analysis for Countries boundaries from marine regions ####
-
-###_______________________________Read Me_____________________________________________#
-#### Data License and references ###
-# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
-# Flanders Marine Institute (2018).
-Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10.
-Available online at http://www.marineregions.org/.
-https://doi.org/10.14284/312
-
+```{r Neighbours_Control_Pannel, eval = F, echo = F}
+
+###___________________Read Me_____________________#
 #### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
-###________________________________________________________________________________#
+###_______________________________________________#
 
@@
 path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-# #The File
+
+# The File
 fnam_world <- "SAUEEZ_July2015.shp"
-# #Load it!
-# 
+
+# Load it!
 World_EEZs <- st_read(dsn = path_world,
@@
 
+```
+
+```{r Neighbours_Subroutine, eval = F, echo = T}
+
 # Run Function (Ran and saved May 27 2019 at 6pm)
@@
 
-####_________________________________________ TESTING PERIOD_________________________________________####
+####_________________________________________ TESTING PERIOD_________________________________________###
 # I'm substetting central america to do the whole analysis (smaller EEZs = faster computation) once I have figure out things I'll run for all
@@
 
+This sub routine determines the species exploitation status based on the SAU methodology.
+**Note:** For the current project we do not consider this method to determine the species exploitation status *per se*, but rather a catch trend that *could* indicate that a species is under/over/max exploited.
+
+In the original method the authors analyze stocks, while we analyze at the species level within each EEZ.
+Also (n), the number of species, is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area (LME) is at least 1000 tonnes.
+We removed the last one (LME) and computed all of the species that only followed the first two;
+
+1) The first and last reported landings are at least ten years apart;
+
+2) There are at least five years of consecutive catches
+
+Once those tresholds are met, the status of the species is determined as follows:
+
+- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
+- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
+- Exploited	Landing > 50% of max. landing
+- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
+- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
+
+*Notes* = 3 years average mean
+
 ### Function `EstSppStatus`
 
-```{r Species_Status_fun, eval = T, echo =F}
+This function estimates the exploitation status of a species based on catch data.
+
+```{r funEstSppStatus, eval = T, echo =F}
 
@@
 
+  # Load species' data
   Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
@@
            Value > 0) %>% 
-    group_by(TaxonKey=Species,Year,Territory) %>% # Total catch per country
+    group_by(TaxonKey=Species,Year,Territory) %>% # Estimates total catch per country
     summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
-    group_by(TaxonKey,Territory,Year) %>% 
+    group_by(TaxonKey,Territory,Year) %>% # Running mean as Pauly et la.
     mutate(RMean = rollmean(x = Total_Catch, 3,
@@
                             fill = Total_Catch)
-           ) %>% # Running mean
+    ) %>% 
     select(-Total_Catch) %>% 
@@
     summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
-              Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
-              Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
+              Consecutive = ifelse(max(grp) >= 5,"Yes","No")#, # Step 2. There are at least 5 consecutive catch years
+              # Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes. (CURRENTLY OFF)
     ) %>% 
@@
     ) %>% 
-      filter(Year > Y_Max_Peak) %>% 
+    filter(Year > Y_Max_Peak) %>% # Filter years after peak year
     group_by(TaxonKey,Territory) %>% 
-      top_n(-1,RMean) %>% 
+    top_n(-1,RMean) %>% # find min value
     rename(Post_Max_Min = RMean,
@@
     ) %>% 
-      # Final Evaluation 
+    # Final Species Status Evaluation 
     mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
@@
 
+  # Function Return
+
   # If both datasets have value RETURN BOTH
@@
 
-    # If only No status data, then just return that
+  # If only No status data, then just return No Status Data
   if(nrow(No_Status_Data) > 0 & nrow(Status_Data) == 0){
@@
   }
-
 }
@@
 
-```{r spp_status_data eval = T, echo = F}
+```{r Spp_Status_Control_Pannel, eval = T, echo = F}
 
@@
 
-```{r species_status_routine eval = T, echo = F}
+```{r Spp_Status_Sub_Routine, eval = T, echo = F}
 # Needs to have trans species 
@@
 
-# x <-Species_Status %>% 
-#   group_by(Territory,Status) %>% 
-#   summarise(n())
-
-write.csv(Species_Status,
-          paste(Data_Path,"Distribution_Data/Species_Status.csv",sep=""),
-                row.names = F)
+# Save data
+# write.csv(Species_Status,
+#           paste(Results_Path,"Species_Status.csv",sep=""),
+#                 row.names = F)
 
@@
 
-#### Function `GetSppDist`
-
-This function Read in species distribution from the observation data, ESM models and SAU data
+This is the main step of the project. In this segment we estimate the number of transboundary species existing today in each of the worlds EEZs.
+
+The datasets SAU_D, OCC, and ESM are used as sppecies presence while SAU_C is used as a confirmation of that.
+The `Model Index` is the first treshold and estimates the uncertanty of models.
+Goes from 0 - 1 as follows:
+
+- 1 or 0; All models agree that in the presence of the species
+- 0.75; Three out of four models agree on speices presence
+- 0.50; Two out of four models agree on speices presence
+- 0.25; Only one model flags a speices presence
+- 0; All models agree there is no species there
+
+The `Area_Index` is the second treshold and estimates the proportion of each species distribution in each EEZ.
+It only take into consideration the distribution of the species within the two EEZs, rather than the complete distribution.
+Hence, is mirrord (e.g.
+if EEZ#1 is 0.40, EEZ#2 is 0.6)
+
+** NOTE THAT THE FUNCTION IS SETTED TO OUTPUT RESULTS FOR ALL MODELS **
+
+### Function `GetSppDist`
+
+This function reads in species distribution from the observation data, ESM models and SAU data.
 
@@
 
-    }else{
-
-      # print(paste("No info for this species"))
     }
@@
 
-#### Function `EstTransIndex`
-
-##### NOTES:
-
-###### General:
-- For now using SAU_C as presence absence
-- Grouping by species distribution within EEZ and not EEZ area
-
-###### Tresholds:
-###### Model Index, line ~479
-
-This first treshold estimates the uncertanty of models. Goes from 0 - 1 as follows:
-
-- 1 or 0; All models agree that in the presence of the species
-- 0.75; Three out of four models agree on speices presence
-- 0.50; Two out of four models agree on speices presence
-- 0.25; Only one model flags a speices presence
-- 0; All models agree there is no species there
-
-** NOTE THAT THE FUNCTION IS SETTED TO OUTPUT RESULTS FOR LL MODELS **
-
-###### Distribution Index, line ~482
-
-```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
+### Function `EstTransIndex`
+
+This is the main function of the project, the one that actually estimates if a species is transboundary or not
+
+```{r funEstTransIndex, eval= T ,echo = T,warning = F,message = F}
 

### 2019-10-23 Initial_Analysis.Rmd
Fixed problem with Model_Index

@@
     ) %>%
-    summarise(Model_Index = mean(Value,na.rm=T)
-    ) %>%
-    filter(Model_Index > 0) %>%
+    summarise(Model_Index = sum(Value,na.rm=T)/3
+    ) %>%
+    filter(Model_Index > 0.4) %>% # at least 2 sources agree
     # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #

### 2019-10-23 Initial_Analysis.Rmd
Clean script

@@
 
-#### Function 'Mclapply_Hack'
+### Function `Mclapply_Hack`
+
+This function will hack the `mclappy()` function to work in PC and use multiple cores for the analysis. It was created by someone else and the original version is here: 
+https://www.r-bloggers.com/implementing-mclapply-on-windows-a-primer-on-embarrassingly-parallel-computation-on-multicore-systems-with-r/
 
@@
 # The hack
-# https://www.r-bloggers.com/implementing-mclapply-on-windows-a-primer-on-embarrassingly-parallel-computation-on-multicore-systems-with-r/
 
@@
 
-## Principal Routine
-
-#### Control Pannel
-
-```{r EEZ_Control_Pannel, eval = T, echo = F}
+### **Principal Routine**
+
+```{r Trans_Spp_Control_Pannel, eval = T, echo = F}
 
@@
 # Determine forlder for saving results
-Folder <- "Trans_Results"
-Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
-
-if(file.exists(Results_Path) == TRUE){
-  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
-}else{
-  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = ""))
-  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
-}
+Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",sep = "")
 
@@
 # Just a warning for me not to forget
-print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level and will be saved at",Folder))
-```
-
-#### Run Routine
-```{r Routine_parallel, eval = F, echo = F}
+print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level and will be saved at",Results_Path))
+```
+
+```{r Trans_Spp_Routine, eval = F, echo = F}
 
@@
 
-## Function `GetTransResults`
+## Functions needed
+
+### Function `GetTransResults`
+
+This function simply reads in the files and import them all as on large d.f
 
@@
 
-## Function `CleanResults`
-
-```{r cleaning_function, eval = T, echo = F}
+### Function `CleanResults`
+
+There are quite a few inconsistencies between the names of territories within the SAU shapefile, the distribution data and the UN database.
+The following function cleans up the names, some of them manually some of the automatic.
+It also removes the "transboundary nature" of those species shared by two territories that belong to the same nation (e.g.
+Brazil mainland and Brazil (Fernando de Noronha) or US Gulf of Mexico and US East coast).
+Finally, there is an annoying thing coding issue between MAC and Windows related to characters so I have to also fix for that, manually.
+
+```{r funCleanResults, eval = T, echo = F}
 
@@
 
-# Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
+# Clean out countries that share with their own borders (e.g. Brazil mainland and Brazil (Fernando de Noronha))
   Auto_Remove_Territories <- Data %>%   
@@
   # List of territories to eliminate (No other neighobors but mainland)
-
   Islands_to_Remove <- c(
@@
   # Complete list of territories to remove from dataset (Including islands)
-
   Territories_to_Remove <- Data %>% 
@@
     select(-8,-9) %>% 
-    # Fixe coding issues between MAC and Windows
+    # Fix coding issues between MAC and Windows
     mutate(
@@
 
+In here we load and cleaned the multiple external datasets requred to produce the manuscript figures
+
 ```{r Load_Results_Data, eval = F}
@@
 Jurisdiction <- "EEZ"
-Folder <- "Trans_Results"
 
 # Updates result's path for the jurisdiction
-Results_Path <- paste(Results_Path,Jurisdiction,"/",Folder,"/",sep="")
+Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
 
@@
 path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
-# #The File
+
+# The File
 fnam_world_land <- "ne_50m_admin_0_countries.shp"
 
+# Load it!
 World_land_sf <- st_read(dsn = path_world_land,
@@
 
-# Load EEZ shapefiles 
-# SAU shapefile name and paths
+# Load SAU shapefile name and paths
 
@@
 path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-# #The File
-
+
+# The File
 fnam_world <- "SAUEEZ_July2015.shp"
+
+# Load it!
 World_sf <- st_read(dsn = path_world,
@@
 # ---------------------------- #
-
-if(Sys.info()[7] == "carmelia"){ # For Carmelia
-
-  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
-}else{  # For Hall and The Beast
 
@@
 
-  # Read SAu Status Data
+# Read Species Status Data (Sub-routine Species Status)
 Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep ="")) %>% 
@@
 
-  # Load and clean Transboundary results
+# Load and clean transboundary results
 Results_Trans <- GetTransResults(Spp)
@@
 
-} # closes ifstatement for carmelia temporal files
-
 ```
@@
 
-```{r Results_Tresholds, eval =F, echo = F}
-
-#### Determine transboundary stocks and countries based on selected trsholds ####
+Determine transboundary stocks and countries based on selected trsholds. We created two tresholds (levels of uncertanty), in here we can chose which level we wanna work with.
+
+```{r Results_Tresholds, eval = F, echo = F}
 
@@
 
-```{r Data_per_Territory}
+Determine the number of species per territory
+
+```{r Data_per_Territory, eval = F, echo = F}
 
@@
 
+# Get Catch data for mapping (Currently not used)
+
+# Catch_Country <- Sau_Catch_Data %>% 
+#   group_by(FishingRegion=Territory) %>% 
+#   summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
+#   filter(!(is.na(FishingRegion))) %>% 
+#   left_join(Clean_sau_eez_fes) %>% 
+#   group_by(Territory = fishing_entity) %>% 
+#   summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
+#   mutate(Territory = gsub("USA","United States of America",Territory))
+
 # Get Catch and Revenue data for mapping
-
-Catch_Country <- Sau_Catch_Data %>% 
-  group_by(FishingRegion=Territory) %>% 
-  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
-  filter(!(is.na(FishingRegion))) %>% 
-  left_join(Clean_sau_eez_fes) %>% 
-  group_by(Territory = fishing_entity) %>% 
-  summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
-  mutate(Territory = gsub("USA","United States of America",Territory))
-
-# Or revenue data %>%
 
@@
   group_by(Territory) %>% 
-  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% 
+  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% # Million of USD
   mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
@@
   filter(Total_USD > 0)
-
 ```
@@
 ### Map of Transboundary Species
+
+Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country
 
@@
 
-# Data <- World_sf_si_land %>% 
-#   as_tibble() %>% 
-#   select(Territory, BinsLan)
-# 
-# Data_EEZ <- World_sf_si %>% 
-#   as_tibble() %>% 
-#   select(Territory, Bins)
-# 
-# 
-# ### EEZ shapefile
-# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
-# 
-# eez = spTransform(eez, CRS("+proj=longlat"))
-# eez = spTransform(eez, CRS("+proj=wintri"))
-# eez = fortify(eez) 
-# 
-# World_sf_si <- World_sf %>%
-#   st_transform(crs = 4326
-# 
-# #### Round map tryout 
-# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
-# 
-# mapworld<- mapworld %>% 
-#   rename(Territory = id) %>% 
-#   left_join(Data,
-#             by = "Territory") %>% 
-#   left_join(Data_EEZ,
-#             by = "Territory") %>% 
-#   rename(id = Territory)
-# 
-# # head(mapworld)
-# 
-# #create map boundary
-# ll.to.wt <- function (points)
-#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
-#                             CRS("+proj=wintri")))
-#  
-# lseq = seq(-85, 85, by=.25)
-# boundary <- ll.to.wt(data.frame(
-#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
-#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
-#  
-# # New facet label names for dose variable
-# ggplot()+
-#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
-#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
-#   geom_polygon(data = mapworld, 
-#                aes(
-#                  x = long,
-#                  y = lat,
-#                  group = group,
-#                  fill = BinsLan
-#                ),
-#                colour="grey") +
-#   geom_polygon(data = mapworld, 
-#                aes(
-#                  x = long,
-#                  y = lat,
-#                  group = group,
-#                  fill = Bins)
-#                ) +
-#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
-  # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
-  # geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
-  #                 box.padding = unit(0.5, "lines"),
-  #                 point.padding = unit(0.5, "lines"),
-  #                 segment.color = 'grey50') +
-  # scale_radius(range = c(1, 2)) #+
-  # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
-  # theme_map()+
-#   theme(legend.key = element_blank(),
-#         strip.background = element_blank(),
-#         legend.position = "none",
-#         text = element_text(size=12,face="bold"))+
-#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
-# y=tag_facet(q, tag_pool = c("d","e","f"))
-
 ```
@@
 
-```{r Circular_Data, eval = T, echo = F}
+```{r Circular_Country_Data, eval = T, echo = F}
 
@@
 
-```{r Top_country_Circle_Diagram, eval =F, echo = F}
-
-# Top 10 species
-
-# Number of countries shared by each Species
-Top_10_Countries <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No"
-         ) %>% 
-  group_by(Country_Territory) %>% 
-  summarise(
-    n_countries = length(unique(TaxonKey))
-  ) %>% 
-  top_n(10,n_countries)
-
-# Countries that share the top 10
-Top_Ten_Countries <- Clean_Results_Trans %>% 
-  filter(
-         Area_Index < Min_AI |
-         Area_Index > Max_AI,
-         Model_Index == MI,
-         Same_Nation == "No",
-         Country_Territory %in% Top_10_Countries$Country_Territory
-         ) %>% 
-  group_by(from=CT_fishing_entity,
-           to=NT_fishing_entity
-           ) %>% 
-  summarise(value=n()
-            ) %>% 
-  ungroup() %>% 
-  mutate(from = paste("F", from),
-         to = paste("T", to)
-         )
-
-####________________###
-# Circulize package ####
-# https://jokergoo.github.io/circlize_book/book/
-####________________###
-
-# To set links collor 
-Bins <- as.numeric(cut(Top_Ten_Countries$value,breaks = 5))
-
-# Basic plot
-circos.clear()
-chordDiagram(Top_Ten_Countries, 
-             annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
-             annotationTrackHeight = c(0.001, 0.05), # set links close to the axis
-             directional = 1, # direction of arrows
-             direction.type = c("diffHeight", "arrows"), # use arrows
-             grid.col = "white",
-             col = ifelse(Bins == 1,"#046C9A", # deep blue
-                          ifelse(Bins == 2,"#78B7C5", #light blue
-                                 ifelse(Bins == 3,"#EBCC2A", #yellow
-                                        ifelse(Bins == 4, "#E1AF00", #cream
-                                               "#F21A00")))), #red
-             link.arr.col = wes_palette("Zissou1"),
-             link.arr.type = "big.arrow",# make links big arrows
-             diffHeight = uh(1, "mm"), # brings the arrow to the bottom of the source
-             # annotationTrack = "grid", # no labels
-             scale = FALSE, # fraction of total instead of absolute value
-             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Top_Ten_Countries))))) # I have no idea but helps with the labels
-    ) 
-#  Rest of eddits
-circos.track(track.index = 1, panel.fun = function(x, y) {
-    xlim = get.cell.meta.data("xlim")
-    xplot = get.cell.meta.data("xplot")
-    ylim = get.cell.meta.data("ylim")
-    sector.name = get.cell.meta.data("sector.index")
-
-    circos.text(mean(xlim),
-                ylim[1], 
-                sector.name, 
-                facing = "clockwise",
-                niceFacing = TRUE,
-                adj = c(-0.2, 0.5),
-                col = "black")
-
-}, bg.border = NA)
-
-```
-
 ## Analysis per Species
 
-```{r n_species_country, eval = T, echo =F}
+Create figures that are based in species (e.g. number of countries each species has)
+
+```{r Circular_Spp_Data, eval = T, echo =F}
 
@@
 # Use rfishbase to get species environment
-
 Species_list <- Species_Trans %>% 
@@
 
-Species_environ_list <- rbind(species(Species_list, 
+Species_environ_list <- rbind(species(Species_list, #species from rfishbase package
                                       fields = species_fields$habitat[4])
@@
   arrange(group,value) %>% 
-  filter(value > 20)  # remove all species under 10 (way too many to plot!)
+  filter(value > 20)  # remove all species under 20 (way too many to plot!)
 
@@
 
+# Set a number of 'empty bar' to add at the end of each group
 Char <- as.factor(Species_Data$group)
-
-# Set a number of 'empty bar' to add at the end of each group
 empty_bar <- 2
@@
 
+### ------------------- ###
 # Make the plot
+### ------------------- ###
 ggplot(Species_Data, 
@@
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, 
+               aes(x = end, y = 100, xend = start, yend = 100), 
+               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
+  geom_segment(data=grid_data,
+               aes(x = end, y = 80, xend = start, yend = 80),  
+               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
+  geom_segment(data=grid_data, 
+               aes(x = end, y = 60, xend = start, yend = 60),  
+               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
+  geom_segment(data=grid_data, 
+               aes(x = end, y = 40, xend = start, yend = 40),  
+               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
+  geom_segment(data=grid_data, 
+               aes(x = end, y = 20, xend = start, yend = 20), 
+               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
   # Add median lines for each gropup
-  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
-               alpha=1, size=0.5 , inherit.aes = FALSE ) +
+  geom_segment(data=median_data, 
+               aes(x = end, y = median, xend = start+5, yend = median, colour = group),
+               alpha=1, size=0.5 , inherit.aes = FALSE) +
   # Add text showing the value of each line
@@
            color=Ticks_Color, 
-           size=3 , 
+           size=3, 
            angle=0, 
@@
   )
-# 
+
 ggsave(
@@
 }
+
+```
+
+```{r round_map, eval = F, echo = F}
+# #### Round map tryout
+
+# ### EEZ shapefile
+# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
+# 
+# eez = spTransform(eez, CRS("+proj=longlat"))
+# eez = spTransform(eez, CRS("+proj=wintri"))
+# eez = fortify(eez) 
+# 
+# World_sf_si <- World_sf %>%
+#   st_transform(crs = 4326
+#
+
+# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
+# 
+# mapworld<- mapworld %>% 
+#   rename(Territory = id) %>% 
+#   left_join(Data,
+#             by = "Territory") %>% 
+#   left_join(Data_EEZ,
+#             by = "Territory") %>% 
+#   rename(id = Territory)
+# 
+# # head(mapworld)
+# 
+# #create map boundary
+# ll.to.wt <- function (points)
+#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
+#                             CRS("+proj=wintri")))
+#  
+# lseq = seq(-85, 85, by=.25)
+# boundary <- ll.to.wt(data.frame(
+#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
+#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
+#  
+# # New facet label names for dose variable
+# ggplot()+
+#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
+#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
+#   geom_polygon(data = mapworld, 
+#                aes(
+#                  x = long,
+#                  y = lat,
+#                  group = group,
+#                  fill = BinsLan
+#                ),
+#                colour="grey") +
+#   geom_polygon(data = mapworld, 
+#                aes(
+#                  x = long,
+#                  y = lat,
+#                  group = group,
+#                  fill = Bins)
+#                ) +
+#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
+  # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
+  # geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
+  #                 box.padding = unit(0.5, "lines"),
+  #                 point.padding = unit(0.5, "lines"),
+  #                 segment.color = 'grey50') +
+  # scale_radius(range = c(1, 2)) #+
+  # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
+  # theme_map()+
+#   theme(legend.key = element_blank(),
+#         strip.background = element_blank(),
+#         legend.position = "none",
+#         text = element_text(size=12,face="bold"))+
+#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
+# y=tag_facet(q, tag_pool = c("d","e","f"))
 
@@
 ```
+
+```{r Top_country_Circle_Diagram, eval =F, echo = F}
+
+# Top 10 species
+
+# Number of countries shared by each Species
+Top_10_Countries <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No"
+         ) %>% 
+  group_by(Country_Territory) %>% 
+  summarise(
+    n_countries = length(unique(TaxonKey))
+  ) %>% 
+  top_n(10,n_countries)
+
+# Countries that share the top 10
+Top_Ten_Countries <- Clean_Results_Trans %>% 
+  filter(
+         Area_Index < Min_AI |
+         Area_Index > Max_AI,
+         Model_Index == MI,
+         Same_Nation == "No",
+         Country_Territory %in% Top_10_Countries$Country_Territory
+         ) %>% 
+  group_by(from=CT_fishing_entity,
+           to=NT_fishing_entity
+           ) %>% 
+  summarise(value=n()
+            ) %>% 
+  ungroup() %>% 
+  mutate(from = paste("F", from),
+         to = paste("T", to)
+         )
+
+####________________###
+# Circulize package ####
+# https://jokergoo.github.io/circlize_book/book/
+####________________###
+
+# To set links collor 
+Bins <- as.numeric(cut(Top_Ten_Countries$value,breaks = 5))
+
+# Basic plot
+circos.clear()
+chordDiagram(Top_Ten_Countries, 
+             annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
+             annotationTrackHeight = c(0.001, 0.05), # set links close to the axis
+             directional = 1, # direction of arrows
+             direction.type = c("diffHeight", "arrows"), # use arrows
+             grid.col = "white",
+             col = ifelse(Bins == 1,"#046C9A", # deep blue
+                          ifelse(Bins == 2,"#78B7C5", #light blue
+                                 ifelse(Bins == 3,"#EBCC2A", #yellow
+                                        ifelse(Bins == 4, "#E1AF00", #cream
+                                               "#F21A00")))), #red
+             link.arr.col = wes_palette("Zissou1"),
+             link.arr.type = "big.arrow",# make links big arrows
+             diffHeight = uh(1, "mm"), # brings the arrow to the bottom of the source
+             # annotationTrack = "grid", # no labels
+             scale = FALSE, # fraction of total instead of absolute value
+             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Top_Ten_Countries))))) # I have no idea but helps with the labels
+    ) 
+#  Rest of eddits
+circos.track(track.index = 1, panel.fun = function(x, y) {
+    xlim = get.cell.meta.data("xlim")
+    xplot = get.cell.meta.data("xplot")
+    ylim = get.cell.meta.data("ylim")
+    sector.name = get.cell.meta.data("sector.index")
+
+    circos.text(mean(xlim),
+                ylim[1], 
+                sector.name, 
+                facing = "clockwise",
+                niceFacing = TRUE,
+                adj = c(-0.2, 0.5),
+                col = "black")
+
+}, bg.border = NA)
+
+```

### 2019-10-25 Initial_Analysis.Rmd
New times with 32 cores
MOVED GETSPPDIST FUNCTION UP SINCE IT IS USED BY STATUSFUNCTION

@@
 
+### Function `GetSppDist`
+
+This function reads in species distribution from the observation data, ESM models and SAU data.
+
+```{r GetSppDist, eval = T, echo = T}
+
+#### The function
+# NOTES
+# For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
+
+GetSppDist=function(Spp,Model,Coord){
+
+  Distpath <- paste(Data_Path,"Distribution_Data/",sep="")
+  INDEX = seq(1,259200,1)
+  # INDEX <- Coordinates$INDEX
+
+  # SAU Distributions
+  if(Model == "SAU_D"){
+    File_Name <- paste("SAU_Distribution/DIST_GOOD_SP_")
+  }
+
+  # SAU Catch
+  if(Model == "SAU_C"){
+    File_Name <- paste("SAU_data_per_species/CATCH_SP_")
+  }
+
+  # Occurence
+  if(Model == "Occ"){
+    File_Name <- paste("Occurence/OCCURENCE_JULIANO_")
+  }
+
+  # ENM Model
+  if(Model == "ENM"){
+    File_Name <- paste("ENM/ENM_JULIANO_")
+  }
+
+  # DBEM Data
+  # if(Model == "DBEM"){
+  #   Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData
+  #   Final_Path <- "ENM"
+  #   File_Name <- paste("ENM_JULIANO",Spp,".mat",sep="")
+  # }
+
+  if(Model == "All"){
+
+    Models_List <- c(paste(Distpath,"SAU_Distribution/DIST_GOOD_SP_",Spp,".mat",sep =""),
+                     paste(Distpath,"Occurence/OCCURENCE_JULIANO_",Spp,".mat",sep=""),
+                     paste(Distpath,"ENM/ENM_JULIANO_",Spp,".mat",sep="")
+    )
+
+    # Jumps species not modeled. NOTE: We only need one as ENM, Occ and SAU Dis have all the same 939 spp
+    if(file.exists(Models_List[1])){
+
+      Load <- lapply(Models_List, FUN=R.matlab::readMat, na.strings=0)
+
+      sppdist <- as.data.frame(bind_cols(Load)) %>% 
+        mutate(
+          INDEX = INDEX,
+          TaxonKey = Spp
+        )
+      colnames(sppdist) <- c("SAU_D","Occ","ENM","INDEX","TaxonKey")
+
+      #### Step for SAU catch data that has to be averaged
+      File_Name <- paste("SAU_data_per_species/CATCH_SP_")
+      SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
+
+      # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
+      SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
+        select(CATCH.1:CATCH.65) %>% 
+        mutate(INDEX = INDEX) %>% 
+        gather("Year","Catch",CATCH.56:CATCH.65) %>% # Last 10 years of data
+        group_by(INDEX) %>% 
+        summarise(SAU_C = mean(Catch,na.rm=T))
+
+      # Join both tables
+      sppdist <- sppdist %>% 
+        left_join(SAU_C_data,
+                  by = "INDEX") %>% 
+        select(TaxonKey,INDEX,everything()) %>% 
+        left_join(CoorG,
+                  by = "INDEX")
+
+      # Fix coordinate system incompatibility between Gab and DBEM
+      sppdist <- suppressWarnings(sppdist[order(sppdist$Latitude, rev(sppdist$Longitude),decreasing=TRUE), ] %>% 
+                                    mutate(INDEX = seq(1,259200,1)) %>% 
+                                    gather("Model","Value",3:6) %>%
+                                    mutate(Value = ifelse(is.na(Value), 0, Value)) # Converting NA's to ceros
+      )
+
+      getSppDist = sppdist
+
+    }
+
+  }else{
+
+    # Merge paths
+    SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
+
+    if(file.exists(SppPath) == TRUE){
+
+      #Install (if needed) R.matlab package
+      if(!require(R.matlab)){
+        install.packages("R.matlab")
+      }
+
+      # Read Files
+
+      sppdist <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
+        mutate(INDEX = INDEX,
+               Species = Spp) %>% 
+        left_join(Coord)
+
+      # Fix coordinate system incompatibility between Gab and DBEM
+      sppdist <- sppdist[order(sppdist$Latitude, rev(sppdist$Longitude),decreasing=TRUE), ] %>% 
+        mutate(INDEX = seq(1,259200,1))
+
+      # Return 
+      getSppDist=sppdist
+
+    }else{
+      print(paste("No info for this species",Spp, "in",Model))
+    }
+
+  }
+}
+
+#______ Test ______#
+
+# Variables outside function
+# head(GetSppDist(600004,"SAU_D")) # Works
+# head(GetSppDist(600004,"SAU_C")) # Works
+# head(GetSppDist(600004,"Occurence")) # Works
+# head(GetSppDist(600004,"ENM")) # Works
+# head(GetSppDist(600004,"All")) # Works
+
+```
+
 ### Function `EstSppStatus`
@@
     ) %>% 
-    gather("Step","Treshold",Years_appart:Catch_over) %>% 
+    gather("Step","Treshold",Years_appart:Consecutive) %>% 
     group_by(TaxonKey,Territory) %>% 
@@
 ** NOTE THAT THE FUNCTION IS SETTED TO OUTPUT RESULTS FOR ALL MODELS **
-
-### Function `GetSppDist`
-
-This function reads in species distribution from the observation data, ESM models and SAU data.
-
-```{r GetSppDist, eval = T, echo = T}
-
-#### The function
-# NOTES
-# For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
-
-GetSppDist=function(Spp,Model,Coord){
-
-  Distpath <- paste(Data_Path,"Distribution_Data/",sep="")
-  INDEX = seq(1,259200,1)
-  # INDEX <- Coordinates$INDEX
-
-  # SAU Distributions
-  if(Model == "SAU_D"){
-    File_Name <- paste("SAU_Distribution/DIST_GOOD_SP_")
-  }
-
-  # SAU Catch
-  if(Model == "SAU_C"){
-    File_Name <- paste("SAU_data_per_species/CATCH_SP_")
-  }
-
-  # Occurence
-  if(Model == "Occ"){
-    File_Name <- paste("Occurence/OCCURENCE_JULIANO_")
-  }
-
-  # ENM Model
-  if(Model == "ENM"){
-    File_Name <- paste("ENM/ENM_JULIANO_")
-  }
-
-  # DBEM Data
-  # if(Model == "DBEM"){
-  #   Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData
-  #   Final_Path <- "ENM"
-  #   File_Name <- paste("ENM_JULIANO",Spp,".mat",sep="")
-  # }
-
-  if(Model == "All"){
-
-    Models_List <- c(paste(Distpath,"SAU_Distribution/DIST_GOOD_SP_",Spp,".mat",sep =""),
-                     paste(Distpath,"Occurence/OCCURENCE_JULIANO_",Spp,".mat",sep=""),
-                     paste(Distpath,"ENM/ENM_JULIANO_",Spp,".mat",sep="")
-    )
-
-    # Jumps species not modeled. NOTE: We only need one as ENM, Occ and SAU Dis have all the same 939 spp
-    if(file.exists(Models_List[1])){
-
-      Load <- lapply(Models_List, FUN=R.matlab::readMat, na.strings=0)
-
-      sppdist <- as.data.frame(bind_cols(Load)) %>% 
-        mutate(
-          INDEX = INDEX,
-          TaxonKey = Spp
-        )
-      colnames(sppdist) <- c("SAU_D","Occ","ENM","INDEX","TaxonKey")
-
-      #### Step for SAU catch data that has to be averaged
-      File_Name <- paste("SAU_data_per_species/CATCH_SP_")
-      SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
-
-      # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
-      SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
-        select(CATCH.1:CATCH.65) %>% 
-        mutate(INDEX = INDEX) %>% 
-        gather("Year","Catch",CATCH.56:CATCH.65) %>% # Last 10 years of data
-        group_by(INDEX) %>% 
-        summarise(SAU_C = mean(Catch,na.rm=T))
-
-      # Join both tables
-      sppdist <- sppdist %>% 
-        left_join(SAU_C_data,
-                  by = "INDEX") %>% 
-        select(TaxonKey,INDEX,everything()) %>% 
-        left_join(CoorG,
-                  by = "INDEX")
-
-      # Fix coordinate system incompatibility between Gab and DBEM
-      sppdist <- suppressWarnings(sppdist[order(sppdist$Latitude, rev(sppdist$Longitude),decreasing=TRUE), ] %>% 
-                                    mutate(INDEX = seq(1,259200,1)) %>% 
-                                    gather("Model","Value",3:6) %>%
-                                    mutate(Value = ifelse(is.na(Value), 0, Value)) # Converting NA's to ceros
-      )
-
-      getSppDist = sppdist
-
-    }
-
-  }else{
-
-    # Merge paths
-    SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
-
-    if(file.exists(SppPath) == TRUE){
-
-      #Install (if needed) R.matlab package
-      if(!require(R.matlab)){
-        install.packages("R.matlab")
-      }
-
-      # Read Files
-
-      sppdist <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
-        mutate(INDEX = INDEX,
-               Species = Spp) %>% 
-        left_join(Coord)
-
-      # Fix coordinate system incompatibility between Gab and DBEM
-      sppdist <- sppdist[order(sppdist$Latitude, rev(sppdist$Longitude),decreasing=TRUE), ] %>% 
-        mutate(INDEX = seq(1,259200,1))
-
-      # Return 
-      getSppDist=sppdist
-
-    }else{
-      print(paste("No info for this species",Spp, "in",Model))
-    }
-
-  }
-}
-
-#______ Test ______#
-
-# Variables outside function
-# head(GetSppDist(600004,"SAU_D")) # Works
-# head(GetSppDist(600004,"SAU_C")) # Works
-# head(GetSppDist(600004,"Occurence")) # Works
-# head(GetSppDist(600004,"ENM")) # Works
-# head(GetSppDist(600004,"All")) # Works
-
-```
 
@@
 
-```{r Trans_Spp_Control_Pannel, eval = T, echo = F}
+```{r Trans_Spp_Control_Pannel, eval = F, echo = F}
 
@@
 # user   system  elapsed 
- #8117.72  1991.91 10296.00
+# 8117.72  1991.91 10296.00
+
+# Data on time for the Beast with 32 cores
+ #  user  system elapsed 
+# 7831.10 1327.27 9261.48
 
@@
   # Set the path for each file
-  Distpath <- paste(Results_Path,Spp,sep="")
+  Distpath <- paste(Results_Path,"Trans_Results/",Spp,sep="")
 
@@
 
-```{r funCleanResults, eval = T, echo = F}
+```{r funCleanResults, eval = F, echo = F}
 
@@
   Auto_Remove_Territories <- Data %>% 
+    filter(!is.na(Territory),
+           !is.na(Neighbour)) %>% 
     rename(FishingRegion=Territory) %>% 
@@
 # Read Species Status Data (Sub-routine Species Status)
-Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep ="")) %>% 
-  rename(TaxonKey = Species)
+Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep =""))
 
 # List of species
-Spp <- list.files(paste(Results_Path,sep=""))[-829]
+Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]
 
@@
     Area_Index <= Max_AI,
-    Model_Index == MI
+    Model_Index >= MI
   )
@@
 
-Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Value.png", sep = "")
+Plot_Name <- paste("New_100_25_Bins_Value.png", sep = "")
 
@@
        units = "in",
-       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+       path = Figures_Path
 )
@@
 
-```{r Circular_Country_Data, eval = T, echo = F}
+```{r Circular_Country_Data, eval = F, echo = F}
 
@@
 Status_Data_Plot <- Tresholded_T_Data %>% 
-  mutate(TaxonKey = as.character(TaxonKey)) %>% 
+  # mutate(TaxonKey = as.character(TaxonKey)) %>% 
   # rename(Territory = CT_fishing_entity) %>% 
@@
   geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
-  scale_fill_viridis(discrete=TRUE) +
+  # scale_fill_viridis(discrete=TRUE) +
 
@@
 
-```{r Territories_Circluar_Plot, eval = T, echo = T}
+```{r Territories_Circluar_Plot, eval = F, echo = T}
 
@@
 to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
-to_add$individual <- rep(letters[1:6], each=empty_bar*nObsType)
+# to_add$individual <- rep(letters[1:6], each=empty_bar*nObsType)
 data <- bind_rows(data, to_add)
@@
   group_by(group) %>% 
-  summarize(start=min(id,na.rm=T), end=max(id,na.rm=T) - empty_bar) %>% 
+  summarize(start=min(id,na.rm=T), 
+            end=max(id,na.rm=T) - empty_bar) %>% 
   rowwise() %>% 
@@
   # Add the stacked bar
-  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
-  scale_fill_manual("Continent",
+  geom_bar(aes(x=as.factor(id), y=value, fill=observation,group=group), stat="identity", alpha=0.5) +
+  scale_fill_manual("Catch Trend",
                     values = c(wes_palette(n = 5, name = "Darjeeling1"),
@@
 
-```{r Circular_Spp_Data, eval = T, echo =F}
+```{r Circular_Spp_Data, eval = F, echo =F}
 
@@
 
-```{r species_circluar_plot, eval = T, echo = T}
+```{r species_circluar_plot, eval = F, echo = T}
 

### 2019-11-06 Initial_Analysis.Rmd
Included some parenthesis in the status species function

@@
     # Final Species Status Evaluation 
-    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Rebuilding",
                            ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
-                                  ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                         ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
-                                                ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                  ifelse(RMean > (Max_Peak*0.50),"Max Exploited",
+                                         ifelse(Year > Y_Max_Peak & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Over Exploited",
+                                                ifelse(Year > Y_Max_Peak & RMean < (Max_Peak*0.10),"Collapsed",
                                                        "No Status")
@@
                            )
-    )
-    ) %>% 
+    )) %>% 
     filter(Year > 2004) %>% # last 10 years of data
@@
 # Save data
-# write.csv(Species_Status,
-#           paste(Results_Path,"Species_Status.csv",sep=""),
-#                 row.names = F)
+write.csv(Species_Status,
+          paste(Results_Path,"Species_Status.csv",sep=""),
+                row.names = F)
 
@@
 # Species list to get species names
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
-Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/SppTaxonName.csv",sep=""))
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep=""))
+Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep=""))
 
@@
 Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep =""))
+# Status_Data <- Species_Status
 
@@
 
-length(unique(Total_trans_n$TaxonKey)) #674 spp
+length(unique(Total_trans_n$TaxonKey)) #633 spp at 100% and 25%
 
@@
 
-Countries_Data_Plot <- Tresholded_T_Data %>% 
-  group_by(Territory = CT_fishing_entity) %>% 
-  summarise(value = length(unique(TaxonKey))) %>% 
-  left_join(UN_Regions, by ="Territory") %>%
-  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-  rename(FishingRegion=Territory) %>% 
-  left_join(Clean_sau_eez_fes) %>% 
-  group_by(individual = fishing_entity,group) %>% 
-  summarise(Total_trans = sum(value,na.rm=T)) %>% 
-  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
-  filter(!is.na(individual)) %>% 
-  select(individual,group,value) %>% 
-  arrange(group,value)
+# Countries_Data_Plot <- Tresholded_T_Data %>% 
+#   group_by(Territory = CT_fishing_entity) %>% 
+#   summarise(value = length(unique(TaxonKey))) %>% 
+#   left_join(UN_Regions, by ="Territory") %>%
+#   mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+#   rename(FishingRegion=Territory) %>% 
+#   left_join(Clean_sau_eez_fes) %>% 
+#   group_by(individual = fishing_entity,group) %>% 
+#   summarise(Total_trans = sum(value,na.rm=T)) %>% 
+#   mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
+#   filter(!is.na(individual)) %>% 
+#   select(individual,group,value) %>% 
+#   arrange(group,value)
 
@@
 
-Discrete_Data_Plot <- Tresholded_D_Data %>% 
-  summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
-  mutate(value = ifelse(value <= -100,-100,value)) %>% 
-  left_join(UN_Regions, by ="Territory") %>%
-  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-  filter(!is.na(Territory)) %>% 
-  select(individual = Territory,
-         group,
-         value)
+# Discrete_Data_Plot <- Tresholded_D_Data %>% 
+#   summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
+#   mutate(value = ifelse(value <= -100,-100,value)) %>% 
+#   left_join(UN_Regions, by ="Territory") %>%
+#   mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+#   filter(!is.na(Territory)) %>% 
+#   select(individual = Territory,
+#          group,
+#          value)
 
@@
 # Include possible missing countries in bothe datasets
-Countries_Data_Plot <- Discrete_Data_Plot %>% 
-  anti_join(Countries_Data_Plot,
-            by = c("individual","group")) %>% 
-  mutate(Total_Discrete = 0) %>% 
-  bind_rows(Countries_Data_Plot)
-
-Discrete_Data_Plot <- Countries_Data_Plot %>% 
-  anti_join(Discrete_Data_Plot,
-            by = c("individual","group")) %>% 
-  mutate(value = 0) %>% 
-  bind_rows(Discrete_Data_Plot)
-
-```
-
-```{r}
-
-data <- data.frame(
-  individual=paste( "Mister ", seq(1,60), sep=""),
-  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
-  value1=sample( seq(10,100), 60, replace=T),
-  value2=sample( seq(10,100), 60, replace=T),
-  value3=sample( seq(10,100), 60, replace=T)
-)
+# Countries_Data_Plot <- Discrete_Data_Plot %>% 
+#   anti_join(Countries_Data_Plot,
+#             by = c("individual","group")) %>% 
+#   mutate(Total_Discrete = 0) %>% 
+#   bind_rows(Countries_Data_Plot)
+
+# Discrete_Data_Plot <- Countries_Data_Plot %>% 
+#   anti_join(Discrete_Data_Plot,
+#             by = c("individual","group")) %>% 
+#   mutate(value = 0) %>% 
+#   bind_rows(Discrete_Data_Plot)
+
+```
+
+```{r Territories_Circluar_Plot, eval = F, echo = T}
+
+# -------------------------- #
+# Data manipulation for plot
+# -------------------------- #
+
+# Set a number of 'empty bar' to add at the end of each Georegion
+Char <- as.factor(Status_Data_Plot$group) # Set groups to factors
+
+##### COPY PASTE
 
 # Transform data in a tidy format (long format)
-data <- data %>% gather(key = "observation", value="value", -c(1,2))
+data <- Status_Data_Plot
 
@@
 empty_bar <- 2
-nObsType <- nlevels(as.factor(data$observation))
-to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group)*nObsType, ncol(data)) )
-colnames(to_add) <- colnames(data)
-to_add$group <- rep(levels(data$group), each=empty_bar*nObsType )
-data <- rbind(data, to_add)
-data <- data %>% arrange(group, individual)
-data$id <- rep( seq(1, nrow(data)/nObsType) , each=nObsType)
+nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
+to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
+colnames(to_add) <- colnames(Status_Data_Plot)
+to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
+to_add$value <- NA
+to_add$observation <- NA
+# to_add$individual <- to_add$group
+
+data <- Status_Data_Plot %>% 
+  bind_rows(to_add) %>% 
+  ungroup() %>% 
+  mutate(individual = forcats::fct_explicit_na(individual),
+         group = forcats::fct_explicit_na(group)) %>%
+  group_by(group,individual) %>% 
+  mutate(id = as.integer(individual),
+         order = as.integer(group))
+
+# data$id <- as.integer(data$individual,na.rm=T)
 
 # Get the name and the y position of each label
-label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
+label_data <- data %>% 
+  # filter(value > 0) %>% 
+  group_by(id, individual) %>% 
+  summarize(tot=sum(value,na.rm=T))
+
 number_of_bar <- nrow(label_data)
@@
 
+label_data <- label_data %>% 
+  mutate(individual = ifelse(individual == "(Missing)",paste(" "),paste(individual)))
+
 # prepare a data frame for base lines
@@
   group_by(group) %>% 
-  summarize(start=min(id), end=max(id) - empty_bar) %>% 
+  summarize(start=min(id,na.rm=T), 
+            end=max(id,na.rm=T) - empty_bar,
+            median = median(value, na.rm = T)) %>% 
   rowwise() %>% 
@@
 
-# Make the plot
-ggplot(data) +
-
-  # Add the stacked bar
-  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
-  # scale_fill_viridis(discrete=TRUE) +
-
+data %>% 
+  # filter(observation != "Np Status") %>% 
+  ggplot() + 
+  geom_bar(aes(x=id,
+               y=value, 
+               fill=observation),
+           stat="identity", 
+           alpha=0.5) +
+  scale_fill_manual("Catch Trend",
+                    values = c(
+                      "#FF0000", # collapsed,
+                      "#046C94", # Developing
+                      "#00A08A", #Max exp.
+                      "grey", #no status
+                      "#F98400", #over exp
+                      "#5BBCD6" # Rebuilding
+                    ),
+                    na.value = "white"
+  ) +
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=1, size=1 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), linetype = "dashed", colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = -50, xend = start, yend = -50), linetype = "dashed", colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
   # Add text showing the value of each 100/75/50/25 lines
-  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
-
-  ylim(-150,max(label_data$tot, na.rm=T)) +
+  ggplot2::annotate("text", 
+                    # x = rep(max(data$id),3),
+                    x =c(1,0.2,1,0.8),
+                    y = c(-50, 0, 50, 100),
+                    label = c("50","0", "50", "100") , 
+                    color="black", 
+                    size=5.5, 
+                    angle=0, 
+                    # fontface="bold",
+                    hjust=1) +
+
+  ylim(-100,101) +
   theme_minimal() +
   theme(
-    legend.position = "none",
+    legend.position = c(0.93,0.14),
+    legend.key.size = unit(1,"cm"),
+    legend.title = element_text(size = 16),
+    legend.text = element_text(size = 14),
     axis.text = element_blank(),
@@
   ) +
-  coord_polar() +
-
   # Add labels on top of each bar
-  geom_text(data=label_data, aes(x=id, y=tot+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +
-
-  # Add base line information
-  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
-  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
-
-```
-
-```{r Territories_Circluar_Plot, eval = F, echo = T}
-
-# -------------------------- #
-# Data manipulation for plot
-# -------------------------- #
-
-# Set a number of 'empty bar' to add at the end of each Georegion
-Char <- as.factor(Status_Data_Plot$group) # Set groups to factors
-
-##### COPY PASTE
-
-# Transform data in a tidy format (long format)
-data <- Status_Data_Plot
-
-# Set a number of 'empty bar' to add at the end of each group
-empty_bar <- 5
-nObsType <- nlevels(as.factor(data$observation))
-to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(data)) )
-colnames(to_add) <- colnames(data)
-to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
-# to_add$individual <- rep(letters[1:6], each=empty_bar*nObsType)
-data <- bind_rows(data, to_add)
-data <- data %>% arrange(group, individual) %>% rowwise() %>%  mutate(id = as.numeric(as.factor(individual)))
-data$id <- as.numeric(as.factor(data$individual))
-
-# Get the name and the y position of each label
-label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
-number_of_bar <- nrow(label_data)
-angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
-label_data$hjust <- ifelse( angle < -90, 1, 0)
-label_data$angle <- ifelse(angle < -90, angle+180, angle)
-
-# prepare a data frame for base lines
-base_data <-  data %>% 
-  group_by(group) %>% 
-  summarize(start=min(id,na.rm=T), 
-            end=max(id,na.rm=T) - empty_bar) %>% 
-  rowwise() %>% 
-  mutate(title=mean(c(start, end)))
-
-# prepare a data frame for grid (scales)
-grid_data <- base_data
-grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
-grid_data$start <- grid_data$start - 1
-grid_data <- grid_data[-1,]
-
-data <- data %>% 
-  ungroup() %>% 
-  mutate(individual = ifelse(is.na(observation),NA,observation))
-
-ggplot(data) + 
-  # Add the stacked bar
-  geom_bar(aes(x=as.factor(id), y=value, fill=observation,group=group), stat="identity", alpha=0.5) +
-  scale_fill_manual("Catch Trend",
-                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 1, name = "Darjeeling2")
-                    ),
-                    na.value = "white"
-  ) +
-
-  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-
-  # Add text showing the value of each 100/75/50/25 lines
-  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
-
-  ylim(-150,max(label_data$tot, na.rm=T)) +
-  theme_minimal() +
-  theme(
-    legend.position = "right",
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() +
-
-  # Add labels on top of each bar
-  geom_text(data=label_data, aes(x=id, y=max(tot,na.rm=T), label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2, angle= label_data$angle, inherit.aes = FALSE ) +
-
-  # Add base line information
-  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
-  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,1,0,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
-
-#### END COPY PASTE
-
-empty_bar <- 5
-nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
-to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
-colnames(to_add) <- colnames(Status_Data_Plot)
-to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
-Status_Data_Plot <- bind_rows(Status_Data_Plot, to_add)
-Status_Data_Plot <- Status_Data_Plot %>% arrange(group, individual)
-# Status_Data_Plot$id <- c(rep(seq(1,round(nrow(Status_Data_Plot)/nObsType)) , each=nObsType),128)
-Status_Data_Plot$id <- as.numeric(as.factor(Status_Data_Plot$individual))
-
-# Get the name and the y position of each label
-
-# Top n of each group label
-Top_Countries <- Status_Data_Plot %>% 
-  group_by(group) %>% 
-  top_n(5,value)
-
-# Create labels for all but top 5
-# Get the name and the y position of each label
-
-label_data <- Status_Data_Plot %>% 
-  group_by(id, individual) %>% 
-  summarize(tot=sum(value))
-
-label_data <- Status_Data_Plot 
-number_of_bar <- nrow(label_data)
-angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
-label_data$hjust <- ifelse( angle < -90, 1, 0)
-label_data$angle <- ifelse(angle < -90, angle+180, angle)
-
-# Remove top 5
-label_data_rest <- label_data %>% 
-  filter(!individual %in% Top_Countries$individual)
-
-# Create labels for top 5
-Top_label_data <- label_data %>% 
-  filter(individual %in% Top_Countries$individual)
-
-# prepare a data frame for base lines
-base_data <- Status_Data_Plot %>% 
-  group_by(group) %>% 
-  summarize(start=min(id,na.rm=T), 
-            end=max(id,na.rm=T) - empty_bar, 
-            median = median(value, na.rm = T)
-            ) %>% 
-  rowwise() %>% 
-  mutate(title=mean(c(start, end)))
-
-# prepare a data frame for grid (scales)
-grid_data <- base_data
-grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
-grid_data$start <- grid_data$start - 1
-# grid_data[1,2] <- 5 # Manually include Africa for the median
-# grid_data[1,3] <- 1
-
-# Median data
-median_data <- grid_data %>% 
-  mutate_at(vars(start,end),
-            .funs = as.numeric)
-
-# -------------------------- #
-# Make the plot
-# -------------------------- #
-
-# Global Variables
-Seq_axis <- seq(0,100,20)
-Plot_Limit <- max(Status_Data_Plot$value,na.rm=T)
-Plot_Limit_Low <- -50
-Ticks_Color <- "grey50"
-
-ggplot(Status_Data_Plot) +
-
-  # Add the stacked bar
-  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
-  # scale_fill_viridis(discrete=TRUE) +
-
-  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
-
-  # Add text showing the value of each 100/75/50/25 lines
-  ggplot2::annotate("text", x = rep(max(Status_Data_Plot$id,na.rm=T),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
-
-  ylim(-150,max(label_data$value, na.rm=T)) +
-  theme_minimal() +
-  theme(
-    legend.position = "none",
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() +
-
-  # Add labels on top of each bar
-  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +
-
-  # Add base line information
-  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
-  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0,1,1), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
-
-# Base plot
-ggplot(Status_Data_Plot,
-       aes(x=as.factor(id), 
-           y=value,
-           fill=observation)
-) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
-  geom_bar(aes(x=as.factor(id),
-               y=value,
-               fill=observation),
-           stat="identity",
-           alpha=0.5) +
-  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) +
-  # Add median lines for each gropup
-  # geom_segment(data=median_data,
-  #              aes(x = end,
-  #                  y = median,
-  #                  xend = start+5, 
-  #                  yend = median,
-  #                  colour = group),
-  #              alpha=1,
-  #              size=0.5 , 
-  #              inherit.aes = FALSE ) +
-  # Add text showing the value of each line
-  annotate("text", 
-           x = rep(max(Status_Data_Plot$id),length(Seq_axis)),
-           y = Seq_axis,
-           label = c("<-100",as.character(Seq_axis)[2:(length(Seq_axis)-1)],">100"),
-           color = Ticks_Color, 
-           size= 4, 
-           angle = 0, 
-           # fontface="bold",
-           hjust=1) +
-  ylim(-150,max(label_data$value, na.rm=T)) +
-  theme_minimal() +
-  theme(
-    legend.position = "none",
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() +
-  #Country labels
-  geom_text(data=label_data_rest,
-            aes(x=id,
-                y=Plot_Limit,
-                label=individual,
-                hjust=hjust), 
-            color="black",
-            # fontface="bold",
-            alpha=1,
-            size=2.5,
-            angle= label_data_rest$angle,
-            inherit.aes = FALSE) +
-  # Bold top 3 
-  geom_text(data=Top_label_data,
-            aes(x=id, y=Plot_Limit,
+  geom_text(data=label_data,
+            aes(
+              x = id,
+              # x=reorder(id,order),
+                # y=max(tot,na.rm=T),
+                # y=tot +1,
+                y = 101,
                 label=individual,
@@
             alpha=1,
-            size=2.5,
-            angle= Top_label_data$angle,
-            inherit.aes = FALSE) +
-  # Add base line information
-  geom_segment(data=base_data, 
-               aes(x = start, 
-                   y = 0, 
-                   xend = end, 
-                   yend = 0
-                   ), 
-               colour = "black",
-               alpha=0.8, 
-               size=0.6 , 
-               inherit.aes = FALSE) +
-  ylim(Plot_Limit_Low,Plot_Limit) + # sets the circle the first value the central the last value how wide
-  theme_minimal() +
+            size=3,
+            angle= label_data$angle,
+            inherit.aes = FALSE ) +
   coord_polar()
-  theme(
-    # legend.position = c(0.5,0.5),
-    # legend.position = "",
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() + 
-  scale_fill_manual("Continent",
-                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 4, name = "Darjeeling2"),
-                               "black","grey","blue"
-                    ),
-                    na.value = "white"
-  ) +
-  scale_colour_manual("Continent",
-                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                                 wes_palette(n = 4, name = "Darjeeling2"),
-                                 "black","grey","blue"
-                      ),
-                      na.value = "white")
 
@@
     plot = last_plot(),
-    width = 12,
-    height = 12,
+    width = 16,
+    height = 14,
     units = "in",
-    filename = "Territory_circular_both.png",
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+    filename = "Territory_circular_status.png",
+    path = Figures_Path
   )

### 2019-11-07 Initial_Analysis.Rmd
Fixed issue with duplicated species status.

@@
   "wesanderson",
+  "tidyverse",
   "circlize", # For circular plot
@@
 
+Spp <- 600006
+Coord <- CoorG
+
 EstSppStatus <- function(Spp,Coord){
@@
     select(TaxonKey,Territory) %>% 
-    mutate(Status = "No Status")
+    mutate(Status = "No Trend")
 
@@
     top_n(-1,RMean) %>% # find min value
+    group_by(TaxonKey,Y_Max_Peak,Territory,Max_Peak,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl 2013-2014)
+    summarise(Year = min(Year)) %>% 
     rename(Post_Max_Min = RMean,
@@
                                                 ifelse(Year > Y_Max_Peak & RMean < (Max_Peak*0.10),"Collapsed",
-                                                       "No Status")
-                                         )
-                                  )
-                           )
-    )) %>% 
-    filter(Year > 2004) %>% # last 10 years of data
+                                                       "No Trend")
+                                         )
+                                  )
+                           )
+    )
+    )
+
+  # Determine the final status using the top category over the last 10 years
+  Determine_Status_Data <- Status_Data %>% 
+    filter(Year > 2004) %>% # last 10 years of data (2005-2014)
     group_by(TaxonKey,Territory,Status) %>%
@@
     group_by(TaxonKey,Territory) %>%
-    top_n(1,n_Status) %>%
-    select(-n_Status)
+    top_n(1,n_Status)
+
+  # Fix cases where you have equal categories.
+  Duplicates <- Determine_Status_Data %>% 
+    ungroup() %>% 
+    janitor::get_dupes(Territory) %>% 
+    select(TaxonKey,Territory) %>% 
+    pull(Territory) %>% 
+    unique()
+
+  # In this case we sue the last year's category
+  Duplicates_Status <- Status_Data %>% 
+  filter(Territory %in% Duplicates,
+         Year == 2014) %>%
+    ungroup() %>%
+    select(TaxonKey,Territory,Status)
+
+  # Build Final Status database
+  Final_Status_Data <- Determine_Status_Data %>% 
+    filter(!Territory %in% Duplicates) %>% 
+    bind_rows(Duplicates_Status)
 
@@
   # If both datasets have value RETURN BOTH
-  if(nrow(No_Status_Data) > 0 & nrow(Status_Data) > 0){
+  if(nrow(No_Status_Data) > 0 & nrow(Final_Status_Data) > 0){
 
     Fun_Result <- bind_rows(No_Status_Data,
-                            Status_Data)
+                            Final_Status_Data)
   }
@@
   # If only No status data, then just return No Status Data
-  if(nrow(No_Status_Data) > 0 & nrow(Status_Data) == 0){
+  if(nrow(No_Status_Data) > 0 & nrow(Final_Status_Data) == 0){
     return(No_Status_Data)
   }else{
-    return(Status_Data)
+    return(Final_Status_Data)
   }
@@
 # Save data
-write.csv(Species_Status,
-          paste(Results_Path,"Species_Status.csv",sep=""),
-                row.names = F)
-
+# readr::write_csv(Species_Status,
+#           "Species_Status.csv")
+# head(Species_Status)
 ```
@@
 # Read Species Status Data (Sub-routine Species Status)
-Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep =""))
+Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep =""))
 # Status_Data <- Species_Status
@@
 Status_Data_Plot <- Tresholded_T_Data %>% 
-  # mutate(TaxonKey = as.character(TaxonKey)) %>%
+  mutate(TaxonKey = as.character(TaxonKey)) %>%
   # rename(Territory = CT_fishing_entity) %>% 
-  left_join(Status_Data, 
+  left_join(Species_Status, 
             by =c("Territory","TaxonKey")
@@
 head(x)
+
+```
+
+### Number of Collapsed USA species
+
+```{r Collapsed_USA, eval = F ,echo = T,warning = F,message = F}
+
+#  At the end, the ram legacy and the SAU are tide in results...
+
+USA_Collapsed <- Species_Status %>% 
+  filter(str_detect(Territory, pattern="USA")#,
+         # Status == "Collapsed"
+  ) %>% 
+  ungroup() %>% 
+  mutate(TaxonKey = as.numeric(TaxonKey)) %>%
+  left_join(Exploited_Species)
+
+# Comparring to RAM legacy in the W pacific coast
+
+# Sabelfish match
+# Pacifc sardine no data ram
+# Chillipepper match
+# Lincod no match althou circular path in RAM
+# Dover no match by far...
+# Chub mackerel... match
+# Petral metch
+# Black Rockfish No mach...ish
+# Widow rockfish no match
+# Starry flounder no match
+# Rex sole no data RAM
+# Pacific ocean percCollapsed Vs Overfished
+#
 

### 2019-11-07 Initial_Analysis.Rmd
Included the janitor package and some details on the Species Status function

@@
   "data.table", # Read dataframe (Fast!)
-  "dplyr", # Data manipulation
-  "tidyr", # Data manipulation
-  "ggplot2", #Nice grpahs and spatial analysis
   "wesanderson",
-  "tidyverse",
+  "tidyverse", # for all data wrangling and ggplot
+  "janitor", # for data cleaning
   "circlize", # For circular plot
@@
 
+Finally we choose the reporting year based on the most frequent status in the last 10 years of data.
+In cases where there was a mach between status (e.g.
+Cayman Islands for species 6000006 had 5 *Max Exploited* and 5 *Overexploted*) then we report the status at the last year of data.
+
 ### Function `GetSppDist`
@@
 
-Spp <- 600006
-Coord <- CoorG
+Spp <- 600004
 
@@
   # Fix cases where you have equal categories.
+  suppressMessages( # supresses "No duplicate combinations found of: Territ"
     Duplicates <- Determine_Status_Data %>% 
@@
       unique()
+  )
 
@@
     mclapply(
-      Species_List,
+      Species_List[1:2],
       FUN = EstSppStatus,

### 2019-11-07 Initial_Analysis.Rmd
Fixed problem of multiple years of max catch data (e.g. caymans)

@@
 
-Spp <- 600004
+Spp <- 601417
 
@@
   Status_Data <- Data %>% 
+    # filter(Territory == "Israel (Red Sea)") %>%  # For testing
     anti_join(No_Status_Data, # Removes no status data
@@
     top_n(1,RMean) %>% 
+    group_by(TaxonKey,Territory,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl all years)
+    summarise(Year = min(Year)) %>%
     rename(Max_Peak = RMean,
@@
 
+## Overall results
+
+```{r Data_per_Territory, eval = F, echo = F}
+
+# Number of Transboundary Species
+Total_trans_n <- Clean_Results_Trans %>% 
+  filter(
+    Area_Index >= Min_AI,
+    Area_Index <= Max_AI,
+    Model_Index >= MI
+  ) %>% 
+  pull(TaxonKey) %>% 
+  length(unique())
+
+```
+
 ## Results per Territory
@@
   )
-
-# Number of Transboundary Species
-Total_trans_n <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index >= Min_AI,
-    Area_Index <= Max_AI,
-    Model_Index >= MI
-  )
-
-length(unique(Total_trans_n$TaxonKey)) #633 spp at 100% and 25%
 

### 2019-11-08 Manuscript_Draft.Rmd
Drafted some more results

@@
 We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species.
-Our results suggest that there are XXX transboundary species in the world that account for XXX t landings generating USD xxx in fishing revenue to a total of USD xxxx in the fishing sector.
-These numbers represent an important contribution to global fish production and revenue estimated in XXX and XXX, respectively, highlighting the importance of transboundary stocks worldwide[@REf][@REf].
+Our results suggest that there are `r Total_trans_n` transboundary species in the world, wich is **something** related to what Caddy (1997) estimated and more than double of that of Teh and Sumaila (2010) [@Teh].
 
-Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
-The overall fish production of transboundary species is relative lower than the number of species within each EEZ, with the exception of some punctual cases like Peru, Chile, Norway, and Ireland where fewer species produce higher landings (Fig 1).
+Tranboundary fisheries are quite important worldwide in terms of both landings and revenue as they are responsable for XXX tones of landings generating USD `r Total_Trans_Rev` million in fishing revenue.
+This represents XX% of the catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world.
+All these values are higher than previouslly reported by Teh and Sumaila (2010) up to 20006 where the maximum amount was 45% in the mid-1990s [@Teh].
+The importance of these species exceeds in EEZs like the United States, Peru and Norway where fewer species are responsable for higer landing values (Fig 1).
 
@@
 
-It is not surprising then, that countries within this regions hold the most amount of transboundary species.
-Some African, Asian, and European countries house over 100 species within their EEZs.
-Only the US presents over 100 transboundary species outside those continents, once all three sub-EEZs (Atlantic and Pacific coast as well as Alaska arctic and subarctic) are accounted for (Fig.
-2).
+Transboundary fisheries are vast in regions whith historic fisheries-related conflicts [@Spikjers].
+Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
+Some of these regions have been identified as most conflictive since 1970s with conflicts arrousing to even armed conflicts.
+Moreover, as climate change shifts species distributions and new transboundary species arrose [@Pinsky] as seen in past cases like the Pacific salmon [@REF], or the Macrrell waars [@Spijkers].
+The joint management of shared stocks could be key to not only sustain fisheries into the future but also avoid international conflict [@REF].
+
+Management of shared stocks have to be something.
+Although catch trends do not reflect stock status [@REf_Haters], they can inform provide a panoram of the situation when no other data is available [@Pauly].
+In the case of transboundary species, we did not find a strong pattern suggesting a specific case (Fig 2).
 
 ![**Number of transboundary and discrete species by country and continent**](./Figures/Fig2.png)
-
-<!-- Will run statistics to see if I can show the "why" of trans spp -->
-There is no clear visual pattern regarding transboundary and discrete species, however, from the three countries that house the most amount of discrete stocks, Australia, New Zeland and the US are among the larger in terms of EEZ length, in the other hand, Brazil has only two neighbors along its large latitudinal coast, suggesting not a lot of connection points for sharing species.
-<!-- End of statistics paragraph -->
 

### 2019-11-08 Manuscript_Draft.Rmd
Minor Changes

--- 2019-10-14 Manuscript_Draft.Rmd
@@
 ---
-title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum )"
-authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1^, William W.L. Cheung^1^"
-date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
+title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum)"
+authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
+date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
 # subtitle: "Fish do not need Visas (16/40 character maximum)"
@@
 
-```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+```{r Ch2_setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
   "knitr",
-  "kableExtra"
+  "kableExtra",
+  "png",
+  "grid",
+  "here"
+
 )
@@
 Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua].
-However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy.
-The delimitation of Economic Exclusive Zones (EEZs) virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
+However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy [@Alexa].
+The delimitation of Economic Exclusive Zones (EEZs) in the arly 80's virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
 However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
-In here, we show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.
+In here, we take the most detailed database of marine fished species to show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.
 
@@
 
-![**Number of transboundary species by EEZ and their production by country**](./Figures/Fig1.png)
+```{r Call_Map, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}
+
+img <- readPNG(here("./Figures/Fig1.png"))
+grid.raster(img)
+```
 
@@
 
-![**Number of transboundary and discrete species by country and continent**](./Figures/Fig2.png)
+```{r Call_Country_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary and discrete species by country and continent"}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
 
@@
 
-![**Number of countries shared by transboundary species.** Showing only species that share > 20 countries](./Figures/Fig3.png)
+```{r Call_Spp_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+
+img <- readPNG(here("./Figures/Fig3.png"))
+grid.raster(img)
+```
 

### 2019-11-11 Initial_Analysis.Rmd

@@
     mclapply(
-      Species_List[1:2],
+      Species_List,
       FUN = EstSppStatus,
@@
 # Save data
-# readr::write_csv(Species_Status,
-#           "Species_Status.csv")
+readr::write_csv(Species_Status,
+                 paste(Results_Path,"Species_Status.csv",sep="")
+                 )
 # head(Species_Status)
@@
 # Read Sau Catch Data
-Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
+SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
   filter(!is.na(Territory))
@@
 # Read Sau Value Data (Thank you Tim!)
-Sau_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
+SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
   group_by(fishing_entity_id,TaxonKey=taxon_key) %>% 
@@
 
+# -------------------------- #
 # Number of Transboundary Species
-Total_trans_n <- Clean_Results_Trans %>% 
+# -------------------------- #
+
+Total_trans <- Clean_Results_Trans %>% 
   filter(
@@
     Model_Index >= MI
-  ) %>% 
+  )
+
+Total_trans_n <- Total_trans %>% 
   pull(TaxonKey) %>% 
-  length(unique())
+  unique() %>% 
+  length()
+
+# -------------------------- #
+# Total Revenue
+# -------------------------- #
+
+Total_Trans_Rev <- SAU_Revenue_Data %>% 
+  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
+  group_by() %>% 
+  summarise(Total =sum(Mean_Value)/1000000)# total revenue within EEZs of the world from sau.org
+
+Per_Trans_Rev <- SAU_Revenue_Data %>% 
+  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
+  group_by() %>% 
+  summarise(Total =sum(Mean_Value)/1000000) %>%  # million
+  pull()/160000*100
 
@@
 Status_Data_Plot <- Tresholded_T_Data %>% 
-  mutate(TaxonKey = as.character(TaxonKey)) %>%
+  # mutate(TaxonKey = as.character(TaxonKey)) %>%
   # rename(Territory = CT_fishing_entity) %>% 
-  left_join(Species_Status, 
+  left_join(Status_Data, 
             by =c("Territory","TaxonKey")

### 2019-11-11 Initial_Analysis.Rmd
Updates stock status function to account for multiple years with same catch data

@@
 
-Spp <- 601417
+# Spp <- 601417
 
@@
     top_n(1,RMean) %>% 
-    group_by(TaxonKey,Territory,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl all years)
+    group_by(TaxonKey,Territory,RMean) %>%  # Solves for years with the same Max catch data (e.g. Cayman Isl all years)
     summarise(Year = min(Year)) %>%
@@
     top_n(-1,RMean) %>% # find min value
-    group_by(TaxonKey,Y_Max_Peak,Territory,Max_Peak,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl 2013-2014)
+    group_by(TaxonKey,Y_Max_Peak,Territory,Max_Peak,RMean) %>%  # Solves for years with the same min after peak catch data (e.g. Cayman Isl 2013-2014)
     summarise(Year = min(Year)) %>% 

### 2019-11-11 Initial_Analysis.Rmd
Updates to stauts plot for Vicky analysis

--- 2019-11-11 Initial_Analysis.Rmd
@@
 
-Spp <- 601417
-
-EstSppStatus <- function(Spp,Coord){
+# Spp <- 601417
+
+EstSppStatus <- function(Spp,Coord,Save_Path = "NA", Per_Taxa = F){
 
@@
     arrange(INDEX) %>% 
-    left_join(Index_Code,
+    left_join(Index_Code, # Match species catch with INDEX
               by = "INDEX") %>% 
@@
     summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
-    group_by(TaxonKey,Territory,Year) %>% # Running mean as Pauly et la.
+    group_by(TaxonKey,Territory,Year) %>% # Running mean as Kleisner & Pauly 2012
     mutate(RMean = rollmean(x = Total_Catch, 3,
-                            align = "right",
+                            align = "left",
                             fill = Total_Catch)
@@
 
-  # Determine the final status using the top category over the last 10 years
+  #_______________#
+  # Function Return 
+  #_______________#
+
+  ### Save the data for each species in all years if Per_taxa = T
+
+  if(Per_Taxa == T){
+
+    Save_path <- NA
+
+    if(is.na(Save_path) == TRUE){
+
+      Save_Path <- Results_Path # standar result's path in my Drobo
+    }
+
+    # File name for each species
+    Name <- paste(Save_Path,"Stock_Status/",Spp,"_Status.csv",sep="")
+
+    # Save file for each species
+    write_csv(Status_Data,
+              Data_Name)
+  }else{
+
+    ### Determine the final status using the top category over the last 10 years
+
     Determine_Status_Data <- Status_Data %>% 
@@
 
-  # In this case we sue the last year's category
+    # In case we have a tide, we use the last year's category
     Duplicates_Status <- Status_Data %>% 
@@
 
-  # Function Return
-
     # If both datasets have value RETURN BOTH
@@
     }
+  } # close if per taxa
 }

### 2019-11-11 Manuscript_Draft.Rmd
Updates to intro

@@
 output:
+  word_document:
+    reference_docx: ./Manuscript_Instructions/science_template.docx
   pdf_document:
     fig_caption: yes
-  word_document:
-    reference_docx: ./Manuscript_Instructions/science_template.docx
 geometry: margin=1in
@@
 
-<!-- # Introduction (~600 words) -->
+<!-- # Introduction (~555/500 words) -->
 
@@
 However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
-In here, we take the most detailed database of marine fished species to show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.
 
@@
 While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the transboundary nature of the species [@Teh:2015gd].
-Therefore, 40 years after UNCLOS, the question of how many transboundary species exists in the world is still unanswered.
+And so, despite recent research higlighting the interconnection of marine species [@Nandini], transboundary species are yet to be identified at a global scale.
 This is of uppermost need as the fisheries management approach differs substantially between EEZ-discreet and shared species [@Mills].
 
- <!-- **Results and discussion** (1000 words) -->
+ <!-- **Methods summary** (~140/250 words) -->
 
-We combined a series of datasets and species distribution models to estimate the number of transboundary fished species and their contribution to food security and economics of the world.
-We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species.
-Our results suggest that there are `r Total_trans_n` transboundary species in the world, wich is **something** related to what Caddy (1997) estimated and more than double of that of Teh and Sumaila (2010) [@Teh].
+In here, we overlap the known distribution of **968** marine fish species with XXX Economic Exclusive Zones of  the wrold to map the global number of transboundary species and and their contribution to gloabal catch and landed value.
+We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@TEH].
 
-Tranboundary fisheries are quite important worldwide in terms of both landings and revenue as they are responsable for XXX tones of landings generating USD `r Total_Trans_Rev` million in fishing revenue.
-This represents XX% of the catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world.
+We combined multiple species distribution data-sources and developed a series of criterias to determine if a species was transboundary.
+Current species distributions were obtained from an observational database of world marine species [@REFNEreus], an environmental niche model based on environmental variables and multiple algorithms [@REF], and a species distribution model based on species traits [@Zeler].
+The first criteria to determine if a species is transboundary was to Criteria #1.
+Followed by
+
+our study provides a first empirical approximation to understand the true transboundary nature of the world fisheries, a world that is deeply coonected by larval dynamics [@nandini], fishing fleets [@Kurosawa_Juanito], and shared management [@RFMOS].
+
+<!-- **Results and discussion** (~500/1000 words) -->
+
+As Caddy (1997) pointed out, virtaully all coastal nations share at least one transboundary species with their neighbours, however, some countries share over 100 species with sourronding EZS (Fig.
+1).
+According ot our model, there are a total of `r Total_trans_n` transboundary species in the world, more than double of what had been previouslly estimated [@Teh:2015gd].
+Transboundary fisheries are vast in regions whith historic fisheries-related conflicts [@Spikjers].
+Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
+Some of these regions have been identified as most conflictive since 1970s with conflicts arrousing to even armed conflicts.
+Conflicts over shared resources in these regions include...
+EXAMPLES.
+
+Conflicts in these regions will be exacerabted by climate change.
+As species shift their known distributions to cope with a changing ocean, new transboundary species will arrose, challenging the management of shared stocks worldwide [@Pinsky].
+Climate change has previouslly caused conlfict between important fishing nations such as Canada and the United States over Pacific salmon (*Oriche spp.*) back in the 1980's [@REF], France and Italy over XXX in the 1990's, and more recnetly Iralnd and the European Union over Macrrell (*species*) [@Spijkers].
+The identification of transboundary species is a first step to determine the transboundary nature of a shared stock and establish a joint management plan, key to not only sustain fisheries into the future but also avoid international conflict [@REF].
+
+Tranboundary fisheries are quite important worldwide in terms of both landings and revenue.
+In the last ten years, the global feleet has landed an average of XXX tones, generating USD `r Total_Trans_Rev` million in fishing revenue.
+This represents XX% of the gloabl catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world.
 All these values are higher than previouslly reported by Teh and Sumaila (2010) up to 20006 where the maximum amount was 45% in the mid-1990s [@Teh].
@@
 
-Transboundary fisheries are vast in regions whith historic fisheries-related conflicts [@Spikjers].
-Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
-Some of these regions have been identified as most conflictive since 1970s with conflicts arrousing to even armed conflicts.
-Moreover, as climate change shifts species distributions and new transboundary species arrose [@Pinsky] as seen in past cases like the Pacific salmon [@REF], or the Macrrell waars [@Spijkers].
-The joint management of shared stocks could be key to not only sustain fisheries into the future but also avoid international conflict [@REF].
-
-Management of shared stocks have to be something.
-Although catch trends do not reflect stock status [@REf_Haters], they can inform provide a panoram of the situation when no other data is available [@Pauly].
-In the case of transboundary species, we did not find a strong pattern suggesting a specific case (Fig 2).
+Management of shared stocks have to be improved if we are to achieve the sustainable goals of SDGs...
+Although catch trends do not reflect stock status [@REf_Haters], they can inform provide valuable information of the situation when no other data is available [@Pauly].
+Based on our catch trend clasification, XX% of countries are harvesting their shared stocks between 10 and 50% of the maximum historical catch (Cat, Max.Eplo), followed by XX% harvesting between 10-50% of the maximum historic catch (Cat.), and XX% harvesting something else (Cat.)  (Fig 2).
+Several emipiracal [@REF;@REF;@REF] and modelled studies [@REF;@REF;@REF;] have shown that cooperation will have beeter outcomes for shared fisheries management.
+Blablablabala
 

### 2019-11-11 Initial_Analysis.Rmd
Fixed details on species status function related to the saving part

@@
 
-# Spp <- 601417
-
-EstSppStatus <- function(Spp,Coord,Save_Path = "NA", Per_Taxa = F){
+Spp <- 601417
+Coord = CoorG
+EstSppStatus <- function(Spp,Coord, Save_Path = "NA", Per_Taxa = NA){
 
@@
 
-    Save_path <- NA
-
-    if(is.na(Save_path) == TRUE){
+   # Select onlyZ 
+    Status_Data <- Status_Data %>%
+      ungroup() %>%
+      select(TaxonKey,Territory,Year, Status)
+
+    if(is.na(Save_Path) == TRUE){
 
@@
     # File name for each species
-    Name <- paste(Save_Path,"Stock_Status/",Spp,"_Status.csv",sep="")
+    Name <- paste(Save_Path,Spp,"_Status.csv",sep="")
 
@@
     write_csv(Status_Data,
-              Data_Name)
+              Name)
   }else{
@@
     mclapply(
-      Species_List,
+   Species_List[1:2],
       FUN = EstSppStatus,
-      Coord = CoorG  # Gabriels coordinate system for read species dist
+      Coord = CoorG,  # Gabriels coordinate system for read species dist
+   Per_Taxa = T,
+   Save_Path = "Z:/Vicky/Stock_Status/"
    )

### 2019-11-20 Manuscript_Draft.Rmd
Updates to manuscript

--- 2019-11-11 Manuscript_Draft.Rmd
@@
 ---
-title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum)"
+title: "Title: Fish do not need Visas: the transboundary nature of world fished species"
 authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
@@
 However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy [@Alexa].
-The delimitation of Economic Exclusive Zones (EEZs) in the arly 80's virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
+The delimitation of Economic Exclusive Zones (EEZs) in the early 80's virtually spitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
 However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
-In here, we take the most detailed database of marine fished species to show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.
 
@@
 The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over 200 nautical miles of their coasts [@UN:1982].
-Despite intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management area had no input from biogeography; ignoring species distributions created what we know today as shared stocks [@REF].
+Despite intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas had no input from bio-geography; ignoring species distributions created what we know today as shared stocks.
 The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary, those stocks that are shared by 2 or more neighboring coastal nations; (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas; and (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas.
-
 The origination of shared stocks required the establishment of new fisheries management methods.
-Managers and scientists adopted a game theory approach where collaboration would most likely result in the best overall outcome for nations sharing a common resource [@REF].
+Managers and scientists adopted a game theory approach where collaboration would most likely result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga].
 Lack of collaboration in shared stocks threatens the stock's sustainability [@REF], reduces the profitability potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica?].
-Moreover, new emerging conflicts are expected as climate change shifts the distribution of marine species and new shared fisheries emerge [@Pinsky:2018cb].
 
@@
 While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the transboundary nature of the species [@Teh:2015gd].
-Therefore, 40 years after UNCLOS, the question of how many transboundary species exists in the world is still unanswered.
+And so, despite recent research highlighting the interconnection of marine species [@Nandini], transboundary species are yet to be identified at a global scale.
 This is of uppermost need as the fisheries management approach differs substantially between EEZ-discreet and shared species [@Mills].
+Moreover, international conflicts over shared resources are expected as climate change shifts the distribution of marine species and new shared fisheries emerge [@Pinsky:2018cb].
 
- <!-- **Results and discussion** (1000 words) -->
+ <!-- **Methods summary** (250/250 words) -->
 
-We combined a series of datasets and species distribution models to estimate the number of transboundary fished species and their contribution to food security and economics of the world.
-We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species.
-Our results suggest that there are `r Total_trans_n` transboundary species in the world, wich is **something** related to what Caddy (1997) estimated and more than double of that of Teh and Sumaila (2010) [@Teh].
+In here, we overlap the known distribution of **968** marine fish species with **256** Economic Exclusive Zones of the world to map the number of transboundary species and and their contribution to global catch and landed value.
+We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@TEH].
 
-Tranboundary fisheries are quite important worldwide in terms of both landings and revenue as they are responsable for XXX tones of landings generating USD `r Total_Trans_Rev` million in fishing revenue.
-This represents XX% of the catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world.
-All these values are higher than previouslly reported by Teh and Sumaila (2010) up to 20006 where the maximum amount was 45% in the mid-1990s [@Teh].
-The importance of these species exceeds in EEZs like the United States, Peru and Norway where fewer species are responsable for higer landing values (Fig 1).
+We combined multiple species distribution data-sources and developed a series of criteria to determine if a species was transboundary.
+Current species distributions were obtained from an observational database of world marine species [@REFNEreus] and two structurally different species distribution models [@REFGabs; @Zeler].
+The first criteria to determine if a species is transboundary was related to the agreement of the data-sources regarding the presence of a species in a single grid-cell.
+The second criteria was established to confirm the presence of a species by using a specially detailed catch data [@Zeler].
+Finally, the third criteria accounted for the spatial distribution of the species between the neighboring EEZs.
+In addition to present the number of transboundary stocks, we estimated their contribution in terms of fishing revenue and landings and categorize them depending on their catch trend [@Pauly 2012].
+Our study provides a first empirical approximation to understand the true transboundary nature of the world fisheries, a world that is deeply connected by larval dynamics [@nandini], fishing fleets [@Kurosawa_Juanito], and shared management [@RFMOS].
+
+<!-- **Results and discussion** (~500/1000 words) -->
+
+As Caddy (1997) pointed out, virtually all coastal nations share at least one transboundary species with their neighbors with some sharing over 100 species with surrounding EEZs (Fig.
+1).
+With the current state of knowledge of fished species and their distributions, we estimate a total of `r Total_trans_n` transboundary species in the world, more than double of what had been previously estimated [@Teh:2015gd].
+These fisheries are important in terms of both landings and revenue.
+In the last ten years, the global fleet has landed an average of XXX tones, generating USD `r Total_Trans_Rev` million in fishing revenue from shared stocks fished within EEZs.
+This represents **XX**% of the global catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world.
+All these values are higher than previously estimated [@Teh].
+The importance of these species exceeds in EEZs like the United States where **XX** species are responsible for up to **XX** millions USD and Peru where **17** species are responsible for XXX million USD (Fig 1).
+Transboundary fisheries are vast and economically important in regions with historic fisheries-related conflicts.
+The Asian region has seen 43.0% of all international fisheries conflicts since 2000; Europe, where 11.5% of fishing conflicts occur since 1974s [@Spijkers:2019cz], has been involved in a conflict between Ireland and the European Union over mackerel since 2007 [@Spijkers:2017ij], and finally, the Mediterranean has seen conflicts since the 1980's [@Kliot:1989kv].
+The identification of current transboundary species is a first step towards establishing joint management plan of marine resources [@Link:2010ei], key to not only sustain fisheries but also avoid international conflict.
 
@@
 
-Transboundary fisheries are vast in regions whith historic fisheries-related conflicts [@Spikjers].
-Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1).
-Some of these regions have been identified as most conflictive since 1970s with conflicts arrousing to even armed conflicts.
-Moreover, as climate change shifts species distributions and new transboundary species arrose [@Pinsky] as seen in past cases like the Pacific salmon [@REF], or the Macrrell waars [@Spijkers].
-The joint management of shared stocks could be key to not only sustain fisheries into the future but also avoid international conflict [@REF].
+![**Number of transboundary species by EEZ and their production by country**](./Figures/Fig1.png)
 
-Management of shared stocks have to be something.
-Although catch trends do not reflect stock status [@REf_Haters], they can inform provide a panoram of the situation when no other data is available [@Pauly].
-In the case of transboundary species, we did not find a strong pattern suggesting a specific case (Fig 2).
+The two regions of the world with most shared species (North East and Central Atlantic) present quite different management scenarios.
+For the North East Atlantic, fisheries are managed by the European Union and quotas allocated by species and regulatory area, with some of them (e.g.
+Iceland and Norway) potentially having good fisheries management [@Melnychuk:2017gh].
+In the other hand, fisheries along the west coast of Africa need to be improved, with countries like Nigeria where stock status, management, and enforcement is lacking [@Melnychuk:2017gh].
+Ironically, this region has long been exploited by foreign European fleets with questionable fishing rights systems [@Mills:2004dj] and even some illegal activities [@Belhabib:2015bl].
+Thus, just having joint management plans for shared stocks between neighbors will not be enough to achieve the sustainable goals of SDGs [@].
+Countries need to work together towards a more equitable system of global fishing rights, combat illegal fishing both within their EEZs and outside them, and address global threats such as climate change and overfishing.
 
@@
 
-All species that share over >100 countries are widely distributed pelagic species such as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) with a median of 65, 42, and 38 species per pelagic oceanic, bathymetric and nerictic species, respectively.
-The median for all other ecosystem preferences is under 35 as many of these species are not so widely distribute globally.
+Empirical analysis suggest that cooperation will have better outcomes for shared fisheries management.
+Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*)[@Diekert:2010gp], and between Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+However, few evidence exists today regarding the true efficiency of transboundary fisheries plans.
+Indeed, there are some successful bilateral management plans for species such as Pacific Halibut between Canada and the US as well [@REference?] and multilateral treaties like the Pacific Nauru Agreement that manages 30% of global skipjack tuna in the South Pacific Islands [@Aqorau:2018bh].
+However, the effectiveness of Regional Fisheries Management Organizations, responsible for managing high migratory stocks in areas beyond national jurisdiction, has been previously questioned [@CullisSuzuki:2010fi].
+Countries that are today harvesting species at rates less than 50% of the historical maximum catch (Category C) should be paying extra care in these species (Fig.
+2).
+While these catch trends do not reflect stock status [@@Branch:2011br], they could reassemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
+The rebuilding of a transboundary species could be strongly impacted by uncoordinated efforts of countries harvesting the same species but with different objectives [@Ref].
+
+Management of transboundary fisheries needs to be looking forward.
+As species shift their known distributions to cope with a changing ocean, new transboundary species will arose, challenging the management of shared stocks worldwide [@Pinsky].
+Conflicts in regions with high abundance of transboundary species will likely be exacerbated by climate change, as already seen in the dispute of Ireland and the European Union over Mackerel (*species*) [@Spijkers].
+Understanding how climate change will affect the biogeography of marine species is a key element for proper spatial-based fisheries management, not only at the EEZ level, but also other levels of spatial tools [@Alexa, @Song:2017iua].
+
+Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@REF].
+Maybe not surprisingly, highly migratory pelagic-oceanic species such as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are among the more shared resources in the world with a median of 40 nations sharing these resources.
+These species are very important in terms of economic value as they (global) average revenue exceeds USDXXX.
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these might be cosmopolitan but not necessarily highly migratory (e.g.
+*Solea solea*, *Panulirus argus*) (Fig.
+3).
+However, less distributed species must not be ignored.
+The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even if a population swims between the borders of two nations, their larvae could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+Moreover, many coastal communities, specially in developing regions, and highly dependent on fishing local fish (e.g.
+reef fish) for food security and improved livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf].
 
@@
 ```
+
+![**Number of countries shared by transboundary species. Showing only species that share > 20 countries**](./Figures/Fig3.png)
+
+<!-- Overview of West African fisheries under climate change: Impacts, vulnerabilities and adaptive responses of the artisanal and industrial sectors -->
+<!-- https://www.sciencedirect.com/science/article/pii/S0308597X16302901#bib4 -->
 
@@
 Our method is based on a series of criteria to be met and the overlap of species distributions and the spatial boundary of the world's EEZs.
-For the current analysis we work at the species level and adopt FAO's definition of transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf; @FAO].
+For the current analysis we work at the species level and adopt the Food and Agricultural Organization (FAO) definition of transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf; @FAO].
 All data was scaled at a 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
@@
 Each source represent a different method of estimating the distribution of a given species and thus, provides a more robust result.
-Only those commercial fished species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species, XX% of the reported marine species in the SAU database and XX% of the reported taxa of the FAO (**See S1_Data**).
+Only those commercial fished species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species, 100% of the reported marine species in the SAU database and XX% of the reported taxa of the FAO (**See S1_Data**).
 
@@
 Global environmental conditions were obtained and results averaged from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory's (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
-For each species, we only considered models with an area under the curve larger than 0.7 and outputs from the models were average between *1970* and *2000* [@Asch:2018ca; @Reygondeau:2019uh].
+See [@Asch:2018ca; @Reygondeau:2019uh] for model's details.
 
@@
 the latitudinal region where a species is not seen in between poles) is estimated for each species.
+See [@Close:2006ux; @Palomares:wg] for model's details.
 
@@
   kable("latex", booktabs = T,
-        caption = "Summary table of data sources ussed in the current analysis") %>%
+        caption = "Summary table of data sources used in the current analysis") %>%
   kable_styling(full_width = F) %>%
@@
 
-### Criteria 1; Neighbouring EEZs
+### Criteria 1; Neighboring EEZs
 
@@
 We assume that this would reduce the differences between species and stock as is more likely that neighboring species belong to the same stock, rather than, lets say, Cod in Norway and Canada.
-However, the analysis here presented was kept at the species level.
+However, the analysis here presented was kept at the species level and stocks within countries were not considered.
 
@@
 Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf* *R* package [@SF:package].
-When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appears in more than one sub-region.
+When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appeared in more than one sub-region.
 Species that were present in EEZs that were non-continental territories neighboring other countries were kept (e.g.
@@
 Therefore, all species that were not reported as caught in any single year between the reference years (1970 to 2000) in a given grid-cell were dropped, regardless of the *Species Index*.
-The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, and thus validating the models.
+The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, thus validating the models.
 
@@
 
-Fisheries are important contributors to the world economy and livelihoods.
 We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
@@
 similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-Additionally, we used a previously estimated country-level multiplyer to understand the total direct, indirect, and induced impact of transboundary species on each country [@Dyck:2010ez].
-A continent average was used when no country-level multiplyer was available.
-
-We use the SAU catch data to estimate catch trends over time and determine the potential exploitation status of each species within a EEZ [@Grainger:1996tk; @Kleisner:2011wn].
-Despite a possible overestimation of overexploited and collapsed stocks when using only catch data [@Branch:2011br], this method can still shed a light on stock status when only catch data is available [@FAO:2011vz; @FAO:2018KK; @Kleisner:2011wn].
-However, the results should be seen as potential species status, rather than the true status of each species.
-We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years, and their catch was more than 1,000 tonnes.
-Five categories were drown from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
-Finally, we reported the predominant status over the last ten years of catch data (2004-2014).
+The contribution of transboundary species was done by aggregating the catch of each species that happened within the EEZ of the countries sharing that species.
+For this study, we did not include catch from areas beyong national jurisdiction.
+Finally, we use the catch data to determine the exploitaiton category of each sepcies within a EEZ.
+Although this method has previouslly used to estimate stock status [@Grainger:1996tk; @Kleisner:2011wn], the categories presented here are intended to be seen as catch trends, and not status of each species.
+We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years.
+Three categories were drown from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
+Finally, we reported the predominant category over the last ten years of catch data (2004-2014).
 
@@
 
-Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")
+### Original version
+
+# Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")
+
+# Rules <- c(
+#   "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
+#   "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
+#   "Catch > (Max Catch*0.50)", #Max Exp.
+#   "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
+#   "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
+#   "Non of the above rules applied"
+# )
+
+# data.frame(Stock_Status,
+#            Rules) %>% 
+#   kable("latex", booktabs = T,
+#         caption = "Rules to determine the status of each transboundary species") %>%
+#   kable_styling(full_width = F) %>%
+#   column_spec(1,width = "3cm") %>% #wraps text in column2
+#   column_spec(2,width = "13cm") #%>% #wraps text in column2
+
+### Grouped version
+
+Stock_Status <- c("A - Growing Fishery","B - Stable Fishery"," C - Fishery under 10% of Peak","No Status")
 
 Rules <- c(
-  "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
-  "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
-  "Catch > (Max Catch*0.50)", #Max Exp.
-  "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
-  "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
-  "Non of the above rules applyed"
+  "(Year of Catch > Year Post Max.
+Min.
+& Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50)) or Year of Catch < Year of Max.
+Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Rebuilding or #Developing
+  "Catch > (Max Catch*0.50)", #Max Expploitation
+  "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50) or Catch < Max. Catch*0.10", #Over explpoited or collapsed
+  "Non of the above rules applied"
 )

### 2019-11-20 Manuscript_Draft.Rmd
Draft to share with Colette and Gabriel

@@
 ---
-title: "Title: Fish do not need Visas: the transboundary nature of world fished species"
-authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
+title: "Fish do not need Visas: the transboundary nature of world fished species"
+author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
 date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
+subtitle: "DRAFT DO NOT SHARE"
 # subtitle: "Fish do not need Visas (16/40 character maximum)"
@@
   word_document:
-    reference_docx: ./Manuscript_Instructions/science_template.docx
+    # reference_docx: ./Manuscript_Instructions/science_template.docx
   pdf_document:
@@
   chunk_output_type: console
-bibliography: ./References/FishForVisa_Ref.bib
-csl: ./References/science.csl
+# bibliography: ./References/FishForVisa_Ref.bib
+# csl: ./References/science.csl
 ---
@@
 
-# **One Sentence Summary** (~ 125 characters)
+<!-- # One Sentence Summary (~ 125 characters) -->
 
@@
 
-- Field code: *Fisheries*
+<!-- - Field code: *Fisheries* -->
 
-# **Abstract** (~125 words)
+<!-- # **Abstract** (~125 words) -->
 
@@
 
+# Main Article
 <!-- # Introduction (~555/500 words) -->
@@
 Species are not randomly distributed in the world.
-The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutionary process [@REF].
+The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors  and their influence in the evolutionary process [@Hunch].
 Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua].
@@
 However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
+Answer this question is a key step in creating suitable management plans that allows a sustainable use of marine resources.
 
@@
 Managers and scientists adopted a game theory approach where collaboration would most likely result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga].
-Lack of collaboration in shared stocks threatens the stock's sustainability [@REF], reduces the profitability potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica?].
+Lack of collaboration in shared stocks threatens the stock's sustainability [@REF], reduces the profitability potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica].
+This is also true when considering the emminent impacts of climate change on the distribution of marine species around the globe [@SumailaLamCheung]
 
@@
 
-```{r Call_Map, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}
 
@@
 
-```{r Call_Spp_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+```{r Call_Spp_Circular, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
 
@@
 ![**Number of countries shared by transboundary species. Showing only species that share > 20 countries**](./Figures/Fig3.png)
+
+Transboundary species are globally distributed with some regions presenting a high concentration of shared species.
+Their global contribution to fishing revenue and capture is compelling, with transboundary species playing an important role in many fishing nations.
+Some of these regions like southern Asia and western Africa, are historically marked by fisheries conflicts becoming hotspots for achieving jointly management of shared species.
+Climate change is likely to have important effects in the management of these species as they shift their distributions following their ideal environment.
+Identifying transboundary species within neighboring EEZs is the first step towards a joint management that can result in sustainable fisheries management.
 

### 2019-11-26 Manuscript_Draft.Rmd
FIrst manuscript draft shared with Colette and Gabriel

@@
 editor_options:
-  chunk_output_type: console
+  chunk_output_type: inline
 # bibliography: ./References/FishForVisa_Ref.bib
@@
 
-In here, we overlap the known distribution of **968** marine fish species with **256** Economic Exclusive Zones of the world to map the number of transboundary species and and their contribution to global catch and landed value.
+In here, we overlap the known distribution of **968** marine fish species with 248 Economic Exclusive Zones of 175 countries to map the number of transboundary species and and their contribution to global catch and landed value.
 We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@TEH].
@@
 1).
-With the current state of knowledge of fished species and their distributions, we estimate a total of `r Total_trans_n` transboundary species in the world, more than double of what had been previously estimated [@Teh:2015gd].
+With the current state of knowledge of fished species and their distributions, we estimate a total of 633 transboundary species in the world, more than double of what had been previously estimated [@Teh:2015gd].
 These fisheries are important in terms of both landings and revenue.
-In the last ten years, the global fleet has landed an average of XXX tones, generating USD `r Total_Trans_Rev` million in fishing revenue from shared stocks fished within EEZs.
-This represents **XX**% of the global catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world.
+In the last ten years, the global fleet has landed an average of XXX tones, generating USD 79.7 million in fishing revenue from shared stocks fished within EEZs.
+This represents **X**% of the global catch and 49.8% of total revenue generated by those fisheries in all EEZs of the world.
 All these values are higher than previously estimated [@Teh].
-The importance of these species exceeds in EEZs like the United States where **XX** species are responsible for up to **XX** millions USD and Peru where **17** species are responsible for XXX million USD (Fig 1).
+The importance of these species exceeds in EEZs like the United States where 116 species are responsible for up to 12.20 millions USD and Peru where 28 species are responsible for USD 5.2 million  (Fig 1).
 Transboundary fisheries are vast and economically important in regions with historic fisheries-related conflicts.
@@
            Rules) %>% 
-  kable("latex", booktabs = T,
+  kable(, booktabs = T,
         caption = "Rules to determine the status of each transboundary species") %>%

### 2019-11-27 Initial_Analysis.Rmd
Draft to share with Colette and Gabriel
Updated RFMO analysis for Gabs and included Figure 3 ressolution

@@
   "ggimage", #for reading images to the circular plot
-  # "cowplot",
-  # "rgdal",
-  # "RColorBrewer",
-  # "knitr",
-  # "kableExtra",
   "ggrepel", # for nice plot labels
   "ggsflabel", # for nice sf_plots labels
-  # "gridExtra",
-  # "ggmap",
-  # "rgeos",
-  # "stringr",
-  # "stringer",
   "spdep", # for poly2nb
@@
   "tools", #Spatial analysis 
-  # "png", # For reading plots in chunk codes
-  # "grid" # For reading plots in chunk codes
   "parallel", # for parallelization
@@
 
+Jursidiction <- "EEZ"
+
 # Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
@@
 
-Spp <- 601417
-Coord = CoorG
+# Spp <- 601417
+# Coord = CoorG
+
 EstSppStatus <- function(Spp,Coord, Save_Path = "NA", Per_Taxa = NA){
@@
 # Spp <- 600004  # Anchovie Equator, Chile and Peru
-# Spp <- 600107 # Tuna Many RFMOs
+Spp <- 600107 # Tuna Many RFMOs
+Spp <- 600004 # Argument 1 must have names (RFMO)
 # Spp <- 600464 # Discrete species 
@@
        # 600004) # transboundary spp
-# Model <- "All"
-# Coord <- CoorG
+Model <- "All"
+Coord <- CoorG
 # 
 # # For EEZ
-# Neighbours <- Neighbours_Data
-# Index_Code <- Index_Code
+Neighbours <- Neighbours_Data
+Index_Code <- Index_Code
 
@@
     # Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
+    Non_Transboundary_Data <- fread(paste(Results_Path,"Trans_Results/Non_Transboundary_Data.csv",sep=""))
 
@@
     # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
+    New_Non_Name <- paste(Results_Path,"Trans_Results/Non_Transboundary_Data.csv",sep="")
     write.csv(New_Non, New_Non_Name, row.names = F)
@@
     File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
-    Save_Path <- paste(Results_Path,File_Name,sep="")
-
-    write.csv(Indexes,
-              Save_Path,
-              row.names = F)
+    Save_Path <- paste(Results_Path,"Trans_Results/",File_Name,sep="")
+
+    write_csv(Indexes,
+              Save_Path)
 
@@
 # Set Spceies list
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep="")) %>%
   filter(TaxonKey %in% Species_List)
@@
 )
+
+head(Dis_Trans)
+# Data for Hall with 8 cores on RFMOs
+# user    system   elapsed 
+# 11375.652  3726.515  8342.296
 
@@
 # Load and clean Discrete results
-Non_Transboundary_Data <- fread(paste(Results_Path,"/Non_Transboundary_Data.csv",sep="")) %>% 
+Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
   filter(!is.na(TaxonKey)) %>% 
@@
 
-### Map of Transboundary Species
+### EEZ Map of Transboundary Species
 
@@
        path = Figures_Path
+)
+
+```
+
+### RFMO Map of Transboundary Species
+
+```{r Territory_Map, eval =F, echo =F}
+
+# Transboundary Species shapefile
+World_sf_si <- RFMOs_sf %>%
+  rename(Territory = Name) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
+  left_join(Transboundary_Spp, by ="Territory")
+
+# Total catch/Revenue shapefile
+World_sf_si_land <- World_land_sf %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
+
+# Get the NA's to be grey
+# Grey_land <- World_sf_si_land %>% 
+#   filter(is.na(Bins))
+
+# Make map
+Plot <- ggplot() +
+  # geom_sf(data = World_sf_si_land) +
+  geom_sf(data = World_sf_si,
+          aes(fill =  reorder(Bins_Plot,n_trans_spp)),
+          colour = "grey20", 
+          size = 0.1
+          ) + # n_trans_spp or Bins
+  geom_sf_label(data = World_sf_si,
+                aes(label = Territory)) +
+  # geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
+  # scale_fill_gradientn(colours = pal,
+  #                      na.value = "white") +
+  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
+  # rev(wes_palette(n = 4, name = "Darjeeling2"))
+  # ),
+  # na.value = "white"
+  # ) +
+  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+                                  "#00A08A",#"#00A08A", #green
+                                  "#F2AD00",#"#F2AD00", # Yellow
+                                  # "#F98400",#"#F98400", #Orange
+                                  "#FF0000"#,"#FF0000" #Red
+  ),
+  na.value = "grey"
+  ) +
+  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
+  #                    na.value = "white"
+  # ) +
+  ggtheme_map()
+
+Plot_Name <- paste("RFMO_100_25_Bins.png", sep = "")
+
+ggsave(Plot_Name,
+       plot = Plot,
+       width = 16,
+       height = 8,
+       units = "in"#,
+       # path = Figures_Path
        )
@@
 # Create labels for all but top 5
-label_data <- Countries_Data 
+label_data <- Species_Data 
 number_of_bar <- nrow(label_data)
@@
 Plot_Limit <- max(Species_Data$value,na.rm=T)
+Ticks_Color <- "black"
 
@@
                inherit.aes = FALSE) +
-  ylim(-100,110) + # sets the circle the first value the central the last value how wide
+  ylim(-50,110) + # sets the circle the first value the central the last value how wide
   theme_minimal() +
@@
   plot = last_plot(),
-  width = 12,
-  height = 12,
+  width = 14,
+  height = 13,
   units = "in",
   filename = "Species_circular_over20.png",
-  path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
+  path = Figures_Path
 )

### 2019-11-27 RFMO Analysis.Rmd
Updated RFMO analysis for Gabs and included Figure 3 ressolution

@@
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO",sep="")
+path_world <- paste(Data_Path,"Spatial_Data/","RFMO","/SAU_RFMO",sep="")
 # #The File
@@
   st_transform(3832) # to match shapefiles
+
+###
+head(RFMOs_sf)
+tail(RFMOs_sf)
+
+IPHC <- RFMOs_sf %>% 
+  filter(Name == "IPHC") %>% 
+  st_simplify(1)
+
+ggplot(IPHC) +
+  geom_sf()
 
@@
 
+head(Neighbours_Data)
 # Creates dummy dataset for Non transboundary species
@@
       Save = "Y",  # For saving
-      Catch = "Y",
+      Catch = "N",
       Jurisdiction_Type = Jurisdiction # For saving in proper path

### 2019-11-28 Initial_Analysis.Rmd
Trying to get the RFMO analysis right

@@
 if(Sys.info()[7] == "carmelia"){
-  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
+  Data_Path <- paste(here::here(),"/Temporal_Data",sep = "")
 }

### 2019-11-28 Manuscript_Draft.Rmd
Addressed Coletts changes and comments until Fig 1.

@@
 title: "Fish do not need Visas: the transboundary nature of world fished species"
-author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
-date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
+author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^3^ and William W.L. Cheung^1^"
+date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
 subtitle: "DRAFT DO NOT SHARE"
@@
 output:
+  pdf_document:
+    fig_caption: yes
   word_document:
     # reference_docx: ./Manuscript_Instructions/science_template.docx
-  pdf_document:
-    fig_caption: yes
 geometry: margin=1in
@@
 
-Species are not randomly distributed in the world.
-The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors  and their influence in the evolutionary process [@Hunch].
-Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua].
-However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy [@Alexa].
-The delimitation of Economic Exclusive Zones (EEZs) in the early 80's virtually spitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
-However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered.
-Answer this question is a key step in creating suitable management plans that allows a sustainable use of marine resources.
+Species distribution around the world is not a random process.
+The area in space and time that a species population occupies is a response to the availability of resources, a series of biotic and abiotic factors, as well as their influence on the evolutionary processes [@Hunch].
+Marine resource management is predicated on knowledge of species distributions as human-made spatial boundaries are inherent to existing management systems (e.g., marine protected areas) [@Song:2017iua].
+However, incorporating the concept of species distribution into fisheries management, or policy, is a relatively recent construct [@Alexa].
+The delineation of Economic Exclusive Zones (EEZs) in the early 80s, for instance, virtually established boundaries across the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
+Forty years after their formal adoption, the question of how many shared species exist in the world based on their distribution is still unanswered.
+Fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
+Climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management (@Mills).
+Thus, answering the questions of how many shared stocks exist in the world, and where these are located, is critical to developing effective and resilient management plans for the continued and future sustainable use and conservation of marine resources.
 
-From 1973 to 1982 the members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989].
-The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over 200 nautical miles of their coasts [@UN:1982].
-Despite intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas had no input from bio-geography; ignoring species distributions created what we know today as shared stocks.
-The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary, those stocks that are shared by 2 or more neighboring coastal nations; (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas; and (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas.
-The origination of shared stocks required the establishment of new fisheries management methods.
-Managers and scientists adopted a game theory approach where collaboration would most likely result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga].
-Lack of collaboration in shared stocks threatens the stock's sustainability [@REF], reduces the profitability potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica].
-This is also true when considering the emminent impacts of climate change on the distribution of marine species around the globe [@SumailaLamCheung]
+From 1973 to 1982, members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 miles from shore [@McRaeandMunro1989].
+The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over the exploration and exploitation of marine resources over 200 nautical miles off their coasts [@UN:1982].
+While intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas was not informed by bio-geography, essentially ignoring species distributions and creating what we know today as shared fish stocks [@Gulland, @Munro2002].
+Fish stocks, are comonly refered in fisheries management as a particular population that is more or less isolated from other stocks of the same species and hence self-sustaining [@FAO:1999tk].
+The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary stocks, shared by 2 or more neighboring coastal nations; (*ii*) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (*iii*) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
+The inception of shared stocks called for the establishment of new fisheries management methods.
+Managers and scientists adopted a game theory approach – or means to analyze strategic interactions among decision-makers – which demonstrates that collaboration is most likely to result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga,@Eide:2013dh].
+Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and lead to conflict between coastal nations [@Spijkers:2017ij], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
+Moreover, under climate change, species distributions will shift [@Cheung2016], resulting in new shared stocks [@Pinsky:2018cb] and highlighting the key role cooperative fisheries management can play in maintaining stocks and profitability [@Nguyen:2018dk] as well as hopefully reducing fisheries conflict [@Spijkers:2019cz].
 
-There is a gap in assessing transboundary species in the world based on their spatial distribution.
-It was estimated in 1997 that there could be up to 1,500 transboundary fish species in the world, however, such estimation lacked a proper assessment due to limited information at the time [@Caddy:1997ue].
-More recently, it was estimated there were 344 shared species, representing a capture of 34.2 × 10^6^ t and a global landed value of USD 30.7 × 10^9^ [@Teh:2015gd].
-While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the transboundary nature of the species [@Teh:2015gd].
-And so, despite recent research highlighting the interconnection of marine species [@Nandini], transboundary species are yet to be identified at a global scale.
-This is of uppermost need as the fisheries management approach differs substantially between EEZ-discreet and shared species [@Mills].
-Moreover, international conflicts over shared resources are expected as climate change shifts the distribution of marine species and new shared fisheries emerge [@Pinsky:2018cb].
+There is a gap in assessing the nature and number of transboundary species in the world based on their spatial distribution.
+Caddy [@Caddy:1997ue] in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
+However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
+More recently, Teh et al.
+[@Teh:2015gd] estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
+While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
+Thus, despite recent research highlighting the interconnection of marine species [@Ramesh:2019va], the total number of transboundary species is yet to be identified at a global scale.
+Yet, such an understanding is critical to effectively managing fisheries, as needs differ substantially between discreet and shared species [@Mills] and climate change will yield new challenges associated with new shared fisheries [@Pinsky:2018cb].
 
@@
 
-In here, we overlap the known distribution of **968** marine fish species with 248 Economic Exclusive Zones of 175 countries to map the number of transboundary species and and their contribution to global catch and landed value.
-We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@TEH].
+In this study, we overlay the known distribution of **968** commercially valuable marine fish species and the Exclusive Economic Zones of 175 coastal countries to determine the total number of transboundary species and their contribution to global catch and landed value.
+We adopt the UN definition of transboundary stocks (shared by neighboring EEZs), but carry out the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
 
-We combined multiple species distribution data-sources and developed a series of criteria to determine if a species was transboundary.
-Current species distributions were obtained from an observational database of world marine species [@REFNEreus] and two structurally different species distribution models [@REFGabs; @Zeler].
-The first criteria to determine if a species is transboundary was related to the agreement of the data-sources regarding the presence of a species in a single grid-cell.
-The second criteria was established to confirm the presence of a species by using a specially detailed catch data [@Zeler].
-Finally, the third criteria accounted for the spatial distribution of the species between the neighboring EEZs.
-In addition to present the number of transboundary stocks, we estimated their contribution in terms of fishing revenue and landings and categorize them depending on their catch trend [@Pauly 2012].
-Our study provides a first empirical approximation to understand the true transboundary nature of the world fisheries, a world that is deeply connected by larval dynamics [@nandini], fishing fleets [@Kurosawa_Juanito], and shared management [@RFMOS].
+We combined multiple species distribution data-sources and developed a series of three criteria to determine if a species is transboundary.
+Current species distributions were obtained from the largest observational database of the world’s marine species [@REFNEreus] and two structurally distinct species distribution models [@REFGabs; @Zeler].
+The first criteria to determine the transboundary nature of a species considered the number of data-sources agreeing that a species was present in a single grid-cell.
+Second, we used spatially explicit catch data [@Zeller] to confirm the occurrence of a species in a given grid cell.
+The species was droped if it was present in any specific grid cell, but no catch was record was found.
+The third criteria considered the spatial distribution of species between neighboring EEZs.
+In addition to determining the number of transboundary stocks, we also estimated the contribution of each to fishing revenues and landings as well as categorized them according to catch trends [@Kleisner:2013gh].
+Our study provides a first empirical approximation of the number of shared commercial species globally, significantly contributing to our understanding of the true transboundary nature of world fisheries and hopefully helping inform the effective management of these resources.
 
@@
 
-As Caddy (1997) pointed out, virtually all coastal nations share at least one transboundary species with their neighbors with some sharing over 100 species with surrounding EEZs (Fig.
+We estimate a total of 633 transboundary species in the world, more than double the number previously estimated [@Teh:2015gd] (Fig.
 1).
-With the current state of knowledge of fished species and their distributions, we estimate a total of 633 transboundary species in the world, more than double of what had been previously estimated [@Teh:2015gd].
-These fisheries are important in terms of both landings and revenue.
-In the last ten years, the global fleet has landed an average of XXX tones, generating USD 79.7 million in fishing revenue from shared stocks fished within EEZs.
-This represents **X**% of the global catch and 49.8% of total revenue generated by those fisheries in all EEZs of the world.
-All these values are higher than previously estimated [@Teh].
-The importance of these species exceeds in EEZs like the United States where 116 species are responsible for up to 12.20 millions USD and Peru where 28 species are responsible for USD 5.2 million  (Fig 1).
-Transboundary fisheries are vast and economically important in regions with historic fisheries-related conflicts.
-The Asian region has seen 43.0% of all international fisheries conflicts since 2000; Europe, where 11.5% of fishing conflicts occur since 1974s [@Spijkers:2019cz], has been involved in a conflict between Ireland and the European Union over mackerel since 2007 [@Spijkers:2017ij], and finally, the Mediterranean has seen conflicts since the 1980's [@Kliot:1989kv].
-The identification of current transboundary species is a first step towards establishing joint management plan of marine resources [@Link:2010ei], key to not only sustain fisheries but also avoid international conflict.
+We also find that fisheries on these species contribute substantially to both landings and revenue.
+Between 2010 and 2016, fleets targeting shared stocks within EEZs landed an average of **X** tonnes, representing **X%** of the global catch (within EEZs), and generating USD 79.7 million in fishing revenue, equivalent to 49.8% of total revenue.
+These values are higher than previously estimated [@Teh].
+The importance of these species exceeds in EEZs like the United States where 116 species are responsible for up to 12.20 million USD and Peru where 28 species are responsible for USD 5.2 million (Fig 1).
+
+We found transboundary fisheries to be of substantial economic importance in regions with historic fisheries-related conflicts.
+The Asian region with a total number of **xxx** transboundary species contributing to **xx**% to the region's total landings and **xx**% of total revenue has experienced 43.0% of all documented international fisheries conflicts since 2000 [@Spijkers:2019cz].
+The European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel since 2007 [@Spijkers:2017ij], a species that is transboundary and contributes **xx** to landings and **xx** in revenue to the countries involved in the dispute.
+The Mediterranean, a region that has experienced conflicts since the 1980s [@Kliot:1989kv], is home to a large number of transboundary stocks that contribute **xx**% to total landings and **xx**% of revenue of countries along the Sea's rim.
+The identification of current transboundary species is a first step towards establishing joint management plans for marine resources [@Link:2010ei], key not only to sustain fisheries over the long term, but also to avoid international conflict.
 
@@
 
-![**Number of transboundary species by EEZ and their production by country**](./Figures/Fig1.png)
+![**Number of transboundary species by EEZ and their revenue by country**](./Figures/Fig1.png)
 
-The two regions of the world with most shared species (North East and Central Atlantic) present quite different management scenarios.
-For the North East Atlantic, fisheries are managed by the European Union and quotas allocated by species and regulatory area, with some of them (e.g.
-Iceland and Norway) potentially having good fisheries management [@Melnychuk:2017gh].
-In the other hand, fisheries along the west coast of Africa need to be improved, with countries like Nigeria where stock status, management, and enforcement is lacking [@Melnychuk:2017gh].
-Ironically, this region has long been exploited by foreign European fleets with questionable fishing rights systems [@Mills:2004dj] and even some illegal activities [@Belhabib:2015bl].
-Thus, just having joint management plans for shared stocks between neighbors will not be enough to achieve the sustainable goals of SDGs [@].
-Countries need to work together towards a more equitable system of global fishing rights, combat illegal fishing both within their EEZs and outside them, and address global threats such as climate change and overfishing.
+The two regions of the world that share the most species (the North East and Central Atlantic) have developed quite different approaches to managing shared stocks.
+In the North East Atlantic, fisheries are managed by the European Union and quotas allocated by species and regulatory area, with some of them (e.g., Iceland and Norway) characterized as having good fisheries management [@Melnychuk:2017gh].
+On the other hand, fisheries along the west coast of Africa could benefit from improvements [@Melnychuk:2017gh].
+Ironically, this region has long been exploited by foreign fleets, including European, sometimes illegally [@Belhabib:2015bl], with questionable fishing rights systems [@Mills:2004dj], and unfair fisheries agreements [@Kaczynski & Fluharty 2002].
+Thus, having joint management plans for shared stocks between neighbors will not be enough to achieve sustainable goal 14, Life Below Water [@SDG].
+Countries need to work together towards a more equitable system of global fishing rights.
 
@@
 Management of transboundary fisheries needs to be looking forward.
-As species shift their known distributions to cope with a changing ocean, new transboundary species will arose, challenging the management of shared stocks worldwide [@Pinsky].
-Conflicts in regions with high abundance of transboundary species will likely be exacerbated by climate change, as already seen in the dispute of Ireland and the European Union over Mackerel (*species*) [@Spijkers].
-Understanding how climate change will affect the biogeography of marine species is a key element for proper spatial-based fisheries management, not only at the EEZ level, but also other levels of spatial tools [@Alexa, @Song:2017iua].
+As species shift their known distributions to cope with a changing ocean, new transboundary species will arise, challenging the management of shared stocks worldwide [@Pinsky].
+Conflicts in regions with a high abundance in transboundary species will likely be exacerbated by climate change, as seen in the ongoing dispute between the European Union, Norway, Iceland and the Faroe Islands over mackerel (**species**) [@Spijkers:2017ij].
+Understanding how climate change will affect the biogeography of marine species, and notably the number of countries' EEZ it spans is a key element to the design of effective long-term spatial-based fisheries management [@Alexa, @Song:2017iua].
 
@@
 
-Transboundary species are globally distributed with some regions presenting a high concentration of shared species.
-Their global contribution to fishing revenue and capture is compelling, with transboundary species playing an important role in many fishing nations.
-Some of these regions like southern Asia and western Africa, are historically marked by fisheries conflicts becoming hotspots for achieving jointly management of shared species.
-Climate change is likely to have important effects in the management of these species as they shift their distributions following their ideal environment.
-Identifying transboundary species within neighboring EEZs is the first step towards a joint management that can result in sustainable fisheries management.
+The global contribution of transboundary species to fishing revenue and capture is compelling, with transboundary species playing an important role in many fishing nations.
+Transboundary species have played and continue to play an important role in fisheries conflicts, with climate change likely to exacerbate this trend given expected shifts in species distribution and the emergence of 'new' shared species.
+Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability and can be flexible to accommodate future changes.
 
@@
 
-In here we present a novel method to estimate whether or not a species is transboundary.
-Our method is based on a series of criteria to be met and the overlap of species distributions and the spatial boundary of the world's EEZs.
-For the current analysis we work at the species level and adopt the Food and Agricultural Organization (FAO) definition of transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf; @FAO].
-All data was scaled at a 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
+We present a novel method to determine whether or not a species can be considered transboundary.
+The method is based on a series of criteria to be met and the overlay of species distributions and the spatial boundaries of the world’s EEZs.
+For the current analysis we work at the species level and adopt the Food and consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf; @FAO].
+All data was scaled to 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
 
@@
 
-To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs we first extract all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions.
-For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
+To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we first extracted all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions.
+For this, we used four data sources of species-distributions: (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
 Each source represent a different method of estimating the distribution of a given species and thus, provides a more robust result.
-Only those commercial fished species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species, 100% of the reported marine species in the SAU database and XX% of the reported taxa of the FAO (**See S1_Data**).
+Only commercial fished species with data from all four sources were included in the analysis.
+The final dataset comprised **XXX** species, **XX**% of the reported marine species in the SAU database and **XX**% of the reported taxa of the FAO (**See S1_Data**).
 
-*i* The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+### *Occurence data*
+
+The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+
+### *Distribution models*
 
@@
 
-*ii* The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxtent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
-Environmental variables modeled were sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
-The ENM-Nereus employed all of the observational data-sources previously mention.
-Global environmental conditions were obtained and results averaged from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory's (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
-See [@Asch:2018ca; @Reygondeau:2019uh] for model's details.
+The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+Environmental variables utilized in the models included sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
+The ENM-Nereus employed all of the observational data-sources previously mentioned.
+Global environmental conditions were obtained and results averaged from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
 
-*iii* The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
+The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
 For each commercial fish species, the model first uses the FAO major fishing areas and countries EEZs to determine a broad distribution.
@@
 The range is delimited even further by expert-review polygons and compared with that of AquaMaps [@Kaschner:2016tl], OBIS and GBIF occurrence data.
-The model then determines a species habitat preference based on the assumptions that the relative abundance of a species is determine by the number of habitats in a grid cell and the distance of the species to each habitat, and the importance of the habitat to the species size.
+The model then determines a species habitat preference based on the assumptions that the relative abundance of a species is determined by the number of habitats in a grid cell and the distance of the species to each habitat, as well as the importance of the habitat to the species size.
 Finally, the species equatorial submergence (e.g.
 the latitudinal region where a species is not seen in between poles) is estimated for each species.
-See [@Close:2006ux; @Palomares:wg] for model's details.
+See [@Close:2006ux; @Palomares:wg] for model details.
 
-*iv* The previous models combine observational data with a series of biotic and abiotic information to determine the probability of a species to be in a given space and time.
+### *Catch data*
+
+The previous models combine observational data with a series of biotic and abiotic information to determine the probability that a species will be found in a given space at a given time.
 However, this does not mean that the species in question will actually be there.
-Although the models used have their own methods of double-check species distributions (e.g.
-ENM-Nereus uses four different species distribution algorithms and SPD-SAU verifies with other models), we used a fourth data-source to corroborate the models' outputs.
-The *Sea Around Us* estimates catch that was not originally reported in the FAO database for each country based on all publicly available information sources.
-Fishing catch are also spatially allocated following a country-by-country catch reconstruction and spatial layers according to each species [@Zeller2016].
-Thus, we used the SAU catch reconstruction from 1970 to 2000 as the fourth dataset to estimate transboundary species and was also used to estimate their catch contribution within EEZs (average 1970-2000).
+While the models do use approaches to double-check species occurrences (e.g.
+ENM-Nereus uses four different species distribution algorithms and SPD-SAU undertakes validation by means of other models), we used a fourth data source to corroborate the models’ outputs.
+The *Sea Around Us* estimates total reconstructed catches - i.e., catches  based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in the FAO data available for each country.
+Catches are also spatially allocated [@Zeller2016].
+Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten yeares of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs (average 2005-2014).
 
@@
 Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states.
-In some cases, criteria also work as indexes to measure the uncertainty in the analysis.
-All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* and code is available at https://github.com/jepa/FishForVisa.
+In some cases, criteria also work as indexes to measure the uncertainty in the analysis as they provided continuos index (e.g.
+from 0 to 1) rather than a discrete, yes or no, index .
+All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the pacages *tidiverse*[@],*data.table*[@],*wesanderson*[@],*janitor*[@],*spdep*[@], *sf*[@],*sp*[@],*rgdal*[@],*tools*[@],*parallel*[@],*rfishbase*[@],*zoo*[@].
+All code is available at https://github.com/jepa/FishForVisa.
 
@@
 The contribution of transboundary species was done by aggregating the catch of each species that happened within the EEZ of the countries sharing that species.
-For this study, we did not include catch from areas beyong national jurisdiction.
-Finally, we use the catch data to determine the exploitaiton category of each sepcies within a EEZ.
-Although this method has previouslly used to estimate stock status [@Grainger:1996tk; @Kleisner:2011wn], the categories presented here are intended to be seen as catch trends, and not status of each species.
+For this study, we did not include catch from areas beyond national jurisdiction.
+Finally, we use the catch data to determine the exploitation category of each species within a EEZ.
+Although this method has previously used to estimate stock status [@Grainger:1996tk; @Kleisner:2011wn], the categories presented here are intended to be seen as catch trends, and not status of each species.
 We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years.
-Three categories were drown from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
+Three categories were drawn from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
 Finally, we reported the predominant category over the last ten years of catch data (2004-2014).

### 2019-11-28 Initial_Analysis.Rmd
Commnet out packages not using

@@
   "janitor", # for data cleaning
-  "circlize", # For circular plot
-  "ggimage", #for reading images to the circular plot
-  "ggrepel", # for nice plot labels
-  "ggsflabel", # for nice sf_plots labels
+  # "circlize", # For circular plot
+  # "ggimage", #for reading images to the circular plot
+  # "ggrepel", # for nice plot labels
+  # "ggsflabel", # for nice sf_plots labels
   "spdep", # for poly2nb
@@
   "sp", #Spatial analysis 
-  "purrr",#Spatial analysis
+  # "purrr",#Spatial analysis
   "rgdal", #Spatial analysis
@@
   "parallel", # for parallelization
-  "taxize", # For getting species names
+  # "taxize", # For getting species names
   "rfishbase", # for species ecosystem affinity

### 2019-11-28 Initial_Analysis.Rmd
Included regional analysis as Colette suggested, still missing Catch

@@
            !is.na(Neighbour)) %>% 
-    rename(FishingRegion=Territory) %>% 
+    rename(eez_name=Territory) %>% 
     left_join(Clean_sau_eez_fes,
-              by = "FishingRegion") %>% 
+              by = "eez_name") %>% 
     select(TaxonKey,
-           Territory= FishingRegion,
-           FishingRegion=Neighbour, 
+           Territory= eez_name,
+           eez_name=Neighbour, 
            Model_Index,
@@
     left_join(Clean_sau_eez_fes,
-              by = "FishingRegion") %>% 
+              by = "eez_name") %>% 
     select(1,2, 
-           Neighbour = FishingRegion,
+           Neighbour = eez_name,
            Model_Index:CT_fishing_entity,
@@
 # Species list to get species names
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep=""))
-Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep=""))
+Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep="")) %>% 
+  clean_names()
+
+Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep="")) %>% 
+  clean_names()
 
 # Spatial Data needed to remove duplicates
-sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))
+sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep="")) %>% 
+  clean_names()
 
 Clean_sau_eez_fes <- sau_eez_fes %>% 
-  gather("Type","FishingRegion",2,4) %>% 
+  gather("Type","fishing_region",2,4) %>% 
   left_join(sau_eez_fes,
@@
   ) %>% 
-  group_by(FishingRegion,fishing_entity) %>% 
+  group_by(eez_name,fishing_entity) %>% 
   summarise(n())
@@
 UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
-  group_by(Territory = Country.or.Area,
-           georegion = Region.Name) %>% 
+  clean_names() %>% 
+  group_by(fishing_entity = country_or_area,
+           georegion = region_name,
+           sub_region = sub_region_name) %>% 
   summarise(n=n()) %>% #merge china's 3 rows
   select(-n) %>% 
-  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
+  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
   ungroup() %>% 
@@
   mutate(
-    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
-    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
-    Territory = gsub( "United States of America", "USA",Territory),
-    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
-    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
-    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
-    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
-    # Territory = gsub("Congo", "Congo, R. of",Territory),
-    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
-    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
-    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
-    Territory = gsub(" and ", " & ",Territory),
-    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
-    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
+    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
+    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
+    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
+    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
+    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
+    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
+    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
+    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
+    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
+    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
+    fishing_entity = gsub(" and ", " & ",fishing_entity),
+    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
+    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity)
   )
@@
                          layer =file_path_sans_ext(fnam_world_land)) %>% 
-  rename(Territory = NAME)
+  rename(fishing_entity = NAME)
 
@@
                     layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(Territory = Name)
+  rename(eez_name = Name)
 
@@
 # Read Sau Catch Data
-SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
-  filter(!is.na(Territory))
+# SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
+  # filter(!is.na(Territory))
 
@@
 SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
-  group_by(fishing_entity_id,TaxonKey=taxon_key) %>% 
-  summarise(Mean_Value = mean(value,na.rm=T))
+  clean_names() %>% 
+  group_by(fishing_entity_id,taxon_key) %>% 
+  summarise(mean_value = mean(value,na.rm=T))
 
 # Read Species Status Data (Sub-routine Species Status)
-Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep =""))
+Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep ="")) %>% 
+  clean_names()
 # Status_Data <- Species_Status
@@
 # Clean results susing function CleanResultsfun
-Clean_Results_Trans <- CleanResults(Results_Trans)
+Clean_Results_Trans <- CleanResults(Results_Trans) %>% 
+  clean_names() %>% 
+  rename(eez_name = territory,
+         fishing_entity = ct_fishing_entity,
+         eez_neighbour = neighbour)
 
 # Load and clean Discrete results
-Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
-  filter(!is.na(TaxonKey)) %>% 
-  select(2:3)
+# Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
+#   filter(!is.na(TaxonKey)) %>% 
+#   select(2:3)
 
@@
   filter(
-    Area_Index >= Min_AI,
-    Area_Index <= Max_AI,
-    Model_Index >= MI
+    area_index >= Min_AI,
+    area_index <= Max_AI,
+    model_index >= MI
   )
@@
 ### Non-transboundary Tresh 1
-Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
-  rename(eez_name = Territory) %>% 
-  left_join(sau_eez_fes) %>% 
-  group_by(Territory = fishing_entity) %>% 
-  summarise(value = length(unique(TaxonKey)),
-            Taxons = paste(unique(TaxonKey),collapse = ";"))
+# Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
+#   rename(eez_name = Territory) %>% 
+#   left_join(sau_eez_fes) %>% 
+#   group_by(Territory = fishing_entity) %>% 
+#   summarise(value = length(unique(TaxonKey)),
+#             Taxons = paste(unique(TaxonKey),collapse = ";"))
 
 ## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
-Tresholded_D_Data <- Clean_Results_Trans %>% 
-  filter(Model_Index == MI) %>% 
-  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
-                               ifelse(Area_Index < Min_AI,NA,
-                                      "Transboundary"))
-  ) %>% 
-  filter(!is.na(Species_Type)) %>% 
-  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
-  summarise(n=n()) %>%
-  spread(Species_Type,n) %>% 
-  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
-  gather("Species_Type","value", Discrete:Transboundary) %>% 
-  filter(!is.na(value),
-         Species_Type == "Discrete") %>% 
-  group_by(Territory = CT_fishing_entity) %>% 
-  summarise(value = length(unique(TaxonKey)),
-            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
-  #  Include discrete species of Trsh. 1
-  bind_rows(Clean_Non_Transboundary_Data) %>%
-  # Data cleaning (group by territory and include georegions for plot)
-  rename(FishingRegion=Territory) %>% 
-  left_join(Clean_sau_eez_fes) %>% 
-  group_by(Territory = fishing_entity)
+# Tresholded_D_Data <- Clean_Results_Trans %>% 
+#   filter(Model_Index == MI) %>% 
+#   mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
+#                                ifelse(Area_Index < Min_AI,NA,
+#                                       "Transboundary"))
+#   ) %>% 
+#   filter(!is.na(Species_Type)) %>% 
+#   group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
+#   summarise(n=n()) %>%
+#   spread(Species_Type,n) %>% 
+#   mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
+#   gather("Species_Type","value", Discrete:Transboundary) %>% 
+#   filter(!is.na(value),
+#          Species_Type == "Discrete") %>% 
+#   group_by(Territory = CT_fishing_entity) %>% 
+#   summarise(value = length(unique(TaxonKey)),
+#             Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
+#   #  Include discrete species of Trsh. 1
+#   bind_rows(Clean_Non_Transboundary_Data) %>%
+#   # Data cleaning (group by territory and include georegions for plot)
+#   rename(FishingRegion=Territory) %>% 
+#   left_join(Clean_sau_eez_fes) %>% 
+#   group_by(Territory = fishing_entity)
 
@@
 Total_trans_n <- Total_trans %>% 
-  pull(TaxonKey) %>% 
+  pull(taxon_key) %>% 
   unique() %>% 
@@
 Total_Trans_Rev <- SAU_Revenue_Data %>% 
-  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
+  filter(taxon_key %in% Total_trans$taxon_key) %>% 
   group_by() %>% 
-  summarise(Total =sum(Mean_Value)/1000000)# total revenue within EEZs of the world from sau.org
+  summarise(Total =sum(mean_value)/1000000)# total revenue within EEZs of the world from sau.org
 
 Per_Trans_Rev <- SAU_Revenue_Data %>% 
-  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
+  filter(taxon_key %in% Total_trans$taxon_key) %>% 
   group_by() %>% 
-  summarise(Total =sum(Mean_Value)/1000000) %>%  # million
+  summarise(Total =sum(mean_value)/1000000) %>%  # million
   pull()/160000*100
@@
 Transboundary_Spp <- Tresholded_T_Data %>% 
-  group_by(Territory) %>% 
+  group_by(eez_name) %>% 
   summarise(
-    n_trans_spp = length(unique(TaxonKey)),
-    n_Neighbours = length(unique(Neighbour)),
-    Trans_Rate = n_trans_spp/n_Neighbours
+    n_trans_spp = length(unique(taxon_key)),
+    n_neighbours = length(unique(eez_neighbour)),
+    trans_Rrate = n_trans_spp/n_neighbours
   ) %>% 
@@
 
-Tresholded_T_Data_x <- Tresholded_T_Data %>% 
-  select(TaxonKey, Territory=CT_fishing_entity)
-
 Revenue_Country <- sau_eez_fes %>% 
-  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
+  group_by(fishing_entity_id, fishing_entity) %>% 
   summarise(n=n()) %>% 
   select(-n) %>% 
-  left_join(Tresholded_T_Data_x) %>% 
-  left_join(Sau_Revenue_Data) %>% 
-  group_by(Territory) %>% 
-  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% # Million of USD
-  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
+  full_join(Tresholded_T_Data,
+            by = "fishing_entity") %>% 
+  group_by(fishing_entity_id,
+           fishing_entity,
+           taxon_key) %>% 
+  summarise(n()) %>% 
+  left_join(SAU_Revenue_Data,
+            by = c("fishing_entity_id","taxon_key")) %>% 
+  group_by(fishing_entity) %>% 
+  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
+  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",fishing_entity),
          Bins = cut(Total_USD,breaks = 4),
@@
   filter(Total_USD > 0)
+
+```
+
+```{r Data_per_Continent, eval = F, echo = F}
+
+Continent_Data <- Revenue_Country %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+  group_by(sub_region) %>% 
+  summarise_if(is.numeric,sum,na.rm=T)
+
+Continent_Data_Trans <- Tresholded_T_Data %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+  group_by(sub_region) %>% 
+  summarise(
+    n_trans_spp = length(unique(taxon_key))
+  ) %>% 
+  left_join(Continent_Data) %>% 
+  mutate(id = seq(1,nrow(Continent_Data_Trans)))
+
+### Prepare data for plot
+
+number_of_bar <- nrow(Continent_Data_Trans)
+
+label_data <- Continent_Data_Trans %>% 
+  arrange(Total_USD) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,nrow(Continent_Data_Trans)),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Latin America &\nthe Caribbean",paste(sub_region))
+  )
+
 ```
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="Territory")
+  left_join(Transboundary_Spp, by ="eez_name")
 
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-  left_join(Revenue_Country, by ="Territory")
+  left_join(Revenue_Country, by ="fishing_entity")
 
@@
 # Make map
-Plot <- ggplot() +
+Map <- ggplot() +
   geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
@@
   ggtheme_map()
+
+####___________________________###
+### Now create the Two circluar bar plots
+####___________________________###
+
+# Revenue Plot
+# Set plot limits
+min_lim <- min(Continent_Data_Trans$Total_USD)
+max_lim <-max(Continent_Data_Trans$Total_USD)
+
+# Set color pal
+pal <- wes_palette("Zissou1",100,type = "continuous")
+
+Rev_Plot <- ggplot(data = Continent_Data_Trans, 
+       aes(x=reorder(id,Total_USD),
+           y=Total_USD, 
+           fill=Total_USD
+           )
+       ) +    
+  ylim(-1500, max_lim+10)+
+  geom_bar(stat="identity") +
+  theme_minimal() +
+  theme(
+    # legend.position = c(0.80,0.50),
+    legend.position = "",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = margin(0,-10,-5,-10,"cm")
+  )  +
+  # Base line
+  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
+               colour = "black", size=0.1, inherit.aes = FALSE) +
+  coord_polar(start = 0) + 
+  geom_text(data=label_data, 
+            aes(x=id,
+                y=Total_USD+10,
+                # label=round(Total_USD_Billion),
+                label=sub_region,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
+            size=2, 
+            angle= label_data$angleb, 
+            inherit.aes = FALSE) +
+  scale_fill_gradientn("Billion USD",
+                       colours = pal)
+
+### Catch plot
+
+Catch_Plot <- ggplot(data = Continent_Data_Trans, 
+       aes(x=reorder(id,Total_USD),
+           y=Total_USD, 
+           fill=Total_USD
+           )
+       ) +    
+  ylim(-1500, max_lim+10)+
+  geom_bar(stat="identity") +
+  theme_minimal() +
+  theme(
+    # legend.position = c(0.80,0.50),
+    legend.position = "",
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = margin(0,-10,-5,-10,"cm")
+  )  +
+  # Base line
+  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
+               colour = "black", size=0.1, inherit.aes = FALSE) +
+  coord_polar(start = 0) + 
+  geom_text(data=label_data, 
+            aes(x=id,
+                y=Total_USD+10,
+                # label=round(Total_USD_Billion),
+                label=sub_region,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
+            size=2, 
+            angle= label_data$angleb, 
+            inherit.aes = FALSE) +
+  scale_fill_gradientn("Tons",
+                       colours = pal)
+
+## Joining everything in one ploit
+
+# library(ggpubr)
+# library(cowplot)
+
+plot <- ggdraw() +
+  # map
+  draw_plot(Map, x = 0, y = 0.4, width = 1, height = 0.6) +
+  # Revenue circular
+  draw_plot(Rev_Plot, x = 0.05, y = 0.1, width = 0.5, height = 0.4) +
+  # Catch circular
+  draw_plot(Catch_Plot, x = 0.5, y = 0.1, width = 0.5, height = 0.4) +
+
+  # Labeks
+  draw_plot_label(label = c("A", "B", "C"), 
+                  size = 30,
+                  x = c(0.1, 0.1, 0.56), 
+                  y = c(1, 0.45, 0.45)
+  )
+
+save_plot("Plot2.png",
+          plot,
+          base_height = 8,
+          base_width = 13)
 

### 2019-11-28 Initial_Analysis.Rmd
Fixed the last name issues with the map

@@
 
-### Non-transboundary Tresh 1
-# Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
-#   rename(eez_name = Territory) %>% 
-#   left_join(sau_eez_fes) %>% 
-#   group_by(Territory = fishing_entity) %>% 
-#   summarise(value = length(unique(TaxonKey)),
-#             Taxons = paste(unique(TaxonKey),collapse = ";"))
-
-## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
-# Tresholded_D_Data <- Clean_Results_Trans %>% 
-#   filter(Model_Index == MI) %>% 
-#   mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
-#                                ifelse(Area_Index < Min_AI,NA,
-#                                       "Transboundary"))
-#   ) %>% 
-#   filter(!is.na(Species_Type)) %>% 
-#   group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
-#   summarise(n=n()) %>%
-#   spread(Species_Type,n) %>% 
-#   mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
-#   gather("Species_Type","value", Discrete:Transboundary) %>% 
-#   filter(!is.na(value),
-#          Species_Type == "Discrete") %>% 
-#   group_by(Territory = CT_fishing_entity) %>% 
-#   summarise(value = length(unique(TaxonKey)),
-#             Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
-#   #  Include discrete species of Trsh. 1
-#   bind_rows(Clean_Non_Transboundary_Data) %>%
-#   # Data cleaning (group by territory and include georegions for plot)
-#   rename(FishingRegion=Territory) %>% 
-#   left_join(Clean_sau_eez_fes) %>% 
-#   group_by(Territory = fishing_entity)
-
 ```
@@
   group_by(fishing_entity_id, fishing_entity) %>% 
-  summarise(n=n()) %>% 
+  summarise(n=n()) %>% # Get all of the fishing entity and id
   select(-n) %>% 
@@
            taxon_key) %>% 
-  summarise(n()) %>% 
+  summarise(n()) %>% # get each taxa per nation
   left_join(SAU_Revenue_Data,
             by = c("fishing_entity_id","taxon_key")) %>% 
-  group_by(fishing_entity) %>% 
+  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
   summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
-  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",fishing_entity),
+  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
+                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
          Bins = cut(Total_USD,breaks = 4),
@@
 
-save_plot("Plot2.png",
+Plot_Name <- paste("100_25_Bins_Value_Region.png", sep = "")
+
+save_plot(Plot_Name,
           plot,
@@
           base_width = 13)
-
-Plot_Name <- paste("New_100_25_Bins_Value.png", sep = "")
 
@@
 #
+
+```
+
+### Fixing Russia Moneeeeey
+
+```{r russia}
+
+# Shapefile names
+Russia_Sf <- World_land_sf %>% 
+  filter(str_detect(fishing_entity,"Russia")) %>% 
+  pull(fishing_entity)
+
+"Russia"
+
+Russia_Trans <- Revenue_Country %>% 
+  filter(str_detect(fishing_entity,"Russia")) %>% 
+  pull(fishing_entity)
+
+"Russian Federation"
+### Laptev and Chukchi are the issue, No Alaska'?
+
+### Wake
+Wake_ssf <- World_sf %>% 
+  filter(str_detect(eez_name,"Wake")) %>% 
+  pull(eez_name)
+
+"Wake Isl. (USA)"
+
+Wake_Trans <- Transboundary_Spp %>% 
+  filter(str_detect(eez_name,"Wake")) %>% 
+  pull(eez_name)
+
+"NA"
+
+Wake_Tresh <- Tresholded_T_Data %>% 
+  filter(str_detect(eez_name,"Wake")) %>% 
+  pull(eez_name)
+
+"NA"
+
+Wake_Raw <- Clean_Results_Trans %>% 
+  filter(str_detect(eez_name,"Wake"))
+
+#### Son todas under 25%.... Por eso
+
+#### Macquarie Island
+Macquarie_Raw <- Clean_Results_Trans %>% 
+  filter(str_detect(eez_name,"Macquarie"))
+
+# Under 25% Bye
+
+### Minomi
+
+Neighbours_Data %>% 
+  filter(str_detect(Territory,"Japan")) %>% 
+  pull(Territory) %>% 
+  unique()
+
+# Not in our shaopefile
 

### 2019-11-28 Initial_Analysis.Rmd
Created and ran function to get catch data for regional plot and supplemental map

@@
 
+## Create Transboundary Catch Database
+
+### Function `EstCatch`
+
+This function just creates a database of total catch per species within each EEZ
+
+```{r EstCatch, eval = F, echo = T}
+
+EstCatch <- function(Spp, Coord, Index_Code){
+
+  SppDist <- GetSppDist(Spp,Model="All",Coord) %>% 
+    filter(
+      Model == "SAU_C",
+      Value > 0) %>% 
+    left_join(Index_Code,
+              by = "INDEX") %>% 
+    group_by(eez_name = Territory,
+             taxon_key = TaxonKey) %>% 
+    summarise(total_catch = sum(Value))
+
+  return(SppDist)
+
+}
+
+# EstCatch(Spp,Coord,Index_Code)
+
+```
+
+```{r control_panel, eval = F, echo = T}
+
+# Removes everything before the number
+Step_One <- gsub(".*_","",list.files(paste(Data_Path,"/Distribution_Data/SAU_data_per_species/",sep="")))
+
+# Species List
+Species_List <- gsub("\\..*","",Step_One)
+
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+```
+
+```{r catch, eval = F, echo = T}
+# Notes, needs GetSppDist
+# Note, It averages the LAST 10 years oe ach gridcell and then adds them together
+
+system.time(
+  SAU_Catch_Data <- bind_rows(
+    mclapply(
+      Species_List,
+      FUN = EstCatch,
+      Coord = CoorG,  # Gabriels coordinate system for read species dist
+      Index_Code = Index_Code
+    )
+  )
+)
+
+# Save dataframe for future
+Save_Path <- paste(Data_Path,"Distribution_Data/sau_catch_country_taxon.csv",sep="")
+write_csv(SAU_Catch_Data,
+          Save_Path)
+
+```
+
 ## Estimate Transboundary Species
@@
 # Spp <- 600004  # Anchovie Equator, Chile and Peru
-Spp <- 600107 # Tuna Many RFMOs
-Spp <- 600004 # Argument 1 must have names (RFMO)
+# Spp <- 600107 # Tuna Many RFMOs
+# Spp <- 600004 # Argument 1 must have names (RFMO)
 # Spp <- 600464 # Discrete species 
@@
        # 600004) # transboundary spp
-Model <- "All"
-Coord <- CoorG
+# Model <- "All"
+# Coord <- CoorG
 # 
 # # For EEZ
-Neighbours <- Neighbours_Data
-Index_Code <- Index_Code
+# Neighbours <- Neighbours_Data
+# Index_Code <- Index_Code
 
@@
     fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
-    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    # fishing_entity = gsub( "United States of America", "USA",fishing_entity),
     fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
@@
     # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
-    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity)
+    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
+    fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
   )
@@
   mutate(
-    sub_region = ifelse(str_detect(sub_region,"Latin"),"Latin America &\nthe Caribbean",paste(sub_region))
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Latin America &\nthe Caribbean",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                        paste(sub_region))
+    )
   )
@@
   # Revenue circular
-  draw_plot(Rev_Plot, x = 0.05, y = 0.1, width = 0.5, height = 0.4) +
+  draw_plot(Rev_Plot, x = 0.1, y = 0.1, width = 0.5, height = 0.4) +
   # Catch circular
-  draw_plot(Catch_Plot, x = 0.5, y = 0.1, width = 0.5, height = 0.4) +
+  draw_plot(Catch_Plot, x = 0.45, y = 0.1, width = 0.5, height = 0.4) +
 
@@
                   size = 30,
-                  x = c(0.1, 0.1, 0.56), 
+                  x = c(0.1, 0.1, 0.5), 
                   y = c(1, 0.45, 0.45)
@@
 
-Plot_Name <- paste("100_25_Bins_Value_Region.png", sep = "")
-
-save_plot(Plot_Name,
+# Plot_Name <- paste("100_25_Bins_Value_Region.png", sep = "")
+
+save_plot("Plot.png",
           plot,

### 2019-11-29 Initial_Analysis.Rmd
Completed Figure one with circular regional contributions

@@
     legend.position = "bottom",
-    legend.key.width =unit(6,"line")
+    legend.key.width =unit(5,"line")
   )
@@
 
-## Create Transboundary Catch Database
+## Get Catch Data
 
@@
 
+### Sub routine for catch data
+
 ```{r control_panel, eval = F, echo = T}
@@
 
-```{r catch, eval = F, echo = T}
+```{r subroutine_get_catch_data, eval = F, echo = T}
 # Notes, needs GetSppDist
@@
 # Read Sau Catch Data
-# SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
-  # filter(!is.na(Territory))
+SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_country_taxon.csv", sep =""))
 
@@
   pull()/160000*100
+
+# -------------------------- #
+# Total Catch
+# -------------------------- #
+
+Total_Trans_Catch <- SAU_Catch_Data %>% 
+  filter(taxon_key %in% Total_trans$taxon_key) %>% 
+  group_by() %>% 
+  summarise(Total =sum(total_catch)/1000000) %>%  # total revenue within EEZs of the world from sau.org
+  pull()
+
+Global_Catch <- 108 # million (estimated from sau.com)
+
+Per_Catch <- (Total_Trans_Catch/Global_Catch)*100
 
@@
 
-# Get Catch data for mapping (Currently not used)
-
-# Catch_Country <- Sau_Catch_Data %>% 
-#   group_by(FishingRegion=Territory) %>% 
-#   summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
-#   filter(!(is.na(FishingRegion))) %>% 
-#   left_join(Clean_sau_eez_fes) %>% 
-#   group_by(Territory = fishing_entity) %>% 
-#   summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
-#   mutate(Territory = gsub("USA","United States of America",Territory))
+# Get Catch data for mapping (Supplemental materials)
+
+Catch_Country <- SAU_Catch_Data_b %>%
+  group_by(eez_name) %>%
+  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>%
+  group_by(fishing_entity) %>%
+  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million
+  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
+                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
+         Bins = cut(fishing_entity_catch,breaks = 4),
+         Bins_Plot = cut(fishing_entity_catch,breaks = 4,
+                         labels = c('super low', 'low','high','super high'))
+  ) %>% 
+  filter(fishing_entity_catch > 0)
 
@@
 
+### Catch Data
+
+# Catch_Country
+
+### Revenue Data
 Continent_Data <- Revenue_Country %>% 
+  left_join(Catch_Country,
+             by = "fishing_entity") %>% 
   left_join(UN_Regions,
@@
 
+# Fix names for plot
+Continent_Data_Trans$sub_region <- Continent_Data_Trans$sub_region %>% 
+  gsub("Northern","N.",.) %>% 
+  gsub("Southern","S.",.) %>% 
+  gsub("Western","W.",.) %>% 
+  gsub("Eastern","E.",.)
+
 ### Prepare data for plot
@@
 
-label_data <- Continent_Data_Trans %>% 
+label_data_rev <- Continent_Data_Trans %>% 
   arrange(Total_USD) %>% # soo it looks like a nice snail :)
@@
   mutate(
-    sub_region = ifelse(str_detect(sub_region,"Latin"),"Latin America &\nthe Caribbean",
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                         ifelse(sub_region =="Northern America","Northern\nAmerica",
@@
 
+label_data_catch <- Continent_Data_Trans %>% 
+  arrange(fishing_entity_catch) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,nrow(Continent_Data_Trans)),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region))
+    )
+  )
+
 ```
@@
 
-```{r Territory_Map, eval =F, echo =F}
+```{r Territory_Map_Round, eval =F, echo =F}
 
@@
   filter(is.na(Bins))
+
+# Create labels for legend
+Labels_Trans <- c(paste(unique(Transboundary_Spp$Bins)),"NA")
+Labels_Rev <- unique(Revenue_Country$Bins)
 
@@
   # ) +
-  ggtheme_map()
+  ggtheme_map() +
+  # Transboundary labels
+  annotate("text", 
+           x =(c(-95,-36,21,80,146)+4),
+           y = -93.5,
+           label = Labels_Trans, 
+           color="black", 
+           size=3, 
+           angle=0, 
+           # fontface="bold",
+           hjust=0) +
+  # Revenue labels
+  annotate("text", 
+           x =c(-100,-48,12,69),
+           y = -110,
+           label = Labels_Rev, 
+           color="black", 
+           size=3, 
+           angle=0, 
+           # fontface="bold",
+           hjust=0) +
+  # Legend Titles
+  annotate("text", 
+           x =-190,
+           y = -93.5,
+           label = "Transboundary Spp. (n)", 
+           color="black", 
+           size=3, 
+           angle=0, 
+           fontface="bold",
+           hjust=0) +
+  annotate("text", 
+           x =-190,
+           y = -110,
+           label = "Revenue (Million USD)", 
+           color="black", 
+           size=3, 
+           angle=0, 
+           fontface="bold",
+           hjust=0) +
+  theme(
+    legend.box.margin = margin(t = -54, l = 130),
+    legend.text = element_blank()#,
+  )
+
+# Map
 
@@
 # Set plot limits
-min_lim <- min(Continent_Data_Trans$Total_USD)
-max_lim <-max(Continent_Data_Trans$Total_USD)
+max_lim <- max(Continent_Data_Trans$Total_USD)
 
@@
   theme(
-    # legend.position = c(0.80,0.50),
-    legend.position = "",
+    legend.position = c(0.74,0.60),
     axis.text = element_blank(),
@@
     panel.grid = element_blank(),
-    plot.margin = margin(0,-10,-5,-10,"cm")
+    plot.margin = margin(0,-10,-6,-10,"cm")
   )  +
@@
   coord_polar(start = 0) + 
-  geom_text(data=label_data, 
+  geom_text(data=label_data_rev, 
             aes(x=id,
@@
             inherit.aes = FALSE) +
-  scale_fill_gradientn("Billion USD",
-                       colours = pal)
+  scale_fill_gradientn("",
+                       colours = pal) +
+  guides(fill = guide_colorbar(label.position = "left")
+  )
 
@@
 
+max_lim <- max(Continent_Data_Trans$fishing_entity_catch)
+
 Catch_Plot <- ggplot(data = Continent_Data_Trans, 
-       aes(x=reorder(id,Total_USD),
-           y=Total_USD, 
-           fill=Total_USD
+                     aes(x=reorder(id,fishing_entity_catch),
+                         y=fishing_entity_catch, 
+                         fill=fishing_entity_catch
                      )
 ) +    
-  ylim(-1500, max_lim+10)+
+  ylim(-1.5, max_lim+1) +
   geom_bar(stat="identity") +
@@
   theme(
-    # legend.position = c(0.80,0.50),
-    legend.position = "",
+    legend.position = c(0.1,0.60),
+    # legend.position = "right",
     axis.text = element_blank(),
@@
     panel.grid = element_blank(),
-    plot.margin = margin(0,-10,-5,-10,"cm")
+    plot.margin = margin(0,-10,-6,-5,"cm")
+    # plot.margin = margin(0,0,-5,0,"cm")
   )  +
   # Base line
-  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
+  geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
                colour = "black", size=0.1, inherit.aes = FALSE) +
   coord_polar(start = 0) + 
-  geom_text(data=label_data, 
+  geom_text(data=label_data_catch, 
             aes(x=id,
-                y=Total_USD+10,
+                y=fishing_entity_catch+0.1,
                 # label=round(Total_USD_Billion),
@@
             inherit.aes = FALSE) +
-  scale_fill_gradientn("Tons",
+  scale_fill_gradientn("",
                        colours = pal)
+
+# Catch_Plot
 
@@
   # map
-  draw_plot(Map, x = 0, y = 0.4, width = 1, height = 0.6) +
+  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
   # Revenue circular
-  draw_plot(Rev_Plot, x = 0.1, y = 0.1, width = 0.5, height = 0.4) +
+  draw_plot(Rev_Plot, x = 0.1, y = 0.07, width = 0.5, height = 0.4) +
   # Catch circular
-  draw_plot(Catch_Plot, x = 0.45, y = 0.1, width = 0.5, height = 0.4) +
+  draw_plot(Catch_Plot, x = 0.45, y = 0.07, width = 0.5, height = 0.4) +
 
   # Labeks
-  draw_plot_label(label = c("A", "B", "C"), 
-                  size = 30,
-                  x = c(0.1, 0.1, 0.5), 
-                  y = c(1, 0.45, 0.45)
-  )
-
-# Plot_Name <- paste("100_25_Bins_Value_Region.png", sep = "")
-
-save_plot("Plot.png",
+  draw_plot_label(label = c("A", "B"), 
+                  size = 20,
+                  x = c(0, 0), 
+                  y = c(1, 0.45)
+  ) +
+  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
+                  size = 8,
+                  x = c(0.333,0.493), 
+                  y = c(0.30,0.28)
+  )
+
+save_plot(paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
           plot,
           base_height = 8,
-          base_width = 13)
-
-ggsave(Plot_Name,
-       plot = Plot,
-       width = 16,
-       height = 8,
-       units = "in",
-       path = Figures_Path
-)
+          base_width = 8)
 

### 2019-11-29 Initial_Analysis.Rmd
Updates clean results function

@@
     filter(Same_Nation == "No") %>% 
-    select(-8,-9) %>% 
+    select(-8,-9)
+
     # Fix coding issues between MAC and Windows
-    mutate(
-    Territory = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Territory),
-    Territory = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Territory),
-    Territory = gsub("R<e9>union (France)","Réunion",Territory),
-    Neighbour = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Neighbour),
-    Neighbour = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Neighbour),
-    Neighbour = gsub(" R<e9>union (France)","Réunion",Neighbour)
-    )
+
+  Clean_Results$Territory <- Clean_Results$Territory %>% 
+    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
+    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
+    gsub("R<e9>union (France)","Réunion",.)
+
+  Clean_Results$Neighbour <- Clean_Results$Neighbour %>% 
+    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
+    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
+    gsub(" R<e9>union (France)","Réunion",.)
+
+  Clean_Results$CT_fishing_entity <- Clean_Results$CT_fishing_entity %>% 
+    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
+    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
+    gsub(" R<e9>union (France)","Réunion",.)
 
@@
 
-Catch_Country <- SAU_Catch_Data_b %>%
+Catch_Country <- SAU_Catch_Data %>%
   group_by(eez_name) %>%
@@
   group_by(fishing_entity) %>%
-  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million
+  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million tones
   mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
@@
 
-save_plot(paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
+save_plot(
+  # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
+  "Plot.png",
   plot,
   base_height = 8,
-          base_width = 8)
+  base_width = 8
+)
 

### 2019-12-16 Manuscript_Draft.Rmd
Updates to draft

@@
 output:
+  word_document:
+    # reference_docx: ./Manuscript_Instructions/science_template.docx
   pdf_document:
     fig_caption: yes
-  word_document:
-    # reference_docx: ./Manuscript_Instructions/science_template.docx
 geometry: margin=1in
@@
 We estimate a total of 633 transboundary species in the world, more than double the number previously estimated [@Teh:2015gd] (Fig.
-1).
+1A).
 We also find that fisheries on these species contribute substantially to both landings and revenue.
-Between 2010 and 2016, fleets targeting shared stocks within EEZs landed an average of **X** tonnes, representing **X%** of the global catch (within EEZs), and generating USD 79.7 million in fishing revenue, equivalent to 49.8% of total revenue.
+Between 2005 and 2014, fleets targeting shared stocks within EEZs landed an average of 69 million tonnes, representing around 64% of the global catch (within EEZs), and generating USD 79.7 million in fishing revenue, equivalent to 49.8% of total revenue.
 These values are higher than previously estimated [@Teh].
-The importance of these species exceeds in EEZs like the United States where 116 species are responsible for up to 12.20 million USD and Peru where 28 species are responsible for USD 5.2 million (Fig 1).
+Transboundary species are particularly important in terms of catch and revenue in regions of the world like Eastern Asia and Latin America and the Caribbean (Fig 1B).
+Particular in Northern America (Bermuda, Canada, Greenland, and the US), a moderate amount of catch (3.4 thousand tons) are worth 11.7 billion USD, highlighting the importance of transboundary species to the economy of the region.
+This is the case of the US where 116 species are responsible for up to 12.20 million USD and Peru where 28 species are responsible for USD 5.2 million (Fig 1A).
 
-We found transboundary fisheries to be of substantial economic importance in regions with historic fisheries-related conflicts.
-The Asian region with a total number of **xxx** transboundary species contributing to **xx**% to the region's total landings and **xx**% of total revenue has experienced 43.0% of all documented international fisheries conflicts since 2000 [@Spijkers:2019cz].
-The European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel since 2007 [@Spijkers:2017ij], a species that is transboundary and contributes **xx** to landings and **xx** in revenue to the countries involved in the dispute.
-The Mediterranean, a region that has experienced conflicts since the 1980s [@Kliot:1989kv], is home to a large number of transboundary stocks that contribute **xx**% to total landings and **xx**% of revenue of countries along the Sea's rim.
-The identification of current transboundary species is a first step towards establishing joint management plans for marine resources [@Link:2010ei], key not only to sustain fisheries over the long term, but also to avoid international conflict.
-
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="A) Number of transboundary species per EEZ and they contribution to countries fishing revenue.
+The number of species is represented in the EEZ while the revenue is represented in the land polygon.
+B) Regional revenue (left) and catch (right) contribution of tranbsoundary species."}
 
@@
 
-![**Number of transboundary species by EEZ and their revenue by country**](./Figures/Fig1.png)
+![**A) Number of transboundary species per EEZ and they contribution to countries fishing revenue.
+The number of species is represented in the EEZ while the revenue is represented in the land polygon.
+B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.**](./Figures/Fig1.png)
+
+We found transboundary fisheries to be of substantial economic importance in regions with historic fisheries-related conflicts.
+The Asian region with a total number of **310** transboundary species contributing  **20'.4 million tons** to the region's total landings and **19.3 billion USD** in revenue has experienced 43.0% of all documented international fisheries conflicts since 2000 [@Spijkers:2019cz].
+The European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel since 2007 [@Spijkers:2017ij], a species that is transboundary and contributes **xx** to landings and **xx** in revenue to the countries involved in the dispute.
+The Mediterranean, a region that has experienced conflicts since the 1980s [@Kliot:1989kv], is home to a large number of transboundary stocks contributing over 6 million tones worth over **8 billion USD** to countries along the Sea's rim.
+The identification of current transboundary species is a first step towards establishing joint management plans for marine resources [@Link:2010ei], key not only to sustain fisheries over the long term, but also to avoid international conflict.
 
@@
 
-```{r Status_Table, eval = T, echo = F}
+```{r Status_Table, eval = F, echo = F}
 
@@
            Rules) %>% 
-  kable(, booktabs = T,
+  kable("latex", booktabs = T,
         caption = "Rules to determine the status of each transboundary species") %>%

### 2019-12-17 Manuscript_Draft.Rmd
Responded to William comments

@@
 ---
-title: "Fish do not need Visas: the transboundary nature of world fished species"
-author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^3^ and William W.L. Cheung^1^"
+title: "Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species"
+author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
 date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
@@
 
-Species distribution around the world is not a random process.
-The area in space and time that a species population occupies is a response to the availability of resources, a series of biotic and abiotic factors, as well as their influence on the evolutionary processes [@Hunch].
-Marine resource management is predicated on knowledge of species distributions as human-made spatial boundaries are inherent to existing management systems (e.g., marine protected areas) [@Song:2017iua].
-However, incorporating the concept of species distribution into fisheries management, or policy, is a relatively recent construct [@Alexa].
-The delineation of Economic Exclusive Zones (EEZs) in the early 80s, for instance, virtually established boundaries across the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management.
-Forty years after their formal adoption, the question of how many shared species exist in the world based on their distribution is still unanswered.
-Fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
-Climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management (@Mills).
-Thus, answering the questions of how many shared stocks exist in the world, and where these are located, is critical to developing effective and resilient management plans for the continued and future sustainable use and conservation of marine resources.
+Distributions of marine species around the world are not bounded by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hunch; @NelsonFishesOfTheWorld].
+However, management of living marine resources is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua].
+The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
+Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives..
+For example, fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
+Climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Mills].
 
-From 1973 to 1982, members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 miles from shore [@McRaeandMunro1989].
-The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over the exploration and exploitation of marine resources over 200 nautical miles off their coasts [@UN:1982].
-While intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas was not informed by bio-geography, essentially ignoring species distributions and creating what we know today as shared fish stocks [@Gulland, @Munro2002].
-Fish stocks, are comonly refered in fisheries management as a particular population that is more or less isolated from other stocks of the same species and hence self-sustaining [@FAO:1999tk].
-The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary stocks, shared by 2 or more neighboring coastal nations; (*ii*) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (*iii*) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
-The inception of shared stocks called for the establishment of new fisheries management methods.
-Managers and scientists adopted a game theory approach – or means to analyze strategic interactions among decision-makers – which demonstrates that collaboration is most likely to result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga,@Eide:2013dh].
-Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and lead to conflict between coastal nations [@Spijkers:2017ij], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
-Moreover, under climate change, species distributions will shift [@Cheung2016], resulting in new shared stocks [@Pinsky:2018cb] and highlighting the key role cooperative fisheries management can play in maintaining stocks and profitability [@Nguyen:2018dk] as well as hopefully reducing fisheries conflict [@Spijkers:2019cz].
-
-There is a gap in assessing the nature and number of transboundary species in the world based on their spatial distribution.
-Caddy [@Caddy:1997ue] in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
+Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that distribute across two or more EEZs (hereafter called shared species) in the world is still unclear.
+Caddy in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
 However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
 More recently, Teh et al.
-[@Teh:2015gd] estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
+(2010) estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
 While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
-Thus, despite recent research highlighting the interconnection of marine species [@Ramesh:2019va], the total number of transboundary species is yet to be identified at a global scale.
-Yet, such an understanding is critical to effectively managing fisheries, as needs differ substantially between discreet and shared species [@Mills] and climate change will yield new challenges associated with new shared fisheries [@Pinsky:2018cb].
+Getting accurate estimates of the number of shared species and where they are located can help develop fisheries management and conservation plans that account for the challenges from transboundary resources management [@Millis].
 
- <!-- **Methods summary** (250/250 words) -->
+## Methods summary (250/250 words)
 
-In this study, we overlay the known distribution of **968** commercially valuable marine fish species and the Exclusive Economic Zones of 175 coastal countries to determine the total number of transboundary species and their contribution to global catch and landed value.
-We adopt the UN definition of transboundary stocks (shared by neighboring EEZs), but carry out the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
+This paper aims to identify the world current transboundary species and determine their contribution to the catch and revenue of the world marine fisheries.
+The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks, shared by 2 or more neighboring coastal nations; (ii) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (iii) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
+We focus on estimating the number of species that meet the first category.
+We overlay the known distribution of **968** commercially valuable marine fish species and the Exclusive Economic Zones of **175** coastal countries to determine the total number of transboundary species and their contribution to global catch and landed value.
+We carry out the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
 
-We combined multiple species distribution data-sources and developed a series of three criteria to determine if a species is transboundary.
-Current species distributions were obtained from the largest observational database of the world’s marine species [@REFNEreus] and two structurally distinct species distribution models [@REFGabs; @Zeler].
-The first criteria to determine the transboundary nature of a species considered the number of data-sources agreeing that a species was present in a single grid-cell.
-Second, we used spatially explicit catch data [@Zeller] to confirm the occurrence of a species in a given grid cell.
-The species was droped if it was present in any specific grid cell, but no catch was record was found.
-The third criteria considered the spatial distribution of species between neighboring EEZs.
-In addition to determining the number of transboundary stocks, we also estimated the contribution of each to fishing revenues and landings as well as categorized them according to catch trends [@Kleisner:2013gh].
-Our study provides a first empirical approximation of the number of shared commercial species globally, significantly contributing to our understanding of the true transboundary nature of world fisheries and hopefully helping inform the effective management of these resources.
+We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
+The first criteria only considered shared species between neighbouring EEZs, rather than the extended distribution.
+We sub-divided EEZs by regions (e.g.
+Mexico Pacific and Mexico Atlantic).
+Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species [@REFNEreus] and two structurally distinct species distribution models [@REFGabs; @Zeller] (see Methods).
+For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
+The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller].
+A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
+Finally, the last criteria determined a spatial treshold to confirm that a species occurs in both neighboring EEZs.
+Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller] and categorized them according to catch trends [@Kleisner:2013gh].
 
-<!-- **Results and discussion** (~500/1000 words) -->
+## Results and discussion (~500/1000 words)
 
-We estimate a total of 633 transboundary species in the world, more than double the number previously estimated [@Teh:2015gd] (Fig.
+Overall, we estimated **633** transboundary species in the world, more than double the number previously estimated [@Teh:2015gd], accounting for **65.4**% of the species analyzed (Fig.
 1A).
-We also find that fisheries on these species contribute substantially to both landings and revenue.
-Between 2005 and 2014, fleets targeting shared stocks within EEZs landed an average of 69 million tonnes, representing around 64% of the global catch (within EEZs), and generating USD 79.7 million in fishing revenue, equivalent to 49.8% of total revenue.
-These values are higher than previously estimated [@Teh].
-Transboundary species are particularly important in terms of catch and revenue in regions of the world like Eastern Asia and Latin America and the Caribbean (Fig 1B).
-Particular in Northern America (Bermuda, Canada, Greenland, and the US), a moderate amount of catch (3.4 thousand tons) are worth 11.7 billion USD, highlighting the importance of transboundary species to the economy of the region.
-This is the case of the US where 116 species are responsible for up to 12.20 million USD and Peru where 28 species are responsible for USD 5.2 million (Fig 1A).
+Between 2005 and 2014, national fleets targeting shared stocks within EEZs landed an average of **69.2** million tonnes, representing **64**% of the EEZ-global catch, and generating USD **79.7** million in fishing revenue, equivalent to **49.8**% of the total revenue of the same period.
+These values are higher than previously estimated [@Teh] and higlight the importance of these stocks at the global level.
+
+Transboundary species are particularly important at the regional and national level.
+In terms of catch and revenue, Eastern Asia and Latin America and the Caribbean are the higher zones (Fig 1B).
+Particular for counties in North America (Bermuda, Canada, Greenland, and the US), a moderate amount of catch (3.4 thousand tons) are worth 11.7 billion USD, highlighting the importance of transboundary species to the economy of the region.
+The EEZs along Western Eurpe, in turn, are home of **X** species responding to the joint fisheries management policy established by the European Union.
+In here, quotas are allocated by species and regulatory area [@Melnychuk:2017gh], making this region **unique** in terms of joint management of a high numer of shared stocks.
+
+At the country level, transboundary species are most valuable for the United States (USD 9,605 million), Russia (USD 6,361 million), China (USD 6,279 million) and Peru (USD 5,211).
+On the other hand, EEZs like that of Portugal, the Mediterranean side of Spain, Senegal, and the UK are rich in transboundary species (n > 110), but these do not represent a large amount of revenue, comparativeley.
+China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018], is the only country categorized high in both number of transboundary species (n = 119) and revenue.
+For the US, 16 species make up 90% of the revenue from transboudary species, with American scallop (*Placopecten magellanicus*) shared with Canada in Georges Bank [@https://elischolar.library.yale.edu/cgi/viewcontent.cgi?article=1008&context=fes-pubs] contributing 41.8% or the revenue.
+Russia shares the largest fished species in the world, Alaskan polllock (*Theragra chalcogramma*) [@SOFIA2018], with both Japan and the US.
+For Russia, this fishery is responsible for 50% of the revenue from transboundary species with other eight species comprising the 90% of revenue.
+In the case of Peru, Peruvian anchoveta (*Engraulis ringens*) and jumbo squid (*Dosidicus gigas*), both shared with Chile, represent almost 90% of the revenue from transboundary species, with anchoveta accounting for 79%.
+
+These results hilights the importance of transboundary species not only at the global and regional levels, but also at the country level.
 
@@
 
-We found transboundary fisheries to be of substantial economic importance in regions with historic fisheries-related conflicts.
-The Asian region with a total number of **310** transboundary species contributing  **20'.4 million tons** to the region's total landings and **19.3 billion USD** in revenue has experienced 43.0% of all documented international fisheries conflicts since 2000 [@Spijkers:2019cz].
-The European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel since 2007 [@Spijkers:2017ij], a species that is transboundary and contributes **xx** to landings and **xx** in revenue to the countries involved in the dispute.
-The Mediterranean, a region that has experienced conflicts since the 1980s [@Kliot:1989kv], is home to a large number of transboundary stocks contributing over 6 million tones worth over **8 billion USD** to countries along the Sea's rim.
-The identification of current transboundary species is a first step towards establishing joint management plans for marine resources [@Link:2010ei], key not only to sustain fisheries over the long term, but also to avoid international conflict.
-
-The two regions of the world that share the most species (the North East and Central Atlantic) have developed quite different approaches to managing shared stocks.
-In the North East Atlantic, fisheries are managed by the European Union and quotas allocated by species and regulatory area, with some of them (e.g., Iceland and Norway) characterized as having good fisheries management [@Melnychuk:2017gh].
-On the other hand, fisheries along the west coast of Africa could benefit from improvements [@Melnychuk:2017gh].
-Ironically, this region has long been exploited by foreign fleets, including European, sometimes illegally [@Belhabib:2015bl], with questionable fishing rights systems [@Mills:2004dj], and unfair fisheries agreements [@Kaczynski & Fluharty 2002].
-Thus, having joint management plans for shared stocks between neighbors will not be enough to achieve sustainable goal 14, Life Below Water [@SDG].
-Countries need to work together towards a more equitable system of global fishing rights.
+We found transboundary fisheries to be of substantial economic importance in regions with past fisheries-related conflicts [@Spijkers:2019cz].
+For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Miller2003].
+Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel [@Spijkers:2017ij], a species that is transboundary and contributes **X** to landings and **X** in revenue to the countries involved in the dispute.
+In addition, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky].
 
@@
 
-We present a novel method to determine whether or not a species can be considered transboundary.
+We determine whether or not a species can be considered transboundary.
 The method is based on a series of criteria to be met and the overlay of species distributions and the spatial boundaries of the world’s EEZs.
@@
 We computed a *Species Index* by dividing the number of datasets that confirm presence of a species in a grid cell over the total amount of datasets (*n* = 3).
-The index is unit-less and represents a scale from 0.3 to 1 where 0.3 means only one dataset reports presence of the species in a grid cell and 1 means agreement between all datasets.
-We selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species (**S1_Map_per_dataset**).
+The index is unit-less and represents a scale from 0.3 to 1 where 0.3 means only one dataset reports presence of the species in a grid cell, 0.6 represents two of three sources, and 1 means agreement between all datasets.
+For the analysis, we selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species (**S1_Map_per_dataset**).
 
@@
 
-```
+# Recicled text (Not to be included)
+
+<!-- From 1973 to 1982, members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 miles from shore [@McRaeandMunro1989].
+The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over the exploration and exploitation of marine resources over 200 nautical miles off their coasts [@UN:1982].
+While intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas was not informed by bio-geography, essentially ignoring species distributions and creating what we know today as shared fish stocks [@Gulland, @Munro2002].
+Fish stocks, are comonly refered in fisheries management as a particular population that is more or less isolated from other stocks of the same species and hence self-sustaining [@FAO:1999tk].
+The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary stocks, shared by 2 or more neighboring coastal nations; (*ii*) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (*iii*) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
+The inception of shared stocks called for the establishment of new fisheries management methods.
+Managers and scientists adopted a game theory approach – or means to analyze strategic interactions among decision-makers – which demonstrates that collaboration is most likely to result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga,@Eide:2013dh].
+Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and lead to conflict between coastal nations [@Spijkers:2017ij], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
+Moreover, under climate change, species distributions will shift [@Cheung2016], resulting in new shared stocks [@Pinsky:2018cb] and highlighting the key role cooperative fisheries management can play in maintaining stocks and profitability [@Nguyen:2018dk] as well as hopefully reducing fisheries conflict [@Spijkers:2019cz].
+-->
+
+<!-- There is a gap in assessing the nature and number of transboundary species in the world based on their spatial distribution.
+Caddy [@Caddy:1997ue] in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
+However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
+More recently, Teh et al.
+[@Teh:2015gd] estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
+While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
+Thus, despite recent research highlighting the interconnection of marine species [@Ramesh:2019va], the total number of transboundary species is yet to be identified at a global scale.
+Yet, such an understanding is critical to effectively managing fisheries, as needs differ substantially between discreet and shared species [@Mills] and climate change will yield new challenges associated with new shared fisheries [@Pinsky:2018cb].
+-->

### 2019-12-17 Initial_Analysis.Rmd
Finished Figure 1 and changed categories of Figure 2. Included some other minimal analysis

@@
     ) %>% 
-    filter(Year > Y_Max_Peak) %>% # Filter years after peak year
+    filter(Year >= Y_Max_Peak) %>% # Filter years after peak year
     group_by(TaxonKey,Territory) %>% 
@@
 # Note, It averages the LAST 10 years oe ach gridcell and then adds them together
+#  I think NA is the ABNJ
 
@@
 Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep ="")) %>% 
-  clean_names()
+  clean_names() %>% 
+  rename(eez_name=territory)
 # Status_Data <- Species_Status
@@
 Max_AI <- 1-Min_AI # Max Area Index
-
 # Model Index
 MI <- 100 # Model Index
-
-####_____End Select Tresholds_______ ###
 
@@
   mutate(
-    Bins = cut(n_trans_spp,breaks = 4),
-    Bins_Plot = cut(n_trans_spp,breaks = 4,
-                    labels = c('super low', 'low', 'high','super high'))
+    Bins = cut(n_trans_spp,breaks = 5),
+    Bins_Plot = cut(n_trans_spp,breaks = 5,
+                    labels = c('super low', 'low','median', 'high','super high'))
   )
@@
                                  ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-         Bins = cut(fishing_entity_catch,breaks = 4),
-         Bins_Plot = cut(fishing_entity_catch,breaks = 4,
-                         labels = c('super low', 'low','high','super high'))
+         Bins = cut(fishing_entity_catch,breaks = 5),
+         Bins_Plot = cut(fishing_entity_catch,breaks = 5,
+                         labels = c('super low', 'low','median','high','super high'))
   ) %>% 
@@
 # Get Catch and Revenue data for mapping
+
+# Set manual breaks for bins
+Rev_Breaks <- c(-1,10,100,1000,5000,10000)
 
@@
   summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
+  ungroup() %>% 
   mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-         Bins = cut(Total_USD,breaks = 4),
-         Bins_Plot = cut(Total_USD,breaks = 4,
-                         labels = c('super low', 'low','high','super high'))
+                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
+                                 ),
+         Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
+         Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
+                         labels = c('super low', 'low','median','high','super high'),
+                         dig.lab = 5 # Removes scientific notaion
+                         )
   ) %>% 
@@
 
+# Contienent level
+Continent_Data <- Revenue_Country %>% 
+  left_join(Catch_Country,
+             by = "fishing_entity") %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
+  group_by(georegion) %>% 
+  summarise_if(is.numeric,sum,na.rm=T)
+
+Continent_Data_Trans <- Tresholded_T_Data %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
+  group_by(georegion) %>% 
+  summarise(
+    n_trans_spp = length(unique(taxon_key))
+  ) %>% 
+  left_join(Continent_Data)
+
 ### Catch Data
@@
 ### Revenue Data
-Continent_Data <- Revenue_Country %>% 
+Subregion_Data <- Revenue_Country %>% 
   left_join(Catch_Country,
@@
 
-Continent_Data_Trans <- Tresholded_T_Data %>% 
+Subregion_Data_Trans <- Tresholded_T_Data %>% 
   left_join(UN_Regions,
@@
   ) %>% 
-  left_join(Continent_Data) %>% 
-  mutate(id = seq(1,nrow(Continent_Data_Trans)))
+  left_join(Subregion_Data) %>% 
+  mutate(id = seq(1,nrow(.)))
 
 # Fix names for plot
-Continent_Data_Trans$sub_region <- Continent_Data_Trans$sub_region %>% 
+Subregion_Data_Trans$sub_region <- Subregion_Data_Trans$sub_region %>% 
   gsub("Northern","N.",.) %>% 
@@
 
-number_of_bar <- nrow(Continent_Data_Trans)
-
-label_data_rev <- Continent_Data_Trans %>% 
+number_of_bar <- nrow(Subregion_Data_Trans)
+
+label_data_rev <- Subregion_Data_Trans %>% 
   arrange(Total_USD) %>% # soo it looks like a nice snail :)
   mutate(
-    id = seq(1,nrow(Continent_Data_Trans)),
+    id = seq(1,nrow(Subregion_Data_Trans)),
     angle = 90 -360 * (id-0.5)/number_of_bar,
@@
 
-label_data_catch <- Continent_Data_Trans %>% 
+label_data_catch <- Subregion_Data_Trans %>% 
   arrange(fishing_entity_catch) %>% # soo it looks like a nice snail :)
   mutate(
-    id = seq(1,nrow(Continent_Data_Trans)),
+    id = seq(1,nrow(Subregion_Data_Trans)),
     angle = 90 -360 * (id-0.5)/number_of_bar,
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")
+  left_join(Transboundary_Spp, by ="eez_name")# %>% 
+  # filter(!is.na(n_trans_spp))
 
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-  left_join(Revenue_Country, by ="fishing_entity")
+  left_join(Revenue_Country, by ="fishing_entity")# %>% 
+  # filter(!is.na(Total_USD))
 
@@
 # Create labels for legend
-Labels_Trans <- c(paste(unique(Transboundary_Spp$Bins)),"NA")
-Labels_Rev <- unique(Revenue_Country$Bins)
+Bins_Trans <- Transboundary_Spp %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+Bins_Rev <- Revenue_Country %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
+# Labels_Trans <- c(paste(unique(Transboundary_Spp$Bins)),"NA")
+# Labels_Rev <- unique(Revenue_Country$Bins)
+
+Labels_Rev <- c("(1-10]",paste(Bins_Rev[2:5]))
 
@@
                                   "#F2AD00",#"#F2AD00", # Yellow
-                                  # "#F98400",#"#F98400", #Orange
+                                  "#F98400",#"#F98400", #Orange
                                   "#FF0000"#,"#FF0000" #Red
   ),
-  na.value = "white"
+  # na.value = "white"
+  na.translate = F
   ) +
@@
   annotate("text", 
-           x =(c(-95,-36,21,80,146)+4),
+           x =(c(-85.5,-30,25,81,136)+5),
            y = -93.5,
@@
   annotate("text", 
-           x =c(-100,-48,12,69),
+           x =(c(-85.5,-31,20,75,131)+5),
            y = -110,
@@
   annotate("text", 
-           x =-190,
+           x =-180,
            y = -93.5,
@@
   annotate("text", 
-           x =-190,
+           x =-180,
            y = -110,
@@
     legend.text = element_blank()#,
-  )
-
+  ) +
+  guides(fill = guide_legend(nrow = 1))
+
+# ggsave("Map.png",
+#        Map,
+#         width = 10,
+#          height = 10,
+         # units = "in")
 # Map
@@
 # Set plot limits
-max_lim <- max(Continent_Data_Trans$Total_USD)
+max_lim <- max(Subregion_Data_Trans$Total_USD)
 
@@
 
-Rev_Plot <- ggplot(data = Continent_Data_Trans, 
+Rev_Plot <- ggplot(data = Subregion_Data_Trans, 
                    aes(x=reorder(id,Total_USD),
@@
             size=2, 
-            angle= label_data$angleb, 
+            angle= label_data_rev$angleb, 
             inherit.aes = FALSE) +
@@
 
-max_lim <- max(Continent_Data_Trans$fishing_entity_catch)
-
-Catch_Plot <- ggplot(data = Continent_Data_Trans, 
+max_lim <- max(Subregion_Data_Trans$fishing_entity_catch)
+
+Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
                      aes(x=reorder(id,fishing_entity_catch),
@@
             size=2, 
-            angle= label_data$angleb, 
+            angle= label_data_catch$angleb, 
             inherit.aes = FALSE) +
@@
 )
+
+```
+
+### China, US, Russia, and Peru
+
+```{r Map_Particulars, eval =F, echo =F}
+
+PeRu <- c("Peru", "Russian Federation","Russia", "Chile", "United States of America","USA")
+
+Total_PeRu <- Revenue_Country %>% 
+  filter(fishing_entity %in% PeRu) %>% 
+  select(1:2) %>% 
+  mutate(fishing_entity = ifelse(fishing_entity == "Russia","Russian Federation",
+                                 ifelse(fishing_entity == "United States of America","USA",fishing_entity))
+  )
+
+Rev_PeRu <- sau_eez_fes %>% 
+  filter(fishing_entity %in% PeRu) %>% 
+  group_by(fishing_entity_id, fishing_entity) %>% 
+  summarise(n=n()) %>% # Get all of the fishing entity and id
+  select(-n) %>% 
+  full_join(Tresholded_T_Data,
+            by = "fishing_entity") %>% 
+  group_by(fishing_entity_id,
+           fishing_entity,
+           taxon_key) %>% 
+  summarise(n()) %>% # get each taxa per nation
+  left_join(SAU_Revenue_Data,
+            by = c("fishing_entity_id","taxon_key")) %>% 
+  left_join(Exploited_Species) %>% 
+  group_by(fishing_entity) %>%
+  top_n(16,mean_value) %>%
+  select(2,3,5) %>% 
+  mutate(mean_value = mean_value/1000000) %>% # Million of USD
+  left_join(Total_PeRu,
+            by = "fishing_entity") %>% 
+  mutate(Ratio = mean_value/Total_USD*100)
+
+Rev_PeRu %>% 
+  group_by(fishing_entity) %>% 
+  summarise(sum(Ratio))
 
@@
 Status_Data_Plot <- Tresholded_T_Data %>% 
-  # mutate(TaxonKey = as.character(TaxonKey)) %>%
-  # rename(Territory = CT_fishing_entity) %>% 
   left_join(Status_Data, 
-            by =c("Territory","TaxonKey")
-  ) %>%
-  mutate(Status = ifelse(is.na(Status),"No Status",Status)) %>% 
-  group_by(Territory,Status) %>% 
-  summarise(value = length(unique(TaxonKey))) %>% 
-  left_join(UN_Regions, by ="Territory") %>%
+            by =c("eez_name","taxon_key")
+  ) %>%
+  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
+  group_by(fishing_entity,status) %>% 
+  summarise(value = length(unique(taxon_key))) %>% 
+  left_join(UN_Regions, by ="fishing_entity") %>%
   mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-  rename(FishingRegion=Territory) %>% 
-  left_join(Clean_sau_eez_fes) %>% 
   group_by(individual = fishing_entity,
            group = Georegion,
-           observation = Status) %>% 
+           observation = status) %>% 
   summarise(Total_trans = sum(value,na.rm=T)) %>% 
   mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
-  filter(!is.na(individual)) %>% 
+  filter(!is.na(individual),
+         !str_detect(individual, "(")
+         )%>% 
   select(individual,observation,group,value) %>% 
   arrange(group,value) %>% 
-  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value))
-
-# Include possible missing countries in bothe datasets
-# Countries_Data_Plot <- Discrete_Data_Plot %>% 
-#   anti_join(Countries_Data_Plot,
-#             by = c("individual","group")) %>% 
-#   mutate(Total_Discrete = 0) %>% 
-#   bind_rows(Countries_Data_Plot)
-
-# Discrete_Data_Plot <- Countries_Data_Plot %>% 
-#   anti_join(Discrete_Data_Plot,
-#             by = c("individual","group")) %>% 
-#   mutate(value = 0) %>% 
-#   bind_rows(Discrete_Data_Plot)
-
+  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
+         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
+                            ifelse(observation == "Max Exploited","Category B",
+                                   ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+                            )
+         )
+         )
 ```
@@
                     values = c(
-                      "#FF0000", # collapsed,
-                      "#046C94", # Developing
-                      "#00A08A", #Max exp.
-                      "grey", #no status
-                      "#F98400", #over exp
-                      "#5BBCD6" # Rebuilding
+                      "#9986A5", # Developing / Rebulding / Cat A / blue
+                      "#79402E", #Max exp. / Cat B / green
+                      "#CCBA72", # collapsed / Overexp. / Cat. C / Red
+                      "#8D8680"
                     ),
@@
 
+### Mackrell war
+
+```{r mackrell, eval = F, echo =F}
+
+Conflict_nations <- c()
+
+Macrell <- Tresholded_T_Data %>% 
+  filter(taxon_key == 600118,
+         eez_name %in% Conflict_nations
+  )
+
+```
+
 Create figures that are based in species (e.g. number of countries each species has)
@@
 Species_Trans <- Tresholded_T_Data %>% 
-  group_by(TaxonKey) %>% 
+  group_by(taxon_key) %>% 
   summarise(
@@
   mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
-         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
+         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp),
+         Category == ifelse(DemersPelag %in% c("Developing","Rebuilding","Category A"),
+                            ifelse(DemersPelag == "Max Exploitation","Category B",
+                                   ifelse(DemersPelag %in% c("Overfished","Collapsed","Category C"),"Category C", "No Category")
+                            )
+         )
+  ) %>% 
   select(individual=scientific_name,
@@
 )
-
-```
-
-### Species status (SAU methods)
-
-Note that (n), the number of ‘stocks’ is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area is at least 1000 tonnes.
-
- 1) The first and last reported landings are at least ten years apart;
-
-2) There are at least five years of consecutive catches; and
-
-3) The catch in a particular area (LME) is at least 1,000 tonnes.
-
-Once those tresholds are met, the status of the species is determined as follows:
-
-- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
-- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
-- Exploited	Landing > 50% of max. landing
-- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
-- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
-
-*Notes* = 3 years average mean
-
-```{r Species_Status, eval = T, echo =F}
-
-CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
-  mutate(INDEX = seq(1,259200,1))
-
-# SAU relations between INDEX and Country's EEZs
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-Index_Code <- EEZIDs_List %>% 
-  left_join(EEZ_CellID) %>% 
-  rename(Territory = Name)
-
-Spp <- GetSppDist(600004, Model = "SAU_C", Coord = CoorG)
-
-Data <- Spp %>% 
-  gather("Year","Value",CATCH.1:CATCH.65) %>% 
-  arrange(INDEX) %>% 
-  mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
-  left_join(Index_Code) %>% 
-  filter(!is.na(EEZID),
-         Value > 0) %>% 
-  group_by(Species,Year,EEZID,Territory) %>% # Total catch per country
-  summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
-  group_by(Species,Territory,EEZID,Year) %>% 
-  mutate(RMean = rollmean(x = Total_Catch, 5, align = "right", fill = Total_Catch)) %>% 
-  group_by(Species,Territory,EEZID)
-
-# head(Data)
-
-# Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
- Tresholds <- Data %>% 
-  arrange(Territory) %>% 
-  group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
-            Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
-            Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
-            ) %>% 
-   gather("Step","Treshold",Years_appart:Catch_over) %>% 
-   filter(Treshold == "Yes")
-
- # Evaluate stocks
-
- # Filter data that does not satisfy tresholds
-
- Landings_Peaks <- Data %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Max_Peak = max(RMean,na.rm=T))
-
- Eval_Data <- Data %>% 
-  semi_join(Tresholds,
-            by = c("Species","Territory")) %>% 
-   left_join(Landings_Peaks,
-             by = c("Species","Territory"))
-
- Peak_Year <- Eval_Data %>% 
-   filter(RMean == Max_Peak) %>% 
-   select(Species,Territory,EEZID,Y_Max_Peak = Year)
-
- Post_Max_Min <- Eval_Data %>% 
-   left_join(Peak_Year) %>% 
-   filter(Year > Y_Max_Peak) %>% 
-   group_by(Species,Territory,EEZID) %>% 
-   summarise(Post_Max_Min = min(RMean,na.rm=T))
-
- Y_Post_Max_Min <- Eval_Data %>% 
-   left_join(Post_Max_Min) %>% 
-   filter(RMean == Post_Max_Min) %>% 
-   select(Species,Territory,EEZID,Y_Post_Max_Min = Year)
-
- Data_Status <- Eval_Data %>% 
-   left_join(Peak_Year,
-             by = c("Species","Territory","EEZID")) %>%
-   left_join(Post_Max_Min,
-             by = c("Species","Territory","EEZID")) %>% 
-   left_join(Y_Post_Max_Min,
-             by = c("Species","Territory","EEZID")) %>% 
-   rename(Y_RMean = Year) %>% 
-   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
-                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
-                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                      "No Status")
-                                        )
-                                 )
-                          )
-   )
-   ) %>% 
-   filter(Y_RMean > 2004) %>% 
-   group_by(Species,EEZID,Territory,Status) %>% 
-   summarise(n_Status= n()) %>% 
-   group_by(Species,EEZID,Territory) %>% 
-   top_n(1,n_Status)
-
- # Manual estimation
-
- data.frame(
-   Y_RMean = 1980,
-   RMean = 642187,
-   Max_Peak = 1298712,
-   Y_Max_Peak = 1990,
-   Post_Max_Min = 681967,
-   Y_Post_Max_Min = 2010,
-   Y_RMean = 2014
- ) %>% 
-   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
-                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))," Over Exploited",
-                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                      "NA")
-                                        )
-                                 )
-                          )
-   )
-   )
-
-```
-
-```{r Top_spp_Circle_Diagram, eval =F, echo = F}
-
-# Top 5 shared species per marine environment (number of countries sharing the species)
-Top_Species <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
-  # group_by(TaxonKey,TaxonName,CommonName,DemersPelag) %>% 
-  # summarise(Sum_Countries =sum(n_countries,na.rm=T)) %>% 
-  group_by(DemersPelag) %>% 
-  top_n(5,n_countries)
-
-# Countries that share the top 10
-Top_Spp_Countries <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index < Min_AI |
-      Area_Index > Max_AI,
-    Model_Index == MI,
-    Same_Nation == "No",
-    TaxonKey %in% Top_Species$TaxonKey
-  ) %>% 
-  left_join(Species_Trans) %>% 
-  rename(scientific_name =TaxonName) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(from = paste(Genus,"\n",Species,sep=""),
-         DemersPelag = replace_na(DemersPelag, "Other")) %>%
-  group_by(
-    # from,
-    from = scientific_name,
-           to=CT_fishing_entity,
-           DemersPelag
-  ) %>% 
-  summarise(value=n()
-  ) #%>%
-  # filter(DemersPelag == "demersal") %>%
-  # select(-DemersPelag)
-
-####________________###
-# Circulize package ####
-# https://jokergoo.github.io/circlize_book/book/
-####________________###
-
-# To set links color 
-Bins <- as.numeric(cut(Top_Spp_Countries$value,breaks = 5)) # By size of sharing
-
-# To get country's flags... https://flagpedia.net/download
-flags <- c(paste("Temporal_Data/flags-mini/",list.files("Temporal_Data/flags-mini/"),sep=""))
-
-# List of Ecosystems
-Classification <- Top_Species %>% group_by(DemersPelag) %>% summarise(n()) %>%  pull(DemersPelag)
-
-####________________ PLOT PER ECOSYSTEM _____________________ ###
-
-for(s in 1:2){ # sclae loop
-  for(i in 1:length(Classification)) {
-    # for(i in 1:2) { # for testing
-
-    # Set scales to plott both absolut and proportional values
-    if(s == 1){
-      Scales <- "TRUE"
-    }else{
-      Scales <- "FALSE"
-    }
-
-    # Saving the plot
-    Plot_name <- paste(Figures_Path,Classification[i],Scales,".tiff",sep="")
-    tiff(Plot_name, width = 5, height = 5, units = 'in', res = 500)
-
-    # Subsetting the data for each plot
-    DemersPelag_i <- Classification[i]
-
-    Data <- Top_Ten_Spp_Countries %>% 
-      filter(DemersPelag %in% DemersPelag_i) %>% 
-      select(-3)
-
-    # Use to set links' colors to each species
-    Speceis_cols <- Data %>% group_by(from) %>% summarise(n()) %>% pull(from)
-
-    # The base plot
-    circos.clear()
-    chordDiagram(Data, 
-                 annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
-                 annotationTrackHeight = c(0.001, 0.1), # set links close to the axis
-                 directional = 1, # direction of arrows
-                 direction.type = c("diffHeight", "arrows"), # use arrows
-                 grid.col = "grey",
-                 # if col == Bins then colors will change depending of value
-                 # col = ifelse(Bins == 1,"#046C9A", # deep blue
-                 #              ifelse(Bins == 2,"#78B7C5", #light blue
-                 #                     ifelse(Bins == 3,"#EBCC2A", #yellow
-                 #                            ifelse(Bins == 4, "#E1AF00", #cream
-                 #                                   "#F21A00")))), #red
-                 # if col == Species_cols then colors will change depending of species
-                 col = ifelse(Data$from == Speceis_cols[1],"#FF0000", # deep blue
-                              ifelse(Data$from == Speceis_cols[2],"#00A08A", #light blue
-                                     ifelse(Data$from == Speceis_cols[3],"#F2AD00", #yellow
-                                            ifelse(Data$from == Speceis_cols[4], "#F98400", #cream
-                                                   "#5BBCD6")))), #red
-                 # link.arr.col = wes_palette("Zissou1"), 
-                 link.arr.type = "big.arrow",# make links big arrows
-                 diffHeight = uh(-0.5, "mm"), # brings the arrow to the bottom of the source
-                 scale = Scales, # fraction of each species to total share of each country instead of absolute value
-                 preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Data))))) # I have no idea but helps with the labels
-    )
-
-    #  Function to inlcude other layers
-    circos.track(track.index = 1, panel.fun = function(x, y) {
-      xlim = get.cell.meta.data("xlim")
-      xplot = get.cell.meta.data("xplot")
-      ylim = get.cell.meta.data("ylim")
-      sector.name = get.cell.meta.data("sector.index")
-
-      # Add labels
-      circos.text(mean(xlim),
-                  ylim[1],
-                  sector.name,
-                  facing = "clockwise",
-                  niceFacing = TRUE,
-                  adj = c(-0.2, 0.5),
-                  col = "black",
-                  cex = 0.6) # size of labels
-
-      # Add country's flags instead of names (still need to link names to falgs)
-
-      # library(EBImage)
-      # pos = circlize:::polar2Cartesian(circlize(CELL_META$xcenter, CELL_META$ycenter))
-      # image = EBImage::readImage(flags[CELL_META$sector.numeric.index])
-      # 
-      # rasterImage(image,
-      #             xleft = pos[1, 1] - 0.006, 
-      #             ybottom = pos[1, 2] - 0.005,
-      #             xright = pos[1, 1] + 0.05,
-      #             ytop = pos[1, 2]+ 0.04
-      #             )
-
-      # END FLAGS TRYOUT
-
-      # Set plot Title
-      Title <- paste("Top",Classification[i], "Species",sep =" ")
-      title(Title)
-
-    }, bg.border = NA) #end of circos.track
-
-    dev.off()
-  } # close for loop
-} #close scale loop
 
@@
 ```
+
+```{r Top_spp_Circle_Diagram, eval =F, echo = F}
+
+# Top 5 shared species per marine environment (number of countries sharing the species)
+Top_Species <- Species_Trans %>% 
+  mutate(scientific_name = paste(Genus,Species)) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
+  # group_by(TaxonKey,TaxonName,CommonName,DemersPelag) %>% 
+  # summarise(Sum_Countries =sum(n_countries,na.rm=T)) %>% 
+  group_by(DemersPelag) %>% 
+  top_n(5,n_countries)
+
+# Countries that share the top 10
+Top_Spp_Countries <- Clean_Results_Trans %>% 
+  filter(
+    Area_Index < Min_AI |
+      Area_Index > Max_AI,
+    Model_Index == MI,
+    Same_Nation == "No",
+    TaxonKey %in% Top_Species$TaxonKey
+  ) %>% 
+  left_join(Species_Trans) %>% 
+  rename(scientific_name =TaxonName) %>%
+  left_join(Species_environ_list) %>% 
+  mutate(from = paste(Genus,"\n",Species,sep=""),
+         DemersPelag = replace_na(DemersPelag, "Other")) %>%
+  group_by(
+    # from,
+    from = scientific_name,
+           to=CT_fishing_entity,
+           DemersPelag
+  ) %>% 
+  summarise(value=n()
+  ) #%>%
+  # filter(DemersPelag == "demersal") %>%
+  # select(-DemersPelag)
+
+####________________###
+# Circulize package ####
+# https://jokergoo.github.io/circlize_book/book/
+####________________###
+
+# To set links color 
+Bins <- as.numeric(cut(Top_Spp_Countries$value,breaks = 5)) # By size of sharing
+
+# To get country's flags... https://flagpedia.net/download
+flags <- c(paste("Temporal_Data/flags-mini/",list.files("Temporal_Data/flags-mini/"),sep=""))
+
+# List of Ecosystems
+Classification <- Top_Species %>% group_by(DemersPelag) %>% summarise(n()) %>%  pull(DemersPelag)
+
+####________________ PLOT PER ECOSYSTEM _____________________ ###
+
+for(s in 1:2){ # sclae loop
+  for(i in 1:length(Classification)) {
+    # for(i in 1:2) { # for testing
+
+    # Set scales to plott both absolut and proportional values
+    if(s == 1){
+      Scales <- "TRUE"
+    }else{
+      Scales <- "FALSE"
+    }
+
+    # Saving the plot
+    Plot_name <- paste(Figures_Path,Classification[i],Scales,".tiff",sep="")
+    tiff(Plot_name, width = 5, height = 5, units = 'in', res = 500)
+
+    # Subsetting the data for each plot
+    DemersPelag_i <- Classification[i]
+
+    Data <- Top_Ten_Spp_Countries %>% 
+      filter(DemersPelag %in% DemersPelag_i) %>% 
+      select(-3)
+
+    # Use to set links' colors to each species
+    Speceis_cols <- Data %>% group_by(from) %>% summarise(n()) %>% pull(from)
+
+    # The base plot
+    circos.clear()
+    chordDiagram(Data, 
+                 annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
+                 annotationTrackHeight = c(0.001, 0.1), # set links close to the axis
+                 directional = 1, # direction of arrows
+                 direction.type = c("diffHeight", "arrows"), # use arrows
+                 grid.col = "grey",
+                 # if col == Bins then colors will change depending of value
+                 # col = ifelse(Bins == 1,"#046C9A", # deep blue
+                 #              ifelse(Bins == 2,"#78B7C5", #light blue
+                 #                     ifelse(Bins == 3,"#EBCC2A", #yellow
+                 #                            ifelse(Bins == 4, "#E1AF00", #cream
+                 #                                   "#F21A00")))), #red
+                 # if col == Species_cols then colors will change depending of species
+                 col = ifelse(Data$from == Speceis_cols[1],"#FF0000", # deep blue
+                              ifelse(Data$from == Speceis_cols[2],"#00A08A", #light blue
+                                     ifelse(Data$from == Speceis_cols[3],"#F2AD00", #yellow
+                                            ifelse(Data$from == Speceis_cols[4], "#F98400", #cream
+                                                   "#5BBCD6")))), #red
+                 # link.arr.col = wes_palette("Zissou1"), 
+                 link.arr.type = "big.arrow",# make links big arrows
+                 diffHeight = uh(-0.5, "mm"), # brings the arrow to the bottom of the source
+                 scale = Scales, # fraction of each species to total share of each country instead of absolute value
+                 preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Data))))) # I have no idea but helps with the labels
+    )
+
+    #  Function to inlcude other layers
+    circos.track(track.index = 1, panel.fun = function(x, y) {
+      xlim = get.cell.meta.data("xlim")
+      xplot = get.cell.meta.data("xplot")
+      ylim = get.cell.meta.data("ylim")
+      sector.name = get.cell.meta.data("sector.index")
+
+      # Add labels
+      circos.text(mean(xlim),
+                  ylim[1],
+                  sector.name,
+                  facing = "clockwise",
+                  niceFacing = TRUE,
+                  adj = c(-0.2, 0.5),
+                  col = "black",
+                  cex = 0.6) # size of labels
+
+      # Add country's flags instead of names (still need to link names to falgs)
+
+      # library(EBImage)
+      # pos = circlize:::polar2Cartesian(circlize(CELL_META$xcenter, CELL_META$ycenter))
+      # image = EBImage::readImage(flags[CELL_META$sector.numeric.index])
+      # 
+      # rasterImage(image,
+      #             xleft = pos[1, 1] - 0.006, 
+      #             ybottom = pos[1, 2] - 0.005,
+      #             xright = pos[1, 1] + 0.05,
+      #             ytop = pos[1, 2]+ 0.04
+      #             )
+
+      # END FLAGS TRYOUT
+
+      # Set plot Title
+      Title <- paste("Top",Classification[i], "Species",sep =" ")
+      title(Title)
+
+    }, bg.border = NA) #end of circos.track
+
+    dev.off()
+  } # close for loop
+} #close scale loop
+
+```
+
+### Species status (SAU methods)
+
+Note that (n), the number of ‘stocks’ is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area is at least 1000 tonnes.
+
+ 1) The first and last reported landings are at least ten years apart;
+
+2) There are at least five years of consecutive catches; and
+
+3) The catch in a particular area (LME) is at least 1,000 tonnes.
+
+Once those tresholds are met, the status of the species is determined as follows:
+
+- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
+- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
+- Exploited	Landing > 50% of max. landing
+- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
+- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
+
+*Notes* = 3 years average mean
+
+```{r Species_Status, eval = T, echo =F}
+
+CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+# SAU relations between INDEX and Country's EEZs
+EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
+EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
+colnames(EEZ_CellID) <- c("EEZID","INDEX")
+
+Index_Code <- EEZIDs_List %>% 
+  left_join(EEZ_CellID) %>% 
+  rename(Territory = Name)
+
+Spp <- GetSppDist(600004, Model = "SAU_C", Coord = CoorG)
+
+Data <- Spp %>% 
+  gather("Year","Value",CATCH.1:CATCH.65) %>% 
+  arrange(INDEX) %>% 
+  mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
+  left_join(Index_Code) %>% 
+  filter(!is.na(EEZID),
+         Value > 0) %>% 
+  group_by(Species,Year,EEZID,Territory) %>% # Total catch per country
+  summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
+  group_by(Species,Territory,EEZID,Year) %>% 
+  mutate(RMean = rollmean(x = Total_Catch, 5, align = "right", fill = Total_Catch)) %>% 
+  group_by(Species,Territory,EEZID)
+
+# head(Data)
+
+# Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
+ Tresholds <- Data %>% 
+  arrange(Territory) %>% 
+  group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
+            Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
+            Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
+            ) %>% 
+   gather("Step","Treshold",Years_appart:Catch_over) %>% 
+   filter(Treshold == "Yes")
+
+ # Evaluate stocks
+
+ # Filter data that does not satisfy tresholds
+
+ Landings_Peaks <- Data %>% 
+  group_by(Species,Territory) %>% 
+  summarise(Max_Peak = max(RMean,na.rm=T))
+
+ Eval_Data <- Data %>% 
+  semi_join(Tresholds,
+            by = c("Species","Territory")) %>% 
+   left_join(Landings_Peaks,
+             by = c("Species","Territory"))
+
+ Peak_Year <- Eval_Data %>% 
+   filter(RMean == Max_Peak) %>% 
+   select(Species,Territory,EEZID,Y_Max_Peak = Year)
+
+ Post_Max_Min <- Eval_Data %>% 
+   left_join(Peak_Year) %>% 
+   filter(Year > Y_Max_Peak) %>% 
+   group_by(Species,Territory,EEZID) %>% 
+   summarise(Post_Max_Min = min(RMean,na.rm=T))
+
+ Y_Post_Max_Min <- Eval_Data %>% 
+   left_join(Post_Max_Min) %>% 
+   filter(RMean == Post_Max_Min) %>% 
+   select(Species,Territory,EEZID,Y_Post_Max_Min = Year)
+
+ Data_Status <- Eval_Data %>% 
+   left_join(Peak_Year,
+             by = c("Species","Territory","EEZID")) %>%
+   left_join(Post_Max_Min,
+             by = c("Species","Territory","EEZID")) %>% 
+   left_join(Y_Post_Max_Min,
+             by = c("Species","Territory","EEZID")) %>% 
+   rename(Y_RMean = Year) %>% 
+   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
+                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
+                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                      "No Status")
+                                        )
+                                 )
+                          )
+   )
+   ) %>% 
+   filter(Y_RMean > 2004) %>% 
+   group_by(Species,EEZID,Territory,Status) %>% 
+   summarise(n_Status= n()) %>% 
+   group_by(Species,EEZID,Territory) %>% 
+   top_n(1,n_Status)
+
+ # Manual estimation
+
+ data.frame(
+   Y_RMean = 1980,
+   RMean = 642187,
+   Max_Peak = 1298712,
+   Y_Max_Peak = 1990,
+   Post_Max_Min = 681967,
+   Y_Post_Max_Min = 2010,
+   Y_RMean = 2014
+ ) %>% 
+   mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
+                          ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
+                                 ifelse(RMean > Max_Peak*0.50,"Max Exploited",
+                                        ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))," Over Exploited",
+                                               ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
+                                                      "NA")
+                                        )
+                                 )
+                          )
+   )
+   )
+
+```

### 2019-12-18 Initial_Analysis.Rmd
Modified figure 4 to inlcude top 5 countries with more catch

@@
   "janitor", # for data cleaning
+  "tidytext" # to order the facet wrap https://juliasilge.com/blog/reorder-within/
   # "circlize", # For circular plot
@@
     legend.position  = "right",
-    legend.title = element_text(size = 14),
-    legend.text = element_text(size = 12),
-    strip.text.x = element_text(size = 12, colour = "black"),
+    legend.title = element_text(size = 14, face = "bold"),
+    legend.text = element_text(size = 16),
+    strip.text.x = element_text(size = 12, colour = "black", face = "bold"),
     strip.text = element_text(size = 12)
@@
          fishing_entity = ct_fishing_entity,
-         eez_neighbour = neighbour)
+         eez_neighbour = neighbour) %>% 
+  mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))
 
@@
   filter(!is.na(individual),
-         !str_detect(individual, "(")
+         !str_detect(individual, ".\\(.") # remove associated territories
          )%>% 
@@
            alpha=0.5) +
-  scale_fill_manual("Catch Trend",
+  scale_fill_manual("Catch Category",
                     values = c(
@@
   summarise(
-    n_countries = length(unique(Territory))
+    n_countries = length(unique(fishing_entity))
   ) %>% 
@@
 Species_list <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>% 
+  mutate(scientific_name = paste(genus,species)) %>% 
   pull(scientific_name)
@@
 Species_Data <- Tresholded_T_Data %>% 
-  group_by(TaxonKey) %>% 
-  summarise(n_trans_spp = length(unique(Territory))) %>% 
+  group_by(taxon_key) %>% 
+  summarise(n_trans_spp = length(unique(fishing_entity))) %>% 
   left_join(Exploited_Species) %>%
-  rename(scientific_name = TaxonName) %>% 
+  rename(scientific_name = taxon_name) %>% 
   left_join(Species_environ_list) %>%
-  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
+  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",
+                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bento-pelagic",paste(DemersPelag)
+                                     )
+                              ),
          n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp),
-         Category == ifelse(DemersPelag %in% c("Developing","Rebuilding","Category A"),
-                            ifelse(DemersPelag == "Max Exploitation","Category B",
-                                   ifelse(DemersPelag %in% c("Overfished","Collapsed","Category C"),"Category C", "No Category")
-                            )
-         )
+         DemersPelag = str_to_title(DemersPelag)
          ) %>% 
@@
   filter(value > 20)  # remove all species under 20 (way too many to plot!)
+
+#### Exosystem based plots
+
+Top_5_Ecosystem <- Species_Data %>% 
+  rename(taxon_name = individual) %>% 
+  group_by(group) %>% 
+  top_n(5,value)
+
+# If you want to show revenue
+# Country_Spp_Data <- sau_eez_fes %>% 
+#   group_by(fishing_entity_id,fishing_entity) %>% 
+#   summarise(n=n()) %>% 
+#   select(-n) %>% 
+#   left_join(SAU_Revenue_Data) %>% 
+#   left_join(Tresholded_T_Data) %>% 
+#   left_join(Exploited_Species) %>% 
+#   left_join(Top_5_Ecosystem) %>% # includes the groups
+#   filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>% 
+#   group_by(fishing_entity,group) %>% 
+#   summarise(top_catch = sum(mean_value)/1000000) %>%  # Million
+#   group_by(group) %>% 
+#   top_n(5)
+
+  # If you want to show catch  
+Country_Spp_Data <- Tresholded_T_Data %>%
+  left_join(Exploited_Species) %>%
+  left_join(Top_5_Ecosystem) %>% # includes the groups
+  filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
+  mutate(taxon_key = as.character(taxon_key)) %>%
+  left_join(SAU_Catch_Data,
+            by = c("eez_name","taxon_key")
+  ) %>%
+  group_by(fishing_entity,group) %>%
+  summarise(top_catch = sum(total_catch)) %>%
+  group_by(group) %>%
+  top_n(5) %>% 
+  mutate(
+    fishing_entity = ifelse(fishing_entity == "Korea (South)", "S. Korea",
+                            ifelse(fishing_entity == "Russian Federation","Russia",
+                                   ifelse(fishing_entity == "Papua New Guinea", "N.Guinea",
+                                          ifelse(fishing_entity == "Solomon Isl.", "Solomon",fishing_entity)))
+    )
+  )
 
@@
 ### ------------------- ###
-ggplot(Species_Data, 
+Spp_circular <- ggplot(Species_Data, 
        aes(x=as.factor(id), 
@@
             alpha=1,
-            size=2.5,
+            size=3,
             angle= label_data_rest$angle,
@@
                 label=individual,
-                hjust=hjust), 
-            color="black",
+                hjust=hjust,
+                color = group), 
+            # color="black",
             fontface="bold.italic",
             alpha=1,
-            size=2.5,
+            size=3,
             angle= Top_label_data$angle,
-            inherit.aes = FALSE) +
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
   # Add base line information
@@
   theme(
-    legend.position = c(0.5,0.5),
+    legend.position = c(1,0.11),
+    legend.text = element_text(size = 13),
+    legend.title = element_text(size = 14, face = "bold"),
     axis.text = element_blank(),
@@
     panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
+    # plot.margin = unit(c(-3.5, -3.5, -4, -4), "cm") #top, right, bottom, left
+    plot.margin = unit(rep(-3.5,4),"cm")
   ) +
@@
                     values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                               wes_palette(n = 4, name = "GrandBudapest2")
+                               wes_palette(n = 3, name = "GrandBudapest2")
                     ),
@@
                       values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                                 wes_palette(n = 4, name = "GrandBudapest2")
+                                 wes_palette(n = 3, name = "GrandBudapest2")
                       ),
@@
 
-ggsave(
-  plot = last_plot(),
-  width = 14,
-  height = 13,
-  units = "in",
-  filename = "Species_circular_over20.png",
-  path = Figures_Path
+#### Ecosystem  preference based plots
+
+Ecosystem_plots <- Country_Spp_Data %>%
+  ungroup() %>% 
+  mutate(name = reorder_within(fishing_entity,top_catch,group)) %>% # to order the facet wrap
+  ggplot() +
+  geom_bar(
+    aes(
+      x = name,
+      y = top_catch/1000,
+      fill = group
+    ), 
+    stat = "identity"
+  ) +
+  labs(x = "",
+       y = "Catch (Thousand tonnes)") +
+  scale_fill_manual("",
+                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
+                               wes_palette(n = 3, name = "GrandBudapest2")
+                    ),
+                    na.value = "white"
+  ) +
+  facet_wrap(~group,
+             nrow=2,
+             scales = "free") +
+  ggtheme_plot() +
+  scale_x_reordered() +
+  theme(legend.position = "",
+        axis.text.x = element_text(size = 11,
+                               angle = 0,
+                               face = "plain"),
+          strip.background = element_blank(),
+  strip.text.x = element_blank()
+  )
+
+### Combined plot
+
+spp_plot <- ggdraw() +
+  # Circular plot
+  draw_plot(Spp_circular, x = 0, y = 0.305, width = 1, height = 0.60) +
+  # Environmental maps
+  draw_plot(Ecosystem_plots, x = 0.02, y = -0.029, width = 0.95, height = 0.26) +
+  # Labeks
+  draw_plot_label(label = c("A", "B"), 
+                  size = 30,
+                  x = c(0, 0), 
+                  y = c(1, 0.27)
+  )
+
+save_plot(
+  paste(Figures_Path,"spp_circular_catch_country.png",sep=""),
+  # "spp_plot.png",
+  spp_plot,
+  base_height = 14,
+  base_width = 14
 )

### 2019-12-18 Initial_Analysis.Rmd
exploring vulnerabillity analysis

@@
   "janitor", # for data cleaning
-  "tidytext" # to order the facet wrap https://juliasilge.com/blog/reorder-within/
+  "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
   # "circlize", # For circular plot
@@
 #   select(2:3)
+
+# Vulnerabillity Data from William
+cc_vul <- fread(paste(Data_Path,"Species_Data/vulspp310817.csv", sep ="")) %>% 
+  rename(taxon_key = V1,
+         ccvul = V2)
+
+fish_vul <- fread(paste(Data_Path,"Species_Data/FishSenIndex.csv", sep ="")) %>% 
+  clean_names()
 
@@
   base_width = 14
+)
+
+```
+
+# Vulnerabillity Assesment
+
+```{r Vulnerabillity, eval = T, echo = F}
+
+trans_vul <- Tresholded_T_Data %>% 
+  group_by(taxon_key) %>% 
+  summarise(
+    n_countries = length(unique(eez_name))
+  ) %>% 
+  left_join(cc_vul) %>% 
+  left_join(fish_vul) %>% 
+  ggplot() +
+  geom_point(
+    aes(
+      x = fishvul,
+      y = n_countries
+    )
+  )
+
+# climate change vulnerabillity?
+modcc <- lm(n_countries~ccvul, data = trans_vul)
+modcc
+summary(modcc)
+
+# fishing vulnerabillity?
+modfis <- lm(n_countries~fishvul, trans_vul)
+modfis
+summary(modfis)
+
+# Together?
+
+modccfis <- lm(n_countries~fishvul + ccvul, trans_vul)
+modccfis
+summary(modccfis)
+
+### What about... Catch Status...
+
+taxon_status <- Tresholded_T_Data %>% 
+  group_by(taxon_key) %>% 
+  summarise(
+    n_countries = length(unique(eez_name))
+  ) %>% 
+  left_join(Status_Data)
+
+modcs <- lm(n_countries~status, taxon_status)
+modcs
+summary(modcs)
+
+ggplot(taxon_status) +
+  geom_boxplot(
+    aes(
+      x = status,
+      y = n_countries
+    )
   )

### 2019-12-23 Manuscript_Draft.Rmd
x
Updates in results and discussion

@@
 
-## Methods summary (250/250 words)
+<!-- ## Methods summary (250/250 words) -->
 
@@
 1A).
-Between 2005 and 2014, national fleets targeting shared stocks within EEZs landed an average of **69.2** million tonnes, representing **64**% of the EEZ-global catch, and generating USD **79.7** million in fishing revenue, equivalent to **49.8**% of the total revenue of the same period.
-These values are higher than previously estimated [@Teh] and higlight the importance of these stocks at the global level.
+Between 2005 and 2014, national fleets targeting shared stocks within EEZs landed an average of **69.2** million tonnes, representing **64**% of the EEZ-global catch, and generating USD **79.7** million in fishing revenue.
+This is equivalent to **49.8**% of the global revenue of the same period.
+These values are higher than previously estimated reinforcing the importance of these stocks at the global level [@Teh].
 
-Transboundary species are particularly important at the regional and national level.
-In terms of catch and revenue, Eastern Asia and Latin America and the Caribbean are the higher zones (Fig 1B).
-Particular for counties in North America (Bermuda, Canada, Greenland, and the US), a moderate amount of catch (3.4 thousand tons) are worth 11.7 billion USD, highlighting the importance of transboundary species to the economy of the region.
-The EEZs along Western Eurpe, in turn, are home of **X** species responding to the joint fisheries management policy established by the European Union.
-In here, quotas are allocated by species and regulatory area [@Melnychuk:2017gh], making this region **unique** in terms of joint management of a high numer of shared stocks.
+Transboundary species are particulary important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from the rest in tn terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+The large variation in revenue from these regions is driven by China (USD 6,279 million), in E.
+Asia and the US (USD 9,605 million) in N.
+America who contribue 55% and 83% of the region's revenue, respectiveley.
+Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with more revenue from transboundary species.
 
-At the country level, transboundary species are most valuable for the United States (USD 9,605 million), Russia (USD 6,361 million), China (USD 6,279 million) and Peru (USD 5,211).
-On the other hand, EEZs like that of Portugal, the Mediterranean side of Spain, Senegal, and the UK are rich in transboundary species (n > 110), but these do not represent a large amount of revenue, comparativeley.
-China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018], is the only country categorized high in both number of transboundary species (n = 119) and revenue.
+Catches, however, are only significantly different in E.
+Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018], getting around 1/3 of its capture from transboundary species.
 For the US, 16 species make up 90% of the revenue from transboudary species, with American scallop (*Placopecten magellanicus*) shared with Canada in Georges Bank [@https://elischolar.library.yale.edu/cgi/viewcontent.cgi?article=1008&context=fes-pubs] contributing 41.8% or the revenue.
 Russia shares the largest fished species in the world, Alaskan polllock (*Theragra chalcogramma*) [@SOFIA2018], with both Japan and the US.
-For Russia, this fishery is responsible for 50% of the revenue from transboundary species with other eight species comprising the 90% of revenue.
+Rhis fishery is responsible for 50% of the Russian revenue from transboundary species, with other eight species comprising the 90% of revenue.
 In the case of Peru, Peruvian anchoveta (*Engraulis ringens*) and jumbo squid (*Dosidicus gigas*), both shared with Chile, represent almost 90% of the revenue from transboundary species, with anchoveta accounting for 79%.
-
-These results hilights the importance of transboundary species not only at the global and regional levels, but also at the country level.
 
@@
 The number of species is represented in the EEZ while the revenue is represented in the land polygon.
-B) Regional revenue (left) and catch (right) contribution of tranbsoundary species."}
+B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.Points = mean +- sd."}
 
@@
 The number of species is represented in the EEZ while the revenue is represented in the land polygon.
-B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.**](./Figures/Fig1.png)
+B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.
+Points = mean +- sd.**](./Figures/Fig1.png)
 
@@
 
-![**Number of transboundary and discrete species by country and continent**](./Figures/Fig2.png)
+There is no significant difference in the exploitaion rate of transboundary species between continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05) as most species are fished over 50% of their historical maximum peak (Category C) in all continents, but Oceania (Fig.2).
+However, the number of species exploited by each country in each category significantly differs from each other (one-way ANOVA *F*(5,442), *f* = 322.9, *p* < 0.001, $\alpha$ = 0.05).
+Overall, most transboundary species are fished over 50% of their once maximum peak (Category C) suggesting that their current exploitation rate is over the maximum sustainable yield [@Kleisner:2011wn].
 
@@
 Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*)[@Diekert:2010gp], and between Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-However, few evidence exists today regarding the true efficiency of transboundary fisheries plans.
+
 Indeed, there are some successful bilateral management plans for species such as Pacific Halibut between Canada and the US as well [@REference?] and multilateral treaties like the Pacific Nauru Agreement that manages 30% of global skipjack tuna in the South Pacific Islands [@Aqorau:2018bh].
@@
 2).
-While these catch trends do not reflect stock status [@@Branch:2011br], they could reassemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
+While these catch trends do not reflect stock status [@Branch:2011br], they could reassemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
 The rebuilding of a transboundary species could be strongly impacted by uncoordinated efforts of countries harvesting the same species but with different objectives [@Ref].
 
-Management of transboundary fisheries needs to be looking forward.
-As species shift their known distributions to cope with a changing ocean, new transboundary species will arise, challenging the management of shared stocks worldwide [@Pinsky].
-Conflicts in regions with a high abundance in transboundary species will likely be exacerbated by climate change, as seen in the ongoing dispute between the European Union, Norway, Iceland and the Faroe Islands over mackerel (**species**) [@Spijkers:2017ij].
-Understanding how climate change will affect the biogeography of marine species, and notably the number of countries' EEZ it spans is a key element to the design of effective long-term spatial-based fisheries management [@Alexa, @Song:2017iua].
+```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category, country, and continent.
+Category A, fishing between 10%-50% of max catch peak after a drop larger than 10% of max peak; Category B, fishing over 50% of max catch peak; Category C, fishing is between 10-50% of max catch peak or less than 10%"}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
+
+![**Number of transboundary species by catch category, country, and continent.
+Category A, fishing between 10%-50% of max catch peak after a drop larger than 10% of max peak; Category B, fishing over 50% of max catch peak; Category C, fishing is between 10-50% of max catch peak or less than 10%**](./Figures/Fig2.png)
 
 Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@REF].
-Maybe not surprisingly, highly migratory pelagic-oceanic species such as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are among the more shared resources in the world with a median of 40 nations sharing these resources.
+Not surprisingly, highly migratory pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are among the more shared resources in the world with a median of 40 nations sharing these resources (Fig 3.).
 These species are very important in terms of economic value as they (global) average revenue exceeds USDXXX.
+
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these might be cosmopolitan but not necessarily highly migratory (e.g.
@@
 The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even if a population swims between the borders of two nations, their larvae could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+
 Moreover, many coastal communities, specially in developing regions, and highly dependent on fishing local fish (e.g.
@@
 ![**Number of countries shared by transboundary species. Showing only species that share > 20 countries**](./Figures/Fig3.png)
+
+Management of transboundary fisheries needs to be looking forward.
+As species shift their known distributions to cope with a changing ocean, new transboundary species will arise, challenging the management of shared stocks worldwide [@Pinsky].
+Conflicts in regions with a high abundance in transboundary species will likely be exacerbated by climate change, as seen in the ongoing dispute between the European Union, Norway, Iceland and the Faroe Islands over mackerel (**species**) [@Spijkers:2017ij].
+Understanding how climate change will affect the biogeography of marine species, and notably the number of countries' EEZ it spans is a key element to the design of effective long-term spatial-based fisheries management [@Alexa, @Song:2017iua].
 

### 2019-12-23 Initial_Analysis.Rmd
Updataed results

@@
   "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
-  # "circlize", # For circular plot
+  "cowplot", # for figures 1 and 3
   # "ggimage", #for reading images to the circular plot
@@
 
-- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
-- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
-- Exploited	Landing > 50% of max. landing
-- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
-- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
+- Rebuilding (Recovering),	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
+- Developing,	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
+- Max Exploited,	Landing > 50% of max. landing
+- Over exploited,	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
+- Collapsed,	Year of landing > year of max. landing AND landing is < 10% of max. landing
 
@@
 
+# RFMO Analysis
+
+```{r RFMO_Data, eval = F}
+
+RFMO_Data <- read.delim("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/RFMO_procedure_outcome.csv")
+
+x <- RFMO_Data %>% 
+  mutate(
+    x = gsub("<.*?>", "", RFMO_Data$primary_species),
+    y = gsub("[\\(\\)]", "", regmatches(x, gregexpr("\\(.*?\\)", x)))
+  )
+
+# Save to remove "" and pass to colomuns in excell
+# write.csv(x,
+#           "rfmos.csv")
+
+rfmos <- read.csv("~/Github/FishForVisa/rfmos.csv")
+  View(rfmos)
+
+list <- rfmos$Taxa
+
+clean_rfmos <- rfmos %>% 
+  gather("taxa","taxon_name",y:X.21) %>% 
+  filter(taxon_name != "") %>% 
+  select(RFMO_name = name,
+         contracting_parties,
+         area,
+         taxon_name)
+
+# write_csv(clean_rfmos,
+#           "clean_rfmos.csv")
+
+### Join with exploited species
+
+clean_rfmos <- clean_rfmos %>% 
+  left_join(Exploited_Species)
+
+```
+
 # Results
@@
 # Requires Clean_sau_eez_fes
-
+# Data <- Results_Trans
 CleanResults <- function(Data){
@@
     gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
-    gsub(" R<e9>union (France)","Réunion",.)
+    gsub("R<e9>union (France)","Réunion",.)
 
@@
 
-# x <- Clean_Results(Discrete_Data)
-
 ```
@@
 # Set Jurisdiction to EEZ or RFMO
-Jurisdiction <- "EEZ"
+# Jurisdiction <- "EEZ"
+Jurisdiction <- "RFMO"
 
@@
   group_by(eez_name,fishing_entity) %>% 
-  summarise(n())
+  summarise(n()) %>% 
+  ungroup() %>% 
+  ### Manually Fix names for estimating catch
+  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece",
+                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
+                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
+                                         ifelse(fishing_entity =="Italy","Italy",
+                                                ifelse(eez_name =="Chile (mainland)","Chile",
+                                                       ifelse(fishing_entity =="Brazil","Brazil",
+                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
+                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
+                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
+                                                                                   paste(eez_name))
+                                                                            )
+                                                                     )
+                                                              )))))),
+         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
+         )
+  )
 
@@
     fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
-    # fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
     fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
@@
     fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
-    fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
+    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
+    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
+    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
+    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),,
+    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
   )
@@
                          layer =file_path_sans_ext(fnam_world_land)) %>% 
-  rename(fishing_entity = NAME)
+  rename(fishing_entity = NAME) %>% 
+  mutate(
+    fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
+    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
+    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
+    fishing_entity = gsub("Dem. Rep. Congo", "Congo, R. of",fishing_entity),
+    fishing_entity = ifelse(fishing_entity=="Congo", "Congo (ex-Zaire)",paste(fishing_entity))
+         )
+
+# View(unique(World_land_sf$fishing_entity))
 
@@
   rename(eez_name = Name)
+
+# View(unique(World_sf$eez_name))
 
@@
   ungroup() %>% 
-  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
-                                 ),
+  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
+                                 # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
+                                 # ),
          Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
@@
   group_by(sub_region) %>% 
-  summarise_if(is.numeric,sum,na.rm=T)
+  summarise_if(is.numeric,c(sum = sum,
+                            m = mean,
+                            sd = sd),
+               na.rm=T)
 
@@
 label_data_rev <- Subregion_Data_Trans %>% 
-  arrange(Total_USD) %>% # soo it looks like a nice snail :)
+  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
   mutate(
@@
 label_data_catch <- Subregion_Data_Trans %>% 
-  arrange(fishing_entity_catch) %>% # soo it looks like a nice snail :)
+  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
   mutate(
@@
   )
-
-```
-
-### EEZ Map of Transboundary Species
-
-Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country
-
-```{r Territory_Map_Round, eval =F, echo =F}
 
@@
 
+```
+
+### EEZ Map of Transboundary Species
+
+Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country
+
+```{r Territory_Map_Round, eval =F, echo =F}
+
 # Create labels for legend
@@
 Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
-# Labels_Trans <- c(paste(unique(Transboundary_Spp$Bins)),"NA")
-# Labels_Rev <- unique(Revenue_Country$Bins)
-
 Labels_Rev <- c("(1-10]",paste(Bins_Rev[2:5]))
@@
   geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
-  # scale_fill_gradientn(colours = pal,
-  #                      na.value = "white") +
-  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
-  # rev(wes_palette(n = 4, name = "Darjeeling2"))
-  # ),
-  # na.value = "white"
-  # ) +
   scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
@@
   ),
-  # na.value = "white"
   na.translate = F
   ) +
-  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
-  #                    na.value = "white"
-  # ) +
   ggtheme_map() +
@@
     legend.box.margin = margin(t = -54, l = 130),
-    legend.text = element_blank()#,
+    legend.text = element_blank(),
   ) +
   guides(fill = guide_legend(nrow = 1))
-
-# ggsave("Map.png",
-#        Map,
-#         width = 10,
-#          height = 10,
-         # units = "in")
-# Map
 
@@
 # Revenue Plot
-# Set plot limits
-max_lim <- max(Subregion_Data_Trans$Total_USD)
 
@@
 
-Rev_Plot <- ggplot(data = Subregion_Data_Trans, 
-                   aes(x=reorder(id,Total_USD),
-                       y=Total_USD, 
-                       fill=Total_USD
+# Set plot limits
+max_lim <- max(Subregion_Data_Trans$Total_USD_sum) +10
+
+Rev_Plot <- ggplot(
+  # Regional plots
+  data = Subregion_Data_Trans, 
+  aes(
+    x=reorder(id,Total_USD_sum),
+    y=Total_USD_sum, 
+    fill=Total_USD_sum
   )
 ) +    
-  ylim(-1500, max_lim+10)+
+  ylim(-1500, max_lim) +
   geom_bar(stat="identity") +
+  # Regional averages
+  geom_point(data = Subregion_Data_Trans,
+             aes(
+               x=reorder(id,Total_USD_sum),
+               y=Total_USD_m
+             ),
+             colour = "black",
+             alpha = 0.5
+  ) +
+  # Regional sds
+  geom_errorbar(
+    aes(
+      ymin=ifelse(Total_USD_m-Total_USD_sd <= 0,0,Total_USD_m-Total_USD_sd), # sets lower to 0
+      ymax=Total_USD_m+Total_USD_sd
+    ), 
+    width=.2,
+    position=position_dodge(.9),
+    alpha = 0.5) +
+  # Looking good
   theme_minimal() +
   theme(
-    legend.position = c(0.74,0.60),
+    legend.position = c(0.73,0.60),
     axis.text = element_blank(),
@@
   # Base line
-  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
-               colour = "black", size=0.1, inherit.aes = FALSE) +
+  # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
+  #              colour = "black", size=0.1, inherit.aes = FALSE) +
   coord_polar(start = 0) + 
@@
             aes(x=id,
-                y=Total_USD+10,
-                # label=round(Total_USD_Billion),
+                y=Total_USD_sum+10,
                 label=sub_region,
@@
   scale_fill_gradientn("",
-                       colours = pal) +
+                       colours = pal,
+                       limits = c(0,16500),
+                       breaks = seq(0,16000,4000)) +
   guides(fill = guide_colorbar(label.position = "left")
@@
 
+###____________###
 ### Catch plot
-
-max_lim <- max(Subregion_Data_Trans$fishing_entity_catch)
+###____________###
+max_lim <- max(Subregion_Data_Trans$fishing_entity_catch_sum) +1
 
 Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
-                     aes(x=reorder(id,fishing_entity_catch),
-                         y=fishing_entity_catch, 
-                         fill=fishing_entity_catch
+                     aes(x=reorder(id,fishing_entity_catch_sum),
+                         y=fishing_entity_catch_sum, 
+                         fill=fishing_entity_catch_sum
                      )
 ) +    
-  ylim(-1.5, max_lim+1) +
+  ylim(-2.1, max_lim) +
   geom_bar(stat="identity") +
+  # Regional averages
+  geom_point(data = Subregion_Data_Trans,
+             aes(
+               x=reorder(id,fishing_entity_catch_sum),
+               y=fishing_entity_catch_m
+             ),
+             colour = "black",
+             alpha = 0.5
+  ) +
+  # Regional sd's
+  geom_errorbar(
+    aes(
+      ymin=ifelse(fishing_entity_catch_m-fishing_entity_catch_sd <= 0,0,fishing_entity_catch_m-fishing_entity_catch_sd),
+      ymax=fishing_entity_catch_m+fishing_entity_catch_sd
+    ), 
+    width=.2,
+    position=position_dodge(.9),
+    alpha = 0.5) +
   theme_minimal() +
@@
     legend.position = c(0.1,0.60),
-    # legend.position = "right",
     axis.text = element_blank(),
@@
     plot.margin = margin(0,-10,-6,-5,"cm")
-    # plot.margin = margin(0,0,-5,0,"cm")
   )  +
   # Base line
-  geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
-               colour = "black", size=0.1, inherit.aes = FALSE) +
+  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
+  #              colour = "black", size=0.1, inherit.aes = FALSE) +
   coord_polar(start = 0) + 
@@
             aes(x=id,
-                y=fishing_entity_catch+0.1,
-                # label=round(Total_USD_Billion),
+                y=fishing_entity_catch_sum+0.1,
                 label=sub_region,
@@
   scale_fill_gradientn("",
-                       colours = pal)
-
-# Catch_Plot
+                       limits = c(0,16.5),
+                       breaks = seq(0,16,4),
+                       colours = pal
+
+  )
 
 ## Joining everything in one ploit
-
-# library(ggpubr)
-# library(cowplot)
 
@@
   # Revenue circular
-  draw_plot(Rev_Plot, x = 0.1, y = 0.07, width = 0.5, height = 0.4) +
+  draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
   # Catch circular
-  draw_plot(Catch_Plot, x = 0.45, y = 0.07, width = 0.5, height = 0.4) +
-
+  draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
   # Labeks
@@
                   size = 8,
-                  x = c(0.333,0.493), 
-                  y = c(0.30,0.28)
+                  x = c(0.330,0.485), 
+                  y = c(0.31,0.29)
   )
@@
 save_plot(
-  # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
-  "Plot.png",
+  paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
+  # "Plot.png",
   plot,
@@
 
-PeRu <- c("Peru", "Russian Federation","Russia", "Chile", "United States of America","USA")
+PeRu <- c("Peru", "Russian Federation", "Chile", "USA")
 
@@
   filter(fishing_entity %in% PeRu) %>% 
-  select(1:2) %>% 
-  mutate(fishing_entity = ifelse(fishing_entity == "Russia","Russian Federation",
-                                 ifelse(fishing_entity == "United States of America","USA",fishing_entity))
-  )
+  select(1:2)
 
@@
 
+### Statistical differences
+
+We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.
+
+```{r statistics_fig1, eval = F, echo = T}
+
+### Using ANOVA to estimate significan differences within regions for revenue and catch of transboundary species
+
+### Prepare Data
+Subregion_Data_stats <- Revenue_Country %>% 
+  left_join(Catch_Country,
+             by = "fishing_entity") %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+  select(fishing_entity,sub_region,Total_USD,fishing_entity_catch)
+
+# Revenue ANOVA
+Rev_aov <- aov(Total_USD~sub_region, data = Subregion_Data_stats)
+Rev_aov
+summary(Rev_aov)
+
+# Df    Sum Sq Mean Sq F value  Pr(>F)    
+# sub_region   16  75628526 4726783    4.91 4.2e-08 ***
+# Residuals   157 151140183  962676
+
+#### There are significant differences. But between what?
+
+#  Post-hoc analysis
+TukeyHSD(Rev_aov)
+
+# Northern America sig than everyone except for Eastern Asia
+# Eastern Asia sig with everyone except with Eastern Europe and North Am.
+
+### Catch ANOVA
+
+Catch_aov <- aov(fishing_entity_catch~sub_region, data = Subregion_Data_stats)
+Catch_aov
+
+summary(Catch_aov)
+
+# sub_region   16  50.63   3.164   3.767 7.2e-06 ***
+# Residuals   155 130.22   0.840                    
+# ---
+# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+#  Post-hoc analysis
+TukeyHSD(Catch_aov)
+```
+
 ### RFMO Map of Transboundary Species
@@
 ```{r Territory_Map, eval =F, echo =F}
+
+head(RFMOs_sf)
 
@@
 World_sf_si <- RFMOs_sf %>%
-  rename(Territory = Name) %>% 
+  rename(eez_name = Name) %>% 
   st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
-  left_join(Transboundary_Spp, by ="Territory")
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
+  left_join(Transboundary_Spp, by ="eez_name")
+
+ICC <- World_sf_si %>% 
+  filter(eez_name == "ICCAT")
 
@@
 Plot <- ggplot() +
-  # geom_sf(data = World_sf_si_land) +
   geom_sf(data = World_sf_si,
-          aes(fill =  reorder(Bins_Plot,n_trans_spp)),
-          colour = "grey20", 
+          aes(
+            fill =  reorder(Bins_Plot,n_trans_spp),
+            colour = reorder(Bins_Plot,n_trans_spp)
+          ), 
           size = 0.1
           ) + # n_trans_spp or Bins
-  geom_sf_label(data = World_sf_si,
-                aes(label = Territory)) +
-  # geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
-  # scale_fill_gradientn(colours = pal,
-  #                      na.value = "white") +
-  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
-  # rev(wes_palette(n = 4, name = "Darjeeling2"))
-  # ),
-  # na.value = "white"
-  # ) +
+  # geom_sf(data = World_sf_si_land) +
   scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
@@
                                   "#F2AD00",#"#F2AD00", # Yellow
-                                  # "#F98400",#"#F98400", #Orange
+                                  "#F98400",#"#F98400", #Orange
                                   "#FF0000"#,"#FF0000" #Red
@@
   ) +
-  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
-  #                    na.value = "white"
-  # ) +
-  ggtheme_map()
-
-Plot_Name <- paste("RFMO_100_25_Bins.png", sep = "")
+  scale_colour_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+                                    "#00A08A",#"#00A08A", #green
+                                    "#F2AD00",#"#F2AD00", # Yellow
+                                    "#F98400",#"#F98400", #Orange
+                                    "#FF0000"#,"#FF0000" #Red
+  ),
+  na.value = "grey"
+  ) +
+  ggtheme_map() +
+  facet_wrap(~eez_name)
+
+Plot_Name <- paste("RFMO_100_25_Bins_facet.png", sep = "")
 
@@
   mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-  group_by(individual = fishing_entity,
-           group = Georegion,
-           observation = status) %>% 
-  summarise(Total_trans = sum(value,na.rm=T)) %>% 
-  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
-  filter(!is.na(individual),
-         !str_detect(individual, ".\\(.") # remove associated territories
-         )%>% 
-  select(individual,observation,group,value) %>% 
+  mutate(value = ifelse(value > 100,100,value)) %>% 
+  filter(!is.na(fishing_entity),
+         !str_detect(fishing_entity, ".\\(.") # remove associated territories
+         ) %>% 
+  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
   arrange(group,value) %>% 
@@
          )
-         )
+         ) %>% 
+  group_by(individual,observation,group) %>% 
+  summarise(value = sum(value))
+
+Status_Plot_Data <- tibble(
+  fishing_entity = rep(unique(Status_Data_Plot$individual),4),
+  observation = rep(unique(Status_Data_Plot$observation),153)
+) %>% 
+  left_join(UN_Regions) %>% 
+  rename(individual = fishing_entity) %>% 
+  full_join(Status_Data_Plot,
+            by = c("individual","observation")
+            ) %>% 
+  mutate(value = ifelse(is.na(value),0,value)#,
+         # group = ifelse(is.na(group),"Other",group)
+         ) %>% 
+  select(individual,observation,group=georegion,value) %>% 
+  filter(group != "other")
+
+# Summary for manuscipt
+
+Status_Data_Plot %>% 
+  mutate(value = ifelse(value <0, value*-1,value)) %>% 
+  group_by(observation) %>% 
+  summarise(tot=sum(value),
+            mean(value),
+            sd(value)) %>% 
+  arrange(desc(tot)) %>% 
+  view()
+
 ```
@@
 # Set a number of 'empty bar' to add at the end of each Georegion
-Char <- as.factor(Status_Data_Plot$group) # Set groups to factors
+Char <- as.factor(Status_Plot_Data$group) # Set groups to factors
 
@@
 # Transform data in a tidy format (long format)
-data <- Status_Data_Plot
+# data <- Status_Data_Plot
 
@@
 empty_bar <- 2
-nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
-to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
-colnames(to_add) <- colnames(Status_Data_Plot)
+nObsType <- nlevels(as.factor(Status_Plot_Data$observation))
+to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Plot_Data)) )
+colnames(to_add) <- colnames(Status_Plot_Data)
 to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
-to_add$value <- NA
-to_add$observation <- NA
+Status_Plot_Data <- rbind(Status_Plot_Data, to_add) # Problem converts to list
+# Status_data <- bind_rows(data,to_add)
+Status_Plot_Data <- Status_Plot_Data %>% arrange(group, individual)
+Status_Plot_Data$id <- rep( seq(1, nrow(Status_Plot_Data)/nObsType) , each=nObsType)
+
+# to_add$value <- NA
+# to_add$observation <- NA
 # to_add$individual <- to_add$group
 
-data <- Status_Data_Plot %>% 
-  bind_rows(to_add) %>% 
-  ungroup() %>% 
-  mutate(individual = forcats::fct_explicit_na(individual),
-         group = forcats::fct_explicit_na(group)) %>%
-  group_by(group,individual) %>% 
-  mutate(id = as.integer(individual),
-         order = as.integer(group))
-
-# data$id <- as.integer(data$individual,na.rm=T)
+# Status_data <- Status_Data_Plot %>%
+#   bind_rows(to_add) %>%
+#   ungroup() %>%
+#   mutate(individual = forcats::fct_explicit_na(individual),
+#          group = forcats::fct_explicit_na(group)) %>%
+#   group_by(group,individual) %>%
+#   mutate(id = as.integer(individual),
+#          order = as.integer(group))
 
 # Get the name and the y position of each label
-label_data <- data %>% 
+label_data <- Status_Plot_Data %>% 
   # filter(value > 0) %>% 
@@
 # prepare a data frame for base lines
-base_data <-  data %>% 
+base_data <-  Status_Plot_Data %>% 
   group_by(group) %>% 
@@
 
-data %>% 
-  # filter(observation != "Np Status") %>% 
+Status_Plot_Data %>%
   ggplot() + 
@@
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=1, size=1 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), linetype = "dashed", colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = -50, xend = start, yend = -50), linetype = "dashed", colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=1, size=0.3 , inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "black", alpha=1, size=0.3, inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "black", alpha=1, size=0.3, inherit.aes = FALSE ) +
+  geom_segment(data=grid_data, aes(x = end, 
+                                   y = -50, 
+                                   xend = start, 
+                                   yend = -50), colour = "black", alpha=1, size=0.3 , inherit.aes = FALSE ) +
   # Add text showing the value of each 100/75/50/25 lines
@@
                     # x = rep(max(data$id),3),
-                    x =c(1,0.2,1,0.8),
+                    x =c(0,0,0.2,0.2),
                     y = c(-50, 0, 50, 100),
@@
                     color="black", 
-                    size=5.5, 
+                    size=5, 
                     angle=0, 
@@
                     hjust=1) +
-
-  ylim(-100,101) +
+  # Add labels on top of each bar
+  geom_text(data=label_data,
+            aes(
+              x = id,
+              y = 101,
+              label=individual,
+              hjust=hjust),
+            color="black",
+            # fontface="bold",
+            alpha=1,
+            size=4,
+            angle= label_data$angle,
+            inherit.aes = FALSE ) +
+  # Continents labels
+  geom_text(data=base_data,
+            aes(x = title,
+                y = 85, 
+                label=group), 
+            hjust=c(1,1,1,0,0,0),
+            colour = "black",
+            # alpha=0, 
+            size=5,
+            fontface="bold",
+            inherit.aes = FALSE) +
+  ylim(-100,105) +
   theme_minimal() +
-  theme(
-    legend.position = c(0.93,0.14),
+  theme(legend.position = c(0.93,0.14),
     legend.key.size = unit(1,"cm"),
@@
     panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  # Add labels on top of each bar
-  geom_text(data=label_data,
-            aes(
-              x = id,
-              # x=reorder(id,order),
-                # y=max(tot,na.rm=T),
-                # y=tot +1,
-                y = 101,
-                label=individual,
-                hjust=hjust),
-            color="black",
-            fontface="bold",
-            alpha=1,
-            size=3,
-            angle= label_data$angle,
-            inherit.aes = FALSE ) +
+    plot.margin = unit(rep(-1,4), "cm")) +
   coord_polar()
@@
     plot = last_plot(),
-    width = 16,
-    height = 14,
+    width = 17,
+    height = 15,
     units = "in",
@@
   )
+
+```
+
+```{r statistics_fig2, eval = F, echo = T}
+
+Status_Data_Stats <- Status_Data_Plot %>% 
+  filter(observation != "No Category")
+
+# Differences between groups
+Stat_con_aov <- aov(value~group, data = Status_Data_Stats)
+Stat_con_aov
+summary(Stat_con_aov)
+
+#  Df Sum Sq Mean Sq F value Pr(>F)
+# group         5   3148   629.6    1.24  0.289 # NO SIG
+# Residuals   443 224996   507.9
+
+Stat_Cat_aov <- aov(value~observation, data = Status_Data_Stats)
+Stat_Cat_aov
+summary(Stat_Cat_aov)
+#              Df Sum Sq Mean Sq F value Pr(>F)    
+# observation   2 134952   67476   322.9 <2e-16 ***
+# Residuals   446  93192     209
+
+TukeyHSD(Stat_Cat_aov)
 
@@
   filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
-  mutate(taxon_key = as.character(taxon_key)) %>%
+  # mutate(taxon_key = as.character(taxon_key)) %>%
   left_join(SAU_Catch_Data,
@@
   )
-
 ```
@@
            alpha=0.5) +
+  # Species names
   geom_text(data=label_data_rest,
@@
                 label=individual,
-                hjust=hjust,
-                color = group), 
-            # color="black",
+                hjust=hjust#,
+                # color = group
+                ),
+            color="black",
             fontface="bold.italic",
@@
 
-### What about... Catch Status...
-
-taxon_status <- Tresholded_T_Data %>% 
-  group_by(taxon_key) %>% 
-  summarise(
-    n_countries = length(unique(eez_name))
-  ) %>% 
-  left_join(Status_Data)
-
-modcs <- lm(n_countries~status, taxon_status)
-modcs
-summary(modcs)
-
-ggplot(taxon_status) +
-  geom_boxplot(
+## Using a MANOVA to test the significant effect of fishvul and ccvul to catchstatus
+
+# Prepare data
+
+Status_Per_Species <- Tresholded_T_Data %>% 
+  left_join(Status_Data, 
+            by =c("eez_name","taxon_key")
+  ) %>%
+  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
+  group_by(taxon_key,status) %>% 
+  summarise(value = length(unique(fishing_entity))) %>% 
+  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
+                            ifelse(status == "Max Exploited","Category B",
+                                   ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+                            )
+                         )
+         ) %>% 
+  left_join(cc_vul) %>% 
+  left_join(fish_vul) %>% 
+  filter(status != "No Category",
+         Categories != "No Category")
+
+# Test for assumptions
+ # - Data Normally distributed (YES)
+
+qqnorm(Status_Per_Species$ccvul) # yes
+qqnorm(Status_Per_Species$fishvul) # yes
+
+ggplot(Status_Per_Species) +
+  geom_histogram(
     aes(
-      x = status,
-      y = n_countries
-    )
-  )
+      # x = fishvul # Yes
+      # x = ccvul #yes
+    )
+  ) +
+  facet_wrap(~status)
+
+# -  n for each group > total of dependent variables (YES)
+# - All groups have common variance-covariance – usually fine if sample sizes for each group are the same or very similar. Otherwise, Box’s M can be used to test. (YES, SAMPLE SIZES ARE THE SAME)
+# - Homoscedasticity
+# - There is a moderate linear correlation between the dependent variables (if too weak, or too strong, a series of one-way ANOVAs may be more appropriate) (NO!)
+
+man_vul <- manova(cbind(ccvul,fishvul)~status,data = Status_Per_Species)
+summary(man_vul)
+
+summary.aov(man_vul)
+
+## Since we don't have linear correlation between dependent variables, we test anovas
+
+### fishvul ANOVA
+
+Fishvul_aov <- aov(fishvul~Categories, data = Status_Per_Species)
+summary(Fishvul_aov)
+
+#   Df Sum Sq Mean Sq F value Pr(>F)
+# Categories     2   2698  1349.2   2.286  0.102 # NO SIG
+# Residuals   1392 821450   590.1               
+# 294 observations deleted due to missingness
+
+### ccvul ANOVA (N)
+
+Ccvul_aov <- aov(ccvul~Categories, data = Status_Per_Species)
+summary(Ccvul_aov)
+# Df Sum Sq Mean Sq F value Pr(>F)
+# Categories     2   1798   899.0   2.181  0.113 # NO SIG
+# Residuals   1686 695057   412.3
 

### 2019-12-24 Initial_Analysis.Rmd
Included RFMO analysis

@@
     fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
-    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),,
+    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
     fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
@@
 # Load and clean transboundary results
-Results_Trans <- GetTransResults(Spp)
+# Results_Trans <- GetTransResults(Spp)
 
@@
 
+### RFMO species list
+
+RFMO_Species <- read.csv(paste(Data_Path,"Spatial_Data/RFMO/clean_rfmos.csv", sep ="")) %>% 
+  clean_names() %>% 
+  left_join(Exploited_Species,
+            by = c("taxon_name"))
+
+# The path
+path_world <- paste(Data_Path,"/Spatial_Data/","RFMO","/SAU_RFMO",sep="")
+# #The File
+fnam_world <- "SAU_RFMO_Sept_2015.shx"
+# #Load it!
+# 
+RFMOs_sf <- st_read(dsn = path_world,
+                      layer =file_path_sans_ext(fnam_world)) %>% 
+  dplyr::rename(Name = RFMO_nm_s) %>% 
+  st_set_crs(3832) %>% # Making sure is same proyection
+  st_transform(3832) # to match shapefiles
+
+Clean_Results_Trans <- Clean_Results_Trans %>% 
+  filter(taxon_key %in% RFMO_Species$taxon_key)
+
 ```
@@
   )
+
+length(unique(Tresholded_T_Data$eez_name))
 
@@
   filter(Total_USD > 0)
+
+####  Data for Jessica
+
+# Data per Territory
+# Transboundary_Jess <- Tresholded_T_Data %>% 
+#   group_by(fishing_entity) %>% 
+#   summarise(
+#     n_trans_spp = length(unique(taxon_key)),
+#     # n_neighbours = length(unique(nt_fishing_entity)),
+#     # trans_Rrate = n_trans_spp/n_neighbours
+#   )
+
+# write_csv(Transboundary_Jess,
+#           "transboundary_species_dec19.csv")
 
@@
 
+### Total from the top 5
+
+Top5 <- c("Peru", "Russian Federation", "Chile", "USA","China")
+
+Total_PeRu <- Revenue_Country %>% 
+  filter(fishing_entity %in% PeRu) %>% 
+  select(1:2) %>% 
+  group_by() %>% 
+  summarise(sum(Total_USD)) %>% 
+  pull()/79745
+
 ```
@@
 
+lenght(unique(Clean_Results_Transboundary$taxon_key))
+
+Transboundary_Spp %>% 
+  ggplot() +
+  geom_bar(
+    aes(
+      x = reorder(eez_name,-n_trans_spp),
+      y = n_trans_spp
+    ),
+    stat = "identity"
+  ) +
+  coord_flip()
+
 head(RFMOs_sf)
@@
   st_transform(crs = 4326) %>% # 4326
-  # st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
   left_join(Transboundary_Spp, by ="eez_name")
 
-ICC <- World_sf_si %>% 
-  filter(eez_name == "ICCAT")
+# ICCAT <-World_sf_si %>% 
+#   filter(eez_name == "ICCAT")
+#
 
@@
 World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
+  st_transform(crs = 4326) #%>% # 4326
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
 
@@
 Plot <- ggplot() +
+  geom_sf(data = World_sf_si_land) +
   geom_sf(data = World_sf_si,
           aes(
-            fill =  reorder(Bins_Plot,n_trans_spp),
-            colour = reorder(Bins_Plot,n_trans_spp)
+            fill =  n_trans_spp#,
+            # colour = reorder(Bins_Plot,n_trans_spp)
           ), 
@@
           ) + # n_trans_spp or Bins
-  # geom_sf(data = World_sf_si_land) +
-  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-                                  "#00A08A",#"#00A08A", #green
-                                  "#F2AD00",#"#F2AD00", # Yellow
-                                  "#F98400",#"#F98400", #Orange
-                                  "#FF0000"#,"#FF0000" #Red
-  ),
-  na.value = "grey"
-  ) +
-  scale_colour_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-                                    "#00A08A",#"#00A08A", #green
-                                    "#F2AD00",#"#F2AD00", # Yellow
-                                    "#F98400",#"#F98400", #Orange
-                                    "#FF0000"#,"#FF0000" #Red
-  ),
-  na.value = "grey"
-  ) +
-  ggtheme_map() +
-  facet_wrap(~eez_name)
-
-Plot_Name <- paste("RFMO_100_25_Bins_facet.png", sep = "")
+  # geom_sf_label(data = World_sf_si,
+  #               aes(label = eez_name)
+  #               ) +
+  scale_fill_gradientn("Number of Shared Species",
+    colours = wes_palette("Zissou1", 100, type = "continuous")) +
+  # scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+  #                                 "#00A08A",#"#00A08A", #green
+  #                                 "#F2AD00",#"#F2AD00", # Yellow
+  #                                 "#F98400",#"#F98400", #Orange
+  #                                 "#FF0000"#,"#FF0000" #Red
+  # ),
+  # na.value = "grey"
+  # ) +
+  # scale_colour_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+  #                                   "#00A08A",#"#00A08A", #green
+  #                                   "#F2AD00",#"#F2AD00", # Yellow
+  #                                   "#F98400",#"#F98400", #Orange
+  #                                   "#FF0000"#,"#FF0000" #Red
+  # ),
+  # na.value = "grey"
+  # ) +
+  ggtheme_map()
+
+Plot_Name <- paste("RFMO_100_25.png", sep = "")
 
@@
   filter(group != "other")
+
+# Number of coastal nations
+length(unique(Status_Data_Plot$individual))
 
@@
 )
+
+```
+
+## Statistics on species
+
+```{r Spp_Stats, eval = T, echo = F}
+
+head(Species_Data)
+
+# Differences between groups
+Stat_spp_aov <- aov(value~group, data = Species_Data)
+Stat_spp_aov
+summary(Stat_spp_aov)
+# Df Sum Sq Mean Sq F value   Pr(>F)    
+# group         5  24836    4967   14.67 5.52e-11 *** (YUP)
+# Residuals   109  36915     339
+
+TukeyHSD(Stat_spp_aov)
 

### 2019-12-24 Manuscript_Draft.Rmd
Included RFMO analysis

@@
 The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
-Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives..
-For example, fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
-Climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Mills].
+Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@REF].
+For example, evironmental fluctuation leading to changes in the stock distribution [@Mills] and fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
+Moreover, climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Mills].
 
@@
 More recently, Teh et al.
-(2010) estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
+(2010) estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million tones and a global landed value of USD 30.7 trillion.
 While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
@@
 We focus on estimating the number of species that meet the first category.
-We overlay the known distribution of **968** commercially valuable marine fish species and the Exclusive Economic Zones of **175** coastal countries to determine the total number of transboundary species and their contribution to global catch and landed value.
+We overlay the known distribution of **968** commercially valuable marine fish species and the Exclusive Economic Zones of 153 coastal countries to determine the total number of transboundary species and their contribution to global catch and landed value.
 We carry out the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
@@
 We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
-The first criteria only considered shared species between neighbouring EEZs, rather than the extended distribution.
-We sub-divided EEZs by regions (e.g.
-Mexico Pacific and Mexico Atlantic).
+The first criteria consisted in only considering shared species between neighbouring EEZs, rather than the extended distribution.
+For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
 Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species [@REFNEreus] and two structurally distinct species distribution models [@REFGabs; @Zeller] (see Methods).
-For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
 The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller].
@@
 1A).
-Between 2005 and 2014, national fleets targeting shared stocks within EEZs landed an average of **69.2** million tonnes, representing **64**% of the EEZ-global catch, and generating USD **79.7** million in fishing revenue.
+Between 2005 and 2014, national fleets targeting shared stocks within EEZs landed an average of **69.2** million tonnes, representing **64**% of the EEZ-global catch, and generating USD **79,745** million in fishing revenue.
 This is equivalent to **49.8**% of the global revenue of the same period.
 These values are higher than previously estimated reinforcing the importance of these stocks at the global level [@Teh].
-
-Transboundary species are particulary important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from the rest in tn terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
-The large variation in revenue from these regions is driven by China (USD 6,279 million), in E.
-Asia and the US (USD 9,605 million) in N.
-America who contribue 55% and 83% of the region's revenue, respectiveley.
-Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with more revenue from transboundary species.
-
-Catches, however, are only significantly different in E.
-Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018], getting around 1/3 of its capture from transboundary species.
-For the US, 16 species make up 90% of the revenue from transboudary species, with American scallop (*Placopecten magellanicus*) shared with Canada in Georges Bank [@https://elischolar.library.yale.edu/cgi/viewcontent.cgi?article=1008&context=fes-pubs] contributing 41.8% or the revenue.
-Russia shares the largest fished species in the world, Alaskan polllock (*Theragra chalcogramma*) [@SOFIA2018], with both Japan and the US.
-Rhis fishery is responsible for 50% of the Russian revenue from transboundary species, with other eight species comprising the 90% of revenue.
-In the case of Peru, Peruvian anchoveta (*Engraulis ringens*) and jumbo squid (*Dosidicus gigas*), both shared with Chile, represent almost 90% of the revenue from transboundary species, with anchoveta accounting for 79%.
 
@@
 
-We found transboundary fisheries to be of substantial economic importance in regions with past fisheries-related conflicts [@Spijkers:2019cz].
-For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Miller2003].
-Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel [@Spijkers:2017ij], a species that is transboundary and contributes **X** to landings and **X** in revenue to the countries involved in the dispute.
-In addition, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky].
+Transboundary species are particulary important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+The large variation in revenue from these regions is driven by China (USD 6,279 million), in E.
+Asia and the US (USD 9,605 million) in N.
+America who contribue 55% and 83% of the region's revenue, respectiveley.
+Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with more revenue from transboundary species.
+These 5 nations are responsable for 30% of the global revenue from transboundary species.
 
-There is no significant difference in the exploitaion rate of transboundary species between continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05) as most species are fished over 50% of their historical maximum peak (Category C) in all continents, but Oceania (Fig.2).
-However, the number of species exploited by each country in each category significantly differs from each other (one-way ANOVA *F*(5,442), *f* = 322.9, *p* < 0.001, $\alpha$ = 0.05).
-Overall, most transboundary species are fished over 50% of their once maximum peak (Category C) suggesting that their current exploitation rate is over the maximum sustainable yield [@Kleisner:2011wn].
+Catches, however, are only significantly different in E.
+Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018], getting around 1/3 of its capture from transboundary species.
+For the US, 16 species make up 90% of the revenue from transboudary species, with American scallop (*Placopecten magellanicus*) shared with Canada in Georges Bank [@https://elischolar.library.yale.edu/cgi/viewcontent.cgi?article=1008&context=fes-pubs] contributing 41.8% or the revenue.
+Russia shares the largest fished species in the world, Alaskan polllock (*Theragra chalcogramma*) [@SOFIA2018], with both Japan and the US.
+This fishery is responsible for 50% of the Russian revenue from transboundary species, with other eight species comprising 90% of the revenue.
+In the case of Peru, Peruvian anchoveta (*Engraulis ringens*) and jumbo squid (*Dosidicus gigas*), both shared with Chile, represent almost 90% of the revenue from transboundary species, with anchoveta accounting for 79%.
 
-Empirical analysis suggest that cooperation will have better outcomes for shared fisheries management.
-Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*)[@Diekert:2010gp], and between Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-
-Indeed, there are some successful bilateral management plans for species such as Pacific Halibut between Canada and the US as well [@REference?] and multilateral treaties like the Pacific Nauru Agreement that manages 30% of global skipjack tuna in the South Pacific Islands [@Aqorau:2018bh].
-However, the effectiveness of Regional Fisheries Management Organizations, responsible for managing high migratory stocks in areas beyond national jurisdiction, has been previously questioned [@CullisSuzuki:2010fi].
-Countries that are today harvesting species at rates less than 50% of the historical maximum catch (Category C) should be paying extra care in these species (Fig.
+The exploitation category of transboundary species significantly differs from each other (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished under 50% of their historical maximum peak (Fig.2).
+This is true for all (but Oceania) continents with no significan difference between them (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05), suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @PaulyNature2013].
+Countries that are today harvesting at this rate (Category C) should be paying extra care in the management of these species (Fig.
 2).
-While these catch trends do not reflect stock status [@Branch:2011br], they could reassemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
-The rebuilding of a transboundary species could be strongly impacted by uncoordinated efforts of countries harvesting the same species but with different objectives [@Ref].
 
@@
 
-Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@REF].
-Not surprisingly, highly migratory pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are among the more shared resources in the world with a median of 40 nations sharing these resources (Fig 3.).
-These species are very important in terms of economic value as they (global) average revenue exceeds USDXXX.
+While these catch trends do not directly reflect stock status [@Branch:2011br] - e.g.
+other factors like markets, fishing policies or extreem events also influence catch volume [@PaulyNature2013] - they could ressemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
+Empirical analysis suggest that management of transboundary species will have better outcomes in terms of fish yield and sustainabillity whith cooperation between nations [@REF].
+Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
 
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these might be cosmopolitan but not necessarily highly migratory (e.g.
-*Solea solea*, *Panulirus argus*) (Fig.
+Collaboration can also reduce conflict between nations over shared ressources.
+Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts like Canada, the US, China and Russia [@Spijkers:2019cz].
+For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Miller2003].
+Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel [@Spijkers:2017ij], a species that is transboundary and contributes **X** to landings and **X** in revenue to the countries involved in the dispute.
+In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky].
+
+First steps for shared management start with information sharing, then this and that. Proper management treaties not only have but can also be stronger in the fase of a canging climate.
+
+Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@NelsonFishesOfTheWorld].
+Not surprisingly, highly migratory pelagic-oceanic species are the only group that significantly differs in terms of sharing countries (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 nations sharing these resources (Fig.
 3).
-However, less distributed species must not be ignored.
-The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even if a population swims between the borders of two nations, their larvae could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-
-Moreover, many coastal communities, specially in developing regions, and highly dependent on fishing local fish (e.g.
-reef fish) for food security and improved livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf].
 
@@
 
-Management of transboundary fisheries needs to be looking forward.
-As species shift their known distributions to cope with a changing ocean, new transboundary species will arise, challenging the management of shared stocks worldwide [@Pinsky].
-Conflicts in regions with a high abundance in transboundary species will likely be exacerbated by climate change, as seen in the ongoing dispute between the European Union, Norway, Iceland and the Faroe Islands over mackerel (**species**) [@Spijkers:2017ij].
-Understanding how climate change will affect the biogeography of marine species, and notably the number of countries' EEZ it spans is a key element to the design of effective long-term spatial-based fisheries management [@Alexa, @Song:2017iua].
+Due to their large migration patterns and presence in areas beyond national jurisdiction, pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are catalogued as stradling species by FAO definitions and globally managed by Regional Fisheries Management Organizations (RFMOs) [@FAO].
+Sixteen major RFMOs in the world oversee the management of 101 species, most of them fished in areas beyond national jurisdiction [@CullisSuzuki:2010fi].
+We estimate that 56.4% of these species (*n* = 57) are actually shared by neighbouring RFMOs with the North Atlantic Salmon Conservation Organization (NASCO), the North East Atlantic Fisheries Commission (NASCO) and the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 30 species with neighbouring RFMOs (Suplemental figure RFMO_MAP).
+
+The catch from these species comes mainly from five South Pacific Islands nations, from which three (Kiribalti, Solomon and Papua New Guinea) are members of the Pacific Nauru Agreement (PNA) (Fig.
+3B).
+The PNA manages 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year [@https://www.ffa.int/nauru_agreement].
+However, the effectiveness of RFMOs responsible for managing high migratory stocks, has been previously questioned [@CullisSuzuki:2010fi].
+
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these might be cosmopolitan but not necessarily highly migratory (e.g.
+*Solea solea*, *Panulirus argus*) (Fig.
+3).
+However, less distributed species must not be ignored.
+The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+
+Moreover, many coastal communities, specially in developing regions, and highly dependent on fishing local fish (e.g.
+reef fish) for food security and improved livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf; @https://www.sciencedirect.com/science/article/pii/S0308597X17308357].
+For example, from the top five countries fishing transboundary reef - associated species, Indonesia, Malaysia and the Philippines are among the higest fish consumption per capita in the world with 20, 60 and 40 kg per year, respectiveley [@https://www.sciencedirect.com/science/article/pii/S0308597X12001315].
+In the Phillipines...
 
@@
 Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability and can be flexible to accommodate future changes.
-
-<!-- Overview of West African fisheries under climate change: Impacts, vulnerabilities and adaptive responses of the artisanal and industrial sectors -->
-<!-- https://www.sciencedirect.com/science/article/pii/S0308597X16302901#bib4 -->
 
@@
 The ENM-Nereus employed all of the observational data-sources previously mentioned.
-Global environmental conditions were obtained and results averaged from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+Global environmental conditions were obtained from 1970 to 2000 and average from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
 See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
@@
 Catches are also spatially allocated [@Zeller2016].
-Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten yeares of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs (average 2005-2014).
+Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten yeares of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 
@@
 from 0 to 1) rather than a discrete, yes or no, index .
-All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the pacages *tidiverse*[@],*data.table*[@],*wesanderson*[@],*janitor*[@],*spdep*[@], *sf*[@],*sp*[@],*rgdal*[@],*tools*[@],*parallel*[@],*rfishbase*[@],*zoo*[@].
+All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the pacages *tidiverse*[@], *data.table*[@], *wesanderson*[@], *janitor*[@], *spdep*[@], *sf*[@], *sp*[@], *rgdal*[@], *tools*[@], *parallel*[@], *rfishbase*[@], *zoo*[@].
 All code is available at https://github.com/jepa/FishForVisa.
@@
 We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
-Therefore, all species that were not reported as caught in any single year between the reference years (1970 to 2000) in a given grid-cell were dropped, regardless of the *Species Index*.
+Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped, regardless of the *Species Index*.
 The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, thus validating the models.
@@
 Three categories were drawn from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
-Finally, we reported the predominant category over the last ten years of catch data (2004-2014).
+Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
 
@@
 
-# Recicled text (Not to be included)
+# Suplements
+
+<!-- # Recicled text (Not to be included) -->
 

### 2019-12-25 Initial_Analysis.Rmd
Included RFMO analysis and missing values for results

@@
 # Set Jurisdiction to EEZ or RFMO
-# Jurisdiction <- "EEZ"
-Jurisdiction <- "RFMO"
+Jurisdiction <- "EEZ"
+# Jurisdiction <- "RFMO"
 
@@
   ) %>% 
-  group_by(eez_name,fishing_entity) %>% 
+  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
   summarise(n()) %>% 
@@
   group_by(fishing_entity_id,taxon_key) %>% 
-  summarise(mean_value = mean(value,na.rm=T))
+  summarise(mean_value = mean(value,na.rm=T)) %>% 
+  left_join(Clean_sau_eez_fes)
 
@@
   rename(eez_name=territory)
-# Status_Data <- Species_Status
 
@@
 
-# Load and clean transboundary results
-# Results_Trans <- GetTransResults(Spp)
-
-# Clean results susing function CleanResultsfun
-Clean_Results_Trans <- CleanResults(Results_Trans) %>% 
+# Read Results
+Clean_Results_Trans <- GetTransResults(Spp) %>% 
+  CleanResults(.) %>% 
   clean_names() %>% 
@@
 
-# Load and clean Discrete results
-# Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
-#   filter(!is.na(TaxonKey)) %>% 
-#   select(2:3)
-
 # Vulnerabillity Data from William
-cc_vul <- fread(paste(Data_Path,"Species_Data/vulspp310817.csv", sep ="")) %>% 
-  rename(taxon_key = V1,
-         ccvul = V2)
-
-fish_vul <- fread(paste(Data_Path,"Species_Data/FishSenIndex.csv", sep ="")) %>% 
-  clean_names()
-
-### RFMO species list
-
-RFMO_Species <- read.csv(paste(Data_Path,"Spatial_Data/RFMO/clean_rfmos.csv", sep ="")) %>% 
+# cc_vul <- fread(paste(Data_Path,"Species_Data/vulspp310817.csv", sep ="")) %>% 
+#   rename(taxon_key = V1,
+#          ccvul = V2)
+
+# fish_vul <- fread(paste(Data_Path,"Species_Data/FishSenIndex.csv", sep ="")) %>% 
+  # clean_names()
+
+# ---------------------------- #
+# RFMOs Results ####
+# ---------------------------- #
+
+# List of species
+Spp_rfmo <- list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Results/RFMO/Trans_Results/")
+
+# List of RMOs
+rfmo_list <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/clean_rfmos.csv") %>% 
   clean_names() %>% 
-  left_join(Exploited_Species,
-            by = c("taxon_name"))
+  left_join(Exploited_Species) %>% 
+  filter(!rfmo_name %in% c("IPHC","PSC","NASCO")) # remove these
+
+# Load and clean transboundary results
+Results_rfmo <- GetTransResults(Spp_rfmo) %>% 
+  clean_names() %>% 
+  rename(rfmo_name = territory) %>% 
+  # left_join(rfmo_list,
+  #           by =c("rfmo_name","taxon_key"))
+  filter(
+    taxon_key %in% rfmo_list$taxon_key, # just the taxa managed by the rfmos
+    !rfmo_name %in% c("IPHC","PSC","NASCO"), # remove these
+    !neighbour %in% c("IPHC","PSC","NASCO") # remove these
+  )
 
@@
                       layer =file_path_sans_ext(fnam_world)) %>% 
-  dplyr::rename(Name = RFMO_nm_s) %>% 
-  st_set_crs(3832) %>% # Making sure is same proyection
-  st_transform(3832) # to match shapefiles
-
-Clean_Results_Trans <- Clean_Results_Trans %>% 
-  filter(taxon_key %in% RFMO_Species$taxon_key)
+  dplyr::rename(Name = RFMO_nm_s)
 
@@
 
-#### Determine transboundary and non-transboundary species and nations
+#### Determine transboundary and species and nations
 
@@
   )
-
-# Get Catch data for mapping (Supplemental materials)
-
-Catch_Country <- SAU_Catch_Data %>%
-  group_by(eez_name) %>%
-  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>%
-  group_by(fishing_entity) %>%
-  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million tones
-  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-         Bins = cut(fishing_entity_catch,breaks = 5),
-         Bins_Plot = cut(fishing_entity_catch,breaks = 5,
-                         labels = c('super low', 'low','median','high','super high'))
-  ) %>% 
-  filter(fishing_entity_catch > 0)
 
@@
 
-```{r Territory_Map_Round, eval =F, echo =F}
+```{r Territory_Map_Round_Revenue, eval =F, echo =F}
 
@@
 
+```{r Territory_Map_Round_Catch, eval =F, echo =F}
+
+# Get Catch data for mapping (Supplemental materials)
+Catch_Breaks <- c(-1,10,100,1000,5000,10000)
+
+Catch_Country <- SAU_Catch_Data %>%
+  group_by(eez_name) %>%
+  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>%
+  group_by(fishing_entity) %>%
+  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
+  mutate(
+    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
+  #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
+         Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
+         Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
+                         labels = c('super low', 'low','median','high','super high'))
+  ) %>% 
+  filter(fishing_entity_catch > 0)
+
+# Create labels for legend
+Bins_Trans <- Transboundary_Spp %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+Bins_Catch <- Catch_Country %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
+Labels_Catch <- c("(1-10]",paste(Bins_Catch[2:5]))
+
+# Transboundary Species shapefile
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326) %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Transboundary_Spp, by ="eez_name")
+
+# Total catch/Revenue shapefile
+World_sf_si_land <- World_land_sf %>%
+  st_transform(crs = 4326) %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
+  left_join(Catch_Country, by ="fishing_entity")
+
+# Get the NA's to be grey
+Grey_land <- World_sf_si_land %>% 
+  filter(is.na(Bins_Plot))
+
+# Make map
+Map <- ggplot() +
+  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,fishing_entity_catch)), colour = "grey80",size = 0.1) +
+  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
+  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
+  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+                                  "#00A08A",#"#00A08A", #green
+                                  "#F2AD00",#"#F2AD00", # Yellow
+                                  "#F98400",#"#F98400", #Orange
+                                  "#FF0000"#,"#FF0000" #Red
+  ),
+  na.translate = F
+  ) +
+  ggtheme_map() +
+  # Transboundary labels
+  annotate("text",
+           x =(c(-85.5,-30,25,81,136)+5),
+           y = -93.5,
+           label = Labels_Trans,
+           color="black",
+           size=3,
+           angle=0,
+           # fontface="bold",
+           hjust=0) +
+  # Catch labels
+  annotate("text",
+           x =(c(-85.5,-31,20,75,131)+5),
+           y = -110,
+           label = Labels_Catch,
+           color="black",
+           size=3,
+           angle=0,
+           # fontface="bold",
+           hjust=0) +
+  # # Legend Titles
+  annotate("text",
+           x =-180,
+           y = -93.5,
+           label = "Transboundary Spp. (n)",
+           color="black",
+           size=3,
+           angle=0,
+           fontface="bold",
+           hjust=0) +
+  annotate("text",
+           x =-180,
+           y = -110,
+           label = "Catch (Thousand tons)",
+           color="black",
+           size=3,
+           angle=0,
+           fontface="bold",
+           hjust=0) +
+  theme(
+    legend.box.margin = margin(t = -54, l = 130),
+    legend.text = element_blank(),
+  ) +
+  guides(fill = guide_legend(nrow = 1))
+
+ggsave(
+    plot = last_plot(),
+    width = 8,
+    height = 5,
+    units = "in",
+    filename = "S1_Catch_EEZ.png"#,
+    # path = Figures_Path
+  )
+
+```
+
 ### China, US, Russia, and Peru
@@
 
-```{r Territory_Map, eval =F, echo =F}
-
-lenght(unique(Clean_Results_Transboundary$taxon_key))
-
-Transboundary_Spp %>% 
+```{r RFMO_Map, eval =F, echo =F}
+
+Tresholded_rfmo_Data <- Results_rfmo %>% 
+  filter(
+    area_index >= Min_AI,
+    area_index <= Max_AI,
+    model_index >= MI
+  ) %>% 
+  group_by(rfmo_name) %>% 
+  summarise(
+    n_trans_spp = length(unique(taxon_key)),
+    n_neighbours = length(unique(neighbour)),
+    trans_Rrate = n_trans_spp/n_neighbours
+  )
+
+# Number of RFMOs
+rfmo_list %>% 
+  pull(rfmo_name) %>% 
+  unique() %>% 
+  length() # 15
+
+# Number of total taxa
+rfmo_list %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length() # 99
+
+# Number of taxa per RFMO
+rfmo_list %>% 
+  group_by(rfmo_name) %>% 
+  summarise(in_trans_spp = length(unique(taxon_key)))
+
+# Number of shared taxa
+Results_rfmo %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length() # 81
+
+### Bar plot
+
+Tresholded_rfmo_Data %>% 
   ggplot() +
@@
     aes(
-      x = reorder(eez_name,-n_trans_spp),
+      x = reorder(rfmo_name,-n_trans_spp),
       y = n_trans_spp
@@
 World_sf_si <- RFMOs_sf %>%
-  rename(eez_name = Name) %>% 
+  filter(!Name %in% c("IPHC","PSC","NASCO")) %>% 
+  rename(rfmo_name = Name) %>% 
   st_transform(crs = 4326) %>% # 4326
   # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")
-
-# ICCAT <-World_sf_si %>% 
-#   filter(eez_name == "ICCAT")
-#
+  left_join(Tresholded_rfmo_Data, by ="rfmo_name")
 
@@
 Plot <- ggplot() +
-  geom_sf(data = World_sf_si_land) +
   geom_sf(data = World_sf_si,
           aes(
-            fill =  n_trans_spp#,
-            # colour = reorder(Bins_Plot,n_trans_spp)
+            fill =  n_trans_spp,
+            colour = n_trans_spp
           ), 
@@
           ) + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land) +
   # geom_sf_label(data = World_sf_si,
@@
   scale_fill_gradientn("Number of Shared Species",
-    colours = wes_palette("Zissou1", 100, type = "continuous")) +
-  # scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-  #                                 "#00A08A",#"#00A08A", #green
-  #                                 "#F2AD00",#"#F2AD00", # Yellow
-  #                                 "#F98400",#"#F98400", #Orange
-  #                                 "#FF0000"#,"#FF0000" #Red
-  # ),
-  # na.value = "grey"
-  # ) +
-  # scale_colour_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-  #                                   "#00A08A",#"#00A08A", #green
-  #                                   "#F2AD00",#"#F2AD00", # Yellow
-  #                                   "#F98400",#"#F98400", #Orange
-  #                                   "#FF0000"#,"#FF0000" #Red
-  # ),
-  # na.value = "grey"
-  # ) +
+    colours = wes_palette("Zissou1", 100, type = "continuous"),
+    limits = c(0,45),
+    breaks = seq(0,45,5)
+    ) +
+  scale_colour_gradientn("Number of Shared Species",
+    colours = wes_palette("Zissou1", 100, type = "continuous"),
+    limits = c(0,45),
+    breaks = seq(0,45,5)
+    ) +
   ggtheme_map()
 
-Plot_Name <- paste("RFMO_100_25.png", sep = "")
+Plot_Name <- paste("S2_RFMO.png", sep = "")
 
@@
        height = 8,
-       units = "in"#,
-       # path = Figures_Path
-       )
-
+       units = "in",
+       path = Figures_Path
+       )
 ```
@@
 
-### Mackrell war
+### Mackerel (Scomber scombrus) war
 
@@
 
-Conflict_nations <- c()
-
-Macrell <- Tresholded_T_Data %>% 
+Exploited_Species %>% 
+  filter(taxon_name == "Scomber scombrus") # 600118
+
+NW_Europe <- UN_Regions %>% 
+  filter(sub_region  %in% c("Western Europe", "Northern Europe")) %>% 
+  pull(fishing_entity) %>% 
+  unique()
+
+Conflict_nations <- c(NW_Europe,"Portugal","Spain")
+
+Mackerel_Rev <- SAU_Revenue_Data %>% 
   filter(taxon_key == 600118,
-         eez_name %in% Conflict_nations
-  )
+         fishing_entity %in% Conflict_nations
+         ) %>% 
+  group_by() %>% 
+  summarise(sum(mean_value))/1000000
+
+Mackerel_Catch <- SAU_Catch_Data %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  filter(taxon_key == 600118,
+         fishing_entity %in% Conflict_nations
+         ) %>% 
+  group_by() %>% 
+  summarise(sum(total_catch))/1000
 
@@
   arrange(group,value)  %>% 
-  filter(value > 20)  # remove all species under 20 (way too many to plot!)
-
-#### Exosystem based plots
+  mutate(
+    individual = ifelse(individual == "Chloroscombrus chrysurus", "C. chrysurus",
+                        ifelse(individual == "Scomberomorus commerson", "S. commerson",
+                               individual)
+    )
+  )
+
+#### Ecosystem based plots
 
@@
 # unique(Species_Data$group)
+
+Species_Data <- Species_Data %>%
+  filter(value > 20)
 
@@
     panel.grid = element_blank(),
-    # plot.margin = unit(c(-3.5, -3.5, -4, -4), "cm") #top, right, bottom, left
-    plot.margin = unit(rep(-3.5,4),"cm")
+    plot.margin = unit(rep(-3.5,4.5),"cm")
   ) +
@@
 
-# Vulnerabillity Assesment
-
-```{r Vulnerabillity, eval = T, echo = F}
-
-trans_vul <- Tresholded_T_Data %>% 
+## RFMO specifics
+
+```{r RFMOs, eval = T, echo = F}
+
+### Results exploration
+
+ICCAT_List <- rfmo_list %>% 
+  filter(rfmo_name == "ICCAT") %>% 
+  pull(taxon_key) %>% 
+  unique()
+
+Tresholded_T_Data %>% 
+  filter(taxon_key %in% ICCAT_List) %>% 
   group_by(taxon_key) %>% 
   summarise(
-    n_countries = length(unique(eez_name))
-  ) %>% 
-  left_join(cc_vul) %>% 
-  left_join(fish_vul) %>% 
-  ggplot() +
-  geom_point(
-    aes(
-      x = fishvul,
-      y = n_countries
-    )
-  )
-
-# climate change vulnerabillity?
-modcc <- lm(n_countries~ccvul, data = trans_vul)
-modcc
-summary(modcc)
-
-# fishing vulnerabillity?
-modfis <- lm(n_countries~fishvul, trans_vul)
-modfis
-summary(modfis)
-
-# Together?
-
-modccfis <- lm(n_countries~fishvul + ccvul, trans_vul)
-modccfis
-summary(modccfis)
-
-## Using a MANOVA to test the significant effect of fishvul and ccvul to catchstatus
-
-# Prepare data
-
-Status_Per_Species <- Tresholded_T_Data %>% 
-  left_join(Status_Data, 
-            by =c("eez_name","taxon_key")
-  ) %>%
-  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
-  group_by(taxon_key,status) %>% 
-  summarise(value = length(unique(fishing_entity))) %>% 
-  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
-                            ifelse(status == "Max Exploited","Category B",
-                                   ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
-                            )
-                         )
-         ) %>% 
-  left_join(cc_vul) %>% 
-  left_join(fish_vul) %>% 
-  filter(status != "No Category",
-         Categories != "No Category")
-
-# Test for assumptions
- # - Data Normally distributed (YES)
-
-qqnorm(Status_Per_Species$ccvul) # yes
-qqnorm(Status_Per_Species$fishvul) # yes
-
-ggplot(Status_Per_Species) +
-  geom_histogram(
-    aes(
-      # x = fishvul # Yes
-      # x = ccvul #yes
-    )
-  ) +
-  facet_wrap(~status)
-
-# -  n for each group > total of dependent variables (YES)
-# - All groups have common variance-covariance – usually fine if sample sizes for each group are the same or very similar. Otherwise, Box’s M can be used to test. (YES, SAMPLE SIZES ARE THE SAME)
-# - Homoscedasticity
-# - There is a moderate linear correlation between the dependent variables (if too weak, or too strong, a series of one-way ANOVAs may be more appropriate) (NO!)
-
-man_vul <- manova(cbind(ccvul,fishvul)~status,data = Status_Per_Species)
-summary(man_vul)
-
-summary.aov(man_vul)
-
-## Since we don't have linear correlation between dependent variables, we test anovas
-
-### fishvul ANOVA
-
-Fishvul_aov <- aov(fishvul~Categories, data = Status_Per_Species)
-summary(Fishvul_aov)
-
-#   Df Sum Sq Mean Sq F value Pr(>F)
-# Categories     2   2698  1349.2   2.286  0.102 # NO SIG
-# Residuals   1392 821450   590.1               
-# 294 observations deleted due to missingness
-
-### ccvul ANOVA (N)
-
-Ccvul_aov <- aov(ccvul~Categories, data = Status_Per_Species)
-summary(Ccvul_aov)
-# Df Sum Sq Mean Sq F value Pr(>F)
-# Categories     2   1798   899.0   2.181  0.113 # NO SIG
-# Residuals   1686 695057   412.3
+    n_countries = length(unique(fishing_entity))
+  )
+
+ICCAT_Trans <- Species_Data %>% 
+  rename(taxon_name = individual) %>% 
+  left_join(Exploited_Species) %>% 
+  filter(taxon_key %in% ICCAT_List)
 
@@
 # y=tag_facet(q, tag_pool = c("d","e","f"))
+
+```
+
+# Vulnerabillity Assesment
+
+```{r Vulnerabillity, eval = T, echo = F}
+
+trans_vul <- Tresholded_T_Data %>% 
+  group_by(taxon_key) %>% 
+  summarise(
+    n_countries = length(unique(eez_name))
+  ) %>% 
+  left_join(cc_vul) %>% 
+  left_join(fish_vul) %>% 
+  ggplot() +
+  geom_point(
+    aes(
+      x = fishvul,
+      y = n_countries
+    )
+  )
+
+# climate change vulnerabillity?
+modcc <- lm(n_countries~ccvul, data = trans_vul)
+modcc
+summary(modcc)
+
+# fishing vulnerabillity?
+modfis <- lm(n_countries~fishvul, trans_vul)
+modfis
+summary(modfis)
+
+# Together?
+
+modccfis <- lm(n_countries~fishvul + ccvul, trans_vul)
+modccfis
+summary(modccfis)
+
+## Using a MANOVA to test the significant effect of fishvul and ccvul to catchstatus
+
+# Prepare data
+
+Status_Per_Species <- Tresholded_T_Data %>% 
+  left_join(Status_Data, 
+            by =c("eez_name","taxon_key")
+  ) %>%
+  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
+  group_by(taxon_key,status) %>% 
+  summarise(value = length(unique(fishing_entity))) %>% 
+  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
+                            ifelse(status == "Max Exploited","Category B",
+                                   ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+                            )
+                         )
+         ) %>% 
+  left_join(cc_vul) %>% 
+  left_join(fish_vul) %>% 
+  filter(status != "No Category",
+         Categories != "No Category")
+
+# Test for assumptions
+ # - Data Normally distributed (YES)
+
+qqnorm(Status_Per_Species$ccvul) # yes
+qqnorm(Status_Per_Species$fishvul) # yes
+
+ggplot(Status_Per_Species) +
+  geom_histogram(
+    aes(
+      # x = fishvul # Yes
+      # x = ccvul #yes
+    )
+  ) +
+  facet_wrap(~status)
+
+# -  n for each group > total of dependent variables (YES)
+# - All groups have common variance-covariance – usually fine if sample sizes for each group are the same or very similar. Otherwise, Box’s M can be used to test. (YES, SAMPLE SIZES ARE THE SAME)
+# - Homoscedasticity
+# - There is a moderate linear correlation between the dependent variables (if too weak, or too strong, a series of one-way ANOVAs may be more appropriate) (NO!)
+
+man_vul <- manova(cbind(ccvul,fishvul)~status,data = Status_Per_Species)
+summary(man_vul)
+
+summary.aov(man_vul)
+
+## Since we don't have linear correlation between dependent variables, we test anovas
+
+### fishvul ANOVA
+
+Fishvul_aov <- aov(fishvul~Categories, data = Status_Per_Species)
+summary(Fishvul_aov)
+
+#   Df Sum Sq Mean Sq F value Pr(>F)
+# Categories     2   2698  1349.2   2.286  0.102 # NO SIG
+# Residuals   1392 821450   590.1               
+# 294 observations deleted due to missingness
+
+### ccvul ANOVA (N)
+
+Ccvul_aov <- aov(ccvul~Categories, data = Status_Per_Species)
+summary(Ccvul_aov)
+# Df Sum Sq Mean Sq F value Pr(>F)
+# Categories     2   1798   899.0   2.181  0.113 # NO SIG
+# Residuals   1686 695057   412.3
 

### 2019-12-25 Manuscript_Draft.Rmd
Included RFMO analysis and missing values for results

@@
 These 5 nations are responsable for 30% of the global revenue from transboundary species.
-
-Catches, however, are only significantly different in E.
-Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018], getting around 1/3 of its capture from transboundary species.
-For the US, 16 species make up 90% of the revenue from transboudary species, with American scallop (*Placopecten magellanicus*) shared with Canada in Georges Bank [@https://elischolar.library.yale.edu/cgi/viewcontent.cgi?article=1008&context=fes-pubs] contributing 41.8% or the revenue.
-Russia shares the largest fished species in the world, Alaskan polllock (*Theragra chalcogramma*) [@SOFIA2018], with both Japan and the US.
-This fishery is responsible for 50% of the Russian revenue from transboundary species, with other eight species comprising 90% of the revenue.
-In the case of Peru, Peruvian anchoveta (*Engraulis ringens*) and jumbo squid (*Dosidicus gigas*), both shared with Chile, represent almost 90% of the revenue from transboundary species, with anchoveta accounting for 79%.
+Peru and Russia lead the production of transboundary species harvesting over 5,000 thousand tones (**Suplemental figure Trans_Catch_MAP**).
+Peru's catches come mainly from Peruvian anchoveta (*Engraulis ringens*), shared with Chile, accounting for 79% of the transboundary species production.
+Similarly, Russia shares the (currently) largest fishery in the world, Alaskan polllock (*Theragra chalcogramma*) with both Japan and the US [@SOFIA2018].
+Despite this, catches are only significantly different in E.
+Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018] getting around 1/3 of its capture from transboundary species, followde by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
 
@@
 Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-
 Collaboration can also reduce conflict between nations over shared ressources.
@@
 For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Miller2003].
-Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel [@Spijkers:2017ij], a species that is transboundary and contributes **X** to landings and **X** in revenue to the countries involved in the dispute.
+Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** thousand tones to landings and USD **968** million in revenue to the countries involved in the dispute.
 In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky].
@@
 Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@NelsonFishesOfTheWorld].
-Not surprisingly, highly migratory pelagic-oceanic species are the only group that significantly differs in terms of sharing countries (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 nations sharing these resources (Fig.
+Not surprisingly, highly migratory pelagic-oceanic species are the only group that significantly differs in terms of sharing countries (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 nations shared per species (Fig.
 3).
@@
 Due to their large migration patterns and presence in areas beyond national jurisdiction, pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are catalogued as stradling species by FAO definitions and globally managed by Regional Fisheries Management Organizations (RFMOs) [@FAO].
-Sixteen major RFMOs in the world oversee the management of 101 species, most of them fished in areas beyond national jurisdiction [@CullisSuzuki:2010fi].
-We estimate that 56.4% of these species (*n* = 57) are actually shared by neighbouring RFMOs with the North Atlantic Salmon Conservation Organization (NASCO), the North East Atlantic Fisheries Commission (NASCO) and the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 30 species with neighbouring RFMOs (Suplemental figure RFMO_MAP).
-
-The catch from these species comes mainly from five South Pacific Islands nations, from which three (Kiribalti, Solomon and Papua New Guinea) are members of the Pacific Nauru Agreement (PNA) (Fig.
+Fifteen major RFMOs in the world oversee the management of 99 species, most of them fished in areas beyond national jurisdiction [@CullisSuzuki:2010fi].
+We estimate that 81.8% of these species (*n* = 81) are actually shared within neighbouring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighbouring RFMOs (**Suplemental figure RFMO_MAP**).
+The catch from pelagic-oceanic species comes mainly from five South Pacific Islands nations, from which three (Kiribalti, Solomon and Papua New Guinea) are members of the Pacific Nauru Agreement (PNA) (Fig.
 3B).
 The PNA manages 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year [@https://www.ffa.int/nauru_agreement].
-However, the effectiveness of RFMOs responsible for managing high migratory stocks, has been previously questioned [@CullisSuzuki:2010fi].
 
@@
 The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-
 Moreover, many coastal communities, specially in developing regions, and highly dependent on fishing local fish (e.g.
@@
 For example, from the top five countries fishing transboundary reef - associated species, Indonesia, Malaysia and the Philippines are among the higest fish consumption per capita in the world with 20, 60 and 40 kg per year, respectiveley [@https://www.sciencedirect.com/science/article/pii/S0308597X12001315].
-In the Phillipines...
 
@@
 
-<!-- # Recicled text (Not to be included) -->
+```{r Call_Sup_1, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
+The number of species is represented in the EEZ while the catch (thousand tonnes) is represented in the land polygon."}
+
+img <- readPNG(here("./Figures/S1_Catch_EEZ.png"))
+grid.raster(img)
+```
+
+![**Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
+The number of species is represented in the EEZ while the catch (thousand tonnes) is represented in the land polygon.
+**](./Figures/S1_Catch_EEZ.png)
+
+```{r Call_Sup_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
+
+img <- readPNG(here("./Figures/S2_RFMO.png"))
+grid.raster(img)
+```
+
+![**Number of shared species by RFMOs. Analysis included with 99 species managed by Fourteen RFMOs **](./Figures/S2_RFMO.png)
+
+**Suplemental figure Trans_Catch_MAP**
+
+# Recicled text (Not to be included)
 
@@
 -->
+
+<!-- However, the effectiveness of RFMOs responsible for managing high migratory stocks, has been previously questioned [@CullisSuzuki:2010fi]. -->

### 2019-12-25 Manuscript_Draft.Rmd
References update

@@
 
-Distributions of marine species around the world are not bounded by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hunch; @NelsonFishesOfTheWorld].
+Distributions of marine species around the world are not bounded by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
 However, management of living marine resources is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua].
@@
 Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@REF].
-For example, evironmental fluctuation leading to changes in the stock distribution [@Mills] and fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
-Moreover, climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Mills].
+For example, evironmental fluctuation leading to changes in the stock distribution [@Munro:2002uf] and fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
+Moreover, climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Miller:2013iv].
 
@@
 For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
-Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species [@REFNEreus] and two structurally distinct species distribution models [@REFGabs; @Zeller] (see Methods).
-The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller].
+Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016] (see Methods).
+The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
 A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
 Finally, the last criteria determined a spatial treshold to confirm that a species occurs in both neighboring EEZs.
-Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller] and categorized them according to catch trends [@Kleisner:2013gh].
+Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
 
@@
 This is equivalent to **49.8**% of the global revenue of the same period.
-These values are higher than previously estimated reinforcing the importance of these stocks at the global level [@Teh].
+These values are higher than previously estimated reinforcing the importance of these stocks at the global level [@Teh:2015gd].
 
@@
 Peru's catches come mainly from Peruvian anchoveta (*Engraulis ringens*), shared with Chile, accounting for 79% of the transboundary species production.
-Similarly, Russia shares the (currently) largest fishery in the world, Alaskan polllock (*Theragra chalcogramma*) with both Japan and the US [@SOFIA2018].
+Similarly, Russia shares the (currently) largest fishery in the world, Alaskan polllock (*Theragra chalcogramma*) with both Japan and the US [@FAO:2018KK].
 Despite this, catches are only significantly different in E.
-Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@SOFIA2018] getting around 1/3 of its capture from transboundary species, followde by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
+Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followde by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
 
 The exploitation category of transboundary species significantly differs from each other (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished under 50% of their historical maximum peak (Fig.2).
-This is true for all (but Oceania) continents with no significan difference between them (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05), suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @PaulyNature2013].
+This is true for all (but Oceania) continents with no significan difference between them (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05), suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
 Countries that are today harvesting at this rate (Category C) should be paying extra care in the management of these species (Fig.
@@
 
-While these catch trends do not directly reflect stock status [@Branch:2011br] - e.g.
-other factors like markets, fishing policies or extreem events also influence catch volume [@PaulyNature2013] - they could ressemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
-Empirical analysis suggest that management of transboundary species will have better outcomes in terms of fish yield and sustainabillity whith cooperation between nations [@REF].
+While these catch trends do not directly reflect stock status - e.g.
+other factors like markets, fishing policies or extreem events also influence catch volume [@Pauly:2013gs; @Branch:2008kk] - they could ressemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
+Empirical analysis suggest that in most cases, management of transboundary species will have better outcomes in terms of fish yield and sustainabillity whith cooperation between nations [@Bailey:2010ga].
 Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
@@
 Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** thousand tones to landings and USD **968** million in revenue to the countries involved in the dispute.
-In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky].
+In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky:2018cb].
 
@@
 
-Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@NelsonFishesOfTheWorld].
+Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@Nelson:2016kk].
 Not surprisingly, highly migratory pelagic-oceanic species are the only group that significantly differs in terms of sharing countries (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 nations shared per species (Fig.
@@
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are catalogued as stradling species by FAO definitions and globally managed by Regional Fisheries Management Organizations (RFMOs) [@FAO].
+Due to their large migration patterns and presence in areas beyond national jurisdiction, pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are catalogued as stradling species and globally managed by Regional Fisheries Management Organizations (RFMOs).
 Fifteen major RFMOs in the world oversee the management of 99 species, most of them fished in areas beyond national jurisdiction [@CullisSuzuki:2010fi].
@@
 The method is based on a series of criteria to be met and the overlay of species distributions and the spatial boundaries of the world’s EEZs.
-For the current analysis we work at the species level and adopt the Food and consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf; @FAO].
+For the current analysis we work at the species level and adopt the Food and consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf].
 All data was scaled to 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
@@
 from 0 to 1) rather than a discrete, yes or no, index .
-All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the pacages *tidiverse*[@], *data.table*[@], *wesanderson*[@], *janitor*[@], *spdep*[@], *sf*[@], *sp*[@], *rgdal*[@], *tools*[@], *parallel*[@], *rfishbase*[@], *zoo*[@].
+All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the pacages *tidiverse*[@PackagetidyverseE:2017vq], *data.table*[@Packagedatatable:2019uh], *wesanderson*[@], *janitor*[@], *spdep*[@], *sf*[@PackagesfSimpleF:2018vp], *sp*[@], *rgdal*[@PackagergadalBind:2018vy], *tools*[@], *parallel*[@], *rfishbase*[@], *zoo*[@].
 All code is available at https://github.com/jepa/FishForVisa.
@@
 We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
-Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf* *R* package [@SF:package].
+Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf*-*R* package.
 When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appeared in more than one sub-region.

### 2019-12-31 Initial_Analysis.Rmd
Changed plots colors

@@
   # "ggsflabel", # for nice sf_plots labels
-  "spdep", # for poly2nb
+  # "spdep", # for poly2nb old
   "sf", #Spatial analysis 
@@
   left_join(SAU_Revenue_Data,
-            by = c("fishing_entity_id","taxon_key")) %>% 
+            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
   group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
@@
 # Catch_Country
+
+Catch_Breaks <- c(-1,10,100,1000,5000,10000)
+
+Catch_Country <- SAU_Catch_Data %>%
+  group_by(eez_name) %>%
+  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>%
+  group_by(fishing_entity) %>%
+  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
+  mutate(
+    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
+  #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
+         Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
+         Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
+                         labels = c('super low', 'low','median','high','super high'))
+  ) %>% 
+  filter(fishing_entity_catch > 0)
 
@@
     units = "in",
-    filename = "Territory_circular_status.png",
-    path = Figures_Path
+    filename = "Plot.png"
+    # filename = "Territory_circular_status.png",
+    # path = Figures_Path
   )
@@
     )
-  )
+  ) %>% 
+  filter(!group %in% c("Bathydemersal","Pelagic"))
 
@@
   filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
-  # mutate(taxon_key = as.character(taxon_key)) %>%
   left_join(SAU_Catch_Data,
@@
   )
+
 ```
@@
   scale_fill_manual("Ecosystem Preference",
-                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                               wes_palette(n = 3, name = "GrandBudapest2")
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 3, name = "Darjeeling2")
                     ),
@@
   scale_colour_manual("Ecosystem Preference",
-                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                                 wes_palette(n = 3, name = "GrandBudapest2")
+                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 3, name = "Darjeeling2")
                       ),
@@
   scale_fill_manual("",
-                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
-                               wes_palette(n = 3, name = "GrandBudapest2")
+                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 3, name = "Darjeeling2")
                     ),
@@
 
-Area_Index_Level <- seq(.1,0.5,0.1)
+Area_Index_Level <- c(seq(.1,0.5,0.1),0.25)
+result <- c(40,35,28,18,4,31.5)
+
+plot(result~Area_Index_Level)
 
@@
     filter(
-      Area_Index >= Area_Index_Level[i],
-      Area_Index <= 1-Area_Index_Level[i],
-      Model_Index == MI
-    ) %>% 
-    group_by(Territory) %>% 
+      area_index >= Area_Index_Level[i],
+      area_index <= 1-Area_Index_Level[i],
+      model_index == MI
+    ) %>% 
+    group_by(eez_name) %>% 
     summarise(
-      n_trans_spp = length(unique(TaxonKey)),
-      n_Neighbours = length(unique(Neighbour)),
+      n_trans_spp = length(unique(taxon_key)),
+      n_Neighbours = length(unique(eez_neighbour)),
       Trans_Rate = n_trans_spp/n_Neighbours
@@
                    binwidth = 10, 
-                   colour = "white"
+                   colour = "white",
+                   fill = ifelse(i!= 6,"grey80","grey20")
     ) +
@@
       y = "Frequency of EEZs",
-      title= paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")
+      title= paste((Area_Index_Level[i]*100),"% area treshold"," (Median ",Median_data,")",sep="")
     ) +
@@
     ggtheme_plot()
-
 }

### 2019-12-31 Manuscript_Draft.Rmd
Finished second draft and started abstract

@@
   chunk_output_type: inline
-# bibliography: ./References/FishForVisa_Ref.bib
-# csl: ./References/science.csl
+bibliography: ./References/FishForVisa_Ref.bib
+csl: ./References/science.csl
 ---
@@
 
+The precense of a species in time and space is linked to a combination of biotic and abiotic factors, but the concept of species distribution is rarely integrated into fisheries management, or policy, .
+
+Identifying what species re transboundary is a first step to the proper management of shared stocks and achieving sustainabillity of marine ressources.
+
+Incorporating the concept of species distribution into fisheries management, or policy, is not allways hapens as shown by the delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s.
+Shared marine ressources are inheratably complex to manage and thus, require special care.
+However, forty years after the formal adoption of EEZs, the question of how many shared species exist in the world based on their distribution is still unanswered.
+Here, we ucombine species' distributions with the nation's EEZs in order to determine the number of transboundary stocks.
+moreover, we identify their importance in terms of catch and revenue and discuss the
+
 <!-- An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 Distributions of marine species around the world are not bounded by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
-However, management of living marine resources is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua].
+Thus, a species can be cosmopolitan and have a broader distribution like the spiny dogfish (*Squalus acanthias*), or endemic like the masu salmon (*Oncorhynchus masou*) who's distribution is limited to the Japanese coast [@Nelson:2016kk].
+However, management of living marine resources is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
 The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
-Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@REF].
-For example, evironmental fluctuation leading to changes in the stock distribution [@Munro:2002uf] and fishing quotas set by different nations for a shared fishery resource have led to conflict [@Spijkers:2017ij].
-Moreover, climate change, which is shifting species distributions, is likely to exacerbate this type of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Miller:2013iv].
+Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Bailey:2010ga].
+For example, environmental fluctuation leading to changes in species distribution of a shared fishery have led to conflict because of changes in the proportion of captures between countries [@Munro:2002uf], or pressure in the quota allocation due to new participants wanting to join the fishery [@Spijkers:2017ij].
+Moreover, climate change, which is shifting species distributions, is likely to exacerbate these types of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Miller:2013iv].
 
-Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that distribute across two or more EEZs (hereafter called shared species) in the world is still unclear.
+Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by 2 or more neighboring coastal nations (hereafter called transboundary species [@Munro:2002uf]) in the world is still unclear.
 Caddy in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
 However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
-More recently, Teh et al.
-(2010) estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million tones and a global landed value of USD 30.7 trillion.
-While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
-Getting accurate estimates of the number of shared species and where they are located can help develop fisheries management and conservation plans that account for the challenges from transboundary resources management [@Millis].
+More recently, Teh and Sumaila (2010) estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million tones and a global landed value of USD 30.7 trillion.
+Such analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
+In here, we overlay the known distribution of **968** commercially valuable marine fish species and the EEZ of 153 coastal countries to identify those that are shared between neighboring EEZs and determine their contribution to the world's fisheries catch and revenue.
 
-<!-- ## Methods summary (250/250 words) -->
+We developed a four-criteria methodology to determine if a species was transboundary (see Methods).
+The first criteria consisted in only considering shared species between neighboring EEZs, rather than the specie's extended distribution.
+For the second criteria we considered a species to be present in a $0.5^o$ x $5^o$ grid cell if all data sources predicted positive occurrence.
+Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016].
+The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
+A species was kept in a grid cell if both predicted species occurrences and catch data were positive.
+Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
+Once transboundary species were identified, we estimated their contribution to fishing landings and revenues using the *Sea Around Us* database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
+We carry out the analysis at the species per EEZ level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
+Despite loosing detail-specific (e.g.
+a species could have multiple stocks within an EEZ),  many fisheries within a country or EEZ are managed at the species level, and recent research has suggested strong connectivity between stocks thousand of kilometers away [@Ramesh:2019va].
 
-This paper aims to identify the world current transboundary species and determine their contribution to the catch and revenue of the world marine fisheries.
-The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks, shared by 2 or more neighboring coastal nations; (ii) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (iii) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
-We focus on estimating the number of species that meet the first category.
-We overlay the known distribution of **968** commercially valuable marine fish species and the Exclusive Economic Zones of 153 coastal countries to determine the total number of transboundary species and their contribution to global catch and landed value.
-We carry out the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
+## Results and discussion (~1000 words)
 
-We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
-The first criteria consisted in only considering shared species between neighbouring EEZs, rather than the extended distribution.
-For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
-Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016] (see Methods).
-The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
-A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
-Finally, the last criteria determined a spatial treshold to confirm that a species occurs in both neighboring EEZs.
-Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
+We identified **633** transboundary species in the world, more than double the number previously estimated [@Teh:2015gd], accounting for **65.4%** of the species analyzed (Fig.
+1A).
+Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **64%** of the EEZ-global catch, and generating USD **79,745** million in fishing revenue.
+This is equivalent to **49.8%** of the global revenue of the same period.
+These values are higher than previously estimated reinforcing the importance of these species at the global level [@Teh:2015gd].
 
-## Results and discussion (~500/1000 words)
-
-Overall, we estimated **633** transboundary species in the world, more than double the number previously estimated [@Teh:2015gd], accounting for **65.4**% of the species analyzed (Fig.
-1A).
-Between 2005 and 2014, national fleets targeting shared stocks within EEZs landed an average of **69.2** million tonnes, representing **64**% of the EEZ-global catch, and generating USD **79,745** million in fishing revenue.
-This is equivalent to **49.8**% of the global revenue of the same period.
-These values are higher than previously estimated reinforcing the importance of these stocks at the global level [@Teh:2015gd].
-
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="A) Number of transboundary species per EEZ and they contribution to countries fishing revenue.
-The number of species is represented in the EEZ while the revenue is represented in the land polygon.
-B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.Points = mean +- sd."}
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and they contribution to fishing catch and revenue.** A) The number of species is represented in the EEZ while revenue from these species fished within the EEZ is represented in the land polygon.
+B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.
+Points = mean +- sd."}
 
@@
 
-![**A) Number of transboundary species per EEZ and they contribution to countries fishing revenue.
-The number of species is represented in the EEZ while the revenue is represented in the land polygon.
+![**Fig.
+1 Number of transboundary species and they contribution to fishing catch and revenue.** A) The number of species is represented in the EEZ while revenue from these species fished within the EEZ is represented in the land polygon.
 B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.
-Points = mean +- sd.**](./Figures/Fig1.png)
+Points = mean +- sd.](./Figures/Fig1.png)
 
-Transboundary species are particulary important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+Transboundary species are particularly important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
 The large variation in revenue from these regions is driven by China (USD 6,279 million), in E.
 Asia and the US (USD 9,605 million) in N.
-America who contribue 55% and 83% of the region's revenue, respectiveley.
+America who contribute 55% and 83% to the region's revenue, respectively.
 Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with more revenue from transboundary species.
-These 5 nations are responsable for 30% of the global revenue from transboundary species.
-Peru and Russia lead the production of transboundary species harvesting over 5,000 thousand tones (**Suplemental figure Trans_Catch_MAP**).
+These five nations are responsible for 30% of the global revenue from transboundary species.
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead the production of transboundary species harvesting over 5,000 thousand tones (**Supplemental figure Trans_Catch_MAP**).
 Peru's catches come mainly from Peruvian anchoveta (*Engraulis ringens*), shared with Chile, accounting for 79% of the transboundary species production.
-Similarly, Russia shares the (currently) largest fishery in the world, Alaskan polllock (*Theragra chalcogramma*) with both Japan and the US [@FAO:2018KK].
+Similarly, Russia shares the Alaskan polllock (*Theragra chalcogramma*) fishery with both Japan and the US.
 Despite this, catches are only significantly different in E.
@@
 
-The exploitation category of transboundary species significantly differs from each other (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished under 50% of their historical maximum peak (Fig.2).
-This is true for all (but Oceania) continents with no significan difference between them (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05), suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
-Countries that are today harvesting at this rate (Category C) should be paying extra care in the management of these species (Fig.
-2).
+Effective management of shared species is a challenging process as it often requires countries to agree on mutual targets in order to achieve sustainable harvest [@Munro:2002uf].
+We found significant differences in the exploitation rate of transboundary species (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished at levels below 50%, sometimes lower than 10%, of their historical maximum peak (Fig.2).
+This is the case of coastal nations in all continents, but Oceania, with no significant difference between continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05), suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
+While these catch trends do not directly reflect stock status - e.g.
+other factors like markets, fishing policies or extreme events also influence catch volume [@Pauly:2013gs; @Branch:2008kk] - they could resemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
+Countries that are today harvesting transboundary species at this rate (Category C) should revise their management policies to make sure these align with sustainable harvest of shared resources [@Munro:2004ug].
 
@@
 
-While these catch trends do not directly reflect stock status - e.g.
-other factors like markets, fishing policies or extreem events also influence catch volume [@Pauly:2013gs; @Branch:2008kk] - they could ressemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
-Empirical analysis suggest that in most cases, management of transboundary species will have better outcomes in terms of fish yield and sustainabillity whith cooperation between nations [@Bailey:2010ga].
-Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Collaboration can also reduce conflict between nations over shared ressources.
+Empirical analysis suggest that in most cases, management of transboundary species will have better outcomes in terms of fish yield when nations cooperate [@Bailey:2010ga].
+Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
+Collaboration can also reduce conflict between nations over shared resources.
 Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts like Canada, the US, China and Russia [@Spijkers:2019cz].
-For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Miller2003].
+For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Munro:2002uf].
 Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** thousand tones to landings and USD **968** million in revenue to the countries involved in the dispute.
@@
 
-First steps for shared management start with information sharing, then this and that. Proper management treaties not only have but can also be stronger in the fase of a canging climate.
+<!-- First steps for shared management start with information sharing, then this and that. Proper management treaties not only have but can also be stronger in the fase of a canging climate. -->
 
-Species can have a cosmopolitan distribution, that is, a broader distribution, or be limited to a specific region, known as endemic [@Nelson:2016kk].
-Not surprisingly, highly migratory pelagic-oceanic species are the only group that significantly differs in terms of sharing countries (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 nations shared per species (Fig.
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], many of which are highly migratory pelagic-oceanic species like skipjack tuna (*Katsuwonus pelamis*), Common dolphinfish (*Coryphaena hippurus*), and tunas (*Thunnus sp.*).
+This is the only group whoes EEZ range (e.g.
+the number of EEZs where the species occur as transboundary) significantly differs from the others (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species (Fig.
 3).
@@
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, pelagic-oceanic species such as skipjack tuna (*Katsuwonus pelamis*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) are catalogued as stradling species and globally managed by Regional Fisheries Management Organizations (RFMOs).
+Due to their large migration patterns and presence in areas beyond national jurisdiction, highly migraroty pelagic fish species are cataloged as straddling and many of them globally managed by Regional Fisheries Management Organizations (RFMOs).
 Fifteen major RFMOs in the world oversee the management of 99 species, most of them fished in areas beyond national jurisdiction [@CullisSuzuki:2010fi].
-We estimate that 81.8% of these species (*n* = 81) are actually shared within neighbouring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighbouring RFMOs (**Suplemental figure RFMO_MAP**).
-The catch from pelagic-oceanic species comes mainly from five South Pacific Islands nations, from which three (Kiribalti, Solomon and Papua New Guinea) are members of the Pacific Nauru Agreement (PNA) (Fig.
-3B).
-The PNA manages 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year [@https://www.ffa.int/nauru_agreement].
+We estimate that 81.8% of these species are actually shared within neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (**Supplemental figure RFMO_MAP**).
+The effectiveness of RFMOs responsible for managing high migratory stocks has been previously questioned [@CullisSuzuki:2010fi; Lodge:2007bt].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested ($B/B_{MSY} > 1$ and $F/F_{MSY} < 1$) with only three stocks currently overfished [@Pons:2016ep].
+Within national waters, we estimated that the catch of transboundary pelagic-oceanic species comes mainly from five Island Nations in the South Pacific from which three (Kiribalti, Solomon and Papua New Guinea) are members of the Pacific Nauru Agreement (Fig 3B).
+The parties to the Nauru Agreement sustainably manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
 
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these might be cosmopolitan but not necessarily highly migratory (e.g.
+<!-- [@https://www.ffa.int/nauru_agreement]  -->
+
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (e.g.
 *Solea solea*, *Panulirus argus*) (Fig.
@@
 The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-Moreover, many coastal communities, specially in developing regions, and highly dependent on fishing local fish (e.g.
-reef fish) for food security and improved livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf; @https://www.sciencedirect.com/science/article/pii/S0308597X17308357].
-For example, from the top five countries fishing transboundary reef - associated species, Indonesia, Malaysia and the Philippines are among the higest fish consumption per capita in the world with 20, 60 and 40 kg per year, respectiveley [@https://www.sciencedirect.com/science/article/pii/S0308597X12001315].
+Moreover, many coastal communities, specially in developing regions, and highly dependent on subsistance fishing (e.g.
+reef fish) for food security and livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf; @Cabral:2018hc].
+For example, from the top five countries fishing transboundary reef - associated species (Fig.
+3B), Indonesia, Malaysia and the Philippines are among the highest fish consumption per capita in the world with 20, 60 and 40 kg per year, respectively [@Foale:2013iw].
+In these countries, reeef fish contributes substantially to both food security and livelehood of coastal communities [@Cabral:2018hc].
 
-The global contribution of transboundary species to fishing revenue and capture is compelling, with transboundary species playing an important role in many fishing nations.
-Transboundary species have played and continue to play an important role in fisheries conflicts, with climate change likely to exacerbate this trend given expected shifts in species distribution and the emergence of 'new' shared species.
-Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability and can be flexible to accommodate future changes.
+Our study identifies the current species shared by neighbouring coastal nations and highlights the importance of these species in terms of global capture and revenue from wild fisheries.
+Our results show that captures and revenues from shared species are higher than previously estimated and particularly important to countries in Northern America and Eastern Asia.
+This result highlights the importance of these fisheries and their potential contribution to regional food security and wellbeing.
+Moreover, the vast majority of transboundary species are harvest at low rates with no geographic variation.
+Previous work has found that collaboration will result in better outcomes for shared marine resources.
+Thus, countries should pay specific attention in the management of the identified transboundary stocks potentially creating collaborative management plans.
+Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
 
@@
 Catches are also spatially allocated [@Zeller2016].
-Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten yeares of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten years of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 
@@
 Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states.
-In some cases, criteria also work as indexes to measure the uncertainty in the analysis as they provided continuos index (e.g.
+In some cases, criteria also work as indexes to measure the uncertainty in the analysis as they provided continuous index (e.g.
 from 0 to 1) rather than a discrete, yes or no, index .
-All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the pacages *tidiverse*[@PackagetidyverseE:2017vq], *data.table*[@Packagedatatable:2019uh], *wesanderson*[@], *janitor*[@], *spdep*[@], *sf*[@PackagesfSimpleF:2018vp], *sp*[@], *rgdal*[@PackagergadalBind:2018vy], *tools*[@], *parallel*[@], *rfishbase*[@], *zoo*[@].
+All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*[@Packagedatatable:2019uh], *janitor*[@PackagejanitorSim:2018ur], *wesanderson*[@Packagewesanderson:2018vn], *rfishbase*[@PackagerfishbaseR:2019th], *R.matlab*[@PackageRmatlabRe:2018un], *sf*[@PackagesfSimpleF:2018vp], *sp*[@PackagespClasses:2019tn], *tidiverse*[@PackagetidyverseE:2017vq], *tidytext*[@PackagetidytextTe:2019vk], and *zoo*[@PackagezooSInfr:2019tm].
 All code is available at https://github.com/jepa/FishForVisa.
@@
 The index is unit-less and represents a scale from 0.3 to 1 where 0.3 means only one dataset reports presence of the species in a grid cell, 0.6 represents two of three sources, and 1 means agreement between all datasets.
-For the analysis, we selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species (**S1_Map_per_dataset**).
+For the analysis, we selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species.
 
@@
 The contribution of transboundary species was done by aggregating the catch of each species that happened within the EEZ of the countries sharing that species.
-For this study, we did not include catch from areas beyond national jurisdiction.
+For this study, we did not include catch nor revenue from areas beyond national jurisdiction.
 Finally, we use the catch data to determine the exploitation category of each species within a EEZ.
-Although this method has previously used to estimate stock status [@Grainger:1996tk; @Kleisner:2011wn], the categories presented here are intended to be seen as catch trends, and not status of each species.
+Although this method has previously used to estimate stock status [@Grainger:1996tk], the categories presented here are intended to be seen as catch trends, and not status of each species.
 We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years.
-Three categories were drawn from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**).
+Three categories were drawn from a method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**) [@Kleisner:2011wn].
 Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
+We perform a series of one-way analysis of variance ( one-way ANOVA) to determine significant differences (statistically) between the means of different groups (e.g.
+categories, regions, species) regarding transboundary species and their contribution in terms of catch and revenue.
 
-```{r Status_Table, eval = F, echo = F}
+```{r Status_Table, eval = T, echo = F}
 
@@
 
-Stock_Status <- c("A - Growing Fishery","B - Stable Fishery"," C - Fishery under 10% of Peak","No Status")
+Categories <- c("A - Growing Fishery",
+                  "B - Stable Fishery",
+                  "C - Fishery under 10% of Peak",
+                  "No Status")
 
@@
 
-data.frame(Stock_Status,
+data.frame(Categories,
            Rules) %>% 
   kable("latex", booktabs = T,
-        caption = "Rules to determine the status of each transboundary species") %>%
+        caption = "Rules to determine the category of each transboundary species") %>%
   kable_styling(full_width = F) %>%
@@
 
-# Suplements
+## Caveats
+
+# Supplements
 
@@
 
-**Suplemental figure Trans_Catch_MAP**
+It is expected that the number of gridcells where a species is present (*Area Index*) would directly influence whether or not a species is considered transboundary.
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (*S3 Index Area*).
+As expected, using a more relaxed value (e.g.
+the species is present within 10% or more of the EEZ) will result in more transboundary species giving a median of 40 EEZs shared per species, while a more strict value (e.g.
+50%) will give a median of 4.
+For the current analysis we presented the results using a 25% *Area Index* threshold (*S3 Index Area* - darker histogram).
 
-# Recicled text (Not to be included)
+```{r Call_Sup_3, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Histogram of transboundary species using different values of Area Index.
+Darker histogram represents used value (25%) in the analysis"}
+
+img <- readPNG(here("./Figures/S2_RFMO.png"))
+grid.raster(img)
+```
+
+![**Histogram of transboundary species using different values of Area Index. Darker histogram represents used value (25%) in the analysis**](./Figures/S3_Area.png)
+
+#References
+
+<!-- # Recicled text (Not to be included) -->
 
@@
 
-<!-- However, the effectiveness of RFMOs responsible for managing high migratory stocks, has been previously questioned [@CullisSuzuki:2010fi]. -->
+<!-- *Getting accurate estimates of the number of shared species and where they are located can help develop fisheries management and conservation plans that account for the challenges from transboundary resources management.*  -->
+
+<!-- The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks, shared by 2 or more neighboring coastal nations; (ii) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (iii) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
+We focus on estimating the number of species that meet the first category.
+-->
+
+<!-- We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
+The first criteria consisted in only considering shared species between neighbouring EEZs, rather than the extended distribution.
+For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
+Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016] (see Methods).
+The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
+A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
+Finally, the last criteria determined a spatial treshold to confirm that a species occurs in both neighboring EEZs.
+Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
+-->
+
+<!-- Only Bluefin (*Thunnus thynnus*) in the Pacific, Bigeye (*Thunnus obesus*) in the west Pacific, and Yellowfin (*Thunnus albacares*) in the Atlantic still experiencing overfishing  -->

### 2019-12-31 Initial_Analysis.Rmd
Colors!

@@
            alpha=0.5) +
+  # scale_fill_manual("Catch Category",
+  #                   values = c(rev(wes_palette(n = 5, name = "Rushmore1")),"grey")
+  #                   ) +
   scale_fill_manual("Catch Category",
                     values = c(
-                      "#9986A5", # Developing / Rebulding / Cat A / blue
-                      "#79402E", #Max exp. / Cat B / green
-                      "#CCBA72", # collapsed / Overexp. / Cat. C / Red
+                      "#046C9A", # Developing / Rebulding / Cat A / blue
+                      "#0B775E", #Max exp. / Cat B / green
+                      "#F2300F", # collapsed / Overexp. / Cat. C / Red
                       "#8D8680"
@@
     units = "in",
-    filename = "Plot.png"
-    # filename = "Territory_circular_status.png",
-    # path = Figures_Path
+    # filename = "Plot.png"
+    filename = "Territory_circular_status.png",
+    path = Figures_Path
   )

### 2020-01-02 Manuscript_Draft.Rmd
Included all information needed for submission

@@
 ---
-title: "Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species"
+title: "Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)"
 author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
 date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
-subtitle: "DRAFT DO NOT SHARE"
-# subtitle: "Fish do not need Visas (16/40 character maximum)"
+# subtitle: "DRAFT DO NOT SHARE"
+subtitle: "Most neighbour nations share marine species (38/40 characters)"
 output:
@@
 
-<!-- # Instructions for submission -->
+# Instructions for submission
 
-<!-- - Journal: *Science*  -->
+- Journal: *Science*
 <!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
@@
 
-<!-- -- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance.
+-- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance.
 Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.
--->
 
-<!-- Policy Forums (1000 to 2000 words, 1-2 figures, and up to 15 references) presents issues related to the intersections between science and society that have policy implications. -->
-
-<!-- In both cases Materials and Methods should be included in supplementary material -->
+<!-- Materials and Methods should be included in supplementary material -->
 
@@
 
-<!-- - Reviewers: Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers. -->
+# Reviewers (5):
+*Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*
 
-<!-- # One Sentence Summary (~ 125 characters) -->
+**Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions)
 
-<!-- A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
-This will appear online adjacent to the title and should not repeat phrases already present there -->
+- **Potential Reviewers (J)**  
+ -- Gakushi Ishimura,  
+ -- Kathleen Miller, National Center for Atmospheric Research, Boulder, Colorado, USA  
+ -- Malin Pinsky, Rutgers University, New Brunswick, New Jersey, USA  
+ -- Steven D. Gaines, University of California, Santa Barbara, Santa Barbara, California, USA
 
-<!-- - Field code: *Fisheries* -->
+- **Excluded Reviewers (J)**  
+-- U. Rashid Sumaila, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada  
+-- Louise S.L. Teh, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada
 
-<!-- # **Abstract** (~125 words) -->
+# One Sentence Summary (125/~125 characters)
+*A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
+This will appear online adjacent to the title and should not repeat phrases already present there*
 
-The precense of a species in time and space is linked to a combination of biotic and abiotic factors, but the concept of species distribution is rarely integrated into fisheries management, or policy, .
+Over 50% of marine fish landings and revenue comes from species shared by neighbouring nations having direct implications to fisheries management.
 
-Identifying what species re transboundary is a first step to the proper management of shared stocks and achieving sustainabillity of marine ressources.
+# Field code (Max. 2)
 
-Incorporating the concept of species distribution into fisheries management, or policy, is not allways hapens as shown by the delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s.
-Shared marine ressources are inheratably complex to manage and thus, require special care.
-However, forty years after the formal adoption of EEZs, the question of how many shared species exist in the world based on their distribution is still unanswered.
-Here, we ucombine species' distributions with the nation's EEZs in order to determine the number of transboundary stocks.
-moreover, we identify their importance in terms of catch and revenue and discuss the
+- *Fisheries*
 
-<!-- An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
-It should be a single paragraph.
--->
+# Abstract (125/~125 words)
+*An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
+It should be a single paragraph.*
+
+Regulatory boundaries and species distributions are not always aligned, therefore marine species often cross multiple Economic Exclusive Zones (EEZs).
+This represents a challenge for fisheries management as the benefits from a shared resource is often maximized through collaboration.
+In here, we combined species distributions and the spatial delimitation of EEZs to identify the number of exploited marine fish species that are shared between neighbouring nations.
+We found that 64% of the world's capture and 50% or revenue comes from 633 shared species, with some countries receiving over 70% of their benefits from a few shared resources.
+Identifying shared species can play a critical role in the sustainability of wild fisheries suggesting a need for collaborative management strategies.
 
@@
 
-## Results and discussion (~1000 words)
+<!-- ## Results and discussion (~1000 words) -->
 
@@
 
-<!-- # **References** (up to 40 for reports and 15 for policy forum) -->
-
 <!-- # **Acknowledgments* * -->
@@
 -->
-<!-- ## Data and materials availability: Any restrictions on materials such as MTAs.  -->
+
+## Data and materials availability
+*Any restrictions on materials such as MTAs.*
+
+Gabriel, is there any restriction with the data?
 
@@
 
-#References
+# References (59/about 30)
 

### 2020-01-02 Manuscript_Draft.Rmd
Reduced text lenght to accomodate the 2500 words (With Refs.). Currently under 2000 (Without Refs.)

@@
  -- Malin Pinsky, Rutgers University, New Brunswick, New Jersey, USA  
+ -- Megan Baily, 
  -- Steven D. Gaines, University of California, Santa Barbara, Santa Barbara, California, USA
@@
 
-Distributions of marine species around the world are not bounded by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
-Thus, a species can be cosmopolitan and have a broader distribution like the spiny dogfish (*Squalus acanthias*), or endemic like the masu salmon (*Oncorhynchus masou*) who's distribution is limited to the Japanese coast [@Nelson:2016kk].
-However, management of living marine resources is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
+Distributions of marine species around the world are not restricted by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
+Thus, a species can have a broader distribution (cosmopolitan), or be endemic [@Nelson:2016kk].
+However, fisheries management is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
 The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
-Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Bailey:2010ga].
-For example, environmental fluctuation leading to changes in species distribution of a shared fishery have led to conflict because of changes in the proportion of captures between countries [@Munro:2002uf], or pressure in the quota allocation due to new participants wanting to join the fishery [@Spijkers:2017ij].
-Moreover, climate change, which is shifting species distributions, is likely to exacerbate these types of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Miller:2013iv].
+Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; @Bailey:2010ga].
+For example, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+Moreover, climate change is likely to exacerbate these types of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Miller:2013iv].
 
-Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by 2 or more neighboring coastal nations (hereafter called transboundary species [@Munro:2002uf]) in the world is still unclear.
-Caddy in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
-However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
-More recently, Teh and Sumaila (2010) estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million tones and a global landed value of USD 30.7 trillion.
-Such analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
-In here, we overlay the known distribution of **968** commercially valuable marine fish species and the EEZ of 153 coastal countries to identify those that are shared between neighboring EEZs and determine their contribution to the world's fisheries catch and revenue.
+Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear due to data limitations [@Caddy:1997ue], and methodological approaches [@Teh:2015gd].
+In here, we aimed to estimate the number of exploited marine fish species shared by neighbouring countries and determine their contribution to global catch and fisheries revenue.
 
-We developed a four-criteria methodology to determine if a species was transboundary (see Methods).
+We overlay the known distribution of **968** commercially valuable marine species and the EEZ of 153 coastal countries and developed a four-criteria methodology to determine if a species was transboundary.
 The first criteria consisted in only considering shared species between neighboring EEZs, rather than the specie's extended distribution.
-For the second criteria we considered a species to be present in a $0.5^o$ x $5^o$ grid cell if all data sources predicted positive occurrence.
-Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016].
-The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
+For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
+The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data.
 A species was kept in a grid cell if both predicted species occurrences and catch data were positive.
 Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
-Once transboundary species were identified, we estimated their contribution to fishing landings and revenues using the *Sea Around Us* database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
+Once transboundary species were identified, we estimated their contribution to fishing landings and revenues and categorized them according to catch trends.
 We carry out the analysis at the species per EEZ level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
@@
 
-We identified **633** transboundary species in the world, more than double the number previously estimated [@Teh:2015gd], accounting for **65.4%** of the species analyzed (Fig.
+We identified **633** transboundary exploited species in the world, more than double the number previously estimated [@Teh:2015gd], accounting for **65.4%** of the species analyzed (Fig.
 1A).
@@
 This is equivalent to **49.8%** of the global revenue of the same period.
-These values are higher than previously estimated reinforcing the importance of these species at the global level [@Teh:2015gd].
+These values are higher than previously estimated [@Teh:2015gd], reinforcing the importance of these species at the global level.
 
@@
 
-![**Fig.
-1 Number of transboundary species and they contribution to fishing catch and revenue.** A) The number of species is represented in the EEZ while revenue from these species fished within the EEZ is represented in the land polygon.
-B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.
+![Fig.
+1.
+Number of transboundary species and they contribution to fishing catch and revenue.
+A) The number of species and revenue are represented in the EEZ and land polygon, respectively.
+B) Contribution of tranbsoundary species to regional revenue (left) and catch (right).
 Points = mean +- sd.](./Figures/Fig1.png)
@@
 Transboundary species are particularly important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
-The large variation in revenue from these regions is driven by China (USD 6,279 million), in E.
+The large variation in revenue from these regions are driven by China (USD 6,279 million) in E.
 Asia and the US (USD 9,605 million) in N.
@@
 Despite this, catches are only significantly different in E.
-Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followde by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
+Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
 
-Effective management of shared species is a challenging process as it often requires countries to agree on mutual targets in order to achieve sustainable harvest [@Munro:2002uf].
+Harvest rates and fisheries management are key to achieve the sustainable development goals [@SDGs].
 We found significant differences in the exploitation rate of transboundary species (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished at levels below 50%, sometimes lower than 10%, of their historical maximum peak (Fig.2).
-This is the case of coastal nations in all continents, but Oceania, with no significant difference between continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05), suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
+This is the case of coastal nations in all continents, but Oceania, with no significant difference between continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05).
 While these catch trends do not directly reflect stock status - e.g.
 other factors like markets, fishing policies or extreme events also influence catch volume [@Pauly:2013gs; @Branch:2008kk] - they could resemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
-Countries that are today harvesting transboundary species at this rate (Category C) should revise their management policies to make sure these align with sustainable harvest of shared resources [@Munro:2004ug].
+Thus suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
+Corroborating the status of species harvested at this rate (Category C) and considering best practices in managing shared resources [@Munro:2004ug; @Lodge:2007bt] could provide crucial to the sustainability of transboundary species.
 
@@
 
-![**Number of transboundary species by catch category, country, and continent.
-Category A, fishing between 10%-50% of max catch peak after a drop larger than 10% of max peak; Category B, fishing over 50% of max catch peak; Category C, fishing is between 10-50% of max catch peak or less than 10%**](./Figures/Fig2.png)
+![Fig.
+2.
+Number of transboundary species by catch category.
+Category A, fishing between 10%-50% of max catch peak after a drop larger than 10% of max peak; Category B, fishing over 50% of max catch peak; Category C, fishing less than 50% of max peak](./Figures/Fig2.png)
 
@@
 Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
+Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], although cooperation and non-cooperation can be a more complex process [@Jensen:2015cf].
 Collaboration can also reduce conflict between nations over shared resources.
@@
 Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** thousand tones to landings and USD **968** million in revenue to the countries involved in the dispute.
-In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe [@Pinsky:2018cb].
+In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe requiring flexible agreements that accommodate future uncertainties [@Pinsky:2018cb].
 
@@
 Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], many of which are highly migratory pelagic-oceanic species like skipjack tuna (*Katsuwonus pelamis*), Common dolphinfish (*Coryphaena hippurus*), and tunas (*Thunnus sp.*).
-This is the only group whoes EEZ range (e.g.
+Pelagic-oceanic species are the only group whoes EEZ range (e.g.
 the number of EEZs where the species occur as transboundary) significantly differs from the others (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species (Fig.
@@
 
-![**Number of countries shared by transboundary species. Showing only species that share > 20 countries**](./Figures/Fig3.png)
+![Fig. 3. EEZ range of ransboundary species. Showing only species that share > 20 countries](./Figures/Fig3.png)
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, highly migraroty pelagic fish species are cataloged as straddling and many of them globally managed by Regional Fisheries Management Organizations (RFMOs).
-Fifteen major RFMOs in the world oversee the management of 99 species, most of them fished in areas beyond national jurisdiction [@CullisSuzuki:2010fi].
-We estimate that 81.8% of these species are actually shared within neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (**Supplemental figure RFMO_MAP**).
+Due to their large migration patterns and presence in areas beyond national jurisdiction, highly migraroty pelagic fish species are cataloged as straddling and many of them managed by Regional Fisheries Management Organizations (RFMOs).
+Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
+We estimate that 81.8% of these species are actually shared within neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas sharing over 40 species with neighboring RFMOs (**Supplemental figure RFMO_MAP**).
 The effectiveness of RFMOs responsible for managing high migratory stocks has been previously questioned [@CullisSuzuki:2010fi; Lodge:2007bt].
@@
 
-# Materials and Methods
+<!-- # Materials and Methods -->
 
-We determine whether or not a species can be considered transboundary.
+<!-- We determine whether or not a species can be considered transboundary.
 The method is based on a series of criteria to be met and the overlay of species distributions and the spatial boundaries of the world’s EEZs.
@@
 All data was scaled to 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
+-->
 
-## Databases on species geographic distributions
+<!-- ## Databases on species geographic distributions -->
 
-To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we first extracted all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions.
+<!-- To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we first extracted all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions.
 For this, we used four data sources of species-distributions: (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
@@
 The final dataset comprised **XXX** species, **XX**% of the reported marine species in the SAU database and **XX**% of the reported taxa of the FAO (**See S1_Data**).
+-->
 
-### *Occurence data*
+<!-- ### *Occurence data* -->
 
-The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+<!-- The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+-->
 
-### *Distribution models*
+<!-- ### *Distribution models* -->
 
-In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU.
+<!-- In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU.
 Although they use the same data, the models are structurally different complementing each other and providing robustness to the results.
+-->
 
-The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+<!-- The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
 Environmental variables utilized in the models included sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
@@
 See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
+-->
 
-The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
+<!-- The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
 For each commercial fish species, the model first uses the FAO major fishing areas and countries EEZs to determine a broad distribution.
@@
 See [@Close:2006ux; @Palomares:wg] for model details.
+-->
 
-### *Catch data*
+<!-- ### *Catch data* -->
 
-The previous models combine observational data with a series of biotic and abiotic information to determine the probability that a species will be found in a given space at a given time.
+<!-- The previous models combine observational data with a series of biotic and abiotic information to determine the probability that a species will be found in a given space at a given time.
 However, this does not mean that the species in question will actually be there.
@@
 Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten years of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+-->
 
@@
 
-## Determine if a species is transboundary
+<!-- ## Determine if a species is transboundary -->
 
-We developed a four-criteria method for determining whether or not a species was transboundary.
+<!-- We developed a four-criteria method for determining whether or not a species was transboundary.
 Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states.
@@
 All code is available at https://github.com/jepa/FishForVisa.
+-->
 
-### Criteria 1; Neighboring EEZs
+<!-- ### Criteria 1; Neighboring EEZs -->
 
-As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries.
+<!-- As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries.
 Hence, the first criteria was that the species would only be transboundary between two neighboring countries, regardless of the species extended distribution.
@@
 However, the analysis here presented was kept at the species level and stocks within countries were not considered.
+-->
 
-We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
+<!-- We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
 Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf*-*R* package.
@@
 Brazil and Fernando de Noronha).
+-->
 
-### Criteria 2; Data agreement
+<!-- ### Criteria 2; Data agreement -->
 
-We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells.
+<!-- We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells.
 We computed a *Species Index* by dividing the number of datasets that confirm presence of a species in a grid cell over the total amount of datasets (*n* = 3).
@@
 For the analysis, we selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species.
+-->
 
-### Criteria 3; Modeling verification
+<!-- ### Criteria 3; Modeling verification -->
 
-We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
+<!-- We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped, regardless of the *Species Index*.
 The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, thus validating the models.
+-->
 
-### Criteria 4; Spatial distribution
+<!-- ### Criteria 4; Spatial distribution -->
 
-Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*.
+<!-- Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*.
 The *Area Index* consist in the proportion of the total species distribution within both EEZs that each neighboring EEZ has.
@@
 Such threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).
+-->
 
-## Fisheries trends
+<!-- ## Fisheries trends -->
 
-We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
+<!-- We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
 The data includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
@@
 categories, regions, species) regarding transboundary species and their contribution in terms of catch and revenue.
+-->
 

### 2020-01-07 Manuscript_Draft.Rmd
Updated manuscript draft and shared with co-authors

@@
 - **Potential Reviewers (J)**  
- -- Gakushi Ishimura,  
+ -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan  
  -- Kathleen Miller, National Center for Atmospheric Research, Boulder, Colorado, USA  
+ -- Louise S.L. Teh, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada  
  -- Malin Pinsky, Rutgers University, New Brunswick, New Jersey, USA  
- -- Megan Baily, 
+ -- Megan Baily, Integrated Ocean and Coastal Governance, Dalhousie University, Halifax, Canada  
  -- Steven D. Gaines, University of California, Santa Barbara, Santa Barbara, California, USA
@@
 - **Excluded Reviewers (J)**
--- U. Rashid Sumaila, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada  
--- Louise S.L. Teh, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada
 
@@
 
+Is worth mention that for the current study we did not consider climate change as a driver of species' distribution.
+Dsitribution shifts are the most recorded response of marine species to the effects of climate change in the ocean [@Poloczanska:2016kk].
+Moreover, catch composition might have already changed in the last five decades [@Cheung:2013gk], and will most likeley continue throuugh the 21^st century [@Cheung:2016jd].
+While considering climate change in the distribution of shared stocks is beyond the scope of this study, it is likely that it will bring at least one new transboundary species per EEZ in the future [@Pinsky:2018cb], while also change the proportion of the distribution (e.g.
+Area Index) that each county's share to a degree that could influecne fisheries management [@Sumailaetal_in_press].
+Exploring the impacts of climate change in share species is key to develop adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
+
 Our study identifies the current species shared by neighbouring coastal nations and highlights the importance of these species in terms of global capture and revenue from wild fisheries.
@@
 ## Data and materials availability
-*Any restrictions on materials such as MTAs.*
 
-Gabriel, is there any restriction with the data?
+All data is available by request of the authors.
 
-<!-- # Materials and Methods -->
+# Materials and Methods
 
-<!-- We determine whether or not a species can be considered transboundary.
+We determine whether or not a species can be considered transboundary.
 The method is based on a series of criteria to be met and the overlay of species distributions and the spatial boundaries of the world’s EEZs.
-For the current analysis we work at the species level and adopt the Food and consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf].
-All data was scaled to 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).
--->
+For the current analysis we work at the species level and consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf].
+All data was scaled to $0.5^o$ x $0.5^o$ lat-long grid cells (*n* = ~180,000 grid cells).
 
-<!-- ## Databases on species geographic distributions -->
+## Databases on species geographic distributions
 
-<!-- To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we first extracted all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions.
+To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their current distributions.
 For this, we used four data sources of species-distributions: (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
@@
 Only commercial fished species with data from all four sources were included in the analysis.
-The final dataset comprised **XXX** species, **XX**% of the reported marine species in the SAU database and **XX**% of the reported taxa of the FAO (**See S1_Data**).
--->
+The final dataset comprised 968 marine species (including andornomus species like salmons), **XX**% of the reported marine species in the SAU database and **XX**% of the reported taxa of the FAO (**See S1_Species_List**).
 
-<!-- ### *Occurence data* -->
+### *Occurence data*
 
-<!-- The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
--->
+The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
-<!-- ### *Distribution models* -->
+### *Distribution models*
 
-<!-- In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU.
+In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU.
 Although they use the same data, the models are structurally different complementing each other and providing robustness to the results.
--->
 
-<!-- The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
 Environmental variables utilized in the models included sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
@@
 See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
--->
 
-<!-- The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
+The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
 For each commercial fish species, the model first uses the FAO major fishing areas and countries EEZs to determine a broad distribution.
@@
 See [@Close:2006ux; @Palomares:wg] for model details.
--->
 
-<!-- ### *Catch data* -->
+### *Catch data*
 
-<!-- The previous models combine observational data with a series of biotic and abiotic information to determine the probability that a species will be found in a given space at a given time.
+The previous models combine observational data with a series of biotic and abiotic information to determine the probability that a species will be found in a given space at a given time.
 However, this does not mean that the species in question will actually be there.
@@
 Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten years of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
--->
 
@@
 
-<!-- ## Determine if a species is transboundary -->
+## Determine if a species is transboundary
 
-<!-- We developed a four-criteria method for determining whether or not a species was transboundary.
+We developed a four-criteria method for determining whether or not a species was transboundary.
 Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states.
@@
 All code is available at https://github.com/jepa/FishForVisa.
--->
 
-<!-- ### Criteria 1; Neighboring EEZs -->
+### Criteria 1; Neighboring EEZs
 
-<!-- As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries.
+As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries.
 Hence, the first criteria was that the species would only be transboundary between two neighboring countries, regardless of the species extended distribution.
-This way, a species such as Atlantic cod (*Gadus morhua*) distributed along the north Atlantic, was only considered transboundary between each of the neighboring nations covering its distribution, rather than the region as a whole.
-We assume that this would reduce the differences between species and stock as is more likely that neighboring species belong to the same stock, rather than, lets say, Cod in Norway and Canada.
-However, the analysis here presented was kept at the species level and stocks within countries were not considered.
--->
-
-<!-- We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
-Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf*-*R* package.
+We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
+Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *R* package *sf*.
 When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appeared in more than one sub-region.
@@
 Brazil and Fernando de Noronha).
--->
+**Sub-states** like Puerto Rico and Hong Kong were added to their **parent** state.
 
-<!-- ### Criteria 2; Data agreement -->
+### Criteria 2; Data agreement
 
-<!-- We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells.
+We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells.
 We computed a *Species Index* by dividing the number of datasets that confirm presence of a species in a grid cell over the total amount of datasets (*n* = 3).
@@
 For the analysis, we selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species.
--->
 
-<!-- ### Criteria 3; Modeling verification -->
+### Criteria 3; Modeling verification
 
-<!-- We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
+We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped, regardless of the *Species Index*.
 The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, thus validating the models.
--->
 
-<!-- ### Criteria 4; Spatial distribution -->
+### Criteria 4; Spatial distribution
 
-<!-- Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*.
+Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*.
 The *Area Index* consist in the proportion of the total species distribution within both EEZs that each neighboring EEZ has.
@@
 Such threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).
--->
 
-<!-- ## Fisheries trends -->
+## Fisheries trends
 
-<!-- We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
+We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
 The data includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
@@
 categories, regions, species) regarding transboundary species and their contribution in terms of catch and revenue.
--->
 
@@
 
-## Caveats
+## Analysis Assumptions and Caveats
+<!-- # Related to Criteria 1 (Neighbours) -->
+We ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
+However, we limited the distribution to neighbouring countries.
+This way, a species such as Atlantic cod (*Gadus morhua*) distributed along the north Atlantic, was only considered transboundary between each of the neighboring nations, rather than the distribution as a whole.
+We assume that this would reduce the gap between species and stock, as is more likely that neighboring species belong to the same stock, rather than, lets say, Cod in Norway and Canada.
+<!-- Related to Criteria 2 (Models) -->
+The models implemented in this analisis are not free of uncertainty.
+Structural differences within Earth System Models results in variations of oceanic conditions, which undoubtedly permeate to the ENM-Nereus.
+We averaged the results from the three models in an effort to capture the structural variation of the models.
+Climate natural variability is a mayor driver of marine species distribution, potentially removing a species from an EEZ for long periods (e.g.
+Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
+Thus, a species' distribution can potentially be reduced or shifted in such way that it only covers one EEZ until the proper oceanic conditions re-expands its distribution.
+To account for such climate variability, we obtained the ESM-Nereus results as an average of oceanic conditions between 1970 and 2000.
+This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Palomares:wg].
+Moreover, the occurrence data is non-time dependant, meaning that we collected all observational data available, regarding of the date when the species was recorded.
+<!-- Related to Criteria 3 (SAU catch data) -->
+In addition, we assumed that, if the SAU reconstruction data recorded a species caught in any given grid cell, then the species was present in that grid cell.
+However, catch data is not exempt of uncertainty [@].
+Thus, our catch data reference period in any given grid cell was between 2005 and 2014, the last ten years of data.
+<!-- Related to Criteria 4; Spatial distribution -->
+Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g.
+all datasets agree on presence) and at least 25% of *Area Index* (e.g.
+the species shared distribution was at least 25% in each EEZ).
+This presents a relative conservative estimate of the number of transboundary species in the world.
+However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (S3_Area.png).
 
@@
 
-img <- readPNG(here("./Figures/S2_RFMO.png"))
+img <- readPNG(here("./Figures/S3_Area.png"))
 grid.raster(img)
@@
 
-# References (59/about 30)
+# References (37/about 30)
 

### 2020-02-04 Manuscript_Draft.Rmd
Started second round of inner comments

@@
 ---
-title: "Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)"
+title: "Fish do not need visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)"
 author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
@@
 - **Potential Reviewers (J)**  
- -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan  
- -- Kathleen Miller, National Center for Atmospheric Research, Boulder, Colorado, USA  
- -- Louise S.L. Teh, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada  
- -- Malin Pinsky, Rutgers University, New Brunswick, New Jersey, USA  
- -- Megan Baily, Integrated Ocean and Coastal Governance, Dalhousie University, Halifax, Canada  
- -- Steven D. Gaines, University of California, Santa Barbara, Santa Barbara, California, USA
+ -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp
+ -- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu
+ -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn
+ -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no
 
@@
 
-Over 50% of marine fish landings and revenue comes from species shared by neighbouring nations having direct implications to fisheries management.
+Species shared by neighboring nations contribute over 50% of marine capture fisheries' landings and revenue with direct implications for fisheries management.
 
@@
 
-Regulatory boundaries and species distributions are not always aligned, therefore marine species often cross multiple Economic Exclusive Zones (EEZs).
-This represents a challenge for fisheries management as the benefits from a shared resource is often maximized through collaboration.
-In here, we combined species distributions and the spatial delimitation of EEZs to identify the number of exploited marine fish species that are shared between neighbouring nations.
-We found that 64% of the world's capture and 50% or revenue comes from 633 shared species, with some countries receiving over 70% of their benefits from a few shared resources.
-Identifying shared species can play a critical role in the sustainability of wild fisheries suggesting a need for collaborative management strategies.
+Regulatory boundaries and species distributions are often not aligned, especially in the case of  marine species crossing multiple Economic Exclusive Zones (EEZs).
+This represents a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits.
+Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine fish species that are shared between neighbouring nations.
+We found that 64% of the world’s catches in the last decade, amounted to 50% of fisheries revenue, comes from 633 shared species.
+Some countries received over 70% of their benefits from a few shared resources.
+This study highlights the large and under-recognized challenge in achieving international fisheries management goals, particularly as species redistribute under climate change.
 
@@
 
-Distributions of marine species around the world are not restricted by human-made boundaries; rather shaped by contemporary biotic and abiotic factors, as well as their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
+Distributions of marine species around the world are not constrained by human-made boundaries; rather they are shaped by biotic and abiotic factors defined by their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
 Thus, a species can have a broader distribution (cosmopolitan), or be endemic [@Nelson:2016kk].
-However, fisheries management is predicated on the definition of “stocks” that are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
+However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
 The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
-Theories and empirical experience demonstrate fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; @Bailey:2010ga].
-For example, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
-Moreover, climate change is likely to exacerbate these types of conflict [@Pinsky:2018cb] and presents further challenges for fisheries management [@Miller:2013iv].
+Theories and empirical experience have show that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; @Bailey:2010ga].
+For instance, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+Moreover, climate change is likely to exacerbate these types of conflict and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and for fisheries management [@Miller:2013iv].
 

### 2020-02-04 Manuscript_Draft.Rmd
First corrections on comments from co authors

@@
 
-Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear due to data limitations [@Caddy:1997ue], and methodological approaches [@Teh:2015gd].
-In here, we aimed to estimate the number of exploited marine fish species shared by neighbouring countries and determine their contribution to global catch and fisheries revenue.
+Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear.
+**Early data limitations allowed only for an informed guessed [@Caddy:1997ue], while recent estimations, followed a litterature review and catch data to address this issue [@Teh:2015gd].
+However, up to date, no method has included the actual distribution of species.
+We hipothesize that the methodological constraints of preious work has underestimate the contribution of these species to global catch and revenue and that the proportoin of transboundary species is larger than previouslly estimated.** Thus, we aimed to estimate the number of exploited marine fish species shared by neighbouring countries and determine their contribution to global catch and fisheries revenue.
+**Moreover, we estimate their importance in terms of catch and revenue by country and also carry the analysis at the ecological level.**
 
-We overlay the known distribution of **968** commercially valuable marine species and the EEZ of 153 coastal countries and developed a four-criteria methodology to determine if a species was transboundary.
-The first criteria consisted in only considering shared species between neighboring EEZs, rather than the specie's extended distribution.
-For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
-The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data.
-A species was kept in a grid cell if both predicted species occurrences and catch data were positive.
-Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
-Once transboundary species were identified, we estimated their contribution to fishing landings and revenues and categorized them according to catch trends.
-We carry out the analysis at the species per EEZ level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@Teh:2015gd].
-Despite loosing detail-specific (e.g.
-a species could have multiple stocks within an EEZ), many fisheries within a country or EEZ are managed at the species level, and recent research has suggested strong connectivity between stocks thousand of kilometers away [@Ramesh:2019va].
+We overlaid the known distribution of **968** commercially valuable marine species responsable for **%%** of global catch, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
+First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.
+we did not include the high seas).
+Secondly, we considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
+The third criteria determined whether a species was exploited within a given grid cell using spatially explicit catch data.
+A species was considered as present in a grid cell if both predicted species occurrences and catch data were positive.
+Finally, we determined a spatial threshold based on the proportion of the species' distribution within each neighboring EEZs to confirm occurance in both EEZs.
+
+Once transboundary species were identified, we estimated their contribution to fisheries catch and revenues and categorized them according to catch trends.
+We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
+Also, recent research has suggested strong connectivity between stocks, even when separated by thousand of kilometers, **and providing additional ecological ground for...** [@Ramesh:2019va].
 
@@
 
-We identified **633** transboundary exploited species in the world, more than double the number previously estimated [@Teh:2015gd], accounting for **65.4%** of the species analyzed (Fig.
+We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed (Fig.
 1A).
-Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **64%** of the EEZ-global catch, and generating USD **79,745** million in fishing revenue.
-This is equivalent to **49.8%** of the global revenue of the same period.
-These values are higher than previously estimated [@Teh:2015gd], reinforcing the importance of these species at the global level.
+Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **64%** of the EEZ-derrived catches, and generating USD **79,745** million in fishing revenue.
+This is equivalent to **49.8%** of the global fishing revenue of the same period.
+These values are more than double the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd], underscoring the importance of transboundary species at the global level.
 
@@
 1.
-Number of transboundary species and they contribution to fishing catch and revenue.
-A) The number of species and revenue are represented in the EEZ and land polygon, respectively.
+Number of transboundary marine species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by colour coding of EEZs and land polygons, respectively.
 B) Contribution of tranbsoundary species to regional revenue (left) and catch (right).
-Points = mean +- sd.](./Figures/Fig1.png)
+Points = mean +- sd.
+Revenue in 2010 real USD](./Figures/Fig1.png)
 
-Transboundary species are particularly important for Northern America (mean = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (mean = 2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
-The large variation in revenue from these regions are driven by China (USD 6,279 million) in E.
+**NOTE: EXPLORE THE REGIONAL SEGMENTATION YOU MADE**
+
+Transboundary species are particularly important economically for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+China (USD 6,279 million) in E.
 Asia and the US (USD 9,605 million) in N.
-America who contribute 55% and 83% to the region's revenue, respectively.
-Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with more revenue from transboundary species.
-These five nations are responsible for 30% of the global revenue from transboundary species.
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead the production of transboundary species harvesting over 5,000 thousand tones (**Supplemental figure Trans_Catch_MAP**).
-Peru's catches come mainly from Peruvian anchoveta (*Engraulis ringens*), shared with Chile, accounting for 79% of the transboundary species production.
+America contribute 55% and 83% to their respective region's revenue, respectively.
+Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with the most fishing revenue generated from transboundary species.
+These five nations are responsible for 30% of the fishing global revenue from transboundary species.
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5,000 thousand tones each on average between 2005 and 2014 (**Supplemental figure Trans_Catch_MAP**).
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and accounting for 79% of the transboundary species production.
 Similarly, Russia shares the Alaskan polllock (*Theragra chalcogramma*) fishery with both Japan and the US.
-Despite this, catches are only significantly different in E.
+Despite the large catch volume of Peru and Russia, regional catches are only significantly different in E.
 Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
+**NOTE: MAKE SURE RUSSIA IS NOT E.ASIA**
 
-Harvest rates and fisheries management are key to achieve the sustainable development goals [@SDGs].
-We found significant differences in the exploitation rate of transboundary species (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished at levels below 50%, sometimes lower than 10%, of their historical maximum peak (Fig.2).
-This is the case of coastal nations in all continents, but Oceania, with no significant difference between continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05).
-While these catch trends do not directly reflect stock status - e.g.
-other factors like markets, fishing policies or extreme events also influence catch volume [@Pauly:2013gs; @Branch:2008kk] - they could resemble fisheries that are over exploited or collapsed [@Kleisner:2011wn].
+We determined the exploitation category of transboundary fisheries according to each country's catch [@Kleisner:2011wn] and also found significant differences among exploitation categories (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished to levels below 50%, sometimes lower than 10%, of their historical maximum catch (Fig.2).
+All regions conformed to this trend, except for Oceania, with no significant difference across continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05).
+While many environmental and social-economic factors such as temperature, markets, fishing policies affect catch volume [@Pauly:2013gs; @Branch:2008kk] previous studies demonstrated that the trends can be used to infer whether a stock is over-exploited or collapsed [@Kleisner:2011wn].
 Thus suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
-Corroborating the status of species harvested at this rate (Category C) and considering best practices in managing shared resources [@Munro:2004ug; @Lodge:2007bt] could provide crucial to the sustainability of transboundary species.
 
-```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category, country, and continent.
-Category A, fishing between 10%-50% of max catch peak after a drop larger than 10% of max peak; Category B, fishing over 50% of max catch peak; Category C, fishing is between 10-50% of max catch peak or less than 10%"}
+**NOTE: THIS (L 118) PARAGRPAH NEEDS WORK**
+
+```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch"}
 
@@
 Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of max catch peak after a drop larger than 10% of max peak; Category B, fishing over 50% of max catch peak; Category C, fishing less than 50% of max peak](./Figures/Fig2.png)
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig2.png)
 
-Empirical analysis suggest that in most cases, management of transboundary species will have better outcomes in terms of fish yield when nations cooperate [@Bailey:2010ga].
-Examples vary between regions and species including Mexico and the United States over Pacific anchovies [@CisnerosMontemayor:2020kv], Norway and Russia over Atlantic cod (*Gadus morhua*) [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], although cooperation and non-cooperation can be a more complex process [@Jensen:2015cf].
-Collaboration can also reduce conflict between nations over shared resources.
-Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts like Canada, the US, China and Russia [@Spijkers:2019cz].
-For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations to compensate losses [@Munro:2002uf].
-Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** thousand tones to landings and USD **968** million in revenue to the countries involved in the dispute.
-In addition to past and present conflicts, climate change could exacerbate conflicts over transboundary species as climate change shifts the distribution of marine species around the globe requiring flexible agreements that accommodate future uncertainties [@Pinsky:2018cb].
+Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Bailey:2010ga].
+Examples of successful co-management include Canada and the United States over Pacific salmon [@REF] and Pacific halibut [@REF], Norway and Russia over Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and capelin (*Mallotus villosus*) in the Barents Sea [@Diekert:2010gp; @Eide:2013dha **NOTE: DOUBLE CHECK REFERENCES]**, and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], and reduce the future profitability potential of the fishery [@Merino:2007jz].
+Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf] and that there are specific cases where cooperation might not be the best strategy [@REF].
+Collaboration can also reduce conflict between nations over shared resources **as climate change shifts the distribution of species**.
+Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the US, China and Russia [@Spijkers:2019cz].
+For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations were introduced to compensate for losses [@Munro:2002uf].
+Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** (**NOTE: %%**) thousand tonnes to catches and USD **968** (**NOTE: %%**) million in revenue to the countries involved in the dispute.
+In addition to past and present conflicts, climate change is likely to exacerbate conflicts over transboundary species due to shifts in their distribution, requiring flexible agreements that accommodate future uncertainties [@Pinsky:2018cb].
 
@@
 
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], many of which are highly migratory pelagic-oceanic species like skipjack tuna (*Katsuwonus pelamis*), Common dolphinfish (*Coryphaena hippurus*), and tunas (*Thunnus sp.*).
-Pelagic-oceanic species are the only group whoes EEZ range (e.g.
-the number of EEZs where the species occur as transboundary) significantly differs from the others (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species (Fig.
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], many of which are highly migratory pelagic-oceanic species like skipjack tuna (*Katsuwonus pelamis*), other tunas (*Thunnus sp.*), sword fish (*Xiphias gladius*), and common dolphinfish (*Coryphaena hippurus*).
+Pelagic-oceanic species are the only group whose EEZ range (i.e., the number of EEZs where the species occur as 'transboundary') was significantly different from other species (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species (Fig.
 3).
@@
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, highly migraroty pelagic fish species are cataloged as straddling and many of them managed by Regional Fisheries Management Organizations (RFMOs).
+Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migraroty pelagic fish species are managed by Regional Fisheries Management Organizations (RFMOs).
 Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
-We estimate that 81.8% of these species are actually shared within neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas sharing over 40 species with neighboring RFMOs (**Supplemental figure RFMO_MAP**).
-The effectiveness of RFMOs responsible for managing high migratory stocks has been previously questioned [@CullisSuzuki:2010fi; Lodge:2007bt].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested ($B/B_{MSY} > 1$ and $F/F_{MSY} < 1$) with only three stocks currently overfished [@Pons:2016ep].
-Within national waters, we estimated that the catch of transboundary pelagic-oceanic species comes mainly from five Island Nations in the South Pacific from which three (Kiribalti, Solomon and Papua New Guinea) are members of the Pacific Nauru Agreement (Fig 3B).
-The parties to the Nauru Agreement sustainably manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
+We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (**Supplemental figure RFMO_MAP**).
+The effectiveness of RFMOs responsible for managing high migratory stocks has been previously questioned [@CullisSuzuki:2010fi; @Lodge:2007bt].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested ($B/B_{MSY} > 1$ and $F/F_{MSY} < 1$) with only three stocks currently considered as overfished ($B/B_{MSY} < 1$ and $F/F_{MSY} > 1$) [@Pons:2016ep].
+Within national waters, we estimated that the catch of transboundary pelagic-oceanic species mainly originates from five large ocean states in the South Pacific, three of which (Kiribati, Solomon Islands and Papua New Guinea) are parties to the Pacific Nauru Agreement (Fig 3B).
+Parties to the Nauru Agreement sustainably manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
+
+**NOTE: Colette will search for a reference related a weird comment "arecenWCPF assessment highlight tt tuna in the Pacific e sustsinabl fisd, but oher species  socks in ot regionsre .
+I will dig up e reference and send it to you - just to make sure  the irmati overlaps"**
 
@@
 
-Is worth mention that for the current study we did not consider climate change as a driver of species' distribution.
-Dsitribution shifts are the most recorded response of marine species to the effects of climate change in the ocean [@Poloczanska:2016kk].
-Moreover, catch composition might have already changed in the last five decades [@Cheung:2013gk], and will most likeley continue throuugh the 21^st century [@Cheung:2016jd].
-While considering climate change in the distribution of shared stocks is beyond the scope of this study, it is likely that it will bring at least one new transboundary species per EEZ in the future [@Pinsky:2018cb], while also change the proportion of the distribution (e.g.
-Area Index) that each county's share to a degree that could influecne fisheries management [@Sumailaetal_in_press].
-Exploring the impacts of climate change in share species is key to develop adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
+In our analyses we did not seek to include climate change as a driver of species’ distribution.
+Distribution shifts are the most commonly recorded response of marine species to the effects of climate change - chiefly warming - in the ocean [@Poloczanska:2016kk].
+Catch composition might have already changed in the last five decades [@Cheung:2013gk], and will continue throuugh the $21^{st}$ century [@Cheung:2016jd].
+Previous study projected that climate change will bring at least one new transboundary species per EEZ in the future [@Pinsky:2018cb], while also change the proportion of the distribution (e.g.
+Area Index) that each county’s share to a degree that could influence fisheries management (*Palacios-Abrantes et.al.
+under review*).
+Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
 
-Our study identifies the current species shared by neighbouring coastal nations and highlights the importance of these species in terms of global capture and revenue from wild fisheries.
+Our study identified species currently shared by neighbouring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
 Our results show that captures and revenues from shared species are higher than previously estimated and particularly important to countries in Northern America and Eastern Asia.
@@
 
-All data is available by request of the authors.
+All data is available from the authors upon request.
 
@@
 
-We determine whether or not a species can be considered transboundary.
-The method is based on a series of criteria to be met and the overlay of species distributions and the spatial boundaries of the world’s EEZs.
-For the current analysis we work at the species level and consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf].
-All data was scaled to $0.5^o$ x $0.5^o$ lat-long grid cells (*n* = ~180,000 grid cells).
+To ascertain whether or not a species can be considered transboundary, we developed a method based on a series of criteria and the overlay of species' distributions and the spatial boundaries of the world’s EEZs.
+All analyses were conducted at the species level and we consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf].
+All data was scaled to $0.5^o$ x $0.5^o$ lat-long grid cells.
 
-## Databases on species geographic distributions
+## Databases of species' geographic distribution
 
-To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their current distributions.
-For this, we used four data sources of species-distributions: (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
-Each source represent a different method of estimating the distribution of a given species and thus, provides a more robust result.
-Only commercial fished species with data from all four sources were included in the analysis.
-The final dataset comprised 968 marine species (including andornomus species like salmons), **XX**% of the reported marine species in the SAU database and **XX**% of the reported taxa of the FAO (**See S1_Species_List**).
+To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their distributions.
+To this end, we used four data sources of species-distributions: (*i*) occurence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
+Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result.
+Only commercial fished species with data from all four sources were included in the analysis **NOTE: WC "Need to discuss how this affect the samples of transboundary species."**.
+The final dataset comprised 968 marine species (including anadromous species like salmononids), **XX%** of the total number of reported marine species in the SAU database and **XX%** of the reported marine taxa of included by the Food and Agricultural Organization of the United Nations (FAO).
+
+<!-- **NOTE: for transboundary lobsters https://books.google.com.ar/books?id=XEElAwNrKZsC&pg=PA224&lpg=PA224&dq=belize+mexico+lobster+shared+stock&source=bl&ots=lsmUH743d_&sig=ACfU3U1P1t7_L8q_YRh3oQGszUO8Lg1jFw&hl=en&sa=X&ved=2ahUKEwiv36qbwbjnAhX3HrkGHYIbCTgQ6AEwFHoECA0QAQ#v=onepage&q=belize%20mexico%20lobster%20shared%20stock&f=false** -->
 
@@
 
-The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+Occurrence data was collected from five publicly available repositories: Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
@@
 
-In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU.
-Although they use the same data, the models are structurally different complementing each other and providing robustness to the results.
+In addition to occurrence data, we used two different methods to estimate species distributions, hereafter referred to as Ecological Niche Model-Nereus (ENM-Nereus) and Species Distribution Model-SAU (SDM-SAU).
+Although they use the same occurrence and environmental data, the models are structurally different complementing each other and providing robustness to the results.
 
-The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
-Environmental variables utilized in the models included sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
+The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Boosted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
 The ENM-Nereus employed all of the observational data-sources previously mentioned.
-Global environmental conditions were obtained from 1970 to 2000 and average from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+Global environmental conditions were average for the period 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
 See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
 
-The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg].
-For each commercial fish species, the model first uses the FAO major fishing areas and countries EEZs to determine a broad distribution.
-It then uses life history information to delimit its range within the FAO fishing area (e.g.
-thermal preference, depth limits).
+The SDM-SAU model follows a five-steps process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Palomares:wg].
+For each commercial species, the model first uses the FAO major fishing areas and countries' EEZs to determine a broad distribution.
+It then uses life history information to delimit its range within the FAO fishing area (e.g., thermal preference, depth limit).
 The range is delimited even further by expert-review polygons and compared with that of AquaMaps [@Kaschner:2016tl], OBIS and GBIF occurrence data.
-The model then determines a species habitat preference based on the assumptions that the relative abundance of a species is determined by the number of habitats in a grid cell and the distance of the species to each habitat, as well as the importance of the habitat to the species size.
+The model then determines a species habitat preference based on the assumption that the relative abundance of a species is determined by the number of habitats in a grid cell and the distance of the species to each habitat, as well as the importance of the habitat to the species size.
 Finally, the species equatorial submergence (e.g.
@@
 However, this does not mean that the species in question will actually be there.
-While the models do use approaches to double-check species occurrences (e.g.
-ENM-Nereus uses four different species distribution algorithms and SPD-SAU undertakes validation by means of other models), we used a fourth data source to corroborate the models’ outputs.
-The *Sea Around Us* estimates total reconstructed catches - i.e., catches  based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in the FAO data available for each country.
+While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SPD-SAU undertakes validation by means of other models), we used a fourth data source to corroborate the models’ outputs.
+The Sea Around Us estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
 Catches are also spatially allocated [@Zeller2016].
-Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 (last ten years of data) as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+**We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries and to reduce the uncertanty embeded in the recosntruction process (See Key uncertanties).**
 
@@
 
-## Determine if a species is transboundary
+## Determining transboundary species trait
 
-We developed a four-criteria method for determining whether or not a species was transboundary.
-Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states.
-In some cases, criteria also work as indexes to measure the uncertainty in the analysis as they provided continuous index (e.g.
-from 0 to 1) rather than a discrete, yes or no, index .
-All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*[@Packagedatatable:2019uh], *janitor*[@PackagejanitorSim:2018ur], *wesanderson*[@Packagewesanderson:2018vn], *rfishbase*[@PackagerfishbaseR:2019th], *R.matlab*[@PackageRmatlabRe:2018un], *sf*[@PackagesfSimpleF:2018vp], *sp*[@PackagespClasses:2019tn], *tidiverse*[@PackagetidyverseE:2017vq], *tidytext*[@PackagetidytextTe:2019vk], and *zoo*[@PackagezooSInfr:2019tm].
+We developed a four-criteria methodology to determine whether or not a species can be considered transboundary.
+Only species that meet all criteria were considered as transboundary and the analysis was undertaken only within the EEZs of coastal states.
+In some cases, criteria can also be interpreted as indices to measure the uncertainty in the analysis as they provide a continuous index (e.g.
+from 0 to 1) rather than a discrete, yes or no, index.
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*[@Packagedatatable:2019uh], *janitor*[@PackagejanitorSim:2018ur], *wesanderson*[@Packagewesanderson:2018vn], *rfishbase*[@PackagerfishbaseR:2019th], *R.matlab*[@PackageRmatlabRe:2018un], *sf*[@PackagesfSimpleF:2018vp], *sp*[@PackagespClasses:2019tn], *tidiverse*[@PackagetidyverseE:2017vq], *tidytext*[@PackagetidytextTe:2019vk], and *zoo*[@PackagezooSInfr:2019tm].
 All code is available at https://github.com/jepa/FishForVisa.
@@
 
-As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries.
-Hence, the first criteria was that the species would only be transboundary between two neighboring countries, regardless of the species extended distribution.
-We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g.
-Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *R* package *sf*.
-When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appeared in more than one sub-region.
-Species that were present in EEZs that were non-continental territories neighboring other countries were kept (e.g.
-Argentina and Falkland Islands), but removed when the non-continental territory belonged to the same nation (e.g.
-Brazil and Fernando de Noronha).
-**Sub-states** like Puerto Rico and Hong Kong were added to their **parent** state.
+As previously mentioned, we define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
+Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
+We defined EEZ boundaries using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), noting that it subdivides EEZs by regions (e.g., Mexico Pacific and Mexico Atlantic), and determined the intersections between polygons using the R package sf.
+When estimating transboundary species, we filtered out those shared by EEZs sub-regions, and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
+Species that were present in EEZs that were non-continental territories neighboring other countries were kept separately (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
+Associated states like Puerto Rico and Hong Kong were added to their associated Sovereign (e.g.
+Puerto Rico with the United States and Hong Kong with China).
 
@@
 
-We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells.
-We computed a *Species Index* by dividing the number of datasets that confirm presence of a species in a grid cell over the total amount of datasets (*n* = 3).
-The index is unit-less and represents a scale from 0.3 to 1 where 0.3 means only one dataset reports presence of the species in a grid cell, 0.6 represents two of three sources, and 1 means agreement between all datasets.
-For the analysis, we selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species.
+We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells.
+We computed a *Species Index* by dividing the number of datasets that confirmed the presence of a species in a grid cell over the total number of datasets (n = 3).
+The index is unit-less and represents a scale from 0.3 to 1, with 0.3 indicating that only one dataset reported the presence of the species in a grid cell, 0.6 two out of three sources, and 1 pointing to agreement across all 3 datasets.
+All analyses only considered cases where *Species Index* = 1 to obtain a more conservative estimate of transboundary species.
 
@@
 
-We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database.
+We assumed that a species was only present in a given grid-cell if it was reported in the Sea Around Us catch database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped, regardless of the *Species Index*.
-The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, thus validating the models.
+This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over a period of time (here 2005 - 2014), thus validating the models.
+See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.
 
@@
 
-Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*.
-The *Area Index* consist in the proportion of the total species distribution within both EEZs that each neighboring EEZ has.
-We determine that a species would be transboundary if both neighboring EEZs enclosed over 25% of the species joint distribution.
-Such threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).
+Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*.
+The *Area Index* consist in the proportion of a given species' overarching shared distribution between neighbouring EEZs accounted for by each individual EEZ.
+We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
+This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).
 
@@
 
-We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017].
-The data includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
+We estimated the economic contribution in 2010 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
+The database we draw from includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
 similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-The contribution of transboundary species was done by aggregating the catch of each species that happened within the EEZ of the countries sharing that species.
+The contribution of transboundary species was derived by aggregating the catch of species occurring within the EEZs of countries sharing that species.
 For this study, we did not include catch nor revenue from areas beyond national jurisdiction.
-Finally, we use the catch data to determine the exploitation category of each species within a EEZ.
-Although this method has previously used to estimate stock status [@Grainger:1996tk], the categories presented here are intended to be seen as catch trends, and not status of each species.
-We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years.
-Three categories were drawn from a method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**) [@Kleisner:2011wn].
+Finally, we used the catch data to determine the exploitation category of each species within a EEZ.
+Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not status for each species.
+We only assessed species within each EEZ for which at least ten years of data were available between the first and last reported catch and with at least five consecutive years of data.
+Three final categories were drawn for each species depending on the catch volume within each EEZ (e.g.
+present, maximum and minimum EEZ's historical catch) and the year (e.g.
+year of maximum historical catch of the species within that EEZ) (**Table XX**) [@Kleisner:2011wn].
 Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
-We perform a series of one-way analysis of variance ( one-way ANOVA) to determine significant differences (statistically) between the means of different groups (e.g.
-categories, regions, species) regarding transboundary species and their contribution in terms of catch and revenue.
+We performed a series of one-way analysis of variance (one-way ANOVA) to determine statistically significant differences between the means of different groups (e.g., regions, species, exploitation category) of transboundary species and their contribution to catch and fishing revenue.
 
@@
 
-## Analysis Assumptions and Caveats
+## Key uncertainties
 <!-- # Related to Criteria 1 (Neighbours) -->
-We ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
-However, we limited the distribution to neighbouring countries.
-This way, a species such as Atlantic cod (*Gadus morhua*) distributed along the north Atlantic, was only considered transboundary between each of the neighboring nations, rather than the distribution as a whole.
-We assume that this would reduce the gap between species and stock, as is more likely that neighboring species belong to the same stock, rather than, lets say, Cod in Norway and Canada.
+We have identified four key uncertainties in the method that may affect the estimation of transboundary stocks.
+Firstly, we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
+However, we defined transboundary only between  neighbouring countries (e.g.
+US and Canada) and did not include countries that were separated by another country (e.g.
+Canada and Mexico) and/or the high seas (e.g.
+Canada and Spain).
 <!-- Related to Criteria 2 (Models) -->
-The models implemented in this analisis are not free of uncertainty.
-Structural differences within Earth System Models results in variations of oceanic conditions, which undoubtedly permeate to the ENM-Nereus.
-We averaged the results from the three models in an effort to capture the structural variation of the models.
-Climate natural variability is a mayor driver of marine species distribution, potentially removing a species from an EEZ for long periods (e.g.
+Secondly, the predicted species distribution is affected by the uncertainties of the environmental data and models used for such predictions.
+Structural differences within Earth System Models results in variations of oceanic conditions, which undoubtedly affect the ENM-Nereus.
+We averaged the results from the three models in an effort to capture the structural variation across models.
+Climate natural variability is a major driver of marine species distribution, potentially removing a species from an EEZ for long periods (e.g.
 Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
-Thus, a species' distribution can potentially be reduced or shifted in such way that it only covers one EEZ until the proper oceanic conditions re-expands its distribution.
-To account for such climate variability, we obtained the ESM-Nereus results as an average of oceanic conditions between 1970 and 2000.
+Thus, a species’ distribution can potentially be reduced or shifted in such way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
+To account for such climate variability, we derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
 This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Palomares:wg].
-Moreover, the occurrence data is non-time dependant, meaning that we collected all observational data available, regarding of the date when the species was recorded.
 <!-- Related to Criteria 3 (SAU catch data) -->
-In addition, we assumed that, if the SAU reconstruction data recorded a species caught in any given grid cell, then the species was present in that grid cell.
-However, catch data is not exempt of uncertainty [@].
-Thus, our catch data reference period in any given grid cell was between 2005 and 2014, the last ten years of data.
+Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+While catch data is not exempt of uncertainty, in most cases, the differences between the Sea Around Us and the FAO self-reported data is smaller towards recent years [@Pauly:2019bf].
+Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
+Likewise, the spatial allocation of the catch is subjected to imprecisions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
+However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and @Zeller2016 for mode details in the spatial allocation of the SAU).
 <!-- Related to Criteria 4; Spatial distribution -->
@@
 This presents a relative conservative estimate of the number of transboundary species in the world.
-However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (S3_Area.png).
+However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (**S3_Area.png**).
 
@@
 
-![**Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
-The number of species is represented in the EEZ while the catch (thousand tonnes) is represented in the land polygon.
-**](./Figures/S1_Catch_EEZ.png)
+![**Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.**](./Figures/S1_Catch_EEZ.png)
 
@@
 
-![**Number of shared species by RFMOs. Analysis included with 99 species managed by Fourteen RFMOs **](./Figures/S2_RFMO.png)
+![**Number of shared species across RFMOs. Analysis included with 99 species managed by Fourteen RFMOs **](./Figures/S2_RFMO.png)
 
-It is expected that the number of gridcells where a species is present (*Area Index*) would directly influence whether or not a species is considered transboundary.
+The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
 Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (*S3 Index Area*).
 As expected, using a more relaxed value (e.g.
-the species is present within 10% or more of the EEZ) will result in more transboundary species giving a median of 40 EEZs shared per species, while a more strict value (e.g.
-50%) will give a median of 4.
-For the current analysis we presented the results using a 25% *Area Index* threshold (*S3 Index Area* - darker histogram).
+the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
+The current analysis utilised a 25% *Area Index* threshold (*S3 Index Area* - darker histogram).
 
@@
 
-![**Histogram of transboundary species using different values of Area Index. Darker histogram represents used value (25%) in the analysis**](./Figures/S3_Area.png)
+![**Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis**](./Figures/S3_Area.png)
 

### 2020-02-07 Manuscript_Draft.Rmd
Manuscript comments

@@
 date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
-# subtitle: "DRAFT DO NOT SHARE"
+# subtitle: "[DRAFT DO NOT SHARE]"
 subtitle: "Most neighbour nations share marine species (38/40 characters)"
@@
 
-# Instructions for submission
+<!-- # Instructions for submission -->
 
-- Journal: *Science*
+<!-- - Journal: *Science* -->
 <!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
@@
 
--- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance.
+<!-- -- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance.
 Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.
+-->
 
@@
 
-# Reviewers (5):
-*Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*
+<!-- # Reviewers (5): -->
+<!-- *Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*   -->
 
-**Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions)
+<!-- **Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions) -->
 
-- **Potential Reviewers (J)**  
- -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp
- -- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu
- -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn
- -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no
+<!-- - **Potential Reviewers (J)**   -->
+<!--  -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp -->
+<!--  -- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu -->
+<!--  -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn -->
+<!--  -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no -->
 
-- **Excluded Reviewers (J)**
+<!-- - **Excluded Reviewers (J)**   -->
 
 # One Sentence Summary (125/~125 characters)
-*A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
-This will appear online adjacent to the title and should not repeat phrases already present there*
+<!-- *A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
+This will appear online adjacent to the title and should not repeat phrases already present there* -->
 
@@
 # Abstract (125/~125 words)
-*An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
-It should be a single paragraph.*
+<!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
+It should be a single paragraph.* -->
 
@@
 Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear.
-**Early data limitations allowed only for an informed guessed [@Caddy:1997ue], while recent estimations, followed a litterature review and catch data to address this issue [@Teh:2015gd].
+Early data limitations allowed only for an informed guessed [@Caddy:1997ue], while recent estimations, followed a litterature review and catch data to address this issue [@Teh:2015gd].
 However, up to date, no method has included the actual distribution of species.
-We hipothesize that the methodological constraints of preious work has underestimate the contribution of these species to global catch and revenue and that the proportoin of transboundary species is larger than previouslly estimated.** Thus, we aimed to estimate the number of exploited marine fish species shared by neighbouring countries and determine their contribution to global catch and fisheries revenue.
-**Moreover, we estimate their importance in terms of catch and revenue by country and also carry the analysis at the ecological level.**
+We hipothesize that the methodological constraints of preious work has underestimate the contribution of these species to global catch and revenue and that the proportoin of transboundary species is larger than previouslly estimated.
+Thus, we aimed to estimate the number of exploited marine fish species shared by neighbouring countries and determine their contribution to global catch and fisheries revenue.*Moreover, we estimate their importance in terms of catch and revenue by country and also carry the analysis at the ecological level.
 
-We overlaid the known distribution of **968** commercially valuable marine species responsable for **%%** of global catch, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
+We overlaid the known distribution of 968 commercially valuable marine species responsable for **XX%** of global catch, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
 First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.
@@
 While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research has suggested strong connectivity between stocks, even when separated by thousand of kilometers, **and providing additional ecological ground for...** [@Ramesh:2019va].
+Also, recent research has suggested strong connectivity between stocks, even when separated by thousand of kilometers [@Ramesh:2019va].
+<!-- **and providing additional ecological ground for...** -->
 
@@
 
-We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed (Fig.
+We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed.
+Transboundary species are partiuclarly abundant in EEZs of western Europe, northwestern Africa, and southeastern Asia (Fig.
 1A).
+Species' composition in these areas is relativly homogenous due to biogeochemical, oceanographic and topography features [@Spalding:2007th; @Reygondeau:2013cd].
+For example north west Africa and and west Europe are part of the Lusitanian large marine ecoregion (LME), similarly the Northern European Seas LME and south east China is part of the Western Coral Triangle LME [@Spalding].
 Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **64%** of the EEZ-derrived catches, and generating USD **79,745** million in fishing revenue.
@@
 
-**NOTE: EXPLORE THE REGIONAL SEGMENTATION YOU MADE**
+<!-- **NOTE: EXPLORE THE REGIONAL SEGMENTATION YOU MADE** -->
 
@@
 Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
-**NOTE: MAKE SURE RUSSIA IS NOT E.ASIA**
+
+<!-- **NOTE: MAKE SURE RUSSIA IS NOT E.ASIA** -->
+
+<!-- However, some regions like the Caribbean stand out as they have multiple small EEZs and belonging to a single LME (in this case Tropical Northwestern Atlantic), yet their number of transboundary species is lower than the preiouslly mentioned regions.
+This is likeley an effect of the reporting -->
 
@@
 
-**NOTE: THIS (L 118) PARAGRPAH NEEDS WORK**
+<!-- **NOTE: THIS (L 118) PARAGRPAH NEEDS WORK** -->
 
@@
 Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Bailey:2010ga].
-Examples of successful co-management include Canada and the United States over Pacific salmon [@REF] and Pacific halibut [@REF], Norway and Russia over Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and capelin (*Mallotus villosus*) in the Barents Sea [@Diekert:2010gp; @Eide:2013dha **NOTE: DOUBLE CHECK REFERENCES]**, and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Examples of successful co-management include Canada and the United States over Pacific salmon [@REF] and Pacific halibut [@REF], Norway and Russia over Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and capelin (*Mallotus villosus*) in the Barents Sea [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
 Lack of collaboration over shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], and reduce the future profitability potential of the fishery [@Merino:2007jz].
 Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf] and that there are specific cases where cooperation might not be the best strategy [@REF].
-Collaboration can also reduce conflict between nations over shared resources **as climate change shifts the distribution of species**.
+Collaboration can also reduce conflict between nations over shared resources as climate change shifts the distribution of species.
 Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the US, China and Russia [@Spijkers:2019cz].
 For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations were introduced to compensate for losses [@Munro:2002uf].
-Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes **698.3** (**NOTE: %%**) thousand tonnes to catches and USD **968** (**NOTE: %%**) million in revenue to the countries involved in the dispute.
+Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes 698.3 thousand tonnes to catches and USD 968 million in revenue to the countries involved in the dispute.
 In addition to past and present conflicts, climate change is likely to exacerbate conflicts over transboundary species due to shifts in their distribution, requiring flexible agreements that accommodate future uncertainties [@Pinsky:2018cb].
+
+<!-- **NOTE: DOUBLE CHECK REFERENCES eddie and derek]** -->
+<!-- **NOTE: add %% to mackrel** -->
 
@@
 
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], many of which are highly migratory pelagic-oceanic species like skipjack tuna (*Katsuwonus pelamis*), other tunas (*Thunnus sp.*), sword fish (*Xiphias gladius*), and common dolphinfish (*Coryphaena hippurus*).
-Pelagic-oceanic species are the only group whose EEZ range (i.e., the number of EEZs where the species occur as 'transboundary') was significantly different from other species (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species (Fig.
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species lke greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as 'transboundary') was significantly different from other groups (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
 3).
@@
 However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested ($B/B_{MSY} > 1$ and $F/F_{MSY} < 1$) with only three stocks currently considered as overfished ($B/B_{MSY} < 1$ and $F/F_{MSY} > 1$) [@Pons:2016ep].
-Within national waters, we estimated that the catch of transboundary pelagic-oceanic species mainly originates from five large ocean states in the South Pacific, three of which (Kiribati, Solomon Islands and Papua New Guinea) are parties to the Pacific Nauru Agreement (Fig 3B).
-Parties to the Nauru Agreement sustainably manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
+In the other hand, less mobile species are often managed at the national level due to localized populations, however, the potential boundary-crossing of these species must not be ignored [@Payne:2008vm].
+The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Levin:2018in; @Payne:2008vm].
 
-**NOTE: Colette will search for a reference related a weird comment "arecenWCPF assessment highlight tt tuna in the Pacific e sustsinabl fisd, but oher species  socks in ot regionsre .
-I will dig up e reference and send it to you - just to make sure  the irmati overlaps"**
+Many coastal communities, particularly in developing regions, are highly dependent on subsistance fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf; @Cabral:2018hc].
+For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
+3B) are among the highest fish consuption countries (> 10 g of fish protein per capita per day) [@FAO].
+In these countries, both pelagic and reeef fishes contribute substantially to both local food security and livelehood [@Cabral:2018hc].
+In the case of Kiribati, the Solomon Islands and Papua New Guinea, they are parties to the Pacific Nauru Agreement that sustainably manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
+
+<!-- **NOTE: Colette will search for a reference related a weird comment "arecenWCPF assessment highlight tt tuna in the Pacific e sustsinabl fisd, but oher species  socks in ot regionsre .
+I will dig up e reference and send it to you - just to make sure  the irmati overlaps"** -->
 
 <!-- [@https://www.ffa.int/nauru_agreement]  -->
-
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (e.g.
-*Solea solea*, *Panulirus argus*) (Fig.
-3).
-However, less distributed species must not be ignored.
-The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-Moreover, many coastal communities, specially in developing regions, and highly dependent on subsistance fishing (e.g.
-reef fish) for food security and livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf; @Cabral:2018hc].
-For example, from the top five countries fishing transboundary reef - associated species (Fig.
-3B), Indonesia, Malaysia and the Philippines are among the highest fish consumption per capita in the world with 20, 60 and 40 kg per year, respectively [@Foale:2013iw].
-In these countries, reeef fish contributes substantially to both food security and livelehood of coastal communities [@Cabral:2018hc].
 
@@
 Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result.
-Only commercial fished species with data from all four sources were included in the analysis **NOTE: WC "Need to discuss how this affect the samples of transboundary species."**.
+Only commercial fished species with data from all four sources were included in the analysis.
 The final dataset comprised 968 marine species (including anadromous species like salmononids), **XX%** of the total number of reported marine species in the SAU database and **XX%** of the reported marine taxa of included by the Food and Agricultural Organization of the United Nations (FAO).
 
+<!-- **NOTE: WC "Need to discuss how this affect the samples of transboundary species."**. -->
 <!-- **NOTE: for transboundary lobsters https://books.google.com.ar/books?id=XEElAwNrKZsC&pg=PA224&lpg=PA224&dq=belize+mexico+lobster+shared+stock&source=bl&ots=lsmUH743d_&sig=ACfU3U1P1t7_L8q_YRh3oQGszUO8Lg1jFw&hl=en&sa=X&ved=2ahUKEwiv36qbwbjnAhX3HrkGHYIbCTgQ6AEwFHoECA0QAQ#v=onepage&q=belize%20mexico%20lobster%20shared%20stock&f=false** -->
@@
 Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-**We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries and to reduce the uncertanty embeded in the recosntruction process (See Key uncertanties).**
+We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries and to reduce the uncertanty embeded in the recosntruction process (See Key uncertanties).
 

### 2020-02-07 Initial_Analysis.Rmd
Estimated Disxrete species per country
Change paths to load data from carmelia

@@
 if(Sys.info()[7] == "carmelia"){
-  Data_Path <- paste(here::here(),"/Temporal_Data",sep = "")
+  Data_Path <- paste(here::here(),"/Temporal_Data/",sep = "")
 }

### 2020-02-07 Initial_Analysis.Rmd
Exploring Colette's comment

@@
 
+# Read Results For Carmelia
+
+# Clean_Results_Trans <- fread(paste(Data_Path,"Results/EEZ/Clean_Results_Trans.csv", sep =""))
+
 # Vulnerabillity Data from William
@@
 
-length(unique(Tresholded_T_Data$eez_name))
+length(unique(Tresholded_T_Data$taxon_key))
+
+Discrete <- Clean_Results_Trans %>% 
+  filter(
+    area_index < Min_AI |
+    area_index > Max_AI |
+    model_index < MI
+  )
+
+# Makes sense?
+# nrow(Tresholded_T_Data) + nrow(Discrete) == nrow(Clean_Results_Trans) # TRUE
+
+#Number of discrete species #170
+
+n_discrete <- Clean_Results_Trans %>% 
+  filter(! taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
+  group_by() %>% 
+  summarize(length(unique(taxon_key))) %>% 
+  pull()
 
@@
 # Not in our shaopefile
+
+```
+
+### UN Data exploration
+
+```{r}
+
+  UN_Regions %>% 
+  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
+  group_by(sub_region) %>% 
+  summarise(n_countries = length(unique(fishing_entity))) %>% 
+  arrange(n_countries)
+
+World_sf %>% 
+  as.data.frame() %>% 
+  left_join(UN_Regions) %>% 
+  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
+  group_by(sub_region) %>% 
+  summarise(Size_EEZ = sum())
 

### 2020-02-11 Initial_Analysis.Rmd
Comments to weighted method

@@
 # -------------------------- #
+# Percentage of capture analyzed
+# -------------------------- #
+
+EEZ_Catch %>% 
+  filter(
+    reporting_status == "Reported",
+    year > 2005) %>% 
+  group_by(year) %>% 
+  summarise(sum_year = sum(tonnes),
+            sum_year_value = sum(landed_value)) %>% 
+  group_by() %>% 
+  summarise(mean(sum_year),
+            mean(sum_year_value)
+  )
+
+Total_Catch_Spp <- 71842644/75202371
+
+# -------------------------- #
 # Number of Transboundary Species
@@
 
-Global_Catch <- 108 # million (estimated from sau.com)
+Global_Catch <- 80 # million (estimated from sau.com)
 
@@
                                paste(sub_region))
-    )
+    ),
+    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
   )
@@
 ```{r Territory_Map_Round_Catch, eval =F, echo =F}
+
+# Get Catch data for mapping (Supplemental materials)
+Catch_Breaks <- c(-1,10,100,1000,5000,10000)
+
+Catch_Country <- SAU_Catch_Data %>%
+  group_by(eez_name) %>%
+  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>%
+  group_by(fishing_entity) %>%
+  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
+  mutate(
+    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
+    #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
+    Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
+    Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
+                    labels = c('super low', 'low','median','high','super high'))
+  ) %>% 
+  filter(fishing_entity_catch > 0)
+
+# Create labels for legend
+Bins_Trans <- Transboundary_Spp %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+Bins_Catch <- Catch_Country %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
+Labels_Catch <- c("(1-10]",paste(Bins_Catch[2:5]))
+
+# Transboundary Species shapefile
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326) %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Transboundary_Spp, by ="eez_name")
+
+# Total catch/Revenue shapefile
+World_sf_si_land <- World_land_sf %>%
+  st_transform(crs = 4326) %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
+  left_join(Catch_Country, by ="fishing_entity")
+
+# Get the NA's to be grey
+Grey_land <- World_sf_si_land %>% 
+  filter(is.na(Bins_Plot))
+
+# Make map
+Map <- ggplot() +
+  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,fishing_entity_catch)), colour = "grey80",size = 0.1) +
+  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
+  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
+  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+                                  "#00A08A",#"#00A08A", #green
+                                  "#F2AD00",#"#F2AD00", # Yellow
+                                  "#F98400",#"#F98400", #Orange
+                                  "#FF0000"#,"#FF0000" #Red
+  ),
+  na.translate = F
+  ) +
+  ggtheme_map() +
+  # Transboundary labels
+  annotate("text",
+           x =(c(-85.5,-30,25,81,136)+5),
+           y = -93.5,
+           label = Labels_Trans,
+           color="black",
+           size=3,
+           angle=0,
+           # fontface="bold",
+           hjust=0) +
+  # Catch labels
+  annotate("text",
+           x =(c(-85.5,-31,20,75,131)+5),
+           y = -110,
+           label = Labels_Catch,
+           color="black",
+           size=3,
+           angle=0,
+           # fontface="bold",
+           hjust=0) +
+  # # Legend Titles
+  annotate("text",
+           x =-180,
+           y = -93.5,
+           label = "Transboundary Spp. (n)",
+           color="black",
+           size=3,
+           angle=0,
+           fontface="bold",
+           hjust=0) +
+  annotate("text",
+           x =-180,
+           y = -110,
+           label = "Catch (Thousand tons)",
+           color="black",
+           size=3,
+           angle=0,
+           fontface="bold",
+           hjust=0) +
+  theme(
+    legend.box.margin = margin(t = -54, l = 130),
+    legend.text = element_blank(),
+  ) +
+  guides(fill = guide_legend(nrow = 1))
+
+ggsave(
+  plot = last_plot(),
+  width = 8,
+  height = 5,
+  units = "in",
+  filename = "S1_Catch_EEZ.png"#,
+  # path = Figures_Path
+)
+
+```
+
+```{r Territory_Map_Round_Weighted, eval =F, echo =F}
 

### 2020-02-11 Initial_Analysis.Rmd
Get data for weighted method

--- 2020-02-07 Initial_Analysis.Rmd
@@
   as.data.frame() %>% 
+  left_join(Clean_sau_eez_fes) %>% 
   left_join(UN_Regions) %>% 
@@
   group_by(sub_region) %>% 
-  summarise(Size_EEZ = sum())
+  summarise(Size_EEZ = sum(Area_km2)) %>% 
+  arrange(desc(Size_EEZ))
 

### 2020-02-11 Manuscript_Draft.Rmd

@@
 
-We overlaid the known distribution of 968 commercially valuable marine species responsable for **XX%** of global catch, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
+We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reported to FAO, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
 First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.
@@
 We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed.
-Transboundary species are partiuclarly abundant in EEZs of western Europe, northwestern Africa, and southeastern Asia (Fig.
-1A).
-Species' composition in these areas is relativly homogenous due to biogeochemical, oceanographic and topography features [@Spalding:2007th; @Reygondeau:2013cd].
-For example north west Africa and and west Europe are part of the Lusitanian large marine ecoregion (LME), similarly the Northern European Seas LME and south east China is part of the Western Coral Triangle LME [@Spalding].
-Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **64%** of the EEZ-derrived catches, and generating USD **79,745** million in fishing revenue.
-This is equivalent to **49.8%** of the global fishing revenue of the same period.
+Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **92%** of the EEZ-derrived catches reported to FAO, and generating USD **79,745** million in fishing revenue.
+This is equivalent to **49.8% (73.16% according to new numbers)** of the global fishing revenue of the same period.
 These values are more than double the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd], underscoring the importance of transboundary species at the global level.
@@
 B) Contribution of tranbsoundary species to regional revenue (left) and catch (right).
+Regions according to the United Nations sub-regions.
 Points = mean +- sd.
@@
 
-Transboundary species are particularly important economically for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+We aggregate countries according to the United Nations sub-regions (**Supplements**) and found that transboundary species are particularly economically important for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
 China (USD 6,279 million) in E.
@@
 Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
-
-<!-- **NOTE: MAKE SURE RUSSIA IS NOT E.ASIA** -->
+Differences in tansboundary fisheries can also be ilustrated in terms of catch-revenue/EEZ $km^2$ (**Supplements_Kmproportion**).
+As an example, Eastern Europe who's EEZ is the $9^{th}$ larger of the groups analized (**Supplemental table**) shoots out as having the most revenue (XXX) and catch (XXX) of species per EEZ area, significantly differing from the rest (**Statistics**).
 

### 2020-02-11 Initial_Analysis.Rmd
Include weight

@@
 
+#### Determine Regions ezs areas
+
+Regional_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  left_join(UN_Regions) %>% 
+  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
+  group_by(sub_region) %>% 
+  summarise(Size_EEZ = sum(Area_km2))
+
 # ---------------------------- #
@@
   ) %>% 
+  left_join(Regional_Area, 
+            by = "eez_name") %>% 
   mutate(
@@
     Bins_Plot = cut(n_trans_spp,breaks = 5,
-                    labels = c('super low', 'low','median', 'high','super high'))
+                    labels = c('super low', 'low','median', 'high','super high')),
+    # Include the weighted method for supplementals
+    Weight_Spp = n_trans_spp/Size_EEZ 
+    Weight_Bins = cut(Weight_Spp,breaks = 5),
+    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
+                    labels = c('super low', 'low','median', 'high','super high')),
   )
@@
   ungroup() %>% 
-  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
-    # ),
+  left_join(Regional_Area, 
+            by = "eez_name") %>% 
+  mutate(
     Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
@@
                     dig.lab = 5 # Removes scientific notaion
+    ),
+     # Include the weighted method for supplementals
+    Weight_Rev = Total_USD/Size_EEZ 
+    Weight_Bins = cut(Weight_Rev,breaks = 5),
+    Weight_Bins_Plot = cut(Weight_Rev,breaks = 5,
+                    labels = c('super low', 'low','median', 'high','super high')),
   )
@@
 
+# Label info
 label_data_rev <- Subregion_Data_Trans %>% 

### 2020-02-12 Initial_Analysis.Rmd
Did some updates

--- 2020-02-11 Initial_Analysis.Rmd
@@
 
+#### Determine Regions ezs areas
+
+EEZ_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  group_by(eez_name) %>% 
+  summarise(Size_EEZ = sum(Area_km2))
+
+Regional_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  left_join(UN_Regions) %>% 
+  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
+  group_by(sub_region) %>% 
+  summarise(Size_Region = sum(Area_km2))
+
 # ---------------------------- #
@@
 # Read Sau Value Data (Thank you Tim!)
-SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
+SAU_Tim_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep =""))
+
+SAU_Sampled_Data <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
   clean_names() %>% 
   group_by(fishing_entity_id,taxon_key) %>% 
-  summarise(mean_value = mean(value,na.rm=T)) %>% 
-  left_join(Clean_sau_eez_fes)
+  summarise_at(c("catch","value"),
+               mean,na.rm=T) %>% 
+  gather("Variable","Value",catch:value)
+
+# Total sampled catch
+Total_Catch <- SAU_Sampled_Data %>% 
+  filter(Variable == "catch") %>% 
+  group_by() %>% 
+  summarize(sum(Value,na.rm=T)) %>% 
+  pull()
 
@@
 
-EEZ_Catch %>% 
-  filter(
-    reporting_status == "Reported",
-    year > 2005) %>% 
-  group_by(year) %>% 
-  summarise(sum_year = sum(tonnes),
-            sum_year_value = sum(landed_value)) %>% 
-  group_by() %>% 
-  summarise(mean(sum_year),
-            mean(sum_year_value)
-  )
-
-Total_Catch_Spp <- 71842644/75202371
+Total_Catch_Spp <- SAU_Sampled_Data/SAU_Total_EEZ_Data
 
@@
 
-Total_Trans_Rev <- SAU_Revenue_Data %>% 
-  filter(taxon_key %in% Total_trans$taxon_key) %>% 
+Total_Trans_Rev <- SAU_Sampled_Data %>% 
+  semi_join(Tresholded_T_Data,
+            by = c("taxon_key"))
+
   group_by() %>% 
@@
   ) %>% 
+  left_join(EEZ_Area, 
+            by = "eez_name") %>% 
   mutate(
@@
     Bins_Plot = cut(n_trans_spp,breaks = 5,
-                    labels = c('super low', 'low','median', 'high','super high'))
+                    labels = c('super low', 'low','median', 'high','super high')),
+    # Include the weighted method for supplementals
+    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
+    Weight_Bins = cut(Weight_Spp,breaks = 5),
+    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
+                    labels = c('super low', 'low','median', 'high','super high')
+                    )
   )
@@
   ungroup() %>% 
-  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
-    # ),
+  # left_join(EEZ_Area, 
+            # by = "eez_name") %>% 
+  mutate(
     Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
@@
                     dig.lab = 5 # Removes scientific notaion
-    )
+    )#,
+     # Include the weighted method for supplementals
+  #   Weight_Rev = Total_USD/Size_EEZ,
+  #   Weight_Bins = cut(Weight_Rev,breaks = 5),
+  #   Weight_Bins_Plot = cut(Weight_Rev,breaks = 5,
+  #                   labels = c('super low', 'low','median', 'high','super high'))
+  # )
   ) %>% 
@@
   mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+  left_join(Regional_Area, 
+            by = "sub_region") %>% 
+  mutate(
+    Weighted_Catch = fishing_entity_catch/Size_Region,
+    Weighted_USD = Total_USD/Size_Region
+    ) %>% 
   group_by(sub_region) %>% 
@@
 
+# Label info Rev
 label_data_rev <- Subregion_Data_Trans %>% 
@@
 
+# Label info Catch
 label_data_catch <- Subregion_Data_Trans %>% 
   arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,nrow(Subregion_Data_Trans)),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region))
+    ),
+    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
+  )
+
+# Label info Weight Catch
+label_data_w_catch <- Subregion_Data_Trans %>% 
+  arrange(Weighted_Catch_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,nrow(Subregion_Data_Trans)),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region))
+    ),
+    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
+  )
+
+# Label info Weight Catch
+label_data_w_rev <- Subregion_Data_Trans %>% 
+  arrange(Weighted_USD_sum) %>% # soo it looks like a nice snail :)
   mutate(
@@
 
-```{r Territory_Map_Round_Weighted, eval =F, echo =F}
-
-# Get Catch data for mapping (Supplemental materials)
-Catch_Breaks <- c(-1,10,100,1000,5000,10000)
-
-Catch_Country <- SAU_Catch_Data %>%
-  group_by(eez_name) %>%
-  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>%
-  group_by(fishing_entity) %>%
-  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
-  mutate(
-    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-    Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
-    Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
-                    labels = c('super low', 'low','median','high','super high'))
-  ) %>% 
-  filter(fishing_entity_catch > 0)
-
-# Create labels for legend
-Bins_Trans <- Transboundary_Spp %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Bins_Catch <- Catch_Country %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
-Labels_Catch <- c("(1-10]",paste(Bins_Catch[2:5]))
-
-# Transboundary Species shapefile
-World_sf_si <- World_sf %>%
-  st_transform(crs = 4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")
-
-# Total catch/Revenue shapefile
-World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-  left_join(Catch_Country, by ="fishing_entity")
-
-# Get the NA's to be grey
-Grey_land <- World_sf_si_land %>% 
-  filter(is.na(Bins_Plot))
-
-# Make map
-Map <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,fishing_entity_catch)), colour = "grey80",size = 0.1) +
-  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
-  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
-  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-                                  "#00A08A",#"#00A08A", #green
-                                  "#F2AD00",#"#F2AD00", # Yellow
-                                  "#F98400",#"#F98400", #Orange
-                                  "#FF0000"#,"#FF0000" #Red
+```{r Weight_Revenue, eval =F, echo =F}
+
+####___________________________###
+### Now create the Two circluar bar plots
+####___________________________###
+
+# Revenue Plot
+
+# Set color pal
+pal <- wes_palette("Zissou1",100,type = "continuous")
+
+# Set plot limits
+max_lim <- max(Subregion_Data_Trans$Weighted_USD_sum) +0.01
+
+Rev_Plot <- ggplot(
+  # Regional plots
+  data = Subregion_Data_Trans, 
+  aes(
+    x=reorder(id,Weighted_USD_sum),
+    y=Weighted_USD_sum, 
+    fill=Weighted_USD_sum
+  )
+) +    
+  ylim(-0.001, max_lim) +
+  geom_bar(stat="identity") +
+  # Regional averages
+  geom_point(data = Subregion_Data_Trans,
+             aes(
+               x=reorder(id,Weighted_USD_m),
+               y=Weighted_USD_m
              ),
-  na.translate = F
+             colour = "black",
+             alpha = 0.5
   ) +
-  ggtheme_map() +
-  # Transboundary labels
-  annotate("text",
-           x =(c(-85.5,-30,25,81,136)+5),
-           y = -93.5,
-           label = Labels_Trans,
+  # Regional sds
+  geom_errorbar(
+    aes(
+      ymin=ifelse(Weighted_USD_m-Weighted_USD_sd <= 0,0,Weighted_USD_m-Weighted_USD_sd), # sets lower to 0
+      ymax=Weighted_USD_m+Weighted_USD_sd
+    ),
+    width=.2,
+    position=position_dodge(.9),
+    alpha = 0.5) +
+  # Looking good
+  theme_minimal() +
+  theme(
+    legend.position = c(0.73,0.60),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = margin(0,-10,-6,-10,"cm")
+  )  +
+  # Base line
+  # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
+  #              colour = "black", size=0.1, inherit.aes = FALSE) +
+  coord_polar(start = 0) + 
+  geom_text(data=label_data_w_rev, 
+            aes(x=id,
+                y=Weighted_USD_sum+0.0001,
+                label=sub_region,
+                hjust=hjust), 
             color="black",
-           size=3,
-           angle=0,
-           # fontface="bold",
-           hjust=0) +
-  # Catch labels
-  annotate("text",
-           x =(c(-85.5,-31,20,75,131)+5),
-           y = -110,
-           label = Labels_Catch,
+            fontface="bold",
+            size=2, 
+            angle= label_data_rev$angleb, 
+            inherit.aes = FALSE) +
+  scale_fill_gradientn("",
+                       colours = pal#,
+                       # limits = c(0,16500),
+                       # breaks = seq(0,16000,4000)
+                       ) +
+  guides(fill = guide_colorbar(label.position = "left")
+  )
+
+###____________###
+### Catch plot
+###____________###
+max_lim <- max(Subregion_Data_Trans$Weighted_Catch_sum) +0.001
+
+Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
+                     aes(x=reorder(id,Weighted_Catch_sum),
+                         y=Weighted_Catch_sum, 
+                         fill=Weighted_Catch_sum
+                     )
+) +    
+  ylim(-0.0003, max_lim) +
+  geom_bar(stat="identity") +
+  # Regional averages
+  geom_point(data = Subregion_Data_Trans,
+             aes(
+               x=reorder(id,Weighted_Catch_sum),
+               y=Weighted_Catch_m
+             ),
+             colour = "black",
+             alpha = 0.5
+  ) +
+  # Regional sd's
+  geom_errorbar(
+    aes(
+      ymin=ifelse(Weighted_Catch_m-Weighted_Catch_sd <= 0,0,Weighted_Catch_m-Weighted_Catch_sd),
+      ymax=Weighted_Catch_m+Weighted_Catch_sd
+    ), 
+    width=.2,
+    position=position_dodge(.9),
+    alpha = 0.5) +
+  theme_minimal() +
+  theme(
+    legend.position = c(0.1,0.60),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = margin(0,-10,-6,-5,"cm")
+  )  +
+  # Base line
+  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
+  #              colour = "black", size=0.1, inherit.aes = FALSE) +
+  coord_polar(start = 0) + 
+  geom_text(data=label_data_w_catch, 
+            aes(x=id,
+                y=Weighted_Catch_sum+0.0001,
+                label=sub_region,
+                hjust=hjust), 
             color="black",
-           size=3,
-           angle=0,
-           # fontface="bold",
-           hjust=0) +
-  # # Legend Titles
-  annotate("text",
-           x =-180,
-           y = -93.5,
-           label = "Transboundary Spp. (n)",
-           color="black",
-           size=3,
-           angle=0,
             fontface="bold",
-           hjust=0) +
-  annotate("text",
-           x =-180,
-           y = -110,
-           label = "Catch (Thousand tons)",
-           color="black",
-           size=3,
-           angle=0,
-           fontface="bold",
-           hjust=0) +
-  theme(
-    legend.box.margin = margin(t = -54, l = 130),
-    legend.text = element_blank(),
+            size=2, 
+            angle= label_data_catch$angleb, 
+            inherit.aes = FALSE) +
+  scale_fill_gradientn("",
+                       # limits = c(0,16.5),
+                       # breaks = seq(0,16,4),
+                       colours = pal
+
+  );Catch_Plot
+
+## Joining everything in one ploit
+
+plot <- ggdraw() +
+  # map
+  # draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
+  # Revenue circular
+  draw_plot(Rev_Plot, x = 0.2, y = 0.5, width = 0.5, height = 0.4) +
+  # Catch circular
+  draw_plot(Catch_Plot, x = 0.46, y = 0.5, width = 0.5, height = 0.4) +
+  # Labeks
+  draw_plot_label(label = c("A", "B"), 
+                  size = 20,
+                  x = c(0.1, 0.5), 
+                  y = c(1,1)
   ) +
-  guides(fill = guide_legend(nrow = 1))
-
-ggsave(
-  plot = last_plot(),
-  width = 8,
-  height = 5,
-  units = "in",
-  filename = "S1_Catch_EEZ.png"#,
-  # path = Figures_Path
+  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
+                  size = 8,
+                  x = c(0.330,0.485), 
+                  y = c(0.31,0.29)
+  )
+
+save_plot(
+  paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
+  # "Plot.png",
+  plot,
+  base_height = 8,
+  base_width = 8
 )

### 2020-02-12 Manuscript_Draft.Rmd
Did some updates

@@
 
-We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reported to FAO, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
+We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reconstruced by the *Sea Around Us*, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
 First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.

### 2020-03-03 Cover_Letter.Rmd
Finalized cover letter

@@
 ---
-title: 'Fish do nor need Visas: Reference Letter'
-author: "Juliano Palacios Abrantes"
-date: '2019-09-18'
-output: pdf_document
+output:
+  word_document: default
+  pdf_document: default
 ---
+[Editor Name] 									     02-22-2020
 
-Should include:
-- Reference to any pre-submission discussions with editors.
-- The title of the paper and a statement of its main point.
-- Any information needed to ensure a fair review process, including related manuscripts submitted to other journals.
-- Names of colleagues who have reviewed the paper.
-- A statement that none of the material has been published or is under consideration for publication elsewhere.
-- Specification of where all data underlying the study are available, or will be deposited, and whether there are any restrictions on data availability such as an MTA.
-- Information on any reference material or additional data files uploaded to the Auxiliary files section (see below).
-- Please also upload a .docx version of your cover letter – see below.
+Title, Science
+
+Dear [Editor Name],
+
+Please find attached our manuscript titled “Marine species do not need visas: the transboundary nature of the world’s exploited marine species” submitted for publication in Science as a Report.
+In here we highlight the large and under-recognized scale of transboundary fisheries and discusses the challenges in achieving international fisheries management goals.
+
+Last year Nandini et al published a paper in Science where they demonstrate that the world of marine fishes is deeply interconnected by larvae.
+Here, we show that this is not only true at the early stages of marine species, but also in later life stages, as marine species distribute across multiple Economic Exclusive Zones.
+We found that 67% of the world’s identified fished species are transboundary and responsible for 80% of the global-EEZs catches and 78.5% of fisheries revenue of the last decade.
+We rely on multiple data sources of species distributions to estimate the number of shared species, their contribution to global, regional and local catch and fishing revenue, and their potential management status.
+We identify that the largest share of transboundary species are oceanic pelagics, and that fisheries catching transboundary species seem to be worse off than those for non-transboundary stocks.
+Our study has direct implications for the management of transboundary species, calling for international cooperation in the management of these fisheries.
+
+Please do not hesitate to contact me if you require more information.
+This manuscript is not being considered for publication in any other journal.
+All code used to analyze the data is currently available at https://github.com/jepa/FishForVisa and data will be available upon request if the paber is published.
+
+Sincerely (on behalf of all authors),
+
+Juliano Palacios Abrantes
+The Institute for Oceans and Fisheries
+ The University of British Columbia

### 2020-03-03 Initial_Analysis.Rmd
All of the weighted and discrete analysis

--- 2020-02-11 Initial_Analysis.Rmd
@@
   "rfishbase", # for species ecosystem affinity
-  "zoo" #for runing mean
+  "zoo", #for runing mean
+  "pgirmess" # for dune test after kurtis wallas
 )
@@
 
+### Function `Figure CreateFigureOne`
+
+This function will create figure one for both catch or value
+
+```{r fun_Figure_1, eval =F, echo =F}
+
+CreateFigureOne <- function(Variable_Selected){
+
+  if(Variable_Selected == "catch"){
+    Map_Label <- "Catch (Thousand Tonnes)"
+    Plot_Name <- "Catch_plot.png"
+  }else{
+    Map_Label <- "Revenue (Million USD)"
+    Plot_Name <- "Rev_plot.png"
+  }
+
+  # Filter vatch/valye data for the variable selecter (Map)
+  Transboundary_Data_Plot <- Value_Trans_Country %>% 
+    filter(Variable %in% Variable_Selected)
+
+  # Total catch/Revenue shapefile
+  World_sf_si_land <- World_land_sf %>%
+    st_transform(crs = 4326) %>% # 4326
+    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
+    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
+    filter(Variable %in% Variable_Selected)
+
+  # Get the NA's to be grey
+  Grey_land <- World_land_sf %>%  
+    filter(!NAME_EN %in% World_sf_si_land$NAME_EN)
+
+  Bins <- Value_Trans_Country %>% 
+    filter(Variable %in% Variable_Selected) %>% 
+    arrange(Bins) %>% 
+    pull(Bins) %>% 
+    unique()
+
+  Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
+  Labels <- c("(1-10]",paste(Bins[2:5]))
+
+  Map <- ggplot() +
+    geom_sf(data = World_sf_si_land,
+            aes(fill = reorder(Bins_Plot,Value)), 
+            colour = "grey80",
+            size = 0.1) +
+    geom_sf(data = World_sf_si,
+            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
+            colour = "grey20",
+            size = 0.1) + # n_trans_spp or Bins
+    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
+    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
+                                    "#00A08A",#"#00A08A", #green
+                                    "#F2AD00",#"#F2AD00", # Yellow
+                                    "#F98400",#"#F98400", #Orange
+                                    "#FF0000"#,"#FF0000" #Red
+    ),
+    na.translate = F
+    ) +
+    ggtheme_map() +
+    # Transboundary labels
+    annotate("text", 
+             x =(c(-85.5,-30,25,81,136)+5),
+             y = -93.5,
+             label = Labels_Trans, 
+             color="black", 
+             size=3, 
+             angle=0, 
+             # fontface="bold",
+             hjust=0) +
+    # Revenue labels
+    annotate("text", 
+             x =(c(-85.5,-31,20,75,131)+5),
+             y = -110,
+             label = Labels, 
+             color="black", 
+             size=3, 
+             angle=0, 
+             # fontface="bold",
+             hjust=0) +
+    # Legend Titles
+    annotate("text", 
+             x =-180,
+             y = -93.5,
+             label = "Transboundary Spp. (n)", 
+             color="black", 
+             size=3, 
+             angle=0, 
+             fontface="bold",
+             hjust=0) +
+    annotate("text", 
+             x =-180,
+             y = -110,
+             label = Map_Label,
+             color="black", 
+             size=3, 
+             angle=0, 
+             fontface="bold",
+             hjust=0) +
+    theme(
+      legend.box.margin = margin(t = -54, l = 130),
+      legend.text = element_blank(),
+    ) +
+    guides(fill = guide_legend(nrow = 1))
+
+  ####___________________________###
+  ### Now create the Two circluar bar plots
+  ####___________________________###
+
+  # Revenue Plot
+
+  # Set plot limits
+
+  max_Rev_lim <- Subregion_Trans_Value %>%
+    filter(Variable == "value") %>%
+    group_by() %>%
+    summarise(max(Value_sum)) %>%
+    pull()
+
+  Subregion_Rev_Data <- Subregion_Trans_Value %>% 
+    filter(Variable == "value")
+
+  Rev_Plot <- ggplot(
+    # Regional plots
+    data = Subregion_Rev_Data,
+    aes(
+      x=reorder(id,Value_sum),
+      y=Value_sum, 
+      fill=Value_sum
+    )
+  ) +    
+    ylim(-1500, max_Rev_lim) +
+    geom_bar(stat="identity") +
+    # Regional averages
+    geom_point(data = Subregion_Rev_Data,
+               aes(
+                 x=reorder(id,Value_sum),
+                 y=Value_m
+               ),
+               colour = "black",
+               alpha = 0.5
+    ) +
+    # Regional sds
+    geom_errorbar(data = Subregion_Rev_Data,
+                  aes(
+                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
+                    ymax=Value_m+Value_sd
+                  ), 
+                  width=.2,
+                  position=position_dodge(.9),
+                  alpha = 0.5) +
+    # Looking good
+    theme_minimal() +
+    theme(
+      legend.position = c(0.73,0.60),
+      axis.text = element_blank(),
+      axis.title = element_blank(),
+      panel.grid = element_blank(),
+      plot.margin = margin(0,-10,-6,-10,"cm")
+    )  +
+    # Base line
+    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
+    #              colour = "black", size=0.1, inherit.aes = FALSE) +
+    coord_polar(start = 0) + 
+    geom_text(data=label_data_rev, 
+              aes(x=id,
+                  y=Value_sum+10,
+                  label=sub_region,
+                  hjust=hjust), 
+              color="black",
+              fontface="bold",
+              size=2, 
+              angle= label_data_rev$angleb, 
+              inherit.aes = FALSE) +
+    scale_fill_gradientn("",
+                         colours = pal,
+                         limits = c(0,12000),
+                         breaks = seq(0,12000,3000)) +
+    guides(fill = guide_colorbar(label.position = "left")
+    )
+
+  ###____________###
+  ### Catch plot
+  ###____________###
+
+  max_Catch_lim <- Subregion_Trans_Value %>% 
+    filter(Variable == "catch") %>% 
+    group_by() %>% 
+    summarise(max(Value_sum)) %>% 
+    pull()
+
+  Subregion_Catch_Data <- Subregion_Trans_Value %>% 
+    filter(Variable == "catch")
+
+  Catch_Plot <- ggplot(data = Subregion_Catch_Data,
+                     aes(x=reorder(id,Value_sum),
+                         y=Value_sum, 
+                         fill=Value_sum
+                     )
+) +    
+  ylim(-1.5, max_Catch_lim) +
+  geom_bar(stat="identity") +
+  # Regional averages
+  geom_point(data = Subregion_Catch_Data,
+             aes(
+               x=reorder(id,Value_sum),
+               y=Value_m
+             ),
+             colour = "black",
+             alpha = 0.5
+  ) +
+  # Regional sd's
+  geom_errorbar(data = Subregion_Catch_Data,
+    aes(
+      ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd),
+      ymax=Value_m+Value_sd
+    ), 
+    width=.2,
+    position=position_dodge(.9),
+    alpha = 0.5) +
+  theme_minimal() +
+  theme(
+    legend.position = c(0.1,0.60),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = margin(0,-10,-6,-5,"cm")
+  )  +
+  # Base line
+  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
+  #              colour = "black", size=0.1, inherit.aes = FALSE) +
+  coord_polar(start = 0) + 
+  geom_text(data=label_data_catch, 
+            aes(x=id,
+                y=ifelse(Value_sum == 12,Value_sum,Value_sum+0.1), # Fix names overlap
+                label=sub_region,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
+            size=2, 
+            angle= label_data_catch$angleb, 
+            inherit.aes = FALSE) +
+  scale_fill_gradientn("",
+                       limits = c(0,12),
+                       breaks = seq(0,12,3),
+                       colours = pal
+  )
+
+  ## Joining everything in one ploit
+
+  plot_all <- ggdraw() +
+  # map
+  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
+  # Revenue circular
+  draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
+  # Catch circular
+  draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
+  # Labeks
+  draw_plot_label(label = c("A", "B"), 
+                  size = 20,
+                  x = c(0, 0), 
+                  y = c(1, 0.45)
+  ) +
+  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
+                  size = 8,
+                  x = c(0.330,0.485), 
+                  y = c(0.31,0.29)
+  )
+
+  save_plot(
+    # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
+    Plot_Name,
+    plot_all,
+    base_height = 8,
+    base_width = 8
+  )
+
+} # End of function
+```
+
 ## Load Results data
@@
   clean_names()
+
+Species_Sampled <- fread(paste(Data_Path,"Distribution_Data/Sampled_Species.csv", sep =""))
 
@@
 
+#### Determine polygon areas
+
+# EEZ Area
+EEZ_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  group_by(eez_name) %>% 
+  summarise(Size_EEZ = sum(Area_km2))
+
+# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
+Entity_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_Results_Trans,
+            by = "eez_name") %>% 
+  group_by(fishing_entity) %>% 
+  summarise(Size_Entity = sum(Area_km2))
+
+# Regional EEZ area
+Regional_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  left_join(UN_Regions) %>% 
+  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
+  group_by(sub_region) %>% 
+  summarise(Size_Region = sum(Area_km2)) %>% 
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+  arrange(sub_region)
+
+# ---------------------------- #
+# Supplement table 2
+# write_csv(Regional_Area,
+          # "Table S1.csv")
+# ---------------------------- #
+
 # ---------------------------- #
@@
 
-# Read Sau Catch Data
-SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_country_taxon.csv", sep =""))
-
 # Read Sau Value Data (Thank you Tim!)
-SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
+SAU_Tim_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep =""))
+
+# Set global values for catch and revenue (within EEZ with re-constructed catch)
+SAU_Global_Data <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
   clean_names() %>% 
   group_by(fishing_entity_id,taxon_key) %>% 
-  summarise(mean_value = mean(value,na.rm=T)) %>% 
-  left_join(Clean_sau_eez_fes)
+  summarise_at(c("catch","value"),
+               mean,na.rm=T) %>% 
+  gather("Variable","Value",catch:value)
 
@@
 
-# Clean_Results_Trans <- fread(paste(Data_Path,"Results/EEZ/Clean_Results_Trans.csv", sep =""))
+Clean_Results_Trans <- fread(paste(Data_Path,"Results/EEZ/Clean_Results_Trans.csv", sep =""))
 
@@
 
-length(unique(Tresholded_T_Data$taxon_key))
+```
+
+## Overall results
+
+```{r Transboundary_Data_per_Territory, eval = F, echo = F}
+
+# -------------------------- #
+# Number of Transboundary and Discrete Species
+# -------------------------- #
+
+n_trans <- Tresholded_T_Data %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length()
+
+# Percentage of transboundary species from sampled
+n_trans/938*100
+
+# -------------------------- #
+# Percentage of capture analyzed
+# -------------------------- #
+
+# Filter Tim's data for only those species we estimate
+Total_SAU_Sampled <- SAU_Global_Data %>%
+  filter(taxon_key %in% Species_Sampled$TaxonKey) %>% 
+  group_by(Variable) %>% 
+  summarize(Total_Sampled = sum(Value,na.rm=T),
+            Sampled_nspp = length(unique(taxon_key))
+            )
+
+# Get the total values for the world excluding not identified species
+Total_SAU_id <- SAU_Global_Data %>% 
+  left_join(Exploited_Species) %>% # list of SAU exploited species identified
+  filter(!is.na(taxon_name)) %>% # reove those NAs 
+  group_by(Variable) %>% 
+  summarize(Total_id = sum(Value,na.rm=T),
+            id_nspp = length(unique(taxon_key))
+            )
+
+# Get the total values for the world including non id species
+Total_SAU_Global <- SAU_Global_Data %>% 
+  group_by(Variable) %>% 
+  summarize(Total_Global = sum(Value,na.rm=T),
+            Global_nspp = length(unique(taxon_key))
+            )
+
+# Percentage catch of species analyzed from the identified species
+Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.57%
+
+# Percentage species analyzed from the identified species
+Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.2%
+
+# When we do not remove the groups that are not species level the number sampled drops to ~60%
+
+### So what species are NOT there? 
+#  Absten species
+# Missing_Species <- SAU_Global_Data %>%
+#   filter(!taxon_key %in% Species_Sampled$TaxonKey) %>% 
+#   left_join(Exploited_Species) %>% 
+#   filter(!is.na(taxon_name)) %>% 
+#   group_by(taxon_key,taxon_name,common_name) %>% 
+#   summarise(sum(Value))
+
+# -------------------------- #
+# Total and percentage Catch and Revenue from Transboundary species
+# -------------------------- #
+
+# Filter SAU data for only those sampled species
+SAU_Sampled_Data <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
+  left_join(Exploited_Species) %>% 
+  filter(!is.na(taxon_name)) %>% 
+  clean_names() %>% 
+  group_by(fishing_entity_id,taxon_key) %>% 
+  summarise_at(c("catch","value"),
+               mean,na.rm=T) %>% 
+  gather("Variable","Value",catch:value)
+
+Summary_Trans <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Sampled_Data) %>% 
+  semi_join(Tresholded_T_Data,
+            by = c("taxon_key","fishing_entity")) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
+  group_by(Variable) %>%
+  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
+  left_join(Total_SAU_Sampled) %>% 
+  left_join(Total_SAU_Global) %>% 
+  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
+         Per_SAU = Total_Trans/Total_Global*100)
+
+```
+
+```{r Discrete_Data_per_Territory, eval = F, echo = F}
+
+Species_Left_Out <- Species_Sampled %>% 
+  filter(!TaxonKey %in% Clean_Results_Trans$taxon_key) %>% 
+  select(taxon_key = TaxonKey)
+
+###_________________###
+# Discrete species
+###_________________###
 
@@
     model_index < MI
-  )
-
-# Makes sense?
-# nrow(Tresholded_T_Data) + nrow(Discrete) == nrow(Clean_Results_Trans) # TRUE
-
-#Number of discrete species #170
-
-n_discrete <- Clean_Results_Trans %>% 
-  filter(! taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
-  group_by() %>% 
-  summarize(length(unique(taxon_key))) %>% 
-  pull()
-
-```
-
-## Overall results
-
-```{r Data_per_Territory, eval = F, echo = F}
-
-# -------------------------- #
-# Percentage of capture analyzed
-# -------------------------- #
-
-EEZ_Catch %>% 
-  filter(
-    reporting_status == "Reported",
-    year > 2005) %>% 
-  group_by(year) %>% 
-  summarise(sum_year = sum(tonnes),
-            sum_year_value = sum(landed_value)) %>% 
-  group_by() %>% 
-  summarise(mean(sum_year),
-            mean(sum_year_value)
-  )
-
-Total_Catch_Spp <- 71842644/75202371
-
-# -------------------------- #
-# Number of Transboundary Species
-# -------------------------- #
-
-Total_trans <- Clean_Results_Trans %>% 
-  filter(
-    area_index >= Min_AI,
-    area_index <= Max_AI,
-    model_index >= MI
-  )
-
-Total_trans_n <- Total_trans %>% 
-  pull(taxon_key) %>% 
-  unique() %>% 
+  ) %>% 
+  # bind_rows(Species_Left_Out) %>% 
+  group_by(taxon_key,fishing_entity,eez_name) %>% 
+  summarise(n()) %>% 
+  anti_join(Tresholded_T_Data,
+            by = c("taxon_key","eez_name"))
+
+# Both categories (trans and Discrete)
+Tresholded_T_Data %>% 
+  semi_join(Discrete,
+            by = "taxon_key") %>% 
+  group_by(taxon_key) %>% 
+  summarise(n()) %>% 
+  pull(unique(taxon_key)) %>% 
   length()
 
-# -------------------------- #
-# Total Revenue
-# -------------------------- #
-
-Total_Trans_Rev <- SAU_Revenue_Data %>% 
-  filter(taxon_key %in% Total_trans$taxon_key) %>% 
-  group_by() %>% 
-  summarise(Total =sum(mean_value)/1000000)# total revenue within EEZs of the world from sau.org
-
-Per_Trans_Rev <- SAU_Revenue_Data %>% 
-  filter(taxon_key %in% Total_trans$taxon_key) %>% 
-  group_by() %>% 
-  summarise(Total =sum(mean_value)/1000000) %>%  # million
-  pull()/160000*100
-
-# -------------------------- #
-# Total Catch
-# -------------------------- #
-
-Total_Trans_Catch <- SAU_Catch_Data %>% 
-  filter(taxon_key %in% Total_trans$taxon_key) %>% 
-  group_by() %>% 
-  summarise(Total =sum(total_catch)/1000000) %>%  # total revenue within EEZs of the world from sau.org
-  pull()
-
-Global_Catch <- 80 # million (estimated from sau.com)
-
-Per_Catch <- (Total_Trans_Catch/Global_Catch)*100
+n_discrete <- length(unique(Discrete$taxon_key))
+
+  Summary_Discrete_B <- Discrete_B %>% 
+  left_join(SAU_Sampled_Data,
+           by = c("taxon_key","eez_name")) %>% 
+  group_by(Variable) %>%
+  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
+  left_join(Total_SAU_Sampled) %>% 
+  left_join(Total_SAU_Global) %>% 
+  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
+         Per_SAU = Total_Discrete/Total_Global*100)
+
+###_________________###
+# Discrete Exclusive
+###_________________###
+
+  # Discrete species (not in Tresholded)
+Discrete_Exclusive <- Clean_Results_Trans %>% 
+  filter(!taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
+  bind_rows(Species_Left_Out) %>% 
+  group_by(taxon_key) %>% 
+  summarise(n())
+
+# Number of discrete species
+n_discrete_exclusive <- length(unique(Discrete_Exclusive$taxon_key))
+
+# Total species
+n_discrete_exclusive + n_trans # 938
+
+Summary_Discrete_Exclusive <- Discrete %>% 
+  left_join(SAU_Sampled_Data) %>% 
+  group_by(Variable) %>%
+  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
+  left_join(Total_SAU_Sampled) %>% 
+  left_join(Total_SAU_Global) %>% 
+  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
+         Per_SAU = Total_Discrete/Total_Global*100)
 
@@
     Bins_Plot = cut(n_trans_spp,breaks = 5,
-                    labels = c('super low', 'low','median', 'high','super high'))
+                    labels = c('super low', 'low','median', 'high','super high')),
+    # Include the weighted method for supplementals
+    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
+    # Weight_Bins = cut(Weight_Spp,breaks = 5),
+    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
+                           labels = c('super low', 'low','median', 'high','super high')
+    )
   )
@@
 # Set manual breaks for bins
-Rev_Breaks <- c(-1,10,100,1000,5000,10000)
-
-Revenue_Country <- sau_eez_fes %>% 
+Map_Breaks <- c(-1,10,100,1000,5000,10000)
+
+Value_Trans_Country <- sau_eez_fes %>% 
+  group_by(fishing_entity_id, fishing_entity) %>% 
+  summarise(n=n()) %>% # Get all of the fishing entity and id
+  select(-n) %>% 
+  left_join(Tresholded_T_Data,
+            by = "fishing_entity") %>% 
+  group_by(fishing_entity_id,
+           fishing_entity,
+           taxon_key) %>% 
+  summarise(n()) %>% # get each taxa per nation
+  left_join(SAU_Sampled_Data,
+            by = c("fishing_entity_id","taxon_key")) %>% 
+  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
+  summarise(
+    Trans_Entity_n = length(unique(taxon_key)),
+    Trans_Total = sum(Value,na.rm=T) #million
+  ) %>%
+  ungroup() %>%
+  filter(!is.na(Variable)) %>% # Momentaneus fix for some reason there are diff. between datasers
+  # Match the sacle limits of both value and and catch 
+  mutate(
+    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
+                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
+                                Trans_Total)
+                         )
+  ) %>% 
+  spread(Variable,Trans_Total) %>% 
+  left_join(Entity_Area, by = "fishing_entity") %>% 
+  # Include the weighted method for supplementals
+  mutate_at(
+    vars(catch,value),
+    funs(weight= ./(Size_Entity/1000000))
+  ) %>% 
+  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
+  group_by(fishing_entity,Variable,Value) %>% 
+  summarise(
+    Bins = cut(Value,breaks = Map_Breaks, dig.lab = 5 ),
+    Bins_Plot = cut(Value,breaks = Map_Breaks,
+                    labels = c('super low', 'low','median','high','super high'),
+                    dig.lab = 5 # Removes scientific notaion
+    )
+  ) %>% 
+  # Convert catch to million tonnes
+  mutate(
+    Value = ifelse(Variable == "catch",Value/1000, #million
+                         Value)
+  )
+
+```
+
+```{r Data_per_Continent, eval = F, echo = F}
+
+# Continental level for transboundary species
+Continent_Trans_Value <- Value_Trans_Country %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
+  group_by(georegion,Variable) %>% 
+  summarise_if(is.numeric,sum,na.rm=T) #%>% 
+  # select(-Size_Entity,-Trans_Entity_n)
+
+## Sub region leven
+
+Subregion_Trans_Value <- Value_Trans_Country %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+  group_by(sub_region,Variable) %>% 
+  summarise_if(is.numeric,c(Value_sum = sum,
+                            Value_m = mean,
+                            Value_sd = sd),
+               na.rm=T) %>%
+  # select(-Size_Entity,-Trans_Entity_n) %>% 
+  arrange(Variable) %>%
+  ungroup() %>% 
+  mutate(id = rep(seq(1,17),4)) %>% 
+  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))
+
+# Fix names for plot
+Subregion_Trans_Value$sub_region <- Subregion_Trans_Value$sub_region %>% 
+  gsub("Northern","N.",.) %>% 
+  gsub("Southern","S.",.) %>% 
+  gsub("Western","W.",.) %>% 
+  gsub("Eastern","E.",.)
+
+# Transboundary Species shapefile
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Transboundary_Spp, by ="eez_name")# %>%
+
+### Prepare data for plot
+
+number_of_bar <- 17 # Number of regions
+
+# Label info Rev
+label_data_rev <- Subregion_Trans_Value %>% 
+  filter(Variable == "value") %>% 
+  arrange(Value_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,number_of_bar),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region))
+    ),
+    sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
+  )
+
+# Label info Catch
+label_data_catch <- Subregion_Trans_Value %>% 
+  filter(Variable == "catch") %>% 
+  arrange(Value_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,number_of_bar),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region))
+    ),
+    sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
+  )
+
+# Create labels for legend
+Bins_Trans <- Transboundary_Spp %>% 
+  arrange(Bins) %>% 
+  pull(Bins) %>% 
+  unique()
+
+```
+
+### EEZ Map of Transboundary Species
+
+Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country
+
+```{r Figure_1}
+
+# Set color pal
+pal <- wes_palette("Zissou1",100,type = "continuous")
+
+# Variable to plot (value or catch)
+Variable_plot <- "catch"
+CreateFigureOne(Variable_plot)
+
+```
+
+```{r Weight_Revenue, eval =F, echo =F}
+
+Weighted_values <-c("value_weight","catch_weight")
+
+# data
+Weighted_Data <- Subregion_Trans_Value %>% 
+  filter(Variable %in% Weighted_values)
+
+# Labels
+
+label_data_rev <- Subregion_Trans_Value %>% 
+  filter(Variable == Weighted_values[1]) %>% 
+  arrange(Value_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,number_of_bar),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region)
+                               )
+    )
+  )
+
+# Label info Catch
+label_data_catch <- Subregion_Trans_Value %>% 
+  filter(Variable == Weighted_values[2]) %>% 
+  arrange(Value_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,number_of_bar),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               paste(sub_region))
+    )
+  )
+
+# Revenue Plot
+
+  # Set plot limits
+
+  max_Rev_lim <- Subregion_Trans_Value %>%
+    filter(Variable == Weighted_values[1]) %>%
+    group_by() %>%
+    summarise(max(Value_sum)) %>%
+    pull()
+
+  Subregion_Rev_Data <- Subregion_Trans_Value %>% 
+    filter(Variable == Weighted_values[1])
+
+  Rev_Plot <- ggplot(
+    # Regional plots
+    data = Subregion_Rev_Data,
+    aes(
+      x=reorder(id,Value_sum),
+      y=Value_sum, 
+      fill=Value_sum
+    )
+  ) +    
+    ylim(-50, 250) +
+    geom_bar(stat="identity") +
+    # Regional averages
+    geom_point(data = Subregion_Rev_Data,
+               aes(
+                 x=reorder(id,Value_sum),
+                 y=Value_m
+               ),
+               colour = "black",
+               alpha = 0.5,
+               size = 0.5
+    ) +
+    # Regional sds
+    geom_errorbar(data = Subregion_Rev_Data,
+                  aes(
+                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
+                    ymax=Value_m+Value_sd
+                  ), 
+                  width=.2,
+                  position=position_dodge(.9),
+                  alpha = 0.5) +
+    # Looking good
+    theme_minimal() +
+    theme(
+      legend.position = "",
+      axis.text = element_blank(),
+      axis.title = element_blank(),
+      panel.grid = element_blank(),
+      plot.margin = margin(1,0,0,-3,"cm")
+    )  +
+    coord_polar(start = 0) + 
+    geom_text(data=label_data_rev, 
+              aes(x=id,
+                  y=Value_sum+1,
+                  label=sub_region,
+                  hjust=hjust), 
+              color="black",
+              fontface="bold",
+              size=2, 
+              angle= label_data_rev$angleb, 
+              inherit.aes = FALSE) +
+    scale_fill_gradientn("",
+                         colours = pal,
+                         limits = c(0,250),
+                         breaks = seq(0,250,50)
+                         );Rev_Plot
+
+  ###____________###
+  ### Catch plot
+  ###____________###
+
+  max_Catch_lim <- Subregion_Trans_Value %>% 
+    filter(Variable == Weighted_values[2]) %>% 
+    group_by() %>% 
+    summarise(max(Value_sum)) %>% 
+    pull()
+
+  Subregion_Catch_Data <- Subregion_Trans_Value %>% 
+    filter(Variable == Weighted_values[2])
+
+  Catch_Plot <- ggplot(data = Subregion_Catch_Data,
+                     aes(x=reorder(id,Value_sum),
+                         y=Value_sum, 
+                         fill=Value_sum
+                     )
+) +    
+  ylim(-50, 251) +
+  geom_bar(stat="identity") +
+  # Regional averages
+  geom_point(data = Subregion_Catch_Data,
+             aes(
+               x=reorder(id,Value_sum),
+               y=Value_m
+             ),
+             colour = "black",
+             alpha = 0.5,
+             size = 0.5
+  ) +
+  # Regional sd's
+  geom_errorbar(data = Subregion_Catch_Data,
+    aes(
+      ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd),
+      ymax=Value_m+Value_sd
+    ), 
+    width=.2,
+    position=position_dodge(.9),
+    alpha = 0.5) +
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    legend.key.width =unit(2,"line"),
+    legend.key.height =unit(0.5,"line"),
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = margin(1,0,0,0,"cm")
+  )  +
+  coord_polar(start = 0) + 
+  geom_text(data=label_data_catch, 
+            aes(x=id,
+                y=ifelse(sub_region=="N. Europe",250,Value_sum+1), # Fix names overlap
+                label=sub_region,
+                hjust=hjust), 
+            color="black",
+            fontface="bold",
+            size=2, 
+            angle= label_data_catch$angleb, 
+            inherit.aes = FALSE) +
+  scale_fill_gradientn("",
+                       limits = c(0,251),
+                       breaks = seq(0,250,50),
+                       colours = pal
+  ); Catch_Plot
+
+  ## Joining everything in one ploit
+
+  # Get legend for cowplot
+legend_plot <- get_legend(Catch_Plot)
+
+# Re-plot without legend
+Catch_Plot <- Catch_Plot +
+  theme(legend.position = "")
+
+  p<- ggdraw() +
+  # Revenue circular
+  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
+  # Catch circular
+  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
+  # Legend
+  draw_plot(legend_plot, x = 0.2, y = 0.1, width = 0.59, height = 0.1) +
+  # Labeks
+  draw_plot_label(label = c("A", "B"),
+                  size = 15,
+                  x = c(0.1, 0.6),
+                  y = c(1, 1)
+  ) +
+  draw_plot_label(
+    label = c("Revenue (USD) | Catch (Tones)","Million per Km2"),
+                  size = 6,
+                  x = c(0.3,0.40),
+                  y = c(0.25,0.22)
+  )
+
+  save_plot(
+    paste(Figures_Path,"weight_plot.png",sep=""),
+    p,
+    base_height = 4,
+    base_width = 6
+  )
+
+```
+
+### China, US, Russia, and Peru
+
+```{r Map_Particulars, eval =F, echo =F}
+
+# Revenue details
+
+Top_Rev_Countries <- c("Peru", "Russian Federation", "Chile", "USA")
+
+Total_Top_Rev <- Value_Trans_Country %>% 
+  filter(Variable == "value") %>% 
+  filter(fishing_entity %in% Top_Rev_Countries) %>% 
+  select(1:3)
+
+Top_Rev <- sau_eez_fes %>% 
+  filter(fishing_entity %in% Top_Rev_Countries) %>% 
   group_by(fishing_entity_id, fishing_entity) %>% 
@@
   summarise(n()) %>% # get each taxa per nation
-  left_join(SAU_Revenue_Data,
-            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
-  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
-  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
+  left_join(SAU_Sampled_Data,
+            by = c("fishing_entity_id","taxon_key")) %>% 
+  filter(Variable == "value") %>% 
+  left_join(Exploited_Species) %>% 
+  group_by(fishing_entity) %>%
+  top_n(16,Value) %>%
+  select(fishing_entity,Variable,Value,taxon_name) %>% 
+  mutate(Top_Value = Value/1000000) %>% # Million of USD
+  select(-Value) %>% 
+  left_join(Total_Top_Rev,
+            by = c("fishing_entity","Variable")
+            ) %>% 
+  mutate(Ratio = Top_Value/Value*100)
+
+Top_Rev %>% 
+  group_by(fishing_entity) %>% 
+  summarise(sum(Ratio))
+
+### Total revenue from the top 5
+
+Top5 <- c("Peru", "Russian Federation", "Chile", "USA","China")
+
+Total_Top5 <- Value_Trans_Country %>% 
+  filter(Variable == "value") %>% 
+  filter(fishing_entity %in% Top_Rev_Countries) %>% 
   ungroup() %>% 
-  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
-    # ),
-    Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
-    Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
-                    labels = c('super low', 'low','median','high','super high'),
-                    dig.lab = 5 # Removes scientific notaion
-    )
-  ) %>% 
-  filter(Total_USD > 0)
-
-####  Data for Jessica
-
-# Data per Territory
-# Transboundary_Jess <- Tresholded_T_Data %>% 
-#   group_by(fishing_entity) %>% 
-#   summarise(
-#     n_trans_spp = length(unique(taxon_key)),
-#     # n_neighbours = length(unique(nt_fishing_entity)),
-#     # trans_Rrate = n_trans_spp/n_neighbours
-#   )
-
-# write_csv(Transboundary_Jess,
-#           "transboundary_species_dec19.csv")
-
-```
-
-```{r Data_per_Continent, eval = F, echo = F}
-
-# Contienent level
-Continent_Data <- Revenue_Country %>% 
-  left_join(Catch_Country,
-            by = "fishing_entity") %>% 
-  left_join(UN_Regions,
-            by = "fishing_entity") %>% 
-  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
-  group_by(georegion) %>% 
-  summarise_if(is.numeric,sum,na.rm=T)
-
-Continent_Data_Trans <- Tresholded_T_Data %>% 
-  left_join(UN_Regions,
-            by = "fishing_entity") %>% 
-  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
-  group_by(georegion) %>% 
-  summarise(
-    n_trans_spp = length(unique(taxon_key))
-  ) %>% 
-  left_join(Continent_Data)
-
-### Catch Data
-
-# Catch_Country
-
-Catch_Breaks <- c(-1,10,100,1000,5000,10000)
-
-Catch_Country <- SAU_Catch_Data %>%
-  group_by(eez_name) %>%
-  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>%
-  group_by(fishing_entity) %>%
-  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
-  mutate(
-    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-    Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
-    Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
-                    labels = c('super low', 'low','median','high','super high'))
-  ) %>% 
-  filter(fishing_entity_catch > 0)
-
-### Revenue Data
-Subregion_Data <- Revenue_Country %>% 
-  left_join(Catch_Country,
-            by = "fishing_entity") %>% 
+  select(fishing_entity,Value) %>% 
+  group_by() %>% 
+  summarise(sum(Value)) %>% 
+  pull()/(Total_SAU_Sampled$Total_Sampled[2]/1000000)*100
+
+```
+
+### Statistical differences
+
+We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.
+
+```{r statistics_fig1, eval = F, echo = T}
+
+### Using ANOVA to estimate significan differences within regions for revenue and catch of transboundary species
+
+Subregion_Data_stats <- Value_Trans_Country %>% 
   left_join(UN_Regions,
@@
   mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
-  group_by(sub_region) %>% 
-  summarise_if(is.numeric,c(sum = sum,
-                            m = mean,
-                            sd = sd),
-               na.rm=T)
-
-Subregion_Data_Trans <- Tresholded_T_Data %>% 
-  left_join(UN_Regions,
-            by = "fishing_entity") %>% 
-  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
-  group_by(sub_region) %>% 
-  summarise(
-    n_trans_spp = length(unique(taxon_key))
-  ) %>% 
-  left_join(Subregion_Data) %>% 
-  mutate(id = seq(1,nrow(.)))
-
-# Fix names for plot
-Subregion_Data_Trans$sub_region <- Subregion_Data_Trans$sub_region %>% 
-  gsub("Northern","N.",.) %>% 
-  gsub("Southern","S.",.) %>% 
-  gsub("Western","W.",.) %>% 
-  gsub("Eastern","E.",.)
-
-### Prepare data for plot
-
-number_of_bar <- nrow(Subregion_Data_Trans)
-
-label_data_rev <- Subregion_Data_Trans %>% 
-  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
-  mutate(
-    id = seq(1,nrow(Subregion_Data_Trans)),
-    angle = 90 -360 * (id-0.5)/number_of_bar,
-    hjust = ifelse(angle < -90,1,0),
-    angleb = ifelse(angle < -90, (angle +180), angle)
-  ) %>% 
-  mutate(
-    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
-                        ifelse(sub_region =="Northern America","Northern\nAmerica",
-                               paste(sub_region))
-    ),
-    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
-  )
-
-label_data_catch <- Subregion_Data_Trans %>% 
-  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
-  mutate(
-    id = seq(1,nrow(Subregion_Data_Trans)),
-    angle = 90 -360 * (id-0.5)/number_of_bar,
-    hjust = ifelse(angle < -90,1,0),
-    angleb = ifelse(angle < -90, (angle +180), angle)
-  ) %>% 
-  mutate(
-    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
-                        ifelse(sub_region =="Northern America","Northern\nAmerica",
-                               paste(sub_region))
-    ),
-    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
-  )
-
-# Transboundary Species shapefile
-World_sf_si <- World_sf %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")# %>% 
-# filter(!is.na(n_trans_spp))
-
-# Total catch/Revenue shapefile
-World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-  left_join(Revenue_Country, by ="fishing_entity")# %>% 
-# filter(!is.na(Total_USD))
-
-# Get the NA's to be grey
-Grey_land <- World_sf_si_land %>% 
-  filter(is.na(Bins))
-
-```
-
-### EEZ Map of Transboundary Species
-
-Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country
-
-```{r Territory_Map_Round_Revenue, eval =F, echo =F}
-
-# Create labels for legend
-Bins_Trans <- Transboundary_Spp %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Bins_Rev <- Revenue_Country %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
-Labels_Rev <- c("(1-10]",paste(Bins_Rev[2:5]))
-
-# Make map
-Map <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
-  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
-  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
-  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-                                  "#00A08A",#"#00A08A", #green
-                                  "#F2AD00",#"#F2AD00", # Yellow
-                                  "#F98400",#"#F98400", #Orange
-                                  "#FF0000"#,"#FF0000" #Red
-  ),
-  na.translate = F
-  ) +
-  ggtheme_map() +
-  # Transboundary labels
-  annotate("text", 
-           x =(c(-85.5,-30,25,81,136)+5),
-           y = -93.5,
-           label = Labels_Trans, 
-           color="black", 
-           size=3, 
-           angle=0, 
-           # fontface="bold",
-           hjust=0) +
-  # Revenue labels
-  annotate("text", 
-           x =(c(-85.5,-31,20,75,131)+5),
-           y = -110,
-           label = Labels_Rev, 
-           color="black", 
-           size=3, 
-           angle=0, 
-           # fontface="bold",
-           hjust=0) +
-  # Legend Titles
-  annotate("text", 
-           x =-180,
-           y = -93.5,
-           label = "Transboundary Spp. (n)", 
-           color="black", 
-           size=3, 
-           angle=0, 
-           fontface="bold",
-           hjust=0) +
-  annotate("text", 
-           x =-180,
-           y = -110,
-           label = "Revenue (Million USD)", 
-           color="black", 
-           size=3, 
-           angle=0, 
-           fontface="bold",
-           hjust=0) +
-  theme(
-    legend.box.margin = margin(t = -54, l = 130),
-    legend.text = element_blank(),
-  ) +
-  guides(fill = guide_legend(nrow = 1))
-
-####___________________________###
-### Now create the Two circluar bar plots
-####___________________________###
-
-# Revenue Plot
-
-# Set color pal
-pal <- wes_palette("Zissou1",100,type = "continuous")
-
-# Set plot limits
-max_lim <- max(Subregion_Data_Trans$Total_USD_sum) +10
-
-Rev_Plot <- ggplot(
-  # Regional plots
-  data = Subregion_Data_Trans, 
-  aes(
-    x=reorder(id,Total_USD_sum),
-    y=Total_USD_sum, 
-    fill=Total_USD_sum
-  )
-) +    
-  ylim(-1500, max_lim) +
-  geom_bar(stat="identity") +
-  # Regional averages
-  geom_point(data = Subregion_Data_Trans,
-             aes(
-               x=reorder(id,Total_USD_sum),
-               y=Total_USD_m
-             ),
-             colour = "black",
-             alpha = 0.5
-  ) +
-  # Regional sds
-  geom_errorbar(
-    aes(
-      ymin=ifelse(Total_USD_m-Total_USD_sd <= 0,0,Total_USD_m-Total_USD_sd), # sets lower to 0
-      ymax=Total_USD_m+Total_USD_sd
-    ), 
-    width=.2,
-    position=position_dodge(.9),
-    alpha = 0.5) +
-  # Looking good
-  theme_minimal() +
-  theme(
-    legend.position = c(0.73,0.60),
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = margin(0,-10,-6,-10,"cm")
-  )  +
-  # Base line
-  # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
-  #              colour = "black", size=0.1, inherit.aes = FALSE) +
-  coord_polar(start = 0) + 
-  geom_text(data=label_data_rev, 
-            aes(x=id,
-                y=Total_USD_sum+10,
-                label=sub_region,
-                hjust=hjust), 
-            color="black",
-            fontface="bold",
-            size=2, 
-            angle= label_data_rev$angleb, 
-            inherit.aes = FALSE) +
-  scale_fill_gradientn("",
-                       colours = pal,
-                       limits = c(0,16500),
-                       breaks = seq(0,16000,4000)) +
-  guides(fill = guide_colorbar(label.position = "left")
-  )
-
-###____________###
-### Catch plot
-###____________###
-max_lim <- max(Subregion_Data_Trans$fishing_entity_catch_sum) +1
-
-Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
-                     aes(x=reorder(id,fishing_entity_catch_sum),
-                         y=fishing_entity_catch_sum, 
-                         fill=fishing_entity_catch_sum
-                     )
-) +    
-  ylim(-2.1, max_lim) +
-  geom_bar(stat="identity") +
-  # Regional averages
-  geom_point(data = Subregion_Data_Trans,
-             aes(
-               x=reorder(id,fishing_entity_catch_sum),
-               y=fishing_entity_catch_m
-             ),
-             colour = "black",
-             alpha = 0.5
-  ) +
-  # Regional sd's
-  geom_errorbar(
-    aes(
-      ymin=ifelse(fishing_entity_catch_m-fishing_entity_catch_sd <= 0,0,fishing_entity_catch_m-fishing_entity_catch_sd),
-      ymax=fishing_entity_catch_m+fishing_entity_catch_sd
-    ), 
-    width=.2,
-    position=position_dodge(.9),
-    alpha = 0.5) +
-  theme_minimal() +
-  theme(
-    legend.position = c(0.1,0.60),
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = margin(0,-10,-6,-5,"cm")
-  )  +
-  # Base line
-  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
-  #              colour = "black", size=0.1, inherit.aes = FALSE) +
-  coord_polar(start = 0) + 
-  geom_text(data=label_data_catch, 
-            aes(x=id,
-                y=fishing_entity_catch_sum+0.1,
-                label=sub_region,
-                hjust=hjust), 
-            color="black",
-            fontface="bold",
-            size=2, 
-            angle= label_data_catch$angleb, 
-            inherit.aes = FALSE) +
-  scale_fill_gradientn("",
-                       limits = c(0,16.5),
-                       breaks = seq(0,16,4),
-                       colours = pal
-
-  )
-
-## Joining everything in one ploit
-
-plot <- ggdraw() +
-  # map
-  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
-  # Revenue circular
-  draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
-  # Catch circular
-  draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
-  # Labeks
-  draw_plot_label(label = c("A", "B"), 
-                  size = 20,
-                  x = c(0, 0), 
-                  y = c(1, 0.45)
-  ) +
-  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
-                  size = 8,
-                  x = c(0.330,0.485), 
-                  y = c(0.31,0.29)
-  )
-
-save_plot(
-  paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
-  # "Plot.png",
-  plot,
-  base_height = 8,
-  base_width = 8
-)
-
-```
-
-```{r Territory_Map_Round_Catch, eval =F, echo =F}
-
-# Get Catch data for mapping (Supplemental materials)
-Catch_Breaks <- c(-1,10,100,1000,5000,10000)
-
-Catch_Country <- SAU_Catch_Data %>%
-  group_by(eez_name) %>%
-  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>%
-  group_by(fishing_entity) %>%
-  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
-  mutate(
-    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-    Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
-    Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
-                    labels = c('super low', 'low','median','high','super high'))
-  ) %>% 
-  filter(fishing_entity_catch > 0)
-
-# Create labels for legend
-Bins_Trans <- Transboundary_Spp %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Bins_Catch <- Catch_Country %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
-Labels_Catch <- c("(1-10]",paste(Bins_Catch[2:5]))
-
-# Transboundary Species shapefile
-World_sf_si <- World_sf %>%
-  st_transform(crs = 4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")
-
-# Total catch/Revenue shapefile
-World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-  left_join(Catch_Country, by ="fishing_entity")
-
-# Get the NA's to be grey
-Grey_land <- World_sf_si_land %>% 
-  filter(is.na(Bins_Plot))
-
-# Make map
-Map <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,fishing_entity_catch)), colour = "grey80",size = 0.1) +
-  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
-  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
-  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-                                  "#00A08A",#"#00A08A", #green
-                                  "#F2AD00",#"#F2AD00", # Yellow
-                                  "#F98400",#"#F98400", #Orange
-                                  "#FF0000"#,"#FF0000" #Red
-  ),
-  na.translate = F
-  ) +
-  ggtheme_map() +
-  # Transboundary labels
-  annotate("text",
-           x =(c(-85.5,-30,25,81,136)+5),
-           y = -93.5,
-           label = Labels_Trans,
-           color="black",
-           size=3,
-           angle=0,
-           # fontface="bold",
-           hjust=0) +
-  # Catch labels
-  annotate("text",
-           x =(c(-85.5,-31,20,75,131)+5),
-           y = -110,
-           label = Labels_Catch,
-           color="black",
-           size=3,
-           angle=0,
-           # fontface="bold",
-           hjust=0) +
-  # # Legend Titles
-  annotate("text",
-           x =-180,
-           y = -93.5,
-           label = "Transboundary Spp. (n)",
-           color="black",
-           size=3,
-           angle=0,
-           fontface="bold",
-           hjust=0) +
-  annotate("text",
-           x =-180,
-           y = -110,
-           label = "Catch (Thousand tons)",
-           color="black",
-           size=3,
-           angle=0,
-           fontface="bold",
-           hjust=0) +
-  theme(
-    legend.box.margin = margin(t = -54, l = 130),
-    legend.text = element_blank(),
-  ) +
-  guides(fill = guide_legend(nrow = 1))
-
-ggsave(
-  plot = last_plot(),
-  width = 8,
-  height = 5,
-  units = "in",
-  filename = "S1_Catch_EEZ.png"#,
-  # path = Figures_Path
-)
-
-```
-
-```{r Territory_Map_Round_Weighted, eval =F, echo =F}
-
-# Get Catch data for mapping (Supplemental materials)
-Catch_Breaks <- c(-1,10,100,1000,5000,10000)
-
-Catch_Country <- SAU_Catch_Data %>%
-  group_by(eez_name) %>%
-  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>%
-  group_by(fishing_entity) %>%
-  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000) %>% # thousand tones
-  mutate(
-    # fishing_entity = ifelse(fishing_entity == "USA","United States of America",
-    #                                ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
-    Bins = cut(fishing_entity_catch,breaks = Catch_Breaks),
-    Bins_Plot = cut(fishing_entity_catch,breaks = Catch_Breaks,
-                    labels = c('super low', 'low','median','high','super high'))
-  ) %>% 
-  filter(fishing_entity_catch > 0)
-
-# Create labels for legend
-Bins_Trans <- Transboundary_Spp %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Bins_Catch <- Catch_Country %>% 
-  arrange(Bins) %>% 
-  pull(Bins) %>% 
-  unique()
-
-Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
-Labels_Catch <- c("(1-10]",paste(Bins_Catch[2:5]))
-
-# Transboundary Species shapefile
-World_sf_si <- World_sf %>%
-  st_transform(crs = 4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")
-
-# Total catch/Revenue shapefile
-World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-  left_join(Catch_Country, by ="fishing_entity")
-
-# Get the NA's to be grey
-Grey_land <- World_sf_si_land %>% 
-  filter(is.na(Bins_Plot))
-
-# Make map
-Map <- ggplot() +
-  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,fishing_entity_catch)), colour = "grey80",size = 0.1) +
-  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
-  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
-  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
-                                  "#00A08A",#"#00A08A", #green
-                                  "#F2AD00",#"#F2AD00", # Yellow
-                                  "#F98400",#"#F98400", #Orange
-                                  "#FF0000"#,"#FF0000" #Red
-  ),
-  na.translate = F
-  ) +
-  ggtheme_map() +
-  # Transboundary labels
-  annotate("text",
-           x =(c(-85.5,-30,25,81,136)+5),
-           y = -93.5,
-           label = Labels_Trans,
-           color="black",
-           size=3,
-           angle=0,
-           # fontface="bold",
-           hjust=0) +
-  # Catch labels
-  annotate("text",
-           x =(c(-85.5,-31,20,75,131)+5),
-           y = -110,
-           label = Labels_Catch,
-           color="black",
-           size=3,
-           angle=0,
-           # fontface="bold",
-           hjust=0) +
-  # # Legend Titles
-  annotate("text",
-           x =-180,
-           y = -93.5,
-           label = "Transboundary Spp. (n)",
-           color="black",
-           size=3,
-           angle=0,
-           fontface="bold",
-           hjust=0) +
-  annotate("text",
-           x =-180,
-           y = -110,
-           label = "Catch (Thousand tons)",
-           color="black",
-           size=3,
-           angle=0,
-           fontface="bold",
-           hjust=0) +
-  theme(
-    legend.box.margin = margin(t = -54, l = 130),
-    legend.text = element_blank(),
-  ) +
-  guides(fill = guide_legend(nrow = 1))
-
-ggsave(
-  plot = last_plot(),
-  width = 8,
-  height = 5,
-  units = "in",
-  filename = "S1_Catch_EEZ.png"#,
-  # path = Figures_Path
-)
-
-```
-
-### China, US, Russia, and Peru
-
-```{r Map_Particulars, eval =F, echo =F}
-
-PeRu <- c("Peru", "Russian Federation", "Chile", "USA")
-
-Total_PeRu <- Revenue_Country %>% 
-  filter(fishing_entity %in% PeRu) %>% 
-  select(1:2)
-
-Rev_PeRu <- sau_eez_fes %>% 
-  filter(fishing_entity %in% PeRu) %>% 
-  group_by(fishing_entity_id, fishing_entity) %>% 
-  summarise(n=n()) %>% # Get all of the fishing entity and id
-  select(-n) %>% 
-  full_join(Tresholded_T_Data,
-            by = "fishing_entity") %>% 
-  group_by(fishing_entity_id,
-           fishing_entity,
-           taxon_key) %>% 
-  summarise(n()) %>% # get each taxa per nation
-  left_join(SAU_Revenue_Data,
-            by = c("fishing_entity_id","taxon_key")) %>% 
-  left_join(Exploited_Species) %>% 
-  group_by(fishing_entity) %>%
-  top_n(16,mean_value) %>%
-  select(2,3,5) %>% 
-  mutate(mean_value = mean_value/1000000) %>% # Million of USD
-  left_join(Total_PeRu,
-            by = "fishing_entity") %>% 
-  mutate(Ratio = mean_value/Total_USD*100)
-
-Rev_PeRu %>% 
-  group_by(fishing_entity) %>% 
-  summarise(sum(Ratio))
-
-### Total from the top 5
-
-Top5 <- c("Peru", "Russian Federation", "Chile", "USA","China")
-
-Total_PeRu <- Revenue_Country %>% 
-  filter(fishing_entity %in% PeRu) %>% 
-  select(1:2) %>% 
-  group_by() %>% 
-  summarise(sum(Total_USD)) %>% 
-  pull()/79745
-
-```
-
-### Statistical differences
-
-We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.
-
-```{r statistics_fig1, eval = F, echo = T}
-
-### Using ANOVA to estimate significan differences within regions for revenue and catch of transboundary species
-
-### Prepare Data
-Subregion_Data_stats <- Revenue_Country %>% 
-  left_join(Catch_Country,
-            by = "fishing_entity") %>% 
-  left_join(UN_Regions,
-            by = "fishing_entity") %>% 
-  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
-  select(fishing_entity,sub_region,Total_USD,fishing_entity_catch)
+  select(fishing_entity,sub_region,Variable,Value) %>% 
+  filter()
+
+# ### Prepare Data
+# Subregion_Data_stats <- Revenue_Country %>% 
+#   left_join(Catch_Country,
+#             by = "fishing_entity") %>% 
+#   left_join(UN_Regions,
+#             by = "fishing_entity") %>% 
+#   mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
+#   select(fishing_entity,sub_region,Total_USD,fishing_entity_catch)
 
 # Revenue ANOVA
-Rev_aov <- aov(Total_USD~sub_region, data = Subregion_Data_stats)
+Subregion_Rev_stats <- Subregion_Data_stats %>% 
+  filter(Variable == "value")
+
+Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
 Rev_aov
@@
 
-Catch_aov <- aov(fishing_entity_catch~sub_region, data = Subregion_Data_stats)
+Subregion_Catch_stats <- Subregion_Data_stats %>% 
+  filter(Variable == "catch")
+
+Catch_aov <- aov(fishing_entity_catch~sub_region, data = Subregion_Catch_stats)
 Catch_aov
@@
 TukeyHSD(Catch_aov)
+
+# Weight ANOVA
+Subregion_Weigh_stats <- Subregion_Data_stats %>% 
+  filter(Variable == "value_weight")
+
+Weight_aov <- aov(Value~sub_region, data = Subregion_Weigh_stats)
+Weight_aov
+summary(Weight_aov)
+
+#  Df Sum Sq Mean Sq F value  Pr(>F)   
+# sub_region   16   6722   420.1   2.411 0.00289 **
+# Residuals   158  27532   174.3                   
+# ---
+# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+#### There are significant differences. But between what?
+
+#  Post-hoc analysis
+TukeyHSD(Rev_aov)
 ```
@@
 
-```{r Circular_Country_Data, eval = F, echo = F}
+```{r Status_Plot_Data, eval = F, echo = F}
 
@@
 
-# Countries_Data_Plot <- Tresholded_T_Data %>% 
-#   group_by(Territory = CT_fishing_entity) %>% 
-#   summarise(value = length(unique(TaxonKey))) %>% 
-#   left_join(UN_Regions, by ="Territory") %>%
-#   mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-#   rename(FishingRegion=Territory) %>% 
-#   left_join(Clean_sau_eez_fes) %>% 
-#   group_by(individual = fishing_entity,group) %>% 
-#   summarise(Total_trans = sum(value,na.rm=T)) %>% 
-#   mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
-#   filter(!is.na(individual)) %>% 
-#   select(individual,group,value) %>% 
-#   arrange(group,value)
-
-# -------------------------- #
-# Discrete data
-# -------------------------- #
-
-# Discrete_Data_Plot <- Tresholded_D_Data %>% 
-#   summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
-#   mutate(value = ifelse(value <= -100,-100,value)) %>% 
-#   left_join(UN_Regions, by ="Territory") %>%
-#   mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-#   filter(!is.na(Territory)) %>% 
-#   select(individual = Territory,
-#          group,
-#          value)
-
-# -------------------------- #
 # Stock status Data
-# -------------------------- #
 
@@
 
+# -------------------------- #
+# Discrete data
+# -------------------------- #
+
+Discrete_Status_Data <- Discrete %>% 
+  left_join(Status_Data, 
+            by =c("eez_name","taxon_key")
+  ) %>%
+  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
+  group_by(fishing_entity,status) %>% 
+  summarise(value = length(unique(taxon_key))) %>% 
+  left_join(UN_Regions, by ="fishing_entity") %>%
+  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+  # mutate(value = ifelse(value > 100,100,value)) %>% 
+  filter(!is.na(fishing_entity),
+         !str_detect(fishing_entity, ".\\(.") # remove associated territories
+  ) %>% 
+  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
+  arrange(group,value) %>% 
+  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
+         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
+                              ifelse(observation == "Max Exploited","Category B",
+                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+                              )
+         )
+  ) %>% 
+  group_by(individual,observation,group) %>% 
+  summarise(value = sum(value))
 ```
@@
 
+# -------------------------- #
+# Transboundary species
+# -------------------------- #
+
 Status_Data_Stats <- Status_Data_Plot %>% 
-  filter(observation != "No Category")
-
-# Differences between groups
-Stat_con_aov <- aov(value~group, data = Status_Data_Stats)
-Stat_con_aov
-summary(Stat_con_aov)
-
+  filter(observation != "No Category") %>%
+  mutate(value = abs(value)) %>%
+
+Total_Trans_Status <- Status_Data_Stats %>% 
+  group_by() %>% 
+  summarise(sum = sum(value)) %>% 
+  pull()
+
+Status_Data_Stats %>% 
+  group_by(observation) %>% 
+  summarise_if(is.numeric,
+               .funs = c(Mean="mean",
+                           sd = "sd",
+                          Sum = "sum")
+  ) %>% 
+  mutate(Sum/Total_Trans_Status*100)
+
+# --------------------- #
+### Check for Asumptions
+# --------------------- #
+
+#### Test for normallity 
+Status_Data_Stats %>%
+  ggplot() +
+  geom_histogram(
+    aes(
+      x = value
+    )
+  ) +
+  facet_wrap(~observation)
+
+bartlett.test(value~observation, Status_Data_Stats)
+
+# Differences between categories of transboundary species
+
+Stat_Cat_kt <- kruskal.test(observation~value, data = Status_Data_Stats)
+Stat_Cat_kt
+
+# Post hock test
+kruskalmc(Status_Data_Stats$value,Status_Data_Stats$observation)
+
+# Stat_Cat_aov <- aov(value~observation, data = Status_Data_Stats)
+# Stat_Cat_aov
+# summary(Stat_Cat_aov)
 #           Df Sum Sq Mean Sq F value Pr(>F)    
-# group         5   3148   629.6    1.24  0.289 # NO SIG
-# Residuals   443 224996   507.9
-
-Stat_Cat_aov <- aov(value~observation, data = Status_Data_Stats)
-Stat_Cat_aov
-summary(Stat_Cat_aov)
+# observation   2  22093   11046   52.88 <2e-16 ***
+# Residuals   446  93170     209
+
+# TukeyHSD(Stat_Cat_aov)
+
+# -------------------------- #
+# Discrete species
+# -------------------------- #
+
+# Run anova within discrete speciess
+
+Discrete_Data_Stats <- Discrete_Status_Data %>% 
+  filter(observation != "No Category") %>%
+  mutate(value = abs(value))
+
+Total_Discrete_Status <- Discrete_Data_Stats %>% 
+  group_by() %>% 
+  summarise(sum = sum(value)) %>% 
+  pull()
+
+Discrete_Data_Stats %>% 
+  group_by(observation) %>% 
+  summarise_if(is.numeric,
+               .funs = c(Mean="mean",
+                           sd = "sd",
+                          Sum = "sum")
+  ) %>% 
+  mutate(Propo_Total = Sum/Total_Discrete_Status*100)
+
+#### Test for normallity 
+Discrete_Data_Stats %>%
+  ggplot() +
+  geom_histogram(
+    aes(
+      x = value
+    )
+  ) +
+  facet_wrap(~observation)
+
+bartlett.test(value~observation, Discrete_Data_Stats)
+
+Stat_discrete_cat_kt <- kruskal.test(observation~value, data = Discrete_Data_Stats)
+Stat_discrete_cat_kt
+
+kruskalmc(Discrete_Data_Stats$value,Discrete_Data_Stats$observation)
+
+# ANOVA of Discrete categories
+Stat_discrete_cat_aov <- aov(value~observation, data = Discrete_Data_Stats)
+Stat_discrete_cat_aov
+summary(Stat_discrete_cat_aov)
+
 #             Df Sum Sq Mean Sq F value   Pr(>F)    
-# observation   2 134952   67476   322.9 <2e-16 ***
-# Residuals   446  93192     209
-
-TukeyHSD(Stat_Cat_aov)
+# observation   2   6442    3221   21.86 1.03e-09 ***
+# Residuals   380  55992     147
+
+TukeyHSD(Stat_discrete_cat_aov)
+# 
+#  diff         lwr       upr     p adj
+# Category B-Category A 3.627759 -0.02854633  7.284065 0.0523425
+# Category C-Category A 9.917391  6.31117452 13.523608 0.0000000
+# Category C-Category B 6.289632  2.79874173  9.780522 0.0000835
+
+# ANOVA of Discrete continents
+# Stat_discrete_cont_aov <- aov(value~group, data = Discrete_Data_Stats)
+# Stat_discrete_cont_aov
+# summary(Stat_discrete_cont_aov)
+
+# Df Sum Sq Mean Sq F value Pr(>F)
+# group         5    962   192.4    1.18  0.318
+# Residuals   377  61472   163.1
+
+# -------------------------- #
+# Comparrison bwtween Discrete
+# and Transboundary species
+# -------------------------- #
+
+#### By Category (Manova)
+
+# Use manova to test for a significant effect of Catch category on discrete and transboundary species simultaneously. Takes into account possible correlations between dependent variables.
+# Decreases Tipe I errors
+
+Manova_Differences <- Status_Data_Stats %>% 
+  rename(Trans_value = value) %>% 
+  left_join(Discrete_Data_Stats, by = c("individual","observation","group")
+  ) %>% 
+  rename(Discrete_value= value) %>% 
+  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value))
+
+#### Test for normallity
+
+Manova_Differences %>% 
+  gather("cat","val",Trans_value,Discrete_value) %>% 
+  ggplot() +
+  geom_histogram(
+    aes(
+      x = val
+    )
+  ) +
+  facet_wrap(~observation+cat)
+
+### Correlation?
+
+plot(Manova_Differences$Trans_value~Manova_Differences$Discrete_value)
+
+cor(Manova_Differences$Trans_value,Manova_Differences$Discrete_value)
+
+mano <- manova(cbind(Discrete_value,Trans_value) ~ observation, data = Manova_Differences)
+summary(mano)
+#     Df  Pillai approx F num Df den Df    Pr(>F)    
+# observation   2 0.20992   26.151      4    892 < 2.2e-16 ***
+# Residuals   446             
+summary.aov(mano)
+# Response Discrete_value :
+#              Df Sum Sq Mean Sq F value    Pr(>F)    
+# observation   2   6918  3458.9  25.684 2.769e-11 ***
+# Residuals   446  60063   134.7                      
+# ---
+# 
+# 
+#  Response Trans_value :
+#              Df Sum Sq Mean Sq F value    Pr(>F)    
+# observation   2  22093 11046.3  52.878 < 2.2e-16 ***
+# Residuals   446  93170   208.9                      
+# ---
+
+#### Run non-parametric to make sure (same)
+
+kruskal.test(Trans_value~Discrete_value, data = Manova_Differences)
+# Kruskal-Wallis chi-squared = 296.66, df = 43, p-value < 2.2e-16
+
+### Multiple wilcox/t.test
+
+Manova_Differences %>% 
+  # group_by(observation) %>% 
+  ungroup() %>% 
+  select(2,4,5) %>% 
+  do(wil = aov(.$Trans_value~.$Discrete_value)) %>% 
+  tidy(wil) %>% 
+  View()
+
+# Also significantly different
+
+#### Chi square maybe???
+
+Chi_data <- Manova_Differences %>% 
+  ungroup() %>% 
+  group_by(observation) %>% 
+  summarise_if(is.numeric,sum) %>% 
+  select(-observation)
+
+chisq.test(Chi_data)
 
@@
 
-Mackerel_Rev <- SAU_Revenue_Data %>% 
+Mackerel <- Clean_sau_eez_fes %>% 
+  group_by(fishing_entity, fishing_entity_id) %>% 
+  summarise(n()) %>% 
+  left_join(SAU_Sampled_Data, by = "fishing_entity_id") %>% 
   filter(taxon_key == 600118,
@@
   ) %>% 
-  group_by() %>% 
-  summarise(sum(mean_value))/1000000
-
-Mackerel_Catch <- SAU_Catch_Data %>% 
-  left_join(Clean_sau_eez_fes) %>% 
-  filter(taxon_key == 600118,
+  group_by(Variable) %>% 
+  summarise(Mac = sum(Value))
+
+### Mackerel percentage of region's total catch
+
+Conflict_Values <- Clean_sau_eez_fes %>% 
+  group_by(fishing_entity, fishing_entity_id) %>% 
+  summarise(n()) %>% 
+  left_join(SAU_Sampled_Data, by = "fishing_entity_id") %>% 
+  filter(
          fishing_entity %in% Conflict_nations
   ) %>% 
-  group_by() %>% 
-  summarise(sum(total_catch))/1000
+  group_by(Variable) %>% 
+  summarise(Conflict= sum(Value))
+
+Mackerel %>% 
+  left_join(Conflict_Values) %>% 
+  mutate(Mac/Conflict*100)
 

### 2020-03-03 Manuscript_Draft.Rmd
Finalized comments from co-authors

--- 2020-02-11 Manuscript_Draft.Rmd
@@
 ---
-title: "Fish do not need visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)"
+title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
 author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
@@
 # subtitle: "[DRAFT DO NOT SHARE]"
-subtitle: "Most neighbour nations share marine species (38/40 characters)"
+subtitle: "Most neighbour nations share marine species"
 output:
@@
 
-Species shared by neighboring nations contribute over 50% of marine capture fisheries' landings and revenue with direct implications for fisheries management.
+Marine species shared by neighboring nations contribute to over 50% of catches and fishing revenue with direct implications for fisheries management.
 
-# Field code (Max. 2)
+<!-- # Field code (Max. 2) -->
 
-- *Fisheries*
+<!-- - *Fisheries* -->
 
-# Abstract (125/~125 words)
+# Abstract (150/~125 words)
 <!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 This represents a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits.
-Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine fish species that are shared between neighbouring nations.
-We found that 64% of the world’s catches in the last decade, amounted to 50% of fisheries revenue, comes from 633 shared species.
-Some countries received over 70% of their benefits from a few shared resources.
+Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighbouring nations.
+We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (47 million tonnes) and 78.5% of fisheries revenue (USD 65 billion) in last decade.
+Some countries received over 70% of their economic benefits from a few shared resources.
 This study highlights the large and under-recognized challenge in achieving international fisheries management goals, particularly as species redistribute under climate change.
 
-# Main Article
+# Main Article (3200/~2500 words)
 <!-- # Introduction (~555/500 words) -->
@@
 Distributions of marine species around the world are not constrained by human-made boundaries; rather they are shaped by biotic and abiotic factors defined by their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
-Thus, a species can have a broader distribution (cosmopolitan), or be endemic [@Nelson:2016kk].
+Thus, a species can have a broader distribution (cosmopolitan) or be endemic [@Nelson:2016kk].
 However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
@@
 Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear.
-Early data limitations allowed only for an informed guessed [@Caddy:1997ue], while recent estimations, followed a litterature review and catch data to address this issue [@Teh:2015gd].
-However, up to date, no method has included the actual distribution of species.
-We hipothesize that the methodological constraints of preious work has underestimate the contribution of these species to global catch and revenue and that the proportoin of transboundary species is larger than previouslly estimated.
-Thus, we aimed to estimate the number of exploited marine fish species shared by neighbouring countries and determine their contribution to global catch and fisheries revenue.*Moreover, we estimate their importance in terms of catch and revenue by country and also carry the analysis at the ecological level.
+Early data limitations on species' distributions allowed only for an informed guess on the number of transboundary species [@Caddy:1997ue] while a more recent study explored the historical contribution of shared stocks following a litterature review [@Teh:2015gd].
+Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
+Here, we aimed to estimate the number of exploited marine species shared by neighbouring countries and determine their contribution to global and regional catch and fisheries revenue.
+Moreover, we categorize species according to their exploitation rate while identifying differences by habitat preference.
+We hipothesize that the methodological constraints of preious work has resulted in an underestimation of the contribution of these species to global catch and revenue, and that the proportoin of transboundary species is larger than previouslly estimated.
 
-We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reported to FAO, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary.
-First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.
-we did not include the high seas).
-Secondly, we considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
-The third criteria determined whether a species was exploited within a given grid cell using spatially explicit catch data.
-A species was considered as present in a grid cell if both predicted species occurrences and catch data were positive.
-Finally, we determined a spatial threshold based on the proportion of the species' distribution within each neighboring EEZs to confirm occurance in both EEZs.
-
-Once transboundary species were identified, we estimated their contribution to fisheries catch and revenues and categorized them according to catch trends.
+We overlaid the known distribution of 938 commercially valuable marine species responsable for an average of 96.5% of global EEZ catch reconstruced by the *Sea Around Us* at the species level between 2005 and 2014, and the EEZ of 153 coastal countries.
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
 While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research has suggested strong connectivity between stocks, even when separated by thousand of kilometers [@Ramesh:2019va].
-<!-- **and providing additional ecological ground for...** -->
-
+Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
+For this analysis we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.
+we did not include the high seas).
+We relay in multiple data sources including occurance, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
+Finally, each neighbouring EEZ had to have more than 25% of a species' distribution in order for the species to be categorized as transboundary.
 <!-- ## Results and discussion (~1000 words) -->
 
-We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed.
-Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **92%** of the EEZ-derrived catches reported to FAO, and generating USD **79,745** million in fishing revenue.
-This is equivalent to **49.8% (73.16% according to new numbers)** of the global fishing revenue of the same period.
-These values are more than double the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd], underscoring the importance of transboundary species at the global level.
+We identified 633 transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing 67.5% of the species analyzed.
+Between 2005 and 2014, national fleets targeting transboundary species within EEZs landed an average of 47.6 million tonnes, representing 79.9% of the EEZ-derrived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
+This is equivalent to 78.5% of the global fishing revenue of the same period.
+These values are more than the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd].
+Based on our assesment (see Methods), 590 transboundary species were also identified as discrete species.
+This is the case of species such as Peruvian anchoveta (*Engraulis ringens*) that is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile.
+The contribution of discrete species (e.g.
+the anchoveta catch of Ecuador) was 14.8 million tonnes representing USD 22,167 million in fishing revenue.
+Within these species, 305 species were considered exclusiveley discrete species, that is, they could be fished by neighbouring nations but were not considered transboundary.
+These species represented only 2.7 million tonnes and 3,691 million USD between 2005 and 2014.
+These results underscore the importance of transboundary species at the global level (Fig.
+1).
 
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and they contribution to fishing catch and revenue.** A) The number of species is represented in the EEZ while revenue from these species fished within the EEZ is represented in the land polygon.
-B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.
-Points = mean +- sd."}
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary marine species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by colour coding of EEZs and land polygons, respectively.
+B) Contribution of tranbsoundary species to regional revenue (left) and catch (right).
+Regions according to the United Nations sub-regions.
+Points = mean +- sd.
+Revenue in 2010 real USD"}
 
@@
 grid.raster(img)
+
 ```
@@
 Points = mean +- sd.
-Revenue in 2010 real USD](./Figures/Fig1.png)
+Revenue in 2010 real USD.](./Figures/Fig1.png)
 
-<!-- **NOTE: EXPLORE THE REGIONAL SEGMENTATION YOU MADE** -->
-
-We aggregate countries according to the United Nations sub-regions (**Supplements**) and found that transboundary species are particularly economically important for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+We aggregate countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *DF*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
 China (USD 6,279 million) in E.
@@
 America contribute 55% and 83% to their respective region's revenue, respectively.
-Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with the most fishing revenue generated from transboundary species.
+Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with the most fishing revenue generated from transboundary species in the last decade.
 These five nations are responsible for 30% of the fishing global revenue from transboundary species.
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5,000 thousand tones each on average between 2005 and 2014 (**Supplemental figure Trans_Catch_MAP**).
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5,000 thousand tones each on average between 2005 and 2014 (Fig S1).
 Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and accounting for 79% of the transboundary species production.
@@
 Despite the large catch volume of Peru and Russia, regional catches are only significantly different in E.
-Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
-Differences in tansboundary fisheries can also be ilustrated in terms of catch-revenue/EEZ $km^2$ (**Supplements_Kmproportion**).
-As an example, Eastern Europe who's EEZ is the $9^{th}$ larger of the groups analized (**Supplemental table**) shoots out as having the most revenue (XXX) and catch (XXX) of species per EEZ area, significantly differing from the rest (**Statistics**).
+Asia (one-way ANOVA; *Df*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons harvested in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
+Differences in tansboundary fisheries can also be ilustrated in terms of catch-revenue/EEZ $km^2$ (Figure S2).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analized (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tonnes per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
 
-<!-- However, some regions like the Caribbean stand out as they have multiple small EEZs and belonging to a single LME (in this case Tropical Northwestern Atlantic), yet their number of transboundary species is lower than the preiouslly mentioned regions.
-This is likeley an effect of the reporting -->
-
-We determined the exploitation category of transboundary fisheries according to each country's catch [@Kleisner:2011wn] and also found significant differences among exploitation categories (one-way ANOVA *F*(5,446), *f* = 324.5, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all) with most species fished to levels below 50%, sometimes lower than 10%, of their historical maximum catch (Fig.2).
-All regions conformed to this trend, except for Oceania, with no significant difference across continents (one-way ANOVA *F*(5,443), *f* = 1.24, *p* = 0.289, $\alpha$ = 0.05).
-While many environmental and social-economic factors such as temperature, markets, fishing policies affect catch volume [@Pauly:2013gs; @Branch:2008kk] previous studies demonstrated that the trends can be used to infer whether a stock is over-exploited or collapsed [@Kleisner:2011wn].
-Thus suggesting that the current global exploitation rate of transboundary species could be over the maximum sustainable yield [@Kleisner:2011wn; @Pauly:2013gs].
-
-<!-- **NOTE: THIS (L 118) PARAGRPAH NEEDS WORK** -->
+We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
+2) [@Kleisner:2011wn].
+Previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
+Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
+We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,446) = 53.9, *p* < 0.001).
+In the case of discrete species, only Category C is significantly different than the rest (one-way ANOVA, *Df*(2,446) = 52.88, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.001).
+On the other hand, for transboundary species, all categories are significantly different (one-way ANOVA, *Df*(2,446) = 52.88, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all categories).
+While many environmental and social-economic factors (e.g.
+temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk], this result suggests that the management of discrete species could be better off as the variation between categories A and B are closer (*p* = 0.052) than for transboundary species (*p* = 0.002).
 
@@
 Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Bailey:2010ga].
-Examples of successful co-management include Canada and the United States over Pacific salmon [@REF] and Pacific halibut [@REF], Norway and Russia over Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and capelin (*Mallotus villosus*) in the Barents Sea [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Examples of successful co-management include Canada and the United States over Pacific salmon [@Song:2017va], Norway and Russia over Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and capelin (*Mallotus villosus*) in the Barents Sea [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
 Lack of collaboration over shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], and reduce the future profitability potential of the fishery [@Merino:2007jz].
-Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf] and that there are specific cases where cooperation might not be the best strategy [@REF].
-Collaboration can also reduce conflict between nations over shared resources as climate change shifts the distribution of species.
+Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf] and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
+Collaboration can also reduce conflict between nations over shared resources as climate change shifts the distribution of species creating tension between countries.
 Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the US, China and Russia [@Spijkers:2019cz].
 For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations were introduced to compensate for losses [@Munro:2002uf].
-Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributes 698.3 thousand tonnes to catches and USD 968 million in revenue to the countries involved in the dispute.
+Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributed an average of 598.4 thousand tonnes to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+The relatively small contribution of mackrell to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
 In addition to past and present conflicts, climate change is likely to exacerbate conflicts over transboundary species due to shifts in their distribution, requiring flexible agreements that accommodate future uncertainties [@Pinsky:2018cb].
@@
 <!-- **NOTE: DOUBLE CHECK REFERENCES eddie and derek]** -->
-<!-- **NOTE: add %% to mackrel** -->
-
-<!-- First steps for shared management start with information sharing, then this and that. Proper management treaties not only have but can also be stronger in the fase of a canging climate. -->
 
 Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species lke greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as 'transboundary') was significantly different from other groups (one-way ANOVA *F*(5,109), *f* = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,109) = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
@@
 
-![Fig. 3. EEZ range of ransboundary species. Showing only species that share > 20 countries](./Figures/Fig3.png)
+![Fig.
+3.
+Number of EEZs shared by transboundary species.
+A) Number of EEZs by species organized by associated habitat according to FishBase.
+Showing only species that share > 20 EEZs.
+B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig3.png)
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migraroty pelagic fish species are managed by Regional Fisheries Management Organizations (RFMOs).
+Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory pelagic fish species are managed by Regional Fisheries Management Organizations (RFMOs).
 Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
-We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (**Supplemental figure RFMO_MAP**).
+We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
+3).
 The effectiveness of RFMOs responsible for managing high migratory stocks has been previously questioned [@CullisSuzuki:2010fi; @Lodge:2007bt].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested ($B/B_{MSY} > 1$ and $F/F_{MSY} < 1$) with only three stocks currently considered as overfished ($B/B_{MSY} < 1$ and $F/F_{MSY} > 1$) [@Pons:2016ep].
-In the other hand, less mobile species are often managed at the national level due to localized populations, however, the potential boundary-crossing of these species must not be ignored [@Payne:2008vm].
-The world of fisheries is highly connected trough larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested with only three stocks currently considered as overfished [@Pons:2016ep].
+In the other hand, species with narrower ranges are often managed at the national level due to localized populations, however, the potential boundary-crossing of these species must not be ignored [@Payne:2008vm].
+The world of fisheries is highly connected through larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
 In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Levin:2018in; @Payne:2008vm].
-
-Many coastal communities, particularly in developing regions, are highly dependent on subsistance fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf; @Cabral:2018hc].
+Many coastal communities, particularly in developing regions, are highly dependent on subsistance fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf].
 For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-3B) are among the highest fish consuption countries (> 10 g of fish protein per capita per day) [@FAO].
+3B) are among the highest fish consuption countries (> 10 g of fish protein per capita per day) [@FAO:2018KK].
 In these countries, both pelagic and reeef fishes contribute substantially to both local food security and livelehood [@Cabral:2018hc].
@@
 
-<!-- **NOTE: Colette will search for a reference related a weird comment "arecenWCPF assessment highlight tt tuna in the Pacific e sustsinabl fisd, but oher species  socks in ot regionsre .
-I will dig up e reference and send it to you - just to make sure  the irmati overlaps"** -->
-
-<!-- [@https://www.ffa.int/nauru_agreement]  -->
-
 In our analyses we did not seek to include climate change as a driver of species’ distribution.
 Distribution shifts are the most commonly recorded response of marine species to the effects of climate change - chiefly warming - in the ocean [@Poloczanska:2016kk].
-Catch composition might have already changed in the last five decades [@Cheung:2013gk], and will continue throuugh the $21^{st}$ century [@Cheung:2016jd].
+Catch composition might have already changed in the last five decades [@Cheung:2013gk] and will continue throuugh the $21^{st}$ century [@Cheung:2016jd].
 Previous study projected that climate change will bring at least one new transboundary species per EEZ in the future [@Pinsky:2018cb], while also change the proportion of the distribution (e.g.
@@
 
-Our study identified species currently shared by neighbouring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
-Our results show that captures and revenues from shared species are higher than previously estimated and particularly important to countries in Northern America and Eastern Asia.
-This result highlights the importance of these fisheries and their potential contribution to regional food security and wellbeing.
-Moreover, the vast majority of transboundary species are harvest at low rates with no geographic variation.
-Previous work has found that collaboration will result in better outcomes for shared marine resources.
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
+Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated.
+This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
+Moreover, we show significant differences in the management of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
+Previous work has found that collaboration will result in better outcomes for shared marine resources [@Bailey:2010ga].
 Thus, countries should pay specific attention in the management of the identified transboundary stocks potentially creating collaborative management plans.
@@
 
-To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their distributions.
-To this end, we used four data sources of species-distributions: (*i*) occurence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**).
+To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the reconstructed list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their current distributions based on an average from 1970-2000.
+The total number of species analized was 938 representing 54% of the average catch reported by the *Sea Around Us* between 2005 and 2014, including generalized categories such as *Marine fish not identified* or *Mollusca*.
+However, because we carried the analysis at the species level, we did not include such generalized categories in our comparrisons.
+Our final sample represents 63.2% of identified species, accounting for 96.52% of the catch identified at the species' level.
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
 Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result.
 Only commercial fished species with data from all four sources were included in the analysis.
-The final dataset comprised 968 marine species (including anadromous species like salmononids), **XX%** of the total number of reported marine species in the SAU database and **XX%** of the reported marine taxa of included by the Food and Agricultural Organization of the United Nations (FAO).
+
+```{r Data_Table, eval = T, echo = F}
+
+Source <- c(
+  "Occurrence data",
+  "Ecological niche model",
+  "Species distribution model",
+  "Catch data"
+)
+
+Abreviation <- c(
+  "Occurrence",
+  "ENM-Nereus",
+  "SDM-SAU",
+  "Catch-SAU"
+)
+Main_Method <- c(
+  "Occurrence data from multiple sources",
+  "Environmental niche model based on environmental variables and different model algorithms",
+  "Species distribution model based on species traits",
+  "Spatial catch allocation based on country-by-country reconstructions"
+)
+
+Sources <-  c(
+  "Reygondeau, 2019",
+  "Asch et al., 2017 & Reygondeau, 2019",
+  "Palomares et al., 2016",
+  "Zeller et al., 2016"
+)
+
+data.frame(Source,
+           Abreviation,
+           Main_Method,
+           Sources) %>% 
+  rename("Main Method"=Main_Method) %>% 
+  kable("latex", booktabs = T,
+        caption = "Summary of data sources to estimate species' distributions.
+All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
+All data is publically available, see references for details.") %>%
+  kable_styling(full_width = F) %>%
+  column_spec(2,width = "8cm") %>% #wraps text in column2
+  column_spec(3,width = "3cm") #%>% #wraps text in column2
+
+```
 
@@
 
-### *Occurence data*
+### *Occurrence data*
 
-Occurrence data was collected from five publicly available repositories: Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+Occurrence data was collected from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
@@
 
-The SDM-SAU model follows a five-steps process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Palomares:wg].
-For each commercial species, the model first uses the FAO major fishing areas and countries' EEZs to determine a broad distribution.
+The SDM-SAU model follows a five-steps process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Pauly:2016uz].
+For each commercial marine species, the model first uses the FAO major fishing areas and countries' EEZs to determine a broad distribution.
 It then uses life history information to delimit its range within the FAO fishing area (e.g., thermal preference, depth limit).
@@
 the latitudinal region where a species is not seen in between poles) is estimated for each species.
-See [@Close:2006ux; @Palomares:wg] for model details.
+See [@Close:2006ux; @Pauly:2016uz] for model details.
 
@@
 
-The previous models combine observational data with a series of biotic and abiotic information to determine the probability that a species will be found in a given space at a given time.
+The previous models combine observational data with a series of biotic and abiotic data to determine the probability that a species will be found in a given space at a given time.
 However, this does not mean that the species in question will actually be there.
@@
 Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries and to reduce the uncertanty embeded in the recosntruction process (See Key uncertanties).
-
-```{r Data_Table, eval = T, echo = F}
-
-Dasets_names <- c(
-  "Occurrence",
-  "ENM-Nereus",
-  "SDM-SAU",
-  "Catch-SAU"
-)
-Brieff_Description <- c(
-  "Occurrence data from multiple sources",
-  "Environmental niche model based on environmental variables and different algorithms",
-  "Species distribution model based on species traits",
-  "Spatial catch allocation based on country-by-country reconstructions"
-)
-
-Sources <-  c(
-  "Reygondeau 2019",
-  "Asch et al., 2017 & Reygondeau 2019",
-  "Palomares et al., 2016",
-  "Zeller et al., 2016"
-)
-
-data.frame(Dasets_names,
-           Brieff_Description,
-           Sources) %>% 
-  kable("latex", booktabs = T,
-        caption = "Summary table of data sources used in the current analysis") %>%
-  kable_styling(full_width = F) %>%
-  column_spec(2,width = "8cm") %>% #wraps text in column2
-  column_spec(3,width = "3cm") #%>% #wraps text in column2
-
-```
+We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries to cathces and revenue from fisheries and to reduce the uncertanty embeded in the reconstruction process (See key uncertanties, below).
 
@@
 from 0 to 1) rather than a discrete, yes or no, index.
-All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*[@Packagedatatable:2019uh], *janitor*[@PackagejanitorSim:2018ur], *wesanderson*[@Packagewesanderson:2018vn], *rfishbase*[@PackagerfishbaseR:2019th], *R.matlab*[@PackageRmatlabRe:2018un], *sf*[@PackagesfSimpleF:2018vp], *sp*[@PackagespClasses:2019tn], *tidiverse*[@PackagetidyverseE:2017vq], *tidytext*[@PackagetidytextTe:2019vk], and *zoo*[@PackagezooSInfr:2019tm].
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
 All code is available at https://github.com/jepa/FishForVisa.
@@
 Species that were present in EEZs that were non-continental territories neighboring other countries were kept separately (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
-Associated states like Puerto Rico and Hong Kong were added to their associated Sovereign (e.g.
+Associated states like Puerto Rico and Hong Kong were added to their Sovereign (e.g.
 Puerto Rico with the United States and Hong Kong with China).
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).
+This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
+S3).
 
@@
 For this study, we did not include catch nor revenue from areas beyond national jurisdiction.
-Finally, we used the catch data to determine the exploitation category of each species within a EEZ.
+Finally, we used the catch data to determine the exploitation category of each species within an EEZ.
 Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not status for each species.
@@
 present, maximum and minimum EEZ's historical catch) and the year (e.g.
-year of maximum historical catch of the species within that EEZ) (**Table XX**) [@Kleisner:2011wn].
+year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
 Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
-We performed a series of one-way analysis of variance (one-way ANOVA) to determine statistically significant differences between the means of different groups (e.g., regions, species, exploitation category) of transboundary species and their contribution to catch and fishing revenue.
+We performed a series of one-way analysis of variance (one-way ANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up].
 
@@
 Canada and Spain).
+Our results are likeley a conservative estimation of transboundary species as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
+Nevertheles, our results are representative of a substantial proportion of the world's marine captches and revenue from economically important marine fisheries.
 <!-- Related to Criteria 2 (Models) -->
@@
 To account for such climate variability, we derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
-This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Palomares:wg].
+This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
 <!-- Related to Criteria 3 (SAU catch data) -->
@@
 This presents a relative conservative estimate of the number of transboundary species in the world.
-However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (**S3_Area.png**).
+However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig.
+S4).
 
@@
 
-![**Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.**](./Figures/S1_Catch_EEZ.png)
+![Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.](./Figures/FigS1.png)
 
-```{r Call_Sup_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
+```{r Call_Sup_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+
+img <- readPNG(here("./Figures/FigS2.png"))
+grid.raster(img)
+```
+
+![Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tonnes. Point sub-region average bars +- s.d.](./Figures/FigS2.png)
+
+```{r Call_Sup_3, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
 
@@
 
-![**Number of shared species across RFMOs. Analysis included with 99 species managed by Fourteen RFMOs **](./Figures/S2_RFMO.png)
+![Number of shared species across RFMOs. Analysis included with 99 species managed by Fourteen RFMOs](./Figures/FigS3.png)
 
 The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (*S3 Index Area*).
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Fig.
+S3).
 As expected, using a more relaxed value (e.g.
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilised a 25% *Area Index* threshold (*S3 Index Area* - darker histogram).
+The current analysis utilised a 25% *Area Index* threshold (Fig.
+S3 - darker histogram).
 
-```{r Call_Sup_3, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Histogram of transboundary species using different values of Area Index.
+```{r Call_Sup_4, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Histogram of transboundary species using different values of Area Index.
 Darker histogram represents used value (25%) in the analysis"}
@@
 
-![**Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis**](./Figures/S3_Area.png)
+![Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
 

### 2020-03-04 Manuscript_Draft.Rmd
Submitted manuscript with figures and references

@@
 author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
-date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
+date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
+^2^Yale University, New Haven, Connecticut, USA.
+^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
 # subtitle: "[DRAFT DO NOT SHARE]"
-subtitle: "Most neighbour nations share marine species"
+subtitle: "Most neighbor nations share marine exploited species"
 output:
   word_document:
-    # reference_docx: ./Manuscript_Instructions/science_template.docx
+    reference_docx: ./Manuscript_Instructions/science_template.docx
   pdf_document:
@@
 ---
+
+* **Corresponding author**: j.palacios@oceans.ubc.ca
 
@@
 
-# One Sentence Summary (125/~125 characters)
+# **One Sentence Summary**
 <!-- *A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
@@
 
-# Abstract (150/~125 words)
+# **Abstract**
 <!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 This represents a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits.
-Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighbouring nations.
-We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (47 million tonnes) and 78.5% of fisheries revenue (USD 65 billion) in last decade.
-Some countries received over 70% of their economic benefits from a few shared resources.
+Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
+We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 65 billion) in the last decade.
+Some countries received over 90% of their catch and economic benefits from a few shared resources.
 This study highlights the large and under-recognized challenge in achieving international fisheries management goals, particularly as species redistribute under climate change.
 
-# Main Article (3200/~2500 words)
+# **Main Article**
 <!-- # Introduction (~555/500 words) -->
@@
 The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
-Theories and empirical experience have show that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; @Bailey:2010ga].
+Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf].
 For instance, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
@@
 Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear.
-Early data limitations on species' distributions allowed only for an informed guess on the number of transboundary species [@Caddy:1997ue] while a more recent study explored the historical contribution of shared stocks following a litterature review [@Teh:2015gd].
+Early data limitations on species' distributions allowed only for an informed guess on the number of transboundary species [@Caddy:1997ue] while a more recent study explored the historical contribution of shared stocks following a literature review [@Teh:2015gd].
 Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
-Here, we aimed to estimate the number of exploited marine species shared by neighbouring countries and determine their contribution to global and regional catch and fisheries revenue.
+Here, we aimed to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
 Moreover, we categorize species according to their exploitation rate while identifying differences by habitat preference.
-We hipothesize that the methodological constraints of preious work has resulted in an underestimation of the contribution of these species to global catch and revenue, and that the proportoin of transboundary species is larger than previouslly estimated.
+We hypothesize that the methodological constraints of previous work has resulted in an underestimation of the contribution of these species to global catch and revenue, and that the proportion of transboundary species is larger than previously estimated.
 
-We overlaid the known distribution of 938 commercially valuable marine species responsable for an average of 96.5% of global EEZ catch reconstruced by the *Sea Around Us* at the species level between 2005 and 2014, and the EEZ of 153 coastal countries.
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 241 EEZs of 198 coastal territories.
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
-For this analysis we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g.
-we did not include the high seas).
-We relay in multiple data sources including occurance, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
-Finally, each neighbouring EEZ had to have more than 25% of a species' distribution in order for the species to be categorized as transboundary.
+We rely on multiple data sources including occurrence, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
+
 <!-- ## Results and discussion (~1000 words) -->
 
-We identified 633 transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing 67.5% of the species analyzed.
-Between 2005 and 2014, national fleets targeting transboundary species within EEZs landed an average of 47.6 million tonnes, representing 79.9% of the EEZ-derrived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
+We identified 633 transboundary exploited species in the world, more than double the previous estimates [@Teh:2015gd], representing 67.5% of the species analyzed.
+Between 2005 and 2014, national fleets targeting transboundary species within EEZs cached an average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
 This is equivalent to 78.5% of the global fishing revenue of the same period.
-These values are more than the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd].
-Based on our assesment (see Methods), 590 transboundary species were also identified as discrete species.
-This is the case of species such as Peruvian anchoveta (*Engraulis ringens*) that is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile.
-The contribution of discrete species (e.g.
-the anchoveta catch of Ecuador) was 14.8 million tonnes representing USD 22,167 million in fishing revenue.
-Within these species, 305 species were considered exclusiveley discrete species, that is, they could be fished by neighbouring nations but were not considered transboundary.
-These species represented only 2.7 million tonnes and 3,691 million USD between 2005 and 2014.
+These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
+Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
+For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador.
+The contribution of discrete species was 14.8 million tons representing USD 22,167 million in fishing revenue.
+Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary.
+These species represented only 2.8 million tons and 3,691 million USD between 2005 and 2014.
 These results underscore the importance of transboundary species at the global level (Fig.
@@
 
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary marine species and their contribution to global fisheries catches and revenue.
-A) The number of species and amount of revenue are represented by colour coding of EEZs and land polygons, respectively.
-B) Contribution of tranbsoundary species to regional revenue (left) and catch (right).
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+B) Contribution of transboundary species to regional revenue (left) and catch (right).
 Regions according to the United Nations sub-regions.
@@
 1.
-Number of transboundary marine species and their contribution to global fisheries catches and revenue.
-A) The number of species and amount of revenue are represented by colour coding of EEZs and land polygons, respectively.
-B) Contribution of tranbsoundary species to regional revenue (left) and catch (right).
+Number of transboundary species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+B) Contribution of transboundary species to regional revenue (left) and catch (right).
 Regions according to the United Nations sub-regions.
@@
 
-We aggregate countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *DF*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
 China (USD 6,279 million) in E.
-Asia and the US (USD 9,605 million) in N.
-America contribute 55% and 83% to their respective region's revenue, respectively.
-Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with the most fishing revenue generated from transboundary species in the last decade.
-These five nations are responsible for 30% of the fishing global revenue from transboundary species.
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5,000 thousand tones each on average between 2005 and 2014 (Fig S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and accounting for 79% of the transboundary species production.
-Similarly, Russia shares the Alaskan polllock (*Theragra chalcogramma*) fishery with both Japan and the US.
-Despite the large catch volume of Peru and Russia, regional catches are only significantly different in E.
-Asia (one-way ANOVA; *Df*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons harvested in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).
-Differences in tansboundary fisheries can also be ilustrated in terms of catch-revenue/EEZ $km^2$ (Figure S2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analized (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tonnes per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+Asia and the USA (USD 9,605 million) contribute 55% and 82% to the total revenues from the E.
+Asia and N.
+America regions, respectively.
+Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig S1).
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
+Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA.
+Transboundary species also contribute largely to fisheries in E.
+Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
+However, when we account for the total area of waters in different EEZs and regions relative to their catches, the importance of transboundary species to European fisheries become apparent (Fig.
+S2, Table S1).
 
 We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
-2) [@Kleisner:2011wn].
+2).
 Previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
-We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,446) = 53.9, *p* < 0.001).
-In the case of discrete species, only Category C is significantly different than the rest (one-way ANOVA, *Df*(2,446) = 52.88, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.001).
-On the other hand, for transboundary species, all categories are significantly different (one-way ANOVA, *Df*(2,446) = 52.88, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05 for all categories).
-While many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk], this result suggests that the management of discrete species could be better off as the variation between categories A and B are closer (*p* = 0.052) than for transboundary species (*p* = 0.002).
+We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
+Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table S2).
+Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
+This result suggests that the management of discrete species could be better off as the variation between Categories A and B is closer (*p* = 0.052) than for transboundary species (*p* = 0.001).
 
@@
 
-Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Bailey:2010ga].
-Examples of successful co-management include Canada and the United States over Pacific salmon [@Song:2017va], Norway and Russia over Atlantic cod (*Gadus morhua*), haddock (*Melanogrammus aeglefinus*) and capelin (*Mallotus villosus*) in the Barents Sea [@Diekert:2010gp; @Eide:2013dha], and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], and reduce the future profitability potential of the fishery [@Merino:2007jz].
-Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf] and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
-Collaboration can also reduce conflict between nations over shared resources as climate change shifts the distribution of species creating tension between countries.
-Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the US, China and Russia [@Spijkers:2019cz].
-For example, the United States and Canada had a dispute over Pacific salmons (*Oncorhynchus sp*) that lasted over 10 years and was only resolved after these two nations set a series of regulations were introduced to compensate for losses [@Munro:2002uf].
-Since 2007, the European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for Atlantic mackerel (*Scomber scombrus*) [@Spijkers:2017ij], a species that is transboundary and contributed an average of 598.4 thousand tonnes to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
-The relatively small contribution of mackrell to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
-In addition to past and present conflicts, climate change is likely to exacerbate conflicts over transboundary species due to shifts in their distribution, requiring flexible agreements that accommodate future uncertainties [@Pinsky:2018cb].
+Empirical analysis suggests that cooperation in the management of transboundary stocks will have better outcomes, although there are specific cases where cooperation might not be the best strategy [@Munro:2002uf].
+Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
+Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
+Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
+Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
 
-<!-- **NOTE: DOUBLE CHECK REFERENCES eddie and derek]** -->
-
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species lke greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,109) = 14.67, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
@@
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory pelagic fish species are managed by Regional Fisheries Management Organizations (RFMOs).
+Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
 Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
 We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
-3).
-The effectiveness of RFMOs responsible for managing high migratory stocks has been previously questioned [@CullisSuzuki:2010fi; @Lodge:2007bt].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 13 species (40 stocks) suggests that most tuna and billfish stocks are sustainably harvested with only three stocks currently considered as overfished [@Pons:2016ep].
-In the other hand, species with narrower ranges are often managed at the national level due to localized populations, however, the potential boundary-crossing of these species must not be ignored [@Payne:2008vm].
-The world of fisheries is highly connected through larvae dispersal [@Ramesh:2019va] and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Levin:2018in; @Payne:2008vm].
-Many coastal communities, particularly in developing regions, are highly dependent on subsistance fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; Wabnitz:2018gf].
+S3).
+The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
+In the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
+However, the potential boundary-crossing of these species must not be ignored.
+The world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Payne:2008vm].
+Many coastal communities, particularly in developing regions, are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
 For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-3B) are among the highest fish consuption countries (> 10 g of fish protein per capita per day) [@FAO:2018KK].
-In these countries, both pelagic and reeef fishes contribute substantially to both local food security and livelehood [@Cabral:2018hc].
-In the case of Kiribati, the Solomon Islands and Papua New Guinea, they are parties to the Pacific Nauru Agreement that sustainably manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
-
-In our analyses we did not seek to include climate change as a driver of species’ distribution.
-Distribution shifts are the most commonly recorded response of marine species to the effects of climate change - chiefly warming - in the ocean [@Poloczanska:2016kk].
-Catch composition might have already changed in the last five decades [@Cheung:2013gk] and will continue throuugh the $21^{st}$ century [@Cheung:2016jd].
-Previous study projected that climate change will bring at least one new transboundary species per EEZ in the future [@Pinsky:2018cb], while also change the proportion of the distribution (e.g.
-Area Index) that each county’s share to a degree that could influence fisheries management (*Palacios-Abrantes et.al.
-under review*).
-Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
+3B) are among the highest fish consumption countries [@FAO:2018KK].
+In these countries, both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
+In the case of Kiribati, the Solomon Islands and Papua New Guinea, they are parties to the Pacific Nauru Agreement that sustainable manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
 
@@
 Moreover, we show significant differences in the management of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
-Previous work has found that collaboration will result in better outcomes for shared marine resources [@Bailey:2010ga].
+Previous work has found that collaboration will result in better outcomes for shared marine resources [@Munro:2002uf].
 Thus, countries should pay specific attention in the management of the identified transboundary stocks potentially creating collaborative management plans.
@@
 
-<!-- # **Acknowledgments* * -->
+# **References**
 
-<!-- ## Funding: include complete funding information;  -->
-<!-- ## Authors contributions: a complete list of contributions to the paper (we encourage you to follow the CRediT model), -->
-<!-- ## Competing interests: competing interests of any of the authors must be listed (all authors must also fill out the Conflict of Interest form).
-Where authors have no competing interests, this should also be declared.
--->
+<div id="refs"></div>
+
+\clearpage
+
+# **Acknowledgments**
+
+We thank T.
+Clark and A.
+Tidd for helpful comments and discussions.
+**Funding**: G.R.
+was supported by the EO Wilson foundation.
+C.W.
+was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
+W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
+**Authors contributions**: J.P.A.
+Conceptualization, methodology, formal analysis, writing original draft.
+G.R.
+Methodology, data curation, writing - review & editing.
+C.W.
+Methodology, writing - review & editing.
+W.W.L.C.
+Supervision, writing - review & editing.
+All authors provided valuable input to the study conceptualization and discussed the results and analysis.
+**Competing interests**: No declared.
+**Data and materials availability**: The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+All code is available at https://github.com/jepa/FishForVisa
 
 ## Data and materials availability
+All data is publicly available online and upon request from the authors.
 
-All data is available from the authors upon request.
+## List of Supplementary Materials
+Figures S1-S4
+Tables S1 -S2
+References in main manuscript (1-27)
 
-# Materials and Methods
-
-To ascertain whether or not a species can be considered transboundary, we developed a method based on a series of criteria and the overlay of species' distributions and the spatial boundaries of the world’s EEZs.
-All analyses were conducted at the species level and we consider transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of neighboring countries [@Munro:2002uf].
-All data was scaled to $0.5^o$ x $0.5^o$ lat-long grid cells.
+# **Materials and Methods**
 
@@
 To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the reconstructed list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their current distributions based on an average from 1970-2000.
-The total number of species analized was 938 representing 54% of the average catch reported by the *Sea Around Us* between 2005 and 2014, including generalized categories such as *Marine fish not identified* or *Mollusca*.
-However, because we carried the analysis at the species level, we did not include such generalized categories in our comparrisons.
+The total number of species analyzed was 938 representing 54% of the average catch reported by the *Sea Around Us* between 2005 and 2014, including generalized categories such as *Marine fish not identified* or *Mollusca*.
+However, because we carried the analysis at the species level, we did not include such generalized categories in our comparisons.
 Our final sample represents 63.2% of identified species, accounting for 96.52% of the catch identified at the species' level.
@@
 
-```{r Data_Table, eval = T, echo = F}
+Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data is publicly available (see Acknowledgments).
+
+```{r Data_Table, eval = F, echo = F}
 
@@
   rename("Main Method"=Main_Method) %>% 
-  kable("latex", booktabs = T,
-        caption = "Summary of data sources to estimate species' distributions.
+  # kable("latex", booktabs = T,
+  #       caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
 All data is publically available, see references for details.") %>%
-  kable_styling(full_width = F) %>%
-  column_spec(2,width = "8cm") %>% #wraps text in column2
-  column_spec(3,width = "3cm") #%>% #wraps text in column2
+  # kable_styling(full_width = F) %>%
+  # column_spec(2,width = "8cm") %>% #wraps text in column2
+  # column_spec(3,width = "3cm") %>% #wraps text in column2
+  write_csv("Table_1.csv")
 
 ```
-
-<!-- **NOTE: WC "Need to discuss how this affect the samples of transboundary species."**. -->
-<!-- **NOTE: for transboundary lobsters https://books.google.com.ar/books?id=XEElAwNrKZsC&pg=PA224&lpg=PA224&dq=belize+mexico+lobster+shared+stock&source=bl&ots=lsmUH743d_&sig=ACfU3U1P1t7_L8q_YRh3oQGszUO8Lg1jFw&hl=en&sa=X&ved=2ahUKEwiv36qbwbjnAhX3HrkGHYIbCTgQ6AEwFHoECA0QAQ#v=onepage&q=belize%20mexico%20lobster%20shared%20stock&f=false** -->
 
@@
 Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries to cathces and revenue from fisheries and to reduce the uncertanty embeded in the reconstruction process (See key uncertanties, below).
+We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
 
@@
 Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*.
-The *Area Index* consist in the proportion of a given species' overarching shared distribution between neighbouring EEZs accounted for by each individual EEZ.
+The *Area Index* consist in the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
@@
 Finally, we used the catch data to determine the exploitation category of each species within an EEZ.
-Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not status for each species.
+Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
+temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk].
 We only assessed species within each EEZ for which at least ten years of data were available between the first and last reported catch and with at least five consecutive years of data.
@@
 year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
+Following this concept, Category A would represent fisheries that are re-building or under-exploited, Category B would be species that are sustainable harvested, and Category C would be species that are over-exploited.
 Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
-We performed a series of one-way analysis of variance (one-way ANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up].
+We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
+We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
+
+Table 2. Rules to determine the category of each analyzed species.
 
@@
            Rules) %>% 
-  kable("latex", booktabs = T,
-        caption = "Rules to determine the category of each transboundary species") %>%
-  kable_styling(full_width = F) %>%
-  column_spec(1,width = "3cm") %>% #wraps text in column2
-  column_spec(2,width = "13cm") #%>% #wraps text in column2
+  # kable("latex", booktabs = T,
+  #       caption = "Rules to determine the category of each transboundary species") %>%
+  # kable_styling(full_width = F) %>%
+  # column_spec(1,width = "3cm") %>% #wraps text in column2
+  # column_spec(2,width = "13cm") %>% #wraps text in column2
+  write_csv("Table_2.csv")
 
@@
 ## Key uncertainties
-<!-- # Related to Criteria 1 (Neighbours) -->
+<!-- # Related to Criteria 1 (neighbors) -->
 We have identified four key uncertainties in the method that may affect the estimation of transboundary stocks.
 Firstly, we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
-However, we defined transboundary only between  neighbouring countries (e.g.
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
+Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
+We limited the distribution of a species by defining transboundary only between neighboring countries (e.g.
 US and Canada) and did not include countries that were separated by another country (e.g.
@@
 Canada and Spain).
-Our results are likeley a conservative estimation of transboundary species as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
-Nevertheles, our results are representative of a substantial proportion of the world's marine captches and revenue from economically important marine fisheries.
+Our results are likely a conservative estimation of transboundary species as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
+Nevertheless, our results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
 <!-- Related to Criteria 2 (Models) -->
@@
 Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
-Likewise, the spatial allocation of the catch is subjected to imprecisions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
+Likewise, the spatial allocation of the catch is subjected to impressions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
 However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and @Zeller2016 for mode details in the spatial allocation of the SAU).
@@
 
-# Supplements
+\clearpage
+
+# **Supplements**
 
 ```{r Call_Sup_1, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
-The number of species is represented in the EEZ while the catch (thousand tonnes) is represented in the land polygon."}
+The number of species is represented in the EEZ while the catch (thousand tons) is represented in the land polygon."}
 
@@
 ![Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.](./Figures/FigS1.png)
+The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)
+
+Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Figure S2).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
 
@@
 
-![Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tonnes. Point sub-region average bars +- s.d.](./Figures/FigS2.png)
+![Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/FigS2.png)
 
@@
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilised a 25% *Area Index* threshold (Fig.
+The current analysis utilized a 25% *Area Index* threshold (Fig.
 S3 - darker histogram).
@@
 ![Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
-
-# References (37/about 30)
 
@@
 <!-- We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
-The first criteria consisted in only considering shared species between neighbouring EEZs, rather than the extended distribution.
+The first criteria consisted in only considering shared species between neighboring EEZs, rather than the extended distribution.
 For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
@@
 A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
-Finally, the last criteria determined a spatial treshold to confirm that a species occurs in both neighboring EEZs.
+Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
 Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].

### 2020-03-04 Initial_Analysis.Rmd
Final details on analysis

@@
 ---
+
+# Read Me
+This script runs the analysis for the manuscript *Marine species do not need visas: the transboundary nature of the world’s exploited marine species* from the data loading to the results analysis.
+Is divided in two parts; *Methods* where the raw data is analyzed and *Results* where the results from the analysis are processed.
 
@@
 
-1. Determine which countries have Neighbouring EEZs  
+1. Determine which countries have Neighboring EEZs  
 1.1. For this we used the Sea Around Us EEZ map that discriminate by oceans and a routine (*Estimate Transboundary Species*) to identify Neighbouring polygons,
@@
 
-2. Overlap distribution maps with Neighbours data  
-2.1. For each species we merged the Neighbours data with their known distribution (SAU distribution and catch,ESMs, and Observation)  
+2. Overlap distribution maps with Neighbors data  
+2.1. For each species we merged the Neighbors data with their known distribution (SAU distribution and catch,ESMs, and Observation)  
 3. Determine transboundary if:  
@@
 
-We create two "confidence level" based on data and area covered, i.e;
-
--
--
+We create two "confidence level" based on data and area covered.
 
@@
 
-This part is to determine the list of species to be analized in the project.
+This part is to determine the list of species to be analyzed in the project.
 Initially this list was limited by the species data from the DBEM, however, as we are not using the DBEM, the limit is now the SAU.
@@
 
-## Determine Neighbourds
-
-This is the first step of the analysis and will determine what EEZs are neighbouring. THe routine creates a final dataset that we then use to estimate transboundary species.
+## Determine Neighbors
+
+This is the first step of the analysis and will determine what EEZs are neighbors. The routine creates a final data-set that we then use to estimate transboundary species.
 
@@
 
-This function determines what EEZs are Neighbours and returns a data.frame of it
+This function determines what EEZs are Neighbors and returns a data.frame of it
 
@@
 
-### Sub Routine; Neighbours
+### Sub Routine; Neighbors
 
@@
 
-Once those tresholds are met, the status of the species is determined as follows:
+Once those thresholds are met, the status of the species is determined as follows:
 
@@
 
-The datasets SAU_D, OCC, and ESM are used as sppecies presence while SAU_C is used as a confirmation of that.
-The `Model Index` is the first treshold and estimates the uncertanty of models.
+The data-sets SAU_D, OCC, and ESM are used as species presence while SAU_C is used as a confirmation of that.
+The `Model Index` is the first threshold and estimates the uncertainty of models.
 Goes from 0 - 1 as follows:
@@
 - 1 or 0; All models agree that in the presence of the species
-- 0.75; Three out of four models agree on speices presence
-- 0.50; Two out of four models agree on speices presence
-- 0.25; Only one model flags a speices presence
+- 0.75; Three out of four models agree on species presence
+- 0.50; Two out of four models agree on species presence
+- 0.25; Only one model flags a species presence
 - 0; All models agree there is no species there
 
-The `Area_Index` is the second treshold and estimates the proportion of each species distribution in each EEZ.
+The `Area_Index` is the second threshold and estimates the proportion of each species distribution in each EEZ.
 It only take into consideration the distribution of the species within the two EEZs, rather than the complete distribution.
-Hence, is mirrord (e.g.
+Hence, is mirror (e.g.
 if EEZ#1 is 0.40, EEZ#2 is 0.6)
@@
 
-There are quite a few inconsistencies between the names of territories within the SAU shapefile, the distribution data and the UN database.
+There are quite a few inconsistencies between the names of territories within the SAU shape file, the distribution data and the UN database.
 The following function cleans up the names, some of them manually some of the automatic.
@@
   if(Variable_Selected == "catch"){
-    Map_Label <- "Catch (Thousand Tonnes)"
+    Map_Label <- "Catch (Thousand Tons)"
     Plot_Name <- "Catch_plot.png"
@@
               aes(x=id,
-                  y=Value_sum+10,
+                  y=Value_sum,
                   label=sub_region,
@@
             aes(x=id,
-                y=ifelse(Value_sum == 12,Value_sum,Value_sum+0.1), # Fix names overlap
+                y=ifelse(Value_sum >= 12,12,Value_sum+0.1), # Fix names overlap
                 label=sub_region,
@@
   ) +
-  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
+  draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
                   size = 8,
@@
 
-In here we load and cleaned the multiple external datasets requred to produce the manuscript figures
+In here we load and cleaned the multiple external data sets required to produce the manuscript figures
 
@@
 
-## Determine Tresholds
-
-Determine transboundary stocks and countries based on selected trsholds. We created two tresholds (levels of uncertanty), in here we can chose which level we wanna work with.
+## Determine Thresholds
+
+Determine transboundary stocks and countries based on selected thresholds. We created two thresholds (levels of uncertainty), in here we can chose which level we wanna work with.
 
@@
 ```{r Transboundary_Data_per_Territory, eval = F, echo = F}
+
+# -------------------------- #
+# Number of EEZs and countries
+# -------------------------- #
+
+# number of eezs
+length(unique(sau_eez_fes$eez_name))
+# Number of coastal territories
+length(unique(sau_eez_fes$fishing_entity))
 
@@
 # Discrete species
+# Species that are transboundary in some cases but discrete in other cases
 ###_________________###
@@
 # Both categories (trans and Discrete)
-Tresholded_T_Data %>% 
+n_discrete <- Tresholded_T_Data %>% 
   semi_join(Discrete,
-            by = "taxon_key") %>% 
+            by = "taxon_key") %>% # those that are not only discrete
   group_by(taxon_key) %>% 
@@
 
-n_discrete <- length(unique(Discrete$taxon_key))
-
-  Summary_Discrete_B <- Discrete_B %>% 
-  left_join(SAU_Sampled_Data,
-           by = c("taxon_key","eez_name")) %>% 
-  group_by(Variable) %>%
-  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
-  left_join(Total_SAU_Sampled) %>% 
-  left_join(Total_SAU_Global) %>% 
-  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
-         Per_SAU = Total_Discrete/Total_Global*100)
-
 ###_________________###
 # Discrete Exclusive
+# Species that are only discrete and are not present in the transboundary category
 ###_________________###
@@
 
+## double check
+
+Discrete_Exclusive %>% 
+  semi_join(Tresholded_T_Data, by = "taxon_key") # 0 ok thes
+
 # Number of discrete species
@@
 
-Summary_Discrete_Exclusive <- Discrete %>% 
+Summary_Discrete_Exclusive <- Discrete_Exclusive %>% 
   left_join(SAU_Sampled_Data) %>% 
@@
 
-# Data per Territory
+# Data per Territory (EEZ)
 Transboundary_Spp <- Tresholded_T_Data %>% 
@@
 Map_Breaks <- c(-1,10,100,1000,5000,10000)
+
+###
+
+Total_Value_EEZ <- sau_eez_fes %>% 
+  group_by(fishing_entity_id, fishing_entity) %>% 
+  summarise(n=n()) %>% # Get all of the fishing entity and id
+  select(-n) %>% 
+  left_join(SAU_Global_Data) %>% 
+  group_by(fishing_entity,Variable) %>% 
+  summarise(Total_Value = sum(Value,na.rm=T))
 
@@
     Trans_Entity_n = length(unique(taxon_key)),
-    Trans_Total = sum(Value,na.rm=T) #million
+    Trans_Total = sum(Value,na.rm=T), #million
   ) %>%
   ungroup() %>%
-  filter(!is.na(Variable)) %>% # Momentaneus fix for some reason there are diff. between datasers
-  # Match the sacle limits of both value and and catch 
+  filter(!is.na(Variable)) %>%
   mutate(
@@
   spread(Variable,Trans_Total) %>% 
-  left_join(Entity_Area, by = "fishing_entity") %>% 
+  left_join(Entity_Area, 
+            by = "fishing_entity") %>% 
   # Include the weighted method for supplementals
@@
   ) %>% 
+  left_join(Total_Value_EEZ,
+            by = c("fishing_entity", "Variable") 
+            ) %>% # uncomment for estimating percentage
   # Convert catch to million tonnes
@@
     Value = ifelse(Variable == "catch",Value/1000, #million
-                         Value)
+                         Value),
+    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
   )
@@
 
-Subregion_Trans_Value <- Value_Trans_Country %>% 
+Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
   left_join(UN_Regions,
@@
   group_by(sub_region,Variable) %>% 
-  summarise_if(is.numeric,c(Value_sum = sum,
-                            Value_m = mean,
-                            Value_sd = sd),
+  summarise_if(is.numeric,c(sum = sum,
+                            m = mean,
+                            sd = sd),
                na.rm=T) %>%
@@
 # Fix names for plot
-Subregion_Trans_Value$sub_region <- Subregion_Trans_Value$sub_region %>% 
+Subregion_Trans_Value <- Subregion_Trans_raw_Value
+
+Subregion_Trans_Value$sub_region <- Subregion_Trans_raw_Value$sub_region %>% 
   gsub("Northern","N.",.) %>% 
@@
                                paste(sub_region))
-    ),
-    sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
+    )#,
+    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
   )
@@
 # Variable to plot (value or catch)
-Variable_plot <- "catch"
+Variable_plot <- "value"
 CreateFigureOne(Variable_plot)
@@
   draw_plot_label(
-    label = c("Revenue (USD) | Catch (Tones)","Million per Km2"),
+    label = c("Revenue (USD) | Catch (Tons)","Million per Km2"),
                   size = 6,
@@
 
-Top_Rev_Countries <- c("Peru", "Russian Federation", "Chile", "USA")
-
+Top_Rev_Countries <- c("China", "Peru", "Russian Federation", "Chile", "USA","Japan")
+
+# Total revenue from Top countries
 Total_Top_Rev <- Value_Trans_Country %>% 
@@
   filter(fishing_entity %in% Top_Rev_Countries) %>% 
-  select(1:3)
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  left_join(Subregion_Trans_raw_Value) %>% 
+  mutate(Per_Top = Value/Value_sum*100) %>% 
+  select(1:3,Per_Top)
 
@@
 
-Top5 <- c("Peru", "Russian Federation", "Chile", "USA","China")
+Top5 <- c("Peru", "Russian Federation", "Japan", "USA","China")
 
@@
 
-### Statistical differences
-
+### Statistical differences within regions
 We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.
@@
 
-Subregion_Data_stats <- Value_Trans_Country %>% 
-  left_join(UN_Regions,
-            by = "fishing_entity") %>% 
-  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
-  select(fishing_entity,sub_region,Variable,Value) %>% 
-  filter()
-
-# ### Prepare Data
-# Subregion_Data_stats <- Revenue_Country %>% 
-#   left_join(Catch_Country,
-#             by = "fishing_entity") %>% 
-#   left_join(UN_Regions,
-#             by = "fishing_entity") %>% 
-#   mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
-#   select(fishing_entity,sub_region,Total_USD,fishing_entity_catch)
-
-# Revenue ANOVA
+### Reveneu ANOVA
+
 Subregion_Rev_stats <- Subregion_Data_stats %>% 
@@
 Rev_aov
+
 summary(Rev_aov)
-
 #              Df    Sum Sq Mean Sq F value   Pr(>F)    
-# sub_region   16  75628526 4726783    4.91 4.2e-08 ***
-# Residuals   157 151140183  962676
-
-#### There are significant differences. But between what?
+# sub_region   16  75738982 4733686   4.948 3.46e-08 ***
+# Residuals   158 151144071  956608
 
 #  Post-hoc analysis
-TukeyHSD(Rev_aov)
-
-# Northern America sig than everyone except for Eastern Asia
-# Eastern Asia sig with everyone except with Eastern Europe and North Am.
+TukeyHSD(Rev_aov) %>% 
+  tidy() %>% 
+  filter(adj.p.value < 0.05)
 
@@
 
-Catch_aov <- aov(fishing_entity_catch~sub_region, data = Subregion_Catch_stats)
+Catch_aov <- aov(Value~sub_region, data = Subregion_Catch_stats)
 Catch_aov
@@
 summary(Catch_aov)
-
-# sub_region   16  50.63   3.164   3.767 7.2e-06 ***
-# Residuals   155 130.22   0.840                    
-# ---
-# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+#  Df Sum Sq Mean Sq F value  Pr(>F)   
+# sub_region   16  27.51  1.7195   2.265 0.00539 **
+# Residuals   158 119.97  0.7593
 
 #  Post-hoc analysis
-TukeyHSD(Catch_aov)
+TukeyHSD(Catch_aov) %>% 
+   tidy() %>% 
+  filter(adj.p.value < 0.05) # Eastern Asia
 
@@
 #  Post-hoc analysis
-TukeyHSD(Rev_aov)
+TukeyHSD(Weight_aov) %>% 
+  tidy() %>% 
+  filter(adj.p.value < 0.05) # Northern Europe
 ```
@@
 
-# Number of coastal nations
-length(unique(Status_Data_Plot$individual))
-
 # Summary for manuscipt
 
-Status_Data_Plot %>% 
+T_Summary <- Status_Data_Plot %>% 
   mutate(value = ifelse(value <0, value*-1,value)) %>% 
@@
             sd(value)) %>% 
-  arrange(desc(tot)) %>% 
-  view()
+  arrange(desc(tot))
 
@@
   summarise(value = sum(value))
+
+# Summary for manuscipt
+
+D_Summary <- Discrete_Status_Data %>% 
+  mutate(value = ifelse(value <0, value*-1,value)) %>% 
+  group_by(observation) %>% 
+  summarise(tot=sum(value),
+            mean(value),
+            sd(value)) %>% 
+  arrange(desc(tot))
+
+#### Supplemental Table 3
+
+# T_Summary %>%
+#   left_join(D_Summary, by = "observation") %>%
+#   mutate(
+#     "Mean Shared" = paste(round(`mean(value).x`,2)," \u00B1 (",round(`sd(value).x`,2),")",sep=""),
+#     "Mean Discrete" = paste(round(`mean(value).y`,2)," \u00B1 (",round(`sd(value).y`,2),")",sep="")
+#     ) %>%
+#   select(1,8:9) %>%
+#   filter(observation != "No Category") %>%
+#   rename(Category = observation) %>%
+#   arrange(Category) %>%
+#   write_csv("Category_summary.csv")
+
 ```
@@
 
+### Statistical differences between species status
+
+Using MANOVA to investigate differences in catch category between discrete and transboundary species
+
 ```{r statistics_fig2, eval = F, echo = T}
 
-# -------------------------- #
-# Transboundary species
-# -------------------------- #
-
-Status_Data_Stats <- Status_Data_Plot %>% 
+#-----------------# 
+# Get Data
+#-----------------#
+
+# Transboundary Data
+Transboundary_Data_Stats <- Status_Plot_Data %>% 
 filter(observation != "No Category") %>%
-  mutate(value = abs(value)) %>%
-
-Total_Trans_Status <- Status_Data_Stats %>% 
-  group_by() %>% 
-  summarise(sum = sum(value)) %>% 
-  pull()
-
-Status_Data_Stats %>% 
-  group_by(observation) %>% 
-  summarise_if(is.numeric,
-               .funs = c(Mean="mean",
-                           sd = "sd",
-                          Sum = "sum")
-  ) %>% 
-  mutate(Sum/Total_Trans_Status*100)
-
-# --------------------- #
-### Check for Asumptions
-# --------------------- #
+  mutate(value = abs(value))
+
+# Discrete Data
+Discrete_Data_Stats <- Discrete_Status_Data %>% 
+  filter(observation != "No Category") %>%
+  mutate(value = abs(value))
+
+#### By Category (Manova)
+
+# Use manova to test for a significant effect of Catch category on discrete and transboundary species simultaneously. Takes into account possible correlations between dependent variables.
+# Decreases Tipe I errors
+
+Manova_Differences <- Transboundary_Data_Stats %>% 
+  rename(Trans_value = value) %>% 
+  left_join(Discrete_Data_Stats, by = c("individual","observation","group")
+  ) %>% 
+  rename(Discrete_value= value) %>% 
+  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value))
+
+#-----------------# 
+## Test assumptions
+#-----------------#
+
+Manova_Differences %>% 
+  gather("cat","val",Trans_value,Discrete_value) %>% 
+  ggplot() +
+  geom_histogram(
+    aes(
+      x = val
+    )
+  ) +
+  facet_wrap(~observation+cat)
+
+### Correlation
+
+plot(Manova_Differences$Trans_value~Manova_Differences$Discrete_value)
+cor(Manova_Differences$Trans_value,Manova_Differences$Discrete_value)
+
+#-----------------# 
+## MANOVA test
+#-----------------#
+
+mano <- manova(cbind(Discrete_value,Trans_value) ~ observation, data = Manova_Differences)
+
+summary(mano)
+# Df  Pillai approx F num Df den Df    Pr(>F)    
+# observation   2 0.21621   27.091      4    894 < 2.2e-16 ***
+# Residuals   447
+
+summary.aov(mano)
+#  Response Discrete_value :
+#              Df Sum Sq Mean Sq F value    Pr(>F)    
+# observation   2   7088  3544.1  26.305 1.584e-11 ***
+# Residuals   447  60226   134.7                      
+# ---
+# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+# 
+#  Response Trans_value :
+#              Df Sum Sq Mean Sq F value    Pr(>F)    
+# observation   2  22778 11389.2  55.005 < 2.2e-16 ***
+# Residuals   447  92555   207.1
+
+#-----------------# 
+## Run non-parametric to make sure
+# Same result
+#-----------------#
+
+# kruskal.test(Trans_value~Discrete_value, data = Manova_Differences)
+# Kruskal-Wallis chi-squared = 100.24, df = 45, p-value = 4.358e-06
+
+#-----------------# 
+## ANOVA test for each category
+#-----------------#
+
+# Transboundary Species
 
 #### Test for normallity 
-Status_Data_Stats %>%
+Transboundary_Data_Stats %>%
   ggplot() +
@@
 
-bartlett.test(value~observation, Status_Data_Stats)
+bartlett.test(value~observation, Transboundary_Data_Stats)
 
@@
 
-Stat_Cat_kt <- kruskal.test(observation~value, data = Status_Data_Stats)
-Stat_Cat_kt
-
-# Post hock test
-kruskalmc(Status_Data_Stats$value,Status_Data_Stats$observation)
-
-# Stat_Cat_aov <- aov(value~observation, data = Status_Data_Stats)
-# Stat_Cat_aov
-# summary(Stat_Cat_aov)
+Stat_Cat_aov <- aov(value~observation, data = Transboundary_Data_Stats)
+Stat_Cat_aov
+summary(Stat_Cat_aov)
 #              Df Sum Sq Mean Sq F value Pr(>F)    
-# observation   2  22093   11046   52.88 <2e-16 ***
-# Residuals   446  93170     209
-
-# TukeyHSD(Stat_Cat_aov)
+# observation   2  22778   11389   55.01 <2e-16 ***
+# Residuals   447  92555     207
+
+TukeyHSD(Stat_Cat_aov)
+#                            diff       lwr       upr     p adj
+# Category B-Category A  5.946667  2.039431  9.853902 0.0011125
+# Category C-Category A 17.160000 13.252765 21.067235 0.0000000
+# Category C-Category B 11.213333  7.306098 15.120569 0.0000000
+
+#-----------------# 
+# Double check the Non parametic test
+# same result
+#-----------------#
+
+# Stat_Cat_kt <- kruskal.test(observation~value, data = Transboundary_Data_Stats)
+# Stat_Cat_kt
+# 
+# # Post hock test
+# kruskalmc(Transboundary_Data_Stats$value,Transboundary_Data_Stats$observation)
 
@@
 # -------------------------- #
-
-# Run anova within discrete speciess
-
-Discrete_Data_Stats <- Discrete_Status_Data %>% 
-  filter(observation != "No Category") %>%
-  mutate(value = abs(value))
-
-Total_Discrete_Status <- Discrete_Data_Stats %>% 
-  group_by() %>% 
-  summarise(sum = sum(value)) %>% 
-  pull()
-
-Discrete_Data_Stats %>% 
-  group_by(observation) %>% 
-  summarise_if(is.numeric,
-               .funs = c(Mean="mean",
-                           sd = "sd",
-                          Sum = "sum")
-  ) %>% 
-  mutate(Propo_Total = Sum/Total_Discrete_Status*100)
 
@@
 
-Stat_discrete_cat_kt <- kruskal.test(observation~value, data = Discrete_Data_Stats)
-Stat_discrete_cat_kt
-
-kruskalmc(Discrete_Data_Stats$value,Discrete_Data_Stats$observation)
-
 # ANOVA of Discrete categories
@@
 
-# ANOVA of Discrete continents
-# Stat_discrete_cont_aov <- aov(value~group, data = Discrete_Data_Stats)
-# Stat_discrete_cont_aov
-# summary(Stat_discrete_cont_aov)
-
-# Df Sum Sq Mean Sq F value Pr(>F)
-# group         5    962   192.4    1.18  0.318
-# Residuals   377  61472   163.1
-
-# -------------------------- #
-# Comparrison bwtween Discrete
-# and Transboundary species
-# -------------------------- #
-
-#### By Category (Manova)
-
-# Use manova to test for a significant effect of Catch category on discrete and transboundary species simultaneously. Takes into account possible correlations between dependent variables.
-# Decreases Tipe I errors
-
-Manova_Differences <- Status_Data_Stats %>% 
-  rename(Trans_value = value) %>% 
-  left_join(Discrete_Data_Stats, by = c("individual","observation","group")
-  ) %>% 
-  rename(Discrete_value= value) %>% 
-  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value))
-
-#### Test for normallity
-
-Manova_Differences %>% 
-  gather("cat","val",Trans_value,Discrete_value) %>% 
-  ggplot() +
-  geom_histogram(
-    aes(
-      x = val
-    )
-  ) +
-  facet_wrap(~observation+cat)
-
-### Correlation?
-
-plot(Manova_Differences$Trans_value~Manova_Differences$Discrete_value)
-
-cor(Manova_Differences$Trans_value,Manova_Differences$Discrete_value)
-
-mano <- manova(cbind(Discrete_value,Trans_value) ~ observation, data = Manova_Differences)
-summary(mano)
-#     Df  Pillai approx F num Df den Df    Pr(>F)    
-# observation   2 0.20992   26.151      4    892 < 2.2e-16 ***
-# Residuals   446             
-summary.aov(mano)
-# Response Discrete_value :
-#              Df Sum Sq Mean Sq F value    Pr(>F)    
-# observation   2   6918  3458.9  25.684 2.769e-11 ***
-# Residuals   446  60063   134.7                      
-# ---
-# 
-# 
-#  Response Trans_value :
-#              Df Sum Sq Mean Sq F value    Pr(>F)    
-# observation   2  22093 11046.3  52.878 < 2.2e-16 ***
-# Residuals   446  93170   208.9                      
-# ---
-
-#### Run non-parametric to make sure (same)
-
-kruskal.test(Trans_value~Discrete_value, data = Manova_Differences)
-# Kruskal-Wallis chi-squared = 296.66, df = 43, p-value < 2.2e-16
-
-### Multiple wilcox/t.test
-
-Manova_Differences %>% 
-  # group_by(observation) %>% 
-  ungroup() %>% 
-  select(2,4,5) %>% 
-  do(wil = aov(.$Trans_value~.$Discrete_value)) %>% 
-  tidy(wil) %>% 
-  View()
-
-# Also significantly different
-
-#### Chi square maybe???
-
-Chi_data <- Manova_Differences %>% 
-  ungroup() %>% 
-  group_by(observation) %>% 
-  summarise_if(is.numeric,sum) %>% 
-  select(-observation)
-
-chisq.test(Chi_data)
-
-```
-
-## Analysis per Species
-
-### Mackerel (Scomber scombrus) war
+#-----------------# 
+# Double check the Non parametic test
+# All different... But it does not show any distance, just the categorial difference
+#-----------------#
+
+Stat_discrete_cat_kt <- kruskal.test(observation~value, data = Discrete_Data_Stats)
+Stat_discrete_cat_kt
+
+kruskalmc(Discrete_Data_Stats$value,Discrete_Data_Stats$observation)
+
+```
+
+## Results per Species
+
+### Mackerel (*Scomber scombrus*) war
 
@@
 
-Species_Data <- Tresholded_T_Data %>% 
+Raw_Species_Data <- Tresholded_T_Data %>% 
   group_by(taxon_key) %>% 
@@
 
-Top_5_Ecosystem <- Species_Data %>% 
+Top_5_Ecosystem <- Raw_Species_Data %>% 
   rename(taxon_name = individual) %>% 
@@
 
-Species_Data <- Species_Data %>%
+Species_Data <- Raw_Species_Data %>%
   filter(value > 20)
@@
 
-## Statistics on species
+### Statistics on Species Ecosystem Preference
 
@@
 
-head(Species_Data)
+head(Raw_Species_Data)
 
 # Differences between groups
-Stat_spp_aov <- aov(value~group, data = Species_Data)
+Stat_spp_aov <- aov(value~group, data = Raw_Species_Data)
 Stat_spp_aov
@@
 #              Df Sum Sq Mean Sq F value Pr(>F)    
-# group         5  24836    4967   14.67 5.52e-11 *** (YUP)
-# Residuals   109  36915     339
-
-TukeyHSD(Stat_spp_aov)
+# group         5  56721   11344   53.82 <2e-16 ***
+# Residuals   597 125844     211
+
+TukeyHSD(Stat_spp_aov) %>% 
+  tidy() %>% 
+  filter(adj.p.value < 0.05) # Pelagic-Oceanic
 
@@
       y = "Frequency of EEZs",
-      title= paste((Area_Index_Level[i]*100),"% area treshold"," (Median ",Median_data,")",sep="")
+      title= paste((Area_Index_Level[i]*100),"% area threshold"," (Median ",Median_data,")",sep="")
     ) +
@@
   units = "in",
-  filename = "Area_Tresholds.png",
+  filename = "Area_Thresholds.png",
   path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Sensitivity_Analysis"
@@
 
-Found the probelm, Gab's coordinate system, hecne the data, are in different system than DBEM and SAU data...
+Found the problem, Gab's coordinate system, hence the data, are in different system than DBEM and SAU data...
 
@@
 
-### Overcounting transboundary stocks
+### Over-counting transboundary stocks
 
 In a first run, Australia results in many transboundary stocks, I believe this is because it is counting the number of countries that that the species share (e.g.
-one species 6 countries = 6 transboundary spp) rather than 1 speces 6 countries = 1 trans spp.
+one species 6 countries = 6 transboundary spp) rather than 1 species 6 countries = 1 trans spp.
 
@@
 
-In the first run. Countries where EEZs are devided but touching (e.g. South Africa inidan and atlantic coasts) are double counted.
-
-This might be fixed with Tayler's data of EEZs to ISOs... He did it manually so it does not work!
+In the first run. Countries where EEZs are divided but touching (e.g. South Africa Indian and Atlantic coasts) are double counted.
+
+This might be fixed with Tyler's data of EEZs to ISOs... He did it manually so it does not work!
 
@@
 
-For some reason Côte de ivory is missing data. It was fixed at the begining when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to cero.
+For some reason Côte de ivory is missing data. It was fixed at the beginning when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to zero.
 
@@
 
-### Maps for each model/dataset
+### Maps for each model/data-set
 ```{Tran_country_Map_All, eval =F, echo =F}
@@
 
-# Vulnerabillity Assesment
+# Vulnerability Assessment
 
@@
 ```
+
+```{r Sub-regional_differences, eval = F}
+
+#-----------------#
+# Sub-regional differences
+#-----------------#
+
+Subregion_Data_stats <- Value_Trans_Country %>%
+  left_join(UN_Regions,
+            by = "fishing_entity") %>%
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>%
+  select(fishing_entity,sub_region,Variable,Value) %>%
+  filter()
+
+# Revenue ANOVA
+Subregion_Rev_stats <- Subregion_Data_stats %>%
+  filter(Variable == "value")
+
+Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
+Rev_aov
+summary(Rev_aov)
+
+# Df    Sum Sq Mean Sq F value  Pr(>F)    
+# sub_region   16  75628526 4726783    4.91 4.2e-08 ***
+# Residuals   157 151140183  962676
+
+#### There are significant differences. But between what?
+
+#  Post-hoc analysis
+TukeyHSD(Rev_aov)
+
+# Northern America sig than everyone except for Eastern Asia
+# Eastern Asia sig with everyone except with Eastern Europe and North Am.
+
+```

### 2020-03-06 Cover_Letter.Rmd
Updated cover letter

--- 2019-09-18 Cover_Letter.Rmd
@@
 ---
-title: 'Fish do nor need Visas: Reference Letter'
-author: "Juliano Palacios Abrantes"
-date: '2019-09-18'
-output: pdf_document
+output:
+  word_document: default
+  pdf_document: default
 ---
 
-Should include:
-- Reference to any pre-submission discussions with editors.
-- The title of the paper and a statement of its main point.
-- Any information needed to ensure a fair review process, including related manuscripts submitted to other journals.
-- Names of colleagues who have reviewed the paper.
-- A statement that none of the material has been published or is under consideration for publication elsewhere.
-- Specification of where all data underlying the study are available, or will be deposited, and whether there are any restrictions on data availability such as an MTA.
-- Information on any reference material or additional data files uploaded to the Auxiliary files section (see below).
-- Please also upload a .docx version of your cover letter – see below.
+Dr. Ali Shilatifard                        03-06-2020
+Editor, *Science Advances*
+
+Dear Dr. Shilatifard,
+
+Please find attached our manuscript titled “Marine species do not need visas: the transboundary nature of the world’s exploited marine species” submitted for publication in *Science Advances*.
+In this paper we highlight the large and under-recognized scale of transboundary fisheries and discuss associated challenges in achieving international fisheries management goals.
+
+Last year *Nandini et al.[^1]* published a paper in Science demonstrating that marine fishes are connected globally by larvae.
+Here, we show that this connectivity importantly also extends to later life stages, as marine species movements span multiple Economic Exclusive Zones, with profound implications for the management of species of high importance for revenue generation and food security.
+We found that **67% of the world’s identified fished species are transboundary**.
+Our results further highlight that these species are responsible for **80% of global-EEZs catches and 78.5% of fisheries revenue over the last decade**.
+We also find that fisheries targeting transboundary species appear worse off than those mainly catching non-transboundary species.
+Our study has direct implications for the management of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
+
+We recommend our paper to be handled by Deputy Editor Dr. Jeremy Jackson and Associate Editor Dr. Jennifer Jacquet and suggest the following reviewers:
+
+- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no  
+- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp  
+- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu  
+- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn
+
+This manuscript is not being considered for publication in any other journal.
+All data is available upon request and the code used to analyze the data can be found at https://github.com/jepa/FishForVisa.
+All contributing authors and institutions have been identified, and the authors have no competing financial interests.
+This manuscript has been reviewed and approved by all authors.
+
+Thank you for your consideration of this submission.
+Sincerely (on behalf of all authors),
+
+Juliano Palacios Abrantes  
+The Institute for Oceans and Fisheries  
+The University of British Columbia
+
+[^1]: 1.	N. Ramesh, J. A. Rising, K. L. Oremus, The small world of global marine fisheries: The cross-boundary consequences of larval dispersal. Science. 364, 1192–1196 (2019).

### 2020-03-06 Manuscript_Draft.Rmd
Changes in the manuscript for submission

@@
 title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
+author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
 date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
@@
 bibliography: ./References/FishForVisa_Ref.bib
-csl: ./References/science.csl
+csl: ./References/nature_cc.csl
 ---
@@
 
-<!-- - Journal: *Science* -->
-<!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
+<!-- - Journal: *Scientific Reports* -->
+<!-- - Information to authors (https://www.nature.com/srep/author-instructions/submission-guidelines) -->
 <!-- - There are two types of article: -->
 
-<!-- -- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance.
-Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.
+<!-- -- Articles should be no more than 11 typeset pages in length.
+As a guide, the main text (not including Abstract, Methods, References and figure legends) should be no more than 4,500 words.
+The maximum title length is 20 words.
+The Abstract (without heading) - which must be no more than 200 words long and contain no references - should serve both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications..
 -->
-
-<!-- Materials and Methods should be included in supplementary material -->
-
-<!-- --- Instructions for preparing an initial manuscript https://www.sciencemag.org/authors/instructions-preparing-initial-manuscript -->
 
@@
 <!-- - **Potential Reviewers (J)**   -->
+<!--  -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no -->
 <!--  -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp -->
@@
 <!--  -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn -->
-<!--  -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no -->
 
@@
 
-# **One Sentence Summary**
-<!-- *A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
-This will appear online adjacent to the title and should not repeat phrases already present there* -->
-
-Marine species shared by neighboring nations contribute to over 50% of catches and fishing revenue with direct implications for fisheries management.
-
-<!-- # Field code (Max. 2) -->
-
-<!-- - *Fisheries* -->
-
-# **Abstract**
+# Abstract
 <!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
-This study highlights the large and under-recognized challenge in achieving international fisheries management goals, particularly as species redistribute under climate change.
+Our analysis suggests that fisheries targeting transboundary species appear worse off than those mainly catching non-transboundary species.
+Our study has direct implications for the management of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
 
-# **Main Article**
-<!-- # Introduction (~555/500 words) -->
+# Introduction
 
@@
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
+Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
+For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
+we did not include the high seas).
 We rely on multiple data sources including occurrence, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
 
-<!-- ## Results and discussion (~1000 words) -->
+## Results and Discussion
 
@@
 
-![Fig.
-1.
-Number of transboundary species and their contribution to global fisheries catches and revenue.
+![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue.
 A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
+1B).
 China (USD 6,279 million) in E.
@@
 America regions, respectively.
-Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
 These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig S1).
+
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig.
+S1).
 Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
-Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA.
+Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
+Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk].
 Transboundary species also contribute largely to fisheries in E.
@@
 Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
-However, when we account for the total area of waters in different EEZs and regions relative to their catches, the importance of transboundary species to European fisheries become apparent (Fig.
-S2, Table S1).
+Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Fig.
+2).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+
+```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
+
+![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)
 
 We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
-2).
+3).
 Previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
+Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
 We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
@@
 
-![Fig.
-2.
+![Figure 3.
 Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig2.png)
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig3.png)
 
-Empirical analysis suggests that cooperation in the management of transboundary stocks will have better outcomes, although there are specific cases where cooperation might not be the best strategy [@Munro:2002uf].
+Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Munro:2002uf].
 Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
 Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf], and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
+<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
+However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
+-->
+
 Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
@@
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-3).
+4).
 
@@
 
-img <- readPNG(here("./Figures/Fig3.png"))
+img <- readPNG(here("./Figures/Fig4.png"))
 grid.raster(img)
@@
 
-![Fig.
-3.
+![Figure 4.
 Number of EEZs shared by transboundary species.
@@
 Showing only species that share > 20 EEZs.
-B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig3.png)
+B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig4.png)
 
@@
 We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
-S3).
+5).
 The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
 However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
-In the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
+
+```{r Call_Fig5, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
+
+img <- readPNG(here("./Figures/Fig5.png"))
+grid.raster(img)
+```
+
+![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](./Figures/Fig5.png)
+
+On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
 However, the potential boundary-crossing of these species must not be ignored.
@@
 
+# Conclusions
+
 Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
@@
 
-# **References**
-
-<div id="refs"></div>
-
-\clearpage
-
-# **Acknowledgments**
-
-We thank T.
-Clark and A.
-Tidd for helpful comments and discussions.
-**Funding**: G.R.
-was supported by the EO Wilson foundation.
-C.W.
-was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
-W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
-**Authors contributions**: J.P.A.
-Conceptualization, methodology, formal analysis, writing original draft.
-G.R.
-Methodology, data curation, writing - review & editing.
-C.W.
-Methodology, writing - review & editing.
-W.W.L.C.
-Supervision, writing - review & editing.
-All authors provided valuable input to the study conceptualization and discussed the results and analysis.
-**Competing interests**: No declared.
-**Data and materials availability**: The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-All code is available at https://github.com/jepa/FishForVisa
-
-## Data and materials availability
-All data is publicly available online and upon request from the authors.
-
-## List of Supplementary Materials
-Figures S1-S4
-Tables S1 -S2
-References in main manuscript (1-27)
-
-# **Materials and Methods**
+# Materials and Methods
 
@@
 from 0 to 1) rather than a discrete, yes or no, index.
-All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
-All code is available at https://github.com/jepa/FishForVisa.
 
@@
 Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
+
+## Statistical analysis
+
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
+All code is available at https://github.com/jepa/FishForVisa.
 We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
 We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
+In cases where the ANOVA assumptions were not clearly meet we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
 
@@
 
+# Data Availability
+The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+All code is available at https://github.com/jepa/FishForVisa
+
 \clearpage
 
-# **Supplements**
+# References
+
+<div id="refs"></div>
+
+\clearpage
+
+# Acknowledgments
+We thank T.
+Clark and A.
+Tidd for helpful comments and discussions.
+G.R.
+was supported by the EO Wilson foundation.
+C.W.
+was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
+W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
+
+# Authors contributions
+J.P.A.
+Conceptualization, methodology, formal analysis, writing original draft.
+G.R.
+Methodology, data curation, writing - review & editing.
+C.W.
+Methodology, writing - review & editing.
+W.W.L.C.
+Supervision, writing - review & editing.
+All authors provided valuable input to the study conceptualization and discussed the results and analysis.
+
+# Additional Information  
+**Competing interests**: No declared.
+
+## Supplements
 
@@
 
-![Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+![Figure S1.
+Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
 The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)
-
-Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Figure S2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
-
-```{r Call_Sup_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
-
-img <- readPNG(here("./Figures/FigS2.png"))
-grid.raster(img)
-```
-
-![Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/FigS2.png)
-
-```{r Call_Sup_3, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
-
-img <- readPNG(here("./Figures/S2_RFMO.png"))
-grid.raster(img)
-```
-
-![Number of shared species across RFMOs. Analysis included with 99 species managed by Fourteen RFMOs](./Figures/FigS3.png)
 
@@
 Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Fig.
-S3).
+S2).
 As expected, using a more relaxed value (e.g.
@@
 The current analysis utilized a 25% *Area Index* threshold (Fig.
-S3 - darker histogram).
+S2 - darker histogram).
 
@@
 
-![Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
+![Figure S2.
+Histogram of number of transboundary species using different Area Index threshold values.
+The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
 

### 2020-04-21 Scripts/Manuscript_Draft.Rmd
Re-organized folders

--- 2020-03-06 Manuscript_Draft.Rmd
@@
 # subtitle: "[DRAFT DO NOT SHARE]"
-subtitle: "Most neighbor nations share marine exploited species"
 output:
+  pdf_document:
+    fig_caption: yes
   word_document:
     # reference_docx: ./Manuscript_Instructions/science_template.docx
-  pdf_document:
-    fig_caption: yes
 geometry: margin=1in
@@
 
-```{r Ch2_setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
 
-## Results and Discussion
+# Results and Discussion
 
@@
 Points = mean +- sd.
-Revenue in 2010 real USD.](./Figures/Fig1.png)
+Revenue in 2010 real USD.](~/GitHub/FishForVisa/Figures/Fig1.png)
 
@@
 
-![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)
+![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](~/GitHub/FishForVisa/Figures/Fig2.png)
 
@@
 Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig3.png)
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](~/GitHub/FishForVisa/Figures/Fig3.png)
 
@@
 Showing only species that share > 20 EEZs.
-B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig4.png)
+B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](~/GitHub/FishForVisa/Figures/Fig4.png)
 
@@
 
-![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](./Figures/Fig5.png)
+![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](~/GitHub/FishForVisa/Figures/Fig5.png)
 
@@
 This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
-S3).
+S2).
 
@@
 However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig.
-S4).
+S2).
 
@@
 Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)
+The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png)
 
@@
 
-img <- readPNG(here("./Figures/S3_Area.png"))
+img <- readPNG(here("./Figures/FigS4.png"))
 grid.raster(img)
@@
 Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
+The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS4.png)
 

### 2020-04-26 Scripts/Manuscript_Draft.Rmd
Update Manuscript_Draft.Rmd

@@
 ```
-
-<!-- # Instructions for submission -->
-
-<!-- - Journal: *Scientific Reports* -->
-<!-- - Information to authors (https://www.nature.com/srep/author-instructions/submission-guidelines) -->
-<!-- - There are two types of article: -->
-
-<!-- -- Articles should be no more than 11 typeset pages in length.
-As a guide, the main text (not including Abstract, Methods, References and figure legends) should be no more than 4,500 words.
-The maximum title length is 20 words.
-The Abstract (without heading) - which must be no more than 200 words long and contain no references - should serve both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications..
--->
-
-<!-- # Reviewers (5): -->
-<!-- *Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*   -->
-
-<!-- **Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions) -->
-
-<!-- - **Potential Reviewers (J)**   -->
-<!--  -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no -->
-<!--  -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp -->
-<!--  -- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu -->
-<!--  -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn -->
-
-<!-- - **Excluded Reviewers (J)**   -->
 

### 2020-04-29 Scripts/Manuscript_Draft.Rmd
Updates for submission

--- 2020-04-21 Scripts/Manuscript_Draft.Rmd
@@
 ^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
-# subtitle: "[DRAFT DO NOT SHARE]"
+subtitle: "[DO NOT SHARE]"
 output:
@@
   chunk_output_type: inline
-bibliography: ./References/FishForVisa_Ref.bib
-csl: ./References/nature_cc.csl
+bibliography: ../References/FishForVisa_Ref.bib
+csl: ../References/nature_cc.csl
 ---
@@
 # Run this chunk before knit so you make sure you have all pkgs installed in R
-
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg)) 
-    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
-  sapply(pkg, require, character.only = TRUE)
-}
+library(MyFunctions)
 
@@
 
-ipak(packages)
+my_lib(packages)
 
@@
 
-# Abstract
+## Abstract
 <!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 65 billion) in the last decade.
+We found that 67% of the world’s identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 65 billion) in the last decade.
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
 Our analysis suggests that fisheries targeting transboundary species appear worse off than those mainly catching non-transboundary species.
-Our study has direct implications for the management of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
+This study has direct implications for the management of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
 
-# Introduction
+## Introduction
 
@@
 
-# Results and Discussion
+## Results and Discussion
 
@@
 Regions according to the United Nations sub-regions.
-Points = mean +- sd.
+Points = mean $\mp$ sd.
 Revenue in 2010 real USD.](~/GitHub/FishForVisa/Figures/Fig1.png)
@@
 
-![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](~/GitHub/FishForVisa/Figures/Fig2.png)
+![**Figure 2.** Weighted benefits of transboundary species by $kmK2$ and UN sub-region.
+A) Million 2010 USD.
+B) Million tons.
+Point sub-region average bars $\mp$ s.d.](~/GitHub/FishForVisa/Figures/Fig2.png)
+**NOTE to legend: These are not million. They are probably thousand**
 
@@
 Showing only species that share > 20 EEZs.
-B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](~/GitHub/FishForVisa/Figures/Fig4.png)
+B) Catchs of main fishing countries fishing each ecosystem preference’s top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014](~/GitHub/FishForVisa/Figures/Fig4.png)
 
@@
 
-# Conclusions
+## Conclusions
 
@@
 
-# Materials and Methods
+## Materials and Methods
 
-## Databases of species' geographic distribution
+### Databases of species' geographic distribution
 
@@
 
-```{r Data_Table, eval = F, echo = F}
+```{r Data_Table, eval = T, echo = F}
 
@@
   rename("Main Method"=Main_Method) %>% 
-  # kable("latex", booktabs = T,
-  #       caption = "Summary of data sources to estimate species' distributions.
+  kable("latex", booktabs = T,
+        caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
 All data is publically available, see references for details.") %>%
-  # kable_styling(full_width = F) %>%
-  # column_spec(2,width = "8cm") %>% #wraps text in column2
-  # column_spec(3,width = "3cm") %>% #wraps text in column2
-  write_csv("Table_1.csv")
+  kable_styling(full_width = F) %>%
+  column_spec(2,width = "8cm") %>% #wraps text in column2
+  column_spec(3,width = "3cm") #%>% #wraps text in column2
+  # write_csv("Table_1.csv")
 
@@
 
-### *Occurrence data*
+#### *Occurrence data*
 
@@
 
-### *Distribution models*
+#### *Distribution models*
 
@@
 
-### *Catch data*
+#### *Catch data*
 
@@
 
-## Determining transboundary species trait
+### Determining transboundary species trait
 
@@
 
-### Criteria 1; Neighboring EEZs
+#### Criteria 1; Neighboring EEZs
 
@@
 
-### Criteria 2; Data agreement
+#### Criteria 2; Data agreement
 
@@
 
-### Criteria 3; Modeling verification
+#### Criteria 3; Modeling verification
 
@@
 
-### Criteria 4; Spatial distribution
+#### Criteria 4; Spatial distribution
 
@@
 
-## Fisheries trends
+### Fisheries trends
 
@@
 
-## Statistical analysis
+### Statistical analysis
 
@@
 
-```{r Status_Table, eval = F, echo = F}
+```{r Status_Table, eval = T, echo = F}
 
@@
            Rules) %>% 
-  # kable("latex", booktabs = T,
-  #       caption = "Rules to determine the category of each transboundary species") %>%
-  # kable_styling(full_width = F) %>%
-  # column_spec(1,width = "3cm") %>% #wraps text in column2
-  # column_spec(2,width = "13cm") %>% #wraps text in column2
-  write_csv("Table_2.csv")
+  kable("latex", booktabs = T,
+        caption = "Rules to determine the category of each transboundary species") %>%
+  kable_styling(full_width = F) %>%
+  column_spec(1,width = "3cm") %>% #wraps text in column2
+  column_spec(2,width = "13cm") #%>% #wraps text in column2
+  # write_csv("Table_2.csv")
 
@@
 
-## Key uncertainties
+### Key uncertainties
 <!-- # Related to Criteria 1 (neighbors) -->
@@
 Likewise, the spatial allocation of the catch is subjected to impressions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
-However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and @Zeller2016 for mode details in the spatial allocation of the SAU).
+However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and [@Zeller2016] for model details in the spatial allocation of the SAU).
 <!-- Related to Criteria 4; Spatial distribution -->
@@
 
-# Data Availability
-The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-All code is available at https://github.com/jepa/FishForVisa
+<!-- Commented out for Thesis -->
+<!-- ## Data Availability -->
+<!-- The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+All code is available at https://github.com/jepa/FishForVisa -->
 
-\clearpage
+<!-- \clearpage -->
 
-# References
+<!-- ## References -->
 
-<div id="refs"></div>
+<!-- <div id="refs"></div> -->
 
-\clearpage
+<!-- \clearpage -->
 
-# Acknowledgments
-We thank T.
+<!-- ## Acknowledgments -->
+<!-- We thank T.
 Clark and A.
@@
 W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
+-->
 
-# Authors contributions
-J.P.A.
+<!-- ## Authors contributions -->
+<!-- J.P.A.
 Conceptualization, methodology, formal analysis, writing original draft.
@@
 All authors provided valuable input to the study conceptualization and discussed the results and analysis.
+-->
 
-# Additional Information  
-**Competing interests**: No declared.
+<!-- ## Additional Information   -->
+<!-- **Competing interests**: No declared.  -->
 
@@
 
-img <- readPNG(here("./Figures/FigS4.png"))
+img <- readPNG(here("./Figures/FigS2.png"))
 grid.raster(img)
@@
 Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS4.png)
+The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS2.png)
 

### 2020-05-03 Scripts/Manuscript_Draft.Rmd
Modified manuscript for thesis

@@
 ---
-title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
-date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
-^2^Yale University, New Haven, Connecticut, USA.
-^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
-subtitle: "[DO NOT SHARE]"
 output:
-  pdf_document:
-    fig_caption: yes
-  word_document:
-    # reference_docx: ./Manuscript_Instructions/science_template.docx
+  bookdown::pdf_book:
+    toc : no
+    keep_tex: no
+    number_sections: yes
+    fig_width: 6 
+    fig_height: 4 
 geometry: margin=1in
@@
 csl: ../References/nature_cc.csl
+header-includes: #allows you to add in your own Latex packages
+- \usepackage{float} #use the 'float' package
+- \floatplacement{figure}{H} #make every figure with caption = h
 ---
-
-* **Corresponding author**: j.palacios@oceans.ubc.ca
 
@@
 
-## Results and Discussion
-
-We identified 633 transboundary exploited species in the world, more than double the previous estimates [@Teh:2015gd], representing 67.5% of the species analyzed.
-Between 2005 and 2014, national fleets targeting transboundary species within EEZs cached an average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
-This is equivalent to 78.5% of the global fishing revenue of the same period.
-These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
-Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
-For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador.
-The contribution of discrete species was 14.8 million tons representing USD 22,167 million in fishing revenue.
-Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary.
-These species represented only 2.8 million tons and 3,691 million USD between 2005 and 2014.
-These results underscore the importance of transboundary species at the global level (Fig.
-1).
-
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catches and revenue.
-A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-B) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions according to the United Nations sub-regions.
-Points = mean +- sd.
-Revenue in 2010 real USD"}
-
-img <- readPNG(here("./Figures/Fig1.png"))
-grid.raster(img)
-
-```
-
-![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue.
-A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-B) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions according to the United Nations sub-regions.
-Points = mean $\mp$ sd.
-Revenue in 2010 real USD.](~/GitHub/FishForVisa/Figures/Fig1.png)
-
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
-1B).
-China (USD 6,279 million) in E.
-Asia and the USA (USD 9,605 million) contribute 55% and 82% to the total revenues from the E.
-Asia and N.
-America regions, respectively.
-In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
-These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
-
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig.
-S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
-Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk].
-Transboundary species also contribute largely to fisheries in E.
-Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
-Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Fig.
-2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
-
-```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
-
-img <- readPNG(here("./Figures/Fig2.png"))
-grid.raster(img)
-```
-
-![**Figure 2.** Weighted benefits of transboundary species by $kmK2$ and UN sub-region.
-A) Million 2010 USD.
-B) Million tons.
-Point sub-region average bars $\mp$ s.d.](~/GitHub/FishForVisa/Figures/Fig2.png)
-**NOTE to legend: These are not million. They are probably thousand**
-
-We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
-3).
-Previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
-We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
-Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table S2).
-Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
-This result suggests that the management of discrete species could be better off as the variation between Categories A and B is closer (*p* = 0.052) than for transboundary species (*p* = 0.001).
-
-```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch"}
-
-img <- readPNG(here("./Figures/Fig2.png"))
-grid.raster(img)
-```
-
-![Figure 3.
-Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](~/GitHub/FishForVisa/Figures/Fig3.png)
-
-Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Munro:2002uf].
-Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
-Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf], and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
-<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
-However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
--->
-
-Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
-The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
-Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
-Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
-
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-4).
-
-```{r Call_Spp_Circular, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
-
-img <- readPNG(here("./Figures/Fig4.png"))
-grid.raster(img)
-```
-
-![Figure 4.
-Number of EEZs shared by transboundary species.
-A) Number of EEZs by species organized by associated habitat according to FishBase.
-Showing only species that share > 20 EEZs.
-B) Catchs of main fishing countries fishing each ecosystem preference’s top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014](~/GitHub/FishForVisa/Figures/Fig4.png)
-
-Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
-Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
-We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
-5).
-The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
-
-```{r Call_Fig5, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
-
-img <- readPNG(here("./Figures/Fig5.png"))
-grid.raster(img)
-```
-
-![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](~/GitHub/FishForVisa/Figures/Fig5.png)
-
-On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
-However, the potential boundary-crossing of these species must not be ignored.
-The world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Payne:2008vm].
-Many coastal communities, particularly in developing regions, are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
-For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-3B) are among the highest fish consumption countries [@FAO:2018KK].
-In these countries, both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
-In the case of Kiribati, the Solomon Islands and Papua New Guinea, they are parties to the Pacific Nauru Agreement that sustainable manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
-
-## Conclusions
-
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated.
-This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
-Moreover, we show significant differences in the management of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
-Previous work has found that collaboration will result in better outcomes for shared marine resources [@Munro:2002uf].
-Thus, countries should pay specific attention in the management of the identified transboundary stocks potentially creating collaborative management plans.
-Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
-
 ## Materials and Methods
@@
 Our final sample represents 63.2% of identified species, accounting for 96.52% of the catch identified at the species' level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:CallTable1)).
 Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result.
@@
 
-Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data is publicly available (see Acknowledgments).
+<!-- Table 1.
+Summary of data sources to estimate species' distributions.
+All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude.
+All data is publicly available (see Acknowledgments).
+-->
 
-```{r Data_Table, eval = T, echo = F}
+```{r CallTable1, eval = T, echo = F}
 
@@
 All data is publically available, see references for details.") %>%
-  kable_styling(full_width = F) %>%
-  column_spec(2,width = "8cm") %>% #wraps text in column2
-  column_spec(3,width = "3cm") #%>% #wraps text in column2
+  kable_styling(full_width = T) %>%
+  column_spec(2,width = "2cm") %>% #wraps text in column2
+  column_spec(3,width = "5cm") #%>% #wraps text in column2
   # write_csv("Table_1.csv")
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
-S2).
+This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(fig:Call-Sup-2)).
 
@@
 present, maximum and minimum EEZ's historical catch) and the year (e.g.
-year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
+year of maximum historical catch of the species within that EEZ) (Table Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
 Following this concept, Category A would represent fisheries that are re-building or under-exploited, Category B would be species that are sustainable harvested, and Category C would be species that are over-exploited.
@@
 
-Table 2. Rules to determine the category of each analyzed species.
+<!-- Table 2. Rules to determine the category of each analyzed species. -->
 
-```{r Status_Table, eval = T, echo = F}
+```{r CallTab2, eval = T, echo = F}
 
@@
            Rules) %>% 
-  kable("latex", booktabs = T,
+  kable("latex", 
+        booktabs = T,
         caption = "Rules to determine the category of each transboundary species") %>%
-  kable_styling(full_width = F) %>%
+  kable_styling(full_width = T) %>%
   column_spec(1,width = "3cm") %>% #wraps text in column2
@@
 This presents a relative conservative estimate of the number of transboundary species in the world.
-However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig.
-S2).
+However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Figure \@(fig:CallSup2)).
 
-<!-- Commented out for Thesis -->
-<!-- ## Data Availability -->
-<!-- The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-All code is available at https://github.com/jepa/FishForVisa -->
+## Results and Discussion
 
-<!-- \clearpage -->
+We identified 633 transboundary exploited species in the world, more than double the previous estimates [@Teh:2015gd], representing 67.5% of the species analyzed.
+Between 2005 and 2014, national fleets targeting transboundary species within EEZs cached an average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
+This is equivalent to 78.5% of the global fishing revenue of the same period.
+These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
+Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
+For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador.
+The contribution of discrete species was 14.8 million tons representing USD 22,167 million in fishing revenue.
+Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary.
+These species represented only 2.8 million tons and 3,691 million USD between 2005 and 2014.
+These results underscore the importance of transboundary species at the global level (Figure \@ref(fig:Figure1)).
 
-<!-- ## References -->
+\clearpage
 
-<!-- <div id="refs"></div> -->
+```{r Figure1, eval = T, fig.width=9, fig.height=12, echo=FALSE, fig.cap="Number of transboundary species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+B) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions according to the United Nations sub-regions.
+Points = mean +- sd.
+Revenue in 2010 real USD"}
 
-<!-- \clearpage -->
+img <- readPNG("~/GitHub/FishForVisa/Figures/Fig1.png")
+grid.raster(img)
 
-<!-- ## Acknowledgments -->
-<!-- We thank T.
-Clark and A.
-Tidd for helpful comments and discussions.
-G.R.
-was supported by the EO Wilson foundation.
-C.W.
-was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
-W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
+```
+
+<!-- ![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+B) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions according to the United Nations sub-regions.
+Points = mean $\mp$ sd.
+Revenue in 2010 real USD.](~/GitHub/FishForVisa/Figures/Fig1.png) -->
+
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Figure \@ref(fig:Figure1)B).
+China (USD 6,279 million) in E.
+Asia and the USA (USD 9,605 million) contribute 55% and 82% to the total revenues from the E.
+Asia and N.
+America regions, respectively.
+In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
+
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Figure \@(fig:CallSup1)).
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
+Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
+Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk].
+Transboundary species also contribute largely to fisheries in E.
+Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
+Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Figure \@ref(fig:CallFigure2)).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TabSup2)), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+
+```{r CallFigure2, eval = t, echo=FALSE, fig.pos = "H", fig.cap="Weighted benefits of transboundary species by $kmK2$ and UN sub-region.
+A) Million 2010 USD.
+B) Tons.
+Point sub-region average bars +- s.d."}
+
+img <- readPNG("~/GitHub/FishForVisa/Figures/Fig2.png")
+grid.raster(img)
+```
+
+<!-- ![**Figure 2.** Weighted benefits of transboundary species by $kmK2$ and UN sub-region.
+A) Million 2010 USD.
+B) Million tons.
+Point sub-region average bars $\mp$ s.d.](~/GitHub/FishForVisa/Figures/Fig2.png) -->
+
+We determined the exploitation category of each species according to the catch trend within each EEZ (Figure \@ref(fig:CallFigure3)).
+Previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
+Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
+We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
+Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table \@ref(tab:TabSup2)).
+Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
+This result suggests that the management of discrete species could be better off as the variation between Categories A and B is closer (*p* = 0.052) than for transboundary species (*p* = 0.001).
+
+```{r CallFigure3, eval = T, fig.width = 10, fig.height = 12, echo=FALSE, fig.cap="Number of transboundary species by catch category.
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch"}
+
+img <- readPNG("~/GitHub/FishForVisa/Figures/Fig3.png")
+grid.raster(img)
+```
+
+<!-- ![Figure 3.
+Number of transboundary species by catch category.
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](~/GitHub/FishForVisa/Figures/Fig3.png) -->
+
+Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Munro:2002uf].
+Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf], and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
+<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
+However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
 -->
 
-<!-- ## Authors contributions -->
-<!-- J.P.A.
-Conceptualization, methodology, formal analysis, writing original draft.
-G.R.
-Methodology, data curation, writing - review & editing.
-C.W.
-Methodology, writing - review & editing.
-W.W.L.C.
-Supervision, writing - review & editing.
-All authors provided valuable input to the study conceptualization and discussed the results and analysis.
--->
+Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
+Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
+Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
+Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
 
-<!-- ## Additional Information   -->
-<!-- **Competing interests**: No declared.  -->
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:CallFigure4)).
+
+```{r CallFigure4, eval = T, fig.width = 10, fig.height = 10, echo=FALSE, fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+
+img <- readPNG("~/GitHub/FishForVisa/Figures/Fig4.png")
+grid.raster(img)
+```
+
+<!-- ![Figure 4.
+Number of EEZs shared by transboundary species.
+A) Number of EEZs by species organized by associated habitat according to FishBase.
+Showing only species that share > 20 EEZs.
+B) Catchs of main fishing countries fishing each ecosystem preference’s top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014](~/GitHub/FishForVisa/Figures/Fig4.png) -->
+
+Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
+Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
+We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Figure \@ref(fig:CallFigure5)).
+The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
+
+```{r CallFigure5, eval = T, echo = FALSE, fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
+
+img <- readPNG("~/GitHub/FishForVisa/Figures/Fig5.png")
+grid.raster(img)
+```
+
+<!-- ![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](~/GitHub/FishForVisa/Figures/Fig5.png) -->
+
+On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
+However, the potential boundary-crossing of these species must not be ignored.
+The world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Payne:2008vm].
+Many coastal communities, particularly in developing regions, are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
+For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Figure \@ref(fig:CallFigure3)B) are among the highest fish consumption countries [@FAO:2018KK].
+In these countries, both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
+In the case of Kiribati, the Solomon Islands and Papua New Guinea, they are parties to the Pacific Nauru Agreement that sustainable manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
+
+## Conclusions
+
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
+Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated.
+This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
+Moreover, we show significant differences in the management of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
+Previous work has found that collaboration will result in better outcomes for shared marine resources [@Munro:2002uf].
+Thus, countries should pay specific attention in the management of the identified transboundary stocks potentially creating collaborative management plans.
+Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
 
@@
 
-```{r Call_Sup_1, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
+```{r CallSup1, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
 The number of species is represented in the EEZ while the catch (thousand tons) is represented in the land polygon."}
 
-img <- readPNG(here("./Figures/S1_Catch_EEZ.png"))
+img <- readPNG("../Figures/FigS1.png")
 grid.raster(img)
@@
 
-![Figure S1.
+<!-- ![Figure S1.
 Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png)
+The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png) -->
 
 The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Fig.
-S2).
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:Call-Sup-2)).
 As expected, using a more relaxed value (e.g.
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Fig.
-S2 - darker histogram).
+The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup2) darker histogram).
 
-```{r Call_Sup_4, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Histogram of transboundary species using different values of Area Index.
+```{r CallSup2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.cap="Histogram of transboundary species using different values of Area Index.
 Darker histogram represents used value (25%) in the analysis"}
 
-img <- readPNG(here("./Figures/FigS2.png"))
+img <- readPNG("../Figures/FigS2.png")
 grid.raster(img)
@@
 
-![Figure S2.
+<!-- ![Figure S2.
 Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS2.png)
+The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS2.png) -->
 

### 2020-05-03 Scripts/Manuscript_Draft.Rmd
Fixed supplement references

@@
 This presents a relative conservative estimate of the number of transboundary species in the world.
-However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Figure \@(fig:CallSup2)).
+However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Figure \@ref(fig:CallSup2)).
 
@@
 
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Figure \@(fig:CallSup1)).
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Figure \@ref(fig:CallSup1)).
 Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
@@
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup2) darker histogram).
+The current analysis utilized a 25% *Area Index* threshold (Figure \@ref(fig:CallSup2) darker histogram).
 

### 2020-06-09 Scripts/Initial_Analysis.Rmd
Re-organized folders
Updates for submission
Re-organization of files

--- 2020-03-04 Initial_Analysis.Rmd
@@
 #### READ ME !!! ####
-# Run this chunk before knit so you make sure you have all pkgs installed in R
-
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg)) 
-    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
-  sapply(pkg, require, character.only = TRUE)
-}
+library(MyFunctions)
 
@@
 
-ipak(packages)
-
-ggtheme_map <- function(base_size = 9, Region = "NA") {
-
-  theme(text             = element_text(#family = "Helvetica",
-    color = "gray30", size = base_size),
-    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
-    panel.background = element_blank(),
-    panel.border     = element_blank(),
-    panel.grid.minor = element_blank(),
-    panel.grid.major = element_line(color = "transparent"),
-    strip.background =element_rect(fill = "transparent"),
-    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
-    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
-    axis.ticks       = element_blank(),
-    axis.text        = element_blank(),
-    axis.title       = element_blank(),
-    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
-    legend.position = "bottom",
-    legend.key.width =unit(5,"line")
-  )
-}
-
-ggtheme_plot <- function() {
-  theme(
-    plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
-    panel.background = element_blank(),
-    strip.background = element_blank(),
-    # strip.text       = element_text(size = base_size, face = "italic"),
-    panel.border     = element_blank(),
-    panel.grid.minor = element_blank(),
-    panel.grid.major = element_blank(),
-    axis.ticks = element_blank(),
-    axis.text.x = element_text(size = 12,
-                               angle = 0,
-                               face = "plain"),
-    axis.text.y = element_text(size = 12),
-    axis.title = element_text(size = 14),
-    legend.key = element_rect(colour = NA, fill = NA),
-    legend.position  = "right",
-    legend.title = element_text(size = 14, face = "bold"),
-    legend.text = element_text(size = 16),
-    strip.text.x = element_text(size = 12, colour = "black", face = "bold"),
-    strip.text = element_text(size = 12)
-  )
-}
+my_lib(packages)
 
@@
 
-## Load Results data
-
-In here we load and cleaned the multiple external data sets required to produce the manuscript figures
-
-```{r Load_Results_Data, eval = F}
-
-# Set Jurisdiction to EEZ or RFMO
-Jurisdiction <- "EEZ"
-# Jurisdiction <- "RFMO"
-
-# Updates result's path for the jurisdiction
-Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
-
-# Species list to get species names
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep="")) %>% 
-  clean_names()
-
-Species_Sampled <- fread(paste(Data_Path,"Distribution_Data/Sampled_Species.csv", sep =""))
-
-Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep="")) %>% 
-  clean_names()
-
-# Spatial Data needed to remove duplicates
-sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep="")) %>% 
-  clean_names()
+### Clean names table
+
+Create a table that matches all names
+
+```{r names_table, eval =F, echo =F}
 
@@
   ### Manually Fix names for estimating catch
-  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece",
+  mutate(sf_eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
                               ifelse(eez_name =="Greenland (Denmark)","Greenland",
@@
                                                                                ifelse(fishing_entity == "Korea (North)","Korea (North)",
-                                                                                   paste(eez_name))
-                                                                     )
-                                                              )
-                                                       )))))),
+                                                                                      ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
+                                                                                             ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
+                                                                                                    ifelse(eez_name =="Viet Nam","Vietnam",
+                                                                                                           ifelse(eez_name =="US Virgin Isl.","US Virgin Islands",
+                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain (Mediterranean and Gulf of Cadiz)",
+                                                                                                                         paste(eez_name)
+                                                                                                                  )
+                                                                                                           )
+                                                                                                    )
+                                                                                             ))))))))))
+  ),	
   fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
@@
 # UN Regions dataset
-UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
+UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
   clean_names() %>% 
-  group_by(fishing_entity = country_or_area,
+  mutate(un_fishing_entity = country_or_area) %>% 
+  group_by(un_fishing_entity,
+           fishing_entity = country_or_area,
            georegion = region_name,
@@
     fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
+    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
     fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
@@
     fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
+  ) %>% 
+  mutate(
+    fishing_entity = ifelse(un_fishing_entity == "Congo","Congo, R. of",
+                            ifelse(un_fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
+    )
+  )
+
+# The path
+path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")
+
+# The File
+fnam_world <- "SAUEEZ_July2015.shp"
+
+# Load it!
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(eez_name = Name)
+
+World_sf_df <- as.tibble(World_sf) %>% 
+  select(sf_eez_name=eez_name,sf_objectid=OBJECTID,sf_eezid=EEZID)
+
+# Vicky
+Clean_sau_eez_fes_new <- Clean_sau_eez_fes %>% 
+  left_join(UN_Regions) %>% 
+  select(-`n()`) %>% 
+  full_join(World_sf_df) %>% 
+  select(1:3,4,8,9,everything())
+
+#  Now check tim sau data
+SAU_Tim_Data %>% 
+  anti_join(Clean_sau_eez_fes_new) %>% 
+  group_by(fishing_entity_id) %>% 
+  summarise(n())
+
+write_csv(Clean_sau_eez_fes_new,
+          "matching_names.csv")
+
+```
+
+## Load Results data
+
+In here we load and cleaned the multiple external data sets required to produce the manuscript figures
+
+```{r Load_Results_Data, eval = F}
+
+Results_Path <- my_path("R")
+
+# Set Jurisdiction to EEZ or RFMO
+Jurisdiction <- "EEZ"
+# Jurisdiction <- "RFMO"
+
+# Updates result's path for the jurisdiction
+Results_Path <- paste(my_path("R"),Jurisdiction,"/",sep="")
+
+# Species list to get species names
+Exploited_Species <- fread(paste(my_path("D"),"Distribution/Species/exploited_species_list.csv",sep="")) %>% 
+  clean_names()
+
+Species_Sampled <- fread(paste(my_path("D"),"Distribution/Sampled_Species.csv", sep =""))
+
+Spp_Clasification <- fread(paste(my_path("D"),"Distribution/Species/SppTaxonName.csv",sep="")) %>% 
+  clean_names()
+
+# Spatial Data needed to remove duplicates
+sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
+  clean_names()
+
+Clean_sau_eez_fes <- sau_eez_fes %>% 
+  gather("Type","fishing_region",2,4) %>% 
+  left_join(sau_eez_fes,
+            by = ("fishing_entity_id")
+  ) %>% 
+  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
+  summarise(n()) %>% 
+  ungroup() %>% 
+  ### Manually Fix names for estimating catch
+  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
+                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
+                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
+                                         ifelse(fishing_entity =="Italy","Italy",
+                                                ifelse(eez_name =="Chile (mainland)","Chile",
+                                                       ifelse(fishing_entity =="Brazil","Brazil",
+                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
+                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
+                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
+                                                                                   ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
+                                                                                          ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
+                                                                                          paste(eez_name)
+                                                                                          )
+                                                                                   )
+                                                                            )
+                                                       )))))))
+                           ),
+         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
+         )
+  )
+
+# UN Regions dataset
+UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
+  clean_names() %>% 
+  # mutate(un_fishing_entity = country_or_area) %>% 
+  group_by(#un_fishing_entity,
+           fishing_entity = country_or_area,
+           georegion = region_name,
+           sub_region = sub_region_name) %>% 
+  summarise(n=n()) %>% #merge china's 3 rows
+  select(-n) %>% 
+  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
+  ungroup() %>% 
+  # Change names to match SAU data and for shorter versions
+  mutate(
+    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
+    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
+    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
+    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
+    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
+    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
+    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
+    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
+    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
+    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
+    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
+    fishing_entity = gsub(" and ", " & ",fishing_entity),
+    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
+    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
+    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
+    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
+    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
+    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
+    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
+  ) %>% 
+  mutate(
+    fishing_entity = ifelse(fishing_entity == "Congo","Congo, R. of",
+                            ifelse(fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
+                            )
   )
@@
 # Manually change congo
-UN_Regions[52,1] <- "Congo, R. of"
+# UN_Regions[52,1] <- "Congo, R. of"
 
 # Load Land shapefile
-path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
+path_world_land <- paste(my_path("G"),"Spatial/ne_50m_admin_0_countries/ne_50m_admin_0_countries",sep="")
 
@@
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
+path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")
 
@@
   rename(eez_name = Name)
-
-# View(unique(World_sf$eez_name))
 
@@
 # Read Sau Value Data (Thank you Tim!)
-SAU_Tim_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep =""))
+SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep =""))
 
@@
 # Read Species Status Data (Sub-routine Species Status)
-Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep ="")) %>% 
+Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
   clean_names() %>% 
-  rename(eez_name=territory)
+  rename(sf_eez_name=territory)
 
@@
 
-Clean_Results_Trans <- fread(paste(Data_Path,"Results/EEZ/Clean_Results_Trans.csv", sep =""))
+Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep =""))
 

### 2020-06-09 Scripts/Manuscript_Draft.Rmd
Re-organization of files

--- 2020-04-29 Scripts/Manuscript_Draft.Rmd
@@
 title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
+author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
 date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
@@
 ^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
-subtitle: "[DO NOT SHARE]"
+# subtitle: "[DRAFT DO NOT SHARE]"
+subtitle: "Most neighbor nations share marine exploited species"
 output:
+  word_document:
+    # reference_docx: ./Manuscript_Instructions/Science_Advances/SA.MS.Template_2018.docx
   pdf_document:
     fig_caption: yes
-  word_document:
-    # reference_docx: ./Manuscript_Instructions/science_template.docx
 geometry: margin=1in
@@
   chunk_output_type: inline
-bibliography: ../References/FishForVisa_Ref.bib
-csl: ../References/nature_cc.csl
+bibliography: ./References/FishForVisa_Ref.bib
+csl: ./References/science.csl
 ---
@@
 # Run this chunk before knit so you make sure you have all pkgs installed in R
-library(MyFunctions)
+
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg)) 
+    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
+  sapply(pkg, require, character.only = TRUE)
+}
 
@@
 
-my_lib(packages)
+ipak(packages)
 
@@
 
-## Abstract
+<!-- # Instructions for submission -->
+
+<!-- - Journal: *Science Advances* -->
+<!-- - Information to authors (https://advances.sciencemag.org/content/information-authors) -->
+<!-- - Research articles: -->
+
+<!-- Research articles should present a major advance and can be short or long (maximum 15,000 words) format.
+Submissions must include an abstract (up to 150 words), an introduction, and sections with brief informative subheadings.
+You may include up to six figures and/or tables and about 40 references.
+Supplementary materials should be limited to information that is not essential for the general understanding of the research presented in the main text and can include data sets, figures, tables, videos, or audio files.
+You may include up to a total of ten figures and/or tables (combined) throughout the supplemental text.
+-->
+
+<!-- # Reviewers (4): -->
+<!-- *Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*   -->
+
+<!-- **Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions) -->
+
+<!-- - **Potential Reviewers (J)**   -->
+<!--  -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp -->
+<!--  -- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu -->
+<!--  -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn -->
+<!--  -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no -->
+
+<!-- - **Excluded Reviewers (J)**   -->
+
+<!-- # **One Sentence Summary** -->
+<!-- *A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
+This will appear online adjacent to the title and should not repeat phrases already present there* -->
+
+<!-- Marine species shared by neighboring nations contribute to over 50% of catches and fishing revenue with direct implications for fisheries management. -->
+
+# **Abstract**
 <!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the world’s identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 65 billion) in the last decade.
+We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 65 billion) in the last decade.
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
-Our analysis suggests that fisheries targeting transboundary species appear worse off than those mainly catching non-transboundary species.
-This study has direct implications for the management of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
+This study highlights the large and under-recognized challenge in achieving international fisheries management goals, particularly as species redistribute under climate change.
 
-## Introduction
+# Introduction
 
@@
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
-For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
-we did not include the high seas).
 We rely on multiple data sources including occurrence, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
 
-## Results and Discussion
+# Results
 
-We identified 633 transboundary exploited species in the world, more than double the previous estimates [@Teh:2015gd], representing 67.5% of the species analyzed.
+## Catch and revenue contribution of transboundary species
+
+We identified 633 transboundary exploited species in the world representing 67.5% of the species analyzed (Fig 1.).
 Between 2005 and 2014, national fleets targeting transboundary species within EEZs cached an average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
 This is equivalent to 78.5% of the global fishing revenue of the same period.
-These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
 Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
@@
 These species represented only 2.8 million tons and 3,691 million USD between 2005 and 2014.
-These results underscore the importance of transboundary species at the global level (Fig.
-1).
 
@@
 
-![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue.
+![Fig.
+1.
+Number of transboundary species and their contribution to global fisheries catches and revenue.
 A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 Regions according to the United Nations sub-regions.
-Points = mean $\mp$ sd.
-Revenue in 2010 real USD.](~/GitHub/FishForVisa/Figures/Fig1.png)
+Points = mean +- sd.
+Revenue in 2010 real USD.](./Figures/Fig1.png)
 
 We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
-1B).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
 China (USD 6,279 million) in E.
@@
 America regions, respectively.
-In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
 These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
-
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig.
-S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
-Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk].
-Transboundary species also contribute largely to fisheries in E.
+Transboundary species also contribute largely to fisheries catch in E.
 Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
 Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
+
 Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Fig.
@@
 
-```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+```{r Call_Fig2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
 
@@
 
-![**Figure 2.** Weighted benefits of transboundary species by $kmK2$ and UN sub-region.
-A) Million 2010 USD.
-B) Million tons.
-Point sub-region average bars $\mp$ s.d.](~/GitHub/FishForVisa/Figures/Fig2.png)
-**NOTE to legend: These are not million. They are probably thousand**
+![Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)
+
+## Exploitation category
 
 We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
-3).
-Previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
+2).
 We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
@@
 Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
-This result suggests that the management of discrete species could be better off as the variation between Categories A and B is closer (*p* = 0.052) than for transboundary species (*p* = 0.001).
 
@@
 
-img <- readPNG(here("./Figures/Fig2.png"))
+img <- readPNG(here("./Figures/Fig3.png"))
 grid.raster(img)
@@
 
-![Figure 3.
+![Fig.
+3.
 Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](~/GitHub/FishForVisa/Figures/Fig3.png)
+Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig3.png)
 
-Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Munro:2002uf].
-Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
-Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf], and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
-<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
-However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
--->
+## Transboundary species occurs at multiple ecosystem preferences
 
-Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
-The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
-Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
-Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
-
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+We categorized species based on their habitat preference and found transboundary species in all cases (Fig 4.).
+However, species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-4).
+3).
 
@@
 
-![Figure 4.
+![Fig.
+4.
 Number of EEZs shared by transboundary species.
@@
 Showing only species that share > 20 EEZs.
-B) Catchs of main fishing countries fishing each ecosystem preference’s top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014](~/GitHub/FishForVisa/Figures/Fig4.png)
+B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig4.png)
 
@@
 Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
-We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
+When applying our analysis at the RFMO level (rather than EEZs), we found that 81.8% of the 99 species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
 5).
-The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
 
@@
 
-![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](~/GitHub/FishForVisa/Figures/Fig5.png)
+![Number of shared species across RFMOs. Analysis included with 99 species managed by Fourteen RFMOs](./Figures/Fig5.png)
 
-On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
+# **Discussion**
+
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
+The number of tranbsoundary species identified in this study are more than double the previous estimates [@Teh:2015gd].
+Similarly, the catch and benefit from these species are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
+These results underscore the importance of transboundary species at the global level.
+China, Japan, Peru, Russia and the USA are among the top seven mejor fishing producers of the world [@FAO:2018KK] and were identified as the nations who economically benefit the most from transboundary species.
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig S1).
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
+Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA.
+Finally, when we account for the total area of waters in different EEZs and regions relative to their catches, the importance of transboundary species to Northern European fisheries become apparent.
+
+Many environmental and social-economic factors (e.g.
+temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk].
+Nevertheless, previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
+Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
+Our results suggests that the management of discrete species could be better off as the variation between Categories A and B are closer (p = 0.052) than for transboundary species (p = 0.002).
+Such result has direct implications for the management of transboundary species, suggesting an urgent need for strengthened international cooperation in the management of these fisheries.
+Empirical analysis suggests that cooperation in the management of transboundary stocks will have better outcomes, although there are specific cases where cooperation might not be the best strategy [@Munro:2002uf].
+Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+
+Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
+Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
+Collaboration can also reduce conflict between nations over shared resources as climate change continues changing the distribution and share proportion of fish stocks among countries.
+Marine species distributions are expected to change up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
+Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
+
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+We found transboundary species regardless of the ecosystem preference, althou pelagic-oceanic species were dominant.
+These species are mostly managed by RFMOs whos effectiveness of has been previously questioned [@CullisSuzuki:2010fi].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
+In the other hand, species with narrower ranges (e.g.
+reef-associated species) are often managed at the national level due to localized populations [@Payne:2008vm].
 However, the potential boundary-crossing of these species must not be ignored.
@@
 
-## Conclusions
-
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
+<!-- Conclussion -->
 Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated.
@@
 
-## Materials and Methods
+<!-- Key uncertainties -->
+We have identified four key uncertainties in the method that may affect the estimation of transboundary stocks (see Methods).
+Firstly, we define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study.
+Secondly, the predicted species distribution is affected by the uncertainties of the environmental data and models used for such predictions.
+Thus, we used multiple sources to determine species' distribution and followed an agreement method between sources to reduce uncertainty.
+Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+We only used this dataset due to the lack of other comparable bases.
+Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g.
+all datasets agree on presence) and at least 25% of *Area Index* (e.g.
+the species shared distribution was at least 25% in each EEZ).
+These selection presents a relative conservative estimate of the number of transboundary species in the world.
 
-### Databases of species' geographic distribution
+# **Materials and Methods**
+
+## Databases of species' geographic distribution
 
@@
 
-```{r Data_Table, eval = T, echo = F}
+```{r Data_Table, eval = F, echo = F}
 
@@
   rename("Main Method"=Main_Method) %>% 
-  kable("latex", booktabs = T,
-        caption = "Summary of data sources to estimate species' distributions.
+  # kable("latex", booktabs = T,
+  #       caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
 All data is publically available, see references for details.") %>%
-  kable_styling(full_width = F) %>%
-  column_spec(2,width = "8cm") %>% #wraps text in column2
-  column_spec(3,width = "3cm") #%>% #wraps text in column2
-  # write_csv("Table_1.csv")
+  # kable_styling(full_width = F) %>%
+  # column_spec(2,width = "8cm") %>% #wraps text in column2
+  # column_spec(3,width = "3cm") %>% #wraps text in column2
+  write_csv("Table_1.csv")
 
@@
 
-#### *Occurrence data*
+### *Occurrence data*
 
@@
 
-#### *Distribution models*
+### *Distribution models*
 
@@
 
-#### *Catch data*
+### *Catch data*
 
@@
 
-### Determining transboundary species trait
+## Determining transboundary species trait
 
@@
 from 0 to 1) rather than a discrete, yes or no, index.
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
+All code is available at https://github.com/jepa/FishForVisa.
 
-#### Criteria 1; Neighboring EEZs
+### Criteria 1; Neighboring EEZs
 
@@
 
-#### Criteria 2; Data agreement
+### Criteria 2; Data agreement
 
@@
 
-#### Criteria 3; Modeling verification
+### Criteria 3; Modeling verification
 
@@
 
-#### Criteria 4; Spatial distribution
+### Criteria 4; Spatial distribution
 
@@
 This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
-S2).
+S3).
 
-### Fisheries trends
+## Fisheries trends
 
@@
 Finally, we used the catch data to determine the exploitation category of each species within an EEZ.
-Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk].
+
+Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status.
+
 We only assessed species within each EEZ for which at least ten years of data were available between the first and last reported catch and with at least five consecutive years of data.
@@
 Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
-
-### Statistical analysis
-
-All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
-All code is available at https://github.com/jepa/FishForVisa.
 We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
 We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
-In cases where the ANOVA assumptions were not clearly meet we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
 
@@
            Rules) %>% 
-  kable("latex", booktabs = T,
-        caption = "Rules to determine the category of each transboundary species") %>%
-  kable_styling(full_width = F) %>%
-  column_spec(1,width = "3cm") %>% #wraps text in column2
-  column_spec(2,width = "13cm") #%>% #wraps text in column2
-  # write_csv("Table_2.csv")
+  # kable("latex", booktabs = T,
+  #       caption = "Rules to determine the category of each transboundary species") %>%
+  # kable_styling(full_width = F) %>%
+  # column_spec(1,width = "3cm") %>% #wraps text in column2
+  # column_spec(2,width = "13cm") %>% #wraps text in column2
+  write_csv("Table_2.csv")
 
@@
 
-### Key uncertainties
+## Key uncertainties
 <!-- # Related to Criteria 1 (neighbors) -->
@@
 Likewise, the spatial allocation of the catch is subjected to impressions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
-However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and [@Zeller2016] for model details in the spatial allocation of the SAU).
+However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and @Zeller2016 for mode details in the spatial allocation of the SAU).
 <!-- Related to Criteria 4; Spatial distribution -->
@@
 However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig.
-S2).
+S4).
 
-<!-- Commented out for Thesis -->
-<!-- ## Data Availability -->
-<!-- The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-All code is available at https://github.com/jepa/FishForVisa -->
+# **References**
 
-<!-- \clearpage -->
+<div id="refs"></div>
 
-<!-- ## References -->
+\clearpage
 
-<!-- <div id="refs"></div> -->
+# **Acknowledgments**
 
-<!-- \clearpage -->
-
-<!-- ## Acknowledgments -->
-<!-- We thank T.
+We thank T.
 Clark and A.
 Tidd for helpful comments and discussions.
-G.R.
+**Funding**: G.R.
 was supported by the EO Wilson foundation.
@@
 W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
--->
-
-<!-- ## Authors contributions -->
-<!-- J.P.A.
+**Authors contributions**: J.P.A.
 Conceptualization, methodology, formal analysis, writing original draft.
@@
 All authors provided valuable input to the study conceptualization and discussed the results and analysis.
--->
+**Competing interests**: No declared.
+**Data and materials availability**: The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+All code is available at https://github.com/jepa/FishForVisa
 
-<!-- ## Additional Information   -->
-<!-- **Competing interests**: No declared.  -->
+## Data and materials availability
+All data is publicly available online and upon request from the authors.
 
-## Supplements
+## List of Supplementary Materials
+Figures S1-S4
+Tables S1 -S2
+References in main manuscript (1-27)
+
+\clearpage
+
+# **Supplements**
 
@@
 
-![Figure S1.
-Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png)
+![Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)
 
@@
 Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Fig.
-S2).
+S3).
 As expected, using a more relaxed value (e.g.
@@
 The current analysis utilized a 25% *Area Index* threshold (Fig.
-S2 - darker histogram).
+S3 - darker histogram).
 
@@
 
-img <- readPNG(here("./Figures/FigS2.png"))
+img <- readPNG(here("./Figures/S3_Area.png"))
 grid.raster(img)
@@
 
-![Figure S2.
-Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS2.png)
+![Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
 

### 2020-06-09 Scripts/RFMO Analysis.Rmd
Re-organization of files

--- 2019-11-27 RFMO Analysis.Rmd
@@
 if(Sys.info()[7] == "carmelia"){
-  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
+  Data_Path <- paste(here::here(),"/Temporal_Data", sep ="")
 }
@@
 # The path
-path_world <- paste(Data_Path,"Spatial_Data/","RFMO","/SAU_RFMO",sep="")
+path_world <- paste(Data_Path,"/Spatial_Data/","RFMO","/SAU_RFMO",sep="")
 # #The File
@@
   filter(Name == "IPHC") %>% 
-  st_simplify(1)
+  st_simplify(preserveTopology = TRUE, dTolerance = 100)
 
 ggplot(IPHC) +
+  geom_sf() +
+  facet_wrap(~OBJECTID)
+
+head(IPHC)
+
+Test <- RFMOs_sf %>% 
+  group_by(OBJECTID, Name) %>% 
+  st_combine()
+
+ggplot(Test) +
   geom_sf()

### 2020-07-14 Scripts/Manuscript_Draft.Rmd
Reviewer one initial comments addressed

@@
 ^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
-# subtitle: "[DRAFT DO NOT SHARE]"
+subtitle: "CORECTIONS ARE IN BOLD. DO NOT UNBOLD"
 subtitle: "Most neighbor nations share marine exploited species"
@@
   word_document:
-    # reference_docx: ./Manuscript_Instructions/Science_Advances/SA.MS.Template_2018.docx
+    # reference_docx: ./Manuscript_Instructions/science_template.docx
   pdf_document:
@@
 
-<!-- - Journal: *Science Advances* -->
-<!-- - Information to authors (https://advances.sciencemag.org/content/information-authors) -->
-<!-- - Research articles: -->
+<!-- - Journal: *Scientific Reports* -->
+<!-- - Information to authors (https://www.nature.com/srep/author-instructions/submission-guidelines) -->
+<!-- - There are two types of article: -->
 
-<!-- Research articles should present a major advance and can be short or long (maximum 15,000 words) format.
-Submissions must include an abstract (up to 150 words), an introduction, and sections with brief informative subheadings.
-You may include up to six figures and/or tables and about 40 references.
-Supplementary materials should be limited to information that is not essential for the general understanding of the research presented in the main text and can include data sets, figures, tables, videos, or audio files.
-You may include up to a total of ten figures and/or tables (combined) throughout the supplemental text.
+<!-- -- Articles should be no more than 11 typeset pages in length.
+As a guide, the main text (not including Abstract, Methods, References and figure legends) should be no more than 4,500 words.
+The maximum title length is 20 words.
+The Abstract (without heading) - which must be no more than 200 words long and contain no references - should serve both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications..
 -->
 
-<!-- # Reviewers (4): -->
+<!-- # Reviewers (5): -->
 <!-- *Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*   -->
@@
 
-<!-- # **One Sentence Summary** -->
-<!-- *A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations.
-This will appear online adjacent to the title and should not repeat phrases already present there* -->
-
-<!-- Marine species shared by neighboring nations contribute to over 50% of catches and fishing revenue with direct implications for fisheries management. -->
-
-# **Abstract**
+# Abstract
 <!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
@@
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
-This study highlights the large and under-recognized challenge in achieving international fisheries management goals, particularly as species redistribute under climate change.
+Our analysis suggests that fisheries targeting transboundary species appear **more intensilly fished** than those mainly catching non-transboundary species.
+Our study has direct implications **for fisheries management** of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
 
@@
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
+Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
+For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
+we did not include the high seas).
 We rely on multiple data sources including occurrence, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
 
-# Results
+## Results and Discussion
 
-## Catch and revenue contribution of transboundary species
+**We identified 633 transboundary exploited species in the world (67.5% of the species analyzed), more than double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **anual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
+This is equivalent to 78.5% of the global fishing revenue of the same period.
+These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
+**Such differences...**
 
-We identified 633 transboundary exploited species in the world representing 67.5% of the species analyzed (Fig 1.).
-Between 2005 and 2014, national fleets targeting transboundary species within EEZs cached an average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
-This is equivalent to 78.5% of the global fishing revenue of the same period.
 Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
-For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador.
-The contribution of discrete species was 14.8 million tons representing USD 22,167 million in fishing revenue.
+For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador (**spatial treshold < 25%**).
+The **anual average contribution of discrete species between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
 Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary.
-These species represented only 2.8 million tons and 3,691 million USD between 2005 and 2014.
+These species represented only **an anual average of** 2.8 million tons and 3,691 million USD between 2005 and 2014.
+These results underscore the importance of transboundary species at the global level (Fig.
+1).
 
@@
 
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions in terms of revenue (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B).
-China (USD 6,279 million) in E.
-Asia and the USA (USD 9,605 million) contribute 55% and 82% to the total revenues from the E.
-Asia and N.
-America regions, respectively.
-Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean **yearly** revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
+1B).
+China (USD 6,279 million) in **Eastern** Asia and the USA **In Northern America** (USD 9,605 million) contribute 55% and 82% to the total revenues.
+In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
 These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
-Transboundary species also contribute largely to fisheries catch in E.
-Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
 
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig.
+S1).
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
+Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
+Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk].
+Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+Particularly, China the world's top fish producer**,** [@FAO:2018KK] **gets** one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
 Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Fig.
 2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the **highest** revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
 
-```{r Call_Fig2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
 
@@
 
-![Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)
+![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)
 
-## Exploitation category
-
-We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
-2).
-We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
+**We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
+3).
+While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
+Therefore, our intention here is not to infere stock status but to show the catch trend of transboundary species between 2005 and 2010.
+In this manner, fisheries under Category A have increased the catch, Category B have a constant catch rate, and Category C have seen a decrease in catch in same time period (See methods)**  We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
 Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table S2).
 Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
+This result suggests that the management of discrete species could be better off as the variation between Categories A and B is closer (*p* = 0.052) than for transboundary species (*p* = 0.001).
 
@@
 
-img <- readPNG(here("./Figures/Fig3.png"))
+img <- readPNG(here("./Figures/Fig2.png"))
 grid.raster(img)
@@
 
-![Fig.
-3.
+![Figure 3.
 Number of transboundary species by catch category.
@@
 
-## Transboundary species occurs at multiple ecosystem preferences
+Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Munro:2002uf].
+Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf], and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
+<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
+However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
+-->
 
-We categorized species based on their habitat preference and found transboundary species in all cases (Fig 4.).
-However, species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
+Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
+Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
+Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
+
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-3).
+4A).
 
@@
 
-![Fig.
-4.
+![Figure 4.
 Number of EEZs shared by transboundary species.
@@
 Showing only species that share > 20 EEZs.
-B) Catchs of main fishing countries fishing each ecosystem preference's top five species in terms of shared EEZs (shown in bold in A) between 2005 and 2014.](./Figures/Fig4.png)
+B) Total catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on A).
+Note that there could be > 5 species due to similar sharing values.](./Figures/Fig4.png)
 
@@
 Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
-When applying our analysis at the RFMO level (rather than EEZs), we found that 81.8% of the 99 species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
+We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
 5).
+The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
+However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
 
@@
 
-![Number of shared species across RFMOs. Analysis included with 99 species managed by Fourteen RFMOs](./Figures/Fig5.png)
+![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](./Figures/Fig5.png)
 
-# **Discussion**
-
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
-The number of tranbsoundary species identified in this study are more than double the previous estimates [@Teh:2015gd].
-Similarly, the catch and benefit from these species are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
-These results underscore the importance of transboundary species at the global level.
-China, Japan, Peru, Russia and the USA are among the top seven mejor fishing producers of the world [@FAO:2018KK] and were identified as the nations who economically benefit the most from transboundary species.
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
-Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA.
-Finally, when we account for the total area of waters in different EEZs and regions relative to their catches, the importance of transboundary species to Northern European fisheries become apparent.
-
-Many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk].
-Nevertheless, previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, over-exploited or collapsed [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are re-building or under-exploited, category B would be species that are sustainably harvested, and Category C would be species that are over-exploited.
-Our results suggests that the management of discrete species could be better off as the variation between Categories A and B are closer (p = 0.052) than for transboundary species (p = 0.002).
-Such result has direct implications for the management of transboundary species, suggesting an urgent need for strengthened international cooperation in the management of these fisheries.
-Empirical analysis suggests that cooperation in the management of transboundary stocks will have better outcomes, although there are specific cases where cooperation might not be the best strategy [@Munro:2002uf].
-Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
-
-Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
-The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
-Collaboration can also reduce conflict between nations over shared resources as climate change continues changing the distribution and share proportion of fish stocks among countries.
-Marine species distributions are expected to change up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
-Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
-
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-We found transboundary species regardless of the ecosystem preference, althou pelagic-oceanic species were dominant.
-These species are mostly managed by RFMOs whos effectiveness of has been previously questioned [@CullisSuzuki:2010fi].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
-In the other hand, species with narrower ranges (e.g.
-reef-associated species) are often managed at the national level due to localized populations [@Payne:2008vm].
+On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
 However, the potential boundary-crossing of these species must not be ignored.
@@
 For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-3B) are among the highest fish consumption countries [@FAO:2018KK].
+**4B**) are among the highest fish consumption countries [@FAO:2018KK].
 In these countries, both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
@@
 
-<!-- Conclussion -->
-Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated.
+# Conclusions
+
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
+Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated **[@Teh:2015gd]**.
 This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
-Moreover, we show significant differences in the management of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
+Moreover, we show significant differences in **the catch trends** of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
 Previous work has found that collaboration will result in better outcomes for shared marine resources [@Munro:2002uf].
@@
 
-<!-- Key uncertainties -->
-We have identified four key uncertainties in the method that may affect the estimation of transboundary stocks (see Methods).
-Firstly, we define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study.
-Secondly, the predicted species distribution is affected by the uncertainties of the environmental data and models used for such predictions.
-Thus, we used multiple sources to determine species' distribution and followed an agreement method between sources to reduce uncertainty.
-Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
-We only used this dataset due to the lack of other comparable bases.
-Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g.
-all datasets agree on presence) and at least 25% of *Area Index* (e.g.
-the species shared distribution was at least 25% in each EEZ).
-These selection presents a relative conservative estimate of the number of transboundary species in the world.
-
-# **Materials and Methods**
+# Materials and Methods
 
@@
 However, because we carried the analysis at the species level, we did not include such generalized categories in our comparisons.
-Our final sample represents 63.2% of identified species, accounting for 96.52% of the catch identified at the species' level.
+Our final sample **(n = 938)** represents 63.2% of identified species, accounting for 96.52% of the catch identified at the species' level.
 To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
-Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result.
+Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result **than using only one data source**.
 Only commercial fished species with data from all four sources were included in the analysis.
@@
 
-Occurrence data was collected from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+Occurrence data was collected by Reygondeau (2019) from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
@@
 Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
-The ENM-Nereus employed all of the observational data-sources previously mentioned.
 Global environmental conditions were average for the period 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-This threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
+**While a species that has less than the selected treshold is not considered transboundary in this paper**, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
 S3).
@@
 
-We estimated the economic contribution in 2010 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
+We estimated the economic contribution in **2020** [@REV] real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
 The database we draw from includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
@@
 For this study, we did not include catch nor revenue from areas beyond national jurisdiction.
-Finally, we used the catch data to determine the exploitation category of each species within an EEZ.
 
-Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status.
-
+We used the catch data to determine the **catch trend** of each species within an EEZ.
+Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
+temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk].
 We only assessed species within each EEZ for which at least ten years of data were available between the first and last reported catch and with at least five consecutive years of data.
@@
 year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are re-building or under-exploited, Category B would be species that are sustainable harvested, and Category C would be species that are over-exploited.
-Finally, we reported the predominant category over the last ten years of catch data (2005-2014).
+Following this concept, Category A would represent fisheries that are **increasing in catch, Category B would be species that have a constant catch rate, and Category C would be species that have seen a decrease in catch in the last 10 years.
+Finally, we reported the predominant category over the time period considered.**
+
+## Statistical analysis
+
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
+All code is available at https://github.com/jepa/FishForVisa.
 We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
 We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
+In cases where the ANOVA assumptions were not clearly meet we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
 
@@
 Likewise, the spatial allocation of the catch is subjected to impressions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
-However, this discrepancy is mainly applicable to data provided by RFMOs in the high seas, which were not included in this study (see http://www.seaaroundus.org/data/#/spatial-catch and @Zeller2016 for mode details in the spatial allocation of the SAU).
 <!-- Related to Criteria 4; Spatial distribution -->
@@
 
-# **References**
+# Data Availability
+The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+All code is available at https://github.com/jepa/FishForVisa
+
+\clearpage
+
+# References
 
@@
 
-# **Acknowledgments**
-
+# Acknowledgments
 We thank T.
@@
 Tidd for helpful comments and discussions.
-**Funding**: G.R.
+G.R.
 was supported by the EO Wilson foundation.
@@
 W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
-**Authors contributions**: J.P.A.
+
+# Authors contributions
+J.P.A.
 Conceptualization, methodology, formal analysis, writing original draft.
@@
 All authors provided valuable input to the study conceptualization and discussed the results and analysis.
+
+# Additional Information  
 **Competing interests**: No declared.
-**Data and materials availability**: The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-All code is available at https://github.com/jepa/FishForVisa
 
-## Data and materials availability
-All data is publicly available online and upon request from the authors.
-
-## List of Supplementary Materials
-Figures S1-S4
-Tables S1 -S2
-References in main manuscript (1-27)
-
-\clearpage
-
-# **Supplements**
+## Supplements
 
@@
 
-![Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+![Figure S1.
+Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
 The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)

### 2020-07-15 Scripts/Initial_Analysis.Rmd
Changed cath trend categories to increasing constant and decreasing

@@
   summarise(value = length(unique(fishing_entity))) %>% 
-  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
-                             ifelse(status == "Max Exploited","Category B",
-                                    ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Increasing",
+                             ifelse(status == "Max Exploited","Constant",
+                                    ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Decreasing", "No Category")
                              )

### 2020-07-15 Scripts/Manuscript_Draft.Rmd
Addressed easy rev.2

@@
 * **Corresponding author**: j.palacios@oceans.ubc.ca
+
+# Reviewing issues
+
+## Questions for Gabs:
+- Occurence data time frame
+- ESM is 1970 to 2000, is this beacuse of cliamte period? Reference?
+- SAU-SDM is only one file right, there are no historic estimations
 
@@
 However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, established political boundaries across the distribution of many species, creating shared species between nations.
+The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 nautical miles (territorial see) to 200 nautical miles** across the distribution of many species, creating shared species between nations [@UnitedNations:1986tl].
 Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf].
@@
 
-Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@Munro:2002uf]) is still unclear.
-Early data limitations on species' distributions allowed only for an informed guess on the number of transboundary species [@Caddy:1997ue] while a more recent study explored the historical contribution of shared stocks following a literature review [@Teh:2015gd].
-Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
+Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@UnitedNations:1986tl]) is still unclear.
+**Early data limitations on species' distributions allowed only for an informed guess of 500 to 1500 transboundary stocks [@Caddy:1997ue] while a more recent study explored the historical contribution of 347 shared stocks following a literature review [@Teh:2015gd].** Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
 Here, we aimed to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
@@
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 241 EEZs of 198 coastal territories.
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 241 EEZs of 198 coastal territories (**See methods**).
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the species analyzed), more than double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **anual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue.
+**We identified 633 transboundary exploited species in the world (67.5% of the species analyzed), more than double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **anual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue **(Fig.
+1)**.
 This is equivalent to 78.5% of the global fishing revenue of the same period.
@@
 For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador (**spatial treshold < 25%**).
-The **anual average contribution of discrete species between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
-Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary.
+The **anual average contribution of discrete species (in our previous example would be only considering Ecuator's anchoveta catch) between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
+Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
 These species represented only **an anual average of** 2.8 million tons and 3,691 million USD between 2005 and 2014.
-These results underscore the importance of transboundary species at the global level (Fig.
-1).
+These results underscore the importance of transboundary species at the global level.
 
@@
 S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production.
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the **national** transboundary species production.
 Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk].
-Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+**Similarly, Russia, Japan and the USA celebrate a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Berring Sea since 1988 [@NOAA:gX6CtUTk].** Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
 Particularly, China the world's top fish producer**,** [@FAO:2018KK] **gets** one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
@@
 While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Therefore, our intention here is not to infere stock status but to show the catch trend of transboundary species between 2005 and 2010.
-In this manner, fisheries under Category A have increased the catch, Category B have a constant catch rate, and Category C have seen a decrease in catch in same time period (See methods)**  We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
+Therefore, our intention here is not to infere stock status but to show the catch trend of transboundary species between 2005 and 2010.**  We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
 Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table S2).
@@
 For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to catches (8.19% of total) and USD 850.2 million in revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to **total** catches (8.19% of total) and USD 850.2 million in **fishing** revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
 The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
@@
 However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
-
-```{r Call_Fig5, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of shared species by RFMOs. Analysis included with 85 species managed by Fourteen RFMOs"}
-
-img <- readPNG(here("./Figures/Fig5.png"))
-grid.raster(img)
-```
-
-![Figure 5. Number of shared species across RFMOs. Analysis included 99 species managed by Fourteen RFMOs according to Cullis-Suzuk and Pauly, 2010.](./Figures/Fig5.png)
+[@FIX_rev3_186]
 
@@
 
-To determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs we used the reconstructed list of commercial marine fish and invertebrate species from the *Sea Around Us* (SAU) database (http://www.seaaroundus.org) and determined their current distributions based on an average from 1970-2000.
-The total number of species analyzed was 938 representing 54% of the average catch reported by the *Sea Around Us* between 2005 and 2014, including generalized categories such as *Marine fish not identified* or *Mollusca*.
-However, because we carried the analysis at the species level, we did not include such generalized categories in our comparisons.
-Our final sample **(n = 938)** represents 63.2% of identified species, accounting for 96.52% of the catch identified at the species' level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
+**The Sea Aorund Us has reconstructed global fisheries catches from 1950 to 2014 identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
+We used the Sea Aorund Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
+The total number of species analyzed was 938 representing 63.2% of identified species and accounting for 96.52% of the catch identified at the species' level.** To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
 Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result **than using only one data source**.
@@
 While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SPD-SAU undertakes validation by means of other models), we used a fourth data source to corroborate the models’ outputs.
-The Sea Around Us estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
+The *Sea Around Us* estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
 Catches are also spatially allocated [@Zeller2016].
-Thus, we used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last ten years of data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
+**Roughly, first it takes each country's officially reported catch data (e.g.
+National, FAO or RFMO).
+Secondly, it uses literature (e.g.
+peer review, grey literature) to identify missing components (e.g.
+species, gears) and and sources of alternative information for missing components.
+It then derives country estimates for missing data and creates time series interpolation.
+Finally the estimated and official data are aggregated for a total reconstructed catch data.
+(See Zeller et al., 2016 for detailed methods)** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+We selected this time frame to investigate the recent (our time frame includes the **last decade of available data**) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
 
@@
 Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies) affect fishing effort and catch volume [@Pauly:2013gs; @Branch:2008kk].
+temperature, markets, fishing policies, **and fishing effort) affect fishing catch volume **[@Pauly:2013gs; @Branch:2008kk].
 We only assessed species within each EEZ for which at least ten years of data were available between the first and last reported catch and with at least five consecutive years of data.

### 2020-07-15 Scripts/Manuscript_Draft.Rmd
Addressed Rev. 4 easy comments

@@
 - SAU-SDM is only one file right, there are no historic estimations
+
+## Figures
+- Fix figure 3 solomon islands
+
+## Analysis
+- Convert revenue to 2019 real USD
 
@@
 The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 nautical miles (territorial see) to 200 nautical miles** across the distribution of many species, creating shared species between nations [@UnitedNations:1986tl].
-Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf].
+**Shared stocks can be classified in transboundary, that is stocks that cross the EEZs of two or more coastal states; straddling, that cross neighboring EEZs and the high seas; and highly migratory stocks, that cross non-neighboring EEZs and the high seas (mainly tuna) [@Munro:2004th].
+For the purpose of this research we focuse on transboundary stocks, those shared by neighbouring EEZs **Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; **@Englander:2019dq**].
 For instance, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
@@
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 241 EEZs of 198 coastal territories (**See methods**).
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 241 EEZs of 198 coastal **countries (See methods**).
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
@@
 
-Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data is publicly available (see Acknowledgments).
+Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data are publicly available (see Acknowledgments).
 
@@
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data is publically available, see references for details.") %>%
+All data are publically available, see references for details.") %>%
   # kable_styling(full_width = F) %>%
@@
 Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
-While catch data is not exempt of uncertainty, in most cases, the differences between the Sea Around Us and the FAO self-reported data is smaller towards recent years [@Pauly:2019bf].
+While catch data are not exempt of uncertainty, in most cases, the differences between the Sea Around Us and the FAO self-reported data are smaller towards recent years [@Pauly:2019bf].
 Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.

### 2020-07-15 Scripts/Initial_Analysis.Rmd
Fix typo on benthopelagic figure 3

@@
   mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",
-                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bento-pelagic",paste(DemersPelag)
+                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bentho-pelagic",paste(DemersPelag)
                               )

### 2020-07-20 Scripts/Initial_Analysis.Rmd
Change projections of maps and fix solomon sld

@@
 # Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
-if(Sys.info()[7] == "jepa88"){
-  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
-}
-if(Sys.info()[7] == "carmelia"){
-  Data_Path <- paste(here::here(),"/Temporal_Data/",sep = "")
-}
-if(Sys.info()[7] == "hall1000"){
-  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
-}
+# if(Sys.info()[7] == "jepa88"){
+#   Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
+# }
+# if(Sys.info()[7] == "carmelia"){
+#   Data_Path <- paste(here::here(),"/Temporal_Data/",sep = "")
+# }
+# if(Sys.info()[7] == "hall1000"){
+#   Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
+# }
 
@@
                             )
-  )
+  ) %>% 
+  filter(fishing_entity != "Solomon Isl." | sub_region != "Micronesia")
 
@@
 # Load Land shapefile
-path_world_land <- paste(my_path("G"),"Spatial/ne_50m_admin_0_countries/ne_50m_admin_0_countries",sep="")
-
-# The File
-fnam_world_land <- "ne_50m_admin_0_countries.shp"
-
-# Load it!
-World_land_sf <- st_read(dsn = path_world_land,
-                         layer =file_path_sans_ext(fnam_world_land)) %>% 
-  rename(fishing_entity = NAME) %>% 
+World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
+  st_transform(crs = "+proj=eck4") %>%
+  rename(fishing_entity = name) %>% 
   mutate(
@@
                     layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(eez_name = Name)
+  rename(eez_name = Name) %>% 
+  st_transform(crs = "+proj=eck4")
 
@@
 
-# Read Sau Value Data (Thank you Tim!)
-SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep =""))
+# Read Sau Value Data (Thank you Tim!) reconstructede data
+# Gross Domestic Product Implicit Price Deflator according to the US Saint Louis Federal Reserve Bank (average of all 2019 quarters) to transform the original 2010 real USD revenue value to 2019 real USD (https://fred.stlouisfed.org/searchresults?st=GDP+Implicit+price+deflator).*
+
+SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
+  mutate(value = value*1.62)
 
@@
 # Read Results
-Clean_Results_Trans <- GetTransResults(Spp) %>% 
-  CleanResults(.) %>% 
-  clean_names() %>% 
-  rename(eez_name = territory,
-         fishing_entity = ct_fishing_entity,
-         eez_neighbour = neighbour) %>% 
+# Clean_Results_Trans <- GetTransResults(Spp) %>% 
+#   CleanResults(.) %>% 
+#   clean_names() %>% 
+#   rename(eez_name = territory,
+#          fishing_entity = ct_fishing_entity,
+#          eez_neighbour = neighbour) %>% 
+#   mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))
+
+# Read Results For Carmelia
+
+Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
   mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))
-
-# Read Results For Carmelia
-
-Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep =""))
-
-# Vulnerabillity Data from William
-# cc_vul <- fread(paste(Data_Path,"Species_Data/vulspp310817.csv", sep ="")) %>% 
-#   rename(taxon_key = V1,
-#          ccvul = V2)
-
-# fish_vul <- fread(paste(Data_Path,"Species_Data/FishSenIndex.csv", sep ="")) %>% 
-# clean_names()
-
-# ---------------------------- #
-# RFMOs Results ####
-# ---------------------------- #
-
-# List of species
-Spp_rfmo <- list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Results/RFMO/Trans_Results/")
-
-# List of RMOs
-rfmo_list <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/clean_rfmos.csv") %>% 
-  clean_names() %>% 
-  left_join(Exploited_Species) %>% 
-  filter(!rfmo_name %in% c("IPHC","PSC","NASCO")) # remove these
-
-# Load and clean transboundary results
-Results_rfmo <- GetTransResults(Spp_rfmo) %>% 
-  clean_names() %>% 
-  rename(rfmo_name = territory) %>% 
-  # left_join(rfmo_list,
-  #           by =c("rfmo_name","taxon_key"))
-  filter(
-    taxon_key %in% rfmo_list$taxon_key, # just the taxa managed by the rfmos
-    !rfmo_name %in% c("IPHC","PSC","NASCO"), # remove these
-    !neighbour %in% c("IPHC","PSC","NASCO") # remove these
-  )
-
-# The path
-path_world <- paste(Data_Path,"/Spatial_Data/","RFMO","/SAU_RFMO",sep="")
-# #The File
-fnam_world <- "SAU_RFMO_Sept_2015.shx"
-# #Load it!
-# 
-RFMOs_sf <- st_read(dsn = path_world,
-                    layer =file_path_sans_ext(fnam_world)) %>% 
-  dplyr::rename(Name = RFMO_nm_s)
 

### 2020-07-23 Scripts/Initial_Analysis.Rmd
Trying to get the rounded map and included VIcky's data to compare results with Teh and Sumaila

@@
   Figures_Path = paste(Data_Path,"Figures/",sep = "")
+}
+
+ggtheme_map <- function(base_size = 9, Region = "NA") {
+
+  theme(text             = element_text(#family = "Helvetica",
+    color = "gray30", size = base_size),
+    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
+    panel.background = element_blank(),
+    panel.border     = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_line(color = "transparent"),
+    strip.background =element_rect(fill = "transparent"),
+    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
+    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
+    axis.ticks       = element_blank(),
+    axis.text        = element_blank(),
+    axis.title       = element_blank(),
+    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
+    legend.position = "bottom",
+    legend.key.width =unit(5,"line")
+  )
 }
@@
   World_sf_si_land <- World_land_sf %>%
-    st_transform(crs = 4326) %>% # 4326
+    # st_transform(crs = 4326) %>% # 4326
+    st_transform(crs = "+proj=eck4") %>%
     st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
@@
   Grey_land <- World_land_sf %>%  
-    filter(!NAME_EN %in% World_sf_si_land$NAME_EN)
+    filter(!fishing_entity %in% World_sf_si_land$fishing_entity)
 
@@
     annotate("text", 
-             x =(c(-85.5,-30,25,81,136)+5),
-             y = -93.5,
+             # x =(c(-85.5,-30,25,81,136)+5),
+             # y = -93.5,
+             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
+             y = -9350000,
              label = Labels_Trans, 
@@
     annotate("text", 
-             x =(c(-85.5,-31,20,75,131)+5),
-             y = -110,
+             # x =(c(-85.5,-31,20,75,131)+5),
+             # y = -110,
+             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
+             y = -1100000,
              label = Labels, 
@@
     annotate("text", 
-             x =-180,
-             y = -93.5,
+             # x =-180,
+             # y = -93.5,
+             x =-18000000,
+             y = -9350000,
              label = "Transboundary Spp. (n)", 
@@
     annotate("text", 
-             x =-180,
-             y = -110,
+             # x =-180,
+             # y = -110,
+             x =-18000000,
+             y = -1100000,
              label = Map_Label,
@@
     theme(
-      legend.box.margin = margin(t = -54, l = 130),
+      # legend.box.margin = margin(t = -54, l = 130),
       legend.text = element_blank(),
@@
 
+# Conuntry Names relation
+
+# matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>% 
+#   mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))
+
 # Spatial Data needed to remove duplicates
@@
   st_transform(crs = "+proj=eck4") %>%
+  # st_transform(crs = 4326) %>% # 4326
   rename(fishing_entity = name) %>% 
@@
     fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
-    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    fishing_entity = gsub( "United States", "USA",fishing_entity),
     fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
@@
 # Load it!
-World_sf <- st_read(dsn = path_world,
+World_sf <- World_sf st_read(dsn = path_world,
                     layer =file_path_sans_ext(fnam_world)) %>% 
@@
   st_transform(crs = "+proj=eck4")
+  # st_transform(crs = 4326) # 4326
 
@@
             by = "eez_name") %>% 
-  group_by(fishing_entity) %>% 
+  group_by(fishing_entity,OBJECTID) %>% 
   summarise(Size_Entity = sum(Area_km2))
@@
 
-SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
-  mutate(value = value*1.62)
+SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) #%>% 
+  # mutate(value = value*1.62)
+
+# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
+# SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2010_14.csv", sep =""))
+
+SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2005_09.csv", sep =""))
 
@@
          Per_SAU = Total_Trans/Total_Global*100)
+
+### New estimates!!!
+
+# Filter SAU data for only those sampled species
+
+SAU_Sampled_Data <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id,eez_name) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
+  left_join(Exploited_Species) %>% 
+  filter(!is.na(taxon_name)) %>% 
+  clean_names() %>% 
+  group_by(fishing_entity_id,taxon_key) %>% 
+  summarise_at(c("catch","value"),
+               mean,na.rm=T) %>% 
+  gather("Variable","Value",catch:value)
+
+x <- Tresholded_T_Data %>% 
+  select(taxon_key,eez_name) %>% 
+  group_by(taxon_key,eez_name) %>% 
+  summarise(n=n()) %>% 
+  ungroup() %>% 
+  select(-n) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>% 
+  left_join(SAU_Sampled_Data,
+            by = c("taxon_key","fishing_entity_id")) %>% 
+  # filter(eezid != 0) %>%
+  group_by(Variable) %>%
+  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
+  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100)
+
+Summary_Trans <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Sampled_Data) %>% 
+  semi_join(Tresholded_T_Data,
+            by = c("taxon_key","fishing_entity")) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
+  group_by(Variable) %>%
+  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
+  left_join(Total_SAU_Sampled) %>% 
+  left_join(Total_SAU_Global) %>% 
+  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
+         Per_SAU = Total_Trans/Total_Global*100)
+
+```
+
+```{r comparriosn_wtih_teh}
+
+# Average data for the last 10 years
+
+SAU_Global_Vicky <- SAU_Vicky_Data %>% 
+  filter(#eezid != 0,
+         year == 2006) %>%
+  group_by(fishing_entity_id,taxon_key,eezid) %>% 
+  summarise_at(c("sumcatch"),
+               mean,na.rm=T)
+
+## Get the total of global data
+Total_SAU_Vicky <- sum(SAU_Global_Vicky$sumcatch,na.rm = T)
+
+Summary_Trans_vicky <- Tresholded_T_Data %>% 
+  select(taxon_key,eez_name) %>% 
+  group_by(taxon_key,eez_name) %>% 
+  summarise(n=n()) %>% 
+  ungroup() %>% 
+  select(-n) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>% 
+  left_join(SAU_Global_Vicky,
+            by = c("taxon_key","fishing_entity_id")) %>% 
+  # filter(eezid != 0) %>%
+  group_by() %>%
+  summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
+  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100);Summary_Trans_vicky
 
@@
 World_sf_si <- World_sf %>%
-  st_transform(crs = 4326) %>% # 4326
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name")# %>%
+  left_join(Transboundary_Spp, by ="eez_name") %>% 
+  st_transform(crs = "+proj=eck4")
+  # st_transform(crs = 4326)
 

### 2020-07-23 Scripts/Manuscript_Draft.Rmd
Included changes for reviwers

@@
 subtitle: "CORECTIONS ARE IN BOLD. DO NOT UNBOLD"
-subtitle: "Most neighbor nations share marine exploited species"
+# subtitle: "Most neighbor nations share marine exploited species"
 output:
@@
 
+## General comments
+- Not sure I understand/respond properly to Rev 3. Lines 58-59.
+
 ## Questions for Gabs:
@@
 - SAU-SDM is only one file right, there are no historic estimations
+- **Rev 1.** Line 132: Why? These last sentence is hard to understand.
+
+## Questions for William:
+- I want to reference both Ocean Canada papers to address a comment, is it fair to reference them as *in press*?
 
@@
 - Convert revenue to 2019 real USD
+
+## To editor
+- Note that revenue has increased substantially. this is because we converted the 2010 real USD to 2018, as suggested by Rev. #3
+
+## Specific comments
+- **Rev 1.** Line 305 to 320:
 
@@
 However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 nautical miles (territorial see) to 200 nautical miles** across the distribution of many species, creating shared species between nations [@UnitedNations:1986tl].
-**Shared stocks can be classified in transboundary, that is stocks that cross the EEZs of two or more coastal states; straddling, that cross neighboring EEZs and the high seas; and highly migratory stocks, that cross non-neighboring EEZs and the high seas (mainly tuna) [@Munro:2004th].
-For the purpose of this research we focuse on transboundary stocks, those shared by neighbouring EEZs **Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; **@Englander:2019dq**].
+The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 nautical miles (territorial see) to 200 nautical miles** across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
+**Shared stocks can be classified in three non-exclusive categories; transboundary, that is stocks that cross the EEZs of two or more coastal states; straddling, that cross neighboring EEZs and the high seas; and highly migratory stocks, that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
+For the purpose of this research we focus on identifying the transboundary nature of marine fished species, that is, those shared by neighboring EEZs, but noting that in some cases these might also be preset in the high seas (e.g.
+straddling).** Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; **@Englander:2019dq**].
 For instance, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
@@
 
-Forty years after the formal adoption of UNCLOS, accurate estimates of the number of exploited marine species that are shared by neighboring nations (hereafter called transboundary species [@UnitedNations:1986tl]) is still unclear.
-**Early data limitations on species' distributions allowed only for an informed guess of 500 to 1500 transboundary stocks [@Caddy:1997ue] while a more recent study explored the historical contribution of 347 shared stocks following a literature review [@Teh:2015gd].** Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
+Forty years after the formal adoption of UNCLOS **and the consequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species that are shared by neighboring nations is still unclear.
+Early data limitations on species' distributions allowed only for an informed guess of 500 to 1500 transboundary stocks [@Caddy:1997ue] while a more recent study explored the historical contribution of 344 shared taxa following a literature review [@Teh:2015gd].** Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
 Here, we aimed to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
@@
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level **(or even as a group of species) like the case of shrimps (e.g.
+Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt], hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf].** Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis **while still making it relevant from a management perspective**.
 For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the species analyzed), more than double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **anual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating USD 65,483 million in fishing revenue **(Fig.
+**We identified 633 transboundary exploited species in the world (67.5% of the species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **annual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating **a yearly average of USD 65,483 million in fishing revenue during the same time period (Fig.
 1)**.
@@
 These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
-**Such differences...**
+**This result suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated.
+However, it is important to mention that the referenced article reports yearly FAO reported catch data for both EEZs and the high seas up to 2006.
+Thus, the divergence between studies can be influenced by the data source and time period in addition to the higher amount of transboundary species identified in the present study.
+However, using the FAO reported data for 2006, the average participation of the identified transboundary species was 61%, still higher than that reported by Teh and Sumaila (2015).**
 
 Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
-For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile, and thus discrete for Ecuador (**spatial treshold < 25%**).
-The **anual average contribution of discrete species (in our previous example would be only considering Ecuator's anchoveta catch) between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
+For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile [@Cashion:2018cg], and thus discrete for Ecuador (**spatial threshold < 10%**).
+The **annual average contribution of discrete species (in our previous example would be only considering Equator's anchoveta catch) between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
 Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
-These species represented only **an anual average of** 2.8 million tons and 3,691 million USD between 2005 and 2014.
+These species represented only **an annual average of** 2.8 million tons and 3,691 million USD between 2005 and 2014.
 These results underscore the importance of transboundary species at the global level.
+
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean **yearly** revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
+1B).
+China (USD 6,279 million) in **Eastern** Asia and the USA **In Northern America** (USD 9,605 million) contribute 55% and 82% to the **annual average** revenues.
+In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211 **million**) and Japan (USD 3,368 **million**) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
 
@@
 Points = mean +- sd.
-Revenue in 2010 real USD.](./Figures/Fig1.png)
-
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean **yearly** revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
-1B).
-China (USD 6,279 million) in **Eastern** Asia and the USA **In Northern America** (USD 9,605 million) contribute 55% and 82% to the total revenues.
-In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,368) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
-These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
+Revenue in 2010 real USD.](../Figures/Fig1.png)
 
@@
 Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-**Similarly, Russia, Japan and the USA celebrate a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Berring Sea since 1988 [@NOAA:gX6CtUTk].** Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+**Similarly, Russia, Japan and the USA celebrate a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea since 1988 [@NOAA:gX6CtUTk].** Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
 Particularly, China the world's top fish producer**,** [@FAO:2018KK] **gets** one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
@@
 2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the **highest** revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the **highest average** revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area between 2005 and 2014, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
 
@@
 
-![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](./Figures/Fig2.png)
+![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](../Figures/Fig2.png)
 
@@
 While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Therefore, our intention here is not to infere stock status but to show the catch trend of transboundary species between 2005 and 2010.**  We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
+Therefore, our intention here is not to infer stock status but to show the catch trend of transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
 Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table S2).
@@
 ```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch"}
+Category A, increasing catch; Category B, stable catch; Category C, decreasing catch"}
 
@@
 
-![Figure 3.
-Number of transboundary species by catch category.
-Category A, fishing between 10%-50% of maximum catch level after a drop larger than 10% of the recorded maximum catch; Category B, fishing over 50% of maximum catch level; Category C, fishing less than 50% of maximum catch](./Figures/Fig3.png)
+![Figure 3. Number of transboundary species by catch category. Actegory A, Increasing catch; Category B, stable catch; Category C, decreasing catch](../Figures/Fig3.png)
 
@@
 Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
-Exploring the detailed impacts of climate change in share species is key to develop local adaptation methods to minimize the effect of such distributional change on the conservation of species as well as the economy and food security of coastal nations.
+Exploring the detailed effects of climate change in the distribution of share species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
+**For example, understanding how climate change will modify the proportion that each neighboring EEZ has over a sharing species [@Palacios-Abrantes_OC], when this change is going to happen, and the economic consequence of such effects can make international treaties more resilient to climate change [@Sumaila_oc].**
 
@@
 4A).
+**This result is not surprising as many of the species with preference for pelagic-oceanic ecosystems categorized as transboundary are actually highly migratory straddling species (species that go from one EEZ to another while crossing the high seas).
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, like the case of Bigeye tuna (Thunnus obesus) (Fig.
+4A)**
 
@@
 B) Total catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on A).
-Note that there could be > 5 species due to similar sharing values.](./Figures/Fig4.png)
+Note that there could be > 5 species due to similar sharing values.
+**Other consist in species that have no classification according to FishBase.**](../Figures/Fig4.png)
 
-Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
-Fifteen major RFMOs in the world oversee the management of 99 species [@CullisSuzuki:2010fi].
-We estimated that 81.8% of these species are shared across neighboring RFMOs, with the International Commission for the Conservation of Atlantic Tunas (ICCAT) sharing over 40 species with neighboring RFMOs (Fig.
-5).
-The effectiveness of RFMOs has been previously questioned [@CullisSuzuki:2010fi].
-However, despite a global expansion of the industrial fleet in the last decade [@Coulter:2020gr], a recent analysis of 40 tuna and billfish stocks suggests that most stocks are sustainable harvested with only three currently considered as overfished [@Pons:2016ep].
-[@FIX_rev3_186]
-
-On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm].
-However, the potential boundary-crossing of these species must not be ignored.
-The world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+**Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
+On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm] and the potential boundary-crossing of these species must not be ignored.** The world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
 In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Payne:2008vm].
@@
 In these countries, both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
-In the case of Kiribati, the Solomon Islands and Papua New Guinea, they are parties to the Pacific Nauru Agreement that sustainable manage 30% of global skipjack tuna [@Aqorau:2018bh], estimated to produce $2 billion worth of fish every year, representing a role model for transboundary fisheries management [@Hanich:2010ht].
 
@@
 Catches are also spatially allocated [@Zeller2016].
-**Roughly, first it takes each country's officially reported catch data (e.g.
+**Roughly, the Sea Around Us method takes each country's officially reported catch data (e.g.
 National, FAO or RFMO).
@@
 It then derives country estimates for missing data and creates time series interpolation.
-Finally the estimated and official data are aggregated for a total reconstructed catch data.
-(See Zeller et al., 2016 for detailed methods)** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+Finally the estimated and official data are aggregated for a total reconstructed catch data See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 We selected this time frame to investigate the recent (our time frame includes the **last decade of available data**) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
@@
 
-We developed a four-criteria methodology to determine whether or not a species can be considered transboundary.
+We developed a **three**-criteria methodology to determine whether or not a species can be considered transboundary.
 Only species that meet all criteria were considered as transboundary and the analysis was undertaken only within the EEZs of coastal states.
@@
 
-We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells.
-We computed a *Species Index* by dividing the number of datasets that confirmed the presence of a species in a grid cell over the total number of datasets (n = 3).
-The index is unit-less and represents a scale from 0.3 to 1, with 0.3 indicating that only one dataset reported the presence of the species in a grid cell, 0.6 two out of three sources, and 1 pointing to agreement across all 3 datasets.
-All analyses only considered cases where *Species Index* = 1 to obtain a more conservative estimate of transboundary species.
+**We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells.
+All analyses only considered cases where all databases matched to obtain a more conservative estimate of transboundary species.
+Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the Sea *Around Us catch* database.
+Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
+This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decadde of data (2005 - 2014), thus validating the models and only selected "current" shared speceies.**
 
-### Criteria 3; Modeling verification
-
-We assumed that a species was only present in a given grid-cell if it was reported in the Sea Around Us catch database.
-Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped, regardless of the *Species Index*.
-This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over a period of time (here 2005 - 2014), thus validating the models.
-See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.
-
-### Criteria 4; Spatial distribution
+### Criteria 3; Spatial distribution
 
@@
 
-We estimated the economic contribution in **2020** [@REV] real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
-The database we draw from includes ex-vessel price from multiple sources and a structured interpolation method (e.g.
+We estimated the economic contribution in **2019** real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
+The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g.
 similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-The contribution of transboundary species was derived by aggregating the catch of species occurring within the EEZs of countries sharing that species.
-For this study, we did not include catch nor revenue from areas beyond national jurisdiction.
+**The dataset is harmonized with the SAU catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs of this study (http://www.seaaroundus.org/data/#/feru).
+We report the average fishing revenue of 2005 to 2014 derivede from the fishing activity within the global EEZs.
+Alike the catch data, for this study we did not include revenue from areas beyond national jurisdiction.
+We used the US Gross Domestic Product Implicit Price Deflator (average of all 2019 quarters) according to the US Saint Louis Federal Reserve Bank (https://fred.stlouisfed.org/searchresults?st=GDP+Implicit+price+deflator) to transform the original 2010 real USD value to 2019 real USD.**
 

### 2020-07-29 Scripts/Manuscript_Draft.Rmd
All comments addressed

@@
 ## Questions for Gabs:
-- Occurence data time frame
-- ESM is 1970 to 2000, is this beacuse of cliamte period? Reference?
-- SAU-SDM is only one file right, there are no historic estimations
+- Teh et al comment. Do we include another data or just the explanation is fine?
 - **Rev 1.** Line 132: Why? These last sentence is hard to understand.
-
-## Questions for William:
-- I want to reference both Ocean Canada papers to address a comment, is it fair to reference them as *in press*?
 
@@
 
-<!-- # Reviewers (5): -->
-<!-- *Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*   -->
-
-<!-- **Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions) -->
-
-<!-- - **Potential Reviewers (J)**   -->
-<!--  -- Claire Armstrong, The Norwegian College of Fishery Science, Tromso, Norway claire.armstrong@uit.no -->
-<!--  -- Gakushi Ishimura, Faculty of Agriculture Department of Food Production and Environmental Management, Iwate University, Morioka, Japan; gakugaku@iwate-u.ac.jp -->
-<!--  -- Rebecca Selden, Wellesley College, Wellesley, MA, USA; bselden@wellesley.edu -->
-<!--  -- Julia Xue, Shanghai Jiao Tong University; juliaxue@ouc.edu.cn -->
-
-<!-- - **Excluded Reviewers (J)**   -->
-
 # Abstract
-<!-- *An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence.
-It should be a single paragraph.* -->
 
@@
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
-Our analysis suggests that fisheries targeting transboundary species appear **more intensilly fished** than those mainly catching non-transboundary species.
+Our analysis suggests that fisheries targeting transboundary species appear **more intensively fished** than those mainly catching non-transboundary species.
 Our study has direct implications **for fisheries management** of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
@@
 **Shared stocks can be classified in three non-exclusive categories; transboundary, that is stocks that cross the EEZs of two or more coastal states; straddling, that cross neighboring EEZs and the high seas; and highly migratory stocks, that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
-For the purpose of this research we focus on identifying the transboundary nature of marine fished species, that is, those shared by neighboring EEZs, but noting that in some cases these might also be preset in the high seas (e.g.
+For the purpose of this research we focus on identifying the transboundary nature of marine fished species, that is, those shared by neighboring EEZs, noting that in some cases these might also be present in the high seas (e.g.
 straddling).** Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; **@Englander:2019dq**].
@@
 Thus, the divergence between studies can be influenced by the data source and time period in addition to the higher amount of transboundary species identified in the present study.
-However, using the FAO reported data for 2006, the average participation of the identified transboundary species was 61%, still higher than that reported by Teh and Sumaila (2015).**
+...
+Using the FAO reported data for 2006, the average participation of the identified transboundary species was 61%, still higher than that reported by Teh and Sumaila (2015).**
 
 Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
-For example, Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile [@Cashion:2018cg], and thus discrete for Ecuador (**spatial threshold < 10%**).
-The **annual average contribution of discrete species (in our previous example would be only considering Equator's anchoveta catch) between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
+For example, we found that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile [@Cashion:2018cg], and thus discrete for Ecuador (**spatial threshold < 10%**).
+The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
 Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
@@
 
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (mean **yearly** revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average yearly** revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
 The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
 1B).
-China (USD 6,279 million) in **Eastern** Asia and the USA **In Northern America** (USD 9,605 million) contribute 55% and 82% to the **annual average** revenues.
-In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211 **million**) and Japan (USD 3,368 **million**) are amongst the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+China (USD 6,279 million) in **Eastern** Asia and the USA **in Northern America** (USD 9,605 million) contribute 55% and 82% to the **annual average** revenues.
+In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211 **million**) and Japan (USD 3,368 **million**) are among the top five countries with the most fishing revenue generated from transboundary species in the last decade.
 These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
@@
 
-![Figure 3. Number of transboundary species by catch category. Actegory A, Increasing catch; Category B, stable catch; Category C, decreasing catch](../Figures/Fig3.png)
+![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Growing trend; Category B, Stable trend; Category C, Shrinking trend](../Figures/Fig3.png)
 
@@
 4A).
-**This result is not surprising as many of the species with preference for pelagic-oceanic ecosystems categorized as transboundary are actually highly migratory straddling species (species that go from one EEZ to another while crossing the high seas).
+**[Colette] This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
+Many of these species are actually highly migratory straddling species (species that go from one EEZ to another while crossing the high seas).
 Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, like the case of Bigeye tuna (Thunnus obesus) (Fig.
-4A)**
+4A).
+Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).**
+
+CW. because they are migratory they fall under the management of RFMOs...
 
@@
 
-**Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
-On the other hand, species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm] and the potential boundary-crossing of these species must not be ignored.** The world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-In addition, coral regions often share multiple species, making coordination among countries key to achieve fisheries and conservation goals [@Payne:2008vm].
-Many coastal communities, particularly in developing regions, are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
+**However, this category also includes species that are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
+Belone belone).
+Species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm] but the potential boundary-crossing of these species must not be ignored.
+In addition, the world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
+Despite coral reef-related species being among the less shared neighboring EEZs identified in this study (Fig.
+4), coral regions, often share multiple species through larvae connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+In some areas like the Caribbean and the Western Indian Ocean, transboundary marine protected areas have been identified as potential tools for achieving fisheries and conservation goals [@Levin:2018in; Perez:2019dm].** The proper management of coral reef species is very important for many coastal communities, particularly in developing regions, that are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
 For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
@@
 
-**The Sea Aorund Us has reconstructed global fisheries catches from 1950 to 2014 identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
-We used the Sea Aorund Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
+**The Sea Around Us has reconstructed global fisheries catches from 1950 to 2014 identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
+We used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
 The total number of species analyzed was 938 representing 63.2% of identified species and accounting for 96.52% of the catch identified at the species' level.** To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
@@
 Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
-Global environmental conditions were average for the period 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+Global environmental conditions were average for the **30-year climate normal period of 1970-2000** and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
 See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
@@
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
-This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decadde of data (2005 - 2014), thus validating the models and only selected "current" shared speceies.**
+This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decade of data (2005 - 2014), thus validating the models and only selected "current" shared species.**
 
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-**While a species that has less than the selected treshold is not considered transboundary in this paper**, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
+**While a species that has less than the selected threshold is not considered transboundary in this paper**, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
 S3).
@@
 **The dataset is harmonized with the SAU catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs of this study (http://www.seaaroundus.org/data/#/feru).
-We report the average fishing revenue of 2005 to 2014 derivede from the fishing activity within the global EEZs.
+We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.
 Alike the catch data, for this study we did not include revenue from areas beyond national jurisdiction.
@@
 temperature, markets, fishing policies, **and fishing effort) affect fishing catch volume **[@Pauly:2013gs; @Branch:2008kk].
-We only assessed species within each EEZ for which at least ten years of data were available between the first and last reported catch and with at least five consecutive years of data.
+We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
 Three final categories were drawn for each species depending on the catch volume within each EEZ (e.g.
@@
 Finally, we reported the predominant category over the time period considered.**
-
-## Statistical analysis
-
-All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
-All code is available at https://github.com/jepa/FishForVisa.
-We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
-We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
-In cases where the ANOVA assumptions were not clearly meet we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
 
@@
                   "B - Stable Fishery",
-                  "C - Fishery under 10% of Peak",
+                  "C - Shrinking Fishery",
                   "No Status")
@@
 ```
+
+## Statistical analysis
+
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
+All code is available at https://github.com/jepa/FishForVisa.
+We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
+We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
+In cases where the ANOVA assumptions were not clearly meet we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
 
@@
 Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](./Figures/FigS1.png)
+The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](../Figures/FigS1.png)
 
-The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
+The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
 Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Fig.
@@
 Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](./Figures/FigS4.png)
+The darker histogram represents the threshold (25%) used in the present analysis](../Figures/FigS2.png)
 

### 2020-07-29 Scripts/Initial_Analysis.Rmd
re-located RFMO analysis

@@
 # 7831.10 1327.27 9261.48
-
-```
-
-# RFMO Analysis
-
-```{r RFMO_Data, eval = F}
-
-RFMO_Data <- read.delim("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/RFMO_procedure_outcome.csv")
-
-x <- RFMO_Data %>% 
-  mutate(
-    x = gsub("<.*?>", "", RFMO_Data$primary_species),
-    y = gsub("[\\(\\)]", "", regmatches(x, gregexpr("\\(.*?\\)", x)))
-  )
-
-# Save to remove "" and pass to colomuns in excell
-# write.csv(x,
-#           "rfmos.csv")
-
-rfmos <- read.csv("~/Github/FishForVisa/rfmos.csv")
-View(rfmos)
-
-list <- rfmos$Taxa
-
-clean_rfmos <- rfmos %>% 
-  gather("taxa","taxon_name",y:X.21) %>% 
-  filter(taxon_name != "") %>% 
-  select(RFMO_name = name,
-         contracting_parties,
-         area,
-         taxon_name)
-
-# write_csv(clean_rfmos,
-#           "clean_rfmos.csv")
-
-### Join with exploited species
-
-clean_rfmos <- clean_rfmos %>% 
-  left_join(Exploited_Species)
 
@@
 # Load it!
-World_sf <- World_sf st_read(dsn = path_world,
+World_sf <- st_read(dsn = path_world,
                     layer =file_path_sans_ext(fnam_world)) %>% 
@@
   mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))
+
+# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
+Entity_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_Results_Trans,
+            by = "eez_name") %>% 
+  group_by(fishing_entity,OBJECTID) %>% 
+  summarise(Size_Entity = sum(Area_km2))
+
+### Tnas and billfish according to Pons 2016
+
+tunas <- c("Katsuwonus pelamis",
+"Thunnus alalunga",
+"Thunnus albacares",
+"Thunnus maccoyii",
+"Thunnus obesus",
+"Thunnus orientalis", 
+"Thunnus thynnus",
+"Xiphias gladius",
+"Istiophorus albicans",
+"Istiophorus platypterus", 
+"Istiompax indica",
+"Makaira nigricans",
+"Kajikia albidus",
+"Kajikia audax",
+"Tetrapturus angustirostris",
+"Tetrapturus belone",
+"Tetrapturus georgii",
+"Tetrapturus pfluegeri")
 
@@
   summarise(
-    Bins = cut(Value,breaks = Map_Breaks, dig.lab = 5 ),
-    Bins_Plot = cut(Value,breaks = Map_Breaks,
+    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
+    Bins_Plot = cut(Value, breaks = Map_Breaks,
                     labels = c('super low', 'low','median','high','super high'),
@@
   filter(adj.p.value < 0.05) # Northern Europe
-```
-
-### RFMO Map of Transboundary Species
-
-```{r RFMO_Map, eval =F, echo =F}
-
-Tresholded_rfmo_Data <- Results_rfmo %>% 
-  filter(
-    area_index >= Min_AI,
-    area_index <= Max_AI,
-    model_index >= MI
-  ) %>% 
-  group_by(rfmo_name) %>% 
-  summarise(
-    n_trans_spp = length(unique(taxon_key)),
-    n_neighbours = length(unique(neighbour)),
-    trans_Rrate = n_trans_spp/n_neighbours
-  )
-
-# Number of RFMOs
-rfmo_list %>% 
-  pull(rfmo_name) %>% 
-  unique() %>% 
-  length() # 15
-
-# Number of total taxa
-rfmo_list %>% 
-  pull(taxon_key) %>% 
-  unique() %>% 
-  length() # 99
-
-# Number of taxa per RFMO
-rfmo_list %>% 
-  group_by(rfmo_name) %>% 
-  summarise(in_trans_spp = length(unique(taxon_key)))
-
-# Number of shared taxa
-Results_rfmo %>% 
-  pull(taxon_key) %>% 
-  unique() %>% 
-  length() # 81
-
-### Bar plot
-
-Tresholded_rfmo_Data %>% 
-  ggplot() +
-  geom_bar(
-    aes(
-      x = reorder(rfmo_name,-n_trans_spp),
-      y = n_trans_spp
-    ),
-    stat = "identity"
-  ) +
-  coord_flip()
-
-head(RFMOs_sf)
-
-# Transboundary Species shapefile
-World_sf_si <- RFMOs_sf %>%
-  filter(!Name %in% c("IPHC","PSC","NASCO")) %>% 
-  rename(rfmo_name = Name) %>% 
-  st_transform(crs = 4326) %>% # 4326
-  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Tresholded_rfmo_Data, by ="rfmo_name")
-
-# Total catch/Revenue shapefile
-World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) #%>% # 4326
-# st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
-
-# Get the NA's to be grey
-# Grey_land <- World_sf_si_land %>% 
-#   filter(is.na(Bins))
-
-# Make map
-Plot <- ggplot() +
-  geom_sf(data = World_sf_si,
-          aes(
-            fill =  n_trans_spp,
-            colour = n_trans_spp
-          ), 
-          size = 0.1
-  ) + # n_trans_spp or Bins
-  geom_sf(data = World_sf_si_land) +
-  # geom_sf_label(data = World_sf_si,
-  #               aes(label = eez_name)
-  #               ) +
-  scale_fill_gradientn("Number of Shared Species",
-                       colours = wes_palette("Zissou1", 100, type = "continuous"),
-                       limits = c(0,45),
-                       breaks = seq(0,45,5)
-  ) +
-  scale_colour_gradientn("Number of Shared Species",
-                         colours = wes_palette("Zissou1", 100, type = "continuous"),
-                         limits = c(0,45),
-                         breaks = seq(0,45,5)
-  ) +
-  ggtheme_map()
-
-Plot_Name <- paste("S2_RFMO.png", sep = "")
-
-ggsave(Plot_Name,
-       plot = Plot,
-       width = 16,
-       height = 8,
-       units = "in",
-       path = Figures_Path
-)
 ```
@@
   filter(adj.p.value < 0.05) # Pelagic-Oceanic
-
-```
-
-## RFMO specifics
-
-```{r RFMOs, eval = T, echo = F}
-
-### Results exploration
-
-ICCAT_List <- rfmo_list %>% 
-  filter(rfmo_name == "ICCAT") %>% 
-  pull(taxon_key) %>% 
-  unique()
-
-Tresholded_T_Data %>% 
-  filter(taxon_key %in% ICCAT_List) %>% 
-  group_by(taxon_key) %>% 
-  summarise(
-    n_countries = length(unique(fishing_entity))
-  )
-
-ICCAT_Trans <- Species_Data %>% 
-  rename(taxon_name = individual) %>% 
-  left_join(Exploited_Species) %>% 
-  filter(taxon_key %in% ICCAT_List)
 
@@
 ```
+
+# RFMO Analysis
+
+```{r RFMO_Data, eval = F}
+
+RFMO_Data <- read.delim("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/RFMO_procedure_outcome.csv")
+
+x <- RFMO_Data %>% 
+  mutate(
+    x = gsub("<.*?>", "", RFMO_Data$primary_species),
+    y = gsub("[\\(\\)]", "", regmatches(x, gregexpr("\\(.*?\\)", x)))
+  )
+
+# Save to remove "" and pass to colomuns in excell
+# write.csv(x,
+#           "rfmos.csv")
+
+rfmos <- read.csv("~/Github/FishForVisa/rfmos.csv")
+View(rfmos)
+
+list <- rfmos$Taxa
+
+clean_rfmos <- rfmos %>% 
+  gather("taxa","taxon_name",y:X.21) %>% 
+  filter(taxon_name != "") %>% 
+  select(RFMO_name = name,
+         contracting_parties,
+         area,
+         taxon_name)
+
+# write_csv(clean_rfmos,
+#           "clean_rfmos.csv")
+
+### Join with exploited species
+
+clean_rfmos <- clean_rfmos %>% 
+  left_join(Exploited_Species)
+
+```
+
+## RFMO specifics
+
+```{r RFMOs, eval = T, echo = F}
+
+### Results exploration
+
+ICCAT_List <- rfmo_list %>% 
+  filter(rfmo_name == "ICCAT") %>% 
+  pull(taxon_key) %>% 
+  unique()
+
+Tresholded_T_Data %>% 
+  filter(taxon_key %in% ICCAT_List) %>% 
+  group_by(taxon_key) %>% 
+  summarise(
+    n_countries = length(unique(fishing_entity))
+  )
+
+ICCAT_Trans <- Species_Data %>% 
+  rename(taxon_name = individual) %>% 
+  left_join(Exploited_Species) %>% 
+  filter(taxon_key %in% ICCAT_List)
+
+```
+
+## RFMO Map of Transboundary Species
+
+```{r RFMO_Map, eval =F, echo =F}
+
+Tresholded_rfmo_Data <- Results_rfmo %>% 
+  filter(
+    area_index >= Min_AI,
+    area_index <= Max_AI,
+    model_index >= MI
+  ) %>% 
+  group_by(rfmo_name) %>% 
+  summarise(
+    n_trans_spp = length(unique(taxon_key)),
+    n_neighbours = length(unique(neighbour)),
+    trans_Rrate = n_trans_spp/n_neighbours
+  )
+
+# Number of RFMOs
+rfmo_list %>% 
+  pull(rfmo_name) %>% 
+  unique() %>% 
+  length() # 15
+
+# Number of total taxa
+rfmo_list %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length() # 99
+
+# Number of taxa per RFMO
+rfmo_list %>% 
+  group_by(rfmo_name) %>% 
+  summarise(in_trans_spp = length(unique(taxon_key)))
+
+# Number of shared taxa
+Results_rfmo %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length() # 81
+
+### Bar plot
+
+Tresholded_rfmo_Data %>% 
+  ggplot() +
+  geom_bar(
+    aes(
+      x = reorder(rfmo_name,-n_trans_spp),
+      y = n_trans_spp
+    ),
+    stat = "identity"
+  ) +
+  coord_flip()
+
+head(RFMOs_sf)
+
+# Transboundary Species shapefile
+World_sf_si <- RFMOs_sf %>%
+  filter(!Name %in% c("IPHC","PSC","NASCO")) %>% 
+  rename(rfmo_name = Name) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Tresholded_rfmo_Data, by ="rfmo_name")
+
+# Total catch/Revenue shapefile
+World_sf_si_land <- World_land_sf %>%
+  st_transform(crs = 4326) #%>% # 4326
+# st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
+
+# Get the NA's to be grey
+# Grey_land <- World_sf_si_land %>% 
+#   filter(is.na(Bins))
+
+# Make map
+Plot <- ggplot() +
+  geom_sf(data = World_sf_si,
+          aes(
+            fill =  n_trans_spp,
+            colour = n_trans_spp
+          ), 
+          size = 0.1
+  ) + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land) +
+  # geom_sf_label(data = World_sf_si,
+  #               aes(label = eez_name)
+  #               ) +
+  scale_fill_gradientn("Number of Shared Species",
+                       colours = wes_palette("Zissou1", 100, type = "continuous"),
+                       limits = c(0,45),
+                       breaks = seq(0,45,5)
+  ) +
+  scale_colour_gradientn("Number of Shared Species",
+                         colours = wes_palette("Zissou1", 100, type = "continuous"),
+                         limits = c(0,45),
+                         breaks = seq(0,45,5)
+  ) +
+  ggtheme_map()
+
+Plot_Name <- paste("S2_RFMO.png", sep = "")
+
+ggsave(Plot_Name,
+       plot = Plot,
+       width = 16,
+       height = 8,
+       units = "in",
+       path = Figures_Path
+)
+```

### 2020-07-29 Scripts/Initial_Analysis.Rmd
Fixed map labels for tubed map

@@
 
+  ####### For testing ###
+
+  gc()
+
+  plot_all <- ggdraw() +
+  # map
+  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
+  draw_plot_label(label = c("A", "B"), 
+                  size = 20,
+                  x = c(0, 0), 
+                  y = c(1, 0.45)
+  )
+
+  save_plot(
+    "Map.png",
+    plot_all,
+    base_height = 8,
+    base_width = 8
+  )
+
+  #######
+
   Map <- ggplot() +
@@
              # y = -93.5,
-             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
-             y = -9350000,
+             x =(c(-8500000,-3000000,2500000,7500000,12800000)),
+             y = -9050000,
              label = Labels_Trans, 
@@
              # y = -110,
-             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
-             y = -1100000,
+             x =(c(-8500000,-3200000,2000000,7000000,12500000)),
+             y = -11000000,
              label = Labels,
@@
              # y = -93.5,
-             x =-18000000,
-             y = -9350000,
+             x =-17000000,
+             y = -9050000,
              label = "Transboundary Spp. (n)", 
@@
              # y = -110,
-             x =-18000000,
-             y = -1100000,
+             x =-17000000,
+             y = -11000000,
              label = Map_Label,
@@
     theme(
-      # legend.box.margin = margin(t = -54, l = 130),
+      legend.box.margin = margin(t = -55, l = 120),
       legend.text = element_blank(),
@@
   group_by(fishing_entity,Variable,Value) %>% 
-  summarise(
+  mutate(
     Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
@@
   # Convert catch to million tonnes
+  ungroup() %>% 
   mutate(

### 2020-07-30 Scripts/Initial_Analysis.Rmd
New Fig1!

@@
   Labels <- c("(1-10]",paste(Bins[2:5]))
-
-  ####### For testing ###
-
-  gc()
-
-  plot_all <- ggdraw() +
-  # map
-  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
-  draw_plot_label(label = c("A", "B"), 
-                  size = 20,
-                  x = c(0, 0), 
-                  y = c(1, 0.45)
-  )
-
-  save_plot(
-    "Map.png",
-    plot_all,
-    base_height = 8,
-    base_width = 8
-  )
-
-  #######
 
@@
     theme(
-      legend.box.margin = margin(t = -55, l = 120),
+      legend.box.margin = margin(t = -58, l = 120),
       legend.text = element_blank(),
@@
                          colours = pal,
-                         limits = c(0,12000),
-                         breaks = seq(0,12000,3000)) +
+                         limits = c(0,14000),
+                         breaks = seq(0,14000,3500)
+                         ) +
     guides(fill = guide_colorbar(label.position = "left")
-    )
+    );Rev_Plot
 
@@
                        colours = pal
-  )
+  );Catch_Plot
 
@@
 
+  gc()
   save_plot(
@@
 
+# World_sf %>% filter(str_detect(eez_name, "Cu"))
+
 #### Determine polygon areas
@@
 
-SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) #%>% 
-  # mutate(value = value*1.62)
+SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
+  mutate(value = 1.16 * value)
 
@@
   clean_names() %>% 
-  rename(sf_eez_name=territory)
+  rename(eez_name=territory) %>% 
+  mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
+         )
 
@@
 Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
-  mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))
+  mutate(eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
+                           ifelse(eez_name == "Curacao (Netherlands)","Curaçao (Netherlands)",eez_name)
+                           ),
+         fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
+                                 ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",fishing_entity))
+         )
 
@@
 # Set manual breaks for bins
-Map_Breaks <- c(-1,10,100,1000,5000,10000)
+Map_Breaks <- c(-1,10,100,1000,2000,12000) 
+# Map_Breaks <- c(-1,20,200,2000,1000,20000)
 
@@
   spread(Variable,Trans_Total) %>% 
-  left_join(Entity_Area, 
-            by = "fishing_entity") %>% 
-  # Include the weighted method for supplementals
-  mutate_at(
-    vars(catch,value),
-    funs(weight= ./(Size_Entity/1000000))
-  ) %>% 
-  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
+  # left_join(Entity_Area,
+  #           by = "fishing_entity") %>%
+  # # Include the weighted method for supplementals
+  # mutate_at(
+  #   vars(catch,value),
+  #   funs(weight= ./(Size_Entity/1000000))
+  # ) %>%
+  # gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
+  gather("Variable","Value",catch:value) %>%
   group_by(fishing_entity,Variable,Value) %>% 
@@
   ungroup() %>% 
-  mutate(id = rep(seq(1,17),4)) %>% 
+  mutate(id = rep(seq(1,17),2)) %>% 
   mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))
@@
   ) %>% 
-  mutate(value = ifelse(is.na(value),0,value)#,
+  mutate(value = ifelse(is.na(value),0,
+                        ifelse(value < -100,-100, # if less than 100, 100
+                               ifelse(value > 100,100, # if more than 100, 100
+                                      value)
+                        )#, # Ser NAs to 0's
                         # group = ifelse(is.na(group),"Other",group)
+  )
   ) %>% 
@@
   # filename = "Plot.png"
-  filename = "Territory_circular_status.png",
-  path = Figures_Path
+  filename = "Territory_circular_status.png"
 )

### 2020-07-30 Scripts/Initial_Analysis.Rmd
Fixed Solomon isl.d and missing spain data

@@
   group_by(id, individual) %>% 
-  summarize(tot=sum(value,na.rm=T))
+  summarize(tot=sum(value,na.rm=T)) %>% 
+  mutate(
+    individual = ifelse(individual == "Saint Vincent & the Grenadines","Snt. Vincent & Grenadines", individual)
+    )
 
@@
                     # x = rep(max(data$id),3),
-                    x =c(0,0,0.2,0.2),
-                    y = c(-50, 0, 50, 100),
-                    label = c("50","0", "50", "100") , 
+                    x =c(0.2,0,0,0.2,0.2),
+                    y = c(-100,-50, 0, 50, 100),
+                    label = c(">100","50","0", "50", ">100") , 
                     color="black", 
@@
               x = id,
-              y = 101,
+              y = 105,
               label=individual,

### 2020-07-30 Scripts/Manuscript_Draft.Rmd
Included new reference for historic EEZ 2020

@@
 However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 nautical miles (territorial see) to 200 nautical miles** across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
+The delineation of Economic Exclusive Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 (territorial see) to 200 nautical miles** across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl; @osthagen:2020hd].
 **Shared stocks can be classified in three non-exclusive categories; transboundary, that is stocks that cross the EEZs of two or more coastal states; straddling, that cross neighboring EEZs and the high seas; and highly migratory stocks, that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].

### 2020-07-30 Scripts/Manuscript_Draft.Rmd
Sent revisions to co authors

@@
 * **Corresponding author**: j.palacios@oceans.ubc.ca
-
-# Reviewing issues
-
-## General comments
-- Not sure I understand/respond properly to Rev 3. Lines 58-59.
-
-## Questions for Gabs:
-- Teh et al comment. Do we include another data or just the explanation is fine?
-- **Rev 1.** Line 132: Why? These last sentence is hard to understand.
-
-## Figures
-- Fix figure 3 solomon islands
-
-## Analysis
-- Convert revenue to 2019 real USD
-
-## To editor
-- Note that revenue has increased substantially. this is because we converted the 2010 real USD to 2018, as suggested by Rev. #3
-
-## Specific comments
-- **Rev 1.** Line 305 to 320:
 
@@
 Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 65 billion) in the last decade.
+We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 75 billion) in the last decade.
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
@@
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 241 EEZs of 198 coastal **countries (See methods**).
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 243 EEZs of 198 coastal **countries (See methods**).
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
@@
 we did not include the high seas).
-We rely on multiple data sources including occurrence, distribution models and catch data and only considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
+We rely on multiple data sources including occurrence, distribution models and catch data and only consider a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
 
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **annual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating **a yearly average of USD 65,483 million in fishing revenue during the same time period (Fig.
-1)**.
+**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **annual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating **a yearly average of USD 75,961 million in fishing revenue during the same time period**.
 This is equivalent to 78.5% of the global fishing revenue of the same period.
-These values are more than the 34.2 million tons and USD 30,700 million in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
-**This result suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated.
-However, it is important to mention that the referenced article reports yearly FAO reported catch data for both EEZs and the high seas up to 2006.
-Thus, the divergence between studies can be influenced by the data source and time period in addition to the higher amount of transboundary species identified in the present study.
-...
-Using the FAO reported data for 2006, the average participation of the identified transboundary species was 61%, still higher than that reported by Teh and Sumaila (2015).**
+These values are more than the 34.2 million tons and USD 35,612 million (**converted to in 2019 USD**) in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
+**Such difference could be due to the utilization of reported catch data by Teh and Sumaila instead of reconstructed data and a time period difference (Teh and Sumaila's study ends in 2006).
+To compare the two studies, we used the FAO global reported data identified at the species level by the *Sea Around Us* and found that in 2006, the 633 transboundary species accounted for 40.4 million tons.
+While this is not necessarily a direct comparison (e.g.
+methodology differences might still exist), it suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated due to an incomplete knowledge on the transboundary nature of marine fished species**
 
 Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
-For example, we found that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile [@Cashion:2018cg], and thus discrete for Ecuador (**spatial threshold < 10%**).
-The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 14.8 million tons representing USD 22,167 million in fishing revenue **over the same time period**.
+For example, our study shows that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile and thus discrete for Ecuador (**spatial threshold between Ecuador and Peru < 10%**) **[@Cashion:2018cg]**.
+The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 10.8 million tons representing USD 19,243 million in fishing revenue **over the same time period**.
 Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
-These species represented only **an annual average of** 2.8 million tons and 3,691 million USD between 2005 and 2014.
+These species represented only **an annual average of** 2.8 million tons and 4,282 million USD between 2005 and 2014.
 These results underscore the importance of transboundary species at the global level.
@@
 Therefore, our intention here is not to infer stock status but to show the catch trend of transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
-Specifically, transboundary species that are only fished by one country are generally less likely to be over-exploited compared to those shared by neighboring countries (Table S2).
+Specifically, **occasions where a transboundary species is only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Table S2)**.
 Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
-This result suggests that the management of discrete species could be better off as the variation between Categories A and B is closer (*p* = 0.052) than for transboundary species (*p* = 0.001).
 
@@
 For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that contributed an average of 598.4 thousand tons to **total** catches (8.19% of total) and USD 850.2 million in **fishing** revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+Mackerel is a transboundary species that **straddles into the high seas** that contributed an average of 598.4 thousand tons to **total** catches (8.19% of total) and USD 850.2 million in **fishing** revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
 The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
 Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
-Exploring the detailed effects of climate change in the distribution of share species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
-**For example, understanding how climate change will modify the proportion that each neighboring EEZ has over a sharing species [@Palacios-Abrantes_OC], when this change is going to happen, and the economic consequence of such effects can make international treaties more resilient to climate change [@Sumaila_oc].**
+Exploring the detailed effects of climate change in the distribution of shared species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
+**For example, understanding how climate change will modify the proportion that each neighboring EEZ has over a sharing species [@PalaciosAbrantes:2020vt], when this change is going to happen, and the economic consequence of such effects can make international treaties more resilient to climate change [@RashidSumaila:tp].**
 
@@
 Note that there could be > 5 species due to similar sharing values.
-**Other consist in species that have no classification according to FishBase.**](../Figures/Fig4.png)
+**Other consist of species that have no classification according to FishBase.**](../Figures/Fig4.png)
 
@@
 Despite coral reef-related species being among the less shared neighboring EEZs identified in this study (Fig.
-4), coral regions, often share multiple species through larvae connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-In some areas like the Caribbean and the Western Indian Ocean, transboundary marine protected areas have been identified as potential tools for achieving fisheries and conservation goals [@Levin:2018in; Perez:2019dm].** The proper management of coral reef species is very important for many coastal communities, particularly in developing regions, that are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
+4), coral regions often share multiple species through larvae connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+In some areas like the Caribbean and the Western Indian Ocean, transboundary marine protected areas have been identified as potential tools for achieving fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].** The proper management of coral reef species is very important for many coastal communities, particularly in developing regions, that are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
 For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
@@
 Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated **[@Teh:2015gd]**.
+Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated**[@Teh:2015gd]**.
 This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
@@
 peer review, grey literature) to identify missing components (e.g.
-species, gears) and and sources of alternative information for missing components.
+species, gears) and sources of alternative information for missing components.
 It then derives country estimates for missing data and creates time series interpolation.
@@
 Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
-We defined EEZ boundaries using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), noting that it subdivides EEZs by regions (e.g., Mexico Pacific and Mexico Atlantic), and determined the intersections between polygons using the R package sf.
-When estimating transboundary species, we filtered out those shared by EEZs sub-regions, and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
+We defined EEZ boundaries using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), **noting that it subdivides EEZs by 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic) including islands territories**, and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
+When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g.
+USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
 Species that were present in EEZs that were non-continental territories neighboring other countries were kept separately (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).

### 2020-07-31 Scripts/Initial_Analysis.Rmd
Fixed all mf anoying country names

@@
                                                                                                            ifelse(eez_name =="US Virgin Isl.","US Virgin Islands",
-                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain (Mediterranean and Gulf of Cadiz)",
+                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain",
                                                                                                                          paste(eez_name)
@@
 
-# matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>% 
-#   mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))
+matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>%
+  mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))
 
 # Spatial Data needed to remove duplicates
-sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
-  clean_names()
-
-Clean_sau_eez_fes <- sau_eez_fes %>% 
-  gather("Type","fishing_region",2,4) %>% 
-  left_join(sau_eez_fes,
-            by = ("fishing_entity_id")
-  ) %>% 
-  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
-  summarise(n()) %>% 
-  ungroup() %>% 
-  ### Manually Fix names for estimating catch
-  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
-                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
-                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
-                                         ifelse(fishing_entity =="Italy","Italy",
-                                                ifelse(eez_name =="Chile (mainland)","Chile",
-                                                       ifelse(fishing_entity =="Brazil","Brazil",
-                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
-                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
-                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
-                                                                                   ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
-                                                                                          ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
-                                                                                          paste(eez_name)
-                                                                                          )
-                                                                                   )
-                                                                            )
-                                                       )))))))
-                           ),
-         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
-         )
-  )
+# sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
+  # clean_names()
+
+# New dara produced by Vicky 
+sau_eez_fes <- read_excel("~/Desktop/EEZ_FishingEntityID_v2_9June2020.xlsx")
+
+Clean_sau_eez_fes <- sau_eez_fes
 
@@
   mutate(
-    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
+    fishing_entity = gsub("","",fishing_entity),
+    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
+    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
+    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
+    fishing_entity = gsub("Mayotte","Mayotte (France)",fishing_entity),
+    fishing_entity = gsub("Guadeloupe","Guadeloupe (France)",fishing_entity),
+    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
+    fishing_entity = gsub("Martinique","Martinique (France)",fishing_entity),
+    fishing_entity = gsub("Montserrat","Montserrat (UK)",fishing_entity),
+    fishing_entity = gsub("New Caledonia","New Caledonia (France)",fishing_entity),
+    fishing_entity = gsub("Niue","Niue (New Zealand)",fishing_entity),
+    fishing_entity = gsub("Norfolk Island","Norfolk Isl. (Australia)",fishing_entity),
+    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
+    fishing_entity = gsub("Pitcairn","Pitcairn (UK)",fishing_entity),
+    fishing_entity = gsub("Puerto Rico","Puerto Rico (USA)",fishing_entity),
+    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
+    fishing_entity = gsub("Anguilla","Anguilla (UK)",fishing_entity),
+    fishing_entity = gsub("Svalbard and Jan Mayen Islands","Svalbard Isl. (Norway)",fishing_entity),
+    fishing_entity = gsub("Tokelau","Tokelau (New Zealand)",fishing_entity),
+    fishing_entity = gsub("Turks & Caicos Islands","Turks & Caicos Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("United States Virgin Islands","US Virgin Isl.",fishing_entity),
+    fishing_entity = gsub("Wallis and Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
+    fishing_entity = gsub("Saint Barthélemy","St Barthelemy (France)",fishing_entity),
+    fishing_entity = gsub("Iran (Islamic Republic of)","Iran",fishing_entity),
+    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
+    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
     fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
     fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
-    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
+    fishing_entity = gsub("United States of America", "USA",fishing_entity),
     fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
     fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
-    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
-    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
-    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
     fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
@@
     fishing_entity = gsub(" and ", " & ",fishing_entity),
-    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
-    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
+    # fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
     fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
-    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
-    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
+    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
     fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
-    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
-  ) %>% 
+    # fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
+    fishing_entity = gsub("Congo","Congo, R. of",fishing_entity),
+    # fishing_entity = gsub("Réunion","Réunion (France)",fishing_entity),
+  ) %>%
+  # Some of them do not work with gsub
   mutate(
-    fishing_entity = ifelse(fishing_entity == "Congo","Congo, R. of",
-                            ifelse(fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
+    fishing_entity = ifelse(fishing_entity == "Venezuela (Bolivarian Republic of)","Venezuela",
+                                 ifelse(fishing_entity == "Democratic Republic of the Congo, R. of","Congo (ex-Zaire)",
+                                        ifelse(fishing_entity == "Iran (Islamic Republic of)","Iran",
+                                               ifelse(fishing_entity == "Saint Martin (French Part)","St Martin",
+                                                      ifelse(fishing_entity == "Cocos (Keeling) Islands","Cocos (Keeling) Isl. (Australia)",
+                                                             ifelse(fishing_entity == "Falkland Islands (Malvinas)","Falkland Isl. (UK)",
+                                                                    ifelse(fishing_entity =="Micronesia (Federated States of)","Micronesia",
+                                                                           ifelse(fishing_entity == "Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",
+                                                                                  ifelse(fishing_entity == "Sint Maarten (Dutch part)","Sint Maarten",
+                                                                                         paste(fishing_entity)
+                                                                                  )
+                                                                           )
+                                                                    )
+                                                             )
+                                                      )
+                                               )
+                                        )
+                                 )
     )
@@
   filter(fishing_entity != "Solomon Isl." | sub_region != "Micronesia")
-
-# Manually change congo
-# UN_Regions[52,1] <- "Congo, R. of"
 
@@
   # st_transform(crs = 4326) %>% # 4326
-  rename(fishing_entity = name) %>% 
+  rename(fishing_entity = name_long) %>% 
   mutate(
-    fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
-    fishing_entity = gsub( "United States", "USA",fishing_entity),
+    fishing_entity = gsub(" and ", " & ",fishing_entity),
+    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
+    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
+    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
+    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
+    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
+    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
+    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
+    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
+    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
+    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
+    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
+    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
+    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
+    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
+    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
+    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
+    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
+    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
+    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
+    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
+    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
+    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
+    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
+    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
+    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
+    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
+    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
+    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
     fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
-    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
-    fishing_entity = gsub("Dem. Rep. Congo", "Congo, R. of",fishing_entity),
-    fishing_entity = ifelse(fishing_entity=="Congo", "Congo (ex-Zaire)",paste(fishing_entity))
+    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
+    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
+    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
+    fishing_entity = gsub("United States", "USA",fishing_entity),
+    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
+    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
+    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
   )
@@
                     layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(eez_name = Name) %>% 
-  st_transform(crs = "+proj=eck4")
-  # st_transform(crs = 4326) # 4326
-
-# World_sf %>% filter(str_detect(eez_name, "Cu"))
-
-#### Determine polygon areas
-
-# EEZ Area
-EEZ_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  group_by(eez_name) %>% 
-  summarise(Size_EEZ = sum(Area_km2))
-
-# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
-Entity_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  left_join(Clean_Results_Trans,
-            by = "eez_name") %>% 
-  group_by(fishing_entity,OBJECTID) %>% 
-  summarise(Size_Entity = sum(Area_km2))
-
-# Regional EEZ area
+  rename(eez_name = Name,
+         eez_id = EEZID) %>% 
+  st_transform(crs = "+proj=eck4") %>% 
+  mutate(
+    eez_id = ifelse(eez_name == "Russia (Laptev to Chukchi Sea)",913,eez_id)
+  )
+
+# Regional UN-sub region area
 Regional_Area <- World_sf %>% 
@@
 SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
+  filter(!fishing_entity_id %in% c(213,223,207,208)) %>%  # Remove high seas and 207 and 208 that we do not know 
+  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
   mutate(value = 1.16 * value)
@@
 
-SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2005_09.csv", sep =""))
-
 # Set global values for catch and revenue (within EEZ with re-constructed catch)
-SAU_Global_Data <- Clean_sau_eez_fes %>%
-  group_by(fishing_entity,fishing_entity_id) %>% 
-  summarise(n=n()) %>% 
-  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
-  clean_names() %>% 
+SAU_Global_Data <- SAU_Tim_Data %>%
   group_by(fishing_entity_id,taxon_key) %>% 
@@
   clean_names() %>% 
-  rename(eez_name=territory) %>% 
-  mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
-         )
+  rename(eez_name=territory) #%>% 
+  # mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
+         # )
 
 # List of species
-Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]
+# Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]
 
@@
   fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
-                                 ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",fishing_entity))
-         )
-
-# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
-Entity_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  left_join(Clean_Results_Trans,
-            by = "eez_name") %>% 
-  group_by(fishing_entity,OBJECTID) %>% 
-  summarise(Size_Entity = sum(Area_km2))
-
-### Tnas and billfish according to Pons 2016
-
-tunas <- c("Katsuwonus pelamis",
-"Thunnus alalunga",
-"Thunnus albacares",
-"Thunnus maccoyii",
-"Thunnus obesus",
-"Thunnus orientalis", 
-"Thunnus thynnus",
-"Xiphias gladius",
-"Istiophorus albicans",
-"Istiophorus platypterus", 
-"Istiompax indica",
-"Makaira nigricans",
-"Kajikia albidus",
-"Kajikia audax",
-"Tetrapturus angustirostris",
-"Tetrapturus belone",
-"Tetrapturus georgii",
-"Tetrapturus pfluegeri")
+                          ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",
+                                 ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)","Spain",fishing_entity)))
+  )
 
@@
 # number of eezs
-length(unique(sau_eez_fes$eez_name))
+length(unique(World_sf$eez_name))
+
 # Number of coastal territories
@@
 # Percentage of transboundary species from sampled
-n_trans/938*100
+n_trans/nrow(Species_Sampled)*100
 
@@
 # Percentage catch of species analyzed from the identified species
-Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.57%
+Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.52%
 
 # Percentage species analyzed from the identified species
-Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.2%
+Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.22%
 
@@
 
+# Numbers for paper
 Summary_Trans <- Clean_sau_eez_fes %>%
@@
   left_join(SAU_Sampled_Data) %>% 
+  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
   semi_join(Tresholded_T_Data,
-            by = c("taxon_key","fishing_entity")) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
-  group_by(Variable) %>%
-  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
-  left_join(Total_SAU_Sampled) %>% 
-  left_join(Total_SAU_Global) %>% 
-  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
-         Per_SAU = Total_Trans/Total_Global*100)
-
-### New estimates!!!
-
-# Filter SAU data for only those sampled species
-
-SAU_Sampled_Data <- Clean_sau_eez_fes %>%
-  group_by(fishing_entity,fishing_entity_id,eez_name) %>% 
-  summarise(n=n()) %>% 
-  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
-  left_join(Exploited_Species) %>% 
-  filter(!is.na(taxon_name)) %>% 
-  clean_names() %>% 
-  group_by(fishing_entity_id,taxon_key) %>% 
-  summarise_at(c("catch","value"),
-               mean,na.rm=T) %>% 
-  gather("Variable","Value",catch:value)
-
-x <- Tresholded_T_Data %>% 
-  select(taxon_key,eez_name) %>% 
-  group_by(taxon_key,eez_name) %>% 
-  summarise(n=n()) %>% 
-  ungroup() %>% 
-  select(-n) %>% 
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>% 
-  left_join(SAU_Sampled_Data,
-            by = c("taxon_key","fishing_entity_id")) %>% 
-  # filter(eezid != 0) %>%
-  group_by(Variable) %>%
-  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
-  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100)
-
-Summary_Trans <- Clean_sau_eez_fes %>%
-  group_by(fishing_entity,fishing_entity_id) %>% 
-  summarise(n=n()) %>% 
-  left_join(SAU_Sampled_Data) %>% 
-  semi_join(Tresholded_T_Data,
-            by = c("taxon_key","fishing_entity")) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
+            by = c("taxon_key","fishing_entity")
+  ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
   group_by(Variable) %>%
@@
             by = "eez_name") %>% 
+  group_by(taxon_key,fishing_entity_id) %>% 
+  summarise(n()) %>% 
   left_join(SAU_Global_Vicky,
             by = c("taxon_key","fishing_entity_id")) %>% 
-  # filter(eezid != 0) %>%
+  # filter(eezid != 0) %>% # I think they used high seas data as well?
   group_by() %>%
   summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
-  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100);Summary_Trans_vicky
+  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100); Summary_Trans_vicky
 
@@
   ) %>% 
-  # bind_rows(Species_Left_Out) %>% 
   group_by(taxon_key,fishing_entity,eez_name) %>% 
@@
   anti_join(Tresholded_T_Data,
-            by = c("taxon_key","eez_name"))
+            by = c("taxon_key","fishing_entity"))
 
@@
 
+Summary_Discrete <- Clean_sau_eez_fes %>%
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(n=n()) %>% 
+  left_join(SAU_Sampled_Data) %>% 
+  semi_join(Discrete,
+            by = c("taxon_key","fishing_entity")
+            ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
+  group_by(Variable) %>%
+  summarise(Total_Dis = sum(Value, na.rm=T)) %>% 
+  left_join(Total_SAU_Sampled) %>% 
+  left_join(Total_SAU_Global) %>% 
+  mutate(Per_sampled = Total_Dis/Total_Sampled*100,
+         Per_SAU = Total_Dis/Total_Global*100)
+
 ###_________________###
@@
   # Discrete species (not in Tresholded)
-Discrete_Exclusive <- Clean_Results_Trans %>% 
+Discrete_Exclusive <- Discrete %>% 
   filter(!taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
@@
   group_by(taxon_key) %>% 
-  summarise(n())
+  summarise(n()) %>% 
+  left_join(Exploited_Species)
 
@@
          Per_SAU = Total_Discrete/Total_Global*100)
+
+```
+
+```{r test, eval = F, echo = F}
+
+Tra <- Summary_Trans %>% 
+  mutate(Type = "Trans")
+
+Dis <- Summary_Discrete %>% 
+  mutate(Type = "Dis")
+
+Solo <- Summary_Discrete_Exclusive %>% 
+  mutate(Type = "Solo")
+
+All <- bind_rows(Tra,Dis,Solo) %>% 
+  select(1:7) %>% 
+  group_by(taxon_key,fishing_entity) %>% 
+  summarise(n())
+
+missing <- anti_join(Total_SAU_Sampled,All,
+          by = c("fishing_entity_id","taxon_key"))
+
+missing %>% 
+  group_by(Variable) %>% 
+  summarise(sum(Value))
+
+# Now
+58242635
+# Goal
+58986239
+
+58986239-58242635
 
@@
   left_join(Top_5_Ecosystem) %>% # includes the groups
-  filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
-  left_join(SAU_Catch_Data,
-            by = c("eez_name","taxon_key")
-  ) %>%
+  left_join(Clean_sau_eez_fes) %>% 
+  left_join(SAU_Sampled_Data,
+            by = c("fishing_entity_id","taxon_key")
+  ) %>%
+  filter(taxon_name %in% Top_5_Ecosystem$taxon_name,
+         Variable == "catch") %>%
   group_by(fishing_entity,group) %>%
-  summarise(top_catch = sum(total_catch)) %>%
+  summarise(top_catch = sum(Value)) %>%
   group_by(group) %>%
@@
              scales = "free") +
-  ggtheme_plot() +
+  # ggtheme_plot() +
+  my_ggtheme_p() +
   scale_x_reordered() +
@@
 save_plot(
-  paste(Figures_Path,"spp_circular_catch_country.png",sep=""),
+  paste("spp_circular_catch_country.png",sep=""),
   # "spp_plot.png",

### 2020-07-31 Scripts/Initial_Analysis.Rmd
Re plotted all figures (all ist gut!)

@@
                          colours = pal,
-                         limits = c(0,14000),
+                         limits = c(0,14100),
                          breaks = seq(0,14000,3500)
@@
 
-# Conuntry Names relation
-
-matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>%
-  mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))
-
-# Spatial Data needed to remove duplicates
-# sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
-  # clean_names()
-
 # New dara produced by Vicky 
-sau_eez_fes <- read_excel("~/Desktop/EEZ_FishingEntityID_v2_9June2020.xlsx")
-
-Clean_sau_eez_fes <- sau_eez_fes
+Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)
 
@@
 
-# View(unique(World_land_sf$fishing_entity))
-
-# head(World_land_sf)
-
 # Load SAU shapefile name and paths
@@
   left_join(UN_Regions) %>% 
-  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
+  filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
   group_by(sub_region) %>% 
-  summarise(Size_Region = sum(Area_km2)) %>% 
+  summarise(Size_Region = sum(Area_km2,na.rm=T)) %>% 
   mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
@@
   clean_names() %>% 
-  rename(eez_name=territory) #%>% 
-  # mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
-         # )
+  rename(eez_name=territory) %>% 
+  mutate(
+    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
+    eez_name = gsub("Chile","Chile (mainland)",eez_name),
+    eez_name = gsub("Curaçao","Curacao",eez_name),
+    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
+    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
+    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
+    eez_name = gsub("Vietnam","Viet Nam",eez_name),
+    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
+                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
+                             ifelse(eez_name == "Greece","Greece (without Crete)",
+                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
+                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
+                                                  ifelse(eez_name == "Italy","Italy (mainland)",
+                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
+                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
+                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
+                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
+                                                                                     ifelse(eez_name =="Spain (Mediterranean and Gulf of Cadiz)","Spain (mainland, Med and Gulf of Cadiz)",
+                                                                                            ifelse(eez_name =="Réunion (France)","Reunion (France)",
+                                                                                     eez_name)
+                                                                       ))
+                                                                       )
+                                                         ))))
+                             )
+                      )
+    )))
 
@@
 Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
-  mutate(eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
-                           ifelse(eez_name == "Curacao (Netherlands)","Curaçao (Netherlands)",eez_name)
-  ),
-  fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
-                          ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",
-                                 ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)","Spain",fishing_entity)))
-  )
+  mutate(
+    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
+    eez_name = gsub("Chile","Chile (mainland)",eez_name),
+    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
+    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
+    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
+    eez_name = gsub("Vietnam","Viet Nam",eez_name),
+    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
+                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
+                             ifelse(eez_name == "Greece","Greece (without Crete)",
+                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
+                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
+                                                  ifelse(eez_name == "Italy","Italy (mainland)",
+                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
+                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
+                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
+                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
+                                                                                     eez_name)
+                                                                       ))
+                                                         ))))
+                             )
+                      )
+    )
+
+Clean_Results_Trans %>% anti_join(Clean_sau_eez_fes, by = "eez_name") %>% 
+  group_by(eez_name) %>% 
+  summarise(n())
 
@@
     model_index >= MI
-  )
+  ) %>% 
+  select(-fishing_entity) %>% 
+  left_join(Clean_sau_eez_fes, by = "eez_name")
 
@@
 
-```{r test, eval = F, echo = F}
-
-Tra <- Summary_Trans %>% 
-  mutate(Type = "Trans")
-
-Dis <- Summary_Discrete %>% 
-  mutate(Type = "Dis")
-
-Solo <- Summary_Discrete_Exclusive %>% 
-  mutate(Type = "Solo")
-
-All <- bind_rows(Tra,Dis,Solo) %>% 
-  select(1:7) %>% 
-  group_by(taxon_key,fishing_entity) %>% 
-  summarise(n())
-
-missing <- anti_join(Total_SAU_Sampled,All,
-          by = c("fishing_entity_id","taxon_key"))
-
-missing %>% 
-  group_by(Variable) %>% 
-  summarise(sum(Value))
-
-# Now
-58242635
-# Goal
-58986239
-
-58986239-58242635
-
-```
-
 ## Results per Territory
@@
 Transboundary_Spp <- Tresholded_T_Data %>% 
-  group_by(eez_name) %>% 
+  group_by(eez_id) %>% 
   summarise(
@@
   ) %>% 
-  left_join(EEZ_Area, 
-            by = "eez_name") %>% 
+  # left_join(EEZ_Area, 
+  #           by = "eez_name") %>% 
   mutate(
@@
     # Include the weighted method for supplementals
-    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
+    # Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
     # Weight_Bins = cut(Weight_Spp,breaks = 5),
-    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
-                           labels = c('super low', 'low','median', 'high','super high')
-    )
+    # Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
+                           # labels = c('super low', 'low','median', 'high','super high')
+    # )
   )
@@
   left_join(Tresholded_T_Data,
-            by = "fishing_entity") %>% 
+            by = c("fishing_entity","fishing_entity_id")
+            ) %>% 
   group_by(fishing_entity_id,
@@
   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Transboundary_Spp, by ="eez_name") %>% 
+  left_join(Transboundary_Spp, by ="eez_id") %>% 
   st_transform(crs = "+proj=eck4")
   # st_transform(crs = 4326)
+
+Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")
 
@@
 ```{r Figure_1}
-
+gc()
 # Set color pal
@@
 # Variable to plot (value or catch)
-Variable_plot <- "value"
+Variable_plot <- "catch"
 CreateFigureOne(Variable_plot)
@@
 # -------------------------- #
-
 # Stock status Data
-
 Status_Data_Plot <- Tresholded_T_Data %>% 
@@
 
+length(unique(Status_Data_Plot$individual))
+length(unique(Status_Data_Plot$observation))
+
 Status_Plot_Data <- tibble(
   fishing_entity = rep(unique(Status_Data_Plot$individual),4),
-  observation = rep(unique(Status_Data_Plot$observation),153)
+  observation = rep(unique(Status_Data_Plot$observation),157)
 ) %>% 
@@
   mutate(
-    individual = ifelse(individual == "Saint Vincent & the Grenadines","Snt. Vincent & Grenadines", individual)
+    individual = ifelse(individual == "Saint Vincent & the Grenadines","Snt. Vincent & Grenadines",
+                        ifelse(individual == "Brunei Darussalam","Burnei",
+                               individual)
+                        )
   )
@@
 
-# If you want to show revenue
-# Country_Spp_Data <- sau_eez_fes %>% 
-#   group_by(fishing_entity_id,fishing_entity) %>% 
-#   summarise(n=n()) %>% 
-#   select(-n) %>% 
-#   left_join(SAU_Revenue_Data) %>% 
-#   left_join(Tresholded_T_Data) %>% 
-#   left_join(Exploited_Species) %>% 
-#   left_join(Top_5_Ecosystem) %>% # includes the groups
-#   filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>% 
-#   group_by(fishing_entity,group) %>% 
-#   summarise(top_catch = sum(mean_value)/1000000) %>%  # Million
-#   group_by(group) %>% 
-#   top_n(5)
+# Just catch data
+Catch_Data <- SAU_Sampled_Data %>% 
+  filter(Variable == "catch")
+
+# Just country names
+country_names <- Clean_sau_eez_fes %>% 
+  select(fishing_entity,fishing_entity_id) %>% 
+  distinct()
 
@@
   left_join(Top_5_Ecosystem) %>% # includes the groups
-  left_join(Clean_sau_eez_fes) %>% 
-  left_join(SAU_Sampled_Data,
+  group_by(taxon_key,taxon_name,fishing_entity_id,fishing_entity,group) %>%
+  summarise(n()) %>% 
+  left_join(Catch_Data,
             by = c("fishing_entity_id","taxon_key")
   ) %>%
-  filter(taxon_name %in% Top_5_Ecosystem$taxon_name,
-         Variable == "catch") %>%
-  group_by(fishing_entity,group) %>%
-  summarise(top_catch = sum(Value)) %>%
+  filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
+  group_by(fishing_entity_id,group) %>%
+  summarise(top_catch = sum(Value,na.rm=T)) %>%
   group_by(group) %>%
   top_n(5) %>% 
+  left_join(country_names, by = "fishing_entity_id") %>% 
   mutate(
@@
 ```{r species_circluar_plot, eval = F, echo = T}
-
-Median_trans <- median(Species_Data$value)
-# hist(Species_Data$value)
-# unique(Species_Data$group)
 
@@
                inherit.aes = FALSE ) +
-  # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median
   # Add text showing the value of each line

### 2020-07-31 Scripts/Initial_Analysis.Rmd
Need to figure out weight method

@@
 
+Entity_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_Results_Trans,
+            by = "eez_name") %>% 
+  group_by(fishing_entity) %>% 
+  summarise(Size_Entity = sum(Area_km2))
+
 # Regional UN-sub region area
@@
   filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
+  select(-geometry) %>% 
   group_by(sub_region) %>% 
@@
 
-SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
-  filter(!fishing_entity_id %in% c(213,223,207,208)) %>%  # Remove high seas and 207 and 208 that we do not know 
+SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
+  # Remove high seas and 207 and 208 that are unknown
+  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
+  # Allocate catch of islands to UK
   mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
-  mutate(value = 1.16 * value)
-
-# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
-# SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2010_14.csv", sep =""))
-
-# Set global values for catch and revenue (within EEZ with re-constructed catch)
-SAU_Global_Data <- SAU_Tim_Data %>%
+  # Convert to 2019 real USD
+  mutate(value = 1.16 * value) %>%
+  # Average 10 years of data
   group_by(fishing_entity_id,taxon_key) %>% 
@@
                                                                                                    eez_name)
-                                                                       ))
-                                                                       )
-                                                         ))))
-                             )
-                      )
-    )))
-
-# List of species
-# Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]
-
-# Read Results
-# Clean_Results_Trans <- GetTransResults(Spp) %>% 
-#   CleanResults(.) %>% 
-#   clean_names() %>% 
-#   rename(eez_name = territory,
-#          fishing_entity = ct_fishing_entity,
-#          eez_neighbour = neighbour) %>% 
-#   mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))
-
-# Read Results For Carmelia
+                                                                                     )
+                                                                              )
+                                                                       )
+                                                                )
+                                                         )
+                                                  )
+                                           )
+                                    )
+                             )
+                      )
+    )
+  )
+
+# Load Transboundary Results
 
@@
                                                                                      eez_name)
-                                                                       ))
-                                                         ))))
-                             )
-                      )
-    )
-
-Clean_Results_Trans %>% anti_join(Clean_sau_eez_fes, by = "eez_name") %>% 
-  group_by(eez_name) %>% 
-  summarise(n())
+                                                                       )
+                                                                )
+                                                         )
+                                                  )
+                                           )
+                                    )
+                             )
+                      )
+    )
+    )
 
@@
 ## Overall results
+
+### Transboundary Species
 
@@
 Total_SAU_id <- SAU_Global_Data %>% 
-  left_join(Exploited_Species) %>% # list of SAU exploited species identified
-  filter(!is.na(taxon_name)) %>% # reove those NAs 
+  filter(taxon_key %in% Exploited_Species$taxon_key) %>%
   group_by(Variable) %>% 
@@
 # Percentage catch of species analyzed from the identified species
-Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.52%
+Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.49%
 
 # Percentage species analyzed from the identified species
-Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.22%
-
-# When we do not remove the groups that are not species level the number sampled drops to ~60%
-
-### So what species are NOT there? 
-#  Absten species
-# Missing_Species <- SAU_Global_Data %>%
-#   filter(!taxon_key %in% Species_Sampled$TaxonKey) %>% 
-#   left_join(Exploited_Species) %>% 
-#   filter(!is.na(taxon_name)) %>% 
-#   group_by(taxon_key,taxon_name,common_name) %>% 
-#   summarise(sum(Value))
+Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.23%
 
@@
 # Filter SAU data for only those sampled species
-SAU_Sampled_Data <- Clean_sau_eez_fes %>%
-  group_by(fishing_entity,fishing_entity_id) %>% 
-  summarise(n=n()) %>% 
-  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
-  left_join(Exploited_Species) %>% 
-  filter(!is.na(taxon_name)) %>% 
-  clean_names() %>% 
-  group_by(fishing_entity_id,taxon_key) %>% 
-  summarise_at(c("catch","value"),
-               mean,na.rm=T) %>% 
-  gather("Variable","Value",catch:value)
+SAU_Sampled_Data <- SAU_Global_Data %>% 
+  filter(taxon_key %in% Exploited_Species$taxon_key)
 
 # Numbers for paper
-Summary_Trans <- Clean_sau_eez_fes %>%
-  group_by(fishing_entity,fishing_entity_id) %>% 
-  summarise(n=n()) %>% 
-  left_join(SAU_Sampled_Data) %>% 
-  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
+
+Summary_Trans <- SAU_Sampled_Data %>% 
   semi_join(Tresholded_T_Data,
-            by = c("taxon_key","fishing_entity")
-  ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
+            by = c("taxon_key","fishing_entity_id")
+  ) %>% 
   group_by(Variable) %>%
@@
 
+### Discussion with Teh
+
 ```{r comparriosn_wtih_teh}
 
-# Average data for the last 10 years
-
-SAU_Global_Vicky <- SAU_Vicky_Data %>% 
+# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
+# Provided by Vicky Lam
+SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep ="")) %>% 
   filter(#eezid != 0,
@@
   summarise_at(c("sumcatch"),
-               mean,na.rm=T)
+               sum,na.rm=T)
 
 ## Get the total of global data
-Total_SAU_Vicky <- sum(SAU_Global_Vicky$sumcatch,na.rm = T)
-
-Summary_Trans_vicky <- Tresholded_T_Data %>% 
-  select(taxon_key,eez_name) %>% 
-  group_by(taxon_key,eez_name) %>% 
-  summarise(n=n()) %>% 
-  ungroup() %>% 
-  select(-n) %>% 
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>% 
-  group_by(taxon_key,fishing_entity_id) %>% 
-  summarise(n()) %>% 
-  left_join(SAU_Global_Vicky,
-            by = c("taxon_key","fishing_entity_id")) %>% 
-  # filter(eezid != 0) %>% # I think they used high seas data as well?
+Total_SAU_FAO <- sum(SAU_FAO_Data$sumcatch,na.rm = T)
+
+# Estimate numbers for paper
+SAU_FAO_Data %>% 
+  semi_join(Tresholded_T_Data,
+            by = c("taxon_key","fishing_entity_id")
+  ) %>% 
   group_by() %>% 
   summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
-  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100); Summary_Trans_vicky
-
-```
+  mutate(Per_Sau_FAO = Total_Trans/Total_SAU_FAO*100)
+
+```
+
+### Discrete Species
+
+Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
 
@@
   anti_join(Tresholded_T_Data,
-            by = c("taxon_key","fishing_entity"))
+            by = c("taxon_key","fishing_entity")) %>% 
+  left_join(Clean_sau_eez_fes)
 
@@
 
-Summary_Discrete <- Clean_sau_eez_fes %>%
-  group_by(fishing_entity,fishing_entity_id) %>% 
-  summarise(n=n()) %>% 
-  left_join(SAU_Sampled_Data) %>% 
+Summary_Discrete <- SAU_Sampled_Data %>% 
   semi_join(Discrete,
-            by = c("taxon_key","fishing_entity")
-            ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
+            by = c("taxon_key","fishing_entity_id")
+  ) %>% 
   group_by(Variable) %>%
-  summarise(Total_Dis = sum(Value, na.rm=T)) %>% 
+  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
   left_join(Total_SAU_Sampled) %>% 
   left_join(Total_SAU_Global) %>% 
-  mutate(Per_sampled = Total_Dis/Total_Sampled*100,
-         Per_SAU = Total_Dis/Total_Global*100)
-
+  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
+         Per_SAU = Total_Trans/Total_Global*100)
+
+```
+
+### Discrete Exclusive
+
+Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary according to our methods of determination (See methods).
+
+```{r Discrete_Exclusive_per_Territory, eval = F, echo = F}
 ###_________________###
@@
 
+# Numbers for paper
 Summary_Discrete_Exclusive <- Discrete_Exclusive %>% 
@@
 
-Determine the number of species per territory
+### Data For Map
+
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America and Eastern Asia
 
 ```{r Data_per_Territory, eval = F, echo = F}
+
+EEZ_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  group_by(eez_id) %>% 
+  summarise(Size_EEZ = sum(Area_km2))
+
+Entity_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  left_join(Clean_Results_Trans,
+            by = "eez_name") %>% 
+  group_by(fishing_entity) %>% 
+  summarise(Size_Entity = sum(Area_km2))
 
@@
   ) %>% 
-  # left_join(EEZ_Area, 
-  #           by = "eez_name") %>% 
+  left_join(EEZ_Area,
+            by = "eez_id") %>%
   mutate(
@@
     # Include the weighted method for supplementals
-    # Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
-    # Weight_Bins = cut(Weight_Spp,breaks = 5),
-    # Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
-                           # labels = c('super low', 'low','median', 'high','super high')
-    # )
+    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
+    Weight_Bins = cut(Weight_Spp,breaks = 5),
+    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
+                           labels = c('super low', 'low','median', 'high','super high')
+    )
   )
@@
 
-Total_Value_EEZ <- sau_eez_fes %>% 
+Total_Value_EEZ <- Clean_sau_eez_fes %>% 
   group_by(fishing_entity_id, fishing_entity) %>% 
@@
 
-Value_Trans_Country <- sau_eez_fes %>% 
+Value_Trans_Country <- Clean_sau_eez_fes %>% 
   group_by(fishing_entity_id, fishing_entity) %>% 
@@
   spread(Variable,Trans_Total) %>% 
-  # left_join(Entity_Area,
-  #           by = "fishing_entity") %>%
-  # # Include the weighted method for supplementals
-  # mutate_at(
-  #   vars(catch,value),
-  #   funs(weight= ./(Size_Entity/1000000))
-  # ) %>%
-  # gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
-  gather("Variable","Value",catch:value) %>%
+  left_join(Entity_Area,
+            by = "fishing_entity") %>%
+  # Include the weighted method for supplementals
+  mutate_at(
+    vars(catch,value),
+    funs(weight= ./(Size_Entity/1000000))
+  ) %>%
+  gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
+  # gather("Variable","Value",catch:value) %>%
   group_by(fishing_entity,Variable,Value) %>% 
@@
 
+### Data for continental analysis
+
 ```{r Data_per_Continent, eval = F, echo = F}
@@
   group_by(georegion,Variable) %>% 
-  summarise_if(is.numeric,sum,na.rm=T) #%>% 
-  # select(-Size_Entity,-Trans_Entity_n)
+  summarise_if(is.numeric,sum,na.rm=T)
 
@@
                na.rm=T) %>%
-  # select(-Size_Entity,-Trans_Entity_n) %>% 
   arrange(Variable) %>%
@@
 
-Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country
+Figure 1.
+Number of transboundary species and their contribution to global fisheries catches and revenue.
+A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+B) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions according to the United Nations sub-regions.
+Points = mean +- sd.
+Revenue in 2010 real USD
 
@@
 
+### China, US, Russia, and Peru
+
+```{r Map_Particulars, eval =F, echo =F}
+
+# Revenue details
+
+Top_Rev_Countries <- c("China", "Peru", "Russian Federation", "Chile", "USA","Japan")
+
+# Total revenue from Top countries
+Total_Top_Rev <- Value_Trans_Country %>% 
+  # filter(Variable == "value") %>% 
+  filter(fishing_entity %in% Top_Rev_Countries) %>% 
+  left_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  left_join(Subregion_Trans_raw_Value) %>% 
+  mutate(Per_Top = Value/Value_sum*100) %>% 
+  select(1:3,Per_Top)
+
+### Percentaga that top 5 represents
+
+Top5 <- c("Peru", "Russian Federation", "Japan", "USA","China")
+
+Total_Top5 <- Value_Trans_Country %>% 
+  filter(Variable == "value") %>% 
+  filter(fishing_entity %in% Top_Rev_Countries) %>% 
+  ungroup() %>% 
+  select(fishing_entity,Value) %>% 
+  group_by() %>% 
+  summarise(sum(Value)) %>% 
+  pull()/(Total_SAU_Sampled$Total_Sampled[2]/1000000)*100
+
+```
+
+### Statistical differences within regions
+We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.
+
+```{r statistics_fig1, eval = F, echo = T}
+
+### Using ANOVA to estimate significan differences within regions for revenue and catch of transboundary species
+
+### Reveneu ANOVA
+
+Subregion_Rev_stats <- Subregion_Data_stats %>% 
+  filter(Variable == "value")
+
+Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
+Rev_aov
+
+summary(Rev_aov)
+#              Df    Sum Sq Mean Sq F value   Pr(>F)    
+# sub_region   16  75738982 4733686   4.948 3.46e-08 ***
+# Residuals   158 151144071  956608
+
+#  Post-hoc analysis
+TukeyHSD(Rev_aov) %>% 
+  tidy() %>% 
+  filter(adj.p.value < 0.05)
+
+### Catch ANOVA
+
+Subregion_Catch_stats <- Subregion_Data_stats %>% 
+  filter(Variable == "catch")
+
+Catch_aov <- aov(Value~sub_region, data = Subregion_Catch_stats)
+Catch_aov
+
+summary(Catch_aov)
+#  Df Sum Sq Mean Sq F value  Pr(>F)   
+# sub_region   16  27.51  1.7195   2.265 0.00539 **
+# Residuals   158 119.97  0.7593
+
+#  Post-hoc analysis
+TukeyHSD(Catch_aov) %>% 
+   tidy() %>% 
+  filter(adj.p.value < 0.05) # Eastern Asia
+
+# Weight ANOVA
+Subregion_Weigh_stats <- Subregion_Data_stats %>% 
+  filter(Variable == "value_weight")
+
+Weight_aov <- aov(Value~sub_region, data = Subregion_Weigh_stats)
+Weight_aov
+summary(Weight_aov)
+
+#  Df Sum Sq Mean Sq F value  Pr(>F)   
+# sub_region   16   6722   420.1   2.411 0.00289 **
+# Residuals   158  27532   174.3                   
+# ---
+# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+#### There are significant differences. But between what?
+
+#  Post-hoc analysis
+TukeyHSD(Weight_aov) %>% 
+  tidy() %>% 
+  filter(adj.p.value < 0.05) # Northern Europe
+```
+
+## Weighted bar plots
+
+### Data for Weighted plot
 ```{r Weight_Revenue, eval =F, echo =F}
+r
+Continent_Trans_Value <- Subregion_Trans_raw_Value %>% 
+  left_join(Regional_Area,
+            by = "sub_region") %>% 
+  mutate(
+    Value_sum= Value_sum*1000000,
+    weighted_value = Value_sum/Size_Region
+    )
 
@@
 
-### China, US, Russia, and Peru
-
-```{r Map_Particulars, eval =F, echo =F}
-
-# Revenue details
-
-Top_Rev_Countries <- c("China", "Peru", "Russian Federation", "Chile", "USA","Japan")
-
-# Total revenue from Top countries
-Total_Top_Rev <- Value_Trans_Country %>% 
-  filter(Variable == "value") %>% 
-  filter(fishing_entity %in% Top_Rev_Countries) %>% 
-  left_join(UN_Regions,
-            by = "fishing_entity") %>% 
-  left_join(Subregion_Trans_raw_Value) %>% 
-  mutate(Per_Top = Value/Value_sum*100) %>% 
-  select(1:3,Per_Top)
-
-Top_Rev <- sau_eez_fes %>% 
-  filter(fishing_entity %in% Top_Rev_Countries) %>% 
-  group_by(fishing_entity_id, fishing_entity) %>% 
-  summarise(n=n()) %>% # Get all of the fishing entity and id
-  select(-n) %>% 
-  full_join(Tresholded_T_Data,
-            by = "fishing_entity") %>% 
-  group_by(fishing_entity_id,
-           fishing_entity,
-           taxon_key) %>% 
-  summarise(n()) %>% # get each taxa per nation
-  left_join(SAU_Sampled_Data,
-            by = c("fishing_entity_id","taxon_key")) %>% 
-  filter(Variable == "value") %>% 
-  left_join(Exploited_Species) %>% 
-  group_by(fishing_entity) %>%
-  top_n(16,Value) %>%
-  select(fishing_entity,Variable,Value,taxon_name) %>% 
-  mutate(Top_Value = Value/1000000) %>% # Million of USD
-  select(-Value) %>% 
-  left_join(Total_Top_Rev,
-            by = c("fishing_entity","Variable")
-            ) %>% 
-  mutate(Ratio = Top_Value/Value*100)
-
-Top_Rev %>% 
-  group_by(fishing_entity) %>% 
-  summarise(sum(Ratio))
-
-### Total revenue from the top 5
-
-Top5 <- c("Peru", "Russian Federation", "Japan", "USA","China")
-
-Total_Top5 <- Value_Trans_Country %>% 
-  filter(Variable == "value") %>% 
-  filter(fishing_entity %in% Top_Rev_Countries) %>% 
-  ungroup() %>% 
-  select(fishing_entity,Value) %>% 
-  group_by() %>% 
-  summarise(sum(Value)) %>% 
-  pull()/(Total_SAU_Sampled$Total_Sampled[2]/1000000)*100
-
-```
-
-### Statistical differences within regions
-We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.
-
-```{r statistics_fig1, eval = F, echo = T}
-
-### Using ANOVA to estimate significan differences within regions for revenue and catch of transboundary species
-
-### Reveneu ANOVA
-
-Subregion_Rev_stats <- Subregion_Data_stats %>% 
-  filter(Variable == "value")
-
-Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
-Rev_aov
-
-summary(Rev_aov)
-#              Df    Sum Sq Mean Sq F value   Pr(>F)    
-# sub_region   16  75738982 4733686   4.948 3.46e-08 ***
-# Residuals   158 151144071  956608
-
-#  Post-hoc analysis
-TukeyHSD(Rev_aov) %>% 
-  tidy() %>% 
-  filter(adj.p.value < 0.05)
-
-### Catch ANOVA
-
-Subregion_Catch_stats <- Subregion_Data_stats %>% 
-  filter(Variable == "catch")
-
-Catch_aov <- aov(Value~sub_region, data = Subregion_Catch_stats)
-Catch_aov
-
-summary(Catch_aov)
-#  Df Sum Sq Mean Sq F value  Pr(>F)   
-# sub_region   16  27.51  1.7195   2.265 0.00539 **
-# Residuals   158 119.97  0.7593
-
-#  Post-hoc analysis
-TukeyHSD(Catch_aov) %>% 
-   tidy() %>% 
-  filter(adj.p.value < 0.05) # Eastern Asia
-
-# Weight ANOVA
-Subregion_Weigh_stats <- Subregion_Data_stats %>% 
-  filter(Variable == "value_weight")
-
-Weight_aov <- aov(Value~sub_region, data = Subregion_Weigh_stats)
-Weight_aov
-summary(Weight_aov)
-
-#  Df Sum Sq Mean Sq F value  Pr(>F)   
-# sub_region   16   6722   420.1   2.411 0.00289 **
-# Residuals   158  27532   174.3                   
-# ---
-# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-#### There are significant differences. But between what?
-
-#  Post-hoc analysis
-TukeyHSD(Weight_aov) %>% 
-  tidy() %>% 
-  filter(adj.p.value < 0.05) # Northern Europe
-```
-
 ### OHI-inspired Circular plot for Territories
+
+*We determined the exploitation category of each species according to the catch trend within each EEZ (Fig. 3).
+
+### Data for Circular plot
 
@@
 ```
+
+### Circular plot
 

### 2020-07-31 Scripts/Initial_Analysis.Rmd
updated statistics

@@
 # Residuals   447
-
-summary.aov(mano)
-#  Response Discrete_value :
-#              Df Sum Sq Mean Sq F value    Pr(>F)    
-# observation   2   7088  3544.1  26.305 1.584e-11 ***
-# Residuals   447  60226   134.7                      
 # ---
@@
 
+     # Df Sum Sq Mean Sq F value Pr(>F)    
+# observation   2  24776   12388   53.93 <2e-16 ***
+# Residuals   459 105436     230
+
 TukeyHSD(Stat_Cat_aov)
@@
 # Category C-Category B 11.213333  7.306098 15.120569 0.0000000
+
+#    diff       lwr      upr     p adj
+# Category B-Category A  5.948052  1.886814 10.00929 0.0018096
+# Category C-Category A 17.629870 13.568633 21.69111 0.0000000
+# Category C-Category B 11.681818  7.620581 15.74306 0.0000000
 
@@
 # Residuals   380  55992     147
+
+# f Sum Sq Mean Sq F value   Pr(>F)    
+# observation   2   5322    2661   25.58 3.76e-11 ***
+# Residuals   382  39740     104
 

### 2020-07-31 Scripts/Manuscript_Draft.Rmd
updated numbers in manuscript

@@
 Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 80% of the global-EEZs catches (48 million tons) and 78.5% of fisheries revenue (USD 75 billion) in the last decade.
+We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 82% of the global-EEZs catches (48 million tons) and 81% of fisheries revenue (USD 77 billion) in the last decade.
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
@@
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 243 EEZs of 198 coastal **countries (See methods**).
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 280 EEZs of 198 coastal **countries (See methods**).
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **annual** average of 47.6 million tons, representing 79.9% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating **a yearly average of USD 75,961 million in fishing revenue during the same time period**.
-This is equivalent to 78.5% of the global fishing revenue of the same period.
-These values are more than the 34.2 million tons and USD 35,612 million (**converted to in 2019 USD**) in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
+**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **annual** average of 48.5 million tons, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating **a yearly average of USD 77,591 million in fishing revenue during the same time period**.
+This is equivalent to 81.3% of the global fishing revenue of the same period.
+These values are more than the 34.2 million tons and USD 40,187 million (**converted to in 2019 USD**) in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
 **Such difference could be due to the utilization of reported catch data by Teh and Sumaila instead of reconstructed data and a time period difference (Teh and Sumaila's study ends in 2006).
-To compare the two studies, we used the FAO global reported data identified at the species level by the *Sea Around Us* and found that in 2006, the 633 transboundary species accounted for 40.4 million tons.
+To compare the two studies, we used the FAO global reported data identified at the species level by the *Sea Around Us* and found that in 2006, the 633 transboundary species accounted for 40.7 million tons.
 While this is not necessarily a direct comparison (e.g.
@@
 For example, our study shows that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile and thus discrete for Ecuador (**spatial threshold between Ecuador and Peru < 10%**) **[@Cashion:2018cg]**.
-The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 10.8 million tons representing USD 19,243 million in fishing revenue **over the same time period**.
+The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 7.3 million tons representing USD 12,710 million in fishing revenue **over the same time period**.
 Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
@@
 
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average yearly** revenue = 3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ 2,667 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,158) = 4.948, *p* < 0.001, $\alpha$ = 0.05) (Fig.
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average yearly** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD).
+The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05) (Fig.
 1B).
-China (USD 6,279 million) in **Eastern** Asia and the USA **in Northern America** (USD 9,605 million) contribute 55% and 82% to the **annual average** revenues.
-In addition to China and the USA, Russia (USD 6,361 million), Peru (USD 5,211 **million**) and Japan (USD 3,368 **million**) are among the top five countries with the most fishing revenue generated from transboundary species in the last decade.
-These five nations are responsible for 40% of the global fisheries revenue from transboundary species.
+China (USD 7,284 million) in **Eastern** Asia and the USA **in Northern America** (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species in the last decade.
+These five nations are responsible for 41% of the global fisheries revenue from transboundary species.
 
@@
 While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Therefore, our intention here is not to infer stock status but to show the catch trend of transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,447) = 27.091, *p* < 0.001).
+Therefore, our intention here is not to infer stock status but to show the catch trend of transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 29.406, *p* < 0.001).
 Specifically, **occasions where a transboundary species is only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Table S2)**.
-Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,447) = 55.01, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,380) = 21.86, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.052).
+Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 53.93, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,382) = 25.58, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.058).
 
@@
 For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that **straddles into the high seas** that contributed an average of 598.4 thousand tons to **total** catches (8.19% of total) and USD 850.2 million in **fishing** revenue (7.17% of total) to the countries involved in the dispute between 2005 and 2014.
+Mackerel is a transboundary species that **straddles into the high seas** that contributed an average of 598.4 thousand tons to **total** catches (8.18% of total) and USD 986.24 million in **fishing** revenue (7.16% of total) to the countries involved in the dispute between 2005 and 2014.
 The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.

### 2020-08-03 Scripts/Initial_Analysis.Rmd
Removed Tablesname

@@
 } # End of function
-```
-
-### Clean names table
-
-Create a table that matches all names
-
-```{r names_table, eval =F, echo =F}
-
-Clean_sau_eez_fes <- sau_eez_fes %>% 
-  gather("Type","fishing_region",2,4) %>% 
-  left_join(sau_eez_fes,
-            by = ("fishing_entity_id")
-  ) %>% 
-  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
-  summarise(n()) %>% 
-  ungroup() %>% 
-  ### Manually Fix names for estimating catch
-  mutate(sf_eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
-                              ifelse(eez_name =="Greenland (Denmark)","Greenland",
-                                     ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
-                                            ifelse(fishing_entity =="Italy","Italy",
-                                                   ifelse(eez_name =="Chile (mainland)","Chile",
-                                                          ifelse(fishing_entity =="Brazil","Brazil",
-                                                                 ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
-                                                                        ifelse(eez_name =="Portugal (mainland)","Portugal",
-                                                                               ifelse(fishing_entity == "Korea (North)","Korea (North)",
-                                                                                      ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
-                                                                                             ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
-                                                                                                    ifelse(eez_name =="Viet Nam","Vietnam",
-                                                                                                           ifelse(eez_name =="US Virgin Isl.","US Virgin Islands",
-                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain",
-                                                                                                                         paste(eez_name)
-                                                                                                                  )
-                                                                                                           )
-                                                                                                    )
-                                                                                             ))))))))))
-  ),	
-  fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
-  )
-  )
-
-# UN Regions dataset
-UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
-  clean_names() %>% 
-  mutate(un_fishing_entity = country_or_area) %>% 
-  group_by(un_fishing_entity,
-           fishing_entity = country_or_area,
-           georegion = region_name,
-           sub_region = sub_region_name) %>% 
-  summarise(n=n()) %>% #merge china's 3 rows
-  select(-n) %>% 
-  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
-  ungroup() %>% 
-  # Change names to match SAU data and for shorter versions
-  mutate(
-    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
-    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
-    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
-    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
-    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
-    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
-    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
-    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
-    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
-    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
-    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
-    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
-    fishing_entity = gsub(" and ", " & ",fishing_entity),
-    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
-    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
-    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
-    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
-    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
-    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
-    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
-  ) %>% 
-  mutate(
-    fishing_entity = ifelse(un_fishing_entity == "Congo","Congo, R. of",
-                            ifelse(un_fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
-    )
-  )
-
-# The path
-path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")
-
-# The File
-fnam_world <- "SAUEEZ_July2015.shp"
-
-# Load it!
-World_sf <- st_read(dsn = path_world,
-                    layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(eez_name = Name)
-
-World_sf_df <- as.tibble(World_sf) %>% 
-  select(sf_eez_name=eez_name,sf_objectid=OBJECTID,sf_eezid=EEZID)
-
-# Vicky
-Clean_sau_eez_fes_new <- Clean_sau_eez_fes %>% 
-  left_join(UN_Regions) %>% 
-  select(-`n()`) %>% 
-  full_join(World_sf_df) %>% 
-  select(1:3,4,8,9,everything())
-
-#  Now check tim sau data
-SAU_Tim_Data %>% 
-  anti_join(Clean_sau_eez_fes_new) %>% 
-  group_by(fishing_entity_id) %>% 
-  summarise(n())
-
-write_csv(Clean_sau_eez_fes_new,
-          "matching_names.csv")
-
 ```

### 2020-08-03 Scripts/Initial_Analysis.Rmd
updated finction of fig 1

@@
 
+  if(Variable_Selected == "value"){
+
     plot_all <- ggdraw() +
@@
     )
+
+  }else{
+    ggsave(
+      plot = Map,
+      width = 17,
+      height = 12,
+      units = "in",
+      filename = Plot_Name
+    )
+  }
 
@@
 
-Entity_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  left_join(Clean_Results_Trans,
-            by = "eez_name") %>% 
-  group_by(fishing_entity) %>% 
-  summarise(Size_Entity = sum(Area_km2))
-
 # Regional UN-sub region area
@@
 
+### Duble check for NA's
+# map(Tresholded_T_Data, ~sum(is.na(.))) # No NA's
+
 ```
@@
 
-```{r comparriosn_wtih_teh}
+```{r comparison_with_Teh_2015, eval = T, echo = F}
 
@@
 
-Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
+Based on our assessment (see Methods), 582 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
 
@@
   ) %>% 
-  group_by(taxon_key,fishing_entity,eez_name) %>% 
-  summarise(n()) %>% 
+  # Needed to correct for names
+  select(-fishing_entity) %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "eez_name") %>% 
+  # Remove Countries that share with other countries
   anti_join(Tresholded_T_Data,
-            by = c("taxon_key","fishing_entity")) %>% 
-  left_join(Clean_sau_eez_fes)
+            by = c("taxon_key","fishing_entity")
+  )
+
+### Duble check for NA's
+# map(Discrete, ~sum(is.na(.))) # No NA's
 
@@
 n_discrete <- Tresholded_T_Data %>% 
-  semi_join(Discrete,
-            by = "taxon_key") %>% # those that are not only discrete
+   # Filter species that are also discrete
+  filter(taxon_key %in% Discrete$taxon_key) %>% 
   group_by(taxon_key) %>% 
@@
 
+# Summary results for paper
 Summary_Discrete <- SAU_Sampled_Data %>% 
@@
 
-## double check
+## Double check no double counting
 
@@
 
-# Total species
+# Double check n = total species (938)
 n_discrete_exclusive + n_trans # 938
@@
 
+# Get the area of each eez provided in the shapefile 
 EEZ_Area <- World_sf %>% 
@@
   group_by(eez_id) %>% 
-  summarise(Size_EEZ = sum(Area_km2))
-
-Entity_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  left_join(Clean_Results_Trans,
-            by = "eez_name") %>% 
-  group_by(fishing_entity) %>% 
-  summarise(Size_Entity = sum(Area_km2))
+  summarise(Size_EEZ = sum(Area_km2)) %>% 
+  left_join(Clean_sau_eez_fes)
+
+Entity_Area <- EEZ_Area %>% 
+  group_by(fishing_entity_id, fishing_entity) %>% 
+  summarise(Size_entity = sum(Size_EEZ)
+            )
 
@@
 Transboundary_Spp <- Tresholded_T_Data %>% 
-  group_by(eez_id) %>% 
+  group_by(eez_id,eez_name) %>% 
   summarise(
@@
   left_join(EEZ_Area,
-            by = "eez_id") %>%
+            by = c("eez_id","eez_name")
+            ) %>%
   mutate(
@@
 # Set manual breaks for bins
-Map_Breaks <- c(-1,10,100,1000,2000,12000) 
-# Map_Breaks <- c(-1,20,200,2000,1000,20000)
-
-###
-
-Total_Value_EEZ <- Clean_sau_eez_fes %>% 
-  group_by(fishing_entity_id, fishing_entity) %>% 
-  summarise(n=n()) %>% # Get all of the fishing entity and id
-  select(-n) %>% 
-  left_join(SAU_Global_Data) %>% 
-  group_by(fishing_entity,Variable) %>% 
+Map_Breaks <- c(-1,10,100,1000,5000,12000)
+
+### Data for land polygon
+# Total_Value_Entity <- Clean_sau_eez_fes %>% 
+#   group_by(fishing_entity_id, fishing_entity) %>% 
+#   summarise(n=n()) %>% # Get all of the fishing entity and id
+#   select(-n) %>% 
+#   left_join(SAU_Global_Data) %>% 
+#   group_by(fishing_entity,Variable) %>% 
+#   summarise(Total_Value = sum(Value,na.rm=T))
+
+# Estimate value per fishing entity
+Total_Value_Entity <- SAU_Global_Data %>% 
+  group_by(fishing_entity_id,Variable) %>% 
   summarise(Total_Value = sum(Value,na.rm=T))
 
-Value_Trans_Country <- Clean_sau_eez_fes %>% 
-  group_by(fishing_entity_id, fishing_entity) %>% 
-  summarise(n=n()) %>% # Get all of the fishing entity and id
-  select(-n) %>% 
-  left_join(Tresholded_T_Data,
-            by = c("fishing_entity","fishing_entity_id")
-            ) %>% 
+# Data for map
+
+Value_Trans_Country <- Tresholded_T_Data %>% 
   group_by(fishing_entity_id,
@@
             by = c("fishing_entity_id","taxon_key")) %>% 
-  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
+  group_by(fishing_entity_id,Variable) %>% # Estimate the amount of dollars of each nation 
   summarise(
@@
   left_join(Entity_Area,
-            by = "fishing_entity") %>%
+            by = c("fishing_entity_id")
+            ) %>%
   # Include the weighted method for supplementals
@@
     vars(catch,value),
-    funs(weight= ./(Size_Entity/1000000))
+    funs(weight= ./(Size_entity/1000000))
   ) %>%
@@
   ) %>% 
-  left_join(Total_Value_EEZ,
-            by = c("fishing_entity", "Variable") 
+  left_join(Total_Value_Entity,
+            by = c("fishing_entity_id", "Variable") 
   ) %>% # uncomment for estimating percentage
@@
 
-### Data for continental analysis
+### Data for continental analysis (round bar plots)
 
@@
 ## Sub region leven
-
 Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
@@
   ungroup() %>% 
-  mutate(id = rep(seq(1,17),2)) %>% 
+  mutate(id = rep(seq(1,17),4)) %>% 
   mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))
@@
 
-Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")
+# Douuble check we are not missing EEZs
+# Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")
 
@@
                         ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
                                paste(sub_region))
+                        )
     )#,
@@
                         ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
                                       paste(sub_region))
-    )#,
-    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
+                        )
+    )
   )
@@
 
-# Variable to plot (value or catch)
-Variable_plot <- "catch"
+# Variable to plot (value,  catch, weighted_catch, weighted_value)
+Variable_plot <- "value"
 CreateFigureOne(Variable_plot)

### 2020-08-03 Scripts/Initial_Analysis.Rmd
Double chekcce all statistics

@@
 
+  ### Labels
+
+  # Label info Rev
+label_data_rev <- Subregion_Trans_Value %>% 
+  filter(Variable == "value") %>% 
+  arrange(Value_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,number_of_bar),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
+                               paste(sub_region))
+                        )
+    )#,
+    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
+  )
+
+# Label info Catch
+label_data_catch <- Subregion_Trans_Value %>% 
+  filter(Variable == "catch") %>% 
+  arrange(Value_sum) %>% # soo it looks like a nice snail :)
+  mutate(
+    id = seq(1,number_of_bar),
+    angle = 90 -360 * (id-0.5)/number_of_bar,
+    hjust = ifelse(angle < -90,1,0),
+    angleb = ifelse(angle < -90, (angle +180), angle)
+  ) %>% 
+  mutate(
+    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
+                        ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
+                                      paste(sub_region))
+                        )
+    )
+  )
+
   # Revenue Plot
@@
   }else{
-    ggsave(
-      plot = Map,
-      width = 17,
-      height = 12,
-      units = "in",
-      filename = Plot_Name
+    plot_all <- ggdraw() +
+      # map
+      draw_plot(Map, x = 0, y = 0, width = 1, height = 1) #+
+      # Revenue circular
+      # draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
+      # # Catch circular
+      # draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
+      # # Labeks
+      # draw_plot_label(label = c("A", "B"), 
+      #                 size = 20,
+      #                 x = c(0, 0), 
+      #                 y = c(1, 0.45)
+      # ) +
+      # draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
+      #                 size = 8,
+      #                 x = c(0.330,0.485), 
+      #                 y = c(0.31,0.29)
+      # )
+
+    save_plot(
+      # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
+      Plot_Name,
+      plot_all,
+      base_height = 5,
+      base_width = 8
     )
@@
 Transboundary_Spp <- Tresholded_T_Data %>% 
-  group_by(eez_id,eez_name) %>% 
+  group_by(eez_name) %>% 
   summarise(
@@
   left_join(EEZ_Area, 
-            by = c("eez_id","eez_name")
-            ) %>%
+            by = "eez_name") %>% 
   mutate(
@@
     Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
-    Weight_Bins = cut(Weight_Spp,breaks = 5),
+    # Weight_Bins = cut(Weight_Spp,breaks = 5),
     Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
@@
 # Douuble check we are not missing EEZs
-# Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")
+Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")
 
@@
 number_of_bar <- 17 # Number of regions
-
-# Label info Rev
-label_data_rev <- Subregion_Trans_Value %>% 
-  filter(Variable == "value") %>% 
-  arrange(Value_sum) %>% # soo it looks like a nice snail :)
-  mutate(
-    id = seq(1,number_of_bar),
-    angle = 90 -360 * (id-0.5)/number_of_bar,
-    hjust = ifelse(angle < -90,1,0),
-    angleb = ifelse(angle < -90, (angle +180), angle)
-  ) %>% 
-  mutate(
-    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
-                        ifelse(sub_region =="Northern America","Northern\nAmerica",
-                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
-                               paste(sub_region))
-                        )
-    )#,
-    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
-  )
-
-# Label info Catch
-label_data_catch <- Subregion_Trans_Value %>% 
-  filter(Variable == "catch") %>% 
-  arrange(Value_sum) %>% # soo it looks like a nice snail :)
-  mutate(
-    id = seq(1,number_of_bar),
-    angle = 90 -360 * (id-0.5)/number_of_bar,
-    hjust = ifelse(angle < -90,1,0),
-    angleb = ifelse(angle < -90, (angle +180), angle)
-  ) %>% 
-  mutate(
-    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
-                        ifelse(sub_region =="Northern America","Northern\nAmerica",
-                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
-                                      paste(sub_region))
-                        )
-    )
-  )
 
@@
 # Variable to plot (value, catch, weighted_catch, weighted_value)
-Variable_plot <- "value"
+Variable_plot <- "catch"
 CreateFigureOne(Variable_plot)
@@
 
+#-----------------#
+# Sub-regional differences
+#-----------------#
+
+Subregion_Data_stats <- Value_Trans_Country %>%
+  left_join(UN_Regions,
+            by = "fishing_entity") %>%
+  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>%
+  select(fishing_entity,sub_region,Variable,Value) %>%
+  filter()
+
 ### Reveneu ANOVA
@@
   tidy() %>% 
-  filter(adj.p.value < 0.05)
+  filter(adj.p.value < 0.05) %>% 
+  View()
 
@@
 ```{r Weight_Revenue, eval =F, echo =F}
-r
+
 Continent_Trans_Value <- Subregion_Trans_raw_Value %>% 
@@
 
-```{r Sub-regional_differences, eval = F}
-
-#-----------------#
-# Sub-regional differences
-#-----------------#
-
-Subregion_Data_stats <- Value_Trans_Country %>%
-  left_join(UN_Regions,
-            by = "fishing_entity") %>%
-  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>%
-  select(fishing_entity,sub_region,Variable,Value) %>%
-  filter()
-
-# Revenue ANOVA
-Subregion_Rev_stats <- Subregion_Data_stats %>%
-  filter(Variable == "value")
-
-Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
-Rev_aov
-summary(Rev_aov)
-
-# Df    Sum Sq Mean Sq F value  Pr(>F)    
-# sub_region   16  75628526 4726783    4.91 4.2e-08 ***
-# Residuals   157 151140183  962676
-
-#### There are significant differences. But between what?
-
-#  Post-hoc analysis
-TukeyHSD(Rev_aov)
-
-# Northern America sig than everyone except for Eastern Asia
-# Eastern Asia sig with everyone except with Eastern Europe and North Am.
-
-```
-
 # RFMO Analysis

### 2020-08-04 Scripts/Initial_Analysis.Rmd
weighted method corrected for bug

@@
 
+# Determine polygon areas
+
+# EEZ Area
+EEZ_Area <- World_sf %>% 
+  as.data.frame() %>% 
+  group_by(eez_id) %>% 
+  summarise(Size_EEZ = sum(Area_km2))
+
+# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
+Entity_Area <- EEZ_Area %>% 
+  left_join(Clean_sau_eez_fes,
+            by = "eez_id") %>% 
+  group_by(fishing_entity,fishing_entity_id) %>% 
+  summarise(Size_Entity = sum(Size_EEZ))
+
 # Regional UN-sub region area
@@
 
-# Get the area of each eez provided in the shapefile 
-EEZ_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  group_by(eez_id) %>% 
-  summarise(Size_EEZ = sum(Area_km2)) %>% 
-  left_join(Clean_sau_eez_fes)
-
-Entity_Area <- EEZ_Area %>% 
-  group_by(fishing_entity_id, fishing_entity) %>% 
-  summarise(Size_entity = sum(Size_EEZ)
-            )
-
 # Data per Territory (EEZ)
 Transboundary_Spp <- Tresholded_T_Data %>% 
-  group_by(eez_name) %>% 
+  left_join(Clean_sau_eez_fes) %>% 
+  group_by(eez_name, eez_id) %>% 
   summarise(
@@
   ) %>% 
-  left_join(EEZ_Area, 
-            by = "eez_name") %>% 
+  ungroup() %>% 
   mutate(
@@
     Bins_Plot = cut(n_trans_spp,breaks = 5,
-                    labels = c('super low', 'low','median', 'high','super high')),
-    # Include the weighted method for supplementals
-    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
-    # Weight_Bins = cut(Weight_Spp,breaks = 5),
-    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                     labels = c('super low', 'low','median', 'high','super high')
@@
 Map_Breaks <- c(-1,10,100,1000,5000,12000)
-
-### Data for land polygon
-# Total_Value_Entity <- Clean_sau_eez_fes %>% 
-#   group_by(fishing_entity_id, fishing_entity) %>% 
-#   summarise(n=n()) %>% # Get all of the fishing entity and id
-#   select(-n) %>% 
-#   left_join(SAU_Global_Data) %>% 
-#   group_by(fishing_entity,Variable) %>% 
-#   summarise(Total_Value = sum(Value,na.rm=T))
 
@@
             by = c("fishing_entity_id","taxon_key")) %>% 
-  group_by(fishing_entity_id,Variable) %>% # Estimate the amount of dollars of each nation 
+  group_by(fishing_entity,fishing_entity_id,Variable) %>% # Estimate the amount of dollars of each nation 
   summarise(
@@
   mutate(
-    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
-                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
+    Trans_Total = ifelse(Variable == "value",Trans_Total, #million /1000000
+                         ifelse(Variable == "catch",Trans_Total, #thousand Trans_Total/1000
                                 Trans_Total)
@@
   left_join(Entity_Area, 
-            by = c("fishing_entity_id")
+            by = c("fishing_entity","fishing_entity_id")
+          # by = "fishing_entity"
   ) %>% 
@@
     vars(catch,value),
-    funs(weight= ./(Size_entity/1000000))
+    funs(weight= ./Size_Entity) # back to USDs
   ) %>% 
   gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
-  # gather("Variable","Value",catch:value) %>%
-  group_by(fishing_entity,Variable,Value) %>% 
   mutate(
@@
             by = c("fishing_entity_id", "Variable") 
-  ) %>% # uncomment for estimating percentage
+  ) %>%
   # Convert catch to million tonnes
@@
                    Value),
-    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
+    Trans_Per = (Value/Total_Value)#*100000000 #Return to percentage
   )
@@
 # Variable to plot (value, catch, weighted_catch, weighted_value)
-Variable_plot <- "catch"
+Variable_plot <- "value"
 CreateFigureOne(Variable_plot)
@@
 
-Continent_Trans_Value <- Subregion_Trans_raw_Value %>% 
-  left_join(Regional_Area,
-            by = "sub_region") %>% 
+Weighted_values <-c("value_weight","catch_weight")
+
+Weighted_Data <- Subregion_Trans_Value %>% 
   mutate(
-    Value_sum= Value_sum*1000000,
-    weighted_value = Value_sum/Size_Region
-    )
-
-Weighted_values <-c("value_weight","catch_weight")
-
-# data
-Weighted_Data <- Subregion_Trans_Value %>% 
-  filter(Variable %in% Weighted_values)
+    Value_sum = ifelse(Variable == "value_weight", Value_sum/1000, Value_sum),
+    Value_m = ifelse(Variable == "value_weight", Value_m/1000, Value_m),
+    Value_sd = ifelse(Variable == "value_weight", Value_sd/1000, Value_sd)
+    ) # Thousand) # Thousand) # Thousand
 
 # Labels
-
-label_data_rev <- Subregion_Trans_Value %>% 
+label_data_rev <- Weighted_Data %>% 
   filter(Variable == Weighted_values[1]) %>% 
@@
                         ifelse(sub_region =="Northern America","Northern\nAmerica",
+                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
                                paste(sub_region)
@@
   )
-
+  )
 # Label info Catch
-label_data_catch <- Subregion_Trans_Value %>% 
+label_data_catch <- Weighted_Data %>% 
   filter(Variable == Weighted_values[2]) %>% 
@@
                         ifelse(sub_region =="Northern America","Northern\nAmerica",
-                               paste(sub_region))
-    )
-  )
-
+                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
+                               paste(sub_region)
+                               )
+    )
+  )
+  )
 # Revenue Plot
-
   # Set plot limits
 
-  max_Rev_lim <- Subregion_Trans_Value %>%
+  max_Rev_lim <- Weighted_Data %>%
     filter(Variable == Weighted_values[1]) %>%
@@
 
-  Subregion_Rev_Data <- Subregion_Trans_Value %>% 
-    filter(Variable == Weighted_values[1])
+  Subregion_Rev_Data <- Weighted_Data %>% 
+    filter(Variable == Weighted_values[1]) %>% 
+    arrange(Value_sum)
 
@@
   ) +    
-    ylim(-50, 250) +
+    ylim(-5, 30) +
     geom_bar(stat="identity") +
@@
       panel.grid = element_blank(),
-      plot.margin = margin(1,0,0,-3,"cm")
+      plot.margin = margin(2,0,0,-3,"cm")
     )  +
@@
             aes(x=id,
-                  y=Value_sum+1,
+                # y=ifelse(sub_region=="N. Europe",250,Value_sum+1), # Fix names overlap
+                y = Value_sum,
                 label=sub_region,
@@
                          colours = pal,
-                         limits = c(0,250),
-                         breaks = seq(0,250,50)
+                         limits = c(0,30),
+                         breaks = seq(0,30,5)
                          );Rev_Plot
@@
 
-  max_Catch_lim <- Subregion_Trans_Value %>% 
+  max_Catch_lim <- Weighted_Data %>% 
     filter(Variable == Weighted_values[2]) %>% 
@@
 
-  Subregion_Catch_Data <- Subregion_Trans_Value %>% 
+  Subregion_Catch_Data <- Weighted_Data %>% 
     filter(Variable == Weighted_values[2])
@@
 ) +    
-  ylim(-50, 251) +
+  ylim(-3.5,20) +
   geom_bar(stat="identity") +
@@
             aes(x=id,
-                y=ifelse(sub_region=="N. Europe",250,Value_sum+1), # Fix names overlap
+                # y=ifelse(sub_region=="N. Europe",250,Value_sum+1), # Fix names overlap
+                y = Value_sum,
                 label=sub_region,
@@
   scale_fill_gradientn("",
-                       limits = c(0,251),
-                       breaks = seq(0,250,50),
+                       limits = c(0,20),
+                       breaks = seq(0,20,5),
                        colours = pal
@@
 legend_plot <- get_legend(Catch_Plot)
-
 # Re-plot without legend
@@
   theme(legend.position = "")
-
   p<- ggdraw() +
@@
   draw_plot_label(
-    label = c("Revenue (USD) | Catch (Tons)","Million per Km2"),
+    label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
                   size = 6,
-                  x = c(0.3,0.40),
+                  x = c(0.23,0.40),
                   y = c(0.25,0.22)
@@
   save_plot(
-    paste(Figures_Path,"weight_plot.png",sep=""),
+    "weight_plot.png",
     p,

### 2020-08-04 Scripts/Initial_Analysis.Rmd
Fixed matching names nightmare and created weight plots

@@
 # Data <- Results_Trans
-CleanResults <- function(Data){
+CleanResults <- function(Data,names_data){
+
+  clean_names_data <- names_data %>% 
+    select(
+      eez_id,
+      fishing_entity_id,
+      fishing_entity = sau_fishing_entity,
+      eez_name = sf_eez_name
+    )
 
@@
   Auto_Remove_Territories <- Data %>% 
-    filter(!is.na(Territory),
-           !is.na(Neighbour)) %>% 
-    rename(eez_name=Territory) %>% 
-    left_join(Clean_sau_eez_fes,
+    filter(!is.na(territory),
+           territory != "NA",
+           !is.na(neighbour),
+           neighbour != "NA") %>% 
+    rename(eez_name=territory) %>% 
+    left_join(clean_names_data,
               by = "eez_name") %>% 
-    select(TaxonKey,
-           Territory= eez_name,
-           eez_name=Neighbour, 
-           Model_Index,
-           Area_Index,
-           CT_fishing_entity= fishing_entity) %>% 
-    left_join(Clean_sau_eez_fes,
+    select(taxon_key,
+           territory = eez_name,
+           eez_name = neighbour, 
+           model_index,
+           area_index,
+           ct_fishing_entity= fishing_entity) %>% 
+    left_join(clean_names_data,
               by = "eez_name") %>% 
     select(1,2, 
-           Neighbour = eez_name,
-           Model_Index:CT_fishing_entity,
-           NT_fishing_entity= fishing_entity,
+           neighbour = eez_name,
+           model_index:ct_fishing_entity,
+           nt_fishing_entity= fishing_entity,
            everything()) %>% 
     mutate(
-      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
-      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
-      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
-    )
+      ct_fishing_entity = ifelse(is.na(ct_fishing_entity),paste(territory),paste(ct_fishing_entity)),
+      nt_fishing_entity = ifelse(is.na(nt_fishing_entity),paste(neighbour),paste(nt_fishing_entity)),
+      Same_Nation = ifelse(ct_fishing_entity==nt_fishing_entity,"Yes","No")
+    ) %>% 
+    filter(neighbour != "NA")
 
@@
     filter(
-      Territory %in% Islands_to_Remove |
-        Neighbour %in% Islands_to_Remove |
-        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
-        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
-        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
-        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
-        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
-        Territory == "Crete (Greece)" & Neighbour == "Grece" |
-        Neighbour == "Crete (Greece)" & Territory == "Grece" |
-        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
-        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
-        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
-        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
-        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
-        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
-        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
-        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
-        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
-        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
-        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
-        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
-        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
-        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
-        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
-        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
-        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
-        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
-        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
-        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
-        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
-        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
-        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
-        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
-    ) %>%
-    group_by(Territory,Neighbour) %>% 
+      territory %in% Islands_to_Remove |
+        neighbour %in% Islands_to_Remove |
+        territory == "Balearic Island (Spain)" & neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
+        territory == "British Virgin Isl. (UK)" & neighbour == "Anguilla" |
+        neighbour == "British Virgin Isl. (UK)" & territory == "Anguilla" |
+        territory == "Corsica (France)" & neighbour == "France (Mediterranean)" |
+        neighbour == "Corsica (France)" & territory == "France (Mediterranean)" |
+        territory == "Crete (Greece)" & neighbour == "Grece" |
+        neighbour == "Crete (Greece)" & territory == "Grece" |
+        territory == "Cyprus (North)" & neighbour == "Cyprus (South)" |
+        neighbour == "Cyprus (North)" & territory == "Cyprus (South)" |
+        territory == "Channel Isl. (UK)" & neighbour == "United Kingdom" |
+        neighbour == "Channel Isl. (UK)" & territory == "United Kingdom" |
+        territory == "Glorieuse Islands (France)" & neighbour == "Mayotte (France)" |
+        neighbour == "Glorieuse Islands (France)" & territory == "Mayotte (France)" |
+        territory == "Guam (USA)" & neighbour == "Northern Marianas (USA)" |
+        neighbour == "Guam (USA)" & territory == "Northern Marianas (USA)" |
+        territory == "Italy" & neighbour == "Sardinia (Italy)" |
+        neighbour == "Italy" & territory == "Sardinia (Italy)" |
+        territory == "Italy" & neighbour == "Sicily (Italy)" |
+        neighbour == "Italy" & territory == "Sicily (Italy)" |
+        territory == "Japan (Daito Islands)" & neighbour == "Japan (main islands)"|
+        neighbour == "Japan (Daito Islands)" & territory == "Japan (main islands)"|
+        territory == "Japan (Daito Islands)" & neighbour == "Japan (Ogasawara Islands)"|
+        neighbour == "Japan (Daito Islands)" & territory == "Japan (Ogasawara Islands)"|
+        territory == "Norway" & neighbour == "Svalbard Isl. (Norway)" |
+        neighbour == "Norway" & territory == "Svalbard Isl. (Norway)" |
+        territory == "Sicily (Italy)" & neighbour == "Sardinia (Italy)" |
+        neighbour == "Sicily (Italy)" & territory == "Sardinia (Italy)" |
+        territory == "South Africa (Atlantic Coast)" & neighbour == "South Africa (Indian Ocean Coast)" |
+        neighbour == "South Africa (Atlantic Coast)" & territory == "South Africa (Indian Ocean Coast)" |
+        territory == "USA (Alaska, Arctic)" & neighbour == "USA (Alaska, Subarctic)" |
+        neighbour == "USA (Alaska, Arctic)" & territory == "USA (Alaska, Subarctic)"
+    ) %>%
+    group_by(territory,neighbour) %>% 
     summarise(n())
@@
     anti_join(Territories_to_Remove,
-              by = c("Territory","Neighbour")
+              by = c("territory","neighbour")
     ) %>% 
     filter(Same_Nation == "No") %>% 
-    select(-8,-9)
-
-  # Fix coding issues between MAC and Windows
-
-  Clean_Results$Territory <- Clean_Results$Territory %>% 
-    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
-    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
-    gsub("R<e9>union (France)","Réunion",.)
-
-  Clean_Results$Neighbour <- Clean_Results$Neighbour %>% 
-    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
-    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
-    gsub("R<e9>union (France)","Réunion",.)
-
-  Clean_Results$CT_fishing_entity <- Clean_Results$CT_fishing_entity %>% 
-    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
-    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
-    gsub("R<e9>union (France)","Réunion",.)
+    select(taxon_key,
+          eez_name = territory,
+          eez_neighbour = neighbour,
+          model_index,
+          area_index
+          )
 
   return(Clean_Results)
-
 }
@@
 
-## Load Results data
-
-In here we load and cleaned the multiple external data sets required to produce the manuscript figures
-
-```{r Load_Results_Data, eval = F}
-
-Results_Path <- my_path("R")
-
-# Set Jurisdiction to EEZ or RFMO
-Jurisdiction <- "EEZ"
-# Jurisdiction <- "RFMO"
-
-# Updates result's path for the jurisdiction
-Results_Path <- paste(my_path("R"),Jurisdiction,"/",sep="")
-
-# Species list to get species names
-Exploited_Species <- fread(paste(my_path("D"),"Distribution/Species/exploited_species_list.csv",sep="")) %>% 
-  clean_names()
-
-Species_Sampled <- fread(paste(my_path("D"),"Distribution/Sampled_Species.csv", sep =""))
-
-Spp_Clasification <- fread(paste(my_path("D"),"Distribution/Species/SppTaxonName.csv",sep="")) %>% 
-  clean_names()
-
-# New dara produced by Vicky 
+### Standarization of names
+
+```{standarize_names, eval = F, echo = F}
+
+### --------------------- ###
+# Sea Around Us eez to fishing entity
 Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)
-
-# UN Regions dataset
+### --------------------- ###
+
+### --------------------- ###
+# UNited Nations Dataset
+### --------------------- ###
 UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
@@
     georegion = region_name,
-    sub_region = sub_region_name) %>% 
+    sub_region = sub_region_name,
+    country_or_area) %>% 
   summarise(n=n()) %>% #merge china's 3 rows
@@
 
-# Load Land shapefile
+### --------------------- ###
+# Natural Earth Shapefile
+### --------------------- ###
+
 World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
@@
     fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
-  )
-
-# Load SAU shapefile name and paths
-
-# The path
+  ) %>% 
+  as.data.frame() %>% 
+  select(-geometry)
+
+### --------------------- ###
+# SAU Shapefile
+### --------------------- ###
 path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")
@@
     eez_id = ifelse(eez_name == "Russia (Laptev to Chukchi Sea)",913,eez_id)
+  ) %>% 
+  clean_names()
+
+World_df <- as.data.frame(World_sf) %>% 
+  select(objectid, eez_id,eez_name)
+
+World_sf %>% anti_join(Clean_sau_eez_fes, by = "eez_id")
+
+# Join all tables with matching names
+
+matching_names <- Clean_sau_eez_fes %>% 
+  full_join(World_df,
+            by = "eez_id") %>% 
+  full_join(UN_Regions,
+            by = "fishing_entity") %>% 
+  full_join(World_land_sf,
+            by = "fishing_entity") %>% 
+  filter(!is.na(fishing_entity_id)) %>% # Remove duplicaates from UN_regions
+  rename(sau_eez_name = eez_name.x,
+         sau_fishing_entity = fishing_entity,
+         sf_eez_name = eez_name.y,
+         sf_object_id = objectid,
+         un_country = country_or_area,
+         un_geo_region = georegion,
+         un_sub_region = sub_region
+  ) %>% 
+  select(
+    eez_id,
+    fishing_entity_id,
+    sau_eez_name,
+    sau_fishing_entity,
+    sf_eez_name,
+    sf_object_id,
+    un_country,
+    un_geo_region,
+    un_sub_region,
+    iso_a3
+  )
+
+# Save data for future
+write_csv(matching_names,
+          "matching_names.csv")
+
+````
+## Load Results data
+
+In here we load and cleaned the multiple external data sets required to produce the manuscript figures
+
+```{r Load_Results_Data, eval = F}
+
+# ----------------- #
+# Misc.
+# ----------------- #
+
+Results_Path <- my_path("R")
+
+# Set Jurisdiction to EEZ or RFMO
+Jurisdiction <- "EEZ"
+# Jurisdiction <- "RFMO"
+
+# Updates result's path for the jurisdiction
+Results_Path <- paste(my_path("R"),Jurisdiction,"/",sep="")
+
+# Dataset to match all SAU names
+matching_names <- my_path("G"),"Spatial/SAU", "matching_names.csv", read = T)
+
+# Species list to get species names
+Exploited_Species <- fread(paste(my_path("D"),"Distribution/Species/exploited_species_list.csv",sep="")) %>%
+  clean_names()
+
+Species_Sampled <- fread(paste(my_path("D"),"Distribution/Sampled_Species.csv", sep =""))
+
+Spp_Clasification <- fread(paste(my_path("D"),"Distribution/Species/SppTaxonName.csv",sep="")) %>% 
+  clean_names()
+
+# ----------------- #
+# Data #
+# ----------------- #
+
+# Load Transbonudary results
+Raw_Results_Trans <- my_path("R","EEZ","Raw_Results_Trans.xlsx", read = T)
+Clean_Results_Trans <- Raw_Results_Trans %>% 
+  CleanResults(.,clean_names) %>% 
+  rename(sf_eez_name = eez_name) %>% 
+  left_join(matching_names,
+            by = "sf_eez_name") %>% 
+  rename(eez_name = sf_eez_name,
+         fishing_entity = sau_fishing_entity)
+
+# New data produced by Vicky to compare with Teh and Sumaila
+Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)
+
+# UN Regions dataset
+UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
+  clean_names() %>% 
+  group_by(
+    un_country = country_or_area,
+    georegion = region_name,
+    sub_region = sub_region_name) %>% 
+  summarise(n=n()) %>% 
+  left_join(matching_names) %>% 
+  ungroup() %>% 
+  distinct(un_country,.keep_all = TRUE) %>% 
+  select(fishing_entity = sau_fishing_entity,georegion,sub_region)
+
+# Load Land shapefile
+World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
+  st_transform(crs = "+proj=eck4") %>%
+  # st_transform(crs = 4326) %>% # 4326
+  left_join(matchig_names,
+            by = "iso_a3") %>% 
+  distinct(iso_a3,.keep_all = TRUE) %>% 
+  rename(fishing_entity = sau_fishing_entity)
+
+# Load SAU shapefile name and paths
+
+# The path
+path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")
+
+# The File
+fnam_world <- "SAUEEZ_July2015.shp"
+
+# Load it!
+World_sf <- st_read(dsn = path_world,
+                    layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(eez_name = Name,
+         eez_id = EEZID) %>% 
+  st_transform(crs = "+proj=eck4") %>% 
+  mutate(
+    eez_id = ifelse(eez_name == "Russia (Laptev to Chukchi Sea)",913,eez_id)
   )
@@
 Entity_Area <- EEZ_Area %>% 
-  left_join(Clean_sau_eez_fes,
+  left_join(matchig_names,
             by = "eez_id") %>% 
-  group_by(fishing_entity,fishing_entity_id) %>% 
+  group_by(fishing_entity = sau_fishing_entity,fishing_entity_id) %>% 
   summarise(Size_Entity = sum(Size_EEZ))
@@
   clean_names() %>% 
-  rename(eez_name=territory) %>% 
-  mutate(
-    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
-    eez_name = gsub("Chile","Chile (mainland)",eez_name),
-    eez_name = gsub("Curaçao","Curacao",eez_name),
-    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
-    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
-    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
-    eez_name = gsub("Vietnam","Viet Nam",eez_name),
-    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
-                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
-                             ifelse(eez_name == "Greece","Greece (without Crete)",
-                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
-                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
-                                                  ifelse(eez_name == "Italy","Italy (mainland)",
-                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
-                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
-                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
-                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
-                                                                                     ifelse(eez_name =="Spain (Mediterranean and Gulf of Cadiz)","Spain (mainland, Med and Gulf of Cadiz)",
-                                                                                            ifelse(eez_name =="Réunion (France)","Reunion (France)",
-                                                                                                   eez_name)
-                                                                                     )
-                                                                              )
-                                                                       )
-                                                                )
-                                                         )
-                                                  )
-                                           )
-                                    )
-                             )
-                      )
-    )
-  )
-
-# Load Transboundary Results
-
-Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
-  mutate(
-    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
-    eez_name = gsub("Chile","Chile (mainland)",eez_name),
-    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
-    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
-    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
-    eez_name = gsub("Vietnam","Viet Nam",eez_name),
-    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
-                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
-                             ifelse(eez_name == "Greece","Greece (without Crete)",
-                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
-                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
-                                                  ifelse(eez_name == "Italy","Italy (mainland)",
-                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
-                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
-                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
-                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
-                                                                                     eez_name)
-                                                                       )
-                                                                )
-                                                         )
-                                                  )
-                                           )
-                                    )
-                             )
-                      )
-    )
-    )
-
+  rename(sf_eez_name=territory) %>% 
+  left_join(clean_names) %>% 
+  rename(eez_name = sau_eez_name)
 ```
@@
     model_index >= MI
-  ) %>% 
-  select(-fishing_entity) %>% 
-  left_join(Clean_sau_eez_fes, by = "eez_name")
+  )
 
@@
 # Number of coastal territories
-length(unique(sau_eez_fes$fishing_entity))
+length(unique(Clean_sau_eez_fes$fishing_entity))
 
@@
   # Needed to correct for names
-  select(-fishing_entity) %>% 
-  left_join(Clean_sau_eez_fes,
-            by = "eez_name") %>% 
+  # select(-fishing_entity) %>% 
+  # left_join(Clean_sau_eez_fes,
+            # by = "eez_name") %>% 
   # Remove Countries that share with other countries
@@
   mutate(
-    Trans_Total = ifelse(Variable == "value",Trans_Total, #million /1000000
-                         ifelse(Variable == "catch",Trans_Total, #thousand Trans_Total/1000
+    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million /1000000
+                         ifelse(Variable == "catch",Trans_Total/1000, #thousand Trans_Total/1000
                                 Trans_Total)
@@
                    Value),
-    Trans_Per = (Value/Total_Value)#*100000000 #Return to percentage
+    Trans_Per = (Value/Total_Value*100000000)#*100000000 #Return to percentage
   )
@@
   mutate(
-    Value_sum = ifelse(Variable == "value_weight", Value_sum/1000, Value_sum),
-    Value_m = ifelse(Variable == "value_weight", Value_m/1000, Value_m),
-    Value_sd = ifelse(Variable == "value_weight", Value_sd/1000, Value_sd)
-    ) # Thousand) # Thousand) # Thousand
+    Value_sum = ifelse(Variable == "value_weight", Value_sum*1000, Value_sum),
+    Value_m = ifelse(Variable == "value_weight", Value_m*1000, Value_m),
+    Value_sd = ifelse(Variable == "value_weight", Value_sd*1000, Value_sd),
+    Value_sum = ifelse(Variable == "catch_weight", Value_sum*1000, Value_sum),
+    Value_m = ifelse(Variable == "catch_weight", Value_m*1000, Value_m),
+    Value_sd = ifelse(Variable == "catch_weight", Value_sd*1000, Value_sd)
+    )
 
@@
     # Looking good
-    theme_minimal() +
+    theme_minimal(base_size = 9) +
     theme(
-      legend.position = "",
+      legend.key.width =unit(1,"line"),
+      legend.key.height =unit(0.9,"line"),
+      legend.position = c(0.86,0.55),
       axis.text = element_blank(),
@@
       panel.grid = element_blank(),
-      plot.margin = margin(2,0,0,-3,"cm")
+      plot.margin = margin(1,0,0,-2.5,"cm") # top,x,x,left
+      # plot.margin = margin(0,-10,-6,-10,"cm")
     )  +
@@
                          limits = c(0,30),
-                         breaks = seq(0,30,5)
-                         );Rev_Plot
+                         breaks = seq(0,30,6)
+                         ) + # puts legend text on the left
+    guides(fill = guide_colorbar(label.position = "left"));Rev_Plot
 
@@
 ) +    
-  ylim(-3.5,20) +
+  ylim(-3.4,20) +
   geom_bar(stat="identity") +
@@
     alpha = 0.5) +
-  theme_minimal() +
+  theme_minimal(base_size = 9) +
   theme(
-    legend.position = "bottom",
-    legend.key.width =unit(2,"line"),
-    legend.key.height =unit(0.5,"line"),
+    # legend.position = "bottom",
+    legend.position = c(0.595,4.52), #0.55
+    legend.key.width =unit(1,"line"),
+    legend.key.height =unit(0.9,"line"),
     axis.text = element_blank(),
     axis.title = element_blank(),
+    axis.text.x = element_text(size = 10),
     panel.grid = element_blank(),
-    plot.margin = margin(1,0,0,0,"cm")
+    plot.margin = margin(1,0,0,0.8,"cm")
   )  +
@@
                        limits = c(0,20),
-                       breaks = seq(0,20,5),
+                       breaks = seq(0,20,4),
                        colours = pal
@@
   # Legend
-  draw_plot(legend_plot, x = 0.2, y = 0.1, width = 0.59, height = 0.1) +
+  draw_plot(legend_plot, x = 0.2, y = 0.05, width = 0.59, height = 0.1) +
   # Labeks
@@
                   size = 15,
-                  x = c(0.1, 0.6),
+                  x = c(0.1, 0.55),
                   y = c(1, 1)
   ) +
+  # draw_plot_label(
+  #   label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
+  #                 size = 6,
+  #                 x = c(0.27,0.49),
+  #                 y = c(0.66,0.63)
+  # )
     draw_plot_label(
-    label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
+    label = c("Revenue     |     Catch",
+              "(Thousand)  |     (Tons)",
+              "(Per Km2)"),
                   size = 6,
-                  x = c(0.23,0.40),
-                  y = c(0.25,0.22)
+                  x = c(0.41,
+                        0.40,
+                        0.48),
+                  y = c(0.675,
+                        0.65,
+                        0.625)
   )
@@
     p,
-    base_height = 4,
-    base_width = 6
+    base_height = 4.2,
+    base_width = 7
   )
@@
 # Old code
+
+```{r}
+
+# Load Land shapefile
+# World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>%
+#   st_transform(crs = "+proj=eck4") %>%
+#   # st_transform(crs = 4326) %>% # 4326
+#   rename(fishing_entity = name_long) %>%
+#   mutate(
+#     fishing_entity = gsub(" and ", " & ",fishing_entity),
+#     fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
+#     fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
+#     fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
+#     fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
+#     fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
+#     fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
+#     fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
+#     fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
+#     fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
+#     fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
+#     fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
+#     fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
+#     fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
+#     fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
+#     fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
+#     fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
+#     fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
+#     fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
+#     fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
+#     fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
+#     fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
+#     fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
+#     fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
+#     fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
+#     fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
+#     fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
+#     fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
+#     fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
+#     fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
+#     fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
+#     fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
+#     fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
+#     fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
+#     fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
+#     fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
+#     fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
+#     fishing_entity = gsub("United States", "USA",fishing_entity),
+#     fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
+#     fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
+#     fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
+#   )
+
+```
+
 ```{r OLD_funEstNeighbours, eval = F, echo=T}

### 2020-08-04 Scripts/Manuscript_Draft.Rmd
updated values

@@
 
-Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
+Based on our assessment (see Methods), 582 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
 For example, our study shows that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile and thus discrete for Ecuador (**spatial threshold between Ecuador and Peru < 10%**) **[@Cashion:2018cg]**.
-The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 7.3 million tons representing USD 12,710 million in fishing revenue **over the same time period**.
+The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 7.5 million tons representing USD 12,941 million in fishing revenue **over the same time period**.
 Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
@@
 
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average yearly** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD).
-The estimated revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05) (Fig.
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average country** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD).
+The estimated **per country** revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05) (Fig.
 1B).

### 2020-08-05 Scripts/Initial_Analysis.Rmd
misc.

@@
     st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
+    left_join(Value_Trans_Country, by ="fishing_entity_id") %>% 
     filter(Variable %in% Variable_Selected)
@@
   Grey_land <- World_land_sf %>%  
-    filter(!fishing_entity %in% World_sf_si_land$fishing_entity)
+    filter(!fishing_entity_id %in% World_sf_si_land$fishing_entity_id)
 
@@
 # Dataset to match all SAU names
-matching_names <- my_path("G"),"Spatial/SAU", "matching_names.csv", read = T)
+matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)
 
@@
 Raw_Results_Trans <- my_path("R","EEZ","Raw_Results_Trans.xlsx", read = T)
+
 Clean_Results_Trans <- Raw_Results_Trans %>% 
-  CleanResults(.,clean_names) %>% 
+  CleanResults(.,matching_names) %>% 
   rename(sf_eez_name = eez_name) %>% 
@@
 # New data produced by Vicky to compare with Teh and Sumaila
-Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)
+# Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)
 
@@
   # st_transform(crs = 4326) %>% # 4326
-  left_join(matchig_names,
+    # rename(sau_fishing_entity = name_long) %>%
+  left_join(matching_names,
             by = "iso_a3") %>% 
@@
 Entity_Area <- EEZ_Area %>% 
-  left_join(matchig_names,
+  left_join(matching_names,
             by = "eez_id") %>% 
@@
 # Regional UN-sub region area
-Regional_Area <- World_sf %>% 
-  as.data.frame() %>% 
-  left_join(Clean_sau_eez_fes) %>% 
+Regional_Area <- Entity_Area %>% 
   left_join(UN_Regions) %>% 
-  filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
-  select(-geometry) %>% 
   group_by(sub_region) %>% 
-  summarise(Size_Region = sum(Area_km2,na.rm=T)) %>% 
-  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
-  arrange(sub_region)
+  summarise(size_region = sum(Size_Entity,na.rm=T))%>% 
+  arrange(size_region)
 
@@
   rename(sf_eez_name=territory) %>% 
-  left_join(clean_names) %>% 
+  left_join(matching_names) %>% 
   rename(eez_name = sau_eez_name)
@@
 length(unique(World_sf$eez_name))
-
 # Number of coastal territories
-length(unique(Clean_sau_eez_fes$fishing_entity))
+length(unique(matching_names$fishing_entity))
 
@@
   ) %>% 
-  # Needed to correct for names
-  # select(-fishing_entity) %>% 
-  # left_join(Clean_sau_eez_fes,
-            # by = "eez_name") %>% 
   # Remove Countries that share with other countries
@@
 Transboundary_Spp <- Tresholded_T_Data %>% 
-  left_join(Clean_sau_eez_fes) %>% 
   group_by(eez_name, eez_id) %>% 

### 2020-08-05 Scripts/Initial_Analysis.Rmd
FIxed images for publication

@@
     st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
-    left_join(Value_Trans_Country, by ="fishing_entity_id") %>% 
+    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
     filter(Variable %in% Variable_Selected)
@@
   Grey_land <- World_land_sf %>%  
-    filter(!fishing_entity_id %in% World_sf_si_land$fishing_entity_id)
+    filter(!fishing_entity %in% World_sf_si_land$fishing_entity)
 
@@
     ),
-    na.translate = F
+    na.translate = F,
+    # labels = comma
     ) +
@@
       # Labeks
-      draw_plot_label(label = c("A", "B"), 
+      draw_plot_label(label = c("a", "b"), 
                       size = 20,
@@
 # Set manual breaks for bins
-Map_Breaks <- c(-1,10,100,1000,5000,12000)
+Map_Breaks <- c(-1,10,100,1,000,5000,12000)
 
@@
   # Labeks
-  draw_plot_label(label = c("A", "B"),
+  draw_plot_label(label = c("a", "b"),
                   size = 15,
@@
 # Just country names
-country_names <- Clean_sau_eez_fes %>% 
-  select(fishing_entity,fishing_entity_id) %>% 
+country_names <- matching_names %>% 
+  select(fishing_entity=sau_fishing_entity,fishing_entity_id) %>% 
   distinct()
@@
   # Labeks
-  draw_plot_label(label = c("A", "B"), 
+  draw_plot_label(label = c("a", "b"), 
                   size = 30,
@@
 # Load Land shapefile
-# World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>%
-#   st_transform(crs = "+proj=eck4") %>%
-#   # st_transform(crs = 4326) %>% # 4326
-#   rename(fishing_entity = name_long) %>%
-#   mutate(
-#     fishing_entity = gsub(" and ", " & ",fishing_entity),
-#     fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
-#     fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
-#     fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
-#     fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
-#     fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
-#     fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
-#     fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
-#     fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
-#     fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
-#     fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
-#     fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
-#     fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
-#     fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
-#     fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
-#     fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
-#     fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
-#     fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
-#     fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
-#     fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
-#     fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
-#     fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
-#     fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
-#     fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
-#     fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
-#     fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
-#     fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
-#     fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
-#     fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
-#     fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
-#     fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
-#     fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
-#     fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
-#     fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
-#     fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
-#     fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
-#     fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
-#     fishing_entity = gsub("United States", "USA",fishing_entity),
-#     fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
-#     fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
-#     fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
-#   )
+World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>%
+  st_transform(crs = "+proj=eck4") %>%
+  # st_transform(crs = 4326) %>% # 4326
+  rename(fishing_entity = name_long) %>%
+  mutate(
+    fishing_entity = gsub(" and ", " & ",fishing_entity),
+    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
+    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
+    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
+    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
+    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
+    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
+    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
+    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
+    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
+    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
+    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
+    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
+    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
+    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
+    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
+    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
+    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
+    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
+    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
+    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
+    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
+    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
+    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
+    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
+    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
+    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
+    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
+    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
+    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
+    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
+    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
+    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
+    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
+    fishing_entity = gsub("United States", "USA",fishing_entity),
+    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
+    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
+    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
+  )
 

### 2020-08-05 Scripts/supplements.Rmd
Created supplements file

---
title: "Supplementary information for Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
author: "Authors: Juliano Palacios-Abrantes, Gabriel Reygondeau, Colette Wabnitz and William W.L. Cheung"
output: pdf_document
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \floatplacement{table}{H}
---

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

library(MyFunctions)

#### Library ####
packages <- c(
  "dplyr", # Data manipulation
  "knitr",
  "kableExtra",
  "png",
  "grid",
  "janitor"
)

my_lib(packages)

```

# Supplementary Figures

```{r Call_Sup_1, eval = T, fig.width=5, fig.height=3, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon."}

img <- readPNG("../Figures/FigS1.png")
grid.raster(img)
```

<!-- ![Figure S1. Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](../Figures/FigS1.png) -->

\clearpage

The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary. Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Supplementary Fig. S2). As expected, using a more relaxed value (e.g. the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4. The current analysis utilized a 25% *Area Index* threshold (Supplementary Fig. S2 - darker histogram).

```{r Call_Sup_4, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis"}

img <- readPNG("../Figures/FigS2.png")
grid.raster(img)
```

<!-- ![Figure S2. Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis](../Figures/FigS2.png) -->

\clearpage

# Supplementary Tables

```{r Call_SupT_1, eval = T, echo = F, fig.pos= "H"}

read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(sub_region) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable("latex",
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations")

```

```{r Call_SupT_2, eval = T, echo = F, fig.pos= "H"}

read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
  kable("latex",
        booktabs = T,
        caption= "Average number of transboundary and discrete species per EEZ for each catch trend")

```

### 2020-08-05 Scripts/Manuscript_Draft.Rmd
updated numbers to reflect re.

@@
 Regions according to the United Nations sub-regions.
-Points = mean +- sd.
+Points = mean $\pm$ sd.
 Revenue in 2010 real USD.](../Figures/Fig1.png)
 
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Fig.
+Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Supplementary Fig.
 S1).
@@
 2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table S1), however, it has the **highest average** revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area between 2005 and 2014, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1), however, it has the second **highest average** revenue (USD 246.7 thousand per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area between 2005 and 2014, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
 
@@
 
-![**Figure 2.** Weighted benefits of transboundary species by Km2 and UN sub-region. A) Million 2010 USD. B) Million tons. Point sub-region average bars +- s.d.](../Figures/Fig2.png)
+![Figure 2.
+Weighted benefits of transboundary species by Km2 and UN sub-region.
+A) Units in thousand 2019 USD.
+B) Units in tons.
+Points are sub-region averages by country $\pm$ s.d.](../Figures/Fig2.png)
 
@@
 Therefore, our intention here is not to infer stock status but to show the catch trend of transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 29.406, *p* < 0.001).
-Specifically, **occasions where a transboundary species is only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Table S2)**.
+Specifically, **occasions where a transboundary species is only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
 Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 53.93, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,382) = 25.58, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.058).
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-**While a species that has less than the selected threshold is not considered transboundary in this paper**, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Fig.
-S3).
+**While a species that has less than the selected threshold is not considered transboundary in this paper**, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Supplementary Fig.
+S2).
 
@@
 We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
-In cases where the ANOVA assumptions were not clearly meet we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
+In cases where the ANOVA assumptions were not clearly met we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
 
@@
 This presents a relative conservative estimate of the number of transboundary species in the world.
-However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Fig.
-S4).
-
-# Data Availability
-The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-All code is available at https://github.com/jepa/FishForVisa
+However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Supplementary Fig.
+S2).
 
@@
 # Additional Information  
-**Competing interests**: No declared.
+**Competing interests**: The author(s) declare no competing interests.
 
-## Supplements
-
-```{r Call_Sup_1, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
-The number of species is represented in the EEZ while the catch (thousand tons) is represented in the land polygon."}
-
-img <- readPNG(here("./Figures/S1_Catch_EEZ.png"))
-grid.raster(img)
-```
-
-![Figure S1.
-Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](../Figures/FigS1.png)
-
-The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Fig.
-S2).
-As expected, using a more relaxed value (e.g.
-the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Fig.
-S2 - darker histogram).
-
-```{r Call_Sup_4, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Histogram of transboundary species using different values of Area Index.
-Darker histogram represents used value (25%) in the analysis"}
-
-img <- readPNG(here("./Figures/S3_Area.png"))
-grid.raster(img)
-```
-
-![Figure S2.
-Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](../Figures/FigS2.png)
+# Data Availability
+The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+The final dataset and code are available at https://github.com/jepa/FishForVisa
 

### 2020-08-05 Scripts/supplements.Rmd
created supplements file

@@
 
-```{r Call_Sup_1, eval = T, fig.width=5, fig.height=3, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+```{r Call_Sup_1, eval = T, fig.width = 9, fig.height = 7, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
 The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon."}
@@
 
-```{r Call_Sup_4, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
+```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
 The darker histogram represents the threshold (25%) used in the present analysis"}
@@
         booktabs = T,
-        caption= "Size of all the EEZs in each sub region determined by the United Nations")
+        caption= "Size of all the EEZs in each sub region determined by the United Nations") %>% 
+  kable_styling(full_width = T)
 
@@
 
-```{r Call_SupT_2, eval = T, echo = F, fig.pos= "H"}
+```{r Call_SupT_2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
 
 read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
+  clean_names() %>% 
+  rename(
+    Category = category,
+    "Mean (s.d.) Transboundary" = mean_shared,
+    "Mean (s.d.) Discrete" = mean_discrete) %>% 
   kable("latex",
         booktabs = T,
-        caption= "Average number of transboundary and discrete species per EEZ for each catch trend")
+        caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
 

### 2020-08-06 Scripts/Manuscript_Draft.Rmd
Incorporated co-authors comments

@@
 ^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
-subtitle: "CORECTIONS ARE IN BOLD. DO NOT UNBOLD"
 # subtitle: "Most neighbor nations share marine exploited species"
@@
 
-Regulatory boundaries and species distributions are often not aligned, especially in the case of marine species crossing multiple Economic Exclusive Zones (EEZs).
-This represents a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits.
-Here, we combined species distributions and the spatial delimitation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the world's identified fished species are transboundary (n = 633) and were responsible for 82% of the global-EEZs catches (48 million tons) and 81% of fisheries revenue (USD 77 billion) in the last decade.
+Regulatory boundaries and species distributions are often not aligned, especially in the case of marine species crossing multiple Exclusive Economic Zones (EEZs).
+This represents a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
+Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
+We found that 67% of the world's identified fished species are transboundary (n = 633).
+Between 2005 and 2014, fisheries targeting these species within the global-EEZs caught in average 48 million tonnes representing an average of USD 77 billion in fishing revenue per year.
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
-Our analysis suggests that fisheries targeting transboundary species appear **more intensively fished** than those mainly catching non-transboundary species.
-Our study has direct implications **for fisheries management** of transboundary species, pointing to the urgent need for strengthened international cooperation in the management of these fisheries.
+Our analysis suggests that catches from transboundary species appear **to be declining** more than those from non-transboundary species.
+Our study has direct implications **for managing** fisheries of transboundary species, highlighting the need for strengthened international cooperation.
 
@@
 
-Distributions of marine species around the world are not constrained by human-made boundaries; rather they are shaped by biotic and abiotic factors defined by their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
-Thus, a species can have a broader distribution (cosmopolitan) or be endemic [@Nelson:2016kk].
-However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The delineation of Economic Exclusive Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 (territorial see) to 200 nautical miles** across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl; @osthagen:2020hd].
-**Shared stocks can be classified in three non-exclusive categories; transboundary, that is stocks that cross the EEZs of two or more coastal states; straddling, that cross neighboring EEZs and the high seas; and highly migratory stocks, that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
-For the purpose of this research we focus on identifying the transboundary nature of marine fished species, that is, those shared by neighboring EEZs, noting that in some cases these might also be present in the high seas (e.g.
-straddling).** Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve stated objectives [@Munro:2002uf; **@Englander:2019dq**].
-For instance, climate-driven changes in species distributions have led to conflict between nations due to changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+Distributions of marine species around the world are not constrained by human-made boundaries; rather they are shaped by biotic and abiotic factors as well as the species' evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
+A species can be widely distributed (cosmopolitan) or endemic [@Nelson:2016kk].
+However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries while such delineation often does not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
+The delineation of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 to 200 nautical miles.** The boundaries of EEZs cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl; @osthagen:2020hd].
+**Shared stocks can be classified as three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that, cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
+Here, our study focuses on the "transboundary" and "straddling" species that are exploited by fisheries operating within EEZs.**
+
+Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].**For instance,** climate-driven changes in species distributions have led to conflicts between nations that were driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
 Moreover, climate change is likely to exacerbate these types of conflict and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and for fisheries management [@Miller:2013iv].
+Therefore, having an accurate understanding of the distribution and scale of transboundary and straddling fish stocks and fisheries is important to inform their sustainable management, particularly under climate change.
 
-Forty years after the formal adoption of UNCLOS **and the consequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species that are shared by neighboring nations is still unclear.
-Early data limitations on species' distributions allowed only for an informed guess of 500 to 1500 transboundary stocks [@Caddy:1997ue] while a more recent study explored the historical contribution of 344 shared taxa following a literature review [@Teh:2015gd].** Thus, no method has included the actual distribution of species in the quantification of transboundary stocks.
-Here, we aimed to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
-Moreover, we categorize species according to their exploitation rate while identifying differences by habitat preference.
-We hypothesize that the methodological constraints of previous work has resulted in an underestimation of the contribution of these species to global catch and revenue, and that the proportion of transboundary species is larger than previously estimated.
+Forty years after the formal adoption of UNCLOS **and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species that are shared by neighboring nations are still unclear.
+With limited biogeographical data, an informed guess suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
+Literature review undertaken by a more recent study included 344 shared taxa and the historical contributions to fisheries [@Teh:2015gd].** However, these previous studies did not include species' biogeography in the quantification of transboundary stocks.
+Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
+Moreover, we categorize species according to their catch trends while identifying the differences between species by habitat preference.
+We hypothesize that the methodological constraints of previous studies has resulted in an underestimation of the number of transboundary stocks and their contribution to global catch and revenue.
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 280 EEZs of 198 coastal **countries (See methods**).
-We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units) due to lack of such biological information for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level **(or even as a group of species) like the case of shrimps (e.g.
-Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt], hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf].** Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis **while still making it relevant from a management perspective**.
+We overlaid the known distribution of 938 commercially valuable marine species that are responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 280 EEZs of 198 coastal **countries (See methods**).
+We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units), due to a lack of such biological information for almost all the species included in this study [@Teh:2015gd].
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level **(or even as groups containing multiple species).
+For example, shrimps (e.g.
+Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] include multiple populations that are exploited by each country’s fisheries but they are managed at the species level in both cases.** Also, recent research has suggested strong connectivity between fish stocks, even when separated by thousands of kilometers [@Ramesh:2019va] through larval dispersal and **adult migration e.g.
+fishing migrating between reefs in neighboring EEZs [Levin:2018in].
+Such ecological connectivity further highlights to the importance of accounting for transboundary stocks using biogeographical information and making the results relevant from a fisheries management perspective**.
 For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting transboundary species within EEZs **caught** an **annual** average of 48.5 million tons, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level, and generating **a yearly average of USD 77,591 million in fishing revenue during the same time period**.
-This is equivalent to 81.3% of the global fishing revenue of the same period.
-These values are more than the 34.2 million tons and USD 40,187 million (**converted to in 2019 USD**) in fishing revenue from shared stocks previously estimated [@Teh:2015gd].
-**Such difference could be due to the utilization of reported catch data by Teh and Sumaila instead of reconstructed data and a time period difference (Teh and Sumaila's study ends in 2006).
-To compare the two studies, we used the FAO global reported data identified at the species level by the *Sea Around Us* and found that in 2006, the 633 transboundary species accounted for 40.7 million tons.
-While this is not necessarily a direct comparison (e.g.
-methodology differences might still exist), it suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated due to an incomplete knowledge on the transboundary nature of marine fished species**
+**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting these transboundary species within EEZs **caught** an **annual** average of 48.5 million tonnes, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level.
+These catches generated **a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) during the same time period.** These values are more than the previously estimated 34.2 million tonnes in catches and USD 40,187 million (**in 2019 value**) in fishing revenue from shared stocks [@Teh:2015gd].**When we re-estimated the transboundary species’ catches using catch data that are consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species we identified here accounted for 40.4 million tonnes of catches i.e., 18% higher than previously estimates.
+Our results suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated due to an incomplete knowledge on the transboundary nature of marine fished species.** The 305 species that are considered non-transboundary (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) contributed a much smaller proportion of catches and revenues compared to those from the 633 transboundary species identified in this study.
+These discrete species represented only **an annual average of** 2.8 million tonnes and 4,282 million USD between 2005 and 2014.
+These results underscore the importance of transboundary species at the global level.
 
-Based on our assessment (see Methods), 582 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).
-For example, our study shows that Peruvian anchoveta (*Engraulis ringens*) is fished by Peru, Chile, and Ecuador but only transboundary between Peru and Chile and thus discrete for Ecuador (**spatial threshold between Ecuador and Peru < 10%**) **[@Cashion:2018cg]**.
-The **annual average contribution of discrete species (in our previous example would be only considering Ecuador's anchoveta catch) between 2005 and 2014** was 7.5 million tons representing USD 12,941 million in fishing revenue **over the same time period**.
-Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary **according to our methods of determination (See methods)**.
-These species represented only **an annual average of** 2.8 million tons and 4,282 million USD between 2005 and 2014.
-These results underscore the importance of transboundary species at the global level.
+In many cases, according to our categorization criteria, a transboundary species can distribute in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans over the EEZs of Peru, Chile, and Ecuador.
+However, our study only counted the transboundary stocks in Peru and Chile [@Cashion:2018cg].
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range **(spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3)** and thus do not meet our criteria to be considered as transboundary stock.
+Situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the 633 transboundary species identified in this study.
+Overall, 590 of the 633 transboundary species have stocks in EEZs that are excluded from being counted as transboundary because they do not meet all our categorization criteria.
+The **annual average contribution from all the excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014** was 10.8 million tonnes, representing USD 19,243 million in fishing revenue **over the same time period.**
 
@@
 1B).
-China (USD 7,284 million) in **Eastern** Asia and the USA **in Northern America** (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species in the last decade.
-These five nations are responsible for 41% of the global fisheries revenue from transboundary species.
+China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues in **Eastern** Asia and **Northern America**, respectively.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014.
+These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
 
@@
 B) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions according to the United Nations sub-regions.
-Points = mean $\pm$ sd.
-Revenue in 2010 real USD.](../Figures/Fig1.png)
+Regions according to the United Nations sub-regions: Northern America (N.
+America), Southern America (S.
+America), Latin America and the Caribbean (Ltn.
+Ame.
+& the Car.) Points = mean $\pm$ sd.
+Revenue in 2019 real USD.](../Figures/Fig1.png)
 
-Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Supplementary Fig.
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], caught over 5.8 million tonnes annually by each country on average between 2005 and 2014 (Supplementary Fig.
 S1).
@@
 Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-**Similarly, Russia, Japan and the USA celebrate a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea since 1988 [@NOAA:gX6CtUTk].** Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-Particularly, China the world's top fish producer**,** [@FAO:2018KK] **gets** one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons).
-Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Fig.
+**Similarly, Russia, Japan and the USA have made a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea since 1988 [@NOAA:gX6CtUTk].** Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+Particularly, China the world's top fish producer [@FAO:2018KK] **gets** one third (5.1 million tonnes) of the total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
+Differences in transboundary fisheries can also be illustrated in terms of catch-revenue over the area of the EEZ $km^2$ (Fig.
 2).
-As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1), however, it has the second **highest average** revenue (USD 246.7 thousand per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area between 2005 and 2014, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).
+As an example, the aggregated area of all EEZs of Northern European countries where transboundary species are present is 3.3 million $Km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+However, it has the second **highest average** revenue (USD 26.1 thousand per $Km^2$) and the **highest average*** catch (19.9 tonnes per $Km^2$) of transboundary species per EEZ area between 2005 and 2014.
+Countries from Western Europe get significantly more revenue from transboundary fisheries per $Km^2$ than from other regions (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05).
 
@@
 ![Figure 2.
-Weighted benefits of transboundary species by Km2 and UN sub-region.
+Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
 A) Units in thousand 2019 USD.
-B) Units in tons.
-Points are sub-region averages by country $\pm$ s.d.](../Figures/Fig2.png)
+B) Units in tonnes.
+Points are sub-region averages $\pm$ s.d.
+by country](../Figures/Fig2.png)
 
-**We determined the exploitation category of each species according to the catch trend within each EEZ (Fig.
+**We determined the catch trend of each species within each EEZ (Fig.
 3).
 While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Therefore, our intention here is not to infer stock status but to show the catch trend of transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** We found significant differences in exploitation categories based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 29.406, *p* < 0.001).
-Specifically, **occasions where a transboundary species is only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
-Significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 53.93, *p* $\leq$ 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) but only Category C for discrete species (one-way ANOVA, *Df*(2,382) = 25.58, *p* < 0.001; $\alpha$ = 0.05; Tukey's post hoc test for Categories C-A and C-B *p* < 0.001, and B-A 0.058).
+Therefore, our intention here is to examine where the catch trends of transboundary species are different from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** Catch trends are classified as increasing (Category A), constant (Category B) or decreasing (Category C).
+We found significant differences within all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001) as opposite to discrete species where no significant differences where registered (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
+We also found significant differences in catch trends when directly comparing transboundary to discrete species (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
+**Overall, transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
 
 ```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, increasing catch; Category B, stable catch; Category C, decreasing catch"}
+Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
 
@@
 
-![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Growing trend; Category B, Stable trend; Category C, Shrinking trend](../Figures/Fig3.png)
+![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend](../Figures/Fig3.png)
 
@@
 For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Mackerel is a transboundary species that **straddles into the high seas** that contributed an average of 598.4 thousand tons to **total** catches (8.18% of total) and USD 986.24 million in **fishing** revenue (7.16% of total) to the countries involved in the dispute between 2005 and 2014.
-The relatively small contribution of mackerel to the involved countries suggests that even a small fraction of the year's catch can lead to important conflicts between neighboring countries.
+Atlantic Mackerel is a transboundary species that **straddles into the high seas**.
+Amongst the countries involved in the 2007 Atlantic mackerel fisheries dispute, mackerel contributed an annual average (between 2005 and 2014) of 598.4 thousand tonnes (8.19%) to these countries’ total catches and USD 850.2 million (7.17%) to their total fishing revenue.
 Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
 Exploring the detailed effects of climate change in the distribution of shared species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
-**For example, understanding how climate change will modify the proportion that each neighboring EEZ has over a sharing species [@PalaciosAbrantes:2020vt], when this change is going to happen, and the economic consequence of such effects can make international treaties more resilient to climate change [@RashidSumaila:tp].**
+**For example, understanding how climate change will modify the proportion of transboundary species that each neighboring EEZ share [@PalaciosAbrantes:2020vt], the time-frame at when the changes in sharing will happen, and the economic consequence of such effects can inform the development of more climate-resilient international treaties [@RashidSumaila:tp]**
 
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystem like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
 Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
@@
 4A).
-**[Colette] This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
-Many of these species are actually highly migratory straddling species (species that go from one EEZ to another while crossing the high seas).
-Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, like the case of Bigeye tuna (Thunnus obesus) (Fig.
+**This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
+Many pelagic-oceanic species are highly migratory and straddle across one EEZ to another while crossing the high seas.
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, like the case of bigeye tuna (Thunnus obesus) (Fig.
 4A).
 Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).**
-
-CW. because they are migratory they fall under the management of RFMOs...
 
@@
 Note that there could be > 5 species due to similar sharing values.
-**Other consist of species that have no classification according to FishBase.**](../Figures/Fig4.png)
+** The category "Other" consists of species that have no classification according to FishBase.**](../Figures/Fig4.png)
 
-**However, this category also includes species that are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
+**Many transboundary species are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
 Belone belone).
+In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
+For example, despite coral reef-related species being among the less shared neighboring EEZs identified in this study (Fig.
+4), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
 Species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm] but the potential boundary-crossing of these species must not be ignored.
-In addition, the world of fisheries is highly connected through larvae dispersal and so, even centralized populations could be supplying populations thousands of kilometers away [@Ramesh:2019va].
-Despite coral reef-related species being among the less shared neighboring EEZs identified in this study (Fig.
-4), coral regions often share multiple species through larvae connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-In some areas like the Caribbean and the Western Indian Ocean, transboundary marine protected areas have been identified as potential tools for achieving fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].** The proper management of coral reef species is very important for many coastal communities, particularly in developing regions, that are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
-For example, all of the top five countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-**4B**) are among the highest fish consumption countries [@FAO:2018KK].
-In these countries, both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
+In some areas like the Caribbean and the Western Indian Ocean, transboundary marine protected areas have been identified as potential tools for achieving fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
+The proper management of coral reef species is very important for many coastal communities, particularly in developing regions, that are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
+For instance some of the top countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
+4B**) are among the highest fish consumption countries [@FAO:2018KK].
+In countries like the Philippines both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
 
@@
 
-Occurrence data was collected by Reygondeau (2019) from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+Occurrence data was collected **by Reygondeau (2019)** from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
@@
 
-The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Boosted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+The ENM-Nereus consists of a multimodel approach based on a Bioclim and a Boosted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
 Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
@@
 It then derives country estimates for missing data and creates time series interpolation.
-Finally the estimated and official data are aggregated for a total reconstructed catch data See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+Finally the estimated and official data are aggregated for a total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.)** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 We selected this time frame to investigate the recent (our time frame includes the **last decade of available data**) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
@@
 We developed a **three**-criteria methodology to determine whether or not a species can be considered transboundary.
-Only species that meet all criteria were considered as transboundary and the analysis was undertaken only within the EEZs of coastal states.
-In some cases, criteria can also be interpreted as indices to measure the uncertainty in the analysis as they provide a continuous index (e.g.
-from 0 to 1) rather than a discrete, yes or no, index.
+Only species that meet all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
+Note that in some cases a species could meet all criteria for some EEZs, but not for other EEZs, these species were still considered as “transboundary”.
 
@@
 Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
-We defined EEZ boundaries using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), **noting that it subdivides EEZs by 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic) including islands territories**, and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
+The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), **noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic) including islands territories**, and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
 When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g.
@@
 We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.
-Alike the catch data, for this study we did not include revenue from areas beyond national jurisdiction.
-We used the US Gross Domestic Product Implicit Price Deflator (average of all 2019 quarters) according to the US Saint Louis Federal Reserve Bank (https://fred.stlouisfed.org/searchresults?st=GDP+Implicit+price+deflator) to transform the original 2010 real USD value to 2019 real USD.**
+We did not include revenue from areas beyond national jurisdiction.
+We used the US Gross Domestic Product Implicit Price Deflator (average of all 2019 quarters) according to the US Saint Louis Federal Reserve Bank (https://fred.stlouisfed.org/searchresults?st=GDP+Implicit+price+deflator) to standardize the original 2010 real USD value to 2019 real USD.**
 
@@
 Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies, **and fishing effort) affect fishing catch volume **[@Pauly:2013gs; @Branch:2008kk].
+temperature, markets, fishing policies, **and fishing effort) affects catches** [@Pauly:2013gs; @Branch:2008kk].
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
@@
 
-Categories <- c("A - Growing Fishery",
-                  "B - Stable Fishery",
-                  "C - Shrinking Fishery",
+Categories <- c("A - Increasing catch trend",
+                  "B - Constant catch trend",
+                  "C - Decreasing catch trend Fishery",
                   "No Status")
@@
 <!-- # Related to Criteria 1 (neighbors) -->
-We have identified four key uncertainties in the method that may affect the estimation of transboundary stocks.
-Firstly, we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
+We have identified four key uncertainties in the method that may affect the estimation of transboundary species Firstly, we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
 While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
@@
 Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
-Thus, a species’ distribution can potentially be reduced or shifted in such way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
+Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
 To account for such climate variability, we derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
@@
 <!-- Related to Criteria 4; Spatial distribution -->
-Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g.
-all datasets agree on presence) and at least 25% of *Area Index* (e.g.
+Finally, the results of this study only considered those species that all datasets agree on presence and at least 25% of *Area Index* (e.g.
 the species shared distribution was at least 25% in each EEZ).
@@
 <!-- Only Bluefin (*Thunnus thynnus*) in the Pacific, Bigeye (*Thunnus obesus*) in the west Pacific, and Yellowfin (*Thunnus albacares*) in the Atlantic still experiencing overfishing  -->
+
+<!-- We found significant differences in catch trends based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).**Transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
+While no significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), significant differences in catch trends for the 305 discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$p = 0.05).
+-->

### 2020-08-06 Scripts/supplements.Rmd
Updated table S2

@@
 
+# read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
+#   clean_names() %>% 
+#   rename(
+#     Category = category,
+#     "Mean (s.d.) Transboundary" = mean_shared,
+#     "Mean (s.d.) Discrete" = mean_discrete) %>% 
+#   kable("latex",
+#         booktabs = T,
+#         caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
+
 read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
   clean_names() %>% 
-  rename(
-    Category = category,
-    "Mean (s.d.) Transboundary" = mean_shared,
-    "Mean (s.d.) Discrete" = mean_discrete) %>% 
+  mutate(
+    "Mean shared" = paste(round(mean_value_x,2)," \u00B1 (",round(sd_value_x,2),")",sep=""),
+    "Mean not-shared" = paste(round(mean_value_y,2)," \u00B1 (",round(sd_value_y,2),")",sep="")
+  ) %>%
+  select(1,8:9) %>%
+  filter(observation != "No Category") %>%
+  rename(Category = observation) %>%
+  arrange(Category) %>% 
   kable("latex",
         booktabs = T,
-        caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
+        caption= "Average \u00B1 (standard deviation) number of shared and non-shared transboundary species per EEZ for each catch trend category")
 

### 2020-08-06 Scripts/Initial_Analysis.Rmd
Updated supplement table S2
Changes to graphs

@@
   if(Variable_Selected == "catch"){
-    Map_Label <- "Catch (Thousand Tons)"
+    Map_Label <- "Catch (Thousand Tonnes)"
     Plot_Name <- "Catch_plot.png"
@@
 
-  Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
-  Labels <- c("(1-10]",paste(Bins[2:5]))
+  # Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
+  Labels_Trans <- c("(1-29]","(29-57]","(57-85]","(85-113]","(113-141]")
+  # Labels <- c("(1-10]",paste(Bins[2:5]))
+  Labels <- c("(1-10]","(10-100]","(100-1000]","(1000-5000]","(5000-12000]")
 
@@
       ) +
-      draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
+      draw_plot_label(label = c("Revenue (USD) | Catch (Tonnes)","(Million)"), 
                       size = 8,
-                      x = c(0.330,0.485), 
+                      x = c(0.325,0.485), 
                       y = c(0.31,0.29)
@@
 
-Discrete_Exclusive %>% 
-  semi_join(Tresholded_T_Data, by = "taxon_key") # 0 ok thes
+# Discrete_Exclusive %>% 
+#   semi_join(Tresholded_T_Data, by = "taxon_key") # 0 ok thes
 
@@
 # Set manual breaks for bins
-Map_Breaks <- c(-1,10,100,1,000,5000,12000)
+Map_Breaks <- c(-1,10,100,1000,5000,12000)
 
@@
 ```{r Weight_Revenue, eval =F, echo =F}
+
+#--------------------------- #
+### Create Suplemental Table S1
+#--------------------------- #
+
+Subregion_Trans_raw_Value %>% 
+  select(sub_region,Size_Entity_sum) %>% 
+  distinct(sub_region,.keep_all = TRUE) %>% 
+  write_csv(.,
+            "Table_S1.csv")
+
+#--------------------------- #
 
@@
 
-#### Supplemental Table 3
-
-# T_Summary %>%
-#   left_join(D_Summary, by = "observation") %>%
-#   mutate(
-#     "Mean Shared" = paste(round(`mean(value).x`,2)," \u00B1 (",round(`sd(value).x`,2),")",sep=""),
-#     "Mean Discrete" = paste(round(`mean(value).y`,2)," \u00B1 (",round(`sd(value).y`,2),")",sep="")
-#     ) %>%
-#   select(1,8:9) %>%
-#   filter(observation != "No Category") %>%
-#   rename(Category = observation) %>%
-#   arrange(Category) %>%
-#   write_csv("Category_summary.csv")
+#### Supplemental Table S2
+
+T_Summary %>%
+  left_join(D_Summary, by = "observation") %>%
+    write_csv("Table_S2.csv")
+
+# -------------------------- #
+# Soley Discrete data
+# -------------------------- #
+
+Exclusive_Discrete_Status_Data <- Discrete_Exclusive %>% 
+  left_join(Status_Data, 
+            by =c("eez_name","taxon_key")
+  ) %>%
+  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
+  group_by(fishing_entity,status) %>% 
+  summarise(value = length(unique(taxon_key))) %>% 
+  left_join(UN_Regions, by ="fishing_entity") %>%
+  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+  # mutate(value = ifelse(value > 100,100,value)) %>% 
+  filter(!is.na(fishing_entity),
+         !str_detect(fishing_entity, ".\\(.") # remove associated territories
+  ) %>% 
+  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
+  arrange(group,value) %>% 
+  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
+         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
+                              ifelse(observation == "Max Exploited","Category B",
+                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+                              )
+         )
+  ) %>% 
+  group_by(individual,observation,group) %>% 
+  summarise(value = sum(value))
 
@@
 
-# Discrete Data
-Discrete_Data_Stats <- Discrete_Status_Data %>% 
+# Discrete Data (trans.not shared)
+Trans_Dis_Data_Stats <- Discrete_Status_Data %>% 
+  filter(observation != "No Category") %>%
+  mutate(value = abs(value))
+
+# Discrete Data (just desrete and not trans.not shared)
+Discrete_Data_Stats <- Exclusive_Discrete_Status_Data %>% 
   filter(observation != "No Category") %>%
@@
   rename(Discrete_value= value) %>% 
-  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value))
+  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value)) %>% 
+  left_join(Trans_Dis_Data_Stats, by = c("individual","observation","group")) %>% 
+  rename(Trans_Discrete_value= value) %>% 
+  mutate(Trans_Discrete_value = ifelse(is.na(Trans_Discrete_value),0,Trans_Discrete_value))
 
@@
 
-mano <- manova(cbind(Discrete_value,Trans_value) ~ observation, data = Manova_Differences)
+mano <- manova(cbind(Discrete_value,Trans_value,Trans_Discrete_value) ~ observation, data = Manova_Differences)
 
@@
 
+# 
+#             Df  Pillai approx F num Df den Df    Pr(>F)    
+# observation   2 0.17329   21.771      4    918 < 2.2e-16 ***
+# Residuals   459                                             
+# ---
+# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+summary.aov(mano)
+
 #-----------------# 
@@
 # Kruskal-Wallis chi-squared = 100.24, df = 45, p-value = 4.358e-06
+
+# New only comparing shared trans to discrete exclusive
+# Kruskal-Wallis chi-squared = 50.723, df = 13, p-value = 2.24e-06
 
@@
 
-TukeyHSD(Stat_discrete_cat_aov)
-# 
-#  diff         lwr       upr     p adj
-# Category B-Category A 3.627759 -0.02854633  7.284065 0.0523425
-# Category C-Category A 9.917391  6.31117452 13.523608 0.0000000
-# Category C-Category B 6.289632  2.79874173  9.780522 0.0000835
-
 #-----------------# 
@@
 kruskalmc(Discrete_Data_Stats$value,Discrete_Data_Stats$observation)
+
+Trans_Dis_Data_Stats
 
@@
       x = name,
-      y = top_catch/1000,
+      y = top_catch/1000, # thusand tons
       fill = group

### 2020-08-07 Scripts/Initial_Analysis.Rmd
All documents submitted to journal for revissions responses

@@
 
+# CPI in 2019/ CPI in 2010 × 2010  value = 2019  value
+
 SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
@@
   # Convert to 2019 real USD
-  mutate(value = 1.16 * value) %>%
+  mutate(values = 1.16 * value) %>%
   # Average 10 years of data
@@
 # Percentage species analyzed from the identified species
-Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.23%
+936/length(unique(SAU_Global_Data$taxon_key))
+
+Total_spp_analyzed <- Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.23%
 
@@
 # Provided by Vicky Lam
-SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep ="")) %>% 
+SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep ="")) %>% 
   filter(#eezid != 0,
@@
                sum,na.rm=T)
+
+SAU_FAO_Data_a <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep =""))
+SAU_FAO_Datab <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep =""))
+
+# FAO data
+total_FAO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
+  filter(eezid != 0) %>% 
+  group_by(fishing_entity_id,taxon_key,eezid) %>% 
+  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
+  group_by() %>% 
+  summarise_at(vars(mean_c),sum)
+
+total_sampled_FO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
+  filter(eezid != 0) %>% 
+  filter(taxon_key %in% Species_Sampled$TaxonKey) %>% 
+  group_by(fishing_entity_id,taxon_key,eezid) %>% 
+  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
+  group_by() %>% 
+  summarise_at(vars(mean_c),sum)
+
+SAU_FAO_Data %>% 
+  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
+  group_by() %>% 
+  summarise(sum(sumcatch))
 
@@
     label = c("Revenue     |     Catch",
-              "(Thousand)  |     (Tons)",
-              "(Per Km2)"),
+              "(Thousand)  |    (Tonnes)",
+              "  (Per km  )"),
                   size = 6,
                   x = c(0.41,
-                        0.40,
+                        0.395,
                         0.48),
@@
                         0.65,
-                        0.625)
+                        0.623)
   )

### 2020-08-07 Scripts/Manuscript_Draft.Rmd
All documents submitted to journal for revissions responses

@@
 Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the world's identified fished species are transboundary (n = 633).
+We found that 67% **of the species analyzed** are transboundary (n = 633).
 Between 2005 and 2014, fisheries targeting these species within the global-EEZs caught in average 48 million tonnes representing an average of USD 77 billion in fishing revenue per year.
@@
 A species can be widely distributed (cosmopolitan) or endemic [@Nelson:2016kk].
-However, fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries while such delineation often does not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The delineation of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 to 200 nautical miles.** The boundaries of EEZs cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl; @osthagen:2020hd].
+Fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries while such delineation often does not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
+The officialization of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].** However, the boundaries of EEZs cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl.
 **Shared stocks can be classified as three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that, cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
@@
 
-Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].**For instance,** climate-driven changes in species distributions have led to conflicts between nations that were driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].
+**For instance,** climate-driven changes in species distributions have led to conflicts between nations that were driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
 Moreover, climate change is likely to exacerbate these types of conflict and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and for fisheries management [@Miller:2013iv].
@@
 For example, shrimps (e.g.
-Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] include multiple populations that are exploited by each country’s fisheries but they are managed at the species level in both cases.** Also, recent research has suggested strong connectivity between fish stocks, even when separated by thousands of kilometers [@Ramesh:2019va] through larval dispersal and **adult migration e.g.
-fishing migrating between reefs in neighboring EEZs [Levin:2018in].
+Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] include multiple populations that are exploited by each country’s fisheries, but they are managed at the species level in both cases.** Also, recent research has suggested strong connectivity between fish stocks, even when separated by thousands of kilometers [@Ramesh:2019va] through larval dispersal and **adult migration e.g.
+fishing migrating between reefs in neighboring EEZs [@Levin:2018in].
 Such ecological connectivity further highlights to the importance of accounting for transboundary stocks using biogeographical information and making the results relevant from a fisheries management perspective**.
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting these transboundary species within EEZs **caught** an **annual** average of 48.5 million tonnes, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level.
+**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting these transboundary species within EEZs **caught** an **annual** average of 48.5 million tonnes, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
+1A).
 These catches generated **a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) during the same time period.** These values are more than the previously estimated 34.2 million tonnes in catches and USD 40,187 million (**in 2019 value**) in fishing revenue from shared stocks [@Teh:2015gd].**When we re-estimated the transboundary species’ catches using catch data that are consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species we identified here accounted for 40.4 million tonnes of catches i.e., 18% higher than previously estimates.
@@
 These results underscore the importance of transboundary species at the global level.
-
-In many cases, according to our categorization criteria, a transboundary species can distribute in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
-For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans over the EEZs of Peru, Chile, and Ecuador.
-However, our study only counted the transboundary stocks in Peru and Chile [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range **(spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3)** and thus do not meet our criteria to be considered as transboundary stock.
-Situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the 633 transboundary species identified in this study.
-Overall, 590 of the 633 transboundary species have stocks in EEZs that are excluded from being counted as transboundary because they do not meet all our categorization criteria.
-The **annual average contribution from all the excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014** was 10.8 million tonnes, representing USD 19,243 million in fishing revenue **over the same time period.**
-
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average country** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD).
-The estimated **per country** revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05) (Fig.
-1B).
-China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues in **Eastern** Asia and **Northern America**, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014.
-These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
 
@@
 B) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions according to the United Nations sub-regions: Northern America (N.
-America), Southern America (S.
-America), Latin America and the Caribbean (Ltn.
+Regions according to the United Nations sub-regions: E.
+= Eastern, N.
+= Northern, S.
+= Southern, W.
+= Western, Ltn.
 Ame.
-& the Car.) Points = mean $\pm$ sd.
+& the Car.
+= Latin America and the Caribbean.
+Points = regional  mean ± sd.
 Revenue in 2019 real USD.](../Figures/Fig1.png)
 
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], caught over 5.8 million tonnes annually by each country on average between 2005 and 2014 (Supplementary Fig.
+In many cases, according to our categorization criteria, a transboundary species can distribute in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans over the EEZs of Peru, Chile, and Ecuador.
+However, our study only counted the transboundary stocks in Peru and Chile [@Cashion:2018cg].
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range **(spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3)** and thus do not meet our criteria to be considered as transboundary stock.
+Situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
+Overall, 590 of the 633 transboundary species have stocks in EEZs that are excluded from being counted as transboundary because they do not meet all our categorization criteria.
+The **annual average contribution from all the excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014** was 10.8 million tonnes, representing USD 19,243 million in fishing revenue **over the same time period.**
+
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average country** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD) (Fig.
+1B).
+The estimated **per country** revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
+China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues from 2005 to 2014  in **Eastern** Asia and **Northern America**, respectively.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
+1A).
+These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
+
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], caught on average between 2005 and 2014 over 5.8 million tonnes by each country on average between 2005 and 2014 (Supplementary Fig.
 S1).
@@
 Particularly, China the world's top fish producer [@FAO:2018KK] **gets** one third (5.1 million tonnes) of the total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
-Differences in transboundary fisheries can also be illustrated in terms of catch-revenue over the area of the EEZ $km^2$ (Fig.
+Differences in transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
 2).
-As an example, the aggregated area of all EEZs of Northern European countries where transboundary species are present is 3.3 million $Km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
-However, it has the second **highest average** revenue (USD 26.1 thousand per $Km^2$) and the **highest average*** catch (19.9 tonnes per $Km^2$) of transboundary species per EEZ area between 2005 and 2014.
-Countries from Western Europe get significantly more revenue from transboundary fisheries per $Km^2$ than from other regions (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05).
+As an example, the aggregated area of all EEZs of Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+However, it has the second **highest average** revenue (USD 26.1 thousand per $km^2$) and the **highest average** catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
+Countries from Western Europe get significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05).
 
@@
 Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
-A) Units in thousand 2019 USD.
-B) Units in tonnes.
+A) Revenue in thousand 2019 USD.
+B) Catch in tonnes.
 Points are sub-region averages $\pm$ s.d.
@@
 
-**We determined the catch trend of each species within each EEZ (Fig.
+**We determined the catch trend of each species within each EEZ classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
 3).
 While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Therefore, our intention here is to examine where the catch trends of transboundary species are different from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).** Catch trends are classified as increasing (Category A), constant (Category B) or decreasing (Category C).
+Therefore, our intention here is to examine where the catch trends of transboundary species are different from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
 We found significant differences within all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001) as opposite to discrete species where no significant differences where registered (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
-We also found significant differences in catch trends when directly comparing transboundary to discrete species (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-**Overall, transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
+We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
+Overall, transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
 
@@
 
-![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend](../Figures/Fig3.png)
+![Figure 3.
+Number of transboundary species by catch trend and EEZ.
+Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend.“No Category” reflect species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.](../Figures/Fig3.png)
 
@@
 Exploring the detailed effects of climate change in the distribution of shared species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
-**For example, understanding how climate change will modify the proportion of transboundary species that each neighboring EEZ share [@PalaciosAbrantes:2020vt], the time-frame at when the changes in sharing will happen, and the economic consequence of such effects can inform the development of more climate-resilient international treaties [@RashidSumaila:tp]**
+**.
+For example, understanding how climate change will modify the proportion of transboundary species that each neighboring EEZ share31, the time-frame at when the changes in sharing will happen, and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@RashidSumaila:tp]**
 
@@
 Showing only species that share > 20 EEZs.
-B) Total catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on A).
+B) Average catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on a).
 Note that there could be > 5 species due to similar sharing values.
@@
 **Many transboundary species are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
-Belone belone).
+Belone belone) (Fig.
+4A).
 In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
 For example, despite coral reef-related species being among the less shared neighboring EEZs identified in this study (Fig.
-4), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+4A), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
 Species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm] but the potential boundary-crossing of these species must not be ignored.
@@
 We used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
-The total number of species analyzed was 938 representing 63.2% of identified species and accounting for 96.52% of the catch identified at the species' level.** To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
+The total number of species analyzed was 938 representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.** To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
 Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result **than using only one data source**.
@@
 The *Sea Around Us* estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
-Catches are also spatially allocated [@Zeller2016].
+Catches are also spatially allocated on a $0.5^{\circ}$ x $0.5^{\circ}$ latitude longitude grid [@Zeller2016].
 **Roughly, the Sea Around Us method takes each country's officially reported catch data (e.g.
@@
 It then derives country estimates for missing data and creates time series interpolation.
-Finally the estimated and official data are aggregated for a total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.)** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+Finally, the estimated and official data are aggregated for a total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.)** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 We selected this time frame to investigate the recent (our time frame includes the **last decade of available data**) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
+Note that in call cases we report the average catch from 2005 to 2014.
 
@@
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
-This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decade of data (2005 - 2014), thus validating the models and only selected "current" shared species.**
+This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decade of data (2005 - 2014), thus validating the models and only selected "current" shared species.
+We acknowledge that this criteria might limit the global distribution of species thus resulting in a conservative estimate of transboundary species.**
 
@@
 We did not include revenue from areas beyond national jurisdiction.
-We used the US Gross Domestic Product Implicit Price Deflator (average of all 2019 quarters) according to the US Saint Louis Federal Reserve Bank (https://fred.stlouisfed.org/searchresults?st=GDP+Implicit+price+deflator) to standardize the original 2010 real USD value to 2019 real USD.**
+We used the monthly average US Consumer Price Index (CPI) according to the U.S.
+Bureau of Labor Statistic (https://www.bls.gov/cpi/) to standardize the original 2010 real USD value to 2019 real USD.**
 
@@
 All code is available at https://github.com/jepa/FishForVisa.
-We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, exploitation categories) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
+We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
 We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
@@
 The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-The final dataset and code are available at https://github.com/jepa/FishForVisa
+The processed results and code are available at https://github.com/jepa/FishForVisa
 

### 2020-08-07 Scripts/supplements.Rmd
All documents submitted to journal for revissions responses

@@
 
-```{r Call_Sup_1, eval = T, fig.width = 9, fig.height = 7, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon."}
+```{r Call_Sup_1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon."}
 

### 2020-08-07 Scripts/Initial_Analysis.Rmd
Cleaned script for reviewers

@@
 
-## Determine Species Status
+## Determine Catch Trends
 
@@
 Cayman Islands for species 6000006 had 5 *Max Exploited* and 5 *Overexploted*) then we report the status at the last year of data.
+
+Categories are:
+
+- Increasing Catch 
+- COnstant Catch
+- Decreasing Catch
 
@@
 # Percentage species analyzed from the identified species
-936/length(unique(SAU_Global_Data$taxon_key))
+936/length(unique(SAU_Global_Data$taxon_key)) # 67.5
 
@@
 # Provided by Vicky Lam
-SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep ="")) %>% 
+SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep ="")) %>% 
   filter(#eezid != 0,
@@
 
-SAU_FAO_Data_a <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep =""))
-SAU_FAO_Datab <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep =""))
-
-# FAO data
-total_FAO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
-  filter(eezid != 0) %>% 
-  group_by(fishing_entity_id,taxon_key,eezid) %>% 
-  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
-  group_by() %>% 
-  summarise_at(vars(mean_c),sum)
-
-total_sampled_FO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
-  filter(eezid != 0) %>% 
-  filter(taxon_key %in% Species_Sampled$TaxonKey) %>% 
-  group_by(fishing_entity_id,taxon_key,eezid) %>% 
-  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
-  group_by() %>% 
-  summarise_at(vars(mean_c),sum)
-
-SAU_FAO_Data %>% 
-  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
-  group_by() %>% 
-  summarise(sum(sumcatch))
-
 ## Get the total of global data
@@
 
-### Discrete Species
+### Non-shared Transboundary
 
@@
 
-### Discrete Exclusive
+### Discrete Species
 
@@
 
-### Data For Map
+### Data For Map (Fig. 1)
 
@@
 
-### EEZ Map of Transboundary Species
+### Map of Transboundary Species
 
@@
 
+````
+
+### Plot weighted bars
+
+```{r, eval = T, echo = F}
   Rev_Plot <- ggplot(
@@
 
-### OHI-inspired Circular plot for Territories
+## OHI-Territories
 
@@
 
-### Mackerel (*Scomber scombrus*) war
+### Mackerel conflict
 
@@
 
-### OHI-inspired Circular plot Species
+### OHI-Species
 
@@
 ```
-
-#Problem solving
-
-### First world Anchovies
-
-In a first run the model suggests anchovies "Engraulis ringens" (600004) is transboundary between US-Mex-Can. I'm exploring this since all four models agree...
-
-Found the problem, Gab's coordinate system, hence the data, are in different system than DBEM and SAU data...
-
-```{r Trans_Spp_Function, eval= F ,echo = T,warning = F,message = F}
-
-### DATA EXTRA NEEDED
-
-# DBEM Coordinate system
-Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
-colnames(Coor) <- c("INDEX","Longitude","Latitude")
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>% 
-  mutate(INDEX = seq(1,259200,1))
-
-# colnames(CoorG) <- c("INDEX","Longitude","Latitude")
-coords <- CoorG[order(CoorG$Latitude, rev(CoorG$Longitude),decreasing=TRUE), ]
-
-# Explore model step by step
-
-# Get Catch Data
-Anchoveta_Dist <- GetSppDist(600004,"All",CoorG)
-
-Anchoveta_Dist_Coor <- Anchoveta_Dist %>% 
-  left_join(CoorG)
-
-# Swap coordinate system to match DBEM and SAU
-Anchoveta_Dist_Coor_Fix <- Anchoveta_Dist_Coor[order(Anchoveta_Dist_Coor$Latitude, rev(Anchoveta_Dist_Coor$Longitude),decreasing=TRUE), ]
-
-x <- Anchoveta_Dist %>% 
-  left_join(EEZ_CellID) %>% 
-  left_join(EEZIDs_List) %>% 
-  filter(
-    # Model == "Occ",
-    Value >0)
-
-# head(x)
-# Exploring using Vicky's data
-
-ggplot(x) +
-  geom_tile(aes(
-    x = Longitude,
-    y = Latitude,
-    fill = Name,
-    color = Name
-  )
-  ) +
-  facet_wrap(~Model)
-
-Spp_Trans <- bind_rows(
-  mclapply(
-    600004, FUN =EstTransIndex, Model = "All", Neighbours = Neighbour_List, Coord = CoorG
-  )
-)
-
-# Estimate total spp distribution within neighbours
-
-Trans_Spp <- SppDist %>%
-  filter(INDEX %in% Neighbours$INDEX) %>% # Filter data only located within EEZs
-  mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
-  group_by(TaxonKey,
-           INDEX
-  ) %>%
-  summarise(Model_Index = mean(Value,na.rm=T)) %>%
-  filter(Model_Index > 0) %>%
-  mutate(Model_Index = Model_Index*100) %>%
-  left_join(Neighbours,
-            by = "INDEX")
-
-Test <- Trans_Spp %>% 
-  filter(Name == "USA (West Coast)" & Model_Index ==100)
-
-# Explore only SAU catch data
-
-# Get Catch Data
-Anchoveta_Dist <- GetSppDist(Spp,"SAU_C")
-
-# Get Mex, Can and USA W coast Grid
-Anchoveta_Dist_EEZ <- Anchoveta_Dist %>%
-
-  Anchoveta_NA <-  Anchoveta_Dist%>% 
-  filter(INDEX %in% North_America$INDEX) %>% 
-  gather("Year","Tonnes",CATCH.1:CATCH.65) %>% 
-  group_by(Year) %>% 
-  summarise(Sum_T = sum(Tonnes, na.rm =T))
-
-```
-
-### Over-counting transboundary stocks
-
-In a first run, Australia results in many transboundary stocks, I believe this is because it is counting the number of countries that that the species share (e.g.
-one species 6 countries = 6 transboundary spp) rather than 1 species 6 countries = 1 trans spp.
-
-**Problem fixed.** Now we can estimate the number of transboundary species as well as the number of countries/regions that each country shares per species.
-
-```{Australia_case, eval =F, echo = F}
-
-Australia <- Results_Data %>% 
-  filter(Name == "Australia")
-
-Original_Australia <-Australia %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
-  ) %>% 
-  group_by(Name,Model_Index) %>% 
-  summarise(n_Trans_Spp = n()) %>% 
-  filter(Model_Index == 100)
-
-## Testing the waters
-
-Explore_Australia <- Australia %>% 
-  filter(Model_Index >= 50#,
-         # Trans_Index >= 0.10
-  ) %>% 
-  slice(1:20) %>% 
-  group_by(Name,Model_Index) %>% 
-  summarise(
-    n_trans = length(unique(TaxonKey)),
-    n_countries = length(unique(Neighbour_Territory)),
-  )
-
-```
-
-### Fixing counts within EEZs
-
-In the first run. Countries where EEZs are divided but touching (e.g. South Africa Indian and Atlantic coasts) are double counted.
-
-This might be fixed with Tyler's data of EEZs to ISOs... He did it manually so it does not work!
-
-```{South_Africa_case, eval =F, echo = F}
-
-# Tyler E.'s' data
-EEZ_ISO <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/EEZID_ISO_TylEd.csv", comment.char="#")
-
-#SAU / Vicky's data
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-# Worlds adata
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/World_EEZ_v10_2018",sep="")
-# #The File
-fnam_world <- "eez_v10.shp"
-# #Load it!
-# 
-World_EEZs <- st_read(dsn = path_world,
-                      layer =file_path_sans_ext(fnam_world))
-
-head(World_EEZs)
-
-World_EEZs %>% 
-  filter(
-    # Territory1 == "South Africa",
-    ISO_Ter1 == "ZAF") %>% 
-  head()
-
-# Get ISO and territory names from world map
-ISO_Ter <- World_EEZs %>%
-  select(ISO_Ter1,Territory1) %>% 
-  as.data.frame() %>% 
-  select(ISO_Ter1,Territory1)
-
-head(ISO_Ter)
-
-# I think EEZID equals ISO when not devided...
-
-EZZID_Yes_ISO <- ISO_Ter %>% 
-  semi_join(ISO_Ter,
-            by ="ISO_Ter1") %>% 
-  rename(Name = Territory1) %>% 
-  # head() %>% 
-  left_join(EEZIDs_List,
-            by = "Name")
-
-EEZ_ISO_Clean <- ISO_Ter %>% 
-  left_join(EEZ_ISO,
-            by = "ISO_Ter1")
-
-SA <- Results_Data %>% 
-  filter(stringr::str_detect(Name,"South Africa"))
-
-## Creating a subset dataset so i can work on my laptop and not remoteley
-
-SubsetData <- Clean_Results %>% 
-  filter(Country_Territory=="USA (East Coast)")
-
-write.csv(SubsetData,
-          "SubsetData.csv",
-          row.names = F) # Using USA East coast and Gulf as example
-
-###_____________________________ ###
-
-# Loading subsetted data
-
-Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/SubsetData.csv")
-
-sau_eez_fes <- read.csv("~/GitHub/FishForVisa/Temporal_Data/sau_eez_fes.csv")
-
-Neighbourd_Territory_T <- Clean_Results %>% 
-  group_by(eez_name=Neighbour_Territory) %>% 
-  summarise() %>%
-  left_join(sau_eez_fes,
-            by = "eez_name") %>% 
-  select(Neighbour_Territory= eez_name,
-         NT_fishing_entity=fishing_entity
-  )
-
-Country_Territory_T <- Clean_Results %>% 
-  group_by(eez_name=Country_Territory) %>% 
-  summarise() %>%
-  left_join(sau_eez_fes,
-            by = "eez_name")  %>% 
-  select(Country_Territory= eez_name,
-         CT_fishing_entity=fishing_entity)
-
-Non_duplicate_Data <- Clean_Results %>%   
-  left_join(Neighbourd_Territory_T,
-            by ="Neighbour_Territory") %>% 
-  left_join(Country_Territory_T,
-            by ="Country_Territory") %>% 
-  mutate(
-    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
-  ) %>% 
-  filter(Same_Nation == "No")
-
-# FIXED!!!!!
-
-```
-
-- **Done debugging**
-
-### Missing stocks
-
-There are places like Peru-Chile or Alaska-Canada that should have trans spp... In Alaska the issue is that Alaska doesn't actually exist as a separate shapefile...
-
-```{r Missing_stocks, eval =F}
-
-Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
-
-Clean_sau_eez_fes <- sau_eez_fes %>% 
-  gather("Type","FishingRegion",2,4) %>% 
-  left_join(sau_eez_fes,
-            by = ("fishing_entity_id")
-  ) %>% 
-  group_by(FishingRegion,fishing_entity) %>% 
-  summarise(n())
-
-# The Alaska paradox
-# It's a problem of the NAs, fixed.
-
-USA_West <- Results_Data %>% 
-  filter(Country_Territory == "USA (West Coast)") %>% 
-  left_join(Exploited_Species,
-            by = "TaxonKey")
-
-# Northern sea Russia
-Russia_map <- World_EEZs %>% 
-  filter(stringr::str_detect(Name,"Russia")) %>% 
-  st_simplify(preserveTopology = TRUE, dTolerance = 100)
-
-head(Russia_map)
-
-ggplot(Russia_map) +
-  geom_sf(aes(fill = Name)) 
-# Shapefiles not matching
-# Russia (Laptev to Chukchi Sea)
-# Russia (Kara Sea)
-
-Russian_Regions <- c("Russia (Laptev to Chukchi Sea)","Russia (Kara Sea)")
-
-Russia_Results <- Results_Data %>% 
-  filter(stringr::str_detect(Country_Territory,"Russia"))
-
-unique(Russia_Results$Country_Territory)
-# Missing Laptev to Chukchi sea
-
-### What about Vicky's data
-#SAU / Vicky's data
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-
-Russia_EEZlist <- EEZIDs_List %>% 
-  filter(stringr::str_detect(Name,"Russia"))
-
-unique(Russia_EEZlist$Name)
-
-### So maybe there are no Neighbours?
-Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/Neighbour_List.csv", sep =""))
-
-Russia_Neighbour <- Neighbour_List %>% 
-  filter(stringr::str_detect(Name,"Russia"))
-
-unique(Russia_Neighbour$Country_Territory)
-
-# OK So Kara Sea has no borders outside Russia, hence white. Now Laptev does have borders but No species... which is weird... Paific Halibut?
-
-# I manually ran the function to see what's going on
-
-# ggplot() +
-#   geom_sf(data = Russia_map, aes(colour = Name)) +
-#   geom_tile(data = subset(SppDist, Value !=0),
-#             aes(
-#     x = Longitude,
-#     y = Latitude,
-#     fill = log10(Value)
-#   ) 
-#   ) +
-#   facet_wrap(~Model)
-
-# The main issue is that there is no catch data there...
-
-```
-
-### Pierrs massive discrete stocks
-
-```{r Pierrs_Discretion, eval = F ,echo = T,warning = F,message = F}
-
-Pierre <-  Clean_Results_Trans %>% 
-  filter(Territory == "Saint Pierre & Miquelon (France)") %>% 
-  left_join(Exploited_Species,
-            by = "TaxonKey")
-
-# Very wrong!
-# using 600051 to see what's the problem with the Area index
-
-# Found the problem, Territory and Neighbour were switched un the last step of the EstTransSpp function
-
-```
-
-### Côte de Ivory missing data
-
-For some reason Côte de ivory is missing data. It was fixed at the beginning when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to zero.
-
-```{Cote_Deivory, eval =F, echo =F}
-
-# It might be a problem in the name côte de'ivory....
-# Nope, both INDEX and neighbours datasets are names alike
-
-# Run getSppDistribution function with this:
-Model="All"
-Coord=CoorG
-
-# Spp <- 600423 #This species should work
-
-# Its a problem with compabillity between Windows and MAC. Fixed by changing the neighbours csv. to excell
-
-# Now Check Vietnam...Curacao and Réunion...
-# In INDEXES "Vietnam" in all others "Viet Nam"
-# Fixed directly on the excell
-
-# The russioan probelmo
-
-# Load neighbours data from previouse routine
-Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.xlsx", sep =""))
-
-EEZCellIUD913 <- EEZ_CellID %>% 
-  filter(EEZID == 913)
-
-R912 <- Neighbours_Data %>% 
-  filter(ID == 912)
-
-R913 <- Neighbours_Data %>% 
-  filter(ID == 913)
-
-anti_join(R912,R913)
-
-Index_Code913 <- Index_Code %>% 
-  filter(EEZID == 913)
-
-Neighbours_Data %>% 
-  filter(INDEX %in% Index_Code913$INDEX)
-
-# SAU relations between INDEX and Country's EEZs
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-# EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-# EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-Index_Code <- EEZIDs_List %>% 
-  left_join(EEZ_CellID) %>% 
-  rename(Territory = Name)
-
-# The path
-path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
-# #The File
-
-fnam_world <- "SAUEEZ_July2015.shp"
-World_sf <- st_read(dsn = path_world,
-                    layer =file_path_sans_ext(fnam_world)) %>% 
-  rename(Territory = Name)
-
-x <- Neighbours_Data %>%
-  select(-Neighbour) %>% 
-  group_by(Territory) %>% 
-  distinct() %>% 
-  anti_join(Index_Code) %>% 
-  group_by(Territory) %>% 
-  summarise(n());x
-
-# World_sf %>% 
-#   filter(Territory %in% x$Territory)
-
-# Fuck it! Re-run Neighbours code...
-
-Russians <- c("Russia (Laptev to Chukchi Sea)", #913
-              "US Virgin Islands") #912
-
-SF_Names <- 850
-
-Russian_Index <- Index_Code %>% 
-  filter(Territory %in% Russians)
-
-unique(Russian_Index$EEZID)
-unique(Russian_Index$Territory)
-
-World_sf %>% 
-  # filter(Territory == "Russia (Laptev to Chukchi Sea)") # EEZid 912
-  # filter(Territory == "Russia (Kara Sea)") # EEZid also 912
-  filter(Territory %in% Russians) %>% 
-  ggplot() +
-  geom_sf(aes(fill = Territory))
-
-unique(Russian_sf$Territory)
-
-# split shapefile by DF
-Russian_id <- World_sf %>% 
-  filter(Territory %in% Russians) %>% 
-  left_join(Russian_Index, by= "Territory") %>%  
-  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
-  filter(EEZID == 913) %>% 
-  st_simplify(preserveTopology = TRUE, dTolerance = 1000)
-
-ggplot(Russian_id) +
-  geom_sf(aes())
-
-# ok!
-
-# split shapefile by DF
-Russia_id_912_913 <- World_sf %>% 
-  filter(Territory %in% Russians) %>% 
-  left_join(Russian_Index, by= "Territory") %>%  
-  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
-  as.data.frame() %>% 
-  ungroup() %>% 
-  select(Territory,INDEX,EEZID)
-
-write.csv(Russia_id_912_913,
-          "Russia_id_912_913.csv",
-          row.names = F)
-
-head(x)
-
-```
-
-### Number of Collapsed USA species
-
-```{r Collapsed_USA, eval = F ,echo = T,warning = F,message = F}
-
-#  At the end, the ram legacy and the SAU are tide in results...
-
-USA_Collapsed <- Species_Status %>% 
-  filter(str_detect(Territory, pattern="USA")#,
-         # Status == "Collapsed"
-  ) %>% 
-  ungroup() %>% 
-  mutate(TaxonKey = as.numeric(TaxonKey)) %>%
-  left_join(Exploited_Species)
-
-# Comparring to RAM legacy in the W pacific coast
-
-# Sabelfish match
-# Pacifc sardine no data ram
-# Chillipepper match
-# Lincod no match althou circular path in RAM
-# Dover no match by far...
-# Chub mackerel... match
-# Petral metch
-# Black Rockfish No mach...ish
-# Widow rockfish no match
-# Starry flounder no match
-# Rex sole no data RAM
-# Pacific ocean percCollapsed Vs Overfished
-#
-
-```
-
-### Fixing Russia Moneeeeey
-
-```{r russia}
-
-# Shapefile names
-Russia_Sf <- World_land_sf %>% 
-  filter(str_detect(fishing_entity,"Russia")) %>% 
-  pull(fishing_entity)
-
-"Russia"
-
-Russia_Trans <- Revenue_Country %>% 
-  filter(str_detect(fishing_entity,"Russia")) %>% 
-  pull(fishing_entity)
-
-"Russian Federation"
-### Laptev and Chukchi are the issue, No Alaska'?
-
-### Wake
-Wake_ssf <- World_sf %>% 
-  filter(str_detect(eez_name,"Wake")) %>% 
-  pull(eez_name)
-
-"Wake Isl. (USA)"
-
-Wake_Trans <- Transboundary_Spp %>% 
-  filter(str_detect(eez_name,"Wake")) %>% 
-  pull(eez_name)
-
-"NA"
-
-Wake_Tresh <- Tresholded_T_Data %>% 
-  filter(str_detect(eez_name,"Wake")) %>% 
-  pull(eez_name)
-
-"NA"
-
-Wake_Raw <- Clean_Results_Trans %>% 
-  filter(str_detect(eez_name,"Wake"))
-
-#### Son todas under 25%.... Por eso
-
-#### Macquarie Island
-Macquarie_Raw <- Clean_Results_Trans %>% 
-  filter(str_detect(eez_name,"Macquarie"))
-
-# Under 25% Bye
-
-### Minomi
-
-Neighbours_Data %>% 
-  filter(str_detect(Territory,"Japan")) %>% 
-  pull(Territory) %>% 
-  unique()
-
-# Not in our shaopefile
-
-```
-
-### UN Data exploration
-
-```{r}
-
-UN_Regions %>% 
-  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
-  group_by(sub_region) %>% 
-  summarise(n_countries = length(unique(fishing_entity))) %>% 
-  arrange(n_countries)
-
-World_sf %>% 
-  as.data.frame() %>% 
-  left_join(Clean_sau_eez_fes) %>% 
-  left_join(UN_Regions) %>% 
-  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
-  group_by(sub_region) %>% 
-  summarise(Size_EEZ = sum(Area_km2)) %>% 
-  arrange(desc(Size_EEZ))
-
-```
-
-# Extra Analysis
-## Extra Analysis; Functions
-
-```{r Trans_Spp_Function_All, eval = F ,echo = T,warning = F,message = F}
-
-# Function to determine whether or not a species is transboundary for each model
-
-# Varibales needed
-# Spp: Species to be analized, data with presence/absence per gridcell
-# Index_EEZ: Reference list of all INDEX that fall within EEZs
-# EEZ_Size: Number of grid-cells that each EEZ has
-# Neighbours: Reference list of neighbouring countries
-
-# Needs getSppDist
-
-#### For testing 
-# Spp <- 600059
-# Model <- "All"
-# Neighbours <- Neighbour_List
-# Coord = CoorG
-# __________________________________
-
-# The function
-EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
-
-  # Get model data from spps
-  SppDist <- GetSppDist(Spp,Model,Coord)
-
-  # Result 1. Number of Countries that share the species
-
-  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
-  Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
-           Model != "SAU_C") %>% # Only using observational and modelled data
-    mutate(Value = ifelse(Value > 0, 1,0)) %>%
-    left_join(EEZ_CellID,
-              by = "INDEX") %>% 
-    left_join(EEZIDs_List,
-              by = "EEZID")
-
-  # MODEL INDEX (TRESHOLDS 1 & 2) #
-  Model_Index_D <- Trans_Spp %>% 
-    group_by(Name,
-             TaxonKey,
-             Model
-    ) %>% 
-    summarise(n_cells_spp = n()) %>% 
-    select(-n_cells_spp)
-
-  #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
-  # The number of species' cells present within each country's EEZ
-
-  #Step 1.  Get EEZ id and Neighbour
-  Neighbours_EEZ <- Neighbours %>% 
-    group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
-    summarise(n=n()) %>% 
-    ungroup() %>% 
-    select(-n)
-
-  # Step 2. Determines the amount of grids present in each country
-  Spp_Grid <- Trans_Spp %>% 
-    group_by(TaxonKey,
-             Model, 
-             EEZID) %>% 
-    summarise(n_spp_eez = length(unique(INDEX))) %>% 
-    left_join(Neighbours_EEZ,
-              by = "EEZID") %>% 
-    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
-           Neighbour_Territory %in% Trans_Spp$Name)
-
-  # Step 3. Sum total grids per Neighbours
-
-  # Split dataframes to merge latter
-  Country_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index, # Un-comment after producing models x datasets
-      TaxonKey,Name=Country_Territory,n_spp_eez
-    )
-
-  Neighbour_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index,
-      TaxonKey,n_spp_eez,Name=Neighbour_Territory, Country_Territory
-    )
-
-  # Merge dataframes to get totals per Neighbourds
-  Area_Index_D <- full_join(Country_Territory_T,
-                            Neighbour_Territory_T, by = c("Name","TaxonKey","Model")) %>%
-    rowwise() %>%
-    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
-    distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbour_Territory = Name,
-           n_spp_Country = n_spp_eez.x,
-           n_spp_Neighbour = n_spp_eez.y) %>% 
-    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
-    select(1:4,6,8)
-
-  #____________ FINAL INDEX TABLE_________ #
-  Indexes <- Model_Index_D %>% 
-    rename(Country_Territory = Name) %>% 
-    full_join(Area_Index_D,
-              by = c("TaxonKey","Country_Territory","Model")
-    ) %>% 
-    filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(Model,TaxonKey,Country_Territory,Neighbour_Territory,everything())
-
-  ### Save spp dataframe
-
-  if(nrow(Indexes) > 0 & Save == "Y"){
-
-    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
-    Save_Path <- paste(Results_Path,"All_Models/",File_Name,sep="")
-
-    write.csv(Indexes,
-              Save_Path,
-              row.names = F)
-
-  }
-
-  if(nrow(Indexes) == 0 & Save == "Y"){
-
-    # Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep=""))
-
-    # Get current Spp that is not transboundary 
-    Current_Spp <- tibble(Non_trans = Spp)
-
-    # Combine new spp with others
-    New_Non <- Non_Transboundary_Data %>% 
-      bind_rows(Current_Spp)
-
-    # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep="")
-    write.csv(New_Non, New_Non_Name, row.names = F)
-
-  }
-
-  ### Function return
-
-  EstTransIndex=Indexes # A dataframe with
-
-}
-
-### Testing Function ####
-# Spp <- 600006
-# Model <- "All"
-# Neighbours <- Neighbour_List
-# 
-# Tryout <- EstTransIndex(Spp,Model,Neighbours,CoorG,Save="N")
-# 
-# Over_20 <-Tryout %>% 
-#     filter(Area_Index > 0.20,
-#            Area_Index < 0.80)
-
-# Spp <- NULL
-# Model <- NULL
-
-```
-
-## Extra Analysis; Results
-
-### Maps for each model/data-set
-```{Tran_country_Map_All, eval =F, echo =F}
-
-World_EEZs_simple <- World_EEZs %>%
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(TenTwenyfive, by ="Name") #%>%
-# filter(!is.na(n_trans)) #%>%
-# st_transform(crs = 3832)
-
-# head(World_EEZs_simple)
-# World_EEZs_simple %>% 
-#   filter(Name == "Chile")
-
-pal <- wes_palette("Zissou1", 100, type = "continuous")
-
-Mod <- unique(TenTwenyfive$Model)
-
-# Loop through all variables
-for(v in 1:length(Mod)){
-
-  Model_List <- Mod[v]
-
-  plot <- ggplot(data = subset(World_EEZs_simple,Model %in% Model_List)) +
-    geom_sf(aes(fill = n_trans)) +
-    scale_fill_gradientn(colours = pal,
-                         na.value = "white") +
-    ggtheme_map() +
-    ggtitle(paste(Model_List))
-
-  # Name plot
-  Plot_Name <- paste(Model_List,"plot.png",sep="_")
-
-  # Save plot
-  ggsave(
-    plot = plot,
-    width = 14,
-    height = 10,
-    units = "in",
-    filename = Plot_Name,
-    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
-  )
-
-}
-
-```
-
-```{r Continent_PNG, eval =F }
-
-names(UN_Regions)
-# Load Land shapefile
-path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
-# #The File
-fnam_world_land <- "ne_50m_admin_0_countries.shp"
-
-World_land_sf <- st_read(dsn = path_world_land,
-                         layer =file_path_sans_ext(fnam_world_land)) %>% 
-  st_transform(crs = 4326)
-
-head(World_land_sf)
-
-Regions <- unique(World_land_sf$REGION_UN)
-# r= 1
-
-for(r in 1:length(Regions)){
-
-  Oceania <- World_land_sf %>%
-    st_transform(crs = 3832)
-
-  Oceania %>% 
-    filter(REGION_UN %in% Regions[5]) %>% 
-    ggplot() +
-    geom_sf(aes(),fill="black",colour = "black") +
-    ggtheme_map() #+
-  # coord_sf(xlim = c(-180, 90), ylim = c(-90, 90), expand = FALSE)
-
-  Plot_Name <-paste(Regions[5],".png",sep="")
-
-  ggsave(Plot_Name,
-         plot = last_plot(),
-         width = 4,
-         height = 4,
-         units = "in",
-         path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Images_Data/"
-  )
-
-}
-
-```
-
-```{r round_map, eval = F, echo = F}
-# #### Round map tryout
-
-# ### EEZ shapefile
-# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
-# 
-# eez = spTransform(eez, CRS("+proj=longlat"))
-# eez = spTransform(eez, CRS("+proj=wintri"))
-# eez = fortify(eez) 
-# 
-# World_sf_si <- World_sf %>%
-#   st_transform(crs = 4326
-#
-
-# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
-# 
-# mapworld<- mapworld %>% 
-#   rename(Territory = id) %>% 
-#   left_join(Data,
-#             by = "Territory") %>% 
-#   left_join(Data_EEZ,
-#             by = "Territory") %>% 
-#   rename(id = Territory)
-# 
-# # head(mapworld)
-# 
-# #create map boundary
-# ll.to.wt <- function (points)
-#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
-#                             CRS("+proj=wintri")))
-#  
-# lseq = seq(-85, 85, by=.25)
-# boundary <- ll.to.wt(data.frame(
-#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
-#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
-#  
-# # New facet label names for dose variable
-# ggplot()+
-#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
-#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
-#   geom_polygon(data = mapworld, 
-#                aes(
-#                  x = long,
-#                  y = lat,
-#                  group = group,
-#                  fill = BinsLan
-#                ),
-#                colour="grey") +
-#   geom_polygon(data = mapworld, 
-#                aes(
-#                  x = long,
-#                  y = lat,
-#                  group = group,
-#                  fill = Bins)
-#                ) +
-#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
-# geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
-# geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
-#                 box.padding = unit(0.5, "lines"),
-#                 point.padding = unit(0.5, "lines"),
-#                 segment.color = 'grey50') +
-# scale_radius(range = c(1, 2)) #+
-# scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
-# theme_map()+
-#   theme(legend.key = element_blank(),
-#         strip.background = element_blank(),
-#         legend.position = "none",
-#         text = element_text(size=12,face="bold"))+
-#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
-# y=tag_facet(q, tag_pool = c("d","e","f"))
-
-```
-
-# Vulnerability Assessment
-
-```{r Vulnerabillity, eval = T, echo = F}
-
-trans_vul <- Tresholded_T_Data %>% 
-  group_by(taxon_key) %>% 
-  summarise(
-    n_countries = length(unique(eez_name))
-  ) %>% 
-  left_join(cc_vul) %>% 
-  left_join(fish_vul) %>% 
-  ggplot() +
-  geom_point(
-    aes(
-      x = fishvul,
-      y = n_countries
-    )
-  )
-
-# climate change vulnerabillity?
-modcc <- lm(n_countries~ccvul, data = trans_vul)
-modcc
-summary(modcc)
-
-# fishing vulnerabillity?
-modfis <- lm(n_countries~fishvul, trans_vul)
-modfis
-summary(modfis)
-
-# Together?
-
-modccfis <- lm(n_countries~fishvul + ccvul, trans_vul)
-modccfis
-summary(modccfis)
-
-## Using a MANOVA to test the significant effect of fishvul and ccvul to catchstatus
-
-# Prepare data
-
-Status_Per_Species <- Tresholded_T_Data %>% 
-  left_join(Status_Data, 
-            by =c("eez_name","taxon_key")
-  ) %>%
-  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
-  group_by(taxon_key,status) %>% 
-  summarise(value = length(unique(fishing_entity))) %>% 
-  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Increasing",
-                             ifelse(status == "Max Exploited","Constant",
-                                    ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Decreasing", "No Category")
-                             )
-  )
-  ) %>% 
-  left_join(cc_vul) %>% 
-  left_join(fish_vul) %>% 
-  filter(status != "No Category",
-         Categories != "No Category")
-
-# Test for assumptions
-# - Data Normally distributed (YES)
-
-qqnorm(Status_Per_Species$ccvul) # yes
-qqnorm(Status_Per_Species$fishvul) # yes
-
-ggplot(Status_Per_Species) +
-  geom_histogram(
-    aes(
-      # x = fishvul # Yes
-      # x = ccvul #yes
-    )
-  ) +
-  facet_wrap(~status)
-
-# -  n for each group > total of dependent variables (YES)
-# - All groups have common variance-covariance – usually fine if sample sizes for each group are the same or very similar. Otherwise, Box’s M can be used to test. (YES, SAMPLE SIZES ARE THE SAME)
-# - Homoscedasticity
-# - There is a moderate linear correlation between the dependent variables (if too weak, or too strong, a series of one-way ANOVAs may be more appropriate) (NO!)
-
-man_vul <- manova(cbind(ccvul,fishvul)~status,data = Status_Per_Species)
-summary(man_vul)
-
-summary.aov(man_vul)
-
-## Since we don't have linear correlation between dependent variables, we test anovas
-
-### fishvul ANOVA
-
-Fishvul_aov <- aov(fishvul~Categories, data = Status_Per_Species)
-summary(Fishvul_aov)
-
-#   Df Sum Sq Mean Sq F value Pr(>F)
-# Categories     2   2698  1349.2   2.286  0.102 # NO SIG
-# Residuals   1392 821450   590.1               
-# 294 observations deleted due to missingness
-
-### ccvul ANOVA (N)
-
-Ccvul_aov <- aov(ccvul~Categories, data = Status_Per_Species)
-summary(Ccvul_aov)
-# Df Sum Sq Mean Sq F value Pr(>F)
-# Categories     2   1798   899.0   2.181  0.113 # NO SIG
-# Residuals   1686 695057   412.3
-
-```
-
-# Old code
-
-```{r}
-
-# Load Land shapefile
-World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>%
-  st_transform(crs = "+proj=eck4") %>%
-  # st_transform(crs = 4326) %>% # 4326
-  rename(fishing_entity = name_long) %>%
-  mutate(
-    fishing_entity = gsub(" and ", " & ",fishing_entity),
-    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
-    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
-    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
-    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
-    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
-    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
-    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
-    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
-    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
-    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
-    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
-    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
-    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
-    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
-    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
-    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
-    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
-    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
-    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
-    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
-    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
-    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
-    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
-    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
-    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
-    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
-    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
-    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
-    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
-    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
-    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
-    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
-    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
-    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
-    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
-    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
-    fishing_entity = gsub("United States", "USA",fishing_entity),
-    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
-    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
-    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
-  )
-
-```
-
-```{r OLD_funEstNeighbours, eval = F, echo=T}
-# Determine which countries are Neighbours
-
-# Method adopted from Adrew Heiss
-# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32
-
-EstNeighbours <- function(Shapefile){
-
-  # Get the list using the poly2nb function
-
-  Neighbour_List <- poly2nb(Shapefile)
-
-  # Convert te nb data to a Matrix of crossing references
-  Neighbour_Matrix <- nb2mat(Neighbour_List,
-                             style="B", 
-                             zero.policy=TRUE)
-
-  # Rename the matrix axis
-  colnames(Neighbour_Matrix) <- rownames(Neighbour_Matrix)
-
-  # Get the names of the countries for identifying them
-  Country_Names <- tibble(id = row.names(Shapefile@data),
-                          Country_Territory = as.character(Shapefile@data$Name),
-                          Neighbour_Territory = Country_Territory,
-                          EEZID = Shapefile@data$EEZID # specific of SAU sf
-  )
-
-  # Clean up and transform the Neighbour matrix
-  Neighbours <- as.data.frame(Neighbour_Matrix) %>%
-    mutate(country = row.names(.)) %>%  # Convert row names to actual column
-    gather(Neighbour, present, -country) %>%  # Convert to long
-    filter(present == 1) %>%  # Only look at cells with a match
-    # Add country names
-    left_join(select(Country_Names,
-                     -Neighbour_Territory), by=c("country" = "id")) %>%
-    left_join(select(Country_Names, 
-                     -Country_Territory), by=c("Neighbour" = "id")) %>% 
-    select(EEZID = EEZID.x,Country_Territory,Neighbour_Territory) # select final column
-
-  # Merge them with SAU data
-
-  DBEM_Neighbours_Data <- EEZIDs_List %>% 
-    left_join(EEZ_CellID, 
-              by = "EEZID") %>% # Asign EEZ id to each country
-    left_join(Neighbours, 
-              by = "EEZID") %>% # Include all Neighbouring countries 
-    filter(Neighbour_Territory != "NA") %>% 
-    left_join(Coor,
-              by = "INDEX") # Inclu
-
-  return(DBEM_Neighbours_Data)
-
-}
-
-### Test function
-
-# Subset data for testing function
-# SAU_Regions <- as.data.frame(unique(World_EEZs$Name))
-
-# Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")
-# Test <- World_EEZs[World_EEZs@data$Name %in% Test_Countries, ]
-
-# Running function
-# getNeighbours(Test)
-
-#### Works beautifully!
-
-```
-
-```{r Trans_Spp_Function, eval= T ,echo = T,warning = F,message = F}
-
-# Function to determine whether or not a species is transboundary
-
-# Varibales needed
-# Spp: Species to be analized, data with presence/absence per gridcell
-# Index_EEZ: Reference list of all INDEX that fall within EEZs
-# EEZ_Size: Number of grid-cells that each EEZ has
-# Neighbours: Reference list of neighbouring countries
-
-# Needs getSppDist
-
-#### For testing 
-# Spp <- 600059
-#Model <- "All"
-#Neighbours <- Neighbour_List
-#Coord = CoorG
-# __________________________________
-
-# The function
-EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){
-
-  # Get model data from spps
-  SppDist <- GetSppDist(Spp,Model,Coord)
-
-  # Result 1. Number of Countries that share the species
-
-  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
-  Trans_Spp <- SppDist %>%
-    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
-           Model != "SAU_C") %>% # Only using observational and modelled data
-    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
-    filter(Value > 0) %>%
-    group_by(TaxonKey,
-             INDEX
-    ) %>%
-    summarise(Model_Index = mean(Value,na.rm=T)
-    ) %>%
-    filter(Model_Index > 0) %>%
-    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
-    left_join(SppDist,
-              by = c("TaxonKey","INDEX")) %>%
-    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
-           Value > 0) %>%
-    mutate(Model_Index = Model_Index*100) %>%
-    select(-Model, -Value, -Latitude,-Longitude) %>%
-    left_join(EEZ_CellID,
-              by = "INDEX") %>% 
-    left_join(EEZIDs_List,
-              by = "EEZID")
-
-  # MODEL INDEX (TRESHOLDS 1 & 2) #
-  Model_Index_D <- Trans_Spp %>% 
-    group_by(Name,
-             TaxonKey,
-             Model_Index
-    ) %>% 
-    summarise(n_cells_spp = n()) %>% 
-    select(-n_cells_spp)
-
-  #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
-  # The number of species' cells present within each country's EEZ
-
-  #Step 1.  Get EEZ id and Neighbour
-  Neighbours_EEZ <- Neighbours %>% 
-    group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
-    summarise(n=n()) %>% 
-    ungroup() %>% 
-    select(-n)
-
-  # Step 2. Determines the amount of grids present in each country
-  Spp_Grid <- Trans_Spp %>% 
-    group_by(TaxonKey,
-             Model_Index, # Un-comment after producing models x datasets
-             EEZID) %>% 
-    summarise(n_spp_eez = length(unique(INDEX))) %>% 
-    left_join(Neighbours_EEZ,
-              by = "EEZID") %>% 
-    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
-           Neighbour_Territory %in% Trans_Spp$Name)
-
-  # Step 3. Sum total grids per Neighbours
-
-  # Split dataframes to merge latter
-  Country_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index, # Un-comment after producing models x datasets
-      TaxonKey,
-      Name=Country_Territory,
-      n_spp_eez
-    )
-
-  Neighbour_Territory_T <- Spp_Grid %>% 
-    ungroup() %>% 
-    select(
-      Model_Index,
-      TaxonKey,n_spp_eez,
-      Name=Neighbour_Territory, 
-      Country_Territory
-    )
-
-  # Merge dataframes to get totals per Neighbourds
-  Area_Index_D <- full_join(Country_Territory_T,
-                            Neighbour_Territory_T, 
-                            by = c("Model_Index","Name","TaxonKey")
-  ) %>%
-    rowwise() %>%
-    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
-    distinct() %>% # Removes false duplicates from `full_join()`
-    rename(Neighbour_Territory = Name,
-           n_spp_Country = n_spp_eez.x,
-           n_spp_Neighbour = n_spp_eez.y) %>% 
-    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
-    select(1:3,6,8)
-
-  #____________ FINAL INDEX TABLE_________ #
-  Indexes <- Model_Index_D %>% 
-    rename(Country_Territory = Name) %>% 
-    full_join(Area_Index_D,
-              by = c("TaxonKey","Country_Territory","Model_Index")
-    ) %>% 
-    filter(!is.na(Area_Index),
-           !is.na(Model_Index) # Uncomment after producing Models x datasets
-    )%>%  # Remove cases where the country does not pass the area_index and viceversa
-    select(TaxonKey,Country_Territory,Neighbour_Territory,everything())
-
-  ### Save spp dataframe
-
-  if(nrow(Indexes) > 0 & Save == "Y"){
-
-    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
-    Save_Path <- paste(Results_Path,File_Name,sep="")
-
-    write.csv(Indexes,
-              Save_Path,
-              row.names = F)
-
-  }
-
-  if(nrow(Indexes) == 0 & Save == "Y"){
-
-    # Reads dataset of Non transboundary species
-    Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))
-
-    # Get current Spp that is not transboundary 
-    Current_Spp <- tibble(TaxonKey = Spp)
-
-    # Combine new spp with others
-    New_Non <- Non_Transboundary_Data %>% 
-      bind_rows(Current_Spp)
-
-    # Set a name for file and saves data
-    New_Non_Name <- paste(Results_Path,"Non_Transboundary_Data.csv",sep="")
-    write.csv(New_Non, New_Non_Name, row.names = F)
-
-  }
-
-  ### Function return
-
-  EstTransIndex=Indexes # A dataframe with
-
-}
-```
-
-```{habitat_barplot, eval =F, echo =F}
-
-Species_data <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
-  mutate(Distance = ifelse(DemersPelag == "reef-associated", 1,
-                           ifelse(DemersPelag =="pelagic-neritic",2,
-                                  ifelse(DemersPelag == "demersal",3,
-                                         ifelse(DemersPelag == "pelagic-oceanic",4,
-                                                ifelse(DemersPelag =="benthopelagic",5,
-                                                       ifelse(DemersPelag =="bathypelagic",6,
-                                                              ifelse(DemersPelag =="bathydemersal",7,
-                                                                     8)))))))
-  ) %>% 
-  group_by(DemersPelag,Distance) %>% 
-  summarise(Countries_Genus = sum(n_countries,na.rm=T),
-            Mean_Countries_Genus = mean(n_countries,na.rm=T),
-            sd_Countries_Genus = sd(n_countries,na.rm=T),
-            N_spp =length(unique(TaxonName))
-  )
-
-ggplot(Species_data,
-       aes(
-         x = reorder(DemersPelag,desc(Distance)),
-         y = Mean_Countries_Genus,
-         fill = Countries_Genus#,
-         # colour = Countries_Genus
-       )
-) +
-  geom_bar(stat = "identity") +
-  # geom_errorbar(data = Species_data,
-  #               aes(
-  #                 x = reorder(DemersPelag,desc(Distance)),
-  #                 ymin=Mean_Countries_Genus-sd_Countries_Genus, # mean +- 2*sd
-  #                 ymax=Mean_Countries_Genus+sd_Countries_Genus
-  #               ),
-  #               colour = "black",
-  #               width=.2,
-  #               linetype = 2,
-  #               size = 0.6,
-  #               alpha = 0.5
-# ) +
-geom_text(data = Species_data, 
-          aes(
-            x = reorder(DemersPelag,desc(Distance)),
-            y = 2,
-            label = paste(as.character(N_spp), "species"),
-          ),
-          colour = "black"
-) +
-  coord_flip() +
-  scale_fill_gradientn("Total number\nof countries",
-                       colours = wes_palette("Zissou1"),
-                       limits = c(0,1500),
-                       breaks = seq(0,1500,250)
-  ) +
-  scale_colour_gradientn("Total number\nof countries",
-                         colours = wes_palette("Zissou1"),
-                         limits = c(0,1500),
-                         breaks = seq(0,1500,250)
-  ) +
-  scale_y_continuous(breaks=seq(0, 40, 5), 
-                     limits=c(0, 40)
-  )+
-  labs(
-    x = "Habitat type",
-    y = "Mean number of countries per habitat"
-  ) +
-  ggtheme_plot()
-
-```
-
-```{r Territories_Circluar_Plot, eval = T, echo = T}
-
-# -------------------------- #
-# Data manipulation for plot
-# -------------------------- #
-
-# Set a number of 'empty bar' to add at the end of each group
-Char <- as.factor(Countries_Data_Plot$group) # Set groups to factors
-empty_bar <- length(unique(Countries_Data_Plot$group))
-to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data_Plot)) )
-colnames(to_add) <- colnames(Countries_Data_Plot)
-to_add$group <- rep(levels(Char), each=empty_bar)
-Countries_Data_Plot <- bind_rows(Countries_Data_Plot, to_add)
-Countries_Data_Plot <- Countries_Data_Plot %>% arrange(group,value)
-Countries_Data_Plot$id <- seq(1, nrow(Countries_Data_Plot))
-
-# Get the name and the y position of each label
-
-# Top n of each group label
-Top_Countries <- Countries_Data_Plot %>% 
-  group_by(group) %>% 
-  top_n(5,value)
-
-# Create labels for all but top 5
-label_data <- Countries_Data_Plot 
-number_of_bar <- nrow(label_data)
-angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
-label_data$hjust <- ifelse( angle < -90, 1, 0)
-label_data$angle <- ifelse(angle < -90, angle+180, angle)
-
-# Remove top 5
-label_data_rest <- label_data %>% 
-  filter(!individual %in% Top_Countries$individual)
-
-# Create labels for top 5
-Top_label_data <- label_data %>% 
-  filter(individual %in% Top_Countries$individual)
-
-# prepare a data frame for base lines
-base_data <- Countries_Data_Plot %>% 
-  group_by(group) %>% 
-  summarize(start=min(id), 
-            end=max(id) - empty_bar, 
-            median = median(value, na.rm = T)
-  ) %>% 
-  rowwise() %>% 
-  mutate(title=mean(c(start, end)))
-
-# prepare a data frame for grid (scales)
-grid_data <- base_data
-grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
-grid_data$start <- grid_data$start - 1
-grid_data[1,2] <- 5 # Manually include Africa for the median
-grid_data[1,3] <- 1
-
-# Median data
-median_data <- grid_data %>% 
-  mutate_at(vars(start,end),
-            .funs = as.numeric)
-
-# -------------------------- #
-# Get id to Discrete data
-# -------------------------- #
-
-Discrete_Data_Plot <- Discrete_Data_Plot %>% 
-  left_join(Countries_Data_Plot,
-            by =c("individual","group")
-  ) %>%
-  mutate(value = ifelse(value.x <= -100,-100,value.x)) %>%
-  select(individual,group,value,id) %>%
-  arrange(group,value)
-
-### make sure they have all same countries
-
-Discrete_Data_Plot %>% 
-  anti_join(Countries_Data_Plot,
-            by = c("individual","group","id"))
-
-# -------------------------- #
-# Make the plot
-# -------------------------- #
-
-# Global Variables
-Seq_axis <- seq(-100,100,20)
-Plot_Limit <- max(Countries_Data_Plot$value,na.rm=T)
-Plot_Limit_Low <- -110
-Ticks_Color <- "grey50"
-
-# Base plot
-ggplot(Countries_Data_Plot,
-       aes(x=as.factor(id), 
-           y=value,
-           fill=group)
-) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
-  geom_bar(aes(x=as.factor(id),
-               y=value,
-               fill=group),
-           stat="identity",
-           alpha=0.5) +
-  geom_bar(data = Discrete_Data_Plot,
-           aes(x=as.factor(id),
-               y=value),
-           stat="identity",
-           alpha=0.5) +
-  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
-  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) + # Cero
-  geom_segment(data=grid_data, aes(x = end, y = -100, xend = start, yend = -100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = -80, xend = start, yend = -80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = -60, xend = start, yend = -60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = -40, xend = start, yend = -40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  geom_segment(data=grid_data, aes(x = end, y = -20, xend = start, yend = -20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
-  # Add median lines for each gropup
-  geom_segment(data=median_data,
-               aes(x = end,
-                   y = median,
-                   xend = start+5, 
-                   yend = median,
-                   colour = group),
-               alpha=1,
-               size=0.5 , 
-               inherit.aes = FALSE ) +
-  # Add text showing the value of each line
-  annotate("text", label = "Transboundary", x = 214, y = 45, size = 5, colour = "grey10", angle = 90) +
-  annotate("text", label = "Discrete", x = 210, y = -45, size = 5, colour = "grey10", angle = 90) +
-  annotate("text", 
-           x = rep(max(Countries_Data_Plot$id),length(Seq_axis)),
-           y = Seq_axis,
-           label = c("<-100",as.character(Seq_axis)[2:(length(Seq_axis)-1)],">100"),
-           color = Ticks_Color, 
-           size= 4, 
-           angle = 0, 
-           # fontface="bold",
-           hjust=1) +
-  geom_bar(aes(x=as.factor(id),
-               y=value,
-               fill=group),
-           stat="identity",
-           alpha=0.5) +
-  #Country labels
-  geom_text(data=label_data_rest,
-            aes(x=id, y=Plot_Limit,
-                label=individual,
-                hjust=hjust), 
-            color="black",
-            # fontface="bold",
-            alpha=1,
-            size=2.5,
-            angle= label_data_rest$angle,
-            inherit.aes = FALSE) +
-  # Bold top 3 
-  geom_text(data=Top_label_data,
-            aes(x=id, y=Plot_Limit,
-                label=individual,
-                hjust=hjust), 
-            color="black",
-            fontface="bold",
-            alpha=1,
-            size=2.5,
-            angle= Top_label_data$angle,
-            inherit.aes = FALSE) +
-  # Add base line information
-  geom_segment(data=base_data, 
-               aes(x = start, 
-                   y = 0, 
-                   xend = end, 
-                   yend = 0
-               ), 
-               colour = "black",
-               alpha=0.8, 
-               size=0.6 , 
-               inherit.aes = FALSE) +
-  ylim(Plot_Limit_Low,Plot_Limit) + # sets the circle the first value the central the last value how wide
-  theme_minimal() +
-  theme(
-    # legend.position = c(0.5,0.5),
-    legend.position = "",
-    axis.text = element_blank(),
-    axis.title = element_blank(),
-    panel.grid = element_blank(),
-    plot.margin = unit(rep(-1,4), "cm") 
-  ) +
-  coord_polar() + 
-  scale_fill_manual("Continent",
-                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 4, name = "Darjeeling2")
-                    ),
-                    na.value = "white"
-  ) +
-  scale_colour_manual("Continent",
-                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
-                                 wes_palette(n = 4, name = "Darjeeling2")
-                      ),
-                      na.value = "white")
-
-# Save plot
-
-# ggsave(
-#     plot = last_plot(),
-#     width = 12,
-#     height = 12,
-#     units = "in",
-#     filename = "Territory_circular_both.png",
-#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
-#   )
-
-```
-
-```{r Top_country_Circle_Diagram, eval =F, echo = F}
-
-# Top 10 species
-
-# Number of countries shared by each Species
-Top_10_Countries <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index < Min_AI |
-      Area_Index > Max_AI,
-    Model_Index == MI,
-    Same_Nation == "No"
-  ) %>% 
-  group_by(Country_Territory) %>% 
-  summarise(
-    n_countries = length(unique(TaxonKey))
-  ) %>% 
-  top_n(10,n_countries)
-
-# Countries that share the top 10
-Top_Ten_Countries <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index < Min_AI |
-      Area_Index > Max_AI,
-    Model_Index == MI,
-    Same_Nation == "No",
-    Country_Territory %in% Top_10_Countries$Country_Territory
-  ) %>% 
-  group_by(from=CT_fishing_entity,
-           to=NT_fishing_entity
-  ) %>% 
-  summarise(value=n()
-  ) %>% 
-  ungroup() %>% 
-  mutate(from = paste("F", from),
-         to = paste("T", to)
-  )
-
-####________________###
-# Circulize package ####
-# https://jokergoo.github.io/circlize_book/book/
-####________________###
-
-# To set links collor 
-Bins <- as.numeric(cut(Top_Ten_Countries$value,breaks = 5))
-
-# Basic plot
-circos.clear()
-chordDiagram(Top_Ten_Countries, 
-             annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
-             annotationTrackHeight = c(0.001, 0.05), # set links close to the axis
-             directional = 1, # direction of arrows
-             direction.type = c("diffHeight", "arrows"), # use arrows
-             grid.col = "white",
-             col = ifelse(Bins == 1,"#046C9A", # deep blue
-                          ifelse(Bins == 2,"#78B7C5", #light blue
-                                 ifelse(Bins == 3,"#EBCC2A", #yellow
-                                        ifelse(Bins == 4, "#E1AF00", #cream
-                                               "#F21A00")))), #red
-             link.arr.col = wes_palette("Zissou1"),
-             link.arr.type = "big.arrow",# make links big arrows
-             diffHeight = uh(1, "mm"), # brings the arrow to the bottom of the source
-             # annotationTrack = "grid", # no labels
-             scale = FALSE, # fraction of total instead of absolute value
-             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Top_Ten_Countries))))) # I have no idea but helps with the labels
-) 
-#  Rest of eddits
-circos.track(track.index = 1, panel.fun = function(x, y) {
-  xlim = get.cell.meta.data("xlim")
-  xplot = get.cell.meta.data("xplot")
-  ylim = get.cell.meta.data("ylim")
-  sector.name = get.cell.meta.data("sector.index")
-
-  circos.text(mean(xlim),
-              ylim[1], 
-              sector.name, 
-              facing = "clockwise",
-              niceFacing = TRUE,
-              adj = c(-0.2, 0.5),
-              col = "black")
-
-}, bg.border = NA)
-
-```
-
-```{r Top_spp_Circle_Diagram, eval =F, echo = F}
-
-# Top 5 shared species per marine environment (number of countries sharing the species)
-Top_Species <- Species_Trans %>% 
-  mutate(scientific_name = paste(Genus,Species)) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(DemersPelag = replace_na(DemersPelag, "Other")) %>% 
-  # group_by(TaxonKey,TaxonName,CommonName,DemersPelag) %>% 
-  # summarise(Sum_Countries =sum(n_countries,na.rm=T)) %>% 
-  group_by(DemersPelag) %>% 
-  top_n(5,n_countries)
-
-# Countries that share the top 10
-Top_Spp_Countries <- Clean_Results_Trans %>% 
-  filter(
-    Area_Index < Min_AI |
-      Area_Index > Max_AI,
-    Model_Index == MI,
-    Same_Nation == "No",
-    TaxonKey %in% Top_Species$TaxonKey
-  ) %>% 
-  left_join(Species_Trans) %>% 
-  rename(scientific_name =TaxonName) %>%
-  left_join(Species_environ_list) %>% 
-  mutate(from = paste(Genus,"\n",Species,sep=""),
-         DemersPelag = replace_na(DemersPelag, "Other")) %>%
-  group_by(
-    # from,
-    from = scientific_name,
-    to=CT_fishing_entity,
-    DemersPelag
-  ) %>% 
-  summarise(value=n()
-  ) #%>%
-# filter(DemersPelag == "demersal") %>%
-# select(-DemersPelag)
-
-####________________###
-# Circulize package ####
-# https://jokergoo.github.io/circlize_book/book/
-####________________###
-
-# To set links color 
-Bins <- as.numeric(cut(Top_Spp_Countries$value,breaks = 5)) # By size of sharing
-
-# To get country's flags... https://flagpedia.net/download
-flags <- c(paste("Temporal_Data/flags-mini/",list.files("Temporal_Data/flags-mini/"),sep=""))
-
-# List of Ecosystems
-Classification <- Top_Species %>% group_by(DemersPelag) %>% summarise(n()) %>%  pull(DemersPelag)
-
-####________________ PLOT PER ECOSYSTEM _____________________ ###
-
-for(s in 1:2){ # sclae loop
-  for(i in 1:length(Classification)) {
-    # for(i in 1:2) { # for testing
-
-    # Set scales to plott both absolut and proportional values
-    if(s == 1){
-      Scales <- "TRUE"
-    }else{
-      Scales <- "FALSE"
-    }
-
-    # Saving the plot
-    Plot_name <- paste(Figures_Path,Classification[i],Scales,".tiff",sep="")
-    tiff(Plot_name, width = 5, height = 5, units = 'in', res = 500)
-
-    # Subsetting the data for each plot
-    DemersPelag_i <- Classification[i]
-
-    Data <- Top_Ten_Spp_Countries %>% 
-      filter(DemersPelag %in% DemersPelag_i) %>% 
-      select(-3)
-
-    # Use to set links' colors to each species
-    Speceis_cols <- Data %>% group_by(from) %>% summarise(n()) %>% pull(from)
-
-    # The base plot
-    circos.clear()
-    chordDiagram(Data, 
-                 annotationTrack = c("grid", "axis"), # keep grid and axis but not labels
-                 annotationTrackHeight = c(0.001, 0.1), # set links close to the axis
-                 directional = 1, # direction of arrows
-                 direction.type = c("diffHeight", "arrows"), # use arrows
-                 grid.col = "grey",
-                 # if col == Bins then colors will change depending of value
-                 # col = ifelse(Bins == 1,"#046C9A", # deep blue
-                 #              ifelse(Bins == 2,"#78B7C5", #light blue
-                 #                     ifelse(Bins == 3,"#EBCC2A", #yellow
-                 #                            ifelse(Bins == 4, "#E1AF00", #cream
-                 #                                   "#F21A00")))), #red
-                 # if col == Species_cols then colors will change depending of species
-                 col = ifelse(Data$from == Speceis_cols[1],"#FF0000", # deep blue
-                              ifelse(Data$from == Speceis_cols[2],"#00A08A", #light blue
-                                     ifelse(Data$from == Speceis_cols[3],"#F2AD00", #yellow
-                                            ifelse(Data$from == Speceis_cols[4], "#F98400", #cream
-                                                   "#5BBCD6")))), #red
-                 # link.arr.col = wes_palette("Zissou1"), 
-                 link.arr.type = "big.arrow",# make links big arrows
-                 diffHeight = uh(-0.5, "mm"), # brings the arrow to the bottom of the source
-                 scale = Scales, # fraction of each species to total share of each country instead of absolute value
-                 preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(Data))))) # I have no idea but helps with the labels
-    )
-
-    #  Function to inlcude other layers
-    circos.track(track.index = 1, panel.fun = function(x, y) {
-      xlim = get.cell.meta.data("xlim")
-      xplot = get.cell.meta.data("xplot")
-      ylim = get.cell.meta.data("ylim")
-      sector.name = get.cell.meta.data("sector.index")
-
-      # Add labels
-      circos.text(mean(xlim),
-                  ylim[1],
-                  sector.name,
-                  facing = "clockwise",
-                  niceFacing = TRUE,
-                  adj = c(-0.2, 0.5),
-                  col = "black",
-                  cex = 0.6) # size of labels
-
-      # Add country's flags instead of names (still need to link names to falgs)
-
-      # library(EBImage)
-      # pos = circlize:::polar2Cartesian(circlize(CELL_META$xcenter, CELL_META$ycenter))
-      # image = EBImage::readImage(flags[CELL_META$sector.numeric.index])
-      # 
-      # rasterImage(image,
-      #             xleft = pos[1, 1] - 0.006, 
-      #             ybottom = pos[1, 2] - 0.005,
-      #             xright = pos[1, 1] + 0.05,
-      #             ytop = pos[1, 2]+ 0.04
-      #             )
-
-      # END FLAGS TRYOUT
-
-      # Set plot Title
-      Title <- paste("Top",Classification[i], "Species",sep =" ")
-      title(Title)
-
-    }, bg.border = NA) #end of circos.track
-
-    dev.off()
-  } # close for loop
-} #close scale loop
-
-```
-
-### Species status (SAU methods)
-
-Note that (n), the number of ‘stocks’ is defined as a time series of a given species, genus or family (higher and pooled groups have been excluded) for which the first and last reported landings are at least 10 years apart, for which there are at least 5 years of consecutive catches and for which the catch in a given area is at least 1000 tonnes.
-
-1) The first and last reported landings are at least ten years apart;
-
-2) There are at least five years of consecutive catches; and
-
-3) The catch in a particular area (LME) is at least 1,000 tonnes.
-
-Once those thresholds are met, the status of the species is determined as follows:
-
-- Rebuilding (Recovering)	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
-- Developing	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
-- Exploited	Landing > 50% of max. landing
-- Over exploited	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
-- Collapsed	Year of landing > year of max. landing AND landing is < 10% of max. landing
-
-*Notes* = 3 years average mean
-
-```{r Species_Status, eval = T, echo =F}
-
-CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
-  mutate(INDEX = seq(1,259200,1))
-
-# SAU relations between INDEX and Country's EEZs
-EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
-EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
-colnames(EEZ_CellID) <- c("EEZID","INDEX")
-
-Index_Code <- EEZIDs_List %>% 
-  left_join(EEZ_CellID) %>% 
-  rename(Territory = Name)
-
-Spp <- GetSppDist(600004, Model = "SAU_C", Coord = CoorG)
-
-Data <- Spp %>% 
-  gather("Year","Value",CATCH.1:CATCH.65) %>% 
-  arrange(INDEX) %>% 
-  mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
-  left_join(Index_Code) %>% 
-  filter(!is.na(EEZID),
-         Value > 0) %>% 
-  group_by(Species,Year,EEZID,Territory) %>% # Total catch per country
-  summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
-  group_by(Species,Territory,EEZID,Year) %>% 
-  mutate(RMean = rollmean(x = Total_Catch, 5, align = "right", fill = Total_Catch)) %>% 
-  group_by(Species,Territory,EEZID)
-
-# head(Data)
-
-# Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
-Tresholds <- Data %>% 
-  arrange(Territory) %>% 
-  group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
-            Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
-            Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
-  ) %>% 
-  gather("Step","Treshold",Years_appart:Catch_over) %>% 
-  filter(Treshold == "Yes")
-
-# Evaluate stocks
-
-# Filter data that does not satisfy tresholds
-
-Landings_Peaks <- Data %>% 
-  group_by(Species,Territory) %>% 
-  summarise(Max_Peak = max(RMean,na.rm=T))
-
-Eval_Data <- Data %>% 
-  semi_join(Tresholds,
-            by = c("Species","Territory")) %>% 
-  left_join(Landings_Peaks,
-            by = c("Species","Territory"))
-
-Peak_Year <- Eval_Data %>% 
-  filter(RMean == Max_Peak) %>% 
-  select(Species,Territory,EEZID,Y_Max_Peak = Year)
-
-Post_Max_Min <- Eval_Data %>% 
-  left_join(Peak_Year) %>% 
-  filter(Year > Y_Max_Peak) %>% 
-  group_by(Species,Territory,EEZID) %>% 
-  summarise(Post_Max_Min = min(RMean,na.rm=T))
-
-Y_Post_Max_Min <- Eval_Data %>% 
-  left_join(Post_Max_Min) %>% 
-  filter(RMean == Post_Max_Min) %>% 
-  select(Species,Territory,EEZID,Y_Post_Max_Min = Year)
-
-Data_Status <- Eval_Data %>% 
-  left_join(Peak_Year,
-            by = c("Species","Territory","EEZID")) %>%
-  left_join(Post_Max_Min,
-            by = c("Species","Territory","EEZID")) %>% 
-  left_join(Y_Post_Max_Min,
-            by = c("Species","Territory","EEZID")) %>% 
-  rename(Y_RMean = Year) %>% 
-  mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                         ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
-                                ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                       ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
-                                              ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                     "No Status")
-                                       )
-                                )
-                         )
-  )
-  ) %>% 
-  filter(Y_RMean > 2004) %>% 
-  group_by(Species,EEZID,Territory,Status) %>% 
-  summarise(n_Status= n()) %>% 
-  group_by(Species,EEZID,Territory) %>% 
-  top_n(1,n_Status)
-
-# Manual estimation
-
-data.frame(
-  Y_RMean = 1980,
-  RMean = 642187,
-  Max_Peak = 1298712,
-  Y_Max_Peak = 1990,
-  Post_Max_Min = 681967,
-  Y_Post_Max_Min = 2010,
-  Y_RMean = 2014
-) %>% 
-  mutate(Status = ifelse(Y_RMean > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
-                         ifelse((Y_RMean < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Y_RMean)),"Developing",
-                                ifelse(RMean > Max_Peak*0.50,"Max Exploited",
-                                       ifelse(Y_RMean > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))," Over Exploited",
-                                              ifelse(Y_RMean > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
-                                                     "NA")
-                                       )
-                                )
-                         )
-  )
-  )
-
-```
-
-# RFMO Analysis
-
-```{r RFMO_Data, eval = F}
-
-RFMO_Data <- read.delim("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/RFMO_procedure_outcome.csv")
-
-x <- RFMO_Data %>% 
-  mutate(
-    x = gsub("<.*?>", "", RFMO_Data$primary_species),
-    y = gsub("[\\(\\)]", "", regmatches(x, gregexpr("\\(.*?\\)", x)))
-  )
-
-# Save to remove "" and pass to colomuns in excell
-# write.csv(x,
-#           "rfmos.csv")
-
-rfmos <- read.csv("~/Github/FishForVisa/rfmos.csv")
-View(rfmos)
-
-list <- rfmos$Taxa
-
-clean_rfmos <- rfmos %>% 
-  gather("taxa","taxon_name",y:X.21) %>% 
-  filter(taxon_name != "") %>% 
-  select(RFMO_name = name,
-         contracting_parties,
-         area,
-         taxon_name)
-
-# write_csv(clean_rfmos,
-#           "clean_rfmos.csv")
-
-### Join with exploited species
-
-clean_rfmos <- clean_rfmos %>% 
-  left_join(Exploited_Species)
-
-```
-
-## RFMO specifics
-
-```{r RFMOs, eval = T, echo = F}
-
-### Results exploration
-
-ICCAT_List <- rfmo_list %>% 
-  filter(rfmo_name == "ICCAT") %>% 
-  pull(taxon_key) %>% 
-  unique()
-
-Tresholded_T_Data %>% 
-  filter(taxon_key %in% ICCAT_List) %>% 
-  group_by(taxon_key) %>% 
-  summarise(
-    n_countries = length(unique(fishing_entity))
-  )
-
-ICCAT_Trans <- Species_Data %>% 
-  rename(taxon_name = individual) %>% 
-  left_join(Exploited_Species) %>% 
-  filter(taxon_key %in% ICCAT_List)
-
-```
-
-## RFMO Map of Transboundary Species
-
-```{r RFMO_Map, eval =F, echo =F}
-
-Tresholded_rfmo_Data <- Results_rfmo %>% 
-  filter(
-    area_index >= Min_AI,
-    area_index <= Max_AI,
-    model_index >= MI
-  ) %>% 
-  group_by(rfmo_name) %>% 
-  summarise(
-    n_trans_spp = length(unique(taxon_key)),
-    n_neighbours = length(unique(neighbour)),
-    trans_Rrate = n_trans_spp/n_neighbours
-  )
-
-# Number of RFMOs
-rfmo_list %>% 
-  pull(rfmo_name) %>% 
-  unique() %>% 
-  length() # 15
-
-# Number of total taxa
-rfmo_list %>% 
-  pull(taxon_key) %>% 
-  unique() %>% 
-  length() # 99
-
-# Number of taxa per RFMO
-rfmo_list %>% 
-  group_by(rfmo_name) %>% 
-  summarise(in_trans_spp = length(unique(taxon_key)))
-
-# Number of shared taxa
-Results_rfmo %>% 
-  pull(taxon_key) %>% 
-  unique() %>% 
-  length() # 81
-
-### Bar plot
-
-Tresholded_rfmo_Data %>% 
-  ggplot() +
-  geom_bar(
-    aes(
-      x = reorder(rfmo_name,-n_trans_spp),
-      y = n_trans_spp
-    ),
-    stat = "identity"
-  ) +
-  coord_flip()
-
-head(RFMOs_sf)
-
-# Transboundary Species shapefile
-World_sf_si <- RFMOs_sf %>%
-  filter(!Name %in% c("IPHC","PSC","NASCO")) %>% 
-  rename(rfmo_name = Name) %>% 
-  st_transform(crs = 4326) %>% # 4326
-  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
-  left_join(Tresholded_rfmo_Data, by ="rfmo_name")
-
-# Total catch/Revenue shapefile
-World_sf_si_land <- World_land_sf %>%
-  st_transform(crs = 4326) #%>% # 4326
-# st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
-
-# Get the NA's to be grey
-# Grey_land <- World_sf_si_land %>% 
-#   filter(is.na(Bins))
-
-# Make map
-Plot <- ggplot() +
-  geom_sf(data = World_sf_si,
-          aes(
-            fill =  n_trans_spp,
-            colour = n_trans_spp
-          ), 
-          size = 0.1
-  ) + # n_trans_spp or Bins
-  geom_sf(data = World_sf_si_land) +
-  # geom_sf_label(data = World_sf_si,
-  #               aes(label = eez_name)
-  #               ) +
-  scale_fill_gradientn("Number of Shared Species",
-                       colours = wes_palette("Zissou1", 100, type = "continuous"),
-                       limits = c(0,45),
-                       breaks = seq(0,45,5)
-  ) +
-  scale_colour_gradientn("Number of Shared Species",
-                         colours = wes_palette("Zissou1", 100, type = "continuous"),
-                         limits = c(0,45),
-                         breaks = seq(0,45,5)
-  ) +
-  ggtheme_map()
-
-Plot_Name <- paste("S2_RFMO.png", sep = "")
-
-ggsave(Plot_Name,
-       plot = Plot,
-       width = 16,
-       height = 8,
-       units = "in",
-       path = Figures_Path
-)
-```

### 2020-08-07 Scripts/RFMO Analysis.Rmd
included FishForVisa RFMO code in old script

@@
 # Old code
+
+## From FishForVisa Main script
+
+## RFMO specifics
+
+```{r RFMOs, eval = T, echo = F}
+
+### Results exploration
+
+ICCAT_List <- rfmo_list %>% 
+  filter(rfmo_name == "ICCAT") %>% 
+  pull(taxon_key) %>% 
+  unique()
+
+Tresholded_T_Data %>% 
+  filter(taxon_key %in% ICCAT_List) %>% 
+  group_by(taxon_key) %>% 
+  summarise(
+    n_countries = length(unique(fishing_entity))
+  )
+
+ICCAT_Trans <- Species_Data %>% 
+  rename(taxon_name = individual) %>% 
+  left_join(Exploited_Species) %>% 
+  filter(taxon_key %in% ICCAT_List)
+
+```
+
+## RFMO Map of Transboundary Species
+
+```{r RFMO_Map, eval =F, echo =F}
+
+Tresholded_rfmo_Data <- Results_rfmo %>% 
+  filter(
+    area_index >= Min_AI,
+    area_index <= Max_AI,
+    model_index >= MI
+  ) %>% 
+  group_by(rfmo_name) %>% 
+  summarise(
+    n_trans_spp = length(unique(taxon_key)),
+    n_neighbours = length(unique(neighbour)),
+    trans_Rrate = n_trans_spp/n_neighbours
+  )
+
+# Number of RFMOs
+rfmo_list %>% 
+  pull(rfmo_name) %>% 
+  unique() %>% 
+  length() # 15
+
+# Number of total taxa
+rfmo_list %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length() # 99
+
+# Number of taxa per RFMO
+rfmo_list %>% 
+  group_by(rfmo_name) %>% 
+  summarise(in_trans_spp = length(unique(taxon_key)))
+
+# Number of shared taxa
+Results_rfmo %>% 
+  pull(taxon_key) %>% 
+  unique() %>% 
+  length() # 81
+
+### Bar plot
+
+Tresholded_rfmo_Data %>% 
+  ggplot() +
+  geom_bar(
+    aes(
+      x = reorder(rfmo_name,-n_trans_spp),
+      y = n_trans_spp
+    ),
+    stat = "identity"
+  ) +
+  coord_flip()
+
+head(RFMOs_sf)
+
+# Transboundary Species shapefile
+World_sf_si <- RFMOs_sf %>%
+  filter(!Name %in% c("IPHC","PSC","NASCO")) %>% 
+  rename(rfmo_name = Name) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
+  left_join(Tresholded_rfmo_Data, by ="rfmo_name")
+
+# Total catch/Revenue shapefile
+World_sf_si_land <- World_land_sf %>%
+  st_transform(crs = 4326) #%>% # 4326
+# st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
+
+# Get the NA's to be grey
+# Grey_land <- World_sf_si_land %>% 
+#   filter(is.na(Bins))
+
+# Make map
+Plot <- ggplot() +
+  geom_sf(data = World_sf_si,
+          aes(
+            fill =  n_trans_spp,
+            colour = n_trans_spp
+          ), 
+          size = 0.1
+  ) + # n_trans_spp or Bins
+  geom_sf(data = World_sf_si_land) +
+  # geom_sf_label(data = World_sf_si,
+  #               aes(label = eez_name)
+  #               ) +
+  scale_fill_gradientn("Number of Shared Species",
+                       colours = wes_palette("Zissou1", 100, type = "continuous"),
+                       limits = c(0,45),
+                       breaks = seq(0,45,5)
+  ) +
+  scale_colour_gradientn("Number of Shared Species",
+                         colours = wes_palette("Zissou1", 100, type = "continuous"),
+                         limits = c(0,45),
+                         breaks = seq(0,45,5)
+  ) +
+  ggtheme_map()
+
+Plot_Name <- paste("S2_RFMO.png", sep = "")
+
+ggsave(Plot_Name,
+       plot = Plot,
+       width = 16,
+       height = 8,
+       units = "in",
+       path = Figures_Path
+)
+```
+
 ```{r OLD_funEstNeighbours, eval = F, echo=T}

### 2020-08-11 Scripts/Manuscript_Draft.Rmd
Fixed quality check comments
Fixed legends requested by journal

@@
 Points = regional  mean ± sd.
-Revenue in 2019 real USD.](../Figures/Fig1.png)
+Revenue in 2019 real USD.
+Figure created using R version 3.5.2.
+Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png)
 
@@
 Points are sub-region averages $\pm$ s.d.
-by country](../Figures/Fig2.png)
+by country.
+Figure created using R version 3.5.2.](../Figures/Fig2.png)
 
@@
 Number of transboundary species by catch trend and EEZ.
-Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend.“No Category” reflect species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.](../Figures/Fig3.png)
+Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend.“No Category” reflect species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Figure created using R version 3.5.2.](../Figures/Fig3.png)
 
@@
 Note that there could be > 5 species due to similar sharing values.
-** The category "Other" consists of species that have no classification according to FishBase.**](../Figures/Fig4.png)
+** The category "Other" consists of species that have no classification according to FishBase.
+Figure created using R version 3.5.2.**](../Figures/Fig4.png)
 
@@
 All code is available at https://github.com/jepa/FishForVisa.
+All maps were made with Natural Earth data available at https://www.naturalearthdata.com/.
 We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].

### 2020-08-12 Scripts/supplements.Rmd

@@
 ```{r Call_Sup_1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon."}
+The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
+Figure created using R version 3.5.2.
+Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively."}
 
@@
 ```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis"}
+The darker histogram represents the threshold (25%) used in the present analysis.
+Figure created using R version 3.5.2."}
 
@@
 ```
+
+We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.

### 2020-08-12 Scripts/Initial_Analysis.Rmd
Updated initial analysis to match sci.rev

@@
 
-This sub routine determines the species exploitation status based on the SAU methodology.
-**Note:** For the current project we do not consider this method to determine the species exploitation status *per se*, but rather a catch trend that *could* indicate that a species is under/over/max exploited.
+This sub routine determines the species exploitation trend based on the SAU methodology.
+**Note:** For the current project we do not consider this method to determine the species exploitation trend *per se*, but rather a catch trend that *could* indicate that a species is under/over/max exploited.
 
@@
 
-Once those thresholds are met, the status of the species is determined as follows:
+Once those thresholds are met, the trend of the species is determined as follows:
 
@@
 
-Finally we choose the reporting year based on the most frequent status in the last 10 years of data.
-In cases where there was a mach between status (e.g.
-Cayman Islands for species 6000006 had 5 *Max Exploited* and 5 *Overexploted*) then we report the status at the last year of data.
+Finally we choose the reporting year based on the most frequent trend in the last 10 years of data.
+In cases where there was a mach between trend (e.g.
+Cayman Islands for species 6000006 had 5 *Max Exploited* and 5 *Overexploted*) then we report the trend at the last year of data.
 
@@
 
-### Function `EstSppStatus`
-
-This function estimates the exploitation status of a species based on catch data.
-
-```{r funEstSppStatus, eval = T, echo =F}
+### Function `EstCatchTrend`
+
+This function estimates the exploitation trend of a species based on catch data.
+
+```{r funEstCatchTrend, eval = T, echo =F}
 
@@
 
-EstSppStatus <- function(Spp,Coord, Save_Path = "NA", Per_Taxa = NA){
+EstCatchTrend <- function(Spp,Coord, Save_Path = "NA", Per_Taxa = NA){
 
@@
 
-  # Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
+  # Tresholds to evaluate stocks if these are not met, then soecies Trend = "No Trend"
   Tresholds_Data <- Data %>% 
@@
 
-  No_Status_Data <- Tresholds_Data %>% 
+  No_Trend_Data <- Tresholds_Data %>% 
     filter(Met_Criteria != "Yes") %>% 
     select(TaxonKey,Territory) %>% 
-    mutate(Status = "No Trend")
+    mutate(Trend = "No Trend")
 
@@
 
-  # Get Variables to perform status metric
-  Status_Data <- Data %>% 
+  # Get Variables to perform Trend metric
+  Trend_Data <- Data %>% 
     # filter(Territory == "Israel (Red Sea)") %>%  # For testing
-    anti_join(No_Status_Data, # Removes no status data
+    anti_join(No_Trend_Data, # Removes no Trend data
               by = c("TaxonKey","Territory")
@@
     ) %>% 
-    # Final Species Status Evaluation 
-    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Rebuilding",
+    # Final Catch Trend Evaluation 
+    mutate(Trend = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Rebuilding",
                            ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
@@
     # Select onlyZ 
-    Status_Data <- Status_Data %>%
+    Trend_Data <- Trend_Data %>%
       ungroup() %>%
-      select(TaxonKey,Territory,Year, Status)
+      select(TaxonKey,Territory,Year, Trend)
 
@@
     # File name for each species
-    Name <- paste(Save_Path,Spp,"_Status.csv",sep="")
+    Name <- paste(Save_Path,Spp,"_Trend.csv",sep="")
 
     # Save file for each species
-    write_csv(Status_Data,
+    write_csv(Trend_Data,
               Name)
@@
 
-    ### Determine the final status using the top category over the last 10 years
-
-    Determine_Status_Data <- Status_Data %>% 
+    ### Determine the final Trend using the top category over the last 10 years
+
+    Determine_Trend_Data <- Trend_Data %>% 
       filter(Year > 2004) %>% # last 10 years of data (2005-2014)
-      group_by(TaxonKey,Territory,Status) %>%
-      summarise(n_Status= n()) %>%
+      group_by(TaxonKey,Territory,Trend) %>%
+      summarise(n_Trend= n()) %>%
       group_by(TaxonKey,Territory) %>%
-      top_n(1,n_Status)
+      top_n(1,n_Trend)
 
@@
     suppressMessages( # supresses "No duplicate combinations found of: Territ"
-      Duplicates <- Determine_Status_Data %>% 
+      Duplicates <- Determine_Trend_Data %>% 
         ungroup() %>% 
@@
     # In case we have a tide, we use the last year's category
-    Duplicates_Status <- Status_Data %>% 
+    Duplicates_Trend <- Trend_Data %>% 
       filter(Territory %in% Duplicates,
@@
       ungroup() %>%
-      select(TaxonKey,Territory,Status)
-
-    # Build Final Status database
-    Final_Status_Data <- Determine_Status_Data %>% 
+      select(TaxonKey,Territory,Trend)
+
+    # Build Final Trend database
+    Final_Trend_Data <- Determine_Trend_Data %>% 
       filter(!Territory %in% Duplicates) %>% 
-      bind_rows(Duplicates_Status)
+      bind_rows(Duplicates_Trend)
 
     # If both datasets have value RETURN BOTH
-    if(nrow(No_Status_Data) > 0 & nrow(Final_Status_Data) > 0){
-
-      Fun_Result <- bind_rows(No_Status_Data,
-                              Final_Status_Data)
+    if(nrow(No_Trend_Data) > 0 & nrow(Final_Trend_Data) > 0){
+
+      Fun_Result <- bind_rows(No_Trend_Data,
+                              Final_Trend_Data)
     }
 
-    # If only No status data, then just return No Status Data
-    if(nrow(No_Status_Data) > 0 & nrow(Final_Status_Data) == 0){
-      return(No_Status_Data)
+    # If only No trend data, then just return No Trend Data
+    if(nrow(No_Trend_Data) > 0 & nrow(Final_Trend_Data) == 0){
+      return(No_Trend_Data)
     }else{
-      return(Final_Status_Data)
+      return(Final_Trend_Data)
     }
@@
 # Testing
-# Test_1 <- EstSppStatus(Species_List[1],CoorG)
+# Test_1 <- EstSppTrend(Species_List[1],CoorG)
 
@@
 
-### Data Species Status
-
-### Sub routine for Species Status
-
-```{r Spp_Status_Control_Pannel, eval = T, echo = F}
+### Data Catch Trend
+
+### Sub routine for Catch Trend
+
+```{r Spp_Trend_Control_Pannel, eval = T, echo = F}
 
@@
 
-```{r Spp_Status_Sub_Routine, eval = T, echo = F}
+```{r Spp_trend_Sub_Routine, eval = T, echo = F}
 # Needs to have trans species 
-Species_Status <- bind_rows(
+Species_Trend <- bind_rows(
   mclapply(
     Species_List[1:2],
-    FUN = EstSppStatus,
+    FUN = EstCatchTrend,
     Coord = CoorG,  # Gabriels coordinate system for read species dist
     Per_Taxa = T,
-    Save_Path = "Z:/Vicky/Stock_Status/"
+    Save_Path = "Z:/Vicky/Stock_Trend/"
   )
@@
 # Save data
-readr::write_csv(Species_Status,
-                 paste(Results_Path,"Species_Status.csv",sep="")
-)
-# head(Species_Status)
+readr::write_csv(Catch_Trend,
+                 paste(Results_Path,"Species_Trend.csv",sep="")
+)
+# head(Species_Trend)
 ```
@@
   select(-n) %>% 
-  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
+  filter(fishing_entity != "") %>%  # there are three rows with "developing" trend as in, the code
   ungroup() %>% 
@@
 
+# For upload to github
+Clean_Results_Trans %>%
+  left_join(Exploited_Species) %>%
+  select(1,taxon_name,2:5,fishing_entity,un_sub_region) %>%
+  write_csv(.,"Clean_Results_Trans.csv")
+
 # New data produced by Vicky to compare with Teh and Sumaila
@@
 
-# Read Species Status Data (Sub-routine Species Status)
-Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
+# Read Scatch trend Data (Sub-routine Catch Trend)
+Trend_Data <- fread(paste(my_path("R"),"EEZ/Species_Trend.csv", sep ="")) %>% 
   clean_names() %>% 
@@
 
-```{r Status_Plot_Data, eval = F, echo = F}
+```{r Trend_Plot_Data, eval = F, echo = F}
 
@@
 # -------------------------- #
-# Stock status Data
-Status_Data_Plot <- Tresholded_T_Data %>% 
-  left_join(Status_Data, 
+# Stock trend Data
+Trend_Data_Plot <- Tresholded_T_Data %>% 
+  left_join(Trend_Data, 
             by =c("eez_name","taxon_key")
   ) %>%
-  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
-  group_by(fishing_entity,status) %>% 
+  mutate(trend = ifelse(is.na(trend),"No Trend",trend)) %>% 
+  group_by(fishing_entity,trend) %>% 
   summarise(value = length(unique(taxon_key))) %>% 
@@
   ) %>% 
-  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
+  select(individual = fishing_entity,observation = trend,group = Georegion,value) %>% 
   arrange(group,value) %>% 
@@
 
-length(unique(Status_Data_Plot$individual))
-length(unique(Status_Data_Plot$observation))
-
-Status_Plot_Data <- tibble(
-  fishing_entity = rep(unique(Status_Data_Plot$individual),4),
-  observation = rep(unique(Status_Data_Plot$observation),157)
+length(unique(Trend_Data_Plot$individual))
+length(unique(Trend_Data_Plot$observation))
+
+Trend_Plot_Data <- tibble(
+  fishing_entity = rep(unique(Trend_Data_Plot$individual),4),
+  observation = rep(unique(Trend_Data_Plot$observation),157)
 ) %>% 
@@
   rename(individual = fishing_entity) %>% 
-  full_join(Status_Data_Plot,
+  full_join(Trend_Data_Plot,
             by = c("individual","observation")
@@
 
-T_Summary <- Status_Data_Plot %>% 
+T_Summary <- Trend_Data_Plot %>% 
   mutate(value = ifelse(value <0, value*-1,value)) %>% 
@@
 
-Discrete_Status_Data <- Discrete %>% 
-  left_join(Status_Data, 
+Discrete_Trend_Data <- Discrete %>% 
+  left_join(Trend_Data, 
             by =c("eez_name","taxon_key")
   ) %>%
-  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
-  group_by(fishing_entity,status) %>% 
+  mutate(trend = ifelse(is.na(trend),"No Trend",trend)) %>% 
+  group_by(fishing_entity,trend) %>% 
   summarise(value = length(unique(taxon_key))) %>% 
@@
 
-D_Summary <- Discrete_Status_Data %>% 
+D_Summary <- Discrete_Trend_Data %>% 
   mutate(value = ifelse(value <0, value*-1,value)) %>% 
@@
 
-Exclusive_Discrete_Status_Data <- Discrete_Exclusive %>% 
-  left_join(Status_Data, 
+Exclusive_Discrete_Trend_Data <- Discrete_Exclusive %>% 
+  left_join(Trend_Data, 
             by =c("eez_name","taxon_key")
   ) %>%
-  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
-  group_by(fishing_entity,status) %>% 
+  mutate(trend = ifelse(is.na(trend),"No Trend",trend)) %>% 
+  group_by(fishing_entity,trend) %>% 
   summarise(value = length(unique(taxon_key))) %>% 
@@
 # Set a number of 'empty bar' to add at the end of each Georegion
-Char <- as.factor(Status_Plot_Data$group) # Set groups to factors
+Char <- as.factor(Trend_Plot_Data$group) # Set groups to factors
 
@@
 # Transform data in a tidy format (long format)
-# data <- Status_Data_Plot
+# data <- Trend_Data_Plot
 
@@
 empty_bar <- 2
-nObsType <- nlevels(as.factor(Status_Plot_Data$observation))
-to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Plot_Data)) )
-colnames(to_add) <- colnames(Status_Plot_Data)
+nObsType <- nlevels(as.factor(Trend_Plot_Data$observation))
+to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Trend_Plot_Data)) )
+colnames(to_add) <- colnames(Trend_Plot_Data)
 to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
-Status_Plot_Data <- rbind(Status_Plot_Data, to_add) # Problem converts to list
-# Status_data <- bind_rows(data,to_add)
-Status_Plot_Data <- Status_Plot_Data %>% arrange(group, individual)
-Status_Plot_Data$id <- rep( seq(1, nrow(Status_Plot_Data)/nObsType) , each=nObsType)
+Trend_Plot_Data <- rbind(Trend_Plot_Data, to_add) # Problem converts to list
+# Trend_data <- bind_rows(data,to_add)
+Trend_Plot_Data <- Trend_Plot_Data %>% arrange(group, individual)
+Trend_Plot_Data$id <- rep( seq(1, nrow(Trend_Plot_Data)/nObsType) , each=nObsType)
 
@@
 
-# Status_data <- Status_Data_Plot %>%
+# Trend_data <- Trend_Data_Plot %>%
 #   bind_rows(to_add) %>%
@@
 # Get the name and the y position of each label
-label_data <- Status_Plot_Data %>% 
+label_data <- Trend_Plot_Data %>% 
   # filter(value > 0) %>% 
@@
 # prepare a data frame for base lines
-base_data <-  Status_Plot_Data %>% 
+base_data <-  Trend_Plot_Data %>% 
   group_by(group) %>% 
@@
 
-Status_Plot_Data %>%
+Trend_Plot_Data %>%
   ggplot() + 
@@
   # filename = "Plot.png"
-  filename = "Territory_circular_status.png"
+  filename = "Territory_circular_trend.png"
 )
@@
 
-### Statistical differences between species status
+### Statistical differences between Catch Trend
 
@@
 # Transboundary Data
-Transboundary_Data_Stats <- Status_Plot_Data %>% 
+Transboundary_Data_Stats <- Trend_Plot_Data %>% 
 filter(observation != "No Category") %>%
@@
 # Discrete Data (trans.not shared)
-Trans_Dis_Data_Stats <- Discrete_Status_Data %>% 
+Trans_Dis_Data_Stats <- Discrete_Trend_Data %>% 
   filter(observation != "No Category") %>%
@@
 # Discrete Data (just desrete and not trans.not shared)
-Discrete_Data_Stats <- Exclusive_Discrete_Status_Data %>% 
+Discrete_Data_Stats <- Exclusive_Discrete_Trend_Data %>% 
   filter(observation != "No Category") %>%

### 2020-09-24 Scripts/Manuscript_Draft.Rmd
Addressed second round of reviews

@@
 
-* **Corresponding author**: j.palacios@oceans.ubc.ca
+**Corresponding** author: j.palacios@oceans.ubc.ca
 
@@
 Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% **of the species analyzed** are transboundary (n = 633).
+We found that 67% of the species analyzed are transboundary (n = 633).
 Between 2005 and 2014, fisheries targeting these species within the global-EEZs caught in average 48 million tonnes representing an average of USD 77 billion in fishing revenue per year.
 Some countries received over 90% of their catch and economic benefits from a few shared resources.
-Our analysis suggests that catches from transboundary species appear **to be declining** more than those from non-transboundary species.
-Our study has direct implications **for managing** fisheries of transboundary species, highlighting the need for strengthened international cooperation.
+Our analysis suggests that catches from transboundary species appear to be declining more than those from non-transboundary species.
+Our study has direct implications for managing fisheries of transboundary species, highlighting the need for strengthened international cooperation.
 
@@
 Fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries while such delineation often does not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The officialization of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries **from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].** However, the boundaries of EEZs cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl.
-**Shared stocks can be classified as three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that, cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
-Here, our study focuses on the "transboundary" and "straddling" species that are exploited by fisheries operating within EEZs.**
+The **acknowledgement** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
+However, the boundaries of EEZs cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl.
+Shared stocks can be classified as three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that, cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
+Here, our study focuses on the "transboundary" and "straddling" species that are exploited by fisheries operating within EEZs.
 
 Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].
-**For instance,** climate-driven changes in species distributions have led to conflicts between nations that were driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+For instance, climate-driven changes in species distributions have led to conflicts between nations that were driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
 Moreover, climate change is likely to exacerbate these types of conflict and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and for fisheries management [@Miller:2013iv].
@@
 
-Forty years after the formal adoption of UNCLOS **and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species that are shared by neighboring nations are still unclear.
+Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling **and highly migratory** resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species that are shared by neighboring nations are still unclear.
 With limited biogeographical data, an informed guess suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
-Literature review undertaken by a more recent study included 344 shared taxa and the historical contributions to fisheries [@Teh:2015gd].** However, these previous studies did not include species' biogeography in the quantification of transboundary stocks.
+Literature review undertaken by a more recent study included 344 shared taxa and the historical contributions to fisheries [@Teh:2015gd].
+However, these previous studies did not include species' biogeography in the quantification of transboundary stocks.
 Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
@@
 
-We overlaid the known distribution of 938 commercially valuable marine species that are responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 280 EEZs of 198 coastal **countries (See methods**).
+We overlaid the known distribution of 938 commercially valuable marine species that are responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 280 EEZs of 198 coastal countries (See methods).
 We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units), due to a lack of such biological information for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level **(or even as groups containing multiple species).
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level (or even as groups containing multiple species).
 For example, shrimps (e.g.
-Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] include multiple populations that are exploited by each country’s fisheries, but they are managed at the species level in both cases.** Also, recent research has suggested strong connectivity between fish stocks, even when separated by thousands of kilometers [@Ramesh:2019va] through larval dispersal and **adult migration e.g.
-fishing migrating between reefs in neighboring EEZs [@Levin:2018in].
-Such ecological connectivity further highlights to the importance of accounting for transboundary stocks using biogeographical information and making the results relevant from a fisheries management perspective**.
-For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
+Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] include multiple populations that are exploited by each country’s fisheries, but they are managed at the species level in both cases.
+**Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
+Such ecological connectivity further highlights to the importance of accounting for transboundary stocks using biogeographical information and making the results relevant from a fisheries management perspective.** For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
 we did not include the high seas).
@@
 
-**We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].** Between 2005 and 2014, national fleets targeting these transboundary species within EEZs **caught** an **annual** average of 48.5 million tonnes, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
+We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
 1A).
-These catches generated **a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) during the same time period.** These values are more than the previously estimated 34.2 million tonnes in catches and USD 40,187 million (**in 2019 value**) in fishing revenue from shared stocks [@Teh:2015gd].**When we re-estimated the transboundary species’ catches using catch data that are consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species we identified here accounted for 40.4 million tonnes of catches i.e., 18% higher than previously estimates.
-Our results suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated due to an incomplete knowledge on the transboundary nature of marine fished species.** The 305 species that are considered non-transboundary (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) contributed a much smaller proportion of catches and revenues compared to those from the 633 transboundary species identified in this study.
-These discrete species represented only **an annual average of** 2.8 million tonnes and 4,282 million USD between 2005 and 2014.
+These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) during the same time period.
+These values are more than the previously estimated 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using catch data that are consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species we identified here accounted for 40.4 million tonnes of catches i.e., 18% higher than previously estimates.
+Our results suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated due to an incomplete knowledge on the transboundary nature of marine fished species.
+The 305 species that are considered non-transboundary (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) contributed a much smaller proportion of catches and revenues compared to those from the 633 transboundary species identified in this study.
+These discrete species represented only an annual average of 2.8 million tonnes and 4,282 million USD between 2005 and 2014.
 These results underscore the importance of transboundary species at the global level.
@@
 
-![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue.
+![Figure 1.
+Number of transboundary species and their contribution to global fisheries catches and revenue.
 A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 
-In many cases, according to our categorization criteria, a transboundary species can distribute in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
 For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans over the EEZs of Peru, Chile, and Ecuador.
 However, our study only counted the transboundary stocks in Peru and Chile [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range **(spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3)** and thus do not meet our criteria to be considered as transboundary stock.
-Situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria to be considered as transboundary stock.
+**A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
 Overall, 590 of the 633 transboundary species have stocks in EEZs that are excluded from being counted as transboundary because they do not meet all our categorization criteria.
-The **annual average contribution from all the excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014** was 10.8 million tonnes, representing USD 19,243 million in fishing revenue **over the same time period.**
+The annual average contribution from all the excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
 
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (**average country** revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD) (Fig.
+We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (average country revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD) (Fig.
 1B).
-The estimated **per country** revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
-China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the **annual average** revenues from 2005 to 2014  in **Eastern** Asia and **Northern America**, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 **million**) and Japan (USD 3,907 **million**) are among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
+The estimated per country revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
+China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenues from 2005 to 2014  in Eastern Asia and Northern America, respectively.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) are among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
 1A).
@@
 S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the **national** transboundary species production.
+Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the national transboundary species production.
 Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-**Similarly, Russia, Japan and the USA have made a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea since 1988 [@NOAA:gX6CtUTk].** Transboundary species also contribute largely to fisheries in **Eastern** Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-Particularly, China the world's top fish producer [@FAO:2018KK] **gets** one third (5.1 million tonnes) of the total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
+Similarly, Russia, Japan and the USA have made a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea since 1988 [@NOAA:gX6CtUTk].
+Transboundary species also contribute largely to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+Particularly, China the world's top fish producer [@FAO:2018KK] gets one third (5.1 million tonnes) of the total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
 Differences in transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
@@
 As an example, the aggregated area of all EEZs of Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
-However, it has the second **highest average** revenue (USD 26.1 thousand per $km^2$) and the **highest average** catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
+However, it has the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
 Countries from Western Europe get significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05).
@@
 
-**We determined the catch trend of each species within each EEZ classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
+We determined the catch trend of each species within each EEZ classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
 3).
@@
 We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-Overall, transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
+Overall, transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2).
 
@@
 For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
-Atlantic Mackerel is a transboundary species that **straddles into the high seas**.
+Atlantic Mackerel is a transboundary species that straddles into the high seas.
 Amongst the countries involved in the 2007 Atlantic mackerel fisheries dispute, mackerel contributed an annual average (between 2005 and 2014) of 598.4 thousand tonnes (8.19%) to these countries’ total catches and USD 850.2 million (7.17%) to their total fishing revenue.
@@
 Exploring the detailed effects of climate change in the distribution of shared species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
-**.
-For example, understanding how climate change will modify the proportion of transboundary species that each neighboring EEZ share31, the time-frame at when the changes in sharing will happen, and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@RashidSumaila:tp]**
+For example, understanding how climate change will modify the proportion of transboundary species that each neighboring EEZ share, the time-frame at when the changes in sharing will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp]
 
@@
 4A).
-**This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
+This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
 Many pelagic-oceanic species are highly migratory and straddle across one EEZ to another while crossing the high seas.
@@
 4A).
-Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).**
+Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
 
@@
 Note that there could be > 5 species due to similar sharing values.
-** The category "Other" consists of species that have no classification according to FishBase.
-Figure created using R version 3.5.2.**](../Figures/Fig4.png)
+The category "Other" consists of species that have no classification according to FishBase.
+Figure created using R version 3.5.2.](../Figures/Fig4.png)
 
-**Many transboundary species are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
+Many transboundary species are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
 Belone belone) (Fig.
@@
 For instance some of the top countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-4B**) are among the highest fish consumption countries [@FAO:2018KK].
+4B) are among the highest fish consumption countries [@FAO:2018KK].
 In countries like the Philippines both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
@@
 Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated**[@Teh:2015gd]**.
+Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated[@Teh:2015gd].
 This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
-Moreover, we show significant differences in **the catch trends** of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
+Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
 Previous work has found that collaboration will result in better outcomes for shared marine resources [@Munro:2002uf].
@@
 
-**The Sea Around Us has reconstructed global fisheries catches from 1950 to 2014 identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
+The Sea Around Us has reconstructed global fisheries catches from 1950 to 2014 identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
 We used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
-The total number of species analyzed was 938 representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.** To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
-Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result **than using only one data source**.
+The total number of species analyzed was 938 representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
+Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result than using only one data source.
 Only commercial fished species with data from all four sources were included in the analysis.
@@
 
-Occurrence data was collected **by Reygondeau (2019)** from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+Occurrence data was collected by Reygondeau (2019) from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
 
@@
 Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
-Global environmental conditions were average for the **30-year climate normal period of 1970-2000** and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+Global environmental conditions were average for the 30-year climate normal period of 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
 See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
@@
 Catches are also spatially allocated on a $0.5^{\circ}$ x $0.5^{\circ}$ latitude longitude grid [@Zeller2016].
-**Roughly, the Sea Around Us method takes each country's officially reported catch data (e.g.
+Roughly, the Sea Around Us method takes each country's officially reported catch data (e.g.
 National, FAO or RFMO).
@@
 It then derives country estimates for missing data and creates time series interpolation.
-Finally, the estimated and official data are aggregated for a total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.)** We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the **last decade of available data**) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
+Finally, the estimated and official data are aggregated for a total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.) We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
 Note that in call cases we report the average catch from 2005 to 2014.
@@
 
-We developed a **three**-criteria methodology to determine whether or not a species can be considered transboundary.
+We developed a three-criteria methodology to determine whether or not a species can be considered transboundary.
 Only species that meet all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
@@
 Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
-The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), **noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic) including islands territories**, and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
+The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic) including islands territories, and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
 When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g.
@@
 
-**We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells.
+We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells.
 All analyses only considered cases where all databases matched to obtain a more conservative estimate of transboundary species.
@@
 This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decade of data (2005 - 2014), thus validating the models and only selected "current" shared species.
-We acknowledge that this criteria might limit the global distribution of species thus resulting in a conservative estimate of transboundary species.**
+We acknowledge that this criteria might limit the global distribution of species thus resulting in a conservative estimate of transboundary species.
 
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-**While a species that has less than the selected threshold is not considered transboundary in this paper**, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Supplementary Fig.
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Supplementary Fig.
 S2).
@@
 
-We estimated the economic contribution in **2019** real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
+We estimated the economic contribution in 2019 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
 The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g.
 similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-**The dataset is harmonized with the SAU catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs of this study (http://www.seaaroundus.org/data/#/feru).
+The dataset is harmonized with the SAU catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs of this study (http://www.seaaroundus.org/data/#/feru).
 We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.
@@
 We used the monthly average US Consumer Price Index (CPI) according to the U.S.
-Bureau of Labor Statistic (https://www.bls.gov/cpi/) to standardize the original 2010 real USD value to 2019 real USD.**
+Bureau of Labor Statistic (https://www.bls.gov/cpi/) to standardize the original 2010 real USD value to 2019 real USD.
 
-We used the catch data to determine the **catch trend** of each species within an EEZ.
+We used the catch data to determine the catch trend of each species within an EEZ.
 Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies, **and fishing effort) affects catches** [@Pauly:2013gs; @Branch:2008kk].
+temperature, markets, fishing policies, and fishing effort) affects catches [@Pauly:2013gs; @Branch:2008kk].
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
@@
 year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are **increasing in catch, Category B would be species that have a constant catch rate, and Category C would be species that have seen a decrease in catch in the last 10 years.
-Finally, we reported the predominant category over the time period considered.**
+Following this concept, Category A would represent fisheries that are increasing in catch, Category B would be species that have a constant catch rate, and Category C would be species that have seen a decrease in catch in the last 10 years.
+Finally, we reported the predominant category over the time period considered.
 
@@
 Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
-We limited the distribution of a species by defining transboundary only between neighboring countries (e.g.
+**It is important to ackonwledge, however, that there is considerable uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species that span over multiple jurisdictions and the high seas such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] compromising management decisions based on meta-populations [@Moore:2020cd].** Here, we limited the distribution of a species by defining transboundary only between neighboring countries (e.g.
 US and Canada) and did not include countries that were separated by another country (e.g.
@@
 # Additional Information  
-**Competing interests**: The author(s) declare no competing interests.
+Competing interests: The author(s) declare no competing interests.
 
@@
 
-<!-- We found significant differences in catch trends based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).**Transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2)**.
+<!-- We found significant differences in catch trends based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).Transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2).
 While no significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), significant differences in catch trends for the 305 discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$p = 0.05).

### 2020-09-28 Scripts/Manuscript_Draft.Rmd
Second round of revissions

@@
 ---
-title: "Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
+title: "The transboundary nature of the world’s exploited marine species"
+author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette C.C. Wabnitz^1,3,4^ and William W.L. Cheung^1^"
 date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
 ^2^Yale University, New Haven, Connecticut, USA.
-^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden."
-# subtitle: "Most neighbor nations share marine exploited species"
+^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden.
+^4^Center for Ocean Solutions, Stanford University, Stanford, United States"
+# subtitle: "WORKING PAPAER. PLEASE DO NOT SHARE"
 output:
@@
 
-Regulatory boundaries and species distributions are often not aligned, especially in the case of marine species crossing multiple Exclusive Economic Zones (EEZs).
-This represents a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
+Regulatory boundaries and species distributions often do not align.
+This is especially the case of marine species crossing multiple Exclusive Economic Zones (EEZs).
+Such movements represent a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
 Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
 We found that 67% of the species analyzed are transboundary (n = 633).
-Between 2005 and 2014, fisheries targeting these species within the global-EEZs caught in average 48 million tonnes representing an average of USD 77 billion in fishing revenue per year.
-Some countries received over 90% of their catch and economic benefits from a few shared resources.
-Our analysis suggests that catches from transboundary species appear to be declining more than those from non-transboundary species.
-Our study has direct implications for managing fisheries of transboundary species, highlighting the need for strengthened international cooperation.
+Between 2005 and 2014, fisheries targeting these species within global-EEZs caught on average 48 million tonnes per year, equivalent to an average of USD 77 billion in annual fishing revenue.
+For select countries, over 90% of their catch and economic benefits were attributable to a few shared resources.
+Our analysis suggests that catches from transboundary species are declining more than those from non-transboundary species.
+Our study has direct implications for managing fisheries on transboundary species, highlighting the need for strengthened effective international cooperation.
 
@@
 
-Distributions of marine species around the world are not constrained by human-made boundaries; rather they are shaped by biotic and abiotic factors as well as the species' evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
+Distributions of marine species around the world are not constrained by human-made boundaries; rather they are shaped by biotic and abiotic factors as well as species' evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk].
 A species can be widely distributed (cosmopolitan) or endemic [@Nelson:2016kk].
-Fisheries management is predicated on the definition of “stocks” that, in most cases, are delineated by human-made spatial boundaries while such delineation often does not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The **acknowledgement** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
-However, the boundaries of EEZs cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl.
-Shared stocks can be classified as three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that, cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
-Here, our study focuses on the "transboundary" and "straddling" species that are exploited by fisheries operating within EEZs.
+Fisheries management is predicated on the definition of “stocks”, delineated, in most cases by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
+The **development** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
+However, EEZ boundaries cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
+Shared stocks can be classified into three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
+Our study focuses on the "transboundary" nature of shared species exploited by fisheries operating within EEZs.
 
-Theories and empirical experience have shown that fisheries targeting resources that straddle between political boundaries complicate fisheries management and potentially reduce its effectiveness to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].
-For instance, climate-driven changes in species distributions have led to conflicts between nations that were driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
-Moreover, climate change is likely to exacerbate these types of conflict and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and for fisheries management [@Miller:2013iv].
-Therefore, having an accurate understanding of the distribution and scale of transboundary and straddling fish stocks and fisheries is important to inform their sustainable management, particularly under climate change.
+Theories and empirical evidence have shown that fisheries targeting resources that straddle political boundaries complicate fisheries management and potentially reduce the effectiveness of policies to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].
+For instance, climate-driven changes in species distributions have led to conflicts between nations driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+Moreover, climate change is likely to exacerbate such conflicts and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and fisheries management [@Miller:2013iv].
+Therefore, having an accurate understanding of the distribution and scale of transboundary and straddling fish stocks as well as associated fisheries is important to inform their sustainable management, particularly under climate change.
 
-Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling **and highly migratory** resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species that are shared by neighboring nations are still unclear.
-With limited biogeographical data, an informed guess suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
-Literature review undertaken by a more recent study included 344 shared taxa and the historical contributions to fisheries [@Teh:2015gd].
-However, these previous studies did not include species' biogeography in the quantification of transboundary stocks.
-Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue.
-Moreover, we categorize species according to their catch trends while identifying the differences between species by habitat preference.
-We hypothesize that the methodological constraints of previous studies has resulted in an underestimation of the number of transboundary stocks and their contribution to global catch and revenue.
+Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling **and highly migratory** resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
+An informed guess based on limited biogeographical data, suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
+A recent literature review included 344 shared taxa and their historical contributions to fisheries [@Teh:2015gd].
+However, these studies did not consider species' biogeography in the quantification of transboundary stocks.
+Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catches aas well as fisheries revenue.
+Moreover, we categorize species according to their catch trends while identifying the differences among species based on habitat preference.
+We hypothesize that the methodological constraints of previous studies resulted in an underestimation of the number of transboundary stocks and their contribution to global catch and revenue.
 
-We overlaid the known distribution of 938 commercially valuable marine species that are responsible for an average of 96.5% of global EEZ catch reconstructed by the *Sea Around Us* at the species level between 2005 and 2014, and 280 EEZs of 198 coastal countries (See methods).
-We define a ‘stock’ unit as a species in an EEZ, instead of using a population ecology definition (genetically or morphological distinct units), due to a lack of such biological information for almost all the species included in this study [@Teh:2015gd].
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catches between 2005 and 2014, and 280 EEZs of 198 coastal countries (See methods).
+We define a ‘stock’ unit as a species in an EEZ, instead of a genetically or morphological distinct units [@Nelson:2016kk], due to a lack of such biological information for almost all the species included in this study [@Teh:2015gd].
 While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level (or even as groups containing multiple species).
-For example, shrimps (e.g.
-Litopenaeus stylirostris or Farfantepenaeus californiensis) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] include multiple populations that are exploited by each country’s fisheries, but they are managed at the species level in both cases.
-**Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
-Such ecological connectivity further highlights to the importance of accounting for transboundary stocks using biogeographical information and making the results relevant from a fisheries management perspective.** For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
+For example, shrimp (e.g.
+*Litopenaeus stylirostris* or *Farfantepenaeus californiensis*) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] are managed at the species level in both cases, yet include multiple populations exploited by each country’s fisheries.
+**Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].** For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
 we did not include the high seas).
-We rely on multiple data sources including occurrence, distribution models and catch data and only consider a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods).
+We rely on multiple data sources including occurrence, distribution models and catch data and only consider a species to be present in a grid cell if all data sources showed positive occurrence (see Methods).
 
@@
 
-We identified 633 transboundary exploited species in the world (67.5% of the 938 species analyzed), almost double the previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of the EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
-1A).
-These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) during the same time period.
-These values are more than the previously estimated 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using catch data that are consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species we identified here accounted for 40.4 million tonnes of catches i.e., 18% higher than previously estimates.
-Our results suggests that the participation of transboundary species in global catch and fishing revenue might have been previously underestimated due to an incomplete knowledge on the transboundary nature of marine fished species.
-The 305 species that are considered non-transboundary (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) contributed a much smaller proportion of catches and revenues compared to those from the 633 transboundary species identified in this study.
-These discrete species represented only an annual average of 2.8 million tonnes and 4,282 million USD between 2005 and 2014.
+We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
+1a).
+These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) over the same time period.
+Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
+Our results suggests that the contribution of transboundary species to global catch and fishing revenue might have been previously underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
+The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
 These results underscore the importance of transboundary species at the global level.
 
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catches and revenue.
-A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-B) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions according to the United Nations sub-regions.
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+b) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions classified according to the United Nations sub-regions.
 Points = mean +- sd.
@@
 ![Figure 1.
-Number of transboundary species and their contribution to global fisheries catches and revenue.
-A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-B) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions according to the United Nations sub-regions: E.
+Number of transboundary species and their contribution to global fisheries catch and revenue.
+a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+b) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions classified according to the United Nations sub-regions: E.
 = Eastern, N.
@@
 In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
-For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans over the EEZs of Peru, Chile, and Ecuador.
-However, our study only counted the transboundary stocks in Peru and Chile [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria to be considered as transboundary stock.
+For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
+However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
 **A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
-Overall, 590 of the 633 transboundary species have stocks in EEZs that are excluded from being counted as transboundary because they do not meet all our categorization criteria.
-The annual average contribution from all the excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
+Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
+The annual average contribution from all excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
 
-We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America (average country revenue = 4,680 $\pm$ 6,000 million USD) and Eastern Asia (3,779 $\pm$ 3,093 million USD) (Fig.
-1B).
-The estimated per country revenues from transboundary species in these two regions are significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
-China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenues from 2005 to 2014  in Eastern Asia and Northern America, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) are among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
-1A).
+At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Fig.
+1b).
+The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
+China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
+1a).
 These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
 
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], caught on average between 2005 and 2014 over 5.8 million tonnes by each country on average between 2005 and 2014 (Supplementary Fig.
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], each responsible for over 5.8 million tonnes annually, on average, between 2005 and 2014  (Supplementary Fig.
 S1).
-Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the national transboundary species production.
-Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp].
-Similarly, Russia, Japan and the USA have made a management agreement over Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea since 1988 [@NOAA:gX6CtUTk].
-Transboundary species also contribute largely to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-Particularly, China the world's top fish producer [@FAO:2018KK] gets one third (5.1 million tonnes) of the total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
-Differences in transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
+Peru's catches consist mainly of Peruvian anchoveta (*Engraulis ringens*) and account for 79% of the national transboundary species production.
+Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp].
+A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
+Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
+Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
 2).
-As an example, the aggregated area of all EEZs of Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
-However, it has the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-Countries from Western Europe get significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Fig.
+2).
 
@@
 Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
-A) Revenue in thousand 2019 USD.
-B) Catch in tonnes.
+a) Revenue in thousand 2019 USD.
+b) Catch in tonnes.
 Points are sub-region averages $\pm$ s.d.
 by country.
-Figure created using R version 3.5.2.](../Figures/Fig2.png)
+Figure created using R version 3.5.2.
+Abbreviations as in Figure 1.](../Figures/Fig2.png)
 
-We determined the catch trend of each species within each EEZ classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
+We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
 3).
-While previous studies demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Therefore, our intention here is to examine where the catch trends of transboundary species are different from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
-We found significant differences within all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001) as opposite to discrete species where no significant differences where registered (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
+While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
+Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
+We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
 We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-Overall, transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2).
+Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Supplementary Table S2).
 
@@
 Number of transboundary species by catch trend and EEZ.
-Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend.“No Category” reflect species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
 Figure created using R version 3.5.2.](../Figures/Fig3.png)
 
-Empirical analysis suggests that in most cases, management of transboundary species will have better outcomes in terms of fish yields when nations cooperate [@Munro:2002uf].
-Examples of successful cooperative-management include Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and create conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
-Yet, we acknowledge that cooperation or lack thereof can be a complex process [@Jensen:2015cf], and that there are specific cases where cooperation might not be the best strategy [@Munro:2015df].
+Empirical analysis suggests that in most cases, management of transboundary species will yield better outcomes in terms of fish catches when nations cooperate [@Munro:2002uf].
+Yet, cooperation can be a complex process [@Jensen:2015cf] with specific cases where joint management might not be the best strategy [@Munro:2015df].
+Examples of successful joint management include agreements between Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and result in conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+
 <!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
@@
 
-Transboundary fisheries are abundant and of economic importance for some of the top countries with past fisheries-related conflicts including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to a climate-driven distribution shift [@Spijkers:2017ij].
+Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to the species climate-driven shift in distribution [@Spijkers:2017ij].
 Atlantic Mackerel is a transboundary species that straddles into the high seas.
-Amongst the countries involved in the 2007 Atlantic mackerel fisheries dispute, mackerel contributed an annual average (between 2005 and 2014) of 598.4 thousand tonnes (8.19%) to these countries’ total catches and USD 850.2 million (7.17%) to their total fishing revenue.
-Climate change is expected to continue changing the distribution and share proportion of fish stocks among countries up to a degree that new transboundary species will emerge [@Pinsky:2018cb], while some species will exit EEZs [@Oremus:2020id].
-Exploring the detailed effects of climate change in the distribution of shared species is key to develop local adaptation methods to anticipate negative impacts to sustainability.
-For example, understanding how climate change will modify the proportion of transboundary species that each neighboring EEZ share, the time-frame at when the changes in sharing will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp]
+Amongst the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) 598.4 thousand tonnes (8.19%) in total catchs and USD 850.2 million (7.17%) in total fishing revenue.
+Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
+Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
+For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
 
-Over 130 marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk], from highly migratory species associated to pelagic-oceanic ecosystem like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), to species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
 Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-4A).
+4a).
 This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
-Many pelagic-oceanic species are highly migratory and straddle across one EEZ to another while crossing the high seas.
-Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, like the case of bigeye tuna (Thunnus obesus) (Fig.
-4A).
-Due to their large migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
+Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Fig.
+4a).
+Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
 
@@
 Number of EEZs shared by transboundary species.
-A) Number of EEZs by species organized by associated habitat according to FishBase.
+a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
 Showing only species that share > 20 EEZs.
-B) Average catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on a).
+b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
 Note that there could be > 5 species due to similar sharing values.
-The category "Other" consists of species that have no classification according to FishBase.
+The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
 Figure created using R version 3.5.2.](../Figures/Fig4.png)
 
-Many transboundary species are not considered highly migratory but still shared by numerous neighboring EEZs (e.g.
-Belone belone) (Fig.
-4A).
+Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g.
+garfish *Belone belone*) (Fig.
+4a).
 In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
-For example, despite coral reef-related species being among the less shared neighboring EEZs identified in this study (Fig.
-4A), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-Species with narrower ranges are often managed at the national level due to localized populations [@Payne:2008vm] but the potential boundary-crossing of these species must not be ignored.
-In some areas like the Caribbean and the Western Indian Ocean, transboundary marine protected areas have been identified as potential tools for achieving fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
-The proper management of coral reef species is very important for many coastal communities, particularly in developing regions, that are highly dependent on subsistence fishing for food security and livelihoods [@CisnerosMontemayor:2016gq; @Wabnitz:2018gf].
-For instance some of the top countries fishing transboundary reef and pelagic-oceanic associated species (Fig.
-4B) are among the highest fish consumption countries [@FAO:2018KK].
-In countries like the Philippines both pelagic and reef fishes contribute substantially to both local food security and livelihood [@Cabral:2018hc].
+For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Fig.
+4a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+However, **it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].** In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
+The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
+For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Fig.
+4b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
+In the Philippines both pelagic and reef fishes contribute substantially to both local food and nutrition security as well as livelihoods [@Cabral:2018hc].
 
@@
 
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species' contribution to global capture and revenue from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than those from discrete species, as well as than previously estimated[@Teh:2015gd].
-This result highlights the importance of transboundary fisheries and their potential contribution to food security and wellbeing.
-Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need for improving the management of transboundary fisheries.
-Previous work has found that collaboration will result in better outcomes for shared marine resources [@Munro:2002uf].
-Thus, countries should pay specific attention in the management of the identified transboundary stocks potentially creating collaborative management plans.
-Identifying existing transboundary species is the first step towards joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
+Our results show that captures and revenues from shared species are substantially higher than previously estimated[@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
+This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.
+Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
+Previous work has highlighted that collaboration is key to better outcomes for shared marine resources [@Munro:2002uf].
+Identifying existing transboundary species is the first step towards cooperative joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
 
@@
 
-The Sea Around Us has reconstructed global fisheries catches from 1950 to 2014 identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
-We used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
-The total number of species analyzed was 938 representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.
+The *Sea Around Us* has reconstructed global fisheries catches from 1950 to 2014, identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
+We used the *Sea Around Us* reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
+The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
 To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
-Each source represents a different method of estimating the distribution of a given species and thus, provides a more robust result than using only one data source.
-Only commercial fished species with data from all four sources were included in the analysis.
+Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
+Only commercial fished species with data from all four sources were included in our analysis.
 
@@
 The range is delimited even further by expert-review polygons and compared with that of AquaMaps [@Kaschner:2016tl], OBIS and GBIF occurrence data.
-The model then determines a species habitat preference based on the assumption that the relative abundance of a species is determined by the number of habitats in a grid cell and the distance of the species to each habitat, as well as the importance of the habitat to the species size.
-Finally, the species equatorial submergence (e.g.
-the latitudinal region where a species is not seen in between poles) is estimated for each species.
+The model then determines a species' habitat-preference based on the assumption that the relative abundance of a species is determined by the number of habitats in a grid cell and the species' distance to each habitat, as well as the importance of the habitat to the total size of the species distribution.
+Finally, the species equatorial submergence (e.g., the latitudinal region where a species is not seen in between poles) is estimated for each species.
 See [@Close:2006ux; @Pauly:2016uz] for model details.
@@
 However, this does not mean that the species in question will actually be there.
-While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SPD-SAU undertakes validation by means of other models), we used a fourth data source to corroborate the models’ outputs.
+While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SDM-SAU undertakes validation by means of other models), we used a fourth data set to corroborate the models’ outputs.
 The *Sea Around Us* estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
 Catches are also spatially allocated on a $0.5^{\circ}$ x $0.5^{\circ}$ latitude longitude grid [@Zeller2016].
-Roughly, the Sea Around Us method takes each country's officially reported catch data (e.g.
+Roughly, the *Sea Around Us* method consist of the following steps.
+First, it takes each country's officially reported catch data (e.g.
 National, FAO or RFMO).
@@
 It then derives country estimates for missing data and creates time series interpolation.
-Finally, the estimated and official data are aggregated for a total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details.) We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
+We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
@@
 We developed a three-criteria methodology to determine whether or not a species can be considered transboundary.
-Only species that meet all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
-Note that in some cases a species could meet all criteria for some EEZs, but not for other EEZs, these species were still considered as “transboundary”.
+Only species that met all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
+Note that in cases where a species met all criteria for some EEZs, but not for other EEZs, these species were still considered as “transboundary”.
 
@@
 
-As previously mentioned, we define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
+As mentioned above, we define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
 Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
-The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org), noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic) including islands territories, and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
+The analysis was undertaken only within the boundaries of the EEZs of coastal states using the *Sea Around Us* shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
 When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g.
 USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
-Species that were present in EEZs that were non-continental territories neighboring other countries were kept separately (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
-Associated states like Puerto Rico and Hong Kong were added to their Sovereign (e.g.
-Puerto Rico with the United States and Hong Kong with China).
+Species that were present in EEZs that were non-continental territories neighboring other countries were kept as separate (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
+Associated states like Puerto Rico and New Caledonia were not considered separately (e.g., Puerto Rico was grouped with the United States and New Caledonia with France).
 
@@
 
-We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells.
-All analyses only considered cases where all databases matched to obtain a more conservative estimate of transboundary species.
+We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the world's $0.5^{\circ}$ x $0.5^{\circ}$ marine grid cells.
+All analyses only considered cases with agreement across all databases to obtain a more conservative estimate of transboundary species.
 Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the Sea *Around Us catch* database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
-This rule assumes that if a commercial species is projected within any fishing country, such a species would have been fished, and thus reported at some point over the last decade of data (2005 - 2014), thus validating the models and only selected "current" shared species.
-We acknowledge that this criteria might limit the global distribution of species thus resulting in a conservative estimate of transboundary species.
+This rule assumes that if a commercial species is projected within the EEZ of any fishing country, such a species would have been fished, and thus likely reported at some point over the last decade of data (2005 - 2014), thereby validating the models and selecting "currently" shared species.
+We acknowledge that this criteria might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
 
@@
 Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*.
-The *Area Index* consist in the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
+The *Area Index* represents the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
@@
 similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-The dataset is harmonized with the SAU catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs of this study (http://www.seaaroundus.org/data/#/feru).
-We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.
+The dataset is harmonized with the *Sea Around Us* catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
+We report average fishing revenue derived from fishing activity within global EEZs between 2005 to 2014.
 We did not include revenue from areas beyond national jurisdiction.
@@
 
-We used the catch data to determine the catch trend of each species within an EEZ.
-Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended as catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g.
-temperature, markets, fishing policies, and fishing effort) affects catches [@Pauly:2013gs; @Branch:2008kk].
+We used catch data as described above to determine the catch trend of each species within an EEZ.
+Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended to represent catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g., temperature, markets, fishing policies, and fishing effort) affect catches [@Pauly:2013gs; @Branch:2008kk].
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn for each species depending on the catch volume within each EEZ (e.g.
-present, maximum and minimum EEZ's historical catch) and the year (e.g.
-year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
-Following this concept, Category A would represent fisheries that are increasing in catch, Category B would be species that have a constant catch rate, and Category C would be species that have seen a decrease in catch in the last 10 years.
+Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
+Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
 Finally, we reported the predominant category over the time period considered.
@@
 We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
-In cases where the ANOVA assumptions were not clearly met we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
+In cases where the ANOVA assumptions were not clearly met, we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm results [@Hollander:2013wz].
 
@@
 <!-- # Related to Criteria 1 (neighbors) -->
-We have identified four key uncertainties in the method that may affect the estimation of transboundary species Firstly, we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), therefore we are not able to identify transboundary stocks within EEZs.
+We have identified four key uncertainties in the method utilized that may affect the estimation of transboundary species.
+Firstly, as we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), we are not able to identify transboundary stocks within EEZs.
 While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research has suggested strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis.
-**It is important to ackonwledge, however, that there is considerable uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
-This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species that span over multiple jurisdictions and the high seas such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] compromising management decisions based on meta-populations [@Moore:2020cd].** Here, we limited the distribution of a species by defining transboundary only between neighboring countries (e.g.
-US and Canada) and did not include countries that were separated by another country (e.g.
-Canada and Mexico) and/or the high seas (e.g.
-Canada and Spain).
-Our results are likely a conservative estimation of transboundary species as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
+Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
+**However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].** Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
+Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
 Nevertheless, our results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
-<!-- Related to Criteria 2 (Models) -->
-Secondly, the predicted species distribution is affected by the uncertainties of the environmental data and models used for such predictions.
-Structural differences within Earth System Models results in variations of oceanic conditions, which undoubtedly affect the ENM-Nereus.
-We averaged the results from the three models in an effort to capture the structural variation across models.
-Climate natural variability is a major driver of marine species distribution, potentially removing a species from an EEZ for long periods (e.g.
+Secondly, the predicted species' distribution is affected by the uncertainties of the environmental data and models used for such predictions.
+Structural differences within Earth System Models result in variations of oceanic conditions, which undoubtedly affect the ENM-Nereus.
+We averaged results from the three models in an effort to capture the structural variation across models.
+Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g.
 Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
@@
 This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
-<!-- Related to Criteria 3 (SAU catch data) -->
-Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
-While catch data are not exempt of uncertainty, in most cases, the differences between the Sea Around Us and the FAO self-reported data are smaller towards recent years [@Pauly:2019bf].
+Thirdly, we assumed that, if the*Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+While catch data are not exempt of uncertainty, in most cases, differences between the*Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
 Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
-Likewise, the spatial allocation of the catch is subjected to impressions, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
-<!-- Related to Criteria 4; Spatial distribution -->
-Finally, the results of this study only considered those species that all datasets agree on presence and at least 25% of *Area Index* (e.g.
-the species shared distribution was at least 25% in each EEZ).
-This presents a relative conservative estimate of the number of transboundary species in the world.
-However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Supplementary Fig.
+Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the*Sea Around Us*.
+Finally, this study’s results only considered species for which all datasets agreed on presence and had and *Area Index* of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
+Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
+Using a smaller *Area Index* will result in more transboundary species (Supplementary Fig.
 S2).
@@
 was supported by the EO Wilson foundation.
-C.W.
+C.C.C.W.
 was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
@@
 Methodology, data curation, writing - review & editing.
-C.W.
+C.C.C.W.
 Methodology, writing - review & editing.
@@
 # Data Availability
-The Sea Around Us datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+The *Sea Around Us* datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
 The processed results and code are available at https://github.com/jepa/FishForVisa
@@
 Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
-Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the SAU database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
+Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the*Sea Around Us* database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
 -->

### 2020-10-05 Scripts/Manuscript_Draft.Rmd

@@
 This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
-Thirdly, we assumed that, if the*Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+Thirdly, we assumed that, if the *Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
 While catch data are not exempt of uncertainty, in most cases, differences between the*Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
 Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
-Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the*Sea Around Us*.
+Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the *Sea Around Us*.
 Finally, this study’s results only considered species for which all datasets agreed on presence and had and *Area Index* of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).

### 2020-10-05 Scripts/supplements.Rmd

@@
 ---
-title: "Supplementary information for Marine species do not need visas: the transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes, Gabriel Reygondeau, Colette Wabnitz and William W.L. Cheung"
+title: "Supplementary information for The transboundary nature of the world’s exploited marine species"
+author: "Authors: Juliano Palacios-Abrantes, Gabriel Reygondeau, Colette C.C. Wabnitz and William W.L. Cheung"
 output: pdf_document

### 2020-10-05 Scripts/Initial_Analysis.Rmd

@@
 # For upload to github
-Clean_Results_Trans %>%
-  left_join(Exploited_Species) %>%
-  select(1,taxon_name,2:5,fishing_entity,un_sub_region) %>%
-  write_csv(.,"Clean_Results_Trans.csv")
+# Clean_Results_Trans %>%
+#   left_join(Exploited_Species) %>%
+#   select(1,taxon_name,2:5,fishing_entity,un_sub_region) %>%
+#   write_csv(.,"Clean_Results_Trans.csv")
 
@@
 
-### Data For Map (Fig. 1)
+### Fig. 1 - Data For Map
 
@@
 
-## Weighted bar plots
+## Fig. 2 - Weighted bar plots
 
@@
   distinct(sub_region,.keep_all = TRUE) %>% 
-  write_csv(.,
-            "Table_S1.csv")
+  arrange(Size_Entity_sum)
+  # write_csv(.,
+            # "Table_S1.csv")
 

### 2020-10-05 Scripts/Manuscript_Draft.Rmd
Fixed indexing

@@
 ---
-title: "The transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette C.C. Wabnitz^1,3,4^ and William W.L. Cheung^1^"
-date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
-^2^Yale University, New Haven, Connecticut, USA.
-^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden.
-^4^Center for Ocean Solutions, Stanford University, Stanford, United States"
-# subtitle: "WORKING PAPAER. PLEASE DO NOT SHARE"
 output:
-  word_document:
-    # reference_docx: ./Manuscript_Instructions/science_template.docx
-  pdf_document:
-    fig_caption: yes
+  bookdown::pdf_book:
+    toc : no
+    keep_tex: no
+    number_sections: yes
+    fig_width: 6 
+    fig_height: 4 
 geometry: margin=1in
@@
 csl: ../References/nature_cc.csl
+header-includes: #allows you to add in your own Latex packages
+- \usepackage{float} #use the 'float' package
+- \floatplacement{figure}{H} #make every figure with caption = h
 ---
-
-**Corresponding** author: j.palacios@oceans.ubc.ca
 
@@
 
-<!-- # Instructions for submission -->
-
-<!-- - Journal: *Scientific Reports* -->
-<!-- - Information to authors (https://www.nature.com/srep/author-instructions/submission-guidelines) -->
-<!-- - There are two types of article: -->
-
-<!-- -- Articles should be no more than 11 typeset pages in length.
-As a guide, the main text (not including Abstract, Methods, References and figure legends) should be no more than 4,500 words.
-The maximum title length is 20 words.
-The Abstract (without heading) - which must be no more than 200 words long and contain no references - should serve both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications..
--->
-
-# Abstract
-
-Regulatory boundaries and species distributions often do not align.
-This is especially the case of marine species crossing multiple Exclusive Economic Zones (EEZs).
-Such movements represent a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
-Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the species analyzed are transboundary (n = 633).
-Between 2005 and 2014, fisheries targeting these species within global-EEZs caught on average 48 million tonnes per year, equivalent to an average of USD 77 billion in annual fishing revenue.
-For select countries, over 90% of their catch and economic benefits were attributable to a few shared resources.
-Our analysis suggests that catches from transboundary species are declining more than those from non-transboundary species.
-Our study has direct implications for managing fisheries on transboundary species, highlighting the need for strengthened effective international cooperation.
-
-# Introduction
+## Introduction
 
@@
 
-# Results and Discussion
+### Materials and Methods
 
-We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
-1a).
-These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) over the same time period.
-Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
-Our results suggests that the contribution of transboundary species to global catch and fishing revenue might have been previously underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
-The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
-These results underscore the importance of transboundary species at the global level.
-
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
-a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-b) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions classified according to the United Nations sub-regions.
-Points = mean +- sd.
-Revenue in 2010 real USD"}
-
-img <- readPNG(here("./Figures/Fig1.png"))
-grid.raster(img)
-
-```
-
-![Figure 1.
-Number of transboundary species and their contribution to global fisheries catch and revenue.
-a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-b) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions classified according to the United Nations sub-regions: E.
-= Eastern, N.
-= Northern, S.
-= Southern, W.
-= Western, Ltn.
-Ame.
-& the Car.
-= Latin America and the Caribbean.
-Points = regional  mean ± sd.
-Revenue in 2019 real USD.
-Figure created using R version 3.5.2.
-Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png)
-
-In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
-For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
-However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
-**A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
-Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
-The annual average contribution from all excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
-
-At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Fig.
-1b).
-The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
-China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
-1a).
-These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
-
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], each responsible for over 5.8 million tonnes annually, on average, between 2005 and 2014  (Supplementary Fig.
-S1).
-Peru's catches consist mainly of Peruvian anchoveta (*Engraulis ringens*) and account for 79% of the national transboundary species production.
-Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp].
-A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
-Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
-Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
-2).
-As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
-However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Fig.
-2).
-
-```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
-
-img <- readPNG(here("./Figures/Fig2.png"))
-grid.raster(img)
-```
-
-![Figure 2.
-Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
-a) Revenue in thousand 2019 USD.
-b) Catch in tonnes.
-Points are sub-region averages $\pm$ s.d.
-by country.
-Figure created using R version 3.5.2.
-Abbreviations as in Figure 1.](../Figures/Fig2.png)
-
-We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
-3).
-While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
-We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
-We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Supplementary Table S2).
-
-```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
-
-img <- readPNG(here("./Figures/Fig2.png"))
-grid.raster(img)
-```
-
-![Figure 3.
-Number of transboundary species by catch trend and EEZ.
-Category A, Increasing; Category B, Constant; Category C, Decreasing.
-“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
-Figure created using R version 3.5.2.](../Figures/Fig3.png)
-
-Empirical analysis suggests that in most cases, management of transboundary species will yield better outcomes in terms of fish catches when nations cooperate [@Munro:2002uf].
-Yet, cooperation can be a complex process [@Jensen:2015cf] with specific cases where joint management might not be the best strategy [@Munro:2015df].
-Examples of successful joint management include agreements between Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and result in conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
-
-<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
-However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
--->
-
-Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to the species climate-driven shift in distribution [@Spijkers:2017ij].
-Atlantic Mackerel is a transboundary species that straddles into the high seas.
-Amongst the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) 598.4 thousand tonnes (8.19%) in total catchs and USD 850.2 million (7.17%) in total fishing revenue.
-Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
-Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
-For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
-
-Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-4a).
-This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
-Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
-Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Fig.
-4a).
-Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
-
-```{r Call_Spp_Circular, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
-
-img <- readPNG(here("./Figures/Fig4.png"))
-grid.raster(img)
-```
-
-![Figure 4.
-Number of EEZs shared by transboundary species.
-a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
-Showing only species that share > 20 EEZs.
-b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
-Note that there could be > 5 species due to similar sharing values.
-The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
-Figure created using R version 3.5.2.](../Figures/Fig4.png)
-
-Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g.
-garfish *Belone belone*) (Fig.
-4a).
-In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
-For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Fig.
-4a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-However, **it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].** In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
-The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
-For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Fig.
-4b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
-In the Philippines both pelagic and reef fishes contribute substantially to both local food and nutrition security as well as livelihoods [@Cabral:2018hc].
-
-# Conclusions
-
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than previously estimated[@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
-This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.
-Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
-Previous work has highlighted that collaboration is key to better outcomes for shared marine resources [@Munro:2002uf].
-Identifying existing transboundary species is the first step towards cooperative joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
-
-# Materials and Methods
-
-## Databases of species' geographic distribution
+### Databases of species' geographic distribution
 
@@
 The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:Data_Table)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
 Only commercial fished species with data from all four sources were included in our analysis.
-
-Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data are publicly available (see Acknowledgments).
 
@@
   rename("Main Method"=Main_Method) %>% 
-  # kable("latex", booktabs = T,
-  #       caption = "Summary of data sources to estimate species' distributions.
+  kable("latex", booktabs = T,
+        caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data are publically available, see references for details.") %>%
-  # kable_styling(full_width = F) %>%
-  # column_spec(2,width = "8cm") %>% #wraps text in column2
-  # column_spec(3,width = "3cm") %>% #wraps text in column2
-  write_csv("Table_1.csv")
-
+All data is publically available, see references for details.") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(2,width = "2cm") %>% #wraps text in column2
+  column_spec(3,width = "5cm") #%>% #wraps text in column2
+  # write_csv("Table_1.csv")
 ```
 
-### *Occurrence data*
+#### *Occurrence data*
 
@@
 
-### Criteria 3; Spatial distribution
+#### Criteria 3; Spatial distribution
 
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Supplementary Fig.
-S2).
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(fig:Call-Sup-2)).
 
-## Fisheries trends
+### Fisheries trends
 
@@
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
+Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
 Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
@@
 
-Table 2. Rules to determine the category of each analyzed species.
+<!-- Table 2. Rules to determine the category of each analyzed species. -->
 
-```{r Status_Table, eval = F, echo = F}
-
-### Original version
-
-# Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")
-
-# Rules <- c(
-#   "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
-#   "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
-#   "Catch > (Max Catch*0.50)", #Max Exp.
-#   "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
-#   "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
-#   "Non of the above rules applied"
-# )
-
-# data.frame(Stock_Status,
-#            Rules) %>% 
-#   kable("latex", booktabs = T,
-#         caption = "Rules to determine the status of each transboundary species") %>%
-#   kable_styling(full_width = F) %>%
-#   column_spec(1,width = "3cm") %>% #wraps text in column2
-#   column_spec(2,width = "13cm") #%>% #wraps text in column2
-
-### Grouped version
+```{r CallTab2, eval = T, echo = F}
 
@@
            Rules) %>% 
-  # kable("latex", booktabs = T,
-  #       caption = "Rules to determine the category of each transboundary species") %>%
-  # kable_styling(full_width = F) %>%
-  # column_spec(1,width = "3cm") %>% #wraps text in column2
-  # column_spec(2,width = "13cm") %>% #wraps text in column2
-  write_csv("Table_2.csv")
+  kable("latex", 
+        booktabs = T,
+        caption = "Rules to determine the category of each transboundary species") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(1,width = "3cm") %>% #wraps text in column2
+  column_spec(2,width = "13cm") #%>% #wraps text in column2
+  # write_csv("Table_2.csv")
 
@@
 Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
-Using a smaller *Area Index* will result in more transboundary species (Supplementary Fig.
-S2).
+Using a smaller *Area Index* will result in more transboundary species (Figure \@ref(fig:CallSup2).
 
-\clearpage
+## Results and Discussion
 
-# References
+We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Figure \@ref(fig:Figure1 a)).
+These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) over the same time period.
+Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
+Our results suggests that the contribution of transboundary species to global catch and fishing revenue might have been previously underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
+The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
+These results underscore the importance of transboundary species at the global level.
+
+```{r Figure1, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+b) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions classified according to the United Nations sub-regions.
+Points = mean +- sd.
+Revenue in 2010 real USD"}
+
+img <- readPNG(here("./Figures/Fig1.png"))
+grid.raster(img)
+
+```
+
+<!-- ![Figure 1.
+Number of transboundary species and their contribution to global fisheries catch and revenue.
+a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+b) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions classified according to the United Nations sub-regions: E.
+= Eastern, N.
+= Northern, S.
+= Southern, W.
+= Western, Ltn.
+Ame.
+& the Car.
+= Latin America and the Caribbean.
+Points = regional  mean ± sd.
+Revenue in 2019 real USD.
+Figure created using R version 3.5.2.
+Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png) -->
+
+In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
+However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
+**A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
+Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
+The annual average contribution from all excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
+
+At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1 b)).
+The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
+China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:Figure1 a)).
+These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
+
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], each responsible for over 5.8 million tonnes annually, on average, between 2005 and 2014  (Supplementary Fig.
+S1).
+Peru's catches consist mainly of Peruvian anchoveta (*Engraulis ringens*) and account for 79% of the national transboundary species production.
+Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp].
+A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
+Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
+Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:Figure2)).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Figure \@ref(fig:Figure2)).
+
+```{r Figure_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
+
+<!-- ![Figure 2.
+Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
+a) Revenue in thousand 2019 USD.
+b) Catch in tonnes.
+Points are sub-region averages $\pm$ s.d.
+by country.
+Figure created using R version 3.5.2.
+Abbreviations as in Figure 1.](../Figures/Fig2.png) -->
+
+We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figure \@ref(fig:Figure3)).
+While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
+Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
+We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
+We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
+Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Supplementary Table S2).
+
+```{r FIgure_3, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
+Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
+
+<!-- ![Figure 3.
+Number of transboundary species by catch trend and EEZ.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Figure created using R version 3.5.2.](../Figures/Fig3.png) -->
+
+Empirical analysis suggests that in most cases, management of transboundary species will yield better outcomes in terms of fish catches when nations cooperate [@Munro:2002uf].
+Yet, cooperation can be a complex process [@Jensen:2015cf] with specific cases where joint management might not be the best strategy [@Munro:2015df].
+Examples of successful joint management include agreements between Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and result in conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+
+Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to the species climate-driven shift in distribution [@Spijkers:2017ij].
+Atlantic Mackerel is a transboundary species that straddles into the high seas.
+Amongst the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) 598.4 thousand tonnes (8.19%) in total catchs and USD 850.2 million (7.17%) in total fishing revenue.
+Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
+Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
+For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
+
+Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:Figure4 a)).
+This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
+Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Figure \@ref(fig:Figure4 a)).
+Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
+
+```{r Figure_4, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+
+img <- readPNG(here("./Figures/Fig4.png"))
+grid.raster(img)
+```
+
+<!-- ![Figure 4.
+Number of EEZs shared by transboundary species.
+a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
+Showing only species that share > 20 EEZs.
+b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
+Note that there could be > 5 species due to similar sharing values.
+The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
+Figure created using R version 3.5.2.](../Figures/Fig4.png) -->
+
+Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g.
+garfish *Belone belone*) (Figure \@ref(fig:Figure4 a)).
+In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
+For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Figure \@ref(fig:Figure4 a)), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+However, **it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].** In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
+The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
+For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Figure \@ref(fig:Figure4 b)) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
+In the Philippines both pelagic and reef fishes contribute substantially to both local food and nutrition security as well as livelihoods [@Cabral:2018hc].
+
+## Conclusions
+
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
+Our results show that captures and revenues from shared species are substantially higher than previously estimated[@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
+This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.
+Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
+Previous work has highlighted that collaboration is key to better outcomes for shared marine resources [@Munro:2002uf].
+Identifying existing transboundary species is the first step towards cooperative joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
+
+## References
 
@@
 
-\clearpage
+## Supplements
 
-# Acknowledgments
-We thank T.
-Clark and A.
-Tidd for helpful comments and discussions.
-G.R.
-was supported by the EO Wilson foundation.
-C.C.C.W.
-was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
-W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
+```{r CallSup1, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
+The number of species is represented in the EEZ while the catch (thousand tons) is represented in the land polygon."}
 
-# Authors contributions
-J.P.A.
-Conceptualization, methodology, formal analysis, writing original draft.
-G.R.
-Methodology, data curation, writing - review & editing.
-C.C.C.W.
-Methodology, writing - review & editing.
-W.W.L.C.
-Supervision, writing - review & editing.
-All authors provided valuable input to the study conceptualization and discussed the results and analysis.
+img <- readPNG("../Figures/FigS1.png")
+grid.raster(img)
+```
 
-# Additional Information  
-Competing interests: The author(s) declare no competing interests.
+<!-- ![Figure S1.
+Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png) -->
 
-# Data Availability
-The *Sea Around Us* datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-The processed results and code are available at https://github.com/jepa/FishForVisa
+The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:CallSup2)).
+As expected, using a more relaxed value (e.g.
+the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
+The current analysis utilized a 25% *Area Index* threshold (Figure \@ref(fig:CallSup2) darker histogram).
 
-<!-- # Recicled text (Not to be included) -->
+```{r CallSup2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.cap="Histogram of transboundary species using different values of Area Index.
+Darker histogram represents used value (25%) in the analysis"}
 
-<!-- From 1973 to 1982, members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 miles from shore [@McRaeandMunro1989].
-The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over the exploration and exploitation of marine resources over 200 nautical miles off their coasts [@UN:1982].
-While intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas was not informed by bio-geography, essentially ignoring species distributions and creating what we know today as shared fish stocks [@Gulland, @Munro2002].
-Fish stocks, are comonly refered in fisheries management as a particular population that is more or less isolated from other stocks of the same species and hence self-sustaining [@FAO:1999tk].
-The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary stocks, shared by 2 or more neighboring coastal nations; (*ii*) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (*iii*) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
-The inception of shared stocks called for the establishment of new fisheries management methods.
-Managers and scientists adopted a game theory approach – or means to analyze strategic interactions among decision-makers – which demonstrates that collaboration is most likely to result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga,@Eide:2013dh].
-Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and lead to conflict between coastal nations [@Spijkers:2017ij], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
-Moreover, under climate change, species distributions will shift [@Cheung2016], resulting in new shared stocks [@Pinsky:2018cb] and highlighting the key role cooperative fisheries management can play in maintaining stocks and profitability [@Nguyen:2018dk] as well as hopefully reducing fisheries conflict [@Spijkers:2019cz].
--->
+img <- readPNG("../Figures/FigS2.png")
+grid.raster(img)
+```
 
-<!-- There is a gap in assessing the nature and number of transboundary species in the world based on their spatial distribution.
-Caddy [@Caddy:1997ue] in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
-However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
-More recently, Teh et al.
-[@Teh:2015gd] estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
-While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
-Thus, despite recent research highlighting the interconnection of marine species [@Ramesh:2019va], the total number of transboundary species is yet to be identified at a global scale.
-Yet, such an understanding is critical to effectively managing fisheries, as needs differ substantially between discreet and shared species [@Mills] and climate change will yield new challenges associated with new shared fisheries [@Pinsky:2018cb].
--->
-
-<!-- *Getting accurate estimates of the number of shared species and where they are located can help develop fisheries management and conservation plans that account for the challenges from transboundary resources management.*  -->
-
-<!-- The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks, shared by 2 or more neighboring coastal nations; (ii) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (iii) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
-We focus on estimating the number of species that meet the first category.
--->
-
-<!-- We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
-The first criteria consisted in only considering shared species between neighboring EEZs, rather than the extended distribution.
-For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
-Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016] (see Methods).
-The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
-A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
-Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
-Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the*Sea Around Us* database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
--->
-
-<!-- Only Bluefin (*Thunnus thynnus*) in the Pacific, Bigeye (*Thunnus obesus*) in the west Pacific, and Yellowfin (*Thunnus albacares*) in the Atlantic still experiencing overfishing  -->
-
-<!-- We found significant differences in catch trends based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).Transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2).
-While no significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), significant differences in catch trends for the 305 discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$p = 0.05).
--->
+<!-- ![Figure S2.
+Histogram of number of transboundary species using different Area Index threshold values.
+The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS2.png) -->

### 2020-10-05 Scripts/Manuscript_Draft.Rmd
removed hilights

@@
 Fisheries management is predicated on the definition of “stocks”, delineated, in most cases by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The **development** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
+The development of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
 However, EEZ boundaries cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
@@
 
-Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling **and highly migratory** resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
+Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling and highly migratory resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
 An informed guess based on limited biogeographical data, suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
@@
 *Litopenaeus stylirostris* or *Farfantepenaeus californiensis*) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] are managed at the species level in both cases, yet include multiple populations exploited by each country’s fisheries.
-**Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].** For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
+Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
+For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
 we did not include the high seas).
@@
 Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
-**However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
-This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].** Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
+However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].
+Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
 Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
@@
 
-In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+In many cases, according to our categorization criteria, a transboundary species can be distributed in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
 For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
@@
 Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
-**A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
+A situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
 Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
@@
 For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Figure \@ref(fig:Figure4 a)), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-However, **it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].** In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
+However, it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
 The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].

### 2020-10-05 Scripts/Manuscript_Draft.Rmd
Set manuscript for thesis

@@
 The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:Data_Table)).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:CallTab1)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
@@
 
-```{r Data_Table, eval = F, echo = F}
+```{r CallTab1, eval = T, echo = F}
 
@@
   rename("Main Method"=Main_Method) %>% 
-  kable("latex", booktabs = T,
+  kable("latex", 
+        booktabs = T,
         caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data is publically available, see references for details.") %>%
+All data is publically available, see references for details") %>%
   kable_styling(full_width = T) %>%
   column_spec(2,width = "2cm") %>% #wraps text in column2
-  column_spec(3,width = "5cm") #%>% #wraps text in column2
-  # write_csv("Table_1.csv")
+  column_spec(3,width = "5cm") # #wraps text in column2
 ```
@@
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
+Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
 Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
@@
   # write_csv("Table_2.csv")
-
 ```
@@
 
-```{r Figure1, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+```{r Figure1, eval = T, fig.width=12, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
 a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 ```
-
-<!-- ![Figure 1.
-Number of transboundary species and their contribution to global fisheries catch and revenue.
-a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-b) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions classified according to the United Nations sub-regions: E.
-= Eastern, N.
-= Northern, S.
-= Southern, W.
-= Western, Ltn.
-Ame.
-& the Car.
-= Latin America and the Caribbean.
-Points = regional  mean ± sd.
-Revenue in 2019 real USD.
-Figure created using R version 3.5.2.
-Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png) -->
 
@@
 Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:Figure2)).
-As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TableS1)).
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
@@
 
-```{r Figure_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+```{r Figure2, eval = T, fig.width=8, fig.height=6, echo=FALSE, fig.pos= "H", fig.cap=""}
 
@@
 ```
-
-<!-- ![Figure 2.
-Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
-a) Revenue in thousand 2019 USD.
-b) Catch in tonnes.
-Points are sub-region averages $\pm$ s.d.
-by country.
-Figure created using R version 3.5.2.
-Abbreviations as in Figure 1.](../Figures/Fig2.png) -->
 
@@
 We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Supplementary Table S2).
+Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:TableS2)).
 
-```{r FIgure_3, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
+```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
 Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
 
-img <- readPNG(here("./Figures/Fig2.png"))
+img <- readPNG(here("./Figures/Fig3.png"))
 grid.raster(img)
@@
 
-```{r Figure_4, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+```{r Figure4, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
 
@@
 
-```{r CallSup1, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.cap="Number of transboundary species per EEZ and they contribution to countries' EEZ catch.
-The number of species is represented in the EEZ while the catch (thousand tons) is represented in the land polygon."}
-
-img <- readPNG("../Figures/FigS1.png")
-grid.raster(img)
+```{r supplements, child = 'supplements.Rmd', eval = T}
 ```
-
-<!-- ![Figure S1.
-Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](~/GitHub/FishForVisa/Figures/FigS1.png) -->
-
-The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:CallSup2)).
-As expected, using a more relaxed value (e.g.
-the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Figure \@ref(fig:CallSup2) darker histogram).
-
-```{r CallSup2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.cap="Histogram of transboundary species using different values of Area Index.
-Darker histogram represents used value (25%) in the analysis"}
-
-img <- readPNG("../Figures/FigS2.png")
-grid.raster(img)
-```
-
-<!-- ![Figure S2.
-Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](~/GitHub/FishForVisa/Figures/FigS2.png) -->

### 2020-10-05 Scripts/supplements.Rmd
Set manuscript for thesis

@@
 ---
-title: "Supplementary information for The transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes, Gabriel Reygondeau, Colette C.C. Wabnitz and William W.L. Cheung"
-output: pdf_document
-header-includes: #allows you to add in your own Latex packages
-- \usepackage{float} #use the 'float' package
-- \floatplacement{figure}{H} #make every figure with caption = h
-- \floatplacement{table}{H}
+output:
+  bookdown::pdf_book:
+    toc : no
+    keep_tex: no
+    number_sections: yes
 ---
 
-```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+```{r setup_sup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
 
-# Supplementary Figures
-
-```{r Call_Sup_1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+```{r CallSup1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
 The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
@@
 The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Supplementary Fig.
-S2).
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:CallSup2)).
 As expected, using a more relaxed value (e.g.
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Supplementary Fig.
-S2 - darker histogram).
+The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup2 - darker histogram).
 
-```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
+```{r CallSup2, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
 The darker histogram represents the threshold (25%) used in the present analysis.
@@
 
-\clearpage
+```{r TableS1, eval = T, echo = F}
 
-# Supplementary Tables
-
-```{r Call_SupT_1, eval = T, echo = F, fig.pos= "H"}
-
-read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
+read.csv("../Tables/Table_S1.csv") %>% 
   clean_names() %>% 
@@
 
-```{r Call_SupT_2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
+```{r TableS2, eval = T, echo = F, message = F, warning = F}
 
@@
 
-read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
+read.csv("../Tables/Table_S2.csv") %>% 
   clean_names() %>% 
@@
 ```
-
-We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.

### 2020-10-06 Scripts/Manuscript_Draft.Rmd
Figures size for thesis

@@
 
-### Materials and Methods
+### Materials and methods
 
@@
 b) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions classified according to the United Nations sub-regions.
-Points = mean +- sd.
-Revenue in 2010 real USD"}
+Regions classified according to the United Nations sub-regions: E.
+= Eastern, N.
+= Northern, S.
+= Southern, W.
+= Western, Ltn.
+Ame.
+& the Car.
+= Latin America and the Caribbean.
+Points = regional  mean \u00B1 sd.
+Revenue in 2019 real USD."}
 
@@
 
-```{r Figure2, eval = T, fig.width=8, fig.height=6, echo=FALSE, fig.pos= "H", fig.cap=""}
+```{r Figure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km^2$ and UN sub-region.
+a) Revenue in thousand 2019 USD.
+b) Catch in tonnes.
+Points are sub-region averages \u00B1 s.d.
+by country."}
 
@@
 
-```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
+```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data."}
 
@@
 ```
-
-<!-- ![Figure 3.
-Number of transboundary species by catch trend and EEZ.
-Category A, Increasing; Category B, Constant; Category C, Decreasing.
-“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
-Figure created using R version 3.5.2.](../Figures/Fig3.png) -->
 
@@
 
-```{r Figure4, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+```{r Figure4, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species.
+a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
+Showing only species that share > 20 EEZs.
+b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
+Note that there could be > 5 species due to similar sharing values.
+The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase."}
 
@@
 ```
-
-<!-- ![Figure 4.
-Number of EEZs shared by transboundary species.
-a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
-Showing only species that share > 20 EEZs.
-b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
-Note that there could be > 5 species due to similar sharing values.
-The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
-Figure created using R version 3.5.2.](../Figures/Fig4.png) -->
 
@@
 
-## References
+<!-- ## References -->
 
-<div id="refs"></div>
+<!-- <div id="refs"></div> -->
 

### 2020-10-07 Scripts/supplements.Rmd
Included abstracts in por and esp.

--- 2020-10-05 Scripts/supplements.Rmd
@@
 
-We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.
+# Translated Abstacts
+
+## Español
+
+Es frecuente que los límites de las herramientas de manejo ambiental y la distribución de especies no coincidan como sucede en el caso de especies marinas que cruzan múltiples Zonas Económicas Exclusivas (ZEE).
+Este tipo de movimiento representa un desafío para el manejo pesquero, ya que las políticas públicas tienden a enfocarse en el nivel nacional; sin embargo, es necesario establecer colaboraciones internacionales para maximizar los beneficios ecológicos, sociales y económicos a largo plazo obtenidos con la captura de especies marinas compartidas.
+En este artículo se combinó la distribución de especies con la delimitación espacial de las ZEE para identificar el número de especies marinas explotadas comercialmente que son compartidas por naciones vecinas (especies transfronterizas).
+Los resultados revelaron que el 67% de las especies analizadas pertenecen a esa categoría (n = 633).
+Entre 2005 y 2014, las pesquerías que tenían como objetivo estas especies y que operaban dentro de las ZEE mundiales capturaron un promedio de 48 millones de toneladas por año, lo que equivale a un promedio de 77 mil millones de dólares en ingresos anuales por pesca.
+Durante este tiempo, más del 90% de las capturas y beneficios económicos de algunos países fue resultado de unos pocos recursos compartidos.
+Así mismo, se demuestra que las capturas de especies transfronterizas están disminuyendo a un ritmo mayor que las no transfronterizas.
+Este estudio tiene implicaciones directas para el manejo pesquero de dichas especies, destacando la necesidad de fortalecer una cooperación internacional eficiente y equitativa.
+
+## Portugues
+
+É frequente que os limites dos instrumentos de gestão de recursos naturais e a distribuição das espécies não coincidam como acontece no caso das espécies marinhas que cruzam múltiplas Zonas Econômicas Exclusivas (ZEE).
+Este tipo de movimento representa um desafio para a gestão pesqueira, já que as políticas públicas tendem a ser focadas ao nível nacional; portanto, colaborações internacionais precisam ser estabelecidas para maximizar os benefícios ecológicos, sociais e econômicos de longo prazo alcançados com a captura de espécies marinhas compartilhadas.
+Neste artigo, a distribuição das espécies foi combinada com a delimitação espacial de ZEEs para identificar o número de espécies marinhas exploradas comercialmente que são compartilhadas por nações vizinhas (espécies transfronteiriças).
+Os resultados revelaram que 67% das espécies analisadas pertencem a essa categoria (n = 633).
+Entre 2005 e 2014, as pescarias que operavam nas ZEEs globais que visam essas espécies capturaram uma média de 48 milhões de toneladas por ano, o que equivale a uma média de $ 77 bilhões em receitas anuais de pesca.
+Durante este tempo, mais de 90% das capturas e benefícios econômicos de alguns países foi resultado de alguns recursos compartilhados.
+Da mesma forma, se mostra que as capturas de essas espécies estão diminuindo a um ritmo maior do que as das não transfronteiriças.
+Este estudo tem implicações diretas para a gestão da pesca de espécies referidas, destacando a necessidade de fortalecer uma cooperação internacional eficiente e equitativa.

### 2020-10-07 Scripts/Manuscript_Draft.Rmd
misc.

--- 2020-10-05 Scripts/Manuscript_Draft.Rmd
@@
 ---
+title: "The transboundary nature of the world’s exploited marine species"
+author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette C.C. Wabnitz^1,3,4^ and William W.L. Cheung^1^"
+date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
+^2^Yale University, New Haven, Connecticut, USA.
+^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden.
+^4^Center for Ocean Solutions, Stanford University, Stanford, United States"
 output:
-  bookdown::pdf_book:
-    toc : no
-    keep_tex: no
-    number_sections: yes
-    fig_width: 6 
-    fig_height: 4 
+  word_document:
+  pdf_document:
+    fig_caption: yes
 geometry: margin=1in
@@
 csl: ../References/nature_cc.csl
-header-includes: #allows you to add in your own Latex packages
-- \usepackage{float} #use the 'float' package
-- \floatplacement{figure}{H} #make every figure with caption = h
 ---
+
+**Corresponding** author: j.palacios@oceans.ubc.ca
 
@@
 
-## Introduction
+<!-- # Instructions for submission -->
+
+<!-- - Journal: *Scientific Reports* -->
+<!-- - Information to authors (https://www.nature.com/srep/author-instructions/submission-guidelines) -->
+<!-- - There are two types of article: -->
+
+<!-- -- Articles should be no more than 11 typeset pages in length.
+As a guide, the main text (not including Abstract, Methods, References and figure legends) should be no more than 4,500 words.
+The maximum title length is 20 words.
+The Abstract (without heading) - which must be no more than 200 words long and contain no references - should serve both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications..
+-->
+
+# Abstract
+
+Regulatory boundaries and species distributions often do not align.
+This is especially the case of marine species crossing multiple Exclusive Economic Zones (EEZs).
+Such movements represent a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
+Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
+We found that 67% of the species analyzed are transboundary (n = 633).
+Between 2005 and 2014, fisheries targeting these species within global-EEZs caught on average 48 million tonnes per year, equivalent to an average of USD 77 billion in annual fishing revenue.
+For select countries, over 90% of their catch and economic benefits were attributable to a few shared resources.
+Our analysis suggests that catches from transboundary species are declining more than those from non-transboundary species.
+Our study has direct implications for managing fisheries on transboundary species, highlighting the need for strengthened effective international cooperation.
+
+# Introduction
 
@@
 Fisheries management is predicated on the definition of “stocks”, delineated, in most cases by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The development of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
+The **development** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
 However, EEZ boundaries cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
@@
 
-Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling and highly migratory resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
+Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling **and highly migratory** resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
 An informed guess based on limited biogeographical data, suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
@@
 *Litopenaeus stylirostris* or *Farfantepenaeus californiensis*) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] are managed at the species level in both cases, yet include multiple populations exploited by each country’s fisheries.
-Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
-For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
+**Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].** For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
 we did not include the high seas).
@@
 
-### Materials and Methods
+# Results and Discussion
 
-### Databases of species' geographic distribution
+We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
+1a).
+These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) over the same time period.
+Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
+Our results suggests that the contribution of transboundary species to global catch and fishing revenue might have been previously underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
+The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
+These results underscore the importance of transboundary species at the global level.
+
+```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+b) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions classified according to the United Nations sub-regions.
+Points = mean +- sd.
+Revenue in 2010 real USD"}
+
+img <- readPNG(here("./Figures/Fig1.png"))
+grid.raster(img)
+
+```
+
+![Figure 1.
+Number of transboundary species and their contribution to global fisheries catch and revenue.
+a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
+b) Contribution of transboundary species to regional revenue (left) and catch (right).
+Regions classified according to the United Nations sub-regions: E.
+= Eastern, N.
+= Northern, S.
+= Southern, W.
+= Western, Ltn.
+Ame.
+& the Car.
+= Latin America and the Caribbean.
+Points = regional  mean ± sd.
+Revenue in 2019 real USD.
+Figure created using R version 3.5.2.
+Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png)
+
+In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
+However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
+**A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
+Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
+The annual average contribution from all excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
+
+At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Fig.
+1b).
+The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
+China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
+1a).
+These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
+
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], each responsible for over 5.8 million tonnes annually, on average, between 2005 and 2014  (Supplementary Fig.
+S1).
+Peru's catches consist mainly of Peruvian anchoveta (*Engraulis ringens*) and account for 79% of the national transboundary species production.
+Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp].
+A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
+Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
+Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
+2).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Fig.
+2).
+
+```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
+
+![Figure 2.
+Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
+a) Revenue in thousand 2019 USD.
+b) Catch in tonnes.
+Points are sub-region averages $\pm$ s.d.
+by country.
+Figure created using R version 3.5.2.
+Abbreviations as in Figure 1.](../Figures/Fig2.png)
+
+We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
+3).
+While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
+Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
+We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
+We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
+Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Supplementary Table S2).
+
+```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
+Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
+
+img <- readPNG(here("./Figures/Fig2.png"))
+grid.raster(img)
+```
+
+![Figure 3.
+Number of transboundary species by catch trend and EEZ.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Figure created using R version 3.5.2.](../Figures/Fig3.png)
+
+Empirical analysis suggests that in most cases, management of transboundary species will yield better outcomes in terms of fish catches when nations cooperate [@Munro:2002uf].
+Yet, cooperation can be a complex process [@Jensen:2015cf] with specific cases where joint management might not be the best strategy [@Munro:2015df].
+Examples of successful joint management include agreements between Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
+Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and result in conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
+
+<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
+However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
+-->
+
+Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to the species climate-driven shift in distribution [@Spijkers:2017ij].
+Atlantic Mackerel is a transboundary species that straddles into the high seas.
+Amongst the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) 598.4 thousand tonnes (8.19%) in total catchs and USD 850.2 million (7.17%) in total fishing revenue.
+Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
+Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
+For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
+
+Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
+Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
+4a).
+This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
+Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Fig.
+4a).
+Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
+
+```{r Call_Spp_Circular, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+
+img <- readPNG(here("./Figures/Fig4.png"))
+grid.raster(img)
+```
+
+![Figure 4.
+Number of EEZs shared by transboundary species.
+a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
+Showing only species that share > 20 EEZs.
+b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
+Note that there could be > 5 species due to similar sharing values.
+The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
+Figure created using R version 3.5.2.](../Figures/Fig4.png)
+
+Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g.
+garfish *Belone belone*) (Fig.
+4a).
+In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
+For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Fig.
+4a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+However, **it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].** In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
+The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
+For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Fig.
+4b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
+In the Philippines both pelagic and reef fishes contribute substantially to both local food and nutrition security as well as livelihoods [@Cabral:2018hc].
+
+# Conclusions
+
+Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
+Our results show that captures and revenues from shared species are substantially higher than previously estimated[@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
+This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.
+Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
+Previous work has highlighted that collaboration is key to better outcomes for shared marine resources [@Munro:2002uf].
+Identifying existing transboundary species is the first step towards cooperative joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
+
+# Materials and Methods
+
+## Databases of species' geographic distribution
 
@@
 The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:CallTab1)).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
@@
 
-```{r CallTab1, eval = T, echo = F}
+Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data are publicly available (see Acknowledgments).
+
+```{r Data_Table, eval = F, echo = F}
 
@@
   rename("Main Method"=Main_Method) %>% 
-  kable("latex", 
-        booktabs = T,
-        caption = "Summary of data sources to estimate species' distributions.
+  # kable("latex", booktabs = T,
+  #       caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data is publically available, see references for details") %>%
-  kable_styling(full_width = T) %>%
-  column_spec(2,width = "2cm") %>% #wraps text in column2
-  column_spec(3,width = "5cm") # #wraps text in column2
+All data are publically available, see references for details.") %>%
+  # kable_styling(full_width = F) %>%
+  # column_spec(2,width = "8cm") %>% #wraps text in column2
+  # column_spec(3,width = "3cm") %>% #wraps text in column2
+  write_csv("Table_1.csv")
+
 ```
 
-#### *Occurrence data*
+### *Occurrence data*
 
@@
 
-#### Criteria 1; Neighboring EEZs
+### Criteria 1; Neighboring EEZs
 
@@
 
-#### Criteria 3; Spatial distribution
+### Criteria 3; Spatial distribution
 
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(fig:Call-Sup-2)).
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Supplementary Fig.
+S2).
 
-### Fisheries trends
+## Fisheries trends
 
@@
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
+Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
 Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
@@
 
-<!-- Table 2. Rules to determine the category of each analyzed species. -->
+Table 2. Rules to determine the category of each analyzed species.
 
-```{r CallTab2, eval = T, echo = F}
+```{r Status_Table, eval = F, echo = F}
+
+### Original version
+
+# Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")
+
+# Rules <- c(
+#   "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
+#   "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
+#   "Catch > (Max Catch*0.50)", #Max Exp.
+#   "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
+#   "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
+#   "Non of the above rules applied"
+# )
+
+# data.frame(Stock_Status,
+#            Rules) %>% 
+#   kable("latex", booktabs = T,
+#         caption = "Rules to determine the status of each transboundary species") %>%
+#   kable_styling(full_width = F) %>%
+#   column_spec(1,width = "3cm") %>% #wraps text in column2
+#   column_spec(2,width = "13cm") #%>% #wraps text in column2
+
+### Grouped version
 
@@
            Rules) %>% 
-  kable("latex", 
-        booktabs = T,
-        caption = "Rules to determine the category of each transboundary species") %>%
-  kable_styling(full_width = T) %>%
-  column_spec(1,width = "3cm") %>% #wraps text in column2
-  column_spec(2,width = "13cm") #%>% #wraps text in column2
-  # write_csv("Table_2.csv")
+  # kable("latex", booktabs = T,
+  #       caption = "Rules to determine the category of each transboundary species") %>%
+  # kable_styling(full_width = F) %>%
+  # column_spec(1,width = "3cm") %>% #wraps text in column2
+  # column_spec(2,width = "13cm") %>% #wraps text in column2
+  write_csv("Table_2.csv")
+
 ```
 
-### Statistical analysis
+## Statistical analysis
 
@@
 Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
-However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
-This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].
-Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
+**However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].** Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
 Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
@@
 Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
-Using a smaller *Area Index* will result in more transboundary species (Figure \@ref(fig:CallSup2).
+Using a smaller *Area Index* will result in more transboundary species (Supplementary Fig.
+S2).
 
-## Results and Discussion
+\clearpage
 
-We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Figure \@ref(fig:Figure1 a)).
-These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) over the same time period.
-Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
-Our results suggests that the contribution of transboundary species to global catch and fishing revenue might have been previously underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
-The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
-These results underscore the importance of transboundary species at the global level.
-
-```{r Figure1, eval = T, fig.width=12, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
-a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
-b) Contribution of transboundary species to regional revenue (left) and catch (right).
-Regions classified according to the United Nations sub-regions.
-Points = mean +- sd.
-Revenue in 2010 real USD"}
-
-img <- readPNG(here("./Figures/Fig1.png"))
-grid.raster(img)
-
-```
-
-In many cases, according to our categorization criteria, a transboundary species can be distributed in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
-For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
-However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
-A situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
-Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
-The annual average contribution from all excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
-
-At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1 b)).
-The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
-China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:Figure1 a)).
-These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
-
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], each responsible for over 5.8 million tonnes annually, on average, between 2005 and 2014  (Supplementary Fig.
-S1).
-Peru's catches consist mainly of Peruvian anchoveta (*Engraulis ringens*) and account for 79% of the national transboundary species production.
-Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp].
-A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
-Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
-China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
-Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:Figure2)).
-As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TableS1)).
-However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Figure \@ref(fig:Figure2)).
-
-```{r Figure2, eval = T, fig.width=8, fig.height=6, echo=FALSE, fig.pos= "H", fig.cap=""}
-
-img <- readPNG(here("./Figures/Fig2.png"))
-grid.raster(img)
-```
-
-We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figure \@ref(fig:Figure3)).
-While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
-We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
-We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:TableS2)).
-
-```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
-
-img <- readPNG(here("./Figures/Fig3.png"))
-grid.raster(img)
-```
-
-<!-- ![Figure 3.
-Number of transboundary species by catch trend and EEZ.
-Category A, Increasing; Category B, Constant; Category C, Decreasing.
-“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
-Figure created using R version 3.5.2.](../Figures/Fig3.png) -->
-
-Empirical analysis suggests that in most cases, management of transboundary species will yield better outcomes in terms of fish catches when nations cooperate [@Munro:2002uf].
-Yet, cooperation can be a complex process [@Jensen:2015cf] with specific cases where joint management might not be the best strategy [@Munro:2015df].
-Examples of successful joint management include agreements between Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
-Lack of collaboration over shared stocks may threaten stock sustainability, reduce the future profitability potential of the fishery, and result in conflict between neighboring nations [@Clark:1980js; @Spijkers:2017ij].
-
-Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to the species climate-driven shift in distribution [@Spijkers:2017ij].
-Atlantic Mackerel is a transboundary species that straddles into the high seas.
-Amongst the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) 598.4 thousand tonnes (8.19%) in total catchs and USD 850.2 million (7.17%) in total fishing revenue.
-Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
-Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
-For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
-
-Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:Figure4 a)).
-This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
-Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
-Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Figure \@ref(fig:Figure4 a)).
-Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
-
-```{r Figure4, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
-
-img <- readPNG(here("./Figures/Fig4.png"))
-grid.raster(img)
-```
-
-<!-- ![Figure 4.
-Number of EEZs shared by transboundary species.
-a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
-Showing only species that share > 20 EEZs.
-b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
-Note that there could be > 5 species due to similar sharing values.
-The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
-Figure created using R version 3.5.2.](../Figures/Fig4.png) -->
-
-Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g.
-garfish *Belone belone*) (Figure \@ref(fig:Figure4 a)).
-In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
-For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Figure \@ref(fig:Figure4 a)), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-However, it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
-In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
-The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
-For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Figure \@ref(fig:Figure4 b)) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
-In the Philippines both pelagic and reef fishes contribute substantially to both local food and nutrition security as well as livelihoods [@Cabral:2018hc].
-
-## Conclusions
-
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than previously estimated[@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
-This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.
-Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
-Previous work has highlighted that collaboration is key to better outcomes for shared marine resources [@Munro:2002uf].
-Identifying existing transboundary species is the first step towards cooperative joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
-
-## References
+# References
 
@@
 
-## Supplements
+\clearpage
 
-```{r supplements, child = 'supplements.Rmd', eval = T}
-```
+# Acknowledgments
+We thank T.
+Clark and A.
+Tidd for helpful comments and discussions.
+G.R.
+was supported by the EO Wilson foundation.
+C.C.C.W.
+was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
+W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
+
+# Authors contributions
+J.P.A.
+Conceptualization, methodology, formal analysis, writing original draft.
+G.R.
+Methodology, data curation, writing - review & editing.
+C.C.C.W.
+Methodology, writing - review & editing.
+W.W.L.C.
+Supervision, writing - review & editing.
+All authors provided valuable input to the study conceptualization and discussed the results and analysis.
+
+# Additional Information  
+Competing interests: The author(s) declare no competing interests.
+
+# Data Availability
+The *Sea Around Us* datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
+The processed results and code are available at https://github.com/jepa/FishForVisa
+
+<!-- # Recicled text (Not to be included) -->
+
+<!-- From 1973 to 1982, members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 miles from shore [@McRaeandMunro1989].
+The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over the exploration and exploitation of marine resources over 200 nautical miles off their coasts [@UN:1982].
+While intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas was not informed by bio-geography, essentially ignoring species distributions and creating what we know today as shared fish stocks [@Gulland, @Munro2002].
+Fish stocks, are comonly refered in fisheries management as a particular population that is more or less isolated from other stocks of the same species and hence self-sustaining [@FAO:1999tk].
+The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary stocks, shared by 2 or more neighboring coastal nations; (*ii*) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (*iii*) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
+The inception of shared stocks called for the establishment of new fisheries management methods.
+Managers and scientists adopted a game theory approach – or means to analyze strategic interactions among decision-makers – which demonstrates that collaboration is most likely to result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga,@Eide:2013dh].
+Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and lead to conflict between coastal nations [@Spijkers:2017ij], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
+Moreover, under climate change, species distributions will shift [@Cheung2016], resulting in new shared stocks [@Pinsky:2018cb] and highlighting the key role cooperative fisheries management can play in maintaining stocks and profitability [@Nguyen:2018dk] as well as hopefully reducing fisheries conflict [@Spijkers:2019cz].
+-->
+
+<!-- There is a gap in assessing the nature and number of transboundary species in the world based on their spatial distribution.
+Caddy [@Caddy:1997ue] in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
+However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
+More recently, Teh et al.
+[@Teh:2015gd] estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
+While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
+Thus, despite recent research highlighting the interconnection of marine species [@Ramesh:2019va], the total number of transboundary species is yet to be identified at a global scale.
+Yet, such an understanding is critical to effectively managing fisheries, as needs differ substantially between discreet and shared species [@Mills] and climate change will yield new challenges associated with new shared fisheries [@Pinsky:2018cb].
+-->
+
+<!-- *Getting accurate estimates of the number of shared species and where they are located can help develop fisheries management and conservation plans that account for the challenges from transboundary resources management.*  -->
+
+<!-- The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks, shared by 2 or more neighboring coastal nations; (ii) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (iii) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
+We focus on estimating the number of species that meet the first category.
+-->
+
+<!-- We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
+The first criteria consisted in only considering shared species between neighboring EEZs, rather than the extended distribution.
+For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
+Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016] (see Methods).
+The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
+A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
+Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
+Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the*Sea Around Us* database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
+-->
+
+<!-- Only Bluefin (*Thunnus thynnus*) in the Pacific, Bigeye (*Thunnus obesus*) in the west Pacific, and Yellowfin (*Thunnus albacares*) in the Atlantic still experiencing overfishing  -->
+
+<!-- We found significant differences in catch trends based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).Transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2).
+While no significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), significant differences in catch trends for the 305 discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$p = 0.05).
+-->

### 2020-10-07 Scripts/Initial_Analysis.Rmd
Changed Figure 3 to percentage for better appreciation

@@
   left_join(matching_names) %>% 
-  rename(eez_name = sau_eez_name)
+  rename(eez_name = sf_eez_name)
 ```
@@
 Trend_Data_Plot <- Tresholded_T_Data %>% 
-  left_join(Trend_Data, 
-            by =c("eez_name","taxon_key")
-  ) %>%
-  mutate(trend = ifelse(is.na(trend),"No Trend",trend)) %>% 
+  left_join(Trend_Data#, 
+            # by =c("eez_name","taxon_key","sf_object_id")
+  ) %>%
+  mutate(trend = ifelse(is.na(status),"No Trend",status)) %>% 
   group_by(fishing_entity,trend) %>% 
@@
 
+#### Convert trends to percentage for plot
+
+Totals_trend <- Trend_Data_Plot %>% 
+  group_by(individual) %>% 
+  summarise(total_trend = sum(abs(value)))
+
+Trend_Data_Plot <- Trend_Data_Plot %>% 
+  left_join(Totals_trend) %>% 
+  mutate(
+    value = round(value/total_trend*100)
+  )
+
 length(unique(Trend_Data_Plot$individual))
@@
 Discrete_Trend_Data <- Discrete %>% 
+  left_join(Trend_Data, 
+            by =c("eez_name","taxon_key")
+  ) %>%
+  mutate(trend = ifelse(is.na(status),"No Trend",status)) %>% 
+  group_by(fishing_entity,trend) %>% 
+  summarise(value = length(unique(taxon_key))) %>% 
+  left_join(UN_Regions, by ="fishing_entity") %>%
+  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
+  # mutate(value = ifelse(value > 100,100,value)) %>% 
+  filter(!is.na(fishing_entity),
+         !str_detect(fishing_entity, ".\\(.") # remove associated territories
+  ) %>% 
+  select(individual = fishing_entity,observation = trend,group = Georegion,value) %>% 
+  arrange(group,value) %>% 
+  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
+         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
+                              ifelse(observation == "Max Exploited","Category B",
+                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
+                              )
+         )
+  ) %>% 
+  group_by(individual,observation,group) %>% 
+  summarise(value = sum(value))
+
+# Summary for manuscipt
+
+D_Summary <- Discrete_Trend_Data %>% 
+  mutate(value = ifelse(value <0, value*-1,value)) %>% 
+  group_by(observation) %>% 
+  summarise(tot=sum(value),
+            mean(value),
+            sd(value)) %>% 
+  arrange(desc(tot))
+
+#### Supplemental Table S2
+
+T_Summary %>%
+  left_join(D_Summary, by = "observation") %>%
+    write_csv("Table_S2.csv")
+
+# -------------------------- #
+# Soley Discrete data
+# -------------------------- #
+
+Exclusive_Discrete_Trend_Data <- Discrete_Exclusive %>% 
   left_join(Trend_Data, 
@@
 
-# Summary for manuscipt
-
-D_Summary <- Discrete_Trend_Data %>% 
-  mutate(value = ifelse(value <0, value*-1,value)) %>% 
-  group_by(observation) %>% 
-  summarise(tot=sum(value),
-            mean(value),
-            sd(value)) %>% 
-  arrange(desc(tot))
-
-#### Supplemental Table S2
-
-T_Summary %>%
-  left_join(D_Summary, by = "observation") %>%
-    write_csv("Table_S2.csv")
-
-# -------------------------- #
-# Soley Discrete data
-# -------------------------- #
-
-Exclusive_Discrete_Trend_Data <- Discrete_Exclusive %>% 
-  left_join(Trend_Data, 
-            by =c("eez_name","taxon_key")
-  ) %>%
-  mutate(trend = ifelse(is.na(trend),"No Trend",trend)) %>% 
-  group_by(fishing_entity,trend) %>% 
-  summarise(value = length(unique(taxon_key))) %>% 
-  left_join(UN_Regions, by ="fishing_entity") %>%
-  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
-  # mutate(value = ifelse(value > 100,100,value)) %>% 
-  filter(!is.na(fishing_entity),
-         !str_detect(fishing_entity, ".\\(.") # remove associated territories
-  ) %>% 
-  select(individual = fishing_entity,observation = trend,group = Georegion,value) %>% 
-  arrange(group,value) %>% 
-  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
-         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
-                              ifelse(observation == "Max Exploited","Category B",
-                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
-                              )
-         )
-  ) %>% 
-  group_by(individual,observation,group) %>% 
-  summarise(value = sum(value))
-
 ```
 
-### Circular plot
+### Fig. 3- Circular plot
 
@@
                     y = c(-100,-50, 0, 50, 100),
-                    label = c(">100","50","0", "50", ">100") , 
+                    label = c("100","50","0", "50", "100") , 
                     color="black", 

### 2020-10-08 Scripts/supplements.Rmd
Included Figure S3 in supplements and corrected numbering

@@
 - \floatplacement{table}{H}
+- \usepackage{caption}
+- \captionsetup[figure]{name= Figure S}
+- \captionsetup[table]{name= Table S}
 ---
@@
 Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon.](../Figures/FigS1.png) -->
+The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
+Figure created using R version 3.5.2.
+Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/FigS1.png) -->
 
@@
 
-The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Supplementary Fig.
-S2).
-As expected, using a more relaxed value (e.g.
-the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Supplementary Fig.
-S2 - darker histogram).
-
-```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis.
+```{r Call_Sup2, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Percentage of transboundary species by catch trend and EEZ.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
 Figure created using R version 3.5.2."}
@@
 <!-- ![Figure S2.
+Percentage of transboundary species by catch trend and EEZ.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Figure created using R version 3.5.2.](../Figures/FigS2.png) -->
+
+\clearpage
+
+The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Supplementary Fig.
+S3).
+As expected, using a more relaxed value (e.g.
+the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
+The current analysis utilized a 25% *Area Index* threshold (Supplementary Fig.
+S3 - darker histogram).
+
+```{r Call_Sup3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
+The darker histogram represents the threshold (25%) used in the present analysis.
+Figure created using R version 3.5.2."}
+
+img <- readPNG("../Figures/FigS3.png")
+grid.raster(img)
+```
+
+<!-- ![Figure S3.
 Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis](../Figures/FigS2.png) -->
+The darker histogram represents the threshold (25%) used in the present analysis.
+Figure created using R version 3.5.2.](../Figures/FigS2.png) -->
 
@@
 
+\clearpage
+
 # Translated Abstacts
@@
 Este estudo tem implicações diretas para a gestão da pesca de espécies referidas, destacando a necessidade de fortalecer uma cooperação internacional eficiente e equitativa.
+
+## Françuais

### 2020-10-08 Scripts/Manuscript_Draft.Rmd
Supplements update

@@
 Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than previously estimated[@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
+Our results show that captures and revenues from shared species are substantially higher than previously estimated [@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
 This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.

### 2020-10-14 Scripts/supplements.Rmd
update suplements for S

@@
 - \usepackage{caption}
-- \captionsetup[figure]{name= Figure S}
-- \captionsetup[table]{name= Table S}
+- \captionsetup[figure]{name = Figure S}
+- \captionsetup[table]{name = Table S}
 ---
@@
   filter(sub_region != "Other") %>% 
-  arrange(sub_region) %>% 
+  arrange(size_entity_sum) %>% 
   rename("UN sub region" = sub_region,
@@
 
-Es frecuente que los límites de las herramientas de manejo ambiental y la distribución de especies no coincidan como sucede en el caso de especies marinas que cruzan múltiples Zonas Económicas Exclusivas (ZEE).
+Es frecuente que los límites de las herramientas de manejo ambiental y la distribución de especies no coincidan, como sucede en el caso de especies marinas que cruzan múltiples Zonas Económicas Exclusivas (ZEE).
 Este tipo de movimiento representa un desafío para el manejo pesquero, ya que las políticas públicas tienden a enfocarse en el nivel nacional; sin embargo, es necesario establecer colaboraciones internacionales para maximizar los beneficios ecológicos, sociales y económicos a largo plazo obtenidos con la captura de especies marinas compartidas.
 En este artículo se combinó la distribución de especies con la delimitación espacial de las ZEE para identificar el número de especies marinas explotadas comercialmente que son compartidas por naciones vecinas (especies transfronterizas).
-Los resultados revelaron que el 67% de las especies analizadas pertenecen a esa categoría (n = 633).
+Los resultados revelaron que el 67% de las especies analizadas pertenecen a esta categoría (n = 633).
 Entre 2005 y 2014, las pesquerías que tenían como objetivo estas especies y que operaban dentro de las ZEE mundiales capturaron un promedio de 48 millones de toneladas por año, lo que equivale a un promedio de 77 mil millones de dólares en ingresos anuales por pesca.
@@
 
-## Portugues
+## Português
 
@@
 
-## Françuais
+## Français
+
+Dans la grande majorité des cas, les limitations spatiales des zones internationales de pêche et la distribution des espèces ne s’alignent pas.
+C’est particulièrement le cas pour les espèces à large distribution qui occupent et migrent à travers plusieurs zones économiques exclusives (ZEE).
+Les mouvements de ces espèces représentent donc un défi pour la gestion durable de leurs stocks.
+En effet, l’évaluation des stocks est actuellement effectuée à une échelle nationale alors qu’une approche internationale est préconisée afin de maximiser les avantages écologiques, sociaux et économiques liés à ces espèces.
+Dans cette étude, nous avons combiné, à l’échelle mondiale, la distribution des espèces marines exploitées ainsi que la distribution des ZEE afin d’identifier le nombre d’espèces marines partagées entre pays avoisinants.
+Nos résultats démontrent que 67% des espèces considérées sont transfrontalières (n = 633).
+Entre 2005 et 2014, les pêcheries ciblant ces espèces dans les ZEE ont capturé, en moyenne, 48 millions de tonnes par an, ce qui équivaut à 77 milliards USD en revenus moyen par an.
+Dans certains cas, plus de 90% des captures et revenus sont attribuables à un nombre restreint d’espèces partagées.
+Notre analyse suggère par ailleurs que les captures d’espèces transfrontalières marquent un déclin plus marqué que celles des autres espèces .
+Dans un contexte de gestion écosystémique des pêches, les résultats de notre étude soulignent l'importance d’une coopération internationale efficace et équitable afin d’atteindre une pêcherie globale durable

### 2020-10-14 Scripts/Manuscript_Draft.Rmd
included proofs

@@
 Regulatory boundaries and species distributions often do not align.
-This is especially the case of marine species crossing multiple Exclusive Economic Zones (EEZs).
-Such movements represent a challenge for fisheries management as policies tend to focus at the national level, yet collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
-Here, we combined species distributions and the spatial delineation of EEZs to identify the number of commercially exploited marine species that are shared between neighboring nations.
+This is especially the case for marine species crossing multiple Exclusive Economic Zones (EEZs).
+Such movements represent a challenge for fisheries management as policies tend to focus at the national level, yet international collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
+Here, we combined species distributions and the spatial delineation of EEZs at the global level to identify the number of commercially exploited marine species that are shared between neighboring nations.
 We found that 67% of the species analyzed are transboundary (n = 633).
@@
 Our analysis suggests that catches from transboundary species are declining more than those from non-transboundary species.
-Our study has direct implications for managing fisheries on transboundary species, highlighting the need for strengthened effective international cooperation.
+Our study has direct implications for managing fisheries targeting transboundary species, highlighting the need for strengthened effective and equitable international cooperation.
 
@@
 Fisheries management is predicated on the definition of “stocks”, delineated, in most cases by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The **development** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s, for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
+The **development** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s [@UnitedNations:1986tl], for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
 However, EEZ boundaries cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
-Shared stocks can be classified into three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more coastal states; "straddling" - stocks that cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
+Shared stocks can be classified into three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more bordering coastal states; "straddling" - stocks that cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
 Our study focuses on the "transboundary" nature of shared species exploited by fisheries operating within EEZs.
 
-Theories and empirical evidence have shown that fisheries targeting resources that straddle political boundaries complicate fisheries management and potentially reduce the effectiveness of policies to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].
-For instance, climate-driven changes in species distributions have led to conflicts between nations driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
+Theory and empirical evidence have shown that fisheries targeting resources that straddle political boundaries complicate fisheries management and potentially reduce the effectiveness of policies to achieve their stated objectives [@Munro:2002uf; @Englander:2019dq].
+For instance, climate-driven changes in species distributions have led to conflicts between nations, driven, at least partly, by changes in the proportion of captures [@Munro:2002uf], quota allocation, and fishery newcomers [@Spijkers:2017ij].
 Moreover, climate change is likely to exacerbate such conflicts and presents new challenges for political relations between neighboring countries [@Pinsky:2018cb] and fisheries management [@Miller:2013iv].
@@
 
-Forty years after the formal adoption of UNCLOS and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling **and highly migratory** resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
-An informed guess based on limited biogeographical data, suggested that there were approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
+Forty years after the formal adoption of UNCLOS [@UnitedNations:1986tl] and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling and highly migratory resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
+An informed guess, based on limited biogeographical data, suggested that there are approximately 500 to 1500 exploited transboundary stocks [@Caddy:1997ue].
 A recent literature review included 344 shared taxa and their historical contributions to fisheries [@Teh:2015gd].
 However, these studies did not consider species' biogeography in the quantification of transboundary stocks.
-Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catches aas well as fisheries revenue.
-Moreover, we categorize species according to their catch trends while identifying the differences among species based on habitat preference.
-We hypothesize that the methodological constraints of previous studies resulted in an underestimation of the number of transboundary stocks and their contribution to global catch and revenue.
+Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catches as well as fisheries revenue.
+Moreover, we categorize species according to their catch trends while identifying differences among species based on habitat preference.
+We hypothesize that the methodological constraints of previous studies resulted in an underestimation of the number of transboundary species and their contribution to global catch and revenue.
 
 We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catches between 2005 and 2014, and 280 EEZs of 198 coastal countries (See methods).
-We define a ‘stock’ unit as a species in an EEZ, instead of a genetically or morphological distinct units [@Nelson:2016kk], due to a lack of such biological information for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level (or even as groups containing multiple species).
-For example, shrimp (e.g.
-*Litopenaeus stylirostris* or *Farfantepenaeus californiensis*) in the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] are managed at the species level in both cases, yet include multiple populations exploited by each country’s fisheries.
-**Moreover, recent research shows connectivity between fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].** For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g.
-we did not include the high seas).
-We rely on multiple data sources including occurrence, distribution models and catch data and only consider a species to be present in a grid cell if all data sources showed positive occurrence (see Methods).
+We define a ‘stock’ unit as a species in an EEZ, instead of a genetically or morphological distinct unit [@Nelson:2016kk], due to the lack of such biological information being available for almost all the species included in this study [@Teh:2015gd].
+While we acknowledge that species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level (or even as groups containing multiple species).
+For example, shrimp (e.g., *Litopenaeus stylirostris* or *Farfantepenaeus californiensis*) along the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] are managed at the species level, yet include multiple populations exploited by each country’s fisheries.
+Moreover, recent research shows connectivity across fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
+For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g., we did not include the high seas).
+We rely on multiple data sources including occurrence, distribution models and catch data, and only consider a species to be present in a grid cell if all data sources showed positive occurrence (see Methods).
 
@@
 We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around us* at the species level (Fig.
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around Us* at the species level (Fig.
 1a).
-These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of the global fishing revenue) over the same time period.
-Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].When we re-estimated the transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
-Our results suggests that the contribution of transboundary species to global catch and fishing revenue might have been previously underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
+These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of global fishing revenue) over the same time period.
+Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].
+When we re-estimated transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
+Our results suggests that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
 The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
@@
 However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as transboundary stock.
-**A situation similar** to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as a transboundary stock.
+A situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
 Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
@@
 
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], each responsible for over 5.8 million tonnes annually, on average, between 2005 and 2014  (Supplementary Fig.
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transbounuadry species catch annually, on average, between 2005 and 2014  (Supplementary Fig.
 S1).
-Peru's catches consist mainly of Peruvian anchoveta (*Engraulis ringens*) and account for 79% of the national transboundary species production.
+Peru's catches consisted mainly of Peruvian anchoveta (*Engraulis ringens*) and accounted for 79% of the national transboundary species production.
 Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp].
@@
 2).
-As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present was 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
@@
 b) Catch in tonnes.
-Points are sub-region averages $\pm$ s.d.
+Points = sub-region mean $\pm$ s.d.
 by country.
@@
 We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
-3).
+3,  Supplementary Fig.
+S2).
 While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2010 relative to historic catch since 1951 (See methods).
+Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see methods).
 We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
@@
 “No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Only showing first 100 species.
 Figure created using R version 3.5.2.](../Figures/Fig3.png)
@@
 Empirical analysis suggests that in most cases, management of transboundary species will yield better outcomes in terms of fish catches when nations cooperate [@Munro:2002uf].
-Yet, cooperation can be a complex process [@Jensen:2015cf] with specific cases where joint management might not be the best strategy [@Munro:2015df].
+Yet, cooperation can be a complex process [@Jensen:2015cf], and in specific cases joint management might not be the best strategy [@Munro:2015df].
 Examples of successful joint management include agreements between Norway and Russia over Atlantic cod (*Gadus morhua*) [@Eide:2013dha] and Namibia and South Africa over hake (*Merluccius spp*) [@Sumaila:2003vw].
@@
 
-<!-- Europe has the higest rate of transboundary species per $km^2$ (Figure 2) which is consistent with their Common Fisheries Policy to manage the EEZ as a whole.
-However, despite some cases of successfull fisheries management, excessive quotas, poorly implemented fishing subsidies, and policy-related issues have failed to control fishing effort threating the sustainabillity of most european stocks [@Khalilian:2010bk].
--->
-
-Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, Russia and the European Union (EU) [@Spijkers:2019cz].
-For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of total allowable catches for Atlantic mackerel (*Scomber scombrus*) due to the species climate-driven shift in distribution [@Spijkers:2017ij].
+Transboundary fisheries are important to a number of countries with notorious fisheries-related conflicts, including Canada, the USA, the European Union (EU) and Russia [@Spijkers:2019cz].
+For example, since 2007, the EU, Norway, Iceland, and the Faroe Islands (Denmark) have been at odds over the size and relative allocation of the total allowable catch for Atlantic mackerel (*Scomber scombrus*) due to the species' climate-driven shift in distribution [@Spijkers:2017ij].
 Atlantic Mackerel is a transboundary species that straddles into the high seas.
-Amongst the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) 598.4 thousand tonnes (8.19%) in total catchs and USD 850.2 million (7.17%) in total fishing revenue.
+Among the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) of 598.4 thousand tonnes (8.19%) in total catch and USD 850.2 million (7.17%) in total fishing revenue.
 Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
 Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
-For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
+For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more anticipatory and climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
 
 Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated to pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) was significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05) with a median of 40 EEZs per species.
+Species associated with pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) is significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05), with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
@@
 
-Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g.
-garfish *Belone belone*) (Fig.
+Many transboundary species are not considered highly migratory, but are still shared by numerous neighboring EEZs (e.g., garfish *Belone belone*) (Fig.
 4a).
-In addition, many fish stocks have meta-populations that are connected through larvae dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
-For example, while coral reef-related species were found to share fewer neighboring EEZs than other species (Fig.
+In addition, many fish stocks have meta-populations that are connected through larval dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
+For example, while coral reef-associated species were found to share fewer neighboring EEZs than other species (Fig.
 4a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
-However, **it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].** In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
-The effective management of coral reef species is critical to many coastal communities, as they tend to highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
+However, it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+In some areas like the Caribbean and the Western Indian Ocean, among other regions, transboundary marine protected areas have been identified as potential tools to support fisheries and conservation goals [@Levin:2018in; @Perez:2019dm].
+The effective management of coral reef species is critical to many coastal communities, as they tend to be highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
 For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Fig.
 4b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
-In the Philippines both pelagic and reef fishes contribute substantially to both local food and nutrition security as well as livelihoods [@Cabral:2018hc].
+In the Philippines, both pelagic and reef fishes contribute substantially to both local food and nutrition security, as well as livelihoods [@Cabral:2018hc].
 
@@
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
-Only commercial fished species with data from all four sources were included in our analysis.
+Only commercially fished species with data from all four sources were included in our analysis.
 
@@
 
-The SDM-SAU model follows a five-steps process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Pauly:2016uz].
+The SDM-SAU model follows a five-step process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Pauly:2016uz].
 For each commercial marine species, the model first uses the FAO major fishing areas and countries' EEZs to determine a broad distribution.
 It then uses life history information to delimit its range within the FAO fishing area (e.g., thermal preference, depth limit).
-The range is delimited even further by expert-review polygons and compared with that of AquaMaps [@Kaschner:2016tl], OBIS and GBIF occurrence data.
+The range is delimited even further by expert-review polygons and compared with distributions from AquaMaps [@Kaschner:2016tl], as well as OBIS and GBIF occurrence data.
 The model then determines a species' habitat-preference based on the assumption that the relative abundance of a species is determined by the number of habitats in a grid cell and the species' distance to each habitat, as well as the importance of the habitat to the total size of the species distribution.
@@
 Roughly, the *Sea Around Us* method consist of the following steps.
-First, it takes each country's officially reported catch data (e.g.
-National, FAO or RFMO).
-Secondly, it uses literature (e.g.
-peer review, grey literature) to identify missing components (e.g.
-species, gears) and sources of alternative information for missing components.
+First, it takes each country's officially reported catch data (e.g., National, FAO or RFMO).
+Secondly, it uses literature (e.g., peer review, grey literature) to identify missing components (e.g., species, gears) and sources of alternative information for missing components.
 It then derives country estimates for missing data and creates time series interpolation.
-Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (See [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
+Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
 We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (See key uncertainties, below).
+We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties, below).
 Note that in call cases we report the average catch from 2005 to 2014.
@@
 The analysis was undertaken only within the boundaries of the EEZs of coastal states using the *Sea Around Us* shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
-When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g.
-USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
+When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
 Species that were present in EEZs that were non-continental territories neighboring other countries were kept as separate (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
@@
 All analyses only considered cases with agreement across all databases to obtain a more conservative estimate of transboundary species.
-Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the Sea *Around Us catch* database.
+Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the *Sea Around Us* database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
@@
 We estimated the economic contribution in 2019 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
-The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g.
-similar countries, species) to fill in data gaps [@Sumaila:2015uc].
+The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g., similar countries, species) to fill in data gaps [@Sumaila:2015uc].
 The dataset is harmonized with the *Sea Around Us* catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
@@
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
+Three final categories were drawn up for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
 Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
-Finally, we reported the predominant category over the time period considered.
+Finally, we report the predominant category over the time period considered.
 
@@
 Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
-**However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
-This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].** Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
+However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].
+Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., the US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
 Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
@@
 We averaged results from the three models in an effort to capture the structural variation across models.
-Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g.
-Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
+Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
 Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
@@
 Thirdly, we assumed that, if the *Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
-While catch data are not exempt of uncertainty, in most cases, differences between the*Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
+While catch data are not exempt of uncertainty, in most cases, differences between the *Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
 Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.

### 2020-10-14 Scripts/Manuscript_Draft.Rmd

@@
 ---
-title: "The transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes*^1^, Gabriel Reygondeau^1,2^, Colette C.C. Wabnitz^1,3,4^ and William W.L. Cheung^1^"
-date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.
-^2^Yale University, New Haven, Connecticut, USA.
-^3^Stockholm Resilience Center, Stockholm University, Stockholm, Sweden.
-^4^Center for Ocean Solutions, Stanford University, Stanford, United States"
 output:
-  word_document:
-  pdf_document:
-    fig_caption: yes
+  bookdown::pdf_book:
+    toc : no
+    keep_tex: no
+    number_sections: yes
+    fig_width: 6 
+    fig_height: 4 
 geometry: margin=1in
@@
 
-<!-- # Instructions for submission -->
-
-<!-- - Journal: *Scientific Reports* -->
-<!-- - Information to authors (https://www.nature.com/srep/author-instructions/submission-guidelines) -->
-<!-- - There are two types of article: -->
-
-<!-- -- Articles should be no more than 11 typeset pages in length.
-As a guide, the main text (not including Abstract, Methods, References and figure legends) should be no more than 4,500 words.
-The maximum title length is 20 words.
-The Abstract (without heading) - which must be no more than 200 words long and contain no references - should serve both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications..
--->
-
-# Abstract
-
-Regulatory boundaries and species distributions often do not align.
-This is especially the case for marine species crossing multiple Exclusive Economic Zones (EEZs).
-Such movements represent a challenge for fisheries management as policies tend to focus at the national level, yet international collaborations are needed to maximize long-term ecological, social and economic benefits of shared marine species.
-Here, we combined species distributions and the spatial delineation of EEZs at the global level to identify the number of commercially exploited marine species that are shared between neighboring nations.
-We found that 67% of the species analyzed are transboundary (n = 633).
-Between 2005 and 2014, fisheries targeting these species within global-EEZs caught on average 48 million tonnes per year, equivalent to an average of USD 77 billion in annual fishing revenue.
-For select countries, over 90% of their catch and economic benefits were attributable to a few shared resources.
-Our analysis suggests that catches from transboundary species are declining more than those from non-transboundary species.
-Our study has direct implications for managing fisheries targeting transboundary species, highlighting the need for strengthened effective and equitable international cooperation.
-
 # Introduction
@@
 Fisheries management is predicated on the definition of “stocks”, delineated, in most cases by human-made spatial boundaries that often do not correspond to biologically-meaningful population units [@Song:2017iua; @FredstonHermann:2018kp].
-The **development** of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s [@UnitedNations:1986tl], for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
+The development of Exclusive Economic Zones (EEZs) under Part V of the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s [@UnitedNations:1986tl], for instance, extended political boundaries from 12 to 200 nautical miles to give coastal nations property rights over marine resources [@osthagen:2020hd].
 However, EEZ boundaries cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
@@
 Therefore, having an accurate understanding of the distribution and scale of transboundary and straddling fish stocks as well as associated fisheries is important to inform their sustainable management, particularly under climate change.
-
 Forty years after the formal adoption of UNCLOS [@UnitedNations:1986tl] and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling and highly migratory resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
@@
 
+### Materials and methods
+
+### Databases of species' geographic distribution
+
+The *Sea Around Us* has reconstructed global fisheries catches from 1950 to 2014, identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
+We used the *Sea Around Us* reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
+The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:CallTab1)).
+Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
+Only commercially fished species with data from all four sources were included in our analysis.
+
+```{r CallTab1, eval = T, echo = F}
+
+Source <- c(
+  "Occurrence data",
+  "Ecological niche model",
+  "Species distribution model",
+  "Catch data"
+)
+
+Abreviation <- c(
+  "Occurrence",
+  "ENM-Nereus",
+  "SDM-SAU",
+  "Catch-SAU"
+)
+Main_Method <- c(
+  "Occurrence data from multiple sources",
+  "Environmental niche model based on environmental variables and different model algorithms",
+  "Species distribution model based on species traits",
+  "Spatial catch allocation based on country-by-country reconstructions"
+)
+
+Sources <-  c(
+  "Reygondeau, 2019",
+  "Asch et al., 2017 & Reygondeau, 2019",
+  "Palomares et al., 2016",
+  "Zeller et al., 2016"
+)
+
+data.frame(Source,
+           Abreviation,
+           Main_Method,
+           Sources) %>% 
+  rename("Main Method"=Main_Method) %>% 
+  kable("latex", 
+        booktabs = T,
+        caption = "Summary of data sources to estimate species' distributions.
+All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
+All data is publically available, see references for details") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(2,width = "2cm") %>% #wraps text in column2
+  column_spec(3,width = "5cm") # #wraps text in column2
+```
+
+#### *Occurrence data*
+
+Occurrence data was collected by Reygondeau (2019) from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
+
+#### *Distribution models*
+
+In addition to occurrence data, we used two different methods to estimate species distributions, hereafter referred to as Ecological Niche Model-Nereus (ENM-Nereus) and Species Distribution Model-SAU (SDM-SAU).
+Although they use the same occurrence and environmental data, the models are structurally different complementing each other and providing robustness to the results.
+
+The ENM-Nereus consists of a multimodel approach based on a Bioclim and a Boosted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
+Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
+Global environmental conditions were average for the 30-year climate normal period of 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
+See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
+
+The SDM-SAU model follows a five-step process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Pauly:2016uz].
+For each commercial marine species, the model first uses the FAO major fishing areas and countries' EEZs to determine a broad distribution.
+It then uses life history information to delimit its range within the FAO fishing area (e.g., thermal preference, depth limit).
+The range is delimited even further by expert-review polygons and compared with distributions from AquaMaps [@Kaschner:2016tl], as well as OBIS and GBIF occurrence data.
+The model then determines a species' habitat-preference based on the assumption that the relative abundance of a species is determined by the number of habitats in a grid cell and the species' distance to each habitat, as well as the importance of the habitat to the total size of the species distribution.
+Finally, the species equatorial submergence (e.g., the latitudinal region where a species is not seen in between poles) is estimated for each species.
+See [@Close:2006ux; @Pauly:2016uz] for model details.
+
+#### *Catch data*
+
+The previous models combine observational data with a series of biotic and abiotic data to determine the probability that a species will be found in a given space at a given time.
+However, this does not mean that the species in question will actually be there.
+While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SDM-SAU undertakes validation by means of other models), we used a fourth data set to corroborate the models’ outputs.
+The *Sea Around Us* estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
+Catches are also spatially allocated on a $0.5^{\circ}$ x $0.5^{\circ}$ latitude longitude grid [@Zeller2016].
+Roughly, the *Sea Around Us* method consist of the following steps.
+First, it takes each country's officially reported catch data (e.g., National, FAO or RFMO).
+Secondly, it uses literature (e.g., peer review, grey literature) to identify missing components (e.g., species, gears) and sources of alternative information for missing components.
+It then derives country estimates for missing data and creates time series interpolation.
+Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
+We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties, below).
+Note that in call cases we report the average catch from 2005 to 2014.
+
+### Determining transboundary species trait
+
+We developed a three-criteria methodology to determine whether or not a species can be considered transboundary.
+Only species that met all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
+Note that in cases where a species met all criteria for some EEZs, but not for other EEZs, these species were still considered as “transboundary”.
+
+#### Criteria 1; Neighboring EEZs
+
+As mentioned above, we define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
+Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
+The analysis was undertaken only within the boundaries of the EEZs of coastal states using the *Sea Around Us* shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
+When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
+Species that were present in EEZs that were non-continental territories neighboring other countries were kept as separate (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
+Associated states like Puerto Rico and New Caledonia were not considered separately (e.g., Puerto Rico was grouped with the United States and New Caledonia with France).
+
+#### Criteria 2; Data agreement
+
+We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the world's $0.5^{\circ}$ x $0.5^{\circ}$ marine grid cells.
+All analyses only considered cases with agreement across all databases to obtain a more conservative estimate of transboundary species.
+Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the *Sea Around Us* database.
+Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
+This rule assumes that if a commercial species is projected within the EEZ of any fishing country, such a species would have been fished, and thus likely reported at some point over the last decade of data (2005 - 2014), thereby validating the models and selecting "currently" shared species.
+We acknowledge that this criteria might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
+
+#### Criteria 3; Spatial distribution
+
+Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*.
+The *Area Index* represents the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
+We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(fig:Call-Sup-2)).
+
+## Fisheries trends
+
+We estimated the economic contribution in 2019 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
+The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g., similar countries, species) to fill in data gaps [@Sumaila:2015uc].
+The dataset is harmonized with the *Sea Around Us* catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
+We report average fishing revenue derived from fishing activity within global EEZs between 2005 to 2014.
+We did not include revenue from areas beyond national jurisdiction.
+We used the monthly average US Consumer Price Index (CPI) according to the U.S.
+Bureau of Labor Statistic (https://www.bls.gov/cpi/) to standardize the original 2010 real USD value to 2019 real USD.
+
+We used catch data as described above to determine the catch trend of each species within an EEZ.
+Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended to represent catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g., temperature, markets, fishing policies, and fishing effort) affect catches [@Pauly:2013gs; @Branch:2008kk].
+We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
+Three final categories were drawn up for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
+Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
+Finally, we report the predominant category over the time period considered.
+
+<!-- Table 2. Rules to determine the category of each analyzed species. -->
+
+```{r CallTab2, eval = T, echo = F}
+
+Categories <- c("A - Increasing catch trend",
+                  "B - Constant catch trend",
+                  "C - Decreasing catch trend Fishery",
+                  "No Status")
+
+Rules <- c(
+  "(Year of Catch > Year Post Max.
+Min.
+& Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50)) or Year of Catch < Year of Max.
+Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Rebuilding or #Developing
+  "Catch > (Max Catch*0.50)", #Max Expploitation
+  "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50) or Catch < Max. Catch*0.10", #Over explpoited or collapsed
+  "Non of the above rules applied"
+)
+
+data.frame(Categories,
+           Rules) %>% 
+  kable("latex", 
+        booktabs = T,
+        caption = "Rules to determine the category of each transboundary species") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(1,width = "3cm") %>% #wraps text in column2
+  column_spec(2,width = "13cm") #%>% #wraps text in column2
+  # write_csv("Table_2.csv")
+```
+
+### Statistical analysis
+
+All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*  [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
+All code is available at https://github.com/jepa/FishForVisa.
+All maps were made with Natural Earth data available at https://www.naturalearthdata.com/.
+We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
+We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
+In cases where the ANOVA assumptions were not clearly met, we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm results [@Hollander:2013wz].
+
+#### Key uncertainties
+
+We have identified four key uncertainties in the method utilized that may affect the estimation of transboundary species.
+Firstly, as we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), we are not able to identify transboundary stocks within EEZs.
+While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
+Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
+However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
+This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].
+Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., the US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
+Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
+Nevertheless, our results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
+Secondly, the predicted species' distribution is affected by the uncertainties of the environmental data and models used for such predictions.
+Structural differences within Earth System Models result in variations of oceanic conditions, which undoubtedly affect the ENM-Nereus.
+We averaged results from the three models in an effort to capture the structural variation across models.
+Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
+Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
+To account for such climate variability, we derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
+This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
+Thirdly, we assumed that, if the *Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+While catch data are not exempt of uncertainty, in most cases, differences between the *Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
+Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
+Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the *Sea Around Us*.
+Finally, this study’s results only considered species for which all datasets agreed on presence and had and *Area Index* of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
+Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
+Using a smaller *Area Index* will result in more transboundary species (Figure \@ref(fig:CallSup2).
+
 # Results and Discussion
@@
 We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around Us* at the species level (Fig.
-1a).
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around Us* at the species level (Figure \@ref(fig:Figure1 a)).
 These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of global fishing revenue) over the same time period.
@@
 
-At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Fig.
-1b).
+At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1 b)).
 The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
 China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Fig.
-1a).
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:Figure1 a)).
 These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
@@
 China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
-Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Fig.
-2).
+Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:Figure2)).
 As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Fig.
-2).
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; \@ref(fig:Figure2)).
 
-```{r Call_Fig_2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+```{r Figure2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
 
@@
 
-# Materials and Methods
+<!-- ## References -->
 
-## Databases of species' geographic distribution
+<!-- <div id="refs"></div> -->
 
-The *Sea Around Us* has reconstructed global fisheries catches from 1950 to 2014, identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
-We used the *Sea Around Us* reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
-The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table 1).
-Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
-Only commercially fished species with data from all four sources were included in our analysis.
+## Supplements
 
-Table 1. Summary of data sources to estimate species' distributions. All data has a resolution  $0.5^{\circ}$ latitude x $0.5^{\circ}$ longitude. All data are publicly available (see Acknowledgments).
-
-```{r Data_Table, eval = F, echo = F}
-
-Source <- c(
-  "Occurrence data",
-  "Ecological niche model",
-  "Species distribution model",
-  "Catch data"
-)
-
-Abreviation <- c(
-  "Occurrence",
-  "ENM-Nereus",
-  "SDM-SAU",
-  "Catch-SAU"
-)
-Main_Method <- c(
-  "Occurrence data from multiple sources",
-  "Environmental niche model based on environmental variables and different model algorithms",
-  "Species distribution model based on species traits",
-  "Spatial catch allocation based on country-by-country reconstructions"
-)
-
-Sources <-  c(
-  "Reygondeau, 2019",
-  "Asch et al., 2017 & Reygondeau, 2019",
-  "Palomares et al., 2016",
-  "Zeller et al., 2016"
-)
-
-data.frame(Source,
-           Abreviation,
-           Main_Method,
-           Sources) %>% 
-  rename("Main Method"=Main_Method) %>% 
-  # kable("latex", booktabs = T,
-  #       caption = "Summary of data sources to estimate species' distributions.
-All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data are publically available, see references for details.") %>%
-  # kable_styling(full_width = F) %>%
-  # column_spec(2,width = "8cm") %>% #wraps text in column2
-  # column_spec(3,width = "3cm") %>% #wraps text in column2
-  write_csv("Table_1.csv")
-
+```{r supplements, child = 'supplements.Rmd', eval = T}
 ```
-
-### *Occurrence data*
-
-Occurrence data was collected by Reygondeau (2019) from five publicly available repositories: FishBase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/), the Intergovernmental Oceanographic Commission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].
-
-### *Distribution models*
-
-In addition to occurrence data, we used two different methods to estimate species distributions, hereafter referred to as Ecological Niche Model-Nereus (ENM-Nereus) and Species Distribution Model-SAU (SDM-SAU).
-Although they use the same occurrence and environmental data, the models are structurally different complementing each other and providing robustness to the results.
-
-The ENM-Nereus consists of a multimodel approach based on a Bioclim and a Boosted Regression Tree model [@Thuiller:2009gp], a Maxent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd].
-Environmental variables utilized in the models include sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca].
-Global environmental conditions were average for the 30-year climate normal period of 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
-See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
-
-The SDM-SAU model follows a five-step process based on species-specific life history data, rather than environmental variables [@Close:2006ux; @Pauly:2016uz].
-For each commercial marine species, the model first uses the FAO major fishing areas and countries' EEZs to determine a broad distribution.
-It then uses life history information to delimit its range within the FAO fishing area (e.g., thermal preference, depth limit).
-The range is delimited even further by expert-review polygons and compared with distributions from AquaMaps [@Kaschner:2016tl], as well as OBIS and GBIF occurrence data.
-The model then determines a species' habitat-preference based on the assumption that the relative abundance of a species is determined by the number of habitats in a grid cell and the species' distance to each habitat, as well as the importance of the habitat to the total size of the species distribution.
-Finally, the species equatorial submergence (e.g., the latitudinal region where a species is not seen in between poles) is estimated for each species.
-See [@Close:2006ux; @Pauly:2016uz] for model details.
-
-### *Catch data*
-
-The previous models combine observational data with a series of biotic and abiotic data to determine the probability that a species will be found in a given space at a given time.
-However, this does not mean that the species in question will actually be there.
-While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SDM-SAU undertakes validation by means of other models), we used a fourth data set to corroborate the models’ outputs.
-The *Sea Around Us* estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
-Catches are also spatially allocated on a $0.5^{\circ}$ x $0.5^{\circ}$ latitude longitude grid [@Zeller2016].
-Roughly, the *Sea Around Us* method consist of the following steps.
-First, it takes each country's officially reported catch data (e.g., National, FAO or RFMO).
-Secondly, it uses literature (e.g., peer review, grey literature) to identify missing components (e.g., species, gears) and sources of alternative information for missing components.
-It then derives country estimates for missing data and creates time series interpolation.
-Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
-We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties, below).
-Note that in call cases we report the average catch from 2005 to 2014.
-
-## Determining transboundary species trait
-
-We developed a three-criteria methodology to determine whether or not a species can be considered transboundary.
-Only species that met all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
-Note that in cases where a species met all criteria for some EEZs, but not for other EEZs, these species were still considered as “transboundary”.
-
-### Criteria 1; Neighboring EEZs
-
-As mentioned above, we define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
-Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
-The analysis was undertaken only within the boundaries of the EEZs of coastal states using the *Sea Around Us* shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
-When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
-Species that were present in EEZs that were non-continental territories neighboring other countries were kept as separate (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
-Associated states like Puerto Rico and New Caledonia were not considered separately (e.g., Puerto Rico was grouped with the United States and New Caledonia with France).
-
-### Criteria 2; Data agreement
-
-We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the world's $0.5^{\circ}$ x $0.5^{\circ}$ marine grid cells.
-All analyses only considered cases with agreement across all databases to obtain a more conservative estimate of transboundary species.
-Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the *Sea Around Us* database.
-Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
-This rule assumes that if a commercial species is projected within the EEZ of any fishing country, such a species would have been fished, and thus likely reported at some point over the last decade of data (2005 - 2014), thereby validating the models and selecting "currently" shared species.
-We acknowledge that this criteria might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
-
-### Criteria 3; Spatial distribution
-
-Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*.
-The *Area Index* represents the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
-We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Supplementary Fig.
-S2).
-
-## Fisheries trends
-
-We estimated the economic contribution in 2019 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
-The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g., similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-The dataset is harmonized with the *Sea Around Us* catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
-We report average fishing revenue derived from fishing activity within global EEZs between 2005 to 2014.
-We did not include revenue from areas beyond national jurisdiction.
-We used the monthly average US Consumer Price Index (CPI) according to the U.S.
-Bureau of Labor Statistic (https://www.bls.gov/cpi/) to standardize the original 2010 real USD value to 2019 real USD.
-
-We used catch data as described above to determine the catch trend of each species within an EEZ.
-Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended to represent catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g., temperature, markets, fishing policies, and fishing effort) affect catches [@Pauly:2013gs; @Branch:2008kk].
-We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn up for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table 2) [@Kleisner:2011wn].
-Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
-Finally, we report the predominant category over the time period considered.
-
-Table 2. Rules to determine the category of each analyzed species.
-
-```{r Status_Table, eval = F, echo = F}
-
-### Original version
-
-# Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")
-
-# Rules <- c(
-#   "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
-#   "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
-#   "Catch > (Max Catch*0.50)", #Max Exp.
-#   "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
-#   "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
-#   "Non of the above rules applied"
-# )
-
-# data.frame(Stock_Status,
-#            Rules) %>% 
-#   kable("latex", booktabs = T,
-#         caption = "Rules to determine the status of each transboundary species") %>%
-#   kable_styling(full_width = F) %>%
-#   column_spec(1,width = "3cm") %>% #wraps text in column2
-#   column_spec(2,width = "13cm") #%>% #wraps text in column2
-
-### Grouped version
-
-Categories <- c("A - Increasing catch trend",
-                  "B - Constant catch trend",
-                  "C - Decreasing catch trend Fishery",
-                  "No Status")
-
-Rules <- c(
-  "(Year of Catch > Year Post Max.
-Min.
-& Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50)) or Year of Catch < Year of Max.
-Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Rebuilding or #Developing
-  "Catch > (Max Catch*0.50)", #Max Expploitation
-  "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50) or Catch < Max. Catch*0.10", #Over explpoited or collapsed
-  "Non of the above rules applied"
-)
-
-data.frame(Categories,
-           Rules) %>% 
-  # kable("latex", booktabs = T,
-  #       caption = "Rules to determine the category of each transboundary species") %>%
-  # kable_styling(full_width = F) %>%
-  # column_spec(1,width = "3cm") %>% #wraps text in column2
-  # column_spec(2,width = "13cm") %>% #wraps text in column2
-  write_csv("Table_2.csv")
-
-```
-
-## Statistical analysis
-
-All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*  [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
-All code is available at https://github.com/jepa/FishForVisa.
-All maps were made with Natural Earth data available at https://www.naturalearthdata.com/.
-We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
-We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
-In cases where the ANOVA assumptions were not clearly met, we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm results [@Hollander:2013wz].
-
-## Key uncertainties
-<!-- # Related to Criteria 1 (neighbors) -->
-We have identified four key uncertainties in the method utilized that may affect the estimation of transboundary species.
-Firstly, as we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), we are not able to identify transboundary stocks within EEZs.
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
-However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
-This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].
-Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., the US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
-Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
-Nevertheless, our results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
-Secondly, the predicted species' distribution is affected by the uncertainties of the environmental data and models used for such predictions.
-Structural differences within Earth System Models result in variations of oceanic conditions, which undoubtedly affect the ENM-Nereus.
-We averaged results from the three models in an effort to capture the structural variation across models.
-Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
-Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
-To account for such climate variability, we derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
-This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
-Thirdly, we assumed that, if the *Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
-While catch data are not exempt of uncertainty, in most cases, differences between the *Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
-Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
-Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the *Sea Around Us*.
-Finally, this study’s results only considered species for which all datasets agreed on presence and had and *Area Index* of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
-Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
-Using a smaller *Area Index* will result in more transboundary species (Supplementary Fig.
-S2).
-
-\clearpage
-
-# References
-
-<div id="refs"></div>
-
-\clearpage
-
-# Acknowledgments
-We thank T.
-Clark and A.
-Tidd for helpful comments and discussions.
-G.R.
-was supported by the EO Wilson foundation.
-C.C.C.W.
-was supported by the Walton Family Foundation (grant 2018-1371), the David and Lucile Packard Foundation (grant 2019-68336), and the Gordon and Betty Moore Foundation (grant GBMF5668.02).
-W.W.L.C was supported by the NSERC Discovery Grant and the SSHRC Partnership.
-
-# Authors contributions
-J.P.A.
-Conceptualization, methodology, formal analysis, writing original draft.
-G.R.
-Methodology, data curation, writing - review & editing.
-C.C.C.W.
-Methodology, writing - review & editing.
-W.W.L.C.
-Supervision, writing - review & editing.
-All authors provided valuable input to the study conceptualization and discussed the results and analysis.
-
-# Additional Information  
-Competing interests: The author(s) declare no competing interests.
-
-# Data Availability
-The *Sea Around Us* datasets used are publicly available at http://www.seaaroundus.org/, the occurrence dataset is all publicly available (see Methods), the ENM-Nereus data can be accessed upon request to G.R.
-The processed results and code are available at https://github.com/jepa/FishForVisa
-
-<!-- # Recicled text (Not to be included) -->
-
-<!-- From 1973 to 1982, members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 miles from shore [@McRaeandMunro1989].
-The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over the exploration and exploitation of marine resources over 200 nautical miles off their coasts [@UN:1982].
-While intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management areas was not informed by bio-geography, essentially ignoring species distributions and creating what we know today as shared fish stocks [@Gulland, @Munro2002].
-Fish stocks, are comonly refered in fisheries management as a particular population that is more or less isolated from other stocks of the same species and hence self-sustaining [@FAO:1999tk].
-The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary stocks, shared by 2 or more neighboring coastal nations; (*ii*) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (*iii*) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
-The inception of shared stocks called for the establishment of new fisheries management methods.
-Managers and scientists adopted a game theory approach – or means to analyze strategic interactions among decision-makers – which demonstrates that collaboration is most likely to result in the best overall outcome for nations sharing a common resource [@Bailey:2010ga,@Eide:2013dh].
-Lack of collaboration in shared stocks may threaten stock sustainability [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and lead to conflict between coastal nations [@Spijkers:2017ij], although cooperation and non-cooperation can be more complex [@Jensen:2015cf].
-Moreover, under climate change, species distributions will shift [@Cheung2016], resulting in new shared stocks [@Pinsky:2018cb] and highlighting the key role cooperative fisheries management can play in maintaining stocks and profitability [@Nguyen:2018dk] as well as hopefully reducing fisheries conflict [@Spijkers:2019cz].
--->
-
-<!-- There is a gap in assessing the nature and number of transboundary species in the world based on their spatial distribution.
-Caddy [@Caddy:1997ue] in 1997 estimated that there could be up to 1,500 transboundary fish species in the world.
-However, such estimation lacked a proper assessment due to limited information on the distribution of species at the time [@Caddy:1997ue].
-More recently, Teh et al.
-[@Teh:2015gd] estimated that 206 species can be considered shared, accounting for a total catch of 34.2 million t and a global landed value of USD 30.7 trillion.
-While this represents a good starting point, the analysis was based on a literature review of shared species and did not include a mechanistic way of determining the transboundary nature of the species [@Teh:2015gd].
-Thus, despite recent research highlighting the interconnection of marine species [@Ramesh:2019va], the total number of transboundary species is yet to be identified at a global scale.
-Yet, such an understanding is critical to effectively managing fisheries, as needs differ substantially between discreet and shared species [@Mills] and climate change will yield new challenges associated with new shared fisheries [@Pinsky:2018cb].
--->
-
-<!-- *Getting accurate estimates of the number of shared species and where they are located can help develop fisheries management and conservation plans that account for the challenges from transboundary resources management.*  -->
-
-<!-- The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks, shared by 2 or more neighboring coastal nations; (ii) straddling stocks, occurring in two or more adjacent national jurisdictions and the high seas; and (iii) highly migratory stocks, found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas.
-We focus on estimating the number of species that meet the first category.
--->
-
-<!-- We used four-criteria that combined multiple species distribution data-sources and the world's EEZs to determine if a species can be considered a “shared species”.
-The first criteria consisted in only considering shared species between neighboring EEZs, rather than the extended distribution.
-For the second criteria we considered a species to be present in a grid cell if all data sources predicted positive occurrence.
-Current species distributions were predicted from occurrence records obtained from publicly available observational databases of the world’s marine species and two structurally distinct species distribution models [@Asch:2018ca; Reygondeau:2019uh; @Zeller2016] (see Methods).
-The third criteria determined whether the species were exploited at the grid cell using spatially explicit catch data [@Zeller2016].
-A species was kept if both catch data and predicted species occurrences were positive at the same spatial cells.
-Finally, the last criteria determined a spatial threshold to confirm that a species occurs in both neighboring EEZs.
-Once we have identified the shared stocks, we estimated the contribution of the species to fishing revenues and landings using the*Sea Around Us* database [@Zeller2016] and categorized them according to catch trends [@Kleisner:2013gh].
--->
-
-<!-- Only Bluefin (*Thunnus thynnus*) in the Pacific, Bigeye (*Thunnus obesus*) in the west Pacific, and Yellowfin (*Thunnus albacares*) in the Atlantic still experiencing overfishing  -->
-
-<!-- We found significant differences in catch trends based on whether or not a species was transboundary (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).Transboundary species that are only fished by one country are generally less likely to have a decreasing catch trend compared to when the species is shared by neighboring countries (Supplementary Table S2).
-While no significant differences were found for all categories within transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), significant differences in catch trends for the 305 discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$p = 0.05).
--->

### 2020-10-14 Scripts/supplements.Rmd
solve issues on merging

--- 2020-10-08 Scripts/supplements.Rmd
@@
 ---
-title: "Supplementary information for The transboundary nature of the world’s exploited marine species"
-author: "Authors: Juliano Palacios-Abrantes, Gabriel Reygondeau, Colette C.C. Wabnitz and William W.L. Cheung"
-output: pdf_document
+output:
+  bookdown::pdf_book:
+    toc : no
+    keep_tex: no
+    number_sections: yes
 header-includes: #allows you to add in your own Latex packages
@@
 - \usepackage{caption}
-- \captionsetup[figure]{name= Figure S}
-- \captionsetup[table]{name= Table S}
 ---
 
-```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+```{r setup_sup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
 The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Supplementary Fig.
-S3).
+Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:CallSup3)).
 As expected, using a more relaxed value (e.g.
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Supplementary Fig.
-S3 - darker histogram).
+The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup3 - darker histogram).
 
-```{r Call_Sup3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
+```{r CallSup3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
 The darker histogram represents the threshold (25%) used in the present analysis.
@@
 
-\clearpage
+```{r TableS1, eval = T, echo = F}
 
-# Supplementary Tables
-
-```{r Call_SupT_1, eval = T, echo = F, fig.pos= "H"}
-
-read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
+read.csv("../Tables/Table_S1.csv") %>% 
   clean_names() %>% 
   filter(sub_region != "Other") %>% 
-  arrange(sub_region) %>% 
+  arrange(size_entity_sum) %>% 
   rename("UN sub region" = sub_region,
@@
 ```
-
-\clearpage
-
-# Translated Abstacts
-
-## Español
-
-Es frecuente que los límites de las herramientas de manejo ambiental y la distribución de especies no coincidan como sucede en el caso de especies marinas que cruzan múltiples Zonas Económicas Exclusivas (ZEE).
-Este tipo de movimiento representa un desafío para el manejo pesquero, ya que las políticas públicas tienden a enfocarse en el nivel nacional; sin embargo, es necesario establecer colaboraciones internacionales para maximizar los beneficios ecológicos, sociales y económicos a largo plazo obtenidos con la captura de especies marinas compartidas.
-En este artículo se combinó la distribución de especies con la delimitación espacial de las ZEE para identificar el número de especies marinas explotadas comercialmente que son compartidas por naciones vecinas (especies transfronterizas).
-Los resultados revelaron que el 67% de las especies analizadas pertenecen a esa categoría (n = 633).
-Entre 2005 y 2014, las pesquerías que tenían como objetivo estas especies y que operaban dentro de las ZEE mundiales capturaron un promedio de 48 millones de toneladas por año, lo que equivale a un promedio de 77 mil millones de dólares en ingresos anuales por pesca.
-Durante este tiempo, más del 90% de las capturas y beneficios económicos de algunos países fue resultado de unos pocos recursos compartidos.
-Así mismo, se demuestra que las capturas de especies transfronterizas están disminuyendo a un ritmo mayor que las no transfronterizas.
-Este estudio tiene implicaciones directas para el manejo pesquero de dichas especies, destacando la necesidad de fortalecer una cooperación internacional eficiente y equitativa.
-
-## Portugues
-
-É frequente que os limites dos instrumentos de gestão de recursos naturais e a distribuição das espécies não coincidam como acontece no caso das espécies marinhas que cruzam múltiplas Zonas Econômicas Exclusivas (ZEE).
-Este tipo de movimento representa um desafio para a gestão pesqueira, já que as políticas públicas tendem a ser focadas ao nível nacional; portanto, colaborações internacionais precisam ser estabelecidas para maximizar os benefícios ecológicos, sociais e econômicos de longo prazo alcançados com a captura de espécies marinhas compartilhadas.
-Neste artigo, a distribuição das espécies foi combinada com a delimitação espacial de ZEEs para identificar o número de espécies marinhas exploradas comercialmente que são compartilhadas por nações vizinhas (espécies transfronteiriças).
-Os resultados revelaram que 67% das espécies analisadas pertencem a essa categoria (n = 633).
-Entre 2005 e 2014, as pescarias que operavam nas ZEEs globais que visam essas espécies capturaram uma média de 48 milhões de toneladas por ano, o que equivale a uma média de $ 77 bilhões em receitas anuais de pesca.
-Durante este tempo, mais de 90% das capturas e benefícios econômicos de alguns países foi resultado de alguns recursos compartilhados.
-Da mesma forma, se mostra que as capturas de essas espécies estão diminuindo a um ritmo maior do que as das não transfronteiriças.
-Este estudo tem implicações diretas para a gestão da pesca de espécies referidas, destacando a necessidade de fortalecer uma cooperação internacional eficiente e equitativa.
-
-## Françuais

### 2020-10-15 Scripts/supplements.Rmd
updated supp names for figures

@@
 
-```{r CallSup1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+```{r FigureS1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
 The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
@@
 
-```{r Call_Sup2, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Percentage of transboundary species by catch trend and EEZ.
+```{r FigureS2, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Percentage of transboundary species by catch trend and EEZ.
 Category A, Increasing; Category B, Constant; Category C, Decreasing.
@@
 
-```{r CallSup3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
+```{r FigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
 The darker histogram represents the threshold (25%) used in the present analysis.

### 2020-10-15 Scripts/Manuscript_Draft.Rmd
Fixed headings
misc

@@
 
-# Introduction
+## Introduction
 
@@
 Therefore, having an accurate understanding of the distribution and scale of transboundary and straddling fish stocks as well as associated fisheries is important to inform their sustainable management, particularly under climate change.
+
 Forty years after the formal adoption of UNCLOS [@UnitedNations:1986tl] and the subsequent 1995 United Nations Fish Stock Agreement for the cooperation on the management and conservation of straddling and highly migratory resources [@UnitedNations:1995fs], accurate estimates of the number of exploited marine species shared by neighboring nations are still unavailable.
@@
 
-### Materials and methods
+## Materials and methods
 
@@
 The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table @\ref(tab:CallTab1)).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table \ref(tab:CallTab1)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(fig:Call-Sup-2)).
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(ref:FigureS2)).
 
-## Fisheries trends
+### Fisheries trends
 
@@
 
-#### Key uncertainties
+### Key uncertainties
 
@@
 Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
-Using a smaller *Area Index* will result in more transboundary species (Figure \@ref(fig:CallSup2).
+Using a smaller *Area Index* will result in more transboundary species (Figure \@ref(fig:FigureS2)).
 
-# Results and Discussion
+## Results and Discussion
 
 We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around Us* at the species level (Figure \@ref(fig:Figure1 a)).
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around Us* at the species level (Figure \@ref(fig:Figure1)a).
 These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of global fishing revenue) over the same time period.
@@
 
-```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+```{r Figure1, eval = T, fig.width=10, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
 a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 Regions classified according to the United Nations sub-regions.
-Points = mean +- sd.
+Points = mean \u00B1 sd.
 Revenue in 2010 real USD"}
@@
 
-![Figure 1.
+<!-- ![Figure 1.
 Number of transboundary species and their contribution to global fisheries catch and revenue.
@@
 Figure created using R version 3.5.2.
-Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png)
+Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png) -->
 
-In many cases, according to our categorization criteria, a transboundary species **can be distributed** in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+In many cases, according to our categorization criteria, a transboundary species can be distributed in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
 For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
@@
 
-At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1 b)).
+At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1)b).
 The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
 China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:Figure1 a)).
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:Figure1)a).
 These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
 
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transbounuadry species catch annually, on average, between 2005 and 2014  (Supplementary Fig.
-S1).
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transbounuadry species catch annually, on average, between 2005 and 2014 (Figure \@ref(fig:FigureS1)).
 Peru's catches consisted mainly of Peruvian anchoveta (*Engraulis ringens*) and accounted for 79% of the national transboundary species production.
@@
 Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:Figure2)).
-As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Supplementary Table S1).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TableS1).
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; \@ref(fig:Figure2)).
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Figure \@ref(fig:Figure2)).
 
-```{r Figure2, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=""}
+```{r Figure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by Km2 and UN sub-region.
+a) Revenue in thousand 2019 USD.
+b) Catch in tonnes.
+Points = sub-region mean \u00B1 s.d.
+by country."}
 
@@
 grid.raster(img)
+
 ```
 
-![Figure 2.
+<!-- ![Figure 2.
 Weighted benefits of transboundary species by $km^{2}$ and UN sub-region.
@@
 Figure created using R version 3.5.2.
-Abbreviations as in Figure 1.](../Figures/Fig2.png)
+Abbreviations as in Figure 1.](../Figures/Fig2.png) -->
 
-We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Fig.
-3,  Supplementary Fig.
-S2).
+We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:Figure3); \@ref(fig:FigureS2)).
 While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
@@
 We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
-Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Supplementary Table S2).
+Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:TableS2)).
 
-```{r Call_Circ_Country, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category.
-Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}
+```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ.
+Category A, Increasing; Category B, Constant; Category C, Decreasing.
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
+Only showing first 100 species."}
 
-img <- readPNG(here("./Figures/Fig2.png"))
+img <- readPNG(here("./Figures/Fig3.png"))
 grid.raster(img)
@@
 
-![Figure 3.
+<!-- ![Figure 3.
 Number of transboundary species by catch trend and EEZ.
@@
 Only showing first 100 species.
-Figure created using R version 3.5.2.](../Figures/Fig3.png)
+Figure created using R version 3.5.2.](../Figures/Fig3.png) -->
 
@@
 Species associated with pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) is significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05), with a median of 40 EEZs per species.
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Fig.
-4a).
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:Figure4)a).
 This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
 Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
-Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Fig.
-4a).
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Figure \@ref(fig:Figure4)a).
 Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
 
-```{r Call_Spp_Circular, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}
+```{r Figure4, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species.
+a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
+Showing only species that share > 20 EEZs.
+b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a).
+Note that there could be > 5 species due to similar sharing values.
+The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase"}
 
@@
 
-![Figure 4.
+<!-- ![Figure 4.
 Number of EEZs shared by transboundary species.
@@
 The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase.
-Figure created using R version 3.5.2.](../Figures/Fig4.png)
+Figure created using R version 3.5.2.](../Figures/Fig4.png) -->
 
-Many transboundary species are not considered highly migratory, but are still shared by numerous neighboring EEZs (e.g., garfish *Belone belone*) (Fig.
-4a).
+Many transboundary species are not considered highly migratory, but are still shared by numerous neighboring EEZs (e.g., garfish *Belone belone*) (Figure \@ref(fig:Figure4)a).
 In addition, many fish stocks have meta-populations that are connected through larval dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
-For example, while coral reef-associated species were found to share fewer neighboring EEZs than other species (Fig.
-4a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement [@Levin:2018in].
+For example, while coral reef-associated species were found to share fewer neighboring EEZs than other species (Figure \@ref(fig:Figure4)a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement.
 However, it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
@@
 The effective management of coral reef species is critical to many coastal communities, as they tend to be highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
-For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Fig.
-4b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
+For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Figure \@ref(fig:Figure4)b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
 In the Philippines, both pelagic and reef fishes contribute substantially to both local food and nutrition security, as well as livelihoods [@Cabral:2018hc].
 
-# Conclusions
+## Conclusions
 

### 2020-11-16 Scripts/Manuscript_Draft.Rmd
fixing table references

@@
 The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table \ref(tab:CallTab1)).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table \@ref(tab:CallTab1)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.

### 2020-11-16 Scripts/Manuscript_Draft.Rmd
changes to manuscript

@@
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catches between 2005 and 2014, and 280 EEZs of 198 coastal countries (See methods).
+We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catches between 2005 and 2014, and 280 EEZs of 198 coastal countries (See Methods).
 We define a ‘stock’ unit as a species in an EEZ, instead of a genetically or morphological distinct unit [@Nelson:2016kk], due to the lack of such biological information being available for almost all the species included in this study [@Teh:2015gd].
@@
 Global environmental conditions were average for the 30-year climate normal period of 1970-2000 and averaged for three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/).
-See [@Asch:2018ca; @Reygondeau:2019uh] for model details.
+See Asch *et al.* [-@Asch:2018ca] and Reygondeau *et al.* [-@Reygondeau:2019uh] for model details.
 
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@(ref:FigureS2)).
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@ref(fig:FigureS2)).
 
@@
 Our results suggests that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
-The 305 non-transboundary species (termed as ‘discrete’ species here, see methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
+The 305 non-transboundary species (termed as ‘discrete’ species here, see Methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
 These results underscore the importance of transboundary species at the global level.
@@
 However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see methods - Criteria 3) and thus do not meet our criteria for consideration as a transboundary stock.
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see Methods - Criteria 3) and thus do not meet our criteria for consideration as a transboundary stock.
 A situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
@@
 While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see methods).
+Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
 We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).

### 2020-11-16 Scripts/supplements.Rmd
yes

@@
 - \usepackage{caption}
+- \captionsetup[figure]{name = Figure A1}
+- \captionsetup[table]{name = Table A1}
 ---
 
-```{r setup_sup, eval = T, echo=F, warning=F,message=F, results='hide'}
-
+```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
 library(MyFunctions)
-
 #### Library ####
@@
 )
+my_lib(packages)
+```
 
-my_lib(packages)
-
-```
+<!-- ## Supplementary Figures -->
 
@@
 Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively."}
-
 img <- readPNG("../Figures/FigS1.png")
@@
 ```
-
-<!-- ![Figure S1.
-Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
-Figure created using R version 3.5.2.
-Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/FigS1.png) -->
 
@@
 Figure created using R version 3.5.2."}
-
 img <- readPNG("../Figures/FigS2.png")
@@
 
-The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:CallSup3)).
+The number of grid cells in which a species is present (Area Index) is expected to directly influence whether or not a species is considered transboundary.
+Therefore, we tested the sensitivity of our results to the Area Index by estimating the number of transboundary species along a gradient of values (Figure \@ref(fig:FigureS3)).
 As expected, using a more relaxed value (e.g.
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup3 - darker histogram).
+The current analysis utilized a 25% Area Index threshold (Figure \@ref(fig:FigureS3)) - darker histogram).
 
-```{r FigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values.
+```{r FigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
 The darker histogram represents the threshold (25%) used in the present analysis.
 Figure created using R version 3.5.2."}
-
 img <- readPNG("../Figures/FigS3.png")
 grid.raster(img)
-
 ```
@@
 
-```{r TableS1, eval = T, echo = F}
+\clearpage
 
-read.csv("../Tables/Table_S1.csv") %>% 
+<!-- ## Supplementary Tables -->
+
+```{r TableS1, eval = T, echo = F, fig.pos= "H"}
+read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
   clean_names() %>% 
@@
         booktabs = T,
-        caption= "Size of all the EEZs in each sub region determined by the United Nations") %>% 
+        caption= "Size of all the EEZs in each sub region determined by the United Nations"
+        ) %>%
   kable_styling(full_width = T)
-
 ```
 
-```{r TableS2, eval = T, echo = F, message = F, warning = F}
-
+```{r TableS2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
 # read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
@@
 #         caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
-
-read.csv("../Tables/Table_S2.csv") %>% 
+read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
   clean_names() %>% 
@@
         caption= "Average \u00B1 (standard deviation) number of shared and non-shared transboundary species per EEZ for each catch trend category")
-
 ```

### 2020-11-16 Scripts/Manuscript_Draft.Rmd
detailas

@@
 - \floatplacement{figure}{H} #make every figure with caption = h
+- \floatplacement{table}{H}
 ---
@@
 
-The *Sea Around Us* has reconstructed global fisheries catches from 1950 to 2014, identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
-We used the *Sea Around Us* reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
-The total number of species analyzed was 938, representing 67% of identified species by the *Sea Around Us* and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (*i*) occurrence data, (*ii*) an Ensemble Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (Table \@ref(tab:CallTab1)).
+The Sea Around Us has reconstructed global fisheries catches from 1950 to 2014, identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
+We used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
+The total number of species analyzed was 938, representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (i) occurrence data, (ii) an Ensemble Environmental Niche Model (ENMs), (iii) a life-history-based distribution model, and (iv) fisheries catch data (Table \@ref(tab:CallTab1)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
@@
 While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SDM-SAU undertakes validation by means of other models), we used a fourth data set to corroborate the models’ outputs.
-The *Sea Around Us* estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
+The Sea Around Us estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
 Catches are also spatially allocated on a $0.5^{\circ}$ x $0.5^{\circ}$ latitude longitude grid [@Zeller2016].
-Roughly, the *Sea Around Us* method consist of the following steps.
+Roughly, the Sea Around Us method consist of the following steps.
 First, it takes each country's officially reported catch data (e.g., National, FAO or RFMO).
@@
 Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
-We used the *Sea Around Us* catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+We used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
 We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties, below).
@@
 Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
-The analysis was undertaken only within the boundaries of the EEZs of coastal states using the *Sea Around Us* shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package *sf* [@PackagesfSimpleF:2018vp].
+The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package sf [@PackagesfSimpleF:2018vp].
 When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
@@
 All analyses only considered cases with agreement across all databases to obtain a more conservative estimate of transboundary species.
-Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the *Sea Around Us* database.
+Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the Sea Around Us database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
@@
 
-Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an *Area Index*.
-The *Area Index* represents the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
+Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an Area Index.
+The Area Index represents the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
@@
 The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g., similar countries, species) to fill in data gaps [@Sumaila:2015uc].
-The dataset is harmonized with the *Sea Around Us* catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
+The dataset is harmonized with the Sea Around Us catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
 We report average fishing revenue derived from fishing activity within global EEZs between 2005 to 2014.
@@
 
-All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table*  [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm].
+All analyses were run using the statistical software R version 3.5.2 (2018-12-20) with the packages data.table  [@Packagedatatable:2019uh], janitor [@PackagejanitorSim:2018ur], wesanderson [@Packagewesanderson:2018vn], rfishbase [@PackagerfishbaseR:2019th], R.matlab [@PackageRmatlabRe:2018un], sf [@PackagesfSimpleF:2018vp], sp [@PackagespClasses:2019tn], tidiverse [@PackagetidyverseE:2017vq], tidytext [@PackagetidytextTe:2019vk], and zoo [@PackagezooSInfr:2019tm].
 All code is available at https://github.com/jepa/FishForVisa.
@@
 We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
-We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions.
+We used the standard R functions for the ANOVA and MANOVA after testing for assumptions.
 In cases where the ANOVA assumptions were not clearly met, we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm results [@Hollander:2013wz].
@@
 This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
-Thirdly, we assumed that, if the *Sea Around Us* reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
-While catch data are not exempt of uncertainty, in most cases, differences between the *Sea Around Us* and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
+Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+While catch data are not exempt of uncertainty, in most cases, differences between the Sea Around Us and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
 Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
-Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the *Sea Around Us*.
-Finally, this study’s results only considered species for which all datasets agreed on presence and had and *Area Index* of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
+Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
+Finally, this study’s results only considered species for which all datasets agreed on presence and had and Area Index of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
 Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
-Using a smaller *Area Index* will result in more transboundary species (Figure \@ref(fig:FigureS2)).
+Using a smaller Area Index will result in more transboundary species (Figure \@ref(fig:FigureS2)).
 
@@
 We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the *Sea Around Us* at the species level (Figure \@ref(fig:Figure1)a).
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the Sea Around Us at the species level (Figure \@ref(fig:Figure1)a).
 These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of global fishing revenue) over the same time period.
@@
 At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1)b).
-The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; *DF*(16,165) = 5.081, *p* < 0.001, $\alpha$ = 0.05).
+The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; DF(16,165) = 5.081, p < 0.001, $\alpha$ = 0.05).
 China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
@@
 A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
-Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05).
+Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; Df(16,158) = 2.265, p = 0.005, $\alpha$ = 0.05).
 China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
@@
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, *Df*(16,165) = 3.267, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.05; Figure \@ref(fig:Figure2)).
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, Df(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:Figure2)).
 
@@
 Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
-We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, *Df*(2,459) = 47.94, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, *Df*(2,106) = 1.885, *p* = 0.157; $\alpha$ = 0.05).
-We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, *Df*(2,459) = 19.001, *p* < 0.001).
+We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, Df(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, Df(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05).
+We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, Df(2,459) = 19.001, p < 0.001).
 Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:TableS2)).
@@
 Most marine fish species occur in tropical and subtropical waters around the world [@Nelson:2016kk; @Reygondeau:2019uh], from highly migratory species associated with pelagic-oceanic ecosystems like tunas (*Thunnus sp.*), to less mobile reef-associated species like greater amberjack (*Seriola dumerili*), and species found in demersal ecosystems like gilthead seabream (*Sparus aurata*).
-Species associated with pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) is significantly different from other groups (one-way ANOVA; *DF*(5,597) = 53.82, *p* < 0.001, $\alpha$ = 0.05; Tukey's post hoc test *p* < 0.05), with a median of 40 EEZs per species.
+Species associated with pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) is significantly different from other groups (one-way ANOVA; DF(5,597) = 53.82, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p < 0.05), with a median of 40 EEZs per species.
 The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:Figure4)a).

### 2020-11-20 Scripts/Manuscript_Draft.Rmd
thesis eddits

@@
 The total number of species analyzed was 938, representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (i) occurrence data, (ii) an Ensemble Environmental Niche Model (ENMs), (iii) a life-history-based distribution model, and (iv) fisheries catch data (Table \@ref(tab:CallTab1)).
+To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (i) occurrence data, (ii) an Ensemble Environmental Niche Model (ENMs), (iii) a life-history-based distribution model, and (iv) fisheries catch data (Table \@ref(tab:ffvTable1)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
@@
 
-```{r CallTab1, eval = T, echo = F}
+```{r ffvTable1, eval = T, echo = F}
 
@@
 Finally, the species equatorial submergence (e.g., the latitudinal region where a species is not seen in between poles) is estimated for each species.
-See [@Close:2006ux; @Pauly:2016uz] for model details.
+See Close *et al.* [-@Close:2006ux] and Pauly *et al.* [-@Pauly:2016uz] for model details.
 
@@
 It then derives country estimates for missing data and creates time series interpolation.
-Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see [@Pauly:2019bf] and [@Zeller2016] for catch reconstruction and spatial allocation details).
+Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see Pauly *et al* [-@Pauly:2019bf] and Zeller *et al.* [-@Zeller2016] for catch reconstruction and spatial allocation details).
 We used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties, below).
+We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties).
 Note that in call cases we report the average catch from 2005 to 2014.
@@
 We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@ref(fig:FigureS2)).
+While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@ref(fig:ffvFigureS2)).
 
@@
 We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
-Three final categories were drawn up for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table \@ref(tab:CallTab2)) [@Kleisner:2011wn].
+Three final categories were drawn up for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table \@ref(tab:ffvTable2)) [@Kleisner:2011wn].
 Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
@@
 
-```{r CallTab2, eval = T, echo = F}
+```{r ffvTable2, eval = T, echo = F}
 
@@
 Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
-Using a smaller Area Index will result in more transboundary species (Figure \@ref(fig:FigureS2)).
+Using a smaller Area Index will result in more transboundary species (Figure \@ref(fig:ffvFigureS2)).
 
@@
 We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
-Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the Sea Around Us at the species level (Figure \@ref(fig:Figure1)a).
+Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the Sea Around Us at the species level (Figure \@ref(fig:ffvFigure1)a).
 These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of global fishing revenue) over the same time period.
@@
 When we re-estimated transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
-Our results suggests that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
+Our results suggest that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
 The 305 non-transboundary species (termed as ‘discrete’ species here, see Methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
@@
 
-```{r Figure1, eval = T, fig.width=10, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+```{r ffvFigure1, eval = T, fig.width=10, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
 a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 
-At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:Figure1)b).
+At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:ffvFigure1)b).
 The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; DF(16,165) = 5.081, p < 0.001, $\alpha$ = 0.05).
 China (USD 7,284 million) and the USA (USD 11,604 million) contribute 55% and 82% to the annual average revenue from 2005 to 2014  in Eastern Asia and Northern America, respectively.
-In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:Figure1)a).
+In addition to China and the USA, Russia (USD 7,379 million), Peru (USD 6,044 million) and Japan (USD 3,907 million) were among the top five countries with the most fishing revenue generated from transboundary species between 2005 and 2014 (Figure \@ref(fig:ffvFigure1)a).
 These five nations were responsible for 41% of the yearly global fisheries revenue from transboundary species.
 
-Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transbounuadry species catch annually, on average, between 2005 and 2014 (Figure \@ref(fig:FigureS1)).
+Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transboundary species catch annually, on average, between 2005 and 2014 (Figure \@ref(fig:ffvFigureS1)).
 Peru's catches consisted mainly of Peruvian anchoveta (*Engraulis ringens*) and accounted for 79% of the national transboundary species production.
@@
 China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
-Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:Figure2)).
-As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TableS1).
+Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:ffvFigure2)).
+As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:ffvTableS1).
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, Df(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:Figure2)).
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, Df(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:ffvFigure2)).
 
-```{r Figure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by Km2 and UN sub-region.
+```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by Km2 and UN sub-region.
 a) Revenue in thousand 2019 USD.
@@
 
-We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:Figure3); \@ref(fig:FigureS2)).
+We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:ffvFigure3); \@ref(fig:ffvFigureS2)).
 While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
@@
 We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, Df(2,459) = 19.001, p < 0.001).
-Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:TableS2)).
+Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:ffvTableS2)).
 
-```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ.
+```{r ffvFigure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ.
 Category A, Increasing; Category B, Constant; Category C, Decreasing.
@@
 Species associated with pelagic-oceanic ecosystems are the only group whose EEZ range (i.e., the number of EEZs where the species occur as transboundary) is significantly different from other groups (one-way ANOVA; DF(5,597) = 53.82, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p < 0.05), with a median of 40 EEZs per species.
-The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:Figure4)a).
+The median for species of all other ecosystem preferences is close to, or less than, 20, as many of these species have a narrower distribution or are less mobile (Figure \@ref(fig:ffvFigure4)a).
 This result is likely an effect of the broad distribution that many of the species with preference for pelagic-oceanic ecosystems have.
 Many pelagic-oceanic species are highly migratory and straddle across EEZs while crossing the high seas.
-Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Figure \@ref(fig:Figure4)a).
+Thus, the number of non-neighboring EEZs sharing a highly migratory species can be over 100, as in the case of bigeye tuna (*Thunnus obesus*) (Figure \@ref(fig:ffvFigure4)a).
 Due to their vast migration patterns and presence in areas beyond national jurisdiction, many highly migratory species are managed by Regional Fisheries Management Organizations (RFMOs).
 
-```{r Figure4, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species.
+```{r ffvFigure4, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species.
 a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
@@
 
-Many transboundary species are not considered highly migratory, but are still shared by numerous neighboring EEZs (e.g., garfish *Belone belone*) (Figure \@ref(fig:Figure4)a).
+Many transboundary species are not considered highly migratory but are still shared by numerous neighboring EEZs (e.g., garfish *Belone belone*) (Figure \@ref(fig:ffvFigure4)a).
 In addition, many fish stocks have meta-populations that are connected through larval dispersal with ‘source’ populations potentially supporting ‘sink’ populations thousands of kilometers away [@Ramesh:2019va].
-For example, while coral reef-associated species were found to share fewer neighboring EEZs than other species (Figure \@ref(fig:Figure4)a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement.
+For example, while coral reef-associated species were found to share fewer neighboring EEZs than other species (Figure \@ref(fig:ffvFigure4)a), coral regions often share multiple species through larval connectivity [@Schill:2015fh] and adult movement.
 However, it is important to acknowledge the uncertainty in the connectivity of marine populations at different life stages from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
@@
 The effective management of coral reef species is critical to many coastal communities, as they tend to be highly dependent on subsistence fishing for food and nutrition security as well as livelihoods [@CisnerosMontemayor:2016gq; @Hanich:2018dh].
-For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Figure \@ref(fig:Figure4)b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
+For instance, a number of countries with the largest catches of transboundary reef and pelagic-oceanic associated species (Figure \@ref(fig:ffvFigure4)b) are also associated with some of the highest rates of fish consumption [@FAO:2018KK].
 In the Philippines, both pelagic and reef fishes contribute substantially to both local food and nutrition security, as well as livelihoods [@Cabral:2018hc].
@@
 
-## Supplements
+<!-- ## Supplements -->
 
-```{r supplements, child = 'supplements.Rmd', eval = T}
+```{r supplements, child = 'supplements.Rmd', eval = F}
 ```

### 2020-11-20 Scripts/supplements.Rmd
thesis eddits

@@
 - \usepackage{caption}
-- \captionsetup[figure]{name = Figure A1}
-- \captionsetup[table]{name = Table A1}
+- \captionsetup[figure]{name = Figure A2}
+- \captionsetup[table]{name = Table A2}
 ---
@@
 
-```{r FigureS1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
+```{r ffvFigureS1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
 The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
@@
 
-```{r FigureS2, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Percentage of transboundary species by catch trend and EEZ.
+```{r ffvFigureS2, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Percentage of transboundary species by catch trend and EEZ.
 Category A, Increasing; Category B, Constant; Category C, Decreasing.
@@
 The number of grid cells in which a species is present (Area Index) is expected to directly influence whether or not a species is considered transboundary.
-Therefore, we tested the sensitivity of our results to the Area Index by estimating the number of transboundary species along a gradient of values (Figure \@ref(fig:FigureS3)).
+Therefore, we tested the sensitivity of our results to the Area Index by estimating the number of transboundary species along a gradient of values (Figure \@ref(fig:ffvFigureS3)).
 As expected, using a more relaxed value (e.g.
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% Area Index threshold (Figure \@ref(fig:FigureS3)) - darker histogram).
+The current analysis utilized a 25% Area Index threshold (Figure \@ref(fig:ffvFigureS3)) - darker histogram).
 
-```{r FigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
+```{r ffvFigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
 The darker histogram represents the threshold (25%) used in the present analysis.
@@
 
-```{r TableS1, eval = T, echo = F, fig.pos= "H"}
+```{r ffvTableS1, eval = T, echo = F, fig.pos= "H"}
 read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
@@
 
-```{r TableS2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
+```{r ffvTableS2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
 # read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 

### 2020-11-25 Scripts/Manuscript_Draft.Rmd
typo

@@
 We averaged results from the three models in an effort to capture the structural variation across models.
-Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr]).
+Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr].
 Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.

### 2020-11-25 Scripts/Manuscript_Draft.Rmd
we for I

@@
 However, these studies did not consider species' biogeography in the quantification of transboundary stocks.
-Here, we aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catches as well as fisheries revenue.
-Moreover, we categorize species according to their catch trends while identifying differences among species based on habitat preference.
-We hypothesize that the methodological constraints of previous studies resulted in an underestimation of the number of transboundary species and their contribution to global catch and revenue.
+Here, I aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catches as well as fisheries revenue.
+Moreover, I categorize species according to their catch trends while identifying differences among species based on habitat preference.
+I hypothesize that the methodological constraints of previous studies resulted in an underestimation of the number of transboundary species and their contribution to global catch and revenue.
 
-We overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catches between 2005 and 2014, and 280 EEZs of 198 coastal countries (See Methods).
-We define a ‘stock’ unit as a species in an EEZ, instead of a genetically or morphological distinct unit [@Nelson:2016kk], due to the lack of such biological information being available for almost all the species included in this study [@Teh:2015gd].
-While we acknowledge that species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level (or even as groups containing multiple species).
+I overlaid the known distribution of 938 commercially valuable marine species responsible for an average of 96.5% of global EEZ catches between 2005 and 2014, and 280 EEZs of 198 coastal countries (See Methods).
+I define a ‘stock’ unit as a species in an EEZ, instead of a genetically or morphological distinct unit [@Nelson:2016kk], due to the lack of such biological information being available for almost all the species included in this study [@Teh:2015gd].
+While I acknowledge that species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level (or even as groups containing multiple species).
 For example, shrimp (e.g., *Litopenaeus stylirostris* or *Farfantepenaeus californiensis*) along the Pacific coast of Mexico [@DiarioOficialdelaFederacionDOF:2018wt] and hammerhead shark (*Sphyrna zygaena*) in Peru [@MAP:2017uf] are managed at the species level, yet include multiple populations exploited by each country’s fisheries.
 Moreover, recent research shows connectivity across fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
-For this analysis we only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g., we did not include the high seas).
-We rely on multiple data sources including occurrence, distribution models and catch data, and only consider a species to be present in a grid cell if all data sources showed positive occurrence (see Methods).
+For this analysis I only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g., I did not include the high seas).
+I rely on multiple data sources including occurrence, distribution models and catch data, and only consider a species to be present in a grid cell if all data sources showed positive occurrence (see Methods).
 
@@
 The Sea Around Us has reconstructed global fisheries catches from 1950 to 2014, identifying commercial marine fish and invertebrates as well as fishing regions [@Zeller2016].
-We used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
+I used the Sea Around Us reconstructed species list to determine the number of transboundary marine species exploited by fisheries within each of the world's EEZs.
 The total number of species analyzed was 938, representing 67% of identified species by the Sea Around Us and accounting for 96.52% of the catch identified at the species’ level.
-To determine the current distribution of exploitable marine species, we used four data sources of species-distributions: (i) occurrence data, (ii) an Ensemble Environmental Niche Model (ENMs), (iii) a life-history-based distribution model, and (iv) fisheries catch data (Table \@ref(tab:ffvTable1)).
+To determine the current distribution of exploitable marine species, I used four data sources of species-distributions: (i) occurrence data, (ii) an Ensemble Environmental Niche Model (ENMs), (iii) a life-history-based distribution model, and (iv) fisheries catch data (Table \@ref(tab:ffvTable1)).
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
@@
 
-In addition to occurrence data, we used two different methods to estimate species distributions, hereafter referred to as Ecological Niche Model-Nereus (ENM-Nereus) and Species Distribution Model-SAU (SDM-SAU).
+In addition to occurrence data, I used two different methods to estimate species distributions, hereafter referred to as Ecological Niche Model-Nereus (ENM-Nereus) and Species Distribution Model-SAU (SDM-SAU).
 Although they use the same occurrence and environmental data, the models are structurally different complementing each other and providing robustness to the results.
@@
 However, this does not mean that the species in question will actually be there.
-While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SDM-SAU undertakes validation by means of other models), we used a fourth data set to corroborate the models’ outputs.
+While the models do use approaches to double-check species occurrences (e.g., ENM-Nereus uses four different species distribution algorithms and SDM-SAU undertakes validation by means of other models), I used a fourth data set to corroborate the models’ outputs.
 The Sea Around Us estimates total reconstructed catches - catches based on all publicly available information sources and including discards, as well as unreported and illegal catches that are not included in available FAO data - for each country.
@@
 Finally, the estimated and official data are aggregated, making up the total reconstructed catch data (see Pauly *et al* [-@Pauly:2019bf] and Zeller *et al.* [-@Zeller2016] for catch reconstruction and spatial allocation details).
-We used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-We selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties).
-Note that in call cases we report the average catch from 2005 to 2014.
+I used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
+I selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties).
+Note that in call cases I report the average catch from 2005 to 2014.
 
@@
 
-We developed a three-criteria methodology to determine whether or not a species can be considered transboundary.
+I developed a three-criteria methodology to determine whether or not a species can be considered transboundary.
 Only species that met all criteria at least once were considered as “transboundary”, while species that did not meet the criteria for any EEZ analyzed were considered as “discrete”.
@@
 
-As mentioned above, we define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
+As mentioned above, I define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
 Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
 The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package sf [@PackagesfSimpleF:2018vp].
-When estimating transboundary species, we filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
+When estimating transboundary species, I filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
 Species that were present in EEZs that were non-continental territories neighboring other countries were kept as separate (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
@@
 
-We used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the world's $0.5^{\circ}$ x $0.5^{\circ}$ marine grid cells.
+I used the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the world's $0.5^{\circ}$ x $0.5^{\circ}$ marine grid cells.
 All analyses only considered cases with agreement across all databases to obtain a more conservative estimate of transboundary species.
-Moreover, we assumed that a species was only present in a given grid-cell if it was reported in the Sea Around Us database.
+Moreover, I assumed that a species was only present in a given grid-cell if it was reported in the Sea Around Us database.
 Therefore, all species that were not reported as caught in any single year between the reference years (2005 to 2014) in a given grid-cell were dropped.
 This rule assumes that if a commercial species is projected within the EEZ of any fishing country, such a species would have been fished, and thus likely reported at some point over the last decade of data (2005 - 2014), thereby validating the models and selecting "currently" shared species.
-We acknowledge that this criteria might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
+I acknowledge that this criteria might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
 
@@
 
-Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, we computed an Area Index.
+Finally, to have a more robust result and not categorize a species as transboundary based on its presence in a single $0.5^{\circ}$ x $0.5^{\circ}$ grid cell within an EEZ, I computed an Area Index.
 The Area Index represents the proportion of a given species' overarching shared distribution between neighboring EEZs accounted for by each individual EEZ.
-We classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
-While a species that has less than the selected threshold is not considered transboundary in this paper, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@ref(fig:ffvFigureS2)).
+I classified a species as transboundary if both neighboring EEZs enclosed over 25% of the species joint shared distribution.
+While a species that has less than the selected threshold is not considered transboundary in this chapter, this threshold can be lowered for a more relaxed result or increased for a more conservative estimate (Figure \@ref(fig:ffvFigureS2)).
 
@@
 
-We estimated the economic contribution in 2019 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
-The database we draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g., similar countries, species) to fill in data gaps [@Sumaila:2015uc].
+I estimated the economic contribution in 2019 real USD of transboundary species for each country using global ex-vessel price data [@Tai2017].
+The database I draw from includes ex-vessel price derived from multiple sources and a structured interpolation method (e.g., similar countries, species) to fill in data gaps [@Sumaila:2015uc].
 The dataset is harmonized with the Sea Around Us catch data to estimate yearly fishing revenue (as ex-vessel price) for all species and EEZs considered in this study (http://www.seaaroundus.org/data/#/feru).
-We report average fishing revenue derived from fishing activity within global EEZs between 2005 to 2014.
-We did not include revenue from areas beyond national jurisdiction.
-We used the monthly average US Consumer Price Index (CPI) according to the U.S.
+I report average fishing revenue derived from fishing activity within global EEZs between 2005 to 2014.
+I did not include revenue from areas beyond national jurisdiction.
+I used the monthly average US Consumer Price Index (CPI) according to the U.S.
 Bureau of Labor Statistic (https://www.bls.gov/cpi/) to standardize the original 2010 real USD value to 2019 real USD.
 
-We used catch data as described above to determine the catch trend of each species within an EEZ.
+I used catch data as described above to determine the catch trend of each species within an EEZ.
 Although this method has previously been used to estimate stock status [@Grainger:1996tk], the categories presented here are intended to represent catch trends, and not fishing status for each species as many environmental and social-economic factors (e.g., temperature, markets, fishing policies, and fishing effort) affect catches [@Pauly:2013gs; @Branch:2008kk].
-We only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
+I only assessed species within each EEZ for which at least ten years of data were available between 1951 and 2014 and with at least five consecutive years of data.
 Three final categories were drawn up for each species depending on catch volume within each EEZ (e.g., present, maximum, and minimum EEZ's historical catch) and the year (e.g., year of maximum historical catch of the species within that EEZ) (Table \@ref(tab:ffvTable2)) [@Kleisner:2011wn].
 Accordingly, Category A represents fisheries that are registering increases in catch (“increasing”); Category B, species that have a constant catch rate (“constant”); and Category C, species that have registered declines in catch over the last 10 years (“decreasing”).
-Finally, we report the predominant category over the time period considered.
+Finally, I report the predominant category over the time period considered.
 
@@
 All maps were made with Natural Earth data available at https://www.naturalearthdata.com/.
-We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
-We used the standard R functions for the ANOVA and MANOVA after testing for assumptions.
-In cases where the ANOVA assumptions were not clearly met, we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm results [@Hollander:2013wz].
+I performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm].
+I used the standard R functions for the ANOVA and MANOVA after testing for assumptions.
+In cases where the ANOVA assumptions were not clearly met, I ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm results [@Hollander:2013wz].
 
@@
 
-We have identified four key uncertainties in the method utilized that may affect the estimation of transboundary species.
-Firstly, as we ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), we are not able to identify transboundary stocks within EEZs.
-While we acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
+I have identified four key uncertainties in the method utilized that may affect the estimation of transboundary species.
+Firstly, as I ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), I are not able to identify transboundary stocks within EEZs.
+While I acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
 Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
@@
 This is of special concern, but-not-limited-to [@Archambault:2016ie], highly migratory species whose ranges span multiple jurisdictions and the high seas, such as tunas [@Moore:2020cd], billfishes [@Sepulveda:2019hq] and sharks [@Vandeperre:2014jk] challenging management decisions based on meta-populations [@Moore:2020cd].
-Here, we limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., the US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
-Consequently, our results likely provide a conservative estimate of transboundary species, as we did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
+Here, I limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., the US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
+Consequently, our results likely provide a conservative estimate of transboundary species, as I did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
 Nevertheless, our results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
@@
 Structural differences within Earth System Models result in variations of oceanic conditions, which undoubtedly affect the ENM-Nereus.
-We averaged results from the three models in an effort to capture the structural variation across models.
+I averaged results from the three models in an effort to capture the structural variation across models.
 Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr].
 Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
-To account for such climate variability, we derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
+To account for such climate variability, I derived the ENM-Nereus results as an average of oceanic conditions between 1970 and 2000.
 This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
-Thirdly, we assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+Thirdly, I assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
 While catch data are not exempt of uncertainty, in most cases, differences between the Sea Around Us and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
-Thus, we limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
+Thus, I limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
 Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
@@
 
-We identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
+I identified 633 exploited transboundary species worldwide (67.5% of the 938 species analyzed), almost double previous estimates [@Teh:2015gd].
 Between 2005 and 2014, national fleets targeting these transboundary species within EEZs caught an annual average of 48.5 million tonnes, representing 82.3% of EEZ-derived catches reconstructed by the Sea Around Us at the species level (Figure \@ref(fig:ffvFigure1)a).
@@
 Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].
-When we re-estimated transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
+When I re-estimated transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
 Our results suggest that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
@@
 
-At a regional level, we found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:ffvFigure1)b).
+At a regional level, I found that transboundary species are particularly economically important for Northern America (average country revenue = USD 4,680 $\pm$ 6,000 million) and Eastern Asia (USD 3,779 $\pm$ 3,093 million) (Figure \@ref(fig:ffvFigure1)b).
 The estimated per country revenues from transboundary species in these two regions is significantly different from other regions (one-way ANOVA; DF(16,165) = 5.081, p < 0.001, $\alpha$ = 0.05).
@@
 
-We determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:ffvFigure3); \@ref(fig:ffvFigureS2)).
+I determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:ffvFigure3); \@ref(fig:ffvFigureS2)).
 While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
 Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
-We found significant differences for all catch trend categories for transboundary species (one-way ANOVA, Df(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, Df(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05).
-We also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, Df(2,459) = 19.001, p < 0.001).
+I found significant differences for all catch trend categories for transboundary species (one-way ANOVA, Df(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, Df(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05).
+I also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, Df(2,459) = 19.001, p < 0.001).
 Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:ffvTableS2)).
@@
 This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.
-Moreover, we show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
+Moreover, I show significant differences in the catch trends of transboundary and discrete species, suggesting a need to improve the management of transboundary fisheries.
 Previous work has highlighted that collaboration is key to better outcomes for shared marine resources [@Munro:2002uf].

### 2020-11-26 Scripts/Manuscript_Draft.Rmd
cross referenced chapters

@@
 output:
-  bookdown::pdf_book:
-    toc : no
-    keep_tex: no
-    number_sections: yes
-    fig_width: 6 
-    fig_height: 4 
-geometry: margin=1in
-editor_options:
-  chunk_output_type: inline
+  bookdown::word_document2
+  # bookdown::pdf_book:
+#     toc : no
+#     keep_tex: no
+#     number_sections: yes
+#     fig_width: 6 
+#     fig_height: 4 
+# geometry: margin=1in
 bibliography: ../References/FishForVisa_Ref.bib
 csl: ../References/nature_cc.csl
-header-includes: #allows you to add in your own Latex packages
-- \usepackage{float} #use the 'float' package
-- \floatplacement{figure}{H} #make every figure with caption = h
-- \floatplacement{table}{H}
 ---
@@
   "knitr",
-  "kableExtra",
+  # "kableExtra",
   "png",
@@
   rename("Main Method"=Main_Method) %>%
-  kable("latex", 
-        booktabs = T,
-        caption = "Summary of data sources to estimate species' distributions.
+  knitr::kable(caption = "Summary of data sources to estimate species' distributions.
+All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
+All data is publically available, see references for details")
+
+  # kable("latex",
+  #       booktabs = T,
+  #       caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
 All data is publically available, see references for details") %>%
-  kable_styling(full_width = T) %>%
-  column_spec(2,width = "2cm") %>% #wraps text in column2
-  column_spec(3,width = "5cm") # #wraps text in column2
+  # kable_styling(full_width = T) %>%
+  # column_spec(2,width = "2cm") %>% #wraps text in column2
+  # column_spec(3,width = "5cm") %>%  # #wraps text in column2
+  # as_image()
 ```
@@
            Rules) %>% 
-  kable("latex", 
-        booktabs = T,
-        caption = "Rules to determine the category of each transboundary species") %>%
-  kable_styling(full_width = T) %>%
-  column_spec(1,width = "3cm") %>% #wraps text in column2
-  column_spec(2,width = "13cm") #%>% #wraps text in column2
+  kable(caption = "Rules to determine the category of each transboundary species") #%>%
+  # kable("latex", 
+  #       booktabs = T,
+  #       caption = "Rules to determine the category of each transboundary species") #%>%
+  # kable_styling(full_width = T) %>%
+  # column_spec(1,width = "3cm") %>% #wraps text in column2
+  # column_spec(2,width = "13cm") #%>% #wraps text in column2
   # write_csv("Table_2.csv")
@@
 Among the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) of 598.4 thousand tonnes (8.19%) in total catch and USD 850.2 million (7.17%) in total fishing revenue.
-Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb], and disappearance of some species from EEZs [@Oremus:2020id].
+Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb, Chapter 4], and disappearance of some species from EEZs [@Oremus:2020id].
 Exploring the detailed effects of climate change on the distribution of shared species is key to the development of local adaptation methods that can anticipate negative impacts to sustainability.
-For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen [@PalaciosAbrantes:2020vt], and the economic consequence of such effects can inform the development of more anticipatory and climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
+For example, understanding how climate change will modify the proportion of transboundary species shared by neighboring EEZs, the time-frame over which such changes will happen (Chapter 4), and the economic consequence of such effects can inform the development of more anticipatory and climate-resilient international treaties improving fisheries management [@Sumaila:2020tp].
 

### 2020-12-09 Scripts/Manuscript_Draft.Rmd
Adressing TC comments

@@
 A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk].
-Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; Df(16,158) = 2.265, p = 0.005, $\alpha$ = 0.05).
+Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; DF(16,158) = 2.265, p = 0.005, $\alpha$ = 0.05).
 China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes).
@@
 However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014.
-At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, Df(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:ffvFigure2)).
+At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, DF(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:ffvFigure2)).
 
-```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by Km2 and UN sub-region.
+```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km2 and UN sub-region.
 a) Revenue in thousand 2019 USD.
@@
 Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
-I found significant differences for all catch trend categories for transboundary species (one-way ANOVA, Df(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, Df(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05).
-I also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, Df(2,459) = 19.001, p < 0.001).
+I found significant differences for all catch trend categories for transboundary species (one-way ANOVA, DF(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, DF(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05).
+I also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, DF(2,459) = 19.001, p < 0.001).
 Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:ffvTableS2)).

### 2020-12-09 Scripts/supplements.Rmd
Adressing TC comments

@@
          "Area of EEZs (Km^2)" = size_entity_sum) %>% 
-  kable("latex",
+  kable(
         booktabs = T,
         caption= "Size of all the EEZs in each sub region determined by the United Nations"
-        ) %>%
-  kable_styling(full_width = T)
+        )# %>%
+  # kable_styling(full_width = T)
 ```
@@
   arrange(Category) %>% 
-  kable("latex",
+  kable(
         booktabs = T,

### 2020-12-14 Scripts/Manuscript_Draft.Rmd
Villy's and Tay's comments

@@
 Moreover, recent research shows connectivity across fish stocks through larval dispersal [@Ramesh:2019va] and adult migration [@Levin:2018in; @Popova:2019fs; @Dunn:2019ca], although considerable level of uncertainty exists at different life stages [@Kaplan:2016hs; @Archambault:2016ie].
-For this analysis I only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g., I did not include the high seas).
+For this analysis, I only considered shared species between neighboring EEZs, rather than the species’ extended distribution (e.g., I did not include the high seas).
 I rely on multiple data sources including occurrence, distribution models and catch data, and only consider a species to be present in a grid cell if all data sources showed positive occurrence (see Methods).
@@
 I selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties).
-Note that in call cases I report the average catch from 2005 to 2014.
+Note that in call cases, I report the average catch from 2005 to 2014.
 
@@
   "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50) or Catch < Max. Catch*0.10", #Over explpoited or collapsed
-  "Non of the above rules applied"
+  "None of the above rules applied"
 )
@@
 I have identified four key uncertainties in the method utilized that may affect the estimation of transboundary species.
-Firstly, as I ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), I are not able to identify transboundary stocks within EEZs.
+Firstly, as I ran the analysis at the species level due to limited spatial-specific data on species sub populations (stocks), I am not able to identify transboundary stocks within EEZs.
 While I acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research suggests strong connectivity between stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
+Also, recent research suggests strong connectivity between some stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
 However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
@@
 I averaged results from the three models in an effort to capture the structural variation across models.
-Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., Anchovies and Sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr].
+Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., anchovies and sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr].
 Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
@@
 This is not an issue for the SDM-SAU as it does not directly require environmental variables [@Pauly:2016uz].
-Thirdly, I assumed that, if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
+Thirdly, I assumed that if the Sea Around Us reconstructed data recorded a species as caught in any given grid cell, then the species was present within that grid cell.
 While catch data are not exempt of uncertainty, in most cases, differences between the Sea Around Us and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
@@
 Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
-Finally, this study’s results only considered species for which all datasets agreed on presence and had and Area Index of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
+Finally, this study’s results only considered species for which all datasets agreed on presence and had an Area Index of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
 Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
@@
 
-```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km2 and UN sub-region.
+```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km U+00Bx2 and UN sub-region.
 a) Revenue in thousand 2019 USD.
@@
 I determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:ffvFigure3); \@ref(fig:ffvFigureS2)).
-While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
+While previous studies have demonstrated that catch trends may be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
 Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
@@
 Atlantic Mackerel is a transboundary species that straddles into the high seas.
-Among the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) of 598.4 thousand tonnes (8.19%) in total catch and USD 850.2 million (7.17%) in total fishing revenue.
+Among the countries involved in the 2007 fisheries dispute, Atlantic mackerel contributed an annual average (between 2005 and 2014) of 598 thousand tonnes (8%) in total catch and USD 850 million (7%) in total fishing revenue.
+
 Climate change is expected to continue changing the distribution and shared proportion of fish stocks among countries, resulting in the emergence of new transboundary species [@Pinsky:2018cb, Chapter 4], and disappearance of some species from EEZs [@Oremus:2020id].

### 2020-12-15 Scripts/Manuscript_Draft.Rmd
William final comments

@@
   "knitr",
-  # "kableExtra",
+  "kableExtra",
   "png",
@@
 Shared stocks can be classified into three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more bordering coastal states; "straddling" - stocks that cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
-Our study focuses on the "transboundary" nature of shared species exploited by fisheries operating within EEZs.
+My study focuses on the "transboundary" nature of shared species exploited by fisheries operating within EEZs.
 
@@
 Each source represents a different method of estimating the distribution of a given species, thus providing a more robust result than an analysis focused on a single data source.
-Only commercially fished species with data from all four sources were included in our analysis.
+Only commercially fished species with data from all four sources were included in my analysis.
 
@@
   rename("Main Method"=Main_Method) %>%
-  knitr::kable(caption = "Summary of data sources to estimate species' distributions.
+  kable("latex",
+        booktabs = T,
+        caption = "Summary of data sources to estimate species' distributions.
+All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
+All data is publically available, see references for details") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(2,width = "2cm") %>% #wraps text in column2
+  column_spec(3,width = "5cm")  # #wraps text in column2
+
+# knitr::kable(caption = "Summary of data sources to estimate species' distributions.
 All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
@@
 
-  # kable("latex",
-  #       booktabs = T,
-  #       caption = "Summary of data sources to estimate species' distributions.
-All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data is publically available, see references for details") %>%
-  # kable_styling(full_width = T) %>%
-  # column_spec(2,width = "2cm") %>% #wraps text in column2
-  # column_spec(3,width = "5cm") %>%  # #wraps text in column2
-  # as_image()
 ```
@@
            Rules) %>% 
-  kable(caption = "Rules to determine the category of each transboundary species") #%>%
-  # kable("latex", 
-  #       booktabs = T,
-  #       caption = "Rules to determine the category of each transboundary species") #%>%
-  # kable_styling(full_width = T) %>%
-  # column_spec(1,width = "3cm") %>% #wraps text in column2
-  # column_spec(2,width = "13cm") #%>% #wraps text in column2
-  # write_csv("Table_2.csv")
+  kable("latex",
+        booktabs = T,
+        caption = "Rules to determine the category of each transboundary species") %>%
+  kable_styling(full_width = T) %>%
+  column_spec(1,width = "3cm") %>% #wraps text in column2
+  column_spec(2,width = "13cm")
+
+  # kable(caption = "Rules to determine the category of each transboundary species") #%>%
 ```
@@
 While I acknowledge that a species could have multiple stocks within an EEZ, many fisheries within a country or EEZ are managed at the species instead of stock level.
-Also, recent research suggests strong connectivity between some stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for our analysis [@Popova:2019fs; @Dunn:2019ca].
+Also, recent research suggests strong connectivity between some stocks, even when separated by thousands of kilometers [@Ramesh:2019va] providing additional ecological ground for my analysis [@Popova:2019fs; @Dunn:2019ca].
 However, it is important to acknowledge that there is considerable uncertainty associated in determining levels of connectivity across time and space for marine populations at different life stages, from larvae [@Kaplan:2016hs] to adults [@Archambault:2016ie].
@@
 Here, I limited the definition of “transboundary” to include species spanning only adjacent countries (e.g., the US and Canada), excluding countries that were separated by another nation (e.g., Canada and Mexico) and/or the high seas (e.g., Canada and Spain).
-Consequently, our results likely provide a conservative estimate of transboundary species, as I did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
-Nevertheless, our results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
+Consequently, my results likely provide a conservative estimate of transboundary species, as I did not cover all marine taxa in the world [@Reygondeau:2019uh] and only analyzed species present in all four data sources.
+Nevertheless, my results are representative of a substantial proportion of the world's marine catches and revenue from economically important marine fisheries.
 Secondly, the predicted species' distribution is affected by the uncertainties of the environmental data and models used for such predictions.
@@
 While catch data are not exempt of uncertainty, in most cases, differences between the Sea Around Us and the FAO self-reported data are smaller towards the end of the time series [@Pauly:2019bf].
-Thus, I limited the catch data reference period in our analyses to between 2005 and 2014, the last ten years of data available.
+Thus, I limited the catch data reference period in my analyses to between 2005 and 2014, the last ten years of data available.
 Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
 Finally, this study’s results only considered species for which all datasets agreed on presence and had an Area Index of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
-Therefore, again, our approach presents a relatively conservative estimate of the number of transboundary species in the world.
+Therefore, again, my approach presents a relatively conservative estimate of the number of transboundary species in the world.
 Using a smaller Area Index will result in more transboundary species (Figure \@ref(fig:ffvFigureS2)).
@@
 These catches generated a yearly average of USD 77,591 million in fishing revenue (78.5% of global fishing revenue) over the same time period.
-Our findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].
+My findings are considerably higher than the previous estimates of 34.2 million tonnes in catches and USD 40,187 million (in 2019 value) in fishing revenue from shared stocks [@Teh:2015gd].
 When I re-estimated transboundary species’ catches using data consistent with those used in previous studies (FAO global reported data in year 2006), the 633 transboundary species identified here accounted for 40.4 million tonnes of annual catches (i.e., 18% higher than previously estimated).
-Our results suggest that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
+My results suggest that the contribution of transboundary species to global catch and fishing revenue might previously have been  underestimated due to an incomplete understanding of the transboundary nature of marine fished species.
 The 305 non-transboundary species (termed as ‘discrete’ species here, see Methods - Determining transboundary species trait) accounted for a much smaller proportion of total catch and revenue; 2.8 million tonnes and USD 4,282 million annually respectively, on average, between 2005 and 2014.
@@
 
-In many cases, according to our categorization criteria, a transboundary species can be distributed in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
+In many cases, according to my categorization criteria, a transboundary species can be distributed in multiple EEZs but only counted as transboundary in a subset of EEZs (see Methods).
 For example, the distribution of Peruvian anchoveta (*Engraulis ringens*) spans the EEZs of Peru, Chile, and Ecuador.
-However, our study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
-Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see Methods - Criteria 3) and thus do not meet our criteria for consideration as a transboundary stock.
+However, my study only considered the stocks in Peru and Chile as transboundary [@Cashion:2018cg].
+Anchoveta in Ecuadorian waters only include a small proportion of the shared distribution range (spatial threshold between Ecuador and Peru < 10%; see Methods - Criteria 3) and thus do not meet my criteria for consideration as a transboundary stock.
 A situation similar to the example of Peruvian anchoveta in Ecuadorian waters is common amongst the transboundary species identified in this study.
-Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet our criteria for consideration as transboundary stock.
+Overall, 590 of the 633 transboundary species have stocks in EEZs that do not meet my criteria for consideration as transboundary stock.
 The annual average contribution from all excluded stocks of transboundary species to fisheries (e.g., Ecuador’s anchoveta catch) between 2005 and 2014 was 10.8 million tonnes, representing USD 19,243 million in fishing revenue over the same time period.
@@
 
-```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km U+00Bx2 and UN sub-region.
+```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km2 and UN sub-region.
 a) Revenue in thousand 2019 USD.
@@
 While previous studies have demonstrated that catch trends may be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status.
-Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
+My intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods).
 I found significant differences for all catch trend categories for transboundary species (one-way ANOVA, DF(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, DF(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05).
@@
 Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
-Our results show that captures and revenues from shared species are substantially higher than previously estimated [@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
+My results show that captures and revenues from shared species are substantially higher than previously estimated [@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.
 This result highlights the importance of transboundary fisheries and their potential contribution to food and nutrition security, as well as livelihoods.

### 2020-12-15 Scripts/supplements.Rmd
William final comments

@@
 Category A, Increasing; Category B, Constant; Category C, Decreasing.
-“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
-Figure created using R version 3.5.2."}
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data."}
 img <- readPNG("../Figures/FigS2.png")
@@
 ```{r ffvFigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis.
-Figure created using R version 3.5.2."}
+The darker histogram represents the threshold (25%) used in the present analysis."}
 img <- readPNG("../Figures/FigS3.png")

### 2020-12-19 Scripts/Manuscript_Draft.Rmd
final remarks

@@
 I used the Sea Around Us catch reconstruction database from 2005 to 2014 as the fourth dataset to estimate transboundary species and to estimate their catch contribution within EEZs.
-I selected this time frame to investigate the recent (our time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties).
+I selected this time frame to investigate the recent (my time frame includes the last decade of available data) contribution of transboundary fisheries to catches and revenue from fisheries and to reduce the uncertainty embedded in the reconstruction process (see Key Uncertainties).
 Note that in call cases, I report the average catch from 2005 to 2014.
@@
 
-```{r ffvFigure1, eval = T, fig.width=10, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
+```{r ffvFigure1, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue.
 a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively.
@@
 Points = mean \u00B1 sd.
-Revenue in 2010 real USD"}
+Revenue in 2010 real USD",fig.scap="Number of transboundary species and their contribution to global fisheries catch and revenue.",out.extra=''}
 
@@
 Points = sub-region mean \u00B1 s.d.
-by country."}
+by country.",fig.scap="Weighted benefits of transboundary species by km2 and UN sub-region.",out.extra=''}
 
@@
 
-```{r ffvFigure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ.
+```{r ffvFigure3, eval = T, fig.width=14, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ.
 Category A, Increasing; Category B, Constant; Category C, Decreasing.
 “No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
-Only showing first 100 species."}
+Only showing first 100 species.",fig.scap="Number of transboundary species by catch trend and EEZ.",out.extra=''}
 
@@
 
-```{r ffvFigure4, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species.
+```{r ffvFigure4, eval = T, fig.width=14, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species.
 a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase.
@@
 Note that there could be > 5 species due to similar sharing values.
-The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase"}
+The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase",fig.scap="Number of EEZs shared by transboundary species.",out.extra=''}
 
@@
 
-Our study identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
+In this chapter, I identified species currently shared by neighboring coastal nations and highlights the importance of these species’ contribution to global catch and revenue derived from wild fisheries.
 My results show that captures and revenues from shared species are substantially higher than previously estimated [@Teh:2015gd] and also much greater than catches and revenues obtained from discrete species.

### 2020-12-19 Scripts/supplements.Rmd
final remarks

--- 2020-12-09 Scripts/supplements.Rmd
@@
 ```{r ffvFigureS1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch.
-The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon.
-Figure created using R version 3.5.2.
-Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively."}
+The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon", fig.scap="Number of transboundary species per EEZ and their contributions to countries' EEZ catch", out.extra=''}
 img <- readPNG("../Figures/FigS1.png")
@@
 Category A, Increasing; Category B, Constant; Category C, Decreasing.
-“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.
-Figure created using R version 3.5.2."}
+“No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.", fig.scap="Percentage of transboundary species by catch trend and EEZ.", out.extra=''}
+
 img <- readPNG("../Figures/FigS2.png")
@@
 the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4.
-The current analysis utilized a 25% Area Index threshold (Figure \@ref(fig:ffvFigureS3)) - darker histogram).
+The current analysis utilized a 25% Area Index threshold (Figure \@ref(fig:ffvFigureS3) - darker histogram).
 
-```{r ffvFigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values.
-The darker histogram represents the threshold (25%) used in the present analysis.
-Figure created using R version 3.5.2."}
+```{r ffvFigureS3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap = "Histogram of number of transboundary species using different Area Index threshold values."}
+
 img <- readPNG("../Figures/FigS3.png")

### 2021-03-14 Scripts/Manuscript_Draft.Rmd
fixed crash

@@
 output:
-  bookdown::word_document2
-  # bookdown::pdf_book:
-#     toc : no
-#     keep_tex: no
-#     number_sections: yes
-#     fig_width: 6 
-#     fig_height: 4 
+  # bookdown::word_document2
+  bookdown::pdf_book:
+    toc: no
+    keep_tex: no
+    number_sections: yes
+    fig_width: 6
+    fig_height: 4
 # geometry: margin=1in
-bibliography: ../References/FishForVisa_Ref.bib
-csl: ../References/nature_cc.csl
+# bibliography: ../References/FishForVisa_Ref.bib
+# csl: ../References/nature_cc.csl
 ---
@@
 
-```{r supplements, child = 'supplements.Rmd', eval = F}
+```{r supplements, child = 'supplements.Rmd', eval = T}
 ```

### 2021-03-19 Scripts/Manuscript_Draft.Rmd
grammatical changes to chapter

@@
 output:
-  # bookdown::word_document2
-  bookdown::pdf_book:
+  bookdown::word_document2:
+  # bookdown::pdf_book:
     toc: no
@@
 # geometry: margin=1in
-# bibliography: ../References/FishForVisa_Ref.bib
+bibliography: ../References/FishForVisa_Ref.bib
 # csl: ../References/nature_cc.csl
@@
 
-```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
+```{r ffsetup, eval = T, echo=F, warning=F,message=F, results='hide'}
 
@@
 
-Abreviation <- c(
+Abbreviation <- c(
   "Occurrence",
@@
 data.frame(Source,
-           Abreviation,
+           Abbreviation,
            Main_Method,
@@
         caption = "Summary of data sources to estimate species' distributions.
-All data has a ressolution of 0.5 degrees latitude x 0.5 degrees longitude.
-All data is publically available, see references for details") %>%
+All data has a resolution of 0.5 degrees latitude x 0.5 degrees longitude.
+All data is publicly available, see references for details") %>%
   kable_styling(full_width = T) %>%
@@
 In addition to occurrence data, I used two different methods to estimate species distributions, hereafter referred to as Ecological Niche Model-Nereus (ENM-Nereus) and Species Distribution Model-SAU (SDM-SAU).
-Although they use the same occurrence and environmental data, the models are structurally different complementing each other and providing robustness to the results.
+Although they use the same occurrence and environmental data, the models are structurally different complementing each other and providing robustness to my results.
 
@@
 As mentioned above, I define transboundary species as those marine species that occur within the EEZs of two or more neighboring countries.
-Hence, according to this criteria a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
+Hence, according to this criterion a species was only considered as transboundary if it was shared between two neighboring countries, regardless of the species extended distribution.
 The analysis was undertaken only within the boundaries of the EEZs of coastal states using the Sea Around Us shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) - noting that it subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico's EEZ is divided in Mexico Pacific and Mexico Atlantic), including islands territories - and determined the intersections between polygons using the R package sf [@PackagesfSimpleF:2018vp].
-When estimating transboundary species, I filtered out those shared by EEZs sub-regions (e.g., USA Gulf of Mexico and USA Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
+When estimating transboundary species, I filtered out those shared by EEZs sub-regions (e.g., US Gulf of Mexico and US Atlantic), and when aggregating results by country, species that occurred in more than one sub-region were only accounted for once.
 Species that were present in EEZs that were non-continental territories neighboring other countries were kept as separate (e.g., Argentina and Falkland Islands), but removed in cases where the non-continental territory belonged to the same nation (e.g., Brazil and Fernando de Noronha).
@@
 This rule assumes that if a commercial species is projected within the EEZ of any fishing country, such a species would have been fished, and thus likely reported at some point over the last decade of data (2005 - 2014), thereby validating the models and selecting "currently" shared species.
-I acknowledge that this criteria might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
+I acknowledge that this criterion might limit the global distribution of species therefore resulting in a conservative estimate of transboundary species.
 
@@
 I averaged results from the three models in an effort to capture the structural variation across models.
-Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., anchovies and sardines "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr].
+Natural climate variability is a major driver of marine species' distributions, potentially removing a species from an EEZ for long periods (e.g., anchovies and sardines' "regimes" in the Eastern Pacific are strongly influenced by water temperature decal oscillations [@Chavez:2003jr].
 Thus, a species’ distribution can potentially be reduced or shifted in such a way that it only covers one EEZ until oceanic conditions change again and the associated species' distribution expands.
@@
 Likewise, the spatial allocation of the catch is subjected to imprecision, mainly produced by differences in the spatial scale of the original data and the method employed by the Sea Around Us.
-Finally, this study’s results only considered species for which all datasets agreed on presence and had an Area Index of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
+Finally, this chapter’s results only considered species for which all datasets agreed on presence and had an Area Index of at least 25% (e.g., the species shared distribution was at least 25% in each EEZ).
 Therefore, again, my approach presents a relatively conservative estimate of the number of transboundary species in the world.

### 2021-03-19 Scripts/Manuscript_Draft.Rmd
added high seas descrete stocks

@@
 However, EEZ boundaries cut across the distribution of many species, creating shared stocks between nations [@UnitedNations:1986tl].
-Shared stocks can be classified into three non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more bordering coastal states; "straddling" - stocks that cross neighboring EEZs and the adjacent high seas; and "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas) [@Munro:2004th].
+Shared stocks can be classified into four non-exclusive categories; "transboundary" - stocks that cross the EEZs of two or more bordering coastal states; "straddling" - stocks that cross neighboring EEZs and the adjacent high seas; "highly migratory" - stocks that cross non-neighboring EEZs and the high seas (mainly tunas); and finally "discrete" - stocks that are only present in the high seas [@Munro:2004th].
 My study focuses on the "transboundary" nature of shared species exploited by fisheries operating within EEZs.

### 2021-04-06 Scripts/Manuscript_Draft.Rmd
Misc. for thesis submission

@@
 output:
-  bookdown::word_document2:
-  # bookdown::pdf_book:
+  bookdown::pdf_book:
     toc: no
@@
     fig_height: 4
+    latex_engine: xelatex
+header-includes:
+   - \usepackage[utf8]{inputenc}
 # geometry: margin=1in
@@
 Identifying existing transboundary species is the first step towards cooperative joint management frameworks that are precautionary, strive for sustainability, and can be flexible to accommodate the uncertain future driven by climate change.
-
-<!-- ## References -->
-
-<!-- <div id="refs"></div> -->
-
-<!-- ## Supplements -->
-
-```{r supplements, child = 'supplements.Rmd', eval = T}
-```

### 2022-06-30 Scripts/Initial_Analysis.Rmd
Incorporated straddling analysis to transboundary analysis

@@
 
+## Methods for straddling stocks
+
+1.- Get transboundary species list
+
+1.1- Remove highly migratory species based on literature
+
+2- High seas shapefile
+
+2.1- FAO Areas ID
+
+3.- Identiy what transboundary species are actually straddling
+
+4.- Be happy, happy like a hippo
+
+### Shapefiles
+
+```{r}
+
+# World land maps
+world_land <- ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
+  st_transform(crs = 4326)# 4326
+
+# ggplot(world_land) +
+#   geom_sf()
+
+# FAO regions
+fao_regions <- my_sf("FAO") %>% 
+  filter(F_LEVEL == "MAJOR")
+st_crs(fao_regions) = 4326
+
+# head(fao_regions)
+
+# fao_regions %>% 
+#   ggplot() +
+#   geom_sf(aes(fill = F_AREA))
+
+# EEZs
+world_eez <- my_sf("SAU",simple = 1000)
+
+# Lon-lat DBEM
+
+# First get Vicky's data to get high seas
+EEZ_CellID <- my_path("Spa","DBEM", "EEZ_CellID.xlsx", read = TRUE)
+colnames(EEZ_CellID) <- c("EEZID","index")
+
+# Now our gridcell
+abny <- my_path("Spa","DBEM","Lon_Lat_DBEM.txt",read = T, header = F) %>% 
+  bind_cols(my_path("Spa","DBEM","WArea.txt",read = T, header = F)) %>% 
+  filter(!index %in% EEZ_CellID$INDEX) %>% 
+  mutate(cat = ifelse(v1>0, "abnj","land")) %>% 
+  select(-v1)
+
+# SAVE FOR COMPLETE DBEM
+complete_lon_lat_dbem <- my_path("Spa","DBEM","Lon_Lat_DBEM.txt",read = T, header = F) %>% 
+  left_join(abny) %>% 
+  mutate(cat = ifelse(is.na(cat), "eez",cat))
+
+# Save for fouture
+# write_csv(complete_lon_lat_dbem, my_path("Spa", "DBEM","complete_lon_lat_dbem.csv"))
+
+  ggplot(complete_lon_lat_dbem) +
+  geom_tile(
+    aes(
+      x = lon,
+      y = lat,
+      fill = cat
+    )
+  )
+
+# All maps test
+# ggplot() +
+#   geom_sf(data = fao_regions, aes()) +
+#   geom_sf(data = world_land, aes()) +
+#   geom_sf(data = world_eez, aes())
+
+  # First get Vicky's data to get high seas
+EEZ_SAU <- my_path("Spa","DBEM", "Updated_EEZList_17June2016.xlsx", read = TRUE)
+colnames(EEZ_SAU) <- c("sau_code","eez")
+
+# First get Vicky's data to get high seas
+EEZ_CellID <- my_path("Spa","DBEM", "EEZ_CellID.xlsx", read = TRUE)
+colnames(EEZ_CellID) <- c("sau_code","index")
+
+complete_sau <- EEZ_SAU %>% 
+  left_join(EEZ_CellID)
+
+#   
+# coords %>% 
+#   left_join(EEZ_CellID) %>% 
+#     rename(sau_eez_id = EEZID) %>% 
+#     gather("code_na","code",f_code:sau_eez_id) %>%
+
+  # write_csv(Coord, my_path("Spa", "DBEM","complete_lon_lat_dbem.csv"))
+```
+
+### Determining straddling stocks
+
+```{r GetSppDistFun}
+
+GetSppDist=function(Spp,Model,Coord){
+
+  Distpath <- paste(Data_Path,"Data/Distribution/",sep="")
+  INDEX = seq(1,259200,1)
+  # INDEX <- Coordinates$INDEX
+
+  # SAU Distributions
+  if(Model == "SAU_D"){
+    File_Name <- paste("SAU_Distribution/DIST_GOOD_SP_")
+  }
+
+  # SAU Catch
+  if(Model == "SAU_C"){
+    File_Name <- paste("SAU_data_per_species/CATCH_SP_")
+  }
+
+  # Occurence
+  if(Model == "Occ"){
+    File_Name <- paste("Occurence/OCCURENCE_JULIANO_")
+  }
+
+  # ENM Model
+  if(Model == "ENM"){
+    File_Name <- paste("ENM/ENM_JULIANO_")
+  }
+
+  # DBEM Data
+  # if(Model == "DBEM"){
+  #   Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData
+  #   Final_Path <- "ENM"
+  #   File_Name <- paste("ENM_JULIANO",Spp,".mat",sep="")
+  # }
+
+  if(Model == "All"){
+
+    Models_List <- c(paste(Distpath,"SAU_Distribution/DIST_GOOD_SP_",Spp,".mat",sep =""),
+                     paste(Distpath,"Occurence/OCCURENCE_JULIANO_",Spp,".mat",sep=""),
+                     paste(Distpath,"ENM/ENM_JULIANO_",Spp,".mat",sep="")
+    )
+
+    # Jumps species not modeled. NOTE: We only need one as ENM, Occ and SAU Dis have all the same 939 spp
+    if(file.exists(Models_List[1])){
+
+      Load <- lapply(Models_List, FUN=R.matlab::readMat, na.strings=0)
+
+      sppdist <- as.data.frame(bind_cols(Load)) %>% 
+        mutate(
+          INDEX = INDEX,
+          TaxonKey = Spp
+        )
+      colnames(sppdist) <- c("SAU_D","Occ","ENM","INDEX","TaxonKey")
+
+      #### Step for SAU catch data that has to be averaged
+      File_Name <- paste("SAU_data_per_species/CATCH_SP_")
+      SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
+
+      # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
+      SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
+        select(CATCH.1:CATCH.65) %>% 
+        mutate(INDEX = INDEX) %>% 
+        gather("Year","Catch",CATCH.56:CATCH.65) %>% # Last 10 years of data
+        group_by(INDEX) %>% 
+        summarise(SAU_C = mean(Catch,na.rm=T))
+
+      # Join both tables
+      sppdist <- sppdist %>% 
+        left_join(SAU_C_data,
+                  by = "INDEX") %>% 
+        select(TaxonKey,INDEX,everything()) %>% 
+        left_join(CoorG,
+                  by = "INDEX")
+
+      # Fix coordinate system incompatibility between Gab and DBEM
+      sppdist <- suppressWarnings(sppdist[order(sppdist$latitude, rev(sppdist$longitude),decreasing=TRUE), ] %>% 
+                                    mutate(INDEX = seq(1,259200,1)) %>% 
+                                    gather("Model","Value",3:6) %>%
+                                    mutate(Value = ifelse(is.na(Value), 0, Value)) # Converting NA's to ceros
+      )
+
+      getSppDist = sppdist
+
+    }
+
+  }else{
+
+    # Merge paths
+    SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
+
+    if(file.exists(SppPath) == TRUE){
+
+      #Install (if needed) R.matlab package
+      if(!require(R.matlab)){
+        install.packages("R.matlab")
+      }
+
+      # Read Files
+
+      sppdist <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
+        mutate(INDEX = INDEX,
+               Species = Spp) %>% 
+        left_join(Coord)
+
+      # Fix coordinate system incompatibility between Gab and DBEM
+      sppdist <- sppdist[order(sppdist$latitude, rev(sppdist$longitude),decreasing=TRUE), ] %>% 
+        mutate(INDEX = seq(1,259200,1))
+
+      # Return 
+      getSppDist=sppdist
+
+    }else{
+      print(paste("No info for this species",Spp, "in",Model))
+    }
+
+  }
+}
+```
+
+```{r StraddIndexFun}
+
+StraddIndex <- function(Spp,Model = "All",Neighbours,Coord,Index_Code){
+
+  # Get model data from spps
+  SppDist <- GetSppDist(Spp,Model,Coord)
+
+    # Result 1. Number of Countries that share the species
+
+  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
+  Trans_Spp <- SppDist %>%
+    filter(#INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
+      Model != "SAU_C") %>% # Only using observational and modelled data
+    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
+    filter(Value > 0) %>%
+    group_by(TaxonKey,
+             INDEX
+    ) %>%
+    summarise(Model_Index = sum(Value,na.rm=T)/3
+    ) %>%
+    filter(Model_Index > 0.4) %>% # at least 2 sources agree
+    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
+    left_join(SppDist,
+              by = c("TaxonKey","INDEX")) %>%
+    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
+           Value > 0) %>%
+    mutate(Model_Index = Model_Index*100) %>%
+    select(-Model, -Value, -latitude,-longitude) %>%
+    rename(index = INDEX) %>% 
+    # joint eez names
+    left_join(Index_Code,
+              by = "index") %>% 
+    # joint fao area names
+    left_join(fao_areas,
+              by = "index") %>% 
+    mutate(
+      territory = ifelse(!is.na(name),name,name_en),
+      category = ifelse(!is.na(name),"eez","fao"),
+    ) %>% 
+    select(1:3,territory,category) %>% 
+    clean_names() %>% 
+    filter(model_index == 100)
+
+  # Distributional test
+  # test <- Trans_Spp %>% 
+    # left_join(coords)
+
+  # ggplot(test) +
+  #   geom_tile(
+  #     aes(
+  #       x = lon,
+  #       y = lat,
+  #       fill = category
+  #     )
+  #   )
+
+  # Step 2.1. Determines not a straddling stock
+  if("fao" %in% Trans_Spp$category == FALSE){
+
+    # output <- Spp_Grid %>% 
+    #   select(
+    #     taxon_key,
+    #     territory,
+    #     neighbour
+    #   ) %>% 
+    #   mutate(straddling = "no")
+    return(print("not a straddling stock"))
+    stop()
+
+  }else{
+
+    # MODEL INDEX (TRESHOLDS 1 & 2) #
+    Model_Index_D <- Trans_Spp %>% 
+      group_by(territory,
+               category,
+               taxon_key,
+               model_index
+      ) %>% 
+      summarise(n_cells_spp = n()) %>% 
+      select(-n_cells_spp)
+
+    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
+    # The number of species' cells present within each country's EEZ
+
+    # if(n_Territory > 1){
+
+    #Step 1.  Get EEZ id and Neighbour
+    Neighbours_List <- neighbours %>%
+      group_by(territory,neighbour) %>%
+      summarise(n=n()) %>%
+      ungroup() %>%
+      select(-n) %>% 
+      left_join(fao_to_sau) %>% 
+      filter(!is.na(territory))
+
+    # Set FAO neighbours... 
+    fao_neighbours <- Neighbours_List %>% 
+      select(territory,fao_area_name) %>% 
+      rename(territory = fao_area_name,
+             neighbour = territory) %>% 
+      group_by(territory, neighbour) %>% 
+      summarise(n())
+
+    fao_territory <- fao_neighbours %>% 
+      rename(territory = neighbour,
+             neighbour = territory)
+
+    neighbours_list_fao <- fao_neighbours %>% 
+      bind_rows(Neighbours_List,fao_territory) %>% 
+      select(-fao_area_name)
+
+    # Step 2. Determines the amount of grids present in each country
+    Spp_Grid <- Trans_Spp %>% 
+      group_by(taxon_key,
+               model_index, # Un-comment after producing models x datasets
+               territory,
+               category) %>% 
+      summarise(n_spp_eez = length(unique(index))) %>% 
+      left_join(neighbours_list_fao,
+                by = "territory") %>% 
+      filter(territory %in% Trans_Spp$territory, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
+             neighbour %in% Trans_Spp$territory)
+
+    # Split dataframes to merge latter
+    Territory_T <- Spp_Grid %>% 
+      filter(category == "eez") %>% 
+      ungroup() %>% 
+      select(
+        model_index, # Un-comment after producing models x datasets
+        taxon_key,
+        Name=territory,
+        n_spp_eez
+      )
+
+    Neighbour_T <- Spp_Grid %>%
+      filter(category == "eez") %>% 
+      ungroup() %>% 
+      select(
+        model_index,
+        taxon_key,
+        n_spp_eez,
+        territory,
+        Name=neighbour,
+        territory
+      )
+
+    fao_grid <- Spp_Grid %>% 
+      filter(category == "fao") %>% 
+      left_join(neighbours_list_fao) %>% 
+      select(Name =neighbour,
+             fao_name = territory,
+             n_spp_eez.z = n_spp_eez)
+
+    # Merge dataframes to get totals per Neighbourds
+    Area_Index_D <- full_join(Territory_T,
+                              Neighbour_T, 
+                              by = c("model_index","Name","taxon_key")
+    ) %>%
+      left_join(fao_grid) %>% 
+      filter(!is.na(fao_name)) %>% # remove non-straddling stocks
+      rowwise() %>%
+      mutate(spp_total = sum(n_spp_eez.x,n_spp_eez.y,n_spp_eez.z,na.rm=T)) %>% # Total gridcelles per Neighbours
+      distinct() %>% # Removes false duplicates from `full_join()`
+      rename(territory = Name,
+             neighbour = territory,
+             n_spp_country = n_spp_eez.x,
+             n_spp_neighbour = n_spp_eez.y,
+             n_spp_fao_area = n_spp_eez.z) %>%
+      # Estimate if it is straddling
+      mutate(stradling_index = (n_spp_fao_area/spp_total)*100)
+
+    ### Save spp dataframe
+
+    output <- Area_Index_D %>% 
+      select(taxon_key,
+             territory,
+             neighbour,
+             fao_name,
+             stradling_index)
+
+    File_Name <- paste(Spp,"_straddling.csv",sep = "")
+    Save_Path <- my_path("R","EEZ/Stradling_Results/", File_Name)
+
+    # Save_Path <- paste(Results_Path,"Trans_Results/",File_Name,sep="")
+
+    write_csv(output,
+              Save_Path)
+  }
+} # closes function
+
+ #Test me  
+# suppressMessages(
+#   StraddIndex(600069, Model = "All", Coord = coords, Index_Code = Index_Code)
+# )
+
+```
+
+### Straddling Control pannel
+
+```{r}
+# DBEM coordinate system
+# complete_lat_lon <- my_path("Spa", "DBEM","complete_lon_lat_dbem.csv", read = T)
+
+# Gabriel's coordinate system
+CoorG <- my_path("G","FishForVisa/Data/Spatial/","coordinates_gab.csv",read =T) %>%
+  mutate(INDEX = seq(1,259200,1))
+
+# Get fao areas on DBEM grid
+fao_areas <- my_path("Spa", "DBEM","complete_lon_lat_dbem.csv", read = T) %>% 
+  filter(cat == "abnj")
+
+# Fao combo
+fao_to_sau <- read_excel("/Volumes/DATA/JULIANO_NEYMAR/Spatial/SAU/EEZ-FAO-Country-Combo.xlsx") %>% 
+  select(territory = eez_name,eez_id,fao_area_name)
+
+# Neighboring dataset
+neighbours <- read_excel("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Data/Spatial/EEZ_Neighbour_List.xlsx") %>% 
+  clean_names() %>% 
+  rename(eez_id = eezid) %>% 
+  left_join(fao_to_sau,
+            by = "eez_id") %>% 
+  select(territory = territory.x,neighbour)
+
+# Load FishForVisa Results
+transboundary_spp <- read_csv("https://media.githubusercontent.com/media/jepa/FishForVisa/master/Data/Results/Clean_Results_Trans.csv") %>% 
+  # Set same filters as in FishForVisa
+  filter(
+    area_index >= 0.25,
+    area_index <= 1-0.25,
+    model_index >= 100
+  )
+
+# DepPelingo
+
+depth_profile <- my_path("G","FishForVisa/Data/Distribution/Species","SppTaxonName.csv", read = T)
+
+# Double check we have 633 species
+length(unique(transboundary_spp$taxon_key)) # 633
+
+coords <- my_path("Spa","DBEM","Lon_Lat_DBEM.txt",read = T, header = F)
+
+Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/" #x
+
+# SAU relations between INDEX and Country's EEZs
+# First get Vicky's data to get high seas
+EEZIDs_List <- my_path("Spa","DBEM", "Updated_EEZList_17June2016.xlsx", read = T) #x
+EEZ_CellID <- my_path("Spa","DBEM", "EEZ_CellID.xlsx", read = TRUE) #x
+colnames(EEZ_CellID) <- c("eezid","index") #x
+
+Index_Code <- EEZIDs_List %>%  #x
+  left_join(EEZ_CellID)
+
+```
+
+```{r run_me, eval = T}
+
+suppressWarnings(
+  suppressMessages(
+    lapply(unique(transboundary_spp$taxon_key), StraddIndex, Model = "All", Coord = coords,
+           Index_Code = Index_Code)
+  )
+)
+
+```
+
 # Results
@@
 
-GetTransResults=function(Spp){
-
+GetTransResults=function(Spp, type = "NA"){
+
+  if(type == "strad"){
+    # Set the path for each file
+  Distpath <- paste(my_path("R","EEZ/Straddling_Results/"),Spp,"_straddling.csv",sep="")
+
+  }else{
   # Set the path for each file
@@
 
+  }
+
   # Loads all files in a df
   Load_Data <- bind_rows(lapply(Distpath, FUN=fread))
-
   return(Load_Data)
@@
 ````
+
+### High migratory species
+
+Remove highly migratory species according to UNCLOS extracted from FAO (Maguire et all).
+The above tuna species listed as highly migratory species in Annex 1 of UNCLOS have extensive distribution on the high seas
+
+Maguire, J-J., Sissenwine, M., Csirke, J., Grainger, R., & Garcia, S. (2006). The state of world highly migratory, straddling and other high seas fishery resources and associated species. FAO.
+
+```{r highly_migratory_species}
+
+high_mig_taxa <- c("Thunnus alalunga", "Thunnus thynnus","Thunnus orientalis","Thunnus obesus","Katsuwonus pelamis", "Thunnus albacares","Thunnus atlanticus","Euthynnus alletteratus","Euthynnus affinis","Thunnus maccoyii", "Auxis thazard", "Auxis rochei",# Tuna-likes
+                   "Tetrapturus angustirostris", "Tetrapturus belone", "Tetrapturus pfluegeri", "Tetrapturus albidus", "Tetrapturus audax", "Tetrapturus georgei", "Makaira indica", "Makaira nigricans","Istiophorus platypterus", "Istiophorus albicans","Xiphias gladius")
+
+length(high_mig_taxa) # 23
+
+high_mig_spp <- my_path("D","Distribution/Species","SppTaxonName.csv", read = T) %>% 
+  filter(taxon_name %in% high_mig_taxa)
+
+nrow(high_mig_spp) # 21
+
+# ---------------- 
+# Missing 4 species
+# missing_hm_spp <- as.data.frame(x = high_mig_taxa) %>% 
+  # filter(!high_mig_taxa %in% high_mig_spp$taxon_name)
+
+# Tetrapturus belone # only found in the med				
+# Tetrapturus georgei # Misspselled, correct name Tetrapturus georgii but not identified in the SAU dataset
+
+# ---------------- # missing data
+```
+
 ## Load Results data
@@
 ```{r Load_Results_Data, eval = F}
+
+# ----------------- #
+# STRADDLING
+# ----------------- #
+fao_areas <- my_path("Spa", "DBEM","complete_lon_lat_dbem.csv", read = T) %>% 
+  filter(cat == "abnj")
+
+# Get species taxon data
+taxon_list <- my_path("G","FishForVisa/Data/Distribution/Species","SppTaxonName.csv", read = T)
+
+# Load straddling species
+# Spp list
+spp_complete <- list.files(my_path("R","EEZ/Straddling_Results/"))
+
+stradling_spp <- str_replace(spp_complete,"\\_.*","")
+
+stradd_data <- bind_rows(
+  lapply(stradling_spp,GetTransResults, type = "strad")
+  ) %>% 
+  left_join(taxon_list) %>% 
+  select(taxon_key,taxon_name,dem_pel, everything()) %>% 
+  mutate(category = ifelse(taxon_key %in% high_mig_spp$taxon_key,"high_migratory","straddling"))
+
+# Complete transboundary data
+
+stradd_hs_spp <- stradd_data %>% 
+  select(taxon_key,category,sf_eez_name = territory, eez_neighbour = neighbour) %>% 
+  unique()
 
@@
 
+# Get species taxon data
+taxon_list <- my_path("G","FishForVisa/Data/Distribution/Species","SppTaxonName.csv", read = T)
+
 Results_Path <- my_path("R")
@@
 
+# STRADDLING: needed
 Species_Sampled <- fread(paste(my_path("D"),"Distribution/Sampled_Species.csv", sep =""))
@@
 
-Clean_Results_Trans <- Raw_Results_Trans %>% 
-  CleanResults(.,matching_names) %>% 
+# Clean_Results_Trans <- Raw_Results_Trans %>% 
+#   CleanResults(.,matching_names) %>% 
+#   rename(sf_eez_name = eez_name) %>% 
+#   left_join(matching_names,
+#             by = "sf_eez_name") %>% 
+#   rename(eez_name = sf_eez_name,
+#          fishing_entity = sau_fishing_entity)
+
+Clean_Results_Trans <- my_path("R","EEZ","Clean_Results_Trans.csv", read = T) %>% 
   rename(sf_eez_name = eez_name) %>% 
-  left_join(matching_names,
-            by = "sf_eez_name") %>% 
-  rename(eez_name = sf_eez_name,
-         fishing_entity = sau_fishing_entity)
+  left_join(matching_names)
 
@@
 
+# Used for STRADDLING too
 SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
@@
 
+## STRADLING
+shared_species <- Tresholded_T_Data %>% 
+  left_join(stradd_hs_spp) %>% 
+  mutate(category = replace_na(category,"transboundary"))
+
+shared_classification <- shared_species %>% 
+  select(taxon_key,category,sf_eez_name) %>% 
+  unique()
+
 ```
@@
 ## Overall results
+
+### Straddling Species
+
+```{r}
+
+# Number of species that are straddling or highly migratory
+stradd_data %>% 
+  group_by(category) %>% 
+  summarize(
+    n_spp = length(unique(taxon_key)),
+    prop = round((length(unique(taxon_key))/633)*100)
+    )
+
+# RESULT
+# category  n_spp   prop of transboundary
+# high_mig	 20	     3		
+# stradd	   84	    13	
+# total     104     16
+
+EEZIDs_List <- my_path("Spa","DBEM", "Updated_EEZList_17June2016.xlsx", read = T) %>% 
+  rename(eez_name = name)
+
+# Econ value
+Summary_Trans <- SAU_Sampled_Data %>% 
+  semi_join(Tresholded_T_Data,
+            by = c("taxon_key","fishing_entity_id")
+  ) %>% 
+  group_by(Variable) %>%
+  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
+  left_join(Total_SAU_Sampled) %>% 
+  left_join(Total_SAU_Global) %>% 
+  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
+         Per_SAU = Total_Trans/Total_Global*100)
+
+```
 

### 2022-07-08 Scripts/Initial_Analysis.Rmd
got high seas data

@@
 
-```{r Fun_GetTransResults, eval = F}
+```{r Fun_GetTransResults, eval = T}
 
@@
   select(taxon_key,category,sf_eez_name = territory, eez_neighbour = neighbour) %>% 
-  unique()
-
+  unique() %>% 
+  left_join(matching_names,
+            by = "sf_eez_name") %>% 
+  select(1:4,fishing_entity_id)
+
+# STRADDLING: Dataset to match all SAU names
+matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)
 # ----------------- #
@@
 Results_Path <- paste(my_path("R"),Jurisdiction,"/",sep="")
-
-# Dataset to match all SAU names
-matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)
 
@@
 
+# STRADDLING
 Clean_Results_Trans <- my_path("R","EEZ","Clean_Results_Trans.csv", read = T) %>% 
@@
   # Convert to 2019 real USD
-  mutate(values = 1.16 * value) %>%
+  mutate(value = 1.16 * value) %>%
   # Average 10 years of data
@@
     model_index >= MI
-  )
+  ) %>% 
+  ## Adding STRADLING component
+  left_join(stradd_hs_spp) %>% 
+  mutate(category = replace_na(category,"transboundary"))
 
@@
 
-## STRADLING
-shared_species <- Tresholded_T_Data %>% 
-  left_join(stradd_hs_spp) %>% 
-  mutate(category = replace_na(category,"transboundary"))
-
-shared_classification <- shared_species %>% 
-  select(taxon_key,category,sf_eez_name) %>% 
-  unique()
+# shared_classification <- shared_species %>% 
+# select(taxon_key,category,fishing_entity_id) %>% 
+# unique()
 
@@
 
-EEZIDs_List <- my_path("Spa","DBEM", "Updated_EEZList_17June2016.xlsx", read = T) %>% 
-  rename(eez_name = name)
-
-# Econ value
-Summary_Trans <- SAU_Sampled_Data %>% 
+stradd_hs_fentity <- stradd_hs_spp %>% 
+  group_by(taxon_key,category, fishing_entity_id) %>% 
+  tally() %>% 
+  select(-n)
+
+# Econ value WITHOUT HIGH SEAS!!!
+Summary_Stradd <-
+  SAU_Sampled_Data %>% 
   semi_join(Tresholded_T_Data,
@@
   ) %>% 
+  left_join(stradd_hs_fentity,
+            by = c("taxon_key","fishing_entity_id")
+  ) %>%
+  mutate(Category = ifelse(is.na(category),"trans",category)) %>%
+  group_by(Variable,Category) %>%
+  summarise(Category_Total = sum(Value, na.rm=T))
+
+Summary_Stradd %>% 
   group_by(Variable) %>% 
-  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
-  left_join(Total_SAU_Sampled) %>% 
-  left_join(Total_SAU_Global) %>% 
-  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
-         Per_SAU = Total_Trans/Total_Global*100)
+  summarise(Total_Trans = sum(Category_Total)) %>% 
+  left_join(Summary_Stradd,
+            by = "Variable") %>% 
+  mutate(
+    percentages = (Category_Total/Total_Trans)*100
+  )
+
+# Econ value WITH HIGH SEAS!!!
+
+# Used for STRADDLING too
+SAU_hs_Data <- bind_rows(
+  my_path("G","SAU/SAU HighSeas 18,48,34,27,21,47 v48-0","SAU HighSeas 18,48,34,27,21,47 v48-0.csv",read = T),
+  my_path("G","SAU/SAU HighSeas 41,31,58,57,51,88 v48-0","SAU HighSeas 41,31,58,57,51,88 v48-0.csv",read = T),
+  my_path("G","SAU/SAU HighSeas 77,67,61,87,81,71 v48-0","SAU HighSeas 77,67,61,87,81,71 v48-0.csv",read = T)
+) %>% 
+  rename(taxon_name = scientific_name) %>% 
+  left_join(taxon_list) %>% 
+  filter(
+    taxon_key %in% stradd_hs_spp$taxon_key,
+    year >= 2005 & year <= 2014,
+    catch_type == "Landings",
+    reporting_status == "Reported"
+  ) %>% 
+  # aggregate all gears
+  group_by(area_name,fishing_entity,taxon_key,taxon_name,year) %>%
+  summarise_at(vars("tonnes","landed_value"),
+               .funs = sum,na.rm = T) %>% 
+  group_by(area_name,fishing_entity,taxon_key) %>% 
+  summarise_at(vars("tonnes","landed_value"),
+               .funs = mean,na.rm = T) %>% 
+    #filter only straddling species
+  semi_join(stradd_hs_fentity,
+            by = c("taxon_key")
+  ) %>% 
+  left_join(stradd_hs_fentity_x) %>% 
+  group_by(area_name,fishing_entity,category) %>% 
+  summarise_at(vars("tonnes","landed_value"),
+               .funs = sum,na.rm = T) %>% 
+  gather("variable","value",tonnes:landed_value)
+
+stradd_hs_fentity_x <- stradd_hs_fentity %>% 
+  group_by(taxon_key,category) %>% 
+  tally()
+
+SAU_hs_Data %>% 
+  group_by(variable,category) %>% 
+  summarise_at(vars(value),sum) %>% 
+  mutate(val_million = value/1000000)
+
+```
+
+## Figures straddling
+
+### MAP straddling
+
+```{r}
+
+World_sf_si <- World_sf %>%
+  st_transform(crs = 4326) %>% # 4326
+  st_simplify(preserveTopology = TRUE, dTolerance = 100)
+
+plot_eez <- stradd_data %>% 
+  group_by(eez_name = territory,category) %>% 
+  summarise(
+    n_species = length(unique(taxon_key))
+  )
+
+plot_fao <- stradd_data %>% 
+  group_by(fao_name,category) %>% 
+  summarise(
+    n_species = length(unique(taxon_key))
+  )
+
+# FAO
+
+fao_regions <- my_sf("FAO") %>% 
+  filter(F_LEVEL == "MAJOR") %>% 
+  select(fao_name= NAME_EN,geometry = the_geom) %>% 
+  left_join(plot_fao) %>% 
+  filter(!is.na(category))
+
+eez_regions <- World_sf %>% 
+  left_join(plot_eez) %>% 
+  filter(!is.na(category))
+
+st_crs(fao_regions) = 4326
+fao_regions <- st_transform(fao_regions, crs = "+proj=eck4")
+
+plot <-ggplot() +
+  geom_sf(data = fao_regions, aes(color = n_species, fill = n_species)) +
+  geom_sf(data = eez_regions, aes(fill = n_species), color = "grey30") +
+  geom_sf(data = World_land_sf, aes(), fill = "grey") +
+  scale_fill_viridis() +
+  scale_color_viridis() +
+  facet_wrap(~category) +
+  my_ggtheme_m(leg_pos = "bottom")
+
+ggsave(
+  plot = plot,
+  width = 17,
+  height = 15,
+  units = "in",
+  filename = "Figures/stradling_maps.png"
+)
+
+```
+
+### Revenue straddling
+
+```{r}
 
